### 2010-05-29 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4971 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}
\special{papersize=8.5in,11in}
\begin{document}

\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\msna{{\rm S/N}^{\rm A}_{912}}
\def\sna{S/N$^{\rm A}_{912}$}
\def\mnull{\nu_{\rm 912}}
\def\nnull{$\nu_{\rm 912}$}
\def\intl{\int\limits}
\def\nstatqso{193}
\def\maxoff{0.4}
\def\clls{1.9 \pm 0.2}
\def\alls{5.2 \pm 1.5}
\def\blls{-0.9^{+0.4}_{-0.05}}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def \mzlls {z_{\rm LLS}}
\def \zlls {$z_{\rm LLS}$}
\def \mzend {z_{\rm end}}
\def \zend {$z_{\rm end}$}
\def \mzstrtt {z_{\rm start}^{\rm S/N^A=2}}
\def \zstrtt {$z_{\rm start}^{\rm S/N^A=2}$}
\def \zstrto {$z_{\rm start}^{\rm S/N^A=1}$}
\def \mzstrto {z_{\rm start}^{\rm S/N^A=1}}
\def \zstrt {$z_{\rm start}$}
\def \mzstrt {z_{\rm start}}
\def\smm{\sum\limits}
\def \lll  {$\lambda_{\rm 912}$}
\def \mlll  {\lambda_{\rm 912}}
\def \mtll  {\tau_{\rm 912}}
\def \tll  {$\tau_{\rm 912}$}
\def \mavtll  {<\mtll>}
\def \tigm  {$\tau_{\rm IGM}$}
\def \mtigm  {\tau_{\rm IGM}}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \ob {$\Omega_b$}
\def \obh {$\Omega_bh^{-2}$}
\def \om {$\Omega_m$}
\def \ol {$\Omega_{\Lambda}$}
\def \gz {$g(z)$}
\def \mgz {g(z)}
\def \lyaf {Lyman--$\alpha$ forest}
\def \fnhi {$f(\mnhi,X)$}
\def \mfnhi {f(\mnhi,X)}
\def \myfnhi {f_{\rm Ly\alpha}(\mnhi,X)}
\def \yfnhi {$f_{\rm Ly\alpha}(\mnhi,X)$}
\def \lfnhi {$f_{\rm LLS}(\mnhi,X)$}
\def \dfnhi {$f_{\rm DLA}(\mnhi,X)$}
\def \sfnhi {$f_{\rm SLLS}(\mnhi,X)$}
\def \mlfnhi {f_{\rm LLS}(\mnhi,X)}
\def \mdfnhi {f_{\rm DLA}(\mnhi,X)}
\def \msfnhi {f_{\rm SLLS}(\mnhi,X)}
\def \ztot {$\Delta z_{\rm TOT}$}
\def \mztot {\Delta z_{\rm TOT}}
\def \mlplls {\ell_{\rm{PLLS}}(z)}
\def \lplls {$\ell_{\rm{PLLS}}(z)$}
\def \mlzlls {\ell_{\rm{LLS}}(z)}
\def \lzlls {$\ell_{\rm{LLS}}(z)$}
\def \mllls {\ell_{\rm{LLS}}(X)}
\def \llls {$\ell_{\rm{LLS}}(X)$}
\def \ldla {$\ell_{\rm{DLA}}(X)$}
\def \lslls{$\ell_{\rm{SLLS}}(X)$}
\def \mlslls{\ell_{\rm{SLLS}}(X)}
\def \nlls {$n_{\rm LLS}$}
\def \slls {$\sigma_{\rm LLS}$}
\def \mnlls {n_{\rm LLS}}
\def \mslls {\sigma_{\rm LLS}}
\def \drlls {$\Delta r_{\rm LLS}$}
\def \mdrlls {\Delta r_{\rm LLS}}
\def \mlmfp {\lambda_{\rm mfp}^{912}}
\def \lmfp {$\lambda_{\rm mfp}^{912}$}
\def \mbplls {\beta_{\rm pLLS}}
\def \bplls {$\beta_{\rm pLLS}$}
\def \btlls {$\beta_{\rm LLS}$}
\def \mbtlls {\beta_{\rm LLS}}
\def \lteff {$\tau_{\rm eff,LL}$}
\def \teff {$\tau_{\rm eff,LL}$}
\def \tlya {$\tau_{\rm eff}^{\rm Ly\alpha}$}
\def \mtlya {\tau_{\rm eff}^{\rm Ly\alpha}}
\def \mteff {\tau_{\rm eff}}
\def \mllteff {\mteff^{912}}
\def \llteff {$\mteff^{912}$}
%\def \llsteff {$\tilde\mtll$}
%\def \mllsteff {\tilde\mtll}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}
\def\mglls {\gamma_{\rm LLS}}
\def\mavgt {<\mtll>}

\title{The SDSS-DR7 Survey for Lyman Limit Systems}

\author{
J. Xavier Prochaska\altaffilmark{1}, 
John M. O'Meara\altaffilmark{2}, 
Gabor Worseck\altaffilmark{1} 
%\& Scott Burles\altaffilmark{3}
}
\altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of California, 1156 High Street, Santa Cruz, CA 95064}
\altaffiltext{2}{Department of Chemistry and Physics, Saint Michael's College.
One Winooski Park, Colchester, VT 05439}

\begin{abstract}
We present the results from a survey for Lyman limit system absorption in the Sloan Digital Sky Survey, Data release 5.  I like abstracts, they are fun!
\end{abstract}

\keywords{absorption lines -- intergalactic medium -- Lyman limit systems -- SDSS}

\section{Introduction}
% JO: Introduce LLS
% JO: Mention previous surveys.
% JO:  Leads into survey size \& bias.
Studies of hydrogen  absorption in the lines of sight towards 
distant quasars have served to both define, and in recent years bring
precision to, our cosmological models for the universe.  
The low density, highly ionized  \lyaf\ lines (a.k.a.\ the intergalactic
medium, IGM), with 
\ion{H}{1} column densities $\mnhi < 10^{17.2} \cm{-2}$,
through their aggregate statistical properties (e.g.\ their
flux power spectrum, mean flux, and column density distributions)
constrain cosmological parameters such as the primordial power spectrum
and the baryonic mass density
\citep[e.g.][]{rau98,cwb+03,mcdonald05,tytler04,fpl+08}.
The high-density, predominantly neutral damped \lya\ systems (DLAs),
with $\mnhi \ge 10^{20.3} \cm{-2}$, trace the gas which forms stars, and
likely represent the progenitors of modern-day galaxies 
\citep[e.g.][]{wlf+95,wgp05,pw09}.

The majority of \lyaf\ lines and the DLAs have, through
analysis of their \lya\ lines, precisely measured \nhi\ values
that permit detailed study of their physical propertiees (e.g.\ metallicity).
For systems with intermediate \nhi\ values ($\approx 10^{18} \cm{-2}$),
however, \lya\ and most of the Lyman series lines lie on the
flat portion of the curve-of-growth and the \nhi\ value is difficult
to cosntrain.
On the other hand, these systems are optically thick to ionizing
radiation and impose a readily identify spectral signature in a quasar
spectrum at the Lyman limit.
These so-called Lyman limit systems (LLS), currently the least-well
studied of \ion{H}{1} absorption systems at high redshift,
are the focus of this manuscript.

Historically, the LLS were among the first class of quasar
absorption line (QAL) systems to be surveyed \citep{tytler84}.
This is because their spectral signature is easy to identify
even with low-resolution, low S/N spectra.  The principal challenge
is that the Lyman limit occurs redward of the atmospheric
cutoff only for systems (hence quasars) with redshifts $z>2.7$.
For lower redshifts, one requires spectrometers on space-bourn
ultraviolet sattelites.
By the mid 1990's, samples of several tens of LLS were generated
spanning redshifts $z 0 - 4$ \citep{ssb89,lzt9X,stengler95,storrie96}.
These results were derived from heterogeneous sets of quasars discovered
from a combination of color-selection, radio detection, and
spectroscopic surveys.    The spectra, too, was acquired with a 
diverse set of instrumentation and therefore varying S/N and spectral
resolution mitigating differing sensitivity to the precise optical
depth at the Lyman limit.  Although the results were not fully
consistent with one another, the general picture that resulted
was a rapidly evolving population of absorption systems reasonably
described by a $(1+z)^{1.5}$ power-law.

Cosmologically, the LLS contribute much if not most of the universe's
opacity to ionizing radiation.  Until recently, the observed incidence
of the LLS provided the only direct means of estimating the mean
free path \lmfp\ at any redshift \citep[e.g.][]{meiksin,madau99,fg08b}.
In a companion paper \citep{pwo09}, we have presented a new
technique to measure the \lmfp\ that circumvents any knowledge
of the LLS.  A more precise census of the LLS will serve as a 
consistency check for this \lmfp\ calculation, but is unlikely to
ever again be a competitive approach.  Instead, the incidence of LLS
can be used in combination with estimates of \lmfp\ to assess the
\nhi\ frequency distribution for gas 
with $\mnhi \approx 10^{16-18} \cm{-2}$, 
a regime that is very difficult to explore by studying individual
absorption systems.   Surveys of the LLS are also likely to 
place tight constraints on $z \sim 3$
cosmological simulations that include radiative transfer.

Physically, the nature of systems that give rise to LLS remains
an open question.  The systems with the largest \nhi\ values
(i.e.\ $\mnhi \ge 10^{19} \cm{-2}$, the so-called the super-LLS and
DLAs) are likely associated with the interstellar medium and
outer regions of high $z$ galaxies.  These high \nhi\ systems, however,
are only a subset of the LLS population.  Unfortunately, a proper
modeling of the LLS almost certainly requires careful modeling of 
radiative transfer which has thus far been beyond the scope of
modern computations.  Indeed, the few studies to date have tended
to severely underestimate the incidence of LLS \citep{katz94,gardnerXX,gnedin}.
In recent simulations of high $z$ galaxy formation, however, 
theorists have placed great attention on `streams' of cold gas that
carry fresh material from the IGM to star-forming galaxies 
\citep{keres99,dekel08}.  These cold streams have relatively large
surface densities ($N_{\rm H} \sim 10^{20} \cm{-2}$) and could therefore
produce Lyman limit absorption provided the material has a
non-negligible neutral fraction.  Consequently, an accurate census
of the LLS with redshift may directly constrain the nature and
prevalence of cold streams in the young universe.

A final, yet perhaps most important, motivation for studying the LLS
is that these systems may dominated the census of metals at all epochs.
The majority of LLS are metal-bearing, showing metal-line transitions of 
common low and high-ions \citep[e.g.][]{p99,pks2000}.
Because the estimated ionization corrections for LLS with 
$\mnhi \approx 10^{18} \cm{-2}$ is large, the observations likely
track only a trace amount of the metals.  [last comment]

[Add shot in the dark(s)?]

In this paper, we survey the homogeneous dataset of quasar
spectra from the Sloan Digital Sky Survey (SDSS), using all 
7 public data releases.  Our observational analysis
aims to produce the most precise measurement of 
the LLS incidence paying careful attention to systematic
biases.  The wavelength coverage and data quality of the SDSS
quasar spectra focusing the survey to $z \approx 3.5$.  Future
work will depend on follow-up obseravtions of well-define
quasar samples at other wavelengths.

The paper is organized as follows.  In $\S$~\ref{sec:def},
we present a set of LLS defintions used throughout the manuscript.
We adopt a cosmology with 
$H_0 = 72 \, h_{72} \, \mkms \, \rm Mpc^{-1}$, 
$\Omega_{\rm m} = 0.3$, and $\Omega_\Lambda = 0.7$
and report proper lengths unless specified.

\section{Lyman Limit System Definitions}
\label{sec:def}

The cross-section of \ion{H}{1} at energies above the Lyman limit
may be approximated by:

\begin{equation}
\sigma_{\rm LL}(\nu \ge \mnull) \approx  
  6.35 \sci{-18} \ltp \frac{\nu}{\mnull} \rtp^{-3} \; \cm{2} \cmma
\end{equation}

\begin{equation}
\mnull = E_{912}/h = c/\mlll \cmma 
\end{equation}

\noindent $E_{912} = 1$\,Ryd.  Specifically, 
$\nu_{\rm LL} = 3.29 \sci{15}$Hz and 
$\mlll = 911.7641$\AA.
This implies a continuum opacity at wavelengths $\lambda \le \mlll$,

\begin{equation}
\mtll(\lambda \le \mlll) \approx \frac{\mnhi}{10^{17.2} \cm{-2}} \ltp 
   \frac{\lambda}{\mlll} \rtp^{-3} \cmma
\end{equation}
where \nhi\ is the \ion{H}{1} column density. 
For a gas `cloud' intersecting a background source with intrinsic flux
$F_{\rm int}(\lambda)$, the observed flux $F_{\rm obs}(\lambda)$
blueward of the Lyman limit is

\begin{equation}
F_{\rm obs}(\lambda \le \mlll) = 
  F_{\rm int}(\lambda) \exp \ltk -\mtll(\lambda) \rtk
\label{eqn:flux}
\end{equation}

In what follows, we will define a `standard' Lyman limit system (LLS) to be
one where $\mtll \ge 2$, i.e.\ $\mnhi \ge 10^{17.5} \cm{-2}$.
This corresponds to greater than 85\%\ attenuation of an 
incident ionizing radiation field. 
By this definition, the class of LLS includes systems with
$10^{20.3} \cm{-2} \le \mnhi \le 10^{19} \cm{-2}$ 
\citep[the so-called super-LLS or sub-DLAs; e.g.][]{opb+07} and systems with
$\mnhi \ge 10^{20.3} \cm{-2}$ \citep[the damped \lya\ systems; e.g.][]{wgp05}.
In a few cases, we will distinguish between these `strong' LLS from 
those with lower \nhi, referring to the latter as LLS.
We also note that our $\mtll \ge 2$ definition for LLS differs
from other works which adopted $\mtll \ge 1$ or $\mtll \ge 1.5$.
Unfortunately, there is no well-established criterion.

Observationally, the absorption of a background source
by a $\mtll \ge 2$ LLS is 
readily apparent, even in low S/N spectra.
We define absorbers with $\mnhi < 10^{17.5} \cm{-2}$ as the 
partial Lyman limit systems (pLLSs).  To survey these systems,
one requires higher quality spectra or an alternate approach to the analysis.

We define the redshift of an LLS as

\begin{equation}
\mzlls \equiv \frac{\mlll^{\rm LLS}}{\mlll} - 1
\end{equation}
where $\mlll^{\rm LLS}$ marks the observed onset of LL absorption.
In practice, this is is often estimated from strong Lyman series lines
(e.g.\ \lya, \lyb) that accompany the Lyman limit opacity.

We define the sub-set of LLS that occur within 3000\kms\
of the emission redshift of the background source as proximate LLS
(PLLS).  We separate the analysis of these systems from the rest
to investigate changes in the incidence of optically thick gas
near high $z$ quasars due to, e.g.\ the quasar's radiation field
and local environment $\S$~\ref{sec:prox}.

Finally, we define the observable \lzlls\ as the average
number of LLS detected per unit redshift at a given redshift.
In the previous literature, this quantity is also expressed
as $n(z)$, $dN/dz$ and $dn/dz$.

\section{SDSS Quasar Sample and Spectroscopy}

One of the primary objectives of the Sloan Digital Sky Survey (SDSS)
was to discover $\sim 100,000$ new quasars across the northern sky
\citep{yaa+00}.  The strategy of the SDSS team to achieve this
ambitious goal was a four-fold process:
(i) obtain deep, multi-band images across a large area of the sky;
(ii) select quasar candidates by demanding a point-like point-spread-function
and imposing color criteria that separate the candidates from the
Galactic stellar locus;
(iii) obtain follow-up spectra for a magnitude-limited sample
with a fiber-fed spectrograph.
The details of target selection and quasar completeness with
redshift is described at length in a series of SDSS papers
\citep{rfn+02}, but see \citep{wp09} for a new and more accurate analysis;  
and
(iv) automatically identify quasars and estimate their redshifts
(\zem) through template fitting to the optical spectroscopy.

Of these steps, the second has the greatest 
impact on a survey for high $z$ Lyman limit systems. 
The key issue for our survey is whether the presence 
of an intervening LLS biases the targeting of the
background quasar for follow-up spectroscopy.  
In effect, a high $z$ LLS severely `reddens' the quasar
at the bluest optical wavelengths of the SDSS imaging.  
With this effect in mind, the SDSS team imposed cuts
on the $(u-g)$ color which better separated the quasar
locus in color pace from the stellar locus.  The net effect,
however, is to bias the spectroscopic follow-up against 
quasar sightlines {\it without} foreground LLS
\citep[][hereafter PWO09]{pwo09}.  Our analysis indicates
an important bias for quasars with $\mzem < 3.6$. 
For this reason, we will limit the statistical analysis
to quasars with $\mzem \ge 3.6$, but we also explore this bias
by considering the incidence of LLS toward quasars with $\mzem = 3.4 - 3.6$.

The quasar spectra analyzed in this paper were taken from the Sloan
Digital Sky Survey, Data Release 7 \citep{sdssdr7}.  
We retrieved
the `best' 1D spectrum for every source flagged as a QSO or HIZ\_QSO.
This totalled 102,418 unique spectra\footnote{  
The spectra were processed through our automated algorithms for
finding absorption-line features and damped \lya\ candidates
\citep{phw05,shf06}.  
Approximately 10 of the spectra failed 
to be processed (primarily because the SDSS-repoted emission redshift
is erroneous) and were removed from any subsequent analysis.}.
The SDSS survey employs a 
fiber-fed, dual-camera spectrometer that provides continuous wavelength coverage
from $\lambda \approx 3800-9200$\AA\ at a spectral resolution of 
FWHM~$\approx 150 \mkms$.
The SDSS team employs a custom, data-reduction pipeline that performs
sky subtraction using emprical measurements from fibers placed
to avoid objects detected in the SDSS images.
The majority of data suffer from excessive sky noise at long
wavelengths ($\lambda > 8000$\AA)
and the instrument throughput and atmospheric absorption
limits the sensitivity at the shortest wavelengths ($\lambda < 4200$\AA).

A survey for \ion{H}{1} Lyman limit absorption in quasar spectra
invovles two principle steps.  First, one must assess
the flux at wavelengths near the Lyman limit
in the quasar's rest-frame, $\lambda \lesssim \mlll(1+\mzem)$.  
We discuss our procedure for this step in the following section.  
The second step is to 
estimate the flux at wavelengths blueward of LLS candidates.
There are several characteristics of the SDSS spectroscopy which
negatively affect this estimate.  A generic concern is the poorer instrument
response at the bluest wavelengths.  At the bluest wavelengths,
many of the spectra exhibit a very low signal-to-noise ratio 
and yield flux estimates consistent with zero, even without an
intervening LLS.
Therefore, we have limited our survey to redshifts $\mzlls \ge 3.3$
corresponding to $\lambda > 3920$\AA.
In practice, we restrict the quasar sample to objects with
$\mzem \ge 3.6$ and perform a search for LLS
at all redshifts, but then only analyze absorption systems with
$\mzlls \ge 3.3$.  We also limit the survey to quasars with
$\mzem \le 5$ because the SDSS spectra of higher redshift objects
are generally too low S/N to permit a robust analysis.
Figure~\ref{fig:snz}a presents histograms of the emission redshifts
for the statistical sample and the signal-to-noise of the
absorbed continuum at the Lyman limit
(\sna; see below for the definition).

Another difficulty with the SDSS spectra at blue wavelengths
is that the two-dimensional spectra of faint sources may be improperly traced.
On occasion, the 1D extractions
include flux from a neighboring object and yield a systematic 
overestimate of the flux.  This effect reduces the estimated opacity
for a LLS.  
Another issue, especially with a fiber-fed spectrometer, is that
the sky model is estimated from nearby fibers that are intentionally
placed on `object-free' regions of the sky.  Although the SDSS
project has worked carefully to mitigate the effects of variable
fiber efficiency and XXX \cite{skysub},  significant misestimates 
of the sky occur.  
We have identified tens of objects where the extracted
flux is significantly negative, indicating an overestimate
in the sky model.  
This may convert a partial LLS (with $\mtll < 1$) into
an LLS.  By a similar token, a proper $\mtll \ge 2$ LLS may
appear as a pLLS if the sky is underestimated.
We proceed under the expectation that this effect
is nearly random, i.e.\ for every underestimate of the sky there
is a corresponding overestimate, but this has not been rigorously
established.  
The SDSS fibers are sufficiently wide
(diameter of $3''$) that they will occasionally include flux
from a projected neighbor.  These coincident objects may be
much fainter than the quasar at redder wavelengths, but they
could contribute all of the flux blueward of a strong LLS
and lead to an underestimate of the LL opacity\footnote{An amusing
(and plausible) systematic effect related to this is contamination
by the light reflected from terestrial satellites crossing the night sky.  
Even a brief `exposure' through the 3$''$ fiber could dominate the
flux at the bluest wavelengths, although this should generally be
mitigated by the fact that the SDSS team aquires 
3 unique exposures per target.}.

\section{The Absorbed Quasar Continuum}
\label{sec:continuum}

Absent any other sources of opacity, one can trivially
estimate \tll\ from
the quasar spectrum through measurements of the flux
both redward and blueward of the observed Lyman limit (Equation~\ref{eqn:flux}).  
In practice, however,
the quasar flux is also attenuated by line opacity from the so-called
\lya\ forest (a.k.a., the intergalactic medium; IGM).
For example, consider a Lyman limit system at $\mzlls = 3.5$
intervening a $\mzem = 4$ quasar.  The LLS attenuates the quasar flux
blueward of $\mlll^{\rm LLS} = 4103$\AA.  At this wavelength,
the quasar spectrum recorded on Earth will also include opacity
from the \lya\ forest at 
$z_{\rm \mlya} = (1+\mzlls)(\mlll/\lambda_{\rm Ly\alpha}) - 1$,
\lyb\ absorption from the IGM at 
$z_{\rm Ly\beta} = (1+\mzlls)(\mlll/\lambda_{\rm Ly\beta}) - 1$, etc.
It is necessary, therefore, to account for these additional sources
of opacity when estimating \tll.

We can express
the observed quasar flux $F_{\rm obs}$ in terms of
the intrinsic flux (just) redward of the Lyman limit $F_{\rm int}$ as

\begin{equation}
F_{\rm obs} (\lambda \gtrsim \mlll) = F_{\rm int} \exp [-\mtigm(\lambda)] \cmma
\end{equation}
where \tigm\ is the effective opacity of the IGM from
Lyman series line-opacity\footnote{In the following, we do not
explicitly derive the 
opacity from metals in the IGM, but these may be considered included in \tigm.}.
The LLS introduces an additional, continuous opacity:

\begin{equation}
F_{\rm obs} (\lambda \le \mlll) = 
  F_{\rm int} \exp [-\mtigm(\lambda) -\mtll(\lambda)] \perd
\end{equation}
A precise estimate of \tll, therefore, requires an estimation
of the absorbed quasar flux not its intrinsic flux.  Conveniently,
this quantity is the observed flux recorded in the spectrum at
$\lambda \gtrsim \mlll$.  
There are still signficant challenges because
the IGM opacity is stochastic on both small (individual Lyman lines)
and modest scales (many 10\AA) 
and 
the intrinsic quasar spectrum (both shape and normalization) varies
from source to source.
We now describe an automated procedure
used to infer the absorbed continuum from each quasar spectrum.

The traditional method of estimating the
quasar continuum is to first identify
regions of unabsorbed quasar flux and then to interpolate a continuum level
between these regions.  For quasars at
high redshift, this method is particularly error prone, because at
wavelengths below \lya\ emission we expect few (and at very
high redshift, none) of the pixels to be free
of absorption from the IGM.   Moreover, this
traditional method frequently requires by-hand modification,
which is time-intensive and subjective to individual biases.
Methods do exist to automatically generate a quasar
continuum from emission-line characteristics \citep[e.g.][]{suzuki+05},
but these are designed to infer the intrinsic quasar spectrum
not the IGM-absorbed continuum.
Our approach is to match a template model of the average absorbed
continuum to each spectrum,
allowing for a large-scale tilt (i.e. a unique underlying power-law slope)
and arbitrary normalization.

Our first step is to derive the templates for the average absorbed
quasar continuum.  Because the line-density of the IGM and therefore \tigm\
increase with redshift, we perform this analysis in small redshift intervals
($\delta z = 0.3$ to 0.6; Figure~\ref{fig:template}). 
For every quasar within the redshift interval,
we shift the spectrum to the quasar rest-frame 
using the SDSS reported \zem\ value.  
Next, we "detilt" the spectrum by removing a power-law shape.
This power-law is determined as follows.  We have
constructed from the SDSS-DR3 dataset an average template spectrum,
archived in XIDL\footnote{http://www.ucolick.org/$\sim$xavier/IDL}
as ``full\_SDSS\_LLS.fits''.
For each individual quasar spectrum,
we sample quasar pixels with wavelengths greater 
than \lya\ emission, divide by the template spectrum,
and measure the spectral slope of the resulting spectrum.

After aligning the spectra in the quasar rest-frame
(nearest pixel), we median-combine the data in each redshift 
interval\footnote{This stack is not optimal for deriving \lya\
forest statistics \citep{dlw08}.}.
The resultant template
represents the median intrinsic quasar continuum modulated by the median
flux decrement of the IGM.  Due to the presence of
Lyman limit systems, the quasar templates will not be useful at
wavelengths near and below the rest-frame Lyman limit;
this portion of the spectrum, however, can be used to 
constrain the mean free path to ionizing radiation \citep{pwo09}.
For wavelengths blueward of 920\AA, therefore,
we set the template to have the value recorded 920\AA.
Conveniently, there are no strong emission features in the
quasar SED at these wavelengths \citep[e.g.][]{telfer02}.
The resultant template spectra are shown in Figure \ref{fig:template}.

With the templates constucted, a model of the absorbed continuum
for each quasar is determined as follows.
First, we shift the observed quasar spectrum to the rest-frame
and divide by the appropriate template spectrum (i.e.\ according to \zem).
Second, we sample the quasar in the wavelength range 
$950 \rm \AA < \lambda < 1800 \rm \AA$ and fit a power-law 
(p$(\lambda)$ = A + B log[$\lambda$/\AA]) to the observed 
flux, weighting by the inverse variance array.
The emission lines in this spectral range may bias the fit,
but we do review and modify these fits (see below).
The product of this power-law with the template, when
shifted to the observed frame, provies our model for the
absorbed quasar continuum.  The power-law parameters derived
in this fashion are listed in Table~\ref{tab:quasars}.
Sample fits are shown in Figure~\ref{fig:ex_conti}.
With these models, we can calculate the ratio of the absorbed
continuum to the $1\sigma$-error array at the Lyman limit,
which we denote as \sna.
Figure~\ref{fig:snz}b shows the distribution of \sna\ values
for the statistical survey.

\section{Lyman Limit System Search and Characterization}
\label{sec:lls}

In the following, we parameterize a LLS by two quantities:
(1) the absorption redshift \zlls\ and
(2) the total \ion{H}{1} column density \nhi.
Although the \ion{H}{1} Lyman series lines are sensitive to the component
structure and the Doppler parameters (also known as $b$-values)
of the `clouds' comprising an LLS,
the opacity blueward of \lll\ is insensitive to the details.
Furthermore, the SDSS spectra are generally of too poor quality
to constrain such structure using the observed Lyman series lines.
Therefore, our model of an LLS assumes a single cloud with a 
Doppler parameter of $b=30 \,\mkms$.
An implication of this parameterization is that two systems with
small redshift separation are modeled as a single system with
the total of the \nhi\ values.  Our tests with mock spectra ($\S$~\ref{sec:mock})
indicate that two absorbers with $\delta z < 0.1$ are often
indistinguishable from a single LLS.  The survey presented here,
therefore, refers to LL absorption smoothed over a redshift
interval of $\delta z \approx 0.1$.  We return to this point
in our presentation and discussion of the survey results.

We have developed an algorithm ({\it sdss\_findlls})
to automatically search for
and characterize LLS absorption in quasar spectra.
In brief, the code generates a set of model spectra
for the line and continuum opacity of
a single LLS with redshifts covering 
$z=z_0=(\lambda_0/\mlll-1)$ to (\zem+0.2) where $\lambda_0$
is the starting redshift of the SDSS spectrum and \zem\ is the
quasar emission redshift reported in the DR7\footnote{Modified by
the analysis of \cite{phh08} where applicable for quasars from 
the DR5 release.}.
The grid of models assumes \nhi\ column densities 
$\log \mnhi = 16.0, 16.2, 16.4, ..., 19.8$
and a Doppler parameter $b = 30 \mkms$.  
We implement a grid with 0.2\,dex spacing in \nhi\ because very
few of the spectra have sufficient S/N to provide a more precise
estimate.  Furthermore, we estimate systematic uncertainties
(e.g.\ continuum placement, sky subtraction) to be of this order.
These models are convolved with the SDSS instrumental
resolution and then applied to the absorbed quasar continuum 
($\S$~\ref{sec:continuum}).
Finally, the code constructs a $\chi^2$ grid in \zlls\ and \nhi\
space, identifies the minimum $\chi^2$, and records the `best-fit' values.  
In general, the spectra provide very little constraint
on \nhi\ for values exceeding $10^{17.5} \cm{-2}$ until the \lya\
profile becomes damped \citep[e.g.][]{phw05}.
Therefore, we report lower limits to \nhi\ for any LLS with 
$\mtll \ge 2$.  This approach differs from previous methods
which focused solely on the Lyman limit \citep[e.g.][]{sl94} or
relied on `by-eye' analysis \citep{lzt9X}.

For sightlines with a single LLS having $\mnhi > 10^{17.2} \cm{-2}$
and good \sna\ (i.e.\ greater than 5 pix$^{-1}$ 
at $\mlll^{em} \equiv \mlll \times [1+\mzem]$),
we find that the automated
algorithm is highly successful on its own.
In practice, however, there are several aspects of the data and
analysis that require visual inspection of the spectra
and interactive modification to the model:
First, many spectra have 
such low S/N that \zlls\ and \nhi\ are poorly determined.
In these cases, the a local minimum in $\chi^2$ can occur which
gives a misestimate of these quantities.
Second, the presence of multiple
absorbers along the sightline (e.g.\ one or more pLLS with a lower
redshift LLS) gives a spectrum that cannot be well
modeled by a single LLS.
Third, a non-negligible number of the spectra
retrieved from the SDSS database purported to be high $z$
quasars are either at a lower redshift or some other astronomical
object altogether.  
Fourth, we found that half of the absorbed continuum models required
scaling to higher or lower value by greater than $10\%$.  
Finally,  we prefer to avoid quasars with 
with strong broad absorption line (BAL) or associated systems
to focus the analysis on intervening LLS.

Given the above complications to an automated analysis, we
built a graphical user interface (GUI) within the IDL software
package ({\it sdss\_chklls}; bundled within XIDL)
that inputs the data and best-fit LLS model for each object.
Two of the authors (JXP and JMO) used this GUI to validate
and/or modify all of the models.  These authors 
flagged erroneous spectra (159 examples), 
strong BAL or associated absorption (quasars showing very strong
\ion{C}{4}, \ion{N}{5}, and \ion{O}{6} absorption; 290 quasars), 
or data with such low
S/N that any analysis was deemed impossible (114 spectra).
For the remainder of sightlines, the authors
could modify the continuum (via a multiplicative scalar; Table~\ref{tab:quasars})
and/or change the model of LLS absorption (i.e.\ \zlls, \nhi).
This includes absorption due to candidate pLLS.  
In many cases, \zlls\ was modified to correspond to the strongest,
local \lya\ absorption line at $\lambda = (1+\mzlls) \times 1215.67$\AA,
especially for those systems that also showed absorption at the
expected wavelength for \lyb.

After every sightline was analyzed in this manner,
the results from the two authors were compared to assess
consistency.  Roughly half of the spectra were reviewed
because of conflicts in the models.
The majority of these were associated 
with the absorbed continuum placement which implied 
differences in the search path of $|\Delta z| > 0.1$
(see $\S$~\ref{sec:path}).
In the majority of these cases, we simply averaged the
two estimations of the continuum.  
The second most frequent conflict was on the definition
of strong BAL absorption, primarily because we did not adopt
uniform or strict criteria.  In most cases, we 
conservatively excluded the sightline.
There were also $\approx 100$ cases where one author estimated
$\log \mnhi = 17.4$ when the other estimated   
$\log \mnhi = 17.6$, i.e., straddling the $\mtll=2$ boundary
that defines our LLS search. 
These were especially scrutinized for the presence of
higher-order Lyman series lines. 
Where necessary, the final best-estimate for \nhi\ was 
deferred to the third author (GW).

Tables~\ref{tab:survey} and \ref{tab:llscand} list the set of 
Lyman limit systems identified in the SDSS-DR7 for systems
that (respectively) influence our statistical analysis and otherwise. 
For each system, we list our best estimate for \zlls\ and the \nhi\ value.
Because the data offer minimal constraint on \nhi\
for values exceeding 10$^{17.6} \cm{-2}$,
in the statistical sample we only report a lower
limit to \nhi\ for all systems with best-estimates of
$\mnhi \ge 10^{17.6} \cm{-2}$. 
For the pLLS, the typical $1\sigma$ uncertainty
is approximately 0.2\,dex for $\mnhi \ge 10^{17} \cm{-2}$
and is dominated by systematic error in
the continuum placement and the stochastic nature of the IGM opacity. 
As noted above,
\zlls\ was frequently modified
in the interactive analysis to correspond to strong \lya\ and
\lyb\ lines.
Our analysis of mock spectra indicate typical redshift
uncertainies of $\sigma(z) < 0.02$ with occasional
`catastrophic failures' due to line-blending or spurious
spectra (Appendix~\ref{appx:mock}).
No attempt was made to improve this
estimate by searching for the presence of metal-line
absorption (e.g.\ \ion{C}{4}) outside the \lya\ forest.
There is a tendency, both in the automated algorithm and in 
interactive analysis, to set \zlls\ at the highest value possible
that can be accomodated by the data.  To this extent, we suspect
that there is a modest bias in our \zlls\ values to slightly
higher redshifts (less than 0.01 on average, but with
the occasional large offset).

Figure~\ref{fig:ex_conti} shows a representative sample of four quasar
spectra, zoomed into the region blueward of \lyb, with the
absorbed continuum and LLS models indicated. 
We provide snapshots of the 
LL region for all quasar spectra in the statistical sample 
online\footnote{http://www.ucolick.org/$\sim$xavier/SDSSLLS}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Survey Path}
\label{sec:path}

Analagous to galaxy surveys where one defines a search
volume based on the depth of imaging and spectroscopic
follow-up, measurements of the incidence of quasar absorption line systems
requires an estimate of the total spectral path sensitive 
to a robust search.  This is generally referred to as the redshift
path covered (by translating observed wavelength into redshift).
For the survey of LLS, we have adopted the following criteria
for including spectral regions in the search.  These are based on our 
automated and interactive analysis of the SDSS spectra, 
our modelling of Keck/LRIS follow-up spectra, and our analysis
of simulated spectra ($\S$~\ref{sec:mock}, Appendix~\ref{appx:keck}):

\begin{enumerate}
\item The search path will begin at a minimum redshift of
  $z_{\rm start} \ge 3.3$
\item For the intervening LLS sample, the search path ends at the redshift
  $z_{\rm end}$
  corresponding to 3000~\kms\ (relativistic) blueward of \zem.
\item The absorbed continuum flux must exceed twice the estimated error array, 
 i.e.\ \sna.
\item The search path begins at a maximum offset of 
   $\delta z = \mzem - z_{\rm start} \le 0.4$.
\end{enumerate}
The first criterion is motivated by the starting wavelength 
of the SDSS spectra ($\lambda_0 \approx 3800$\AA) and the
poorer quality of the data at the bluest wavelengths.
For redshifts less than 3.3, there is insufficient spectral
coverage and/or data quality to confidently assess the
presence of an LLS.  The second criterion minimizes
the influence of the quasar and its environment on
the analysis.  This criterion is relaxed in the study of PLLS.

The third criterion is the most subjective, yet important,
for setting the redshift survey path of each quasar.
Algorithmically,  we impose this constraint by identifying
the first pixel blueward of $\mlll^{\rm em} \equiv \mlll(1+\mzem)$
where our model of the absorbed quasar continuum falls
below twice the median-smoothed (15 pixels) $1\sigma$ error array. 
This pixel defines the starting redshift \zstrtt\ corresponding
to a \sna=2 limit.  
If the first pixel blueward of $\mlll^{\rm em}$ does not satisfy
the S/N threshold, the quasar has zero redshift path, 
i.e.\ $z_{\rm start} = z_{\rm end}$.
One can, of course, define 
starting redshifts
corresponding to higher (or lower) \sna\ limits;  indeed, our
fiducial choice of \sna=2 should be considered arbitrary, although 
it is guided by our analysis of real and simulated spectra.
And to avoid a systematic bias associated with pLLS (see $\S$~\ref{sec:pLLS}),
one must choose the \sna\ criterion to be sufficiently high
to discover $\mtll \ge 2$ LLS even in the presence of a 
pLLS\footnote{Contrary to some of the earliest work 
on LLS \citep[e.g.][]{tytler84},
we do not use surival statistics to estimate the number of LLS
at redshifts below any observed LLS.}.
We investigate the impact of this choice on our results
later in the manuscript.

The starting redshift is further modified by the presence 
of Lyman limit absorption.  In the case of a $\mtll \ge 2$ absorber,
the quasar flux is severely depressed below $\lambda = \mlll (1+\mzlls)$
and we terminate the search path at this wavelength.  
Specifically, this implies $z_{\rm start} \ge \mzlls$ for all
sightlines with an $\mtll \ge 2$ LLS.
For sightlines where one or more pLLS are identified\footnote{Again,
all pLLS should be considered candidates.  Some of the spectral
features modelled as pLLS are instead due to unusual variations
in the absorbed quasar continuum (e.g.\ highly reddened quasars).}, 
we had originally intended to terminate the search once the absorbed 
quasar continuum convolved with the pLLS absorption failed to satisfy
the S/N threshold.  In our analysis of mock spectra, 
however,  we found that this introduces a ``pLLS-bias'' where the
incidence of $\mtll \ge 2$ LLS is overestimated.
In part, our \sna=2 threshold is chosen so that one can 
robustly search for $\mtll \ge 2$ LLS even along sightlines where
one or more pLLS are present.

Table~\ref{tab:survey} presents the list of quasars in SDSS-DR7
that 
(i) have $5 \ge \mzem \ge 3.6$, 
(ii) were not identified to
exhibit strong BAL signatures, and 
(iii) have $3.3 \le \mzstrtt < \mzem$.
There are \nstatqso\ quasars satisfying these criteria.
For each sightline, we list the starting redshifts for
\sna=2 and 3 limits.
We report results for two values of the S/N threshold to
search for data-quality biases. 
Table~\ref{tab:survey} also lists all Lyman limit systems
with $\mzlls \ge \mzstrtt$.  
We do list these quantities for quasars with $\mzem < 3.6$,
but these were not included in our final statistical analysis
because of the bias related to SDSS targeting criteria
previously mentioned by \citep{pwo09}.

Using the values presented in Table~\ref{tab:survey}, it is
straightforward to calculate \zend\ and the redshift search
path for each quasar: $\Delta z_i = \mzend - \mzstrt$.  For
a given \sna\ limit, the total search path for the full dataset is

\begin{equation}
\Delta z_{\rm TOT} = \smm \Delta z_i  \perd
\end{equation}
We calculate $\mztot^{S/N=2} = 96$.
%of XX increase over the combined search paths of all previous
%$z>2$ surveys for LLS \citep{peroux05}.
To maintain a homogeneous sample and set of search criteria,
we do not include previous studies in our analysis.
We compare against previous results in $\S$~\ref{sec:discuss}.

In Figure~\ref{fig:goz}, we present the sensitivity function
\gz\ which expresses the number of SDSS quasars at redshift $z$
where a robust search for LLS is possible.
The several solid curves represent differing \sna\ limits for the survey.
We also present the sensitivity function for proximate LLS (PLLS)
which corresponds to the sample of quasar spectra that satisfy
the $\msna \ge 2$ criterion at 3000~\kms\ blueward of \zem.

With the definition of the search path 
and the identification of the Lyman limit systems along each
sightline ($\S$~\ref{sec:lls}),
it is straightforward to calculate the incidence of intervening
LLS per redshift interval, \lzlls.  
The standard estimator is to compare the total number of LLS
against the total survey path in discrete redshift intervals.
We will return to evaluate \lzlls\ and discuss the values
after exploring several sources of systematic error.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Mock Spectra and Systematic Errors}
\label{appx:mock}

With a survey the size of SDSS, one can quickly reduces the statistical
noise in measurements to very small levels.  In this
regime, one must carefully assess all sources of systematic
error as these may dominate the measurement uncertainty.
To this end, we have conducted a range of tests with mock
spectra as described in this section.

\subsection{Mock Spectra Construction}

We generated a set of 800 mock SDSS quasar 
spectra and analyzed them in the same way as the real data in 
order to assess bias and completeness in our LLS survey. 
The \ion{H}{1} forest absorption spectra 
were generated via a Monte Carlo routine similar 
to the one described in \cite{dww08}, 
assuming that the \lya\ forest is well characterized by 
three independent distributions: 
(i) the \lya\
line-incidence $\ell_\alpha (z) \propto (1+z)^\gamma$, 
(ii) the \ion{H}{1} column density distribution $f(\mnhi) \propto \mnhi^\beta$, 
and (iii) the Doppler parameter distribution parameterized as 
$f(b) \propto b^{-5} \exp{-b_\sigma^4/b^4}$ \citep{hr99}. 
Each simulated line of sight was filled with \ion{H}{1} \lya\ absorption lines at 
$2<z<4.6$ until the \ion{H}{1} \lya\ effective optical depth was consistent with 
\cite{fpl+08}, both in normalization and redshift evolution. We did not model the 
$z\sim 3.2$ dip in the effective optical depth 
measured by Faucher-Giguere et al., 
and instead adopted a simple power-law 
$\tau_{\rm eff}^{\alpha} =0.0011(1+z)^{4.23}$. 
If the number of lines in a given patch of the forest is 
Poisson-distributed, a power-law line density evolution 
$\ell_\alpha (z) \propto (1+z)^\gamma$ yields a power-law 
effective optical depth evolution $\tau_{\rm eff}^\alpha
\propto (1+z)^{\gamma+1}$ \citep{zuo93}. 
The column density distribution was modeled with a single power-law index 
$\beta=-1.5$ for $12<\log(\mnhi)<19$, but with a 0.5\,dex break at 
$\log(\mnhi)=14.5$ in order to account for the dearth of high column density lines, 
consistent with observations \citep[e.g.][]{hkc+95,kim02}. 
For the Doppler parameter distribution we set 
$b_\sigma=24 \, \mkms$ \citep{kim+01}.

Because SLLSs $(19 \le \log(\mnhi)<20.3)$ and DLAs $(\log(\mnhi) \ge 20.3$) have 
different column density distributions and are usually excluded in 
measurements of $\tau_{\rm eff}^\alpha$,
these were added after the $\log(\mnhi)<19$ 
line forest converged to the chosen $\tau_{\rm eff}^\alpha (z)$. 
To constrain the redshift evolution of SLLSs, we combined the sample by 
\cite{opb+07} and the lower limit given in \cite{rtn06}, 
yielding $\ell_{\rm SLLS} (z) \sim 0.066(1+z)^{1.70}$. 
For the SLLS column density distribution we adopted $\beta=-1.4$ 
\citep{opb+07}. 
The DLAs were modeled via $\ell_{\rm DLA} (z) =0.044(1+z)^{1.27}$ \citep{rtn06} 
and $\beta=-2$ \citep{phw05}, 
ignoring deviations in \fnhi\ from a single power law. 
The Doppler parameter distribution was left unchanged.

With the overall opacity of the modeled \lya\ forest consistent with observations, 
and the high column density systems incorporated, we used the generated line lists to compute HI Lyman series (up to Ly30) and Lyman continuum absorption spectra. In total we computed 800 different lines of sight for quasars in the redshift range of our sample, 
160 each at $z=3.4, z=3.6, z=3.8, z=4.0$ and $z=4.2$, respectively. 
From these we then generated mock SDSS spectra. First, the resolved \ion{H}{1} forest spectra were multiplied onto synthetic quasar SEDs generated from principal component spectra \citep{suzuki+05,suzuki06}. 
We then degraded the resolution of the mock spectra to $R=2000$ by convolving them with a Gaussian, and rebinned them to $\delta v=69 \mkms$, matching the approximate 
resolution and pixel size of the SDSS spectra. Finally, we added Gaussian noise to the mock SDSS spectra. In each mock spectrum the S/N was normalized in the quasar continuum 
at 1450\AA\ and varied as a function of flux and wavelength according to the throughput of the SDSS spectrograph. The sky level was approximated as a constant and readout noise was also incorporated. 
Finally, for a subset of the mocks
we imposed a sky subtraction error implemented by subtracting/adding
a constant to the spectrum.
These were generated to mimic such systematic errors
that occasionally occur in the SDSS spectra.

Four representative examples are shown in Figure~\ref{fig:mockex}.

\subsection{LLS Recovery and Sky Subtraction Bias}

Two of the authors (JXP,JMO) analyzed 500 of the mock spectra using
the identical tools and procedures applied to the SDSS spectra;
these steps were done without knowledge 
of the mock line distribution and column densities (constructed by author GW).
The results for the two authors were nearly identical; the following
discussion and figures refer to the results related to JXP.
Figure~\ref{fig:mockdz} summarizes the completeness and several biases
uncovered by our analysis.  In the top panel, all cases where a mock
$\mtll \ge 2$ LLS exists with $\mzabs > 3.2$ and an LLS was `observed'
are presented; these correspond to $> 80\%$ of the cases.  
Specifically, we plot the offset $\delta z$
between the true and
observed LLS absorption redshifts as a function of the \sna\ of the
spectrum.  
We find excellent agreement (small $\delta z$), nearly independent
of the \sna\ of the data.
There are, however, a number of cases with $\delta z > 0.01$, primarily
related to the blending of absorption lines (see below).

The lower panel in Figure~\ref{fig:mockdz} presents those cases
that are false negatives (diamonds) and false positives (triangles).
The latter are very rare. [seem too rare..]
The former, however, did occur quite often in our analysis and can
be divided into two classes:  
(i) cases with $|\delta z| < 0.05$ which are proper false negatives, i.e.\
true $\mtll \ge 2$ LLS that were modeled as pLLS;
(ii) cases with $\delta z > 0.1$ which are sightlines where a
higher $z$ pLLS precluded the detection of a lower $z$ LLS.
The majority of the latter cases 
are due to bona-fide pLLS at higher $z$ which greatly diminish
the S/N of the spectra at shorter wavelengths and `obscure'
the presence of a $\mtll \ge 2$ LLS.
Almost none of these cases, however, satisfy the selection
criteria established in $\S$~\ref{sec:survey};  either the
data have too low \sna\ or the absorption redshift of the LLS
gives $\mzem - \mzabs \ge 0.4$.

The first class of false negatives, meanwhile,
are almost exclusively associated with spectra
that had systematically low estimates for the sky background.
In these cases, a $\mtll \ge 2$ LLS has an apparent flux 
at $\lambda < \mlll$ and therefore was modeled as a pLLS.
This is the dominant effect of a sky subtraction bias.
Although our mock spectra had even numbers of over and under-subtracted
sky backgrounds, only the former
are relatively easy to identify (large
regions of spectra are significantly negative) and ignore.
The net effect of a random sky subtraction error is a 
systematic underestimate in the incidence of LLS.
We stress, however, that the magnitude and frequency of poor
sky subtraction in the mock spectra was intentionally elevated
so that we could explore these effects.  The incidence of
such effects within the SDSS spectra is much lower, an
assertion supported by our follow-up spectra with Keck/LRIS
(Appendix~\ref{sec:keck}).
Therefore, we are confident that the sky subtraction bias 
gives rise to a $<10\%$ systematic error for \lzlls.

\subsection{The pLLS Bias}
\label{sec:pLLS}

Originally, we inteded to perform a search for LLS in spectra
with \sna=1 to maximize the pathlength of the survey 
(a nearly 4$\times$ increase over \sna=2).  Our
tests with mock spectra and follow-up observations with 
Keck/LRIS (Appendix~\ref{appx:lris}) indicated that we 
could robustly identify $\mtll \ge 2$ LLS in such data.
We also noted that many of the spectra showed
pLLS candidates which reduced \sna\ to below 1 and made the
search for $\mtll \ge 2$ LLS more challenging.  Our
reaction was to redefine the search path 
by attenuating the absorbed continuum due to
any identified pLLS candidates and then reapply
the \sna\ criterion for the remaining $z<z_{\rm pLLS}$
spectral range.

In princple, this modification should provide an unbiased
search for $\mtll \ge 2$ LLS.  Our trials with mock spectra,
however, revealed an insidiuous bias associated with this
redefinition of the search path.  Specifically,  it is very
difficult to identify pLLSs when they occur at a small
redshift offset ($\delta z \lesssim 0.1$) redward
from a $\mtll \ge 2$ LLS.
In these cases, instead of the search being terminated at
the redshift of the pLLS with the lower $z$ LLS ignored,
the pLLS is ignored and the LLS is included within the
statistical sample.   Furthermore, the redshift
of the recovered LLS is biased to a higher value which 
reduces the survey pathlength by a small but non-negligible
quantity.  Together, these two effects lead to an overestimate
of \lzlls\ by values ranging from $30-50$\%.  
It is very difficult to precisely estimate the magnitude of this
systematic bias for it depends sensitively on \lzlls, the 
incidence of pLLS, and the quasar \zem\ distribution.
In our opinion, one cannot robustly correct for 
this systematic pLLS bias and we caution against performing
any analysis that would be subject to it.
For these reasons, we {\it ignore} pLLS when defining
the survey path and performing the search for $\mtll \ge 2$ LLS.

\subsection{The Blending Bias}

As noted in the previous sub-section, LLS and pLLS
that lie close to one another in redshift are very difficult
to distinguish as individual systems.
This is even true in the limit where one has spectra with
exquisite S/N and resolution when $\delta z < 0.1$.
With SDSS spectra, the limited information provided by the Lyman
limit and the strongest Lyman series lines is insufficient
to robustly distinguish multiple LLS from a single system.
This leads to a ``Blending Bias'' that manifests itself in several
ways.

First, the blending bias increases the number of LLS
observed because pairs of pLLSs blend together to give a single
system with $\mtll \ge 2$.
Second, the absorption redshifts of the LLSs are shifted to higher
redshifts because one generally adopts \zlls\ from the higher
of the pair of systems.  
This leads to a smaller survey path and possibly a
higher inferred incidence of LLS. 
More importantly (see below), many LLS are shifted into the
proximate region of the quasar. 
This causes an underestimate of \lzlls\
for intervening LLS and an overestimate of PLLS.

We explored the quantitative effects of the blending bias with
the following analysis.  We constructed a set of mock absorption
lines for each quasar in the statistical survey (Table~\ref{tab:survey})
with an incidence set to match our measurements ($\S$~\ref{sec:loz}).
Specifically, we adopted an \nhi\ frequency distribution

\begin{equation}
f(\mnhi,z) = C \mnhi^\beta \, \ltp \frac{1+z}{1+z_*} \rtp^\gamma
\label{eqn:fnmock}
\end{equation}
with $\beta = -1.3$ for $10^{16.5} \cm{-2} \le \mnhi \le 10^{19.5} \cm{-2}$
and $\beta = -2$ for $\mnhi \ge 10^{19.5}$, $z_* = 3.7$,
$\gamma = 5.1$ and $C=1.244 \sci{5}$.
From the mock absorber list we identified all LLS with $\mnhi \ge 10^{17.5} \cm{-2}$.
This formed the control sample.
Then, we blended together all systems with $|\delta z| \le \delta z_j$
where $\delta z_j = [0.01, 0.05, 0.1, 0.2]$ and reidentified systems
satisfying $\mnhi \ge 10^{17.5} \cm{-2}$.  When blending two or more 
systems together, we set \zabs\ to the maximum of all the lines.
Finally, we then calcualted the incidence of LLS using the survey
path and LLS for each $\delta z_j$.

Figure~\ref{fig:bbias}a presents the results of the blending bias in
terms of the enhancement/decrement of the incidence of $\mtll \ge 2$ LLS
relative to the perfect model ($\delta z_j = 0$).
For $\delta z_j < 0.1$, there is only a small and ignoreable effect.
For $\delta z_j \ge 0.1$, however, we predict a systematic underestimate
for the incidence of intervening LLS, especially at $z>4$ where
the absolute incidence is highest.  
This deficit in \lzlls\ runs contrary to expectation and is entirely
due to the redshift bias where the blended LLS end up with \zlls\
within the proximate region.  
In turn, we predict a systematic over-estimate of \lzlls\ 
for PLLS (Figure~\ref{fig:bbias}b).
[JMO: Consider whether this affects any previous work]

Our experiments with mock spectra indicate that we commonly blend
together systems with $\delta z_j = 0.05$ to 0.1, with a weak dependence
on redshift or S/N.  
We conclude, therefore, that the effects of the blending bias
on our SDSS analysis are $< 10\%$ for measurements of \lzlls\
for intervening LLS.
This is below the current level of the statistical
error and we will ignore it in the presentation of the results and
discussion.  For the PLLS, the effect for $\delta z_j = 0.1$ 
ranges from $20-90\%$ and we will report our results on \lzlls\ 
for these absorbers as upper limits, especially for $\mzabs > 4$.

Before closing this section, we stress that the blending bias
affects all previous and future LLS surveys.  In particular,
we caution that the incidence of LLS cannot trivially be
used to constrain the \ion{H}{1} frequency distribution \fnhi,
because the latter assumes that every absorption system is
a unique, identifiable line.  For the LLS in particular (but
this is also true for the \lya\ forest), blending smears these
lines over non-negligible redshift intervals ($\delta z \approx 0.1$)
and this affect must be considered when comparing against 
theoretical line densities.
{\bf [Does this affect our f(N) estimates!!]}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results}
\label{sec:results}

In this section, we present the results of our survey.  We
defer extended discussion of previos work and the implications
of our analysis to the following section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\lzlls: The Incidence of 
Intervening $\mtll \ge 2$ LLS per Redshift Interval}
\label{sec:loz}

The incidence of LLS per redshift interval \lzlls\ 
is a purely observational quantity, i.e.\ its value 
is independent of any assumed cosmology.
Consequently, \lzlls\ has limited physical meaning yet it 
it is the proper starting point for a discussion
of our observational survey.

Following standard
practice, we estimate \lzlls\ from the 
ratio of the number of LLS $(N_{\rm LLS})$
detected in a redshift interval to the total search path
for that redshift interval (\ztot):

\begin{equation}
\mlzlls = \frac{N_{\rm LLS}}{\mztot}  \perd
\label{eqn:loz}
\end{equation}
The error for \lzlls\ from this estimator is assumed to be dominated
by the Poission uncertainty in $N_{\rm LLS}$.  Figure~\ref{fig:loz_lls}
presents the estimates of \lzlls\ for the \sna=2 criterion in
a set of arbitrary redshift intervals chosen to give roughly 
constant $N_{\rm LLS}$ per bin (at least for $z<4$).
Table~\ref{tab:llssumm} lists these values for \sna\ thresholds
of 2 and 3, and we note no dependence with this threshold.

Figure~\ref{fig:loz_lls} reveals that the incidence of $\mtll \ge 2$ LLS
increases monotonically for $z>3.5$.
Following previous work, we have modeled the redshift
evolution in \lzlls\ as a power-law with the functional form:

\begin{equation}
\mlzlls = C_{\rm LLS} \ltk \frac{1+z}{1+z_*} \rtk^{\gamma_{\rm LLS}}
\label{eqn:powlaw}
\end{equation}
setting $z_* \equiv 3.7$.
Using standard maximum likelihood techniques
\citep[e.g.][]{sim96}, we find best-fit values 
to the data at $z \ge 3.5$ of
%These are grabbed from running fig_loz
$C_{\rm LLS} = \clls$ and 
$\mglls = \alls$ (68\%\ c.l.).  The best-fit model
is overplotted on the data in Figure~\ref{fig:loz_lls}.
The relatively large uncertainty in $\gamma_{\rm LLS}$
is due to the small redshift interval covered by our survey.
Nevertheless, we conclude at high confidence ($>95\%$)
that \lzlls\ is increasing at least as steeply as $\mglls = 2$
at $z>3.5$.

For $z <3.5$, Figure~\ref{fig:loz_lls} shows two evaluations
of \lzlls.  The light, solid points show the \lzlls\ 
values derived from our statistical quasar sample with
the restriction that $\mzem \ge 3.6$.  
These values are consistent with an extrapolation
of the best-fit power-law. 
The dotted points in the figure, meanwhile,
show the values of \lzlls\ when one  also surveys
quasars with $3.4 \le \mzem \le 3.6$.  
In this case, we find systematically higher \lzlls\
values which would indicate a non-physical, non-monotonic 
evolution in \lzlls.  These results confirm the findings
of PWO09 that the SDSS targeting criteria for quasar 
spectroscopy biases the sample against sightlines without LLS.
This leads to a systematically high and erroneous \lzlls.

The sub-panel of Figure~\ref{fig:loz_lls} compares the cumulative number of LLS
detected in the survey against redshift both as observed (solid)
and as predicted (dotted) by the best-fit power-law model.  For the
latter, we adopt the $g(z)$ curves for \sna=2 from Figure~\ref{fig:goz}.
A one-sided Kolmogorov-Smirnov test yields a probability $P_{\rm KS} = 0.95$
that the observed distribution is drawn from the adopted power-law
expression.  We conclude that the power-law model is a good
description of the observations.
%We return to a discussion of the relatively large,
%albeit poorly constrained, exponent in $\S$~\ref{sec:discuss}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Incidence of LLS in $\Lambda$CDM}
\label{sec:lox}

If one introduces a cosmological model, the
observed incidence of LLS with redshift \lzlls\ may be translated
into physical
quantities.  Consider first the average distance a photon travels
before encountering an LLS with $\mtll \ge 2$, \drlls.  
Specifically, we define

\begin{equation}
\mdrlls \equiv \mlzlls^{-1} \frac{dr}{dz} \cmma
\end{equation}
where 
\begin{equation}
\frac{dr}{dz}  = \frac{c}{(1+z) H(z)}
\end{equation}
where
\begin{equation}
H(z) = H_0 \ltk \Omega_\Lambda + (1+z)^3 \Omega_m \rtk^{1/2} \perd
\end{equation}
Assuming $\Omega_\Lambda = 0.7, \Omega_m = 0.3$, and  $H_0=72 \mkms \rm Mpc^{-1}$
\citep[e.g.][]{wmap05},
we find \drlls\ ranges from $\approx 100$ to 40\,Mpc proper distance
from $z=3.5$ to $z=4.4$ (Table~\ref{tab:summ}).
This is substantially larger than the seperation of bright quasars 
\citep[several Mpc 
for $L_B \ge 10^{40} \rm \, erg \, s^{-1} \, Hz^{-1}$;][]{fg08b} 
and therefore a simple restatement that 
the universe was reionized before $z=4$.

Another approach toward exploring the origin of absorption systems, 
i.e.\ associating
these systems to structures in the Universe (e.g.\ galaxies, filaments),
is to compute
the number of systems per absorption length \llls \citep[][]{bp69},
where $\ell(X) dX = \ell(z) dz$ and

\begin{equation}
dX = \frac{H_0}{H(z)}(1+z)^2 dz  \perd
\end{equation}
The quantity \llls\ is defined to remain constant if \nlls\ the
comoving number density
of structures giving rise to $\mtll \ge 2$ LLS
times \slls\ the average physical size of the structure 
remains constant, i.e.\ $\mllls \propto \mnlls \mslls$.

Figure~\ref{fig:complox} presents the evolution of \llls\
for our cosmology as a function of redshift (see also
Table~\ref{tab:llssumm}).  
We observe a rise in \llls\ with redshift of roughly two times
over the $\approx 1\,$Gyr from $z=3.4$ to 4.4.
At 99\% confidence, we infer an increase in \llls\ over
this redshift interval.
This follows, of course, from the very steep
redshift evolution observed for \lzlls\ ($\S$~\ref{sec:loz});
in the $\Lambda$CDM cosmology, an \lzlls\ evolution steeper
than $(1+z)^{1/2}$ at $z>3$ implies \llls\ is also increasing.
We conclude
that \nlls\ and/or \slls\ are increasing with redshift
at $z \approx 3.5$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\lfnhi\ at $z \approx 3.7$}

Although our observations and LLS analysis are insensitive
to the \ion{H}{1} column densities of the LLS, 
they do provide an integral
constraint on the frequency distribution of \nhi\ values
when combined with other surveys.
Specifically, we can constrain the
\nhi\ frequency distribution of LLS per absorption length
\lfnhi\ at column densities
$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$ as follows.
Previous surveys of $z>3$ DLAs and SLLSs 
have measured \fnhi\ at $z>3$ covering column densities 
$\mnhi \ge 10^{19} \cm{-2}$ \citep{phw05,opb+07,pw09}.
These authors have parameterized the
distribution functions as single (SLLSs) and double (DLAs) power-laws
of the following form:

\begin{equation}
\msfnhi = C_{\rm SLLS} \mnhi^{\beta_{\rm SLLS}} 
\label{eqn:fslls}
\end{equation}

and

\begin{equation}
\mdfnhi = C_{\rm DLA} \ltp \frac{N}{N_d} \rtp^{\beta_{\rm DLA}}
  \; {\rm where} \; \beta_{\rm DLA} =  
\begin{cases}
\beta_3:  N < N_d ; \quad \\ 
\beta_4:  N \geq N_d \\
\end{cases}
\label{eqn:fdla}
\end{equation}
In Figure~\ref{fig:fn}, we present these frequency distributions
as bands which represent the approximate $1 \sigma$ uncertainties.
For the SLLS we have taken $\beta_{\rm SLLS} = -1.3 \pm 0.2$ and
$C_{\rm SLLS} = 0.25 \pm 0.05$.
These values are in reasonable agreement with other estimates
\citep{petitjean}.
For the DLAs, we have evaluated \fnhi\ from the SDSS-DR5 \citep{pw09}
over the redshift interval $z=[3.4,4.0]$, giving 
$N_d = ?$, $\beta_3 = ?$ and $C_{\rm DLA} = ?$ {\bf [FILL IN]}.
Together, these evaluations give \fnhi\ for $\mnhi> 10^{19} \cm{-2}$
at $z \approx 3.7$.

We can estimate \fnhi\ for the interval $\mnhi = [10^{17.5}, 10^{19}]\cm{-2}$,
which we will refer to as \lfnhi,
under the following assumptions:
(i) \lfnhi\ monotonically increases with decreasing \nhi\ 
and
(ii) \lfnhi\ has a power-law form

\begin{equation}
\mlfnhi = C_{\rm LLS} \mnhi^{\beta_{\rm LLS}}.
\end{equation}
We then impose the integral constraint that 
the incidence of LLS with $\mtll \ge 2$ from our survey equals:

\begin{equation}
\ell_{\rm LLS} (X) = \intl_{10^{17.5} \cm{-2}}^\infty \mfnhi \, d\mnhi \perd
\end{equation}
At $z \approx 3.7$, we estimate $\mlzlls = 0.5 \pm 0.1$ (Figure~\ref{fig:complox})
and find $\mbtlls = \blls$ and $C_{\rm LLS} = \clls$.

A plot of \fnhi\ for $z \approx 3.7$ and $\mnhi \ge 10^{17.5} \cm{-2}$
is shown in Figure~\ref{fig:fn}.
Our analysis reveals that \fnhi\ becomes increasingly shallow
with decreasing \nhi. This was suggested by previous authors
based on similar analysis but with much poorer observational
constraints on \llls\ \citep{phw05,opb+07}.
Our results actually indicate that $\mbtlls > -1$ (95$\%$ c.l.)
which means that the universe has a {\it higher} cross-section to 
sightlines with $\mnhi = 10^{19} \cm{-2}$ than those 
with $\mnhi = 10^{18} \cm{-2}$.

We can extend the analysis of \fnhi\ one step further by adopting
recent results on the mean free path to ionizing radiation
(\lmfp; PWO09).  At $z=3.7$, PWO09 estimate 
$\mlmfp = 47 h^{-1}_{72} \, \rm Mpc$ proper distance.
This implies that the effective optical depth \teff\ is unity 
for a photon travelling a redshift path
$\delta z = \mlmfp (dz/dr) = 0.30$ (i.e., \teff=1 at $z=3.5$ for photons
from a quasar with $\mzem = 3.8$).
The evaluation of \teff\ follows from

\begin{equation}
\mteff(z_{912},\mzq) = \intl_{z_{912}}^{z_q} \intl_{\mnmin}^\infty f(\mnhi,z')
   \lbrace 1 - \exp \ltk - \mnhi \sigma_{\rm ph}(z') \rtk \rbrace d\mnhi dz' 
\label{eqn:teff}
\end{equation}
where $\sigma_{\rm ph}$ is the photoionization cross-section evaluated
at the photon frequency and the results are insensitive to the
minimum \nhi\ column density for any value 
$\mnmin \le 10^{12} \cm{-2}$.

Figure~\ref{fig:mfp} shows the \lmfp\ value at $z=3.7$ from PWO09
as a solid horizontal band, assuming a 15\%\ error. 
The solid curve, meanwhile, corresponds to the evaluation of
Equation~\ref{eqn:teff} using our estimation of \fnhi\ integrated
from $z=3.5$ to $z=3.8$ as a cumulative function of \nmin.
At the limiting \nhi\ value of our survey ($10^{17.5} \cm{-2}$), 
we estimate that 70\%\ of the opacity to ionizing radiation is
contributed by $\mtll \ge 2$ LLS.  We estimate a 20\%\
error in this evaluation (overplotted in the Figure).

It is evident from Figure~\ref{fig:mfp} that systems with 
$\mtll \le 2$ must contribute to \lmfp.
For $\mnmin < 10^{17.5} \cm{-2}$ we continue the calculation
by assuming that \fnhi\ follows a power-law

\begin{equation}
f_{\rm pLLS}(\mnhi < 10^{17.5} \cm{-2}, X) = 
  C_{\rm pLLS} \mnhi^{\beta_{\rm pLLS}} 
\label{eqn:fplls}
\end{equation}
constrained to match \lfnhi\ at $\mnhi = 10^{17.5} \cm{-2}$.
We find that models with $\mbplls \ge -1$ cannot reproduce
the \lmfp\ results.  In fact, the data favor $\mbplls \le -1.5$,
i.e.\ a steeper power-law than inferred for the LLS and than
that commonly observed for the \lya\ forest.  These conclusions
do rely on our
estimations of \llls; slopes as shallow as $-1.5$ are possible
if one ignores constraints from the \lya\ forest.

In Figure~\ref{fig:splinefN}, we make a first attempt at deriving
the full \fnhi\ function for $\mnhi \ge 10^{12} \cm{-2}$ by integrating
all of the constrains discussed thus far and also including the
\lya\ forest.  
For the latter, we assume $\myfnhi \propto \mnhi^{-1.5}$
and we normalize this power-law at $z=3.7$ by matching to the
effective \lya\ optical depth \lteff\ measured by \cite{fpl+08}
assuming a $b$-value distribution
$f(b) \propto b^{-5} \exp{-b_\sigma^4/b^4}$ \citep{hr99}. 
Absent a physical model for \fnhi\ we take an empirical approach.
We will evaluate \fnhi\ as a cubic spline \citep{press92}
defined by the values of 12 spline points at 
$\log \mnhi = [12.0, 14.0, 16.0, 17.5, 19.0, 20.3, 21.7, 22.5]$.
The first, third, and last of these are arbitrarily defined
while the others are taken to correspond to the following
observational constraints:

\begin{enumerate}
\item We minimize $\chi^2$ for the binned evaluations of \fnhi\
of the DLAs \citep{pw09} at $z=3.5$ over the interval 
$\mnhi = [10^{20.3}, 10^{21.7}] \cm{-2}$, where the latter
point corresponds to the `break' in \fnhi\ at high column
densities \citep{phw05}.  This establishes the $y$-values
of the spline points at $\log \mnhi = 20.3$ and 21.7 (Table~\ref{tab:spline}).
For the spline point at $\log \mnhi = 22.5$, we force
$\mfnhi \propto \mnhi^{-4}$ for $\mnhi \ge 10^{21.7} \cm{-2}$.
This spline point has no effect on the analysis.

\item The spline point at $\log \mnhi = 19$ is constrained to give
$\mlslls = 0.2$ \citep{opb+07}.
\item The spline point at $\log \mnhi = 17.5$ is constrained
to give $\mllls = 0.5$ (this paper);
\item The spline point at $\log \mnhi = 16$, whose x-value is 
the most arbitrary, is constrained to give $\mlmfp = 47 \umfp$ (PWO09);
\item The spline points at $\log \mnhi = 12 \; {\rm and} \; 14$
are constrained to give $\mfnhi \propto \mnhi^{-1.5}$ and to
give a \lya\ opacity $\mtlya =$ {\bf XX} \citep{fpl+08}.
\end{enumerate}
This approach has several advantages over our previous \fnhi\ evaluations
(Figures~\ref{fig:fn}, \ref{fig:mfp}): 
(i) introducing the \lya\ forest
places a constraint at low \nhi\ values which implies more of an
interpolative analysis then extrapolative;
(ii) the resulting function is smooth in the first derivative
and continuous in the second derivative.

Table~\ref{tab:spline} lists the spline point values and
Figure~\ref{fig:splinefN} plots the points and the resulting spline
evaluation for \fnhi.  The slope $\beta \equiv d\ln[\mfnhi]/d\ln\mnhi$
at each of the spline points is also given.
Finally, we also show the \fnhi\ evaluations of the SLLS $(z>3$)
and DLAs ($z=3.5$) from \cite{opb+07} and \cite{pw09}.

We will defer a full discussion of the results to the following
section, but offer the following observations.
First, we again find that \fnhi\ is very shallow in the LLS
region with $\beta > -1$ at $\mnhi = 10^{19} \cm{-2}$.
Second, we observed that \fnhi\ becomes steeper than
$\beta = -1.5$ (perhaps steeper than $\beta = -2$) for
$\mnhi \approx 10^{16} \cm{-2}$.  This was first
suggested by \cite{petit93} and subsequently argued for
by \cite{rauch} and \cite{misawa}?

[Comment on the uncertainties in all of this. Juggle the values
about, e.g. bootstrap.  Try the shallower Petitjean slope for the SLLS
if the dN/dX is much different]

\subsection{The Incidence of Proximate LLS}

The results presented thus far all refer to intervening LLS, systems
restricted to have \zlls\ blueward of 3000\kms\ from the quasar
emission redshift.  This restriction was imposed to isolate the
`ambient' IGM and avoid biases related to having performed
the analysis with bright, background quasars.
In the space surrounding a bright quasar, one predicts at least two
such biases:
(1) bright, high $z$ quasars are known to cluster strongly
\citep[$r_0 \approx ? \, h^{-1} \rm Mpc$;][]{shen07}
suggesting these objects trace massive structures in the young universe.
The local environment of bright quasars, therefore, has an uncommonly
high density (at least in dark matter) which may give a higher
incidence of LLS;
(2) the radiation field of the quasar will ionize gas to large
distances, reducing the incidence of LLS.
For damped \lya\ systems, the first effect dominates
as one observes an enhanced rate of proximate DLAs (PDLAs)
relative to the intervening systems \citep{reb06,phh08}.

Following the formalism presented in \cite{phh08}, we have estimated
the incidence of proximate LLS (PLLS) in a series of redshift intervals.
First, we re-measured the quasar emission redshifts for all
systems with $\msna \ge 2$ at the Lyman limit and with 
a $\mtll \ge 2$ LLS within 5000\kms\ of \zem.
{\bf [Do this!]}
The SDSS quasar redshifts reported in the standard DR7 data release
are known to have significant systematic errors. 
Following the prescriptions described in \cite{shen07},
J. Hennawi has kindly remeasured the redshifts for all of the quasars.
Second, we analyzed the quasars whose absorbed continuum at the wavelength
of the Lyman limit corresponding (3000\kms\ blueward of \zem) is
twice the median-smoothed, $1\sigma$ error-array.  This establishes
the survey path.  All PLLS identified redward of this 3000\kms\ offset
form the statistical sample (Table~\ref{tab:PLLS}).
The incidence, \lplls, is then estimated in arbitrary redshift
intervals assuming the same estimator for intervening 
LLS (Equation~\ref{eqn:loz}).
These results are presented in Figure~\ref{fig:prox} and compared
against the incidence of interevening LLS, \lzlls.

Ignoring the data at $z < 3.6$ (which we suspect to be biased high
by the SDSS targeting criteria; PWO09), the
incidence of PLLS roughly tracks that of intervening LLS.
At $z<4$, however, the PLLS show an $\approx 25\%$ lower
incidence than the intervening systems.  The inset figure
shows the observed cumulative number of PLLS (dark curve) versus
the predicted number (light curve) assuming the best-fit power-law
for \lzlls\ of intervening LLS.
A one-sided KS test yields only a 1\%\ probability that the
two distributions are drawn from the same parent population.
The principal implication is that $\mtll \ge 2$ LLS toward
$i<20$\,mag quasars at $z>3.5$ suffer from a proximity effect
of lower incidence presumably due to the ionizing radiation
field of the quasar itself.
Given the observed enhancement of strong LLS at $z \approx \mzem$
along sightlines {\it transverse} to such quasars
\citep{hpb+06}, our results lend further evidence that quasar emission
is anisotropic \citep{hp07}.

Before concluding this section, we comment that the PLLS
analysis is subject to a potentially large systematic error.
In performing our LLS survey, we have identified and removed
all quasars with very strong associated absorption,
e.g.\ BALs.  The intent of this procedure was to remove the
signatures of absorption from gas very local 
($<1$\,kpc) to the quasar from the analysis.  It is possible, however,
that the associated absorption in some of these removed
quasars is due to a PLLS at distances $\gg 1$\,kpc and not very
local gas.
This would lead to an underestimate of \lplls.
Alternatively, we may not have identified all of the
local absorbers and therefore might have overestiamted \lplls.
In either case, we caution that a systematic error of the
order of $10-20\%$ should be attributed to this effect.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Discussion}
\label{sec:discuss}

\begin{itemize}
\item  Compare to previous work; include Misawa
\item  Stack spectrum:  Compare $\tilde\mtll$
\item  What gives rise to LLS?  Why is it only a 9x higher incidence than DLAs?
  What is the connection to $z=0$?
[What is dN/dX today?  How about in simulations?  Is the radius to
17.6 only 3x larger?]
\item  Taueff
\end{itemize}

With an estimation of \lfnhi\ in hand, we can draw several inferences
about the opacity of the Universe to ionizing radiation.  First,
we can estimate the mean opacity at 1\,Ryd for all LLS having $\mtll \ge 2$
by taking a weighted mean,

%NOTE:  See fig_avgtaueff [actually fig_fn] for the exact f(N_HI) actually used

\subsection{Comparisons with Previous Work}

Surveys for Lyman limit systems have been carried out for several
decades now \citep{tytler84,ssb89,lzt93,sl95,sl96,peroux03}.
These have been  performed primarily at optical wavelengths on 
heterogeneous quasar samples drawn from a diverse set of
survey approaches: color-selection, radio detection, slitless
spectroscopy, etc.  The authors also had differing completeness
limits for \tll\ (ranging from 1 to 3) and differing approaches
to establishing the pathlength that establishes \lzlls.  Almost
no attention was given to assessing systematic error, and several
of the effects described in $\S$~\ref{sec:mock} assuredly apply
to the previous works.  It comes with little surprise, therefore,
that many of the previous estiamtes of \lzlls\ are in disagreement
with our results.

In Figure~\ref{fig:literature} we present estimates of \lzlls\
from several previous studies, parameterized as in Equation~\ref{eqn:powlaw}
(Table~\ref{tab:param} lists the parameters).  
Tge dotted lines show estimates from \cite{ssb89} and \cite{lzt91},
which included very few observations at $z>3.5$ and not surprisingly 
had rather discrepant estimates for the high $z$ universe.
The solid curves show the results from \cite{sl94} and \cite{peroux03}
who performed surveys of LLS at $z \sim 4$ using the color-selected
APM quasars.  All of these analyses were claimed to correspond to 
LLS with $\mtll \ge 1$, although a careful review of the literature
raises doubts to this assertion in several cases.  To compare against
our $\mtll \ge 2$ results, therefore, we have boosted each of
our \lzlls\ estimations by $8\%$ which is the correction factor
imlied by the \fnhi\ function derived at $z = 3.7$ (Figure~\ref{fig:fnhi}).

Our results on \lzlls\ are somewhat lower than the values derived 
from the APM surveys, but the values lie within
1.5$\sigma$ of concordance.  The more important difference lies between
the estimations at $z<4$.  All of the previous work, which relied
almost entirely on the surveys of \cite{ssb89} and \cite{lzt93}, 
[assumed] $\mzlls \approx 2$ at $z = 3$ giving a more shallow
evolution for \lzlls\ than observed in the SDSS data.
Our results suggest that the previous work at $z \sim 3$ overestimated
the incidence of LLS.  Actually, the original survey by \cite{ssb89}
is in fair agreement with an extrapolation of our power-law form
for \lzlls\ to $z=3$, but the reanalysis by \cite{sl95} of still
unpublished spectray by Steidel \& Sargent led to a higher estimate
at this redshift.  We suspect that this later work gave \lzlls\ values
that were too high either because of sample variance (i.e.\ small
number statistics) or selection bias in the quasar sample 
\citep[e.g.\ the color-selection bias 
described in][and $\S$~\ref{sec:loz}]{pwo09}.
On this point, we note that if we adopt the \cite{peroux03} estimation
of $\mlzlls = 3$ at $z=3.7$, then the LLS alone predict a mean free path
to ionizing radiation $\mlmfp = 45 \umfp$ that matches the measured
value \citep{pwo09}.  This would mean that gas with $\mtll < 1$
cannot contribute any to \lmfp, a physically impossible scenario.
[It gets worse when you realize this gives a steep LLS f(N) which *must*
monotonically hook onto the LLS.]

[Does the MFP evolution require strong LLS evolution?]

[Calculate MFP from Peroux LLS stats alone]

\subsection{Redshift Evolution}

The redshit evolution in the incidence of LLS \lzlls\ impacts
the evolution of the EUVB at low $z$ and the history of reionization
at high $z$.  Previous work has debated whether \lzlls evolves
as a singe power-law $(1+z)^\mglls$ from $z \approx 0 - 4$.
In $\S$~\ref{sec:loz}, we modeled our observations with a 
single power-law having $\mglls = \alls$.
As noted in the previous sub-section, measurements of \lmfp\ also
suggest a steep evolution in the incidence of LLS at $z<4$. 
We now consider whether a single power-law extrapolation is
a good description of \lzlls\ for $z < 3$.

Survey of other \ion{H}{1} absorption systems have demonstrated
that a single $(1+z)^\gamma$ power-law is a poor description
of the \lya\ forest \citep{weymann} and the damped \lya\ systems
\citep{phh08}.  In the former case, one observes a flattening
in the \lya\ line-density at $z \sim 1$ which has been interpreted
to result from a corresponding decline in the intensity of 
the EUVB \citep{weymann,dave}.  It is plausible that a similar
effect would influence the LLS.

In Figure~\ref{fig:zloz}, we present our estimates of \lzlls\
at $z \sim 3.5$ and the estimate of \lzlls\ at $z \sim 1$
from \cite[][see Howk et al., in prep for a new estimate]{sl95}.
Overplotted on the data is a solid curve that shows the best-fit
power law to the SDSS results.  The dashed curves show $2\sigma$
departures from this model.  It is evident that none of these
curves intersect the low redshift observation.
[Did I remember to boost the \lzlls\ values for $\mtll 2 \to 1$?]
We conclude, with high confidenc, that a strict $(1+z)^\mglls$
power-law does not describe the evolution of \lzlls\ across
all of cosmic time.   [Plot log (1+z) on the x-axis?]
Instead, the data suggest a break in the high $z$ power-law
at $z \sim 2$, similar to that observed for the \lya\ forest
albeit at somewhat higher redshift.

The dash-dot curve, is an attempt to model this break.  
For $z<2.3$, we adopt the power-law form that matches
the \lya\ forest at low redshift ($\mglls = 0.26$) and
demand that it intersect the central value of the \cite{sl95}
measurement.  For $z\ge 2.3$, the model breaks to a $\mglls = 2.78$
power-law, again consistent with the high $z$ evolution of the
\lya\ forest \citep[e.g.][]{kim02}.  This is a reasonably
good description of the data and we conclude that a break
in the power-law description of \lzlls\ likely occurs at $z \approx 2$.
We will test this prediction with an (ongoing) survey for LLS
at $z \sim 2$ in HST/ACS and WFC3 slitless spectra of 
$z \approx 2.3$ quasars (PI: O'Meara).

\subsection{The Average LLS Spectrum}

To gain additional insight into the absorption properties of the
LLS, we have constructed an average (stacked) spectrum 
by (i) shifting each quasar spectrum containing a $\mtll \ge 2$ LLS
to the LLS rest-frame and (ii) straight averaging the fluxed data.
This stacked spectrum is primarily illustrative and has little 
quantitative value.  The resulting spectrum is shown in 
Figure~\ref{fig:stack}.  The peak in emission at 
$\lambda_{\rm r} \approx 1280$\AA\ is from the \lya\ emission
peak of the background quasar.  It is significantly
offset from 1215\AA\ because the stack only includes intervening
LLS, i.e.\ those that are offset by at least 3000 \kms from the 
quasar emission redshift.

The second strongest feature in the
spectrum is the Lyman limit at the expected wavelength of 912\AA.
Shortward of the Lyman limit, one observes a non-zero flux that
extends down to $\approx 770$\AA.  In these relative
flux units, we measure a flux at 900\AA\ of $f({\rm 900 \AA}) = 24$.  
Estimating the absorbed continuum at 960\AA\ to be 
$f({\rm 980 \AA}) = 810$, we calculate an average optical depth
at the Lyman limit of $\mavtll = 3.5$.  This value may be compared
to the average optical depth dervied from our \fnhi\ estimation:

\begin{equation}
\mavtll = - \ln \ltb
\frac{\int \exp[-\mnhi \sigma_{LL}] \mfnhi \, d\mnhi}{\int \mfnhi \, d\mnhi}
\rtb
\label{eqn:avgtau}
\end{equation}
where the integrals are evaluated over the interval
$\mnhi = [10^{17.5},10^{22}] \cm{-2}$.
We find $\mavtll \approx 5$ for our assumed \fnhi\ distribution function.
We compare this directly against the mean spectrum of our LLS sample in 
$\S$~\ref{sec:XX}.

\subsection{The Physical Nature of the LLS}

Viewing the situation in the opposite sense (from high $z$ to low $z$),
we speculate that the decrease in \llls\ results from an increasing
number of ionizing sources that photoevaporate the structures associated
with LLS.   
Indeed, the number density of 
bright quasars is observed to increase from $z=4$ to 3 \citep{qsoevol}.
We postulate that these sources are 
reducing \nlls\ and/or \slls.

To explore this point further,  we
decompose \llls\ into various absorption classes (each with $\mtll \ge 2$)
using constraints from the literature.
In Figure~\ref{fig:complox}, we present the \llls\ values (in cumulative
form) for DLAs \citep{pw09} and super Lyman limit systems 
\citep[SLLS, absorbers with $\mnhi = 10^{19} - 10^{20.3} \cm{-2}$;][]{opb+07}.
For the latter, we assume $\ell_{\rm SLLS}(X) = 0.20$ at all redshifts because
only a single estimate exists at $z>3$. 
We have adopted a 20$\%$ lower (1$\sigma$) value than reported
by \cite{opb+07} to crudely correct for the SDSS quasar targeting bias
that will affect their measurement (PWO09). 
The figure demonstrates that the DLAs (especially) and 
the SLLSs have modest contributions to \llls.
At $z=3.4$, they contribute roughly half of the observed incidence
of $\mtll \ge 2$ LLS but this fraction likely decreases to
$\approx 33\%$ by $z=4$.  This latter conclusion hinges on our asssumptions for 
\lslls, in particular at $z \approx 4$ where the value is not
well constrained.  But, we expect the SLLS to behave similarly
to the DLAs, whose incidence is not increasing significantly at these
redshifts.  We conclude that the observed evolution in \llls\
is driven instead by systems with 
$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$.
By the same token, we infer that the decrease in \llls\ with 
decreasing redshift is related to the photoionization 
of these lower \nhi\ systems by the increasing number
of ionizing sources.  The systems giving rise to DLAs (i.e. galaxies)
are too optically thick to show significant effects 
from an increasing radiation field.
[THIS STUFF MIGHT BE BETTER LEFT TO THE DISCUSSION SECTION]

It is difficult, if not impossible, to produce such an effect
for simple cloud geometries in the influence of an ionizing
radiation field \citep{zm0?}.
We spectulate instead that the LLS with $\mnhi \sim 10^{19} \cm{-2}$
arise in extended, partially collapsed structres, e.g. filaments.
We further hypothesize that the flattening of \fnhi\ may be
associated with the transition from
the optically thick regime to being optically thin.
Finally, we note that the rise in \llls\ with redshift
(Figure~\ref{fig:complox}) implies that \btlls\ likely decreases
(becomes steeper) with increasing redshift.

\section{Summary}

\acknowledgments

Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
Foundation, the Participating Institutions, the National Science Foundation, 
the U.S. Department of Energy, the National Aeronautics and Space 
Administration, the Japanese Monbukagakusho, the Max Planck Society, 
and the Higher Education Funding Council for England. The SDSS Web Site 
is http://www.sdss.org/.

The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions. The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.

J. X. P. and J.M.O. are supported by NASA grant
HST-GO-10878.05-A.  J.X.P and G.W. are partially supported
by an NSF CAREER grant (AST--0548180), and 
by NSF grant AST-0908910.

\appendix

\section{Comparisons with Keck+LRIS Spectra}
\label{appx:keck}

To assess uncertainties (statistical and systematic)
of surveying LLS in the SDSS quasar spectra, we
obtained independent, higher quality spectra using the LRIS spectrometer
\citep{lris} on the Keck I telescope.  
LRIS employs a dichroic to split the data into two
spectral channels, each with its own camera.
For our observations, we employed the d560 dichroic which splits the 
light at $\approx 5600$\AA.
For the blue channel, we used the 640/4000 grism
which provides a dispersion of 0.63 \AA\ per unbinned pixel and has a nominal
wavelength coverage of $3100 \rAA < \lambda < 5600$ \AA.  The blue channel
data was binned by 2 in both the spatial and spectral dimensions. For the red
channel, we used the 600/7500 grating which provides a dispersion of
1.28 \AA\ per unbinned pixel, and which was tilted to provide a wavelength
coverage of $5600 \rAA < \lambda < 8200$\AA.  The red channel data was unbinned.
All observations were obtained using a 1 arcsecond slit which provides
an $\approx 4$\,pixel FWHM corresponding to 
$\approx 290\mkms$ and $\approx 220 \mkms$ for the blue and red
data respectively.
The data were obtained in good sky conditions during a 4 night
run in October~2008 and had
exposure times ranging from 300 to 500 seconds.
The data were reduced using the LowRedux
pipeline\footnote{http://www.ucolick.org/$\sim$xavier/LowRedux/} which
bias subtracts, flat fields, optimally extracts, wavelength and flux
calibrates the data to produce a final 1D spectrum.

The SDSS targets for LRIS observations were chosen to sample a range
of LLS, e.g., LLS with $\mtll \ge 2$, pLLS
candidates, PLLS and spectra without apparent LLS.  Furthermore, 
an emphaisis was placed on quasars with lower S/N SDSS spectra 
to assess the completeness of recovering LLS. 
In all cases, the LRIS spectra have sufficient S/N 
to unambigously detect the presence of absorbers with $\mtll > 1$ 
over the full SDSS wavelength range (i.e.\ $\lambda > 3800$ \AA) for
the intervening LLS survey. 
Particular emphasis was given 
to determine what absorbed continuum S/N cutoff should be applied to
the SDSS sample.  To this end, two of the authors (JXP and JMO)
independently modeled LLS absorption in the LRIS data and 
compared the results to similar analysis of the 
the SDSS spectra.  The same
codes were used to model LLS absorption.  In Table
\ref{tab:lriscomp}, we present the results of these comparisons.  In
Figure \ref{fig:lris} we show a representative sample of the
LRIS data alongside their SDSS counterparts.  For the SDSS data in
Figure \ref{fig:lris}, we also show the continuum level assigned
to each spectrum.

The LRIS/SDSS comparison illustrates that with a choice of absorbed
continuum S/N $>1$ 
we recover nearly 100\%\ of the LLS with  $\mtll > 2$ in the SDSS.  We see this
explicitly in Table \ref{tab:lriscomp}, where we give the values for
\zstrt\ in the SDSS search, where \zstrt\ is the redshift at which
the absorbed continuum S/N crosses the value of 1.  In some cases, we
identify LLS at redshifts lower than \zstrt\ in both the LRIS and
SDSS data.  Although these LLS will not contribute to our results,
they lend additional confidence in our absorbed continuum S/N cutoff.
The only exceptions to the identification of LLS in the LRIS and 
SDSS spectra at S/N~$\ge 1$ are for systemss with $\mtll \approx 2$.
At this optical depth, JXP and JMO did not always
agree, even in the LRIS results. 
(WE NEED TO CHECK ALL THE TABLE RESULTS FOR SILLY MISTAKES).  
This highlights the fact that our results have an inherent uncertainty
in $\log \mnhi$ of $\approx 0.2$\,dex. 
Most importantly, this
disagreement does not appear to depend on the S/N of the spectrum for
the range of S/N we could expect from the SDSS data, and thus does not
effect our choice for the S/N threshold.

\bibliographystyle{/u/xavier/paper/Bibli/apj}
\bibliography{/u/xavier/paper/Bibli/allrefs}

\input{Tables/tab_subqso.tex}
\input{Tables/tab_subsurvey.tex}
\input{Tables/tab_subprox.tex}
\input{Tables/tab_sub_candlls.tex}
\input{Tables/tab_spline.tex}
\input{Tables/tab_summ.tex}
\input{Tables/tab_sdss_lris.tex}
%\input{Tables/tab_lls.tex}
%\input{Tables/tab_lls_nostat.tex}
%\input{Tables/tab_lls_prox.tex}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_qsohist.ps}
\caption{Quasar historgrams
}
\label{fig:snz}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/fig_templates.ps}
\caption{Mean (median?) observed (not intrinsic)
quasar spectra (detilted?) for 
the full SDSS-DR7 (clipping?) in redshift intervals from
top to bottom of $z=(3.4,3.7); (3.7,4.0); (4.0,4.4)$ and
$(4.4, 5.0)$.    
The increasing impact of the \lya\ forest is readily apparent
at wavelengths $\lambda_{\rm rest} < 1200$\AA.
}
\label{fig:template}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_exmpl_conti.ps}
\caption{Representative spectra of the quasars in the statistical sample.
Each example shows the absorbed continuum model (dark blue, dotted)
and the green curve indicates the model that includes LL absorption. 
For this presentation, we have not shown the Lyman series in the model.
The vertical dotted line indicates the Lyman limit wavelength
in the quasar rest-frame, i.e.\ $\lambda = \lambda_{LL} (1+z_{em})$.
}
\label{fig:ex_conti}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_goz.ps}
\caption{Summary of the redshift path surveyed in the SDSS-DR7
for $\mtll \ge 2$ LLS absorption assuming a range of S/N thresholds
(solid curves).  Specifically, $g(z)$ represents the number of 
unique quasars in the SDSS that provide a search for LLS over
the interval $dz$ at redshift $z$.  The dotted curve, meanwhile,
represents the same quantity but for proximate LLS (PLLS; systems
within $\delta v = 3000 \mkms$ of the quasar) and corresponds
to a S/N=2 threshold.  This curves fall rapidly for $z<3.4$
because we limit the analysis to quasars with $\mzem \ge 3.4$.
The non-monotonic nature of $g(z)$ is due primarily to the presence
of LLS along the quasar sightlines which abruptly truncate the search path.
}
\label{fig:goz}
\end{figure}

\begin{figure}
\epsscale{0.7}
\plotone{Figures/mockspec_bw.eps}
\caption{
(a): A spectrum representative of the typical data quality 
(S/N$\sim 2$ at the Lyman limit of the quasar). 
There is a LLS ($z=3.88059, \log\mnhi=18.27$) that can be easily identified 
at this S/N. 
Two $16< \log\mnhi <18.27$ systems at higher $z$ do not yield a 
high \tll\ before the light hits the optically thick system.
(b): A high-S/N spectrum (S/N$\sim 6$ at the Lyman limit of the quasar), 
rendering its partial LLS ($z=3.98387, \log\mnhi=17.24$) 
easily visible. An additional SLLS at lower redshift 
$(z=3.76609, \log\mnhi=19.28)$ sets the flux to zero at the Lyman limit.
(c): A roll-off spectrum. There is a LLS $(z=3.68084, \log\mnhi=17.87)$, 
but there are five $16 < \log \mnhi <17$ systems at higher $z$ that result 
in a roll-off. The S/N at the Lyman limit of the quasar is quite low 
(S/N$\sim 1.5$), the intervening systems further decrease 
the S/N, rendering the LLS invisible.
(d): A spectrum with strongly undersubtracted sky background. The 
first strong system encountered is a LLS 
$(z=3.87495, \log\mnhi=18.34)$, but the flux is above zero even 
after hitting a DLA $(z=3.57678, \log\mnhi=20.43)$. 
You can easily see that the sky subtraction is poor, because 
Lyman alpha of the DLA does not saturate. 
}
\label{fig:mockex}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_mock_dz.ps}
\caption{Offset in redshift $\delta z$ for the `observed' LLS and pLLS
from the \zabs\ value of the nearest true $\mtll \ge 2$ LLS
in our mock spectra.  The analysis is restricted to the highest
\zabs\ LLS along each sightline.
In the upper panel, we show the $\delta z$ value for sightlines
where a LLS was `observed' and actually exists.  These are the majority
of cases $(>80\%$)
and we find small $\delta z$ values with a small, but important
bias to $\delta z > 0.01$.
In the lower panel, we show false negatives (diamonds) and false
positive (triangles) detections.  The former correspond to a true LLS
that was observed as ($\delta z < 0.1$) or hidden by a pLLS ($\delta z > 0.1$).
The misidentifications ($\delta z < 0.1$) are dominated by the mock
spectra with large underestimates in the sky background.  The dominant
effect of a sky subtraction bias is an underestimate in in the incidence
of LLS.
}
\label{fig:mockdz}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_both_bbias.ps}
\caption{Blending bias (enhancement/decrement of \lzlls\ relative
to no bias) for mock absorption line systems for 
(upper) intervening $\mtll \ge 2$ LLS and
(lower) proximate $\mtll \ge 2$ LLS.
The absorption line statistics were set to roughly match the observed
incidence. 
Even for the blending over redshifts $\delta z_j = 0.2$, the bias
for intervening systems is relatively small.
In contrast, the blending bias systematically elevates \lzlls\ for PLLS,
especially at $z>4$.
}
\label{fig:bbias}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_loz.ps}
\caption{Incidence of intervening LLS with $\mtll \ge 2$ \lzlls\
as a function of redshift.  
The binning at $z<4$ is arbitrarily chosen to give roughly the
same number of LLS per sample.  
The solid (blue) line shows the best-fit power-law
to the data at $z > 3.5$:  
$\mlzlls = C_{\rm LLS} [(1+z)/(1+z_*)]^\alpha_{\rm LLS}$, 
with $z_* \equiv 3.7$, $C_{\rm LLS} = \clls$, and
$\beta_{\rm LLS} = \alls$ (68\%\ c.l.).
The gray and solid points at $z < 3.5$ correspond to estimates
of \lzlls\ where one restricts the analysis to quasars
with $\mzem \ge 3.6$.  The dotted points, meanwhile, show
\lzlls\ when one includes quasars with $3.4 \le \mzem \le 3.6$.
These measurements are significantly biased to higher values by the
SDSS quasar-targeting criteria (PWO09).
In the subpanel, 
the black (solid) curve shows the cumulative number of
$\mtll \ge 2$ LLS detected in our survey of the SDSS-DR7
database adopting the \sna=2 threshold.
The blue (dotted) curve shows the predicted number of LLS assuming
the best-fit power-law from Figure~\ref{fig:loz_lls} and adopting the
\sna=2 $g(z)$ function from Figure~\ref{fig:goz}.  
A one-sided KS-test does not rule out the null hypothesis that
the model distribution is statistically different from the observations.
}
\label{fig:loz_lls}
\end{figure}

%\begin{figure}
%\epsscale{0.8}
%\plotone{Figures/fig_cumlz.ps}
%\caption{The black (solid) curve shows the cumulative number of
%$\mtll \ge 2$ LLS detected in our survey of the SDSS-DR7
%database adopting the \sna=2 threshold.
%The blue (dotted) curve shows the predicted number of LLS assuming
%the best-fit power-law from Figure~\ref{fig:loz_lls} and adopting the
%\sna=2 $g(z)$ function from Figure~\ref{fig:goz}.  
%A one-sided KS-test does not rule out the null hypothesis that
%the model distribution is statistically different from the observations.
%}
%\label{fig:cumlz}
%\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_complox.ps}
\caption{
The dashed lines bound our estimate of \llls\ for $\mtll \ge 2$ LLS
as a function of redshift. The widths of the
two lower bands (blue, red) indicate estimates of $\ell(X)$ for
DLAs and SLLS \citep{opb+07,pw09}; see the text for details. 
These bands are plotted on top of one another to indicate their total
contribution to \llls\ (as indicated by the vertical arrows on the right-hand
side of the figure).  The (top) blue band, therefore, represents the 
estimate to \llls\ from LLS
with $\mnhi = 10^{17.5} - 10^{19} \cm{-2}$. 
[COMMENT MORE]
}
\label{fig:complox}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_fn.ps}
\caption{\nhi\ frequency distribution \fnhi\ observed for the 
SLLS \citep[green, $\mnhi = 10^{19} - 10^{20.3} \cm{-2}$;][]{opb+07}
and DLAs \citep[red, $\mnhi \ge 10^{20.3} \cm{-2}$;][]{pw09}.
The blue band is an estiamte of \fnhi\ for LLS having 
$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$ under the assumptions
of a power-law form ($f(\mnhi,X) \propto \mnhi^{\beta_{\rm LLS}}$)
and a monotonic increase from the SLLS, 
and constrained by the incidence of observed $\tau \ge 2$ LLS (this paper).
We find $\mbtlls = -1.0 \pm 0.3$ (90\%\ c.l.) at $z \approx 3.5$.
}
\label{fig:fN}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/fig_mfp.ps}
\caption{This figure shows the mean free path contributed
by absorbers with $\mnhi \ge \mnmin$. For $\mnmin \ge 10^{17.5} \cm{-2}$,
(solid curve) which corresponds to our LLS survey, we have adopted
the estimate of \fnhi\ from Figure~\ref{fig:fN} in the calculation.
We estimate a 20\%\ uncertainy in the contribution of LLS to
\lmfp, as shown in the figure.  For $\mnmin < 10^{17.5} \cm{-2}$,
we assume \fnhi\ follows a simple power-law with exponent \bplls,
and show a series of extrapolations (dash and dotted curves).
The solid (red) horizontal band centered at $47 \umfp$
indicates the measurement of \lmfp\ at $z \approx 3.7$ from PWO09.
These results imply that LLS contribute $\approx 70\%$ of the 
mean free path and that \bplls\ must be steeper than $-1$
and likely steeper than $-1.5$.
}
\label{fig:mfp}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_splinefn.ps}
\caption{The solid black curve shows our full estimation of
\fnhi\ as a spline to the 7 black crosses (plus an 8th cross
at $\log \mnhi = 22.5$ that is not shown; Table~\ref{tab:spline}).
At each spline point, we calculate the local power-law slope
$\beta = dlnf/dln\mnhi$.  The y-values of the
spline points are constrained as follows: 
(1) the points at $\log \mnhi = 20.3, 21.7$ are set to minimize
$\chi^2$ from the binned evaluations of \fnhi\ of the DLAs
at $z=3.5$ \citep{pw09}.  The spline point at $\log \mnhi = 22.5$ is then
constrained to give $\mfnhi \propto \mnhi^{-4}$ for
$\log \mnhi \ge 21.7$;
(2) the spline point at $\log \mnhi = 19$ is placed to give
$\mlslls = 0.2$ \citep{opb+07};
(3) the spline point at $\log \mnhi = 17.5$ is constrained
to give $\mllls = 0.5$ (this paper);
(4) the spline point at $\log \mnhi = 16$, whose x-value is 
the most arbitrary, is constrained to give $\mlmfp = 47 \umfp$ (PWO09);
(5) the spline points at $\log \mnhi = 12 \; {\rm and} \; 14$
are constrained to give $\mfnhi \propto \mnhi^{-1.5}$ and to
give a \lya\ opacity $\mtlya = XX$ \citep{fpl+08}.
}
\label{fig:splinefN}
\end{figure}

\begin{figure}
\epsscale{0.8}
\plotone{Figures/fig_prox_loz.ps}
\caption{The solid and dark points show the incidence of
proximate LLS per unit redshift (PLLS; LLS with $\mtll \ge 2$ that 
occur within 3000\kms\ of the background quasar) against redshift.
These are compared against the same quantity for intervening LLS
(gray points).  The data point at $z<3.6$ corresponds to PLLS
and has been dotted out because it is expected to be biased
by the SDSS targetting criteria (PWO09).  Ignoring that last
point, we find that the incidence of PLLS roughly follows that
of intervening systems but is systematically lower by $\approx 25\%$
at $z<4$.  The inset figure shows the cumulative number of 
PLLS observed (black curve) against the predicted number using
the power-law model for \lzlls\ ($\S$~\ref{sec:loz}) and
the $g(z)$ curve for PLLS (Figure~\ref{fig:goz}).
}
\label{fig:prox}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/fig_literature.ps}
\caption{Comparisons with the literature
}
\label{fig:literature}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/fig_allloz.ps}
\caption{Redshift evolution in \lzlls
}
\label{fig:zloz}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/stack_lls.ps}
\caption{Stack of LLS spectra
}
\label{fig:stack}
\end{figure}

\begin{figure}
\epsscale{0.9}
\plotone{Figures/fig_lris_sdss.ps}
\caption{LRIS spectra
}
\label{fig:lris}
\end{figure}

%\begin{figure}
%\epsscale{0.9}
%\plotone{Figures/fig_mock_loz.ps}
%\caption{l(z) for the Mocks
%}
%\label{fig:mockloz}
%\end{figure}

%\begin{figure}
%\epsscale{0.9}
%\plotone{Figures/fig_loz_prox.ps}
%\caption{$\ell(z)$ for proximate LLS with $\mtll \ge 2$
%}
%\label{fig:loz-lls}
%\end{figure}

\end{document}

### 2010-05-29 Winds/Simple/outflow.cc

@@ -21,14 +21,14 @@ int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins
 
 // grid parameters
-double r_inner   =  7.0;      // inner boundary radius, in kpc
+double r_inner   =  1.0;      // inner boundary radius, in kpc
 double r_outer   = 10.0;      // outer boundary radius, in kpc
-double r_emit    =  7.0;      // boundary to emit from
-double n_0       =  5e-2;     // number density at inner boundary
-double n_law     =    0;      // -1*power law exponent of density law
+double r_emit    =  0.1;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary
+double n_law     =    2.;      // -1*power law exponent of density law
 double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  1.0e7;    // velocity at inner boundary (cm/s)
-double v_law     =    0;      // power law of velocity profile
+double v_min     =  70.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
 double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
@@ -45,9 +45,9 @@ double lambda_0[]   = {2796.352, 2803.531};
 // line oscillator strengths
 double f_lu[]       = {0.6123,     0.3054}; 
 // abundances of element of line
-double abun[]       = {8.5e-5, 8.5e-5};
+double abun[]       = {3.4e-6, 3.4e-6};  // Solar metallicity and 1/10 down for dust
  // lines doppler velocity in cm/s
-double v_doppler    =   1e6;              
+double v_doppler    =   15*1e5;              
 
 // parameters describing voigt profile
 double voigt_a   = 0.1;
@@ -107,7 +107,8 @@ int main(int argc, char **argv)
 double Get_Velocity(double *x, double r)
 {
   //  return v_max*pow(r/r_outer,v_law);
-  return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
+  // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
+  return v_min * pow(r/r_inner, v_law);
 }
 
 
@@ -118,6 +119,7 @@ double Get_Density(double *x, double r)
 {
   if (r == 0) return 0;
[…]

### 2010-06-05 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4984 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,401 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  2e6;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.4;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
+double lambda_0[]   = {2796.352, 2803.531};  
+// line oscillator strengths
+double f_lu[]       = {0.6123,     0.3054}; 
+// abundances of element of line
[…]

### 2010-06-05 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4985 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\naid}{\ion{Na}{I}~$\lambda\lambda 5891, 5897$}
+\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
+\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
+\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
 \def\hub{h_{72}^{-1}}
@@
 \def\mzabs{z_{\rm abs}}
-\def\msna{{\rm S/N}^{\rm A}_{912}}
-\def\sna{S/N$^{\rm A}_{912}$}
-\def\mnull{\nu_{\rm 912}}
-\def\nnull{$\nu_{\rm 912}$}
 \def\intl{\int\limits}
-\def\nstatqso{193}
-\def\maxoff{0.4}
-\def\clls{1.9 \pm 0.2}
-\def\alls{5.2 \pm 1.5}
-\def\blls{-0.9^{+0.4}_{-0.05}}
 \def\cmma{\;\;\; ,}
@@
 \def \mzem {z_{\rm em}}
-\def \mzlls {z_{\rm LLS}}
-\def \zlls {$z_{\rm LLS}$}
-\def \mzend {z_{\rm end}}
-\def \zend {$z_{\rm end}$}
-\def \mzstrtt {z_{\rm start}^{\rm S/N^A=2}}
-\def \zstrtt {$z_{\rm start}^{\rm S/N^A=2}$}
-\def \zstrto {$z_{\rm start}^{\rm S/N^A=1}$}
-\def \mzstrto {z_{\rm start}^{\rm S/N^A=1}}
-\def \zstrt {$z_{\rm start}$}
-\def \mzstrt {z_{\rm start}}
 \def\smm{\sum\limits}
-\def \lll  {$\lambda_{\rm 912}$}
-\def \mlll  {\lambda_{\rm 912}}
-\def \mtll  {\tau_{\rm 912}}
-\def \tll  {$\tau_{\rm 912}$}
-\def \mavtll  {<\mtll>}
-\def \tigm  {$\tau_{\rm IGM}$}
-\def \mtigm  {\tau_{\rm IGM}}
 \def \cmm  {cm$^{-2}$}
@@
 \def \etal {\textit{et al.}}
-\def \ob {$\Omega_b$}
-\def \obh {$\Omega_bh^{-2}$}
-\def \om {$\Omega_m$}
-\def \ol {$\Omega_{\Lambda}$}
-\def \gz {$g(z)$}
-\def \mgz {g(z)}
 \def \lyaf {Lyman--$\alpha$ forest}
-\def \fnhi {$f(\mnhi,X)$}
-\def \mfnhi {f(\mnhi,X)}
-\def \myfnhi {f_{\rm Ly\alpha}(\mnhi,X)}
-\def \yfnhi {$f_{\rm Ly\alpha}(\mnhi,X)$}
-\def \lfnhi {$f_{\rm LLS}(\mnhi,X)$}
-\def \dfnhi {$f_{\rm DLA}(\mnhi,X)$}
-\def \sfnhi {$f_{\rm SLLS}(\mnhi,X)$}
-\def \mlfnhi {f_{\rm LLS}(\mnhi,X)}
-\def \mdfnhi {f_{\rm DLA}(\mnhi,X)}
-\def \msfnhi {f_{\rm SLLS}(\mnhi,X)}
-\def \ztot {$\Delta z_{\rm TOT}$}
-\def \mztot {\Delta z_{\rm TOT}}
-\def \mlplls {\ell_{\rm{PLLS}}(z)}
-\def \lplls {$\ell_{\rm{PLLS}}(z)$}
-\def \mlzlls {\ell_{\rm{LLS}}(z)}
-\def \lzlls {$\ell_{\rm{LLS}}(z)$}
-\def \mllls {\ell_{\rm{LLS}}(X)}
-\def \llls {$\ell_{\rm{LLS}}(X)$}
-\def \ldla {$\ell_{\rm{DLA}}(X)$}
-\def \lslls{$\ell_{\rm{SLLS}}(X)$}
-\def \mlslls{\ell_{\rm{SLLS}}(X)}
-\def \nlls {$n_{\rm LLS}$}
-\def \slls {$\sigma_{\rm LLS}$}
-\def \mnlls {n_{\rm LLS}}
-\def \mslls {\sigma_{\rm LLS}}
-\def \drlls {$\Delta r_{\rm LLS}$}
-\def \mdrlls {\Delta r_{\rm LLS}}
-\def \mlmfp {\lambda_{\rm mfp}^{912}}
-\def \lmfp {$\lambda_{\rm mfp}^{912}$}
-\def \mbplls {\beta_{\rm pLLS}}
-\def \bplls {$\beta_{\rm pLLS}$}
-\def \btlls {$\beta_{\rm LLS}$}
-\def \mbtlls {\beta_{\rm LLS}}
-\def \lteff {$\tau_{\rm eff,LL}$}
-\def \teff {$\tau_{\rm eff,LL}$}
-\def \tlya {$\tau_{\rm eff}^{\rm Ly\alpha}$}
-\def \mtlya {\tau_{\rm eff}^{\rm Ly\alpha}}
-\def \mteff {\tau_{\rm eff}}
-\def \mllteff {\mteff^{912}}
-\def \llteff {$\mteff^{912}$}
-%\def \llsteff {$\tilde\mtll$}
-%\def \mllsteff {\tilde\mtll}
 \def \mnmin {\mnhi^{\rm min}}
@@
 \def \snrlim {SNR$_{lim}$}
-\def\mglls {\gamma_{\rm LLS}}
-\def\mavgt {<\mtll>}
 
-\title{The SDSS-DR7 Survey for Lyman Limit Systems}
+\title{Simple Wind Models}
 
@@
 J. Xavier Prochaska\altaffilmark{1}, 
-John M. O'Meara\altaffilmark{2}, 
-Gabor Worseck\altaffilmark{1} 
+Others
+%John M. O'Meara\altaffilmark{2}, 
+%Gabor Worseck\altaffilmark{1} 
 %\& Scott Burles\altaffilmark{3}
@@
 \altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of California, 1156 High Street, Santa Cruz, CA 95064}
-\altaffiltext{2}{Department of Chemistry and Physics, Saint Michael's College.
-One Winooski Park, Colchester, VT 05439}
+%\altaffiltext{2}{Department of Chemistry and Physics, Saint Michael's College.
+%One Winooski Park, Colchester, VT 05439}
 
 \begin{abstract}
-We present the results from a survey for Lyman limit system absorption in the Sloan Digital Sky Survey, Data release 5.  I like abstracts, they are fun!
+Blah
 \end{abstract}
@@
 \section{Introduction}
-% JO: Introduce LLS
-% JO: Mention previous surveys.
-% JO:  Leads into survey size \& bias.
-Studies of hydrogen  absorption in the lines of sight towards 
-distant quasars have served to both define, and in recent years bring
-precision to, our cosmological models for the universe.  
-The low density, highly ionized  \lyaf\ lines (a.k.a.\ the intergalactic
-medium, IGM), with 
-\ion{H}{1} column densities $\mnhi < 10^{17.2} \cm{-2}$,
-through their aggregate statistical properties (e.g.\ their
-flux power spectrum, mean flux, and column density distributions)
-constrain cosmological parameters such as the primordial power spectrum
-and the baryonic mass density
-\citep[e.g.][]{rau98,cwb+03,mcdonald05,tytler04,fpl+08}.
-The high-density, predominantly neutral damped \lya\ systems (DLAs),
-with $\mnhi \ge 10^{20.3} \cm{-2}$, trace the gas which forms stars, and
-likely represent the progenitors of modern-day galaxies 
-\citep[e.g.][]{wlf+95,wgp05,pw09}.
-
-The majority of \lyaf\ lines and the DLAs have, through
-analysis of their \lya\ lines, precisely measured \nhi\ values
-that permit detailed study of their physical propertiees (e.g.\ metallicity).
-For systems with intermediate \nhi\ values ($\approx 10^{18} \cm{-2}$),
-however, \lya\ and most of the Lyman series lines lie on the
-flat portion of the curve-of-growth and the \nhi\ value is difficult
-to cosntrain.
-On the other hand, these systems are optically thick to ionizing
-radiation and impose a readily identify spectral signature in a quasar
-spectrum at the Lyman limit.
-These so-called Lyman limit systems (LLS), currently the least-well
-studied of \ion{H}{1} absorption systems at high redshift,
-are the focus of this manuscript.
-
-Historically, the LLS were among the first class of quasar
-absorption line (QAL) systems to be surveyed \citep{tytler84}.
-This is because their spectral signature is easy to identify
-even with low-resolution, low S/N spectra.  The principal challenge
-is that the Lyman limit occurs redward of the atmospheric
-cutoff only for systems (hence quasars) with redshifts $z>2.7$.
-For lower redshifts, one requires spectrometers on space-bourn
-ultraviolet sattelites.
-By the mid 1990's, samples of several tens of LLS were generated
-spanning redshifts $z 0 - 4$ \citep{ssb89,lzt9X,stengler95,storrie96}.
-These results were derived from heterogeneous sets of quasars discovered
-from a combination of color-selection, radio detection, and
-spectroscopic surveys.    The spectra, too, was acquired with a 
-diverse set of instrumentation and therefore varying S/N and spectral
-resolution mitigating differing sensitivity to the precise optical
-depth at the Lyman limit.  Although the results were not fully
-consistent with one another, the general picture that resulted
-was a rapidly evolving population of absorption systems reasonably
-described by a $(1+z)^{1.5}$ power-law.
-
-Cosmologically, the LLS contribute much if not most of the universe's
-opacity to ionizing radiation.  Until recently, the observed incidence
-of the LLS provided the only direct means of estimating the mean
-free path \lmfp\ at any redshift \citep[e.g.][]{meiksin,madau99,fg08b}.
-In a companion paper \citep{pwo09}, we have presented a new
-technique to measure the \lmfp\ that circumvents any knowledge
-of the LLS.  A more precise census of the LLS will serve as a 
-consistency check for this \lmfp\ calculation, but is unlikely to
-ever again be a competitive approach.  Instead, the incidence of LLS
-can be used in combination with estimates of \lmfp\ to assess the
-\nhi\ frequency distribution for gas 
-with $\mnhi \approx 10^{16-18} \cm{-2}$, 
-a regime that is very difficult to explore by studying individual
-absorption systems.   Surveys of the LLS are also likely to 
-place tight constraints on $z \sim 3$
-cosmological simulations that include radiative transfer.
-
-Physically, the nature of systems that give rise to LLS remains
-an open question.  The systems with the largest \nhi\ values
-(i.e.\ $\mnhi \ge 10^{19} \cm{-2}$, the so-called the super-LLS and
-DLAs) are likely associated with the interstellar medium and
-outer regions of high $z$ galaxies.  These high \nhi\ systems, however,
-are only a subset of the LLS population.  Unfortunately, a proper
-modeling of the LLS almost certainly requires careful modeling of 
-radiative transfer which has thus far been beyond the scope of
-modern computations.  Indeed, the few studies to date have tended
-to severely underestimate the incidence of LLS \citep{katz94,gardnerXX,gnedin}.
-In recent simulations of high $z$ galaxy formation, however, 
-theorists have placed great attention on `streams' of cold gas that
-carry fresh material from the IGM to star-forming galaxies 
-\citep{keres99,dekel08}.  These cold streams have relatively large
-surface densities ($N_{\rm H} \sim 10^{20} \cm{-2}$) and could therefore
-produce Lyman limit absorption provided the material has a
-non-negligible neutral fraction.  Consequently, an accurate census
-of the LLS with redshift may directly constrain the nature and
-prevalence of cold streams in the young universe.
-
-A final, yet perhaps most important, motivation for studying the LLS
-is that these systems may dominated the census of metals at all epochs.
-The majority of LLS are metal-bearing, showing metal-line transitions of 
-common low and high-ions \citep[e.g.][]{p99,pks2000}.
-Because the estimated ionization corrections for LLS with 
-$\mnhi \approx 10^{18} \cm{-2}$ is large, the observations likely
-track only a trace amount of the metals.  [last comment]
-
-[Add shot in the dark(s)?]
-
-In this paper, we survey the homogeneous dataset of quasar
-spectra from the Sloan Digital Sky Survey (SDSS), using all 
-7 public data releases.  Our observational analysis
-aims to produce the most precise measurement of 
-the LLS incidence paying careful attention to systematic
-biases.  The wavelength coverage and data quality of the SDSS
-quasar spectra focusing the survey to $z \approx 3.5$.  Future
-work will depend on follow-up obseravtions of well-define
-quasar samples at other wavelengths.
-
-The paper is organized as follows.  In $\S$~\ref{sec:def},
-we present a set of LLS defintions used throughout the manuscript.
-We adopt a cosmology with 
-$H_0 = 72 \, h_{72} \, \mkms \, \rm Mpc^{-1}$, 
-$\Omega_{\rm m} = 0.3$, and $\Omega_\Lambda = 0.7$
-and report proper lengths unless specified.
-
-\section{Lyman Limit System Definitions}
-\label{sec:def}
-
-The cross-section of \ion{H}{1} at energies above the Lyman limit
-may be approximated by:
-
-\begin{equation}
-\sigma_{\rm LL}(\nu \ge \mnull) \approx  
-  6.35 \sci{-18} \ltp \frac{\nu}{\mnull} \rtp^{-3} \; \cm{2} \cmma
-\end{equation}
-
-\begin{equation}
-\mnull = E_{912}/h = c/\mlll \cmma 
-\end{equation}
-
-\noindent $E_{912} = 1$\,Ryd.  Specifically, 
-$\nu_{\rm LL} = 3.29 \sci{15}$Hz and 
-$\mlll = 911.7641$\AA.
-This implies a continuum opacity at wavelengths $\lambda \le \mlll$,
-
-\begin{equation}
-\mtll(\lambda \le \mlll) \approx \frac{\mnhi}{10^{17.2} \cm{-2}} \ltp 
-   \frac{\lambda}{\mlll} \rtp^{-3} \cmma
-\end{equation}
-where \nhi\ is the \ion{H}{1} column density. 
-For a gas `cloud' intersecting a background source with intrinsic flux
-$F_{\rm int}(\lambda)$, the observed flux $F_{\rm obs}(\lambda)$
-blueward of the Lyman limit is
-
-\begin{equation}
-F_{\rm obs}(\lambda \le \mlll) = 
-  F_{\rm int}(\lambda) \exp \ltk -\mtll(\lambda) \rtk
-\label{eqn:flux}
-\end{equation}
-
-In what follows, we will define a `standard' Lyman limit system (LLS) to be
-one where $\mtll \ge 2$, i.e.\ $\mnhi \ge 10^{17.5} \cm{-2}$.
-This corresponds to greater than 85\%\ attenuation of an 
-incident ionizing radiation field. 
-By this definition, the class of LLS includes systems with
-$10^{20.3} \cm{-2} \le \mnhi \le 10^{19} \cm{-2}$ 
-\citep[the so-called super-LLS or sub-DLAs; e.g.][]{opb+07} and systems with
-$\mnhi \ge 10^{20.3} \cm{-2}$ \citep[the damped \lya\ systems; e.g.][]{wgp05}.
-In a few cases, we will distinguish between these `strong' LLS from 
-those with lower \nhi, referring to the latter as LLS.
-We also note that our $\mtll \ge 2$ definition for LLS differs
-from other works which adopted $\mtll \ge 1$ or $\mtll \ge 1.5$.
-Unfortunately, there is no well-established criterion.
-
-Observationally, the absorption of a background source
-by a $\mtll \ge 2$ LLS is 
-readily apparent, even in low S/N spectra.
-We define absorbers with $\mnhi < 10^{17.5} \cm{-2}$ as the 
-partial Lyman limit systems (pLLSs).  To survey these systems,
-one requires higher quality spectra or an alternate approach to the analysis.
-
-We define the redshift of an LLS as
-
-\begin{equation}
-\mzlls \equiv \frac{\mlll^{\rm LLS}}{\mlll} - 1
-\end{equation}
-where $\mlll^{\rm LLS}$ marks the observed onset of LL absorption.
-In practice, this is is often estimated from strong Lyman series lines
-(e.g.\ \lya, \lyb) that accompany the Lyman limit opacity.
-
-We define the sub-set of LLS that occur within 3000\kms\
-of the emission redshift of the background source as proximate LLS
-(PLLS).  We separate the analysis of these systems from the rest
-to investigate changes in the incidence of optically thick gas
-near high $z$ quasars due to, e.g.\ the quasar's radiation field
-and local environment $\S$~\ref{sec:prox}.
-
-Finally, we define the observable \lzlls\ as the average
-number of LLS detected per unit redshift at a given redshift.
-In the previous literature, this quantity is also expressed
-as $n(z)$, $dN/dz$ and $dn/dz$.
-
-\section{SDSS Quasar Sample and Spectroscopy}
-
-One of the primary objectives of the Sloan Digital Sky Survey (SDSS)
-was to discover $\sim 100,000$ new quasars across the northern sky
-\citep{yaa+00}.  The strategy of the SDSS team to achieve this
-ambitious goal was a four-fold process:
-(i) obtain deep, multi-band images across a large area of the sky;
-(ii) select quasar candidates by demanding a point-like point-spread-function
-and imposing color criteria that separate the candidates from the
-Galactic stellar locus;
-(iii) obtain follow-up spectra for a magnitude-limited sample
-with a fiber-fed spectrograph.
-The details of target selection and quasar completeness with
-redshift is described at length in a series of SDSS papers
-\citep{rfn+02}, but see \citep{wp09} for a new and more accurate analysis;  
-and
-(iv) automatically identify quasars and estimate their redshifts
-(\zem) through template fitting to the optical spectroscopy.
-
-Of these steps, the second has the greatest 
-impact on a survey for high $z$ Lyman limit systems. 
-The key issue for our survey is whether the presence 
-of an intervening LLS biases the targeting of the
-background quasar for follow-up spectroscopy.  
-In effect, a high $z$ LLS severely `reddens' the quasar
-at the bluest optical wavelengths of the SDSS imaging.  
-With this effect in mind, the SDSS team imposed cuts
-on the $(u-g)$ color which better separated the quasar
-locus in color pace from the stellar locus.  The net effect,
-however, is to bias the spectroscopic follow-up against 
-quasar sightlines {\it without} foreground LLS
-\citep[][hereafter PWO09]{pwo09}.  Our analysis indicates
-an important bias for quasars with $\mzem < 3.6$. 
-For this reason, we will limit the statistical analysis
-to quasars with $\mzem \ge 3.6$, but we also explore this bias
-by considering the incidence of LLS toward quasars with $\mzem = 3.4 - 3.6$.
-
-The quasar spectra analyzed in this paper were taken from the Sloan
-Digital Sky Survey, Data Release 7 \citep{sdssdr7}.  
-We retrieved
-the `best' 1D spectrum for every source flagged as a QSO or HIZ\_QSO.
-This totalled 102,418 unique spectra\footnote{  
-The spectra were processed through our automated algorithms for
-finding absorption-line features and damped \lya\ candidates
-\citep{phw05,shf06}.  
-Approximately 10 of the spectra failed 
-to be processed (primarily because the SDSS-repoted emission redshift
-is erroneous) and were removed from any subsequent analysis.}.
-The SDSS survey employs a 
-fiber-fed, dual-camera spectrometer that provides continuous wavelength coverage
-from $\lambda \approx 3800-9200$\AA\ at a spectral resolution of 
-FWHM~$\approx 150 \mkms$.
-The SDSS team employs a custom, data-reduction pipeline that performs
-sky subtraction using emprical measurements from fibers placed
-to avoid objects detected in the SDSS images.
-The majority of data suffer from excessive sky noise at long
-wavelengths ($\lambda > 8000$\AA)
-and the instrument throughput and atmospheric absorption
-limits the sensitivity at the shortest wavelengths ($\lambda < 4200$\AA).
-
-A survey for \ion{H}{1} Lyman limit absorption in quasar spectra
-invovles two principle steps.  First, one must assess
-the flux at wavelengths near the Lyman limit
-in the quasar's rest-frame, $\lambda \lesssim \mlll(1+\mzem)$.  
-We discuss our procedure for this step in the following section.  
-The second step is to 
-estimate the flux at wavelengths blueward of LLS candidates.
-There are several characteristics of the SDSS spectroscopy which
-negatively affect this estimate.  A generic concern is the poorer instrument
-response at the bluest wavelengths.  At the bluest wavelengths,
-many of the spectra exhibit a very low signal-to-noise ratio 
-and yield flux estimates consistent with zero, even without an
-intervening LLS.
-Therefore, we have limited our survey to redshifts $\mzlls \ge 3.3$
-corresponding to $\lambda > 3920$\AA.
-In practice, we restrict the quasar sample to objects with
-$\mzem \ge 3.6$ and perform a search for LLS
-at all redshifts, but then only analyze absorption systems with
-$\mzlls \ge 3.3$.  We also limit the survey to quasars with
-$\mzem \le 5$ because the SDSS spectra of higher redshift objects
-are generally too low S/N to permit a robust analysis.
-Figure~\ref{fig:snz}a presents histograms of the emission redshifts
-for the statistical sample and the signal-to-noise of the
-absorbed continuum at the Lyman limit
-(\sna; see below for the definition).
-
-Another difficulty with the SDSS spectra at blue wavelengths
-is that the two-dimensional spectra of faint sources may be improperly traced.
-On occasion, the 1D extractions
-include flux from a neighboring object and yield a systematic 
-overestimate of the flux.  This effect reduces the estimated opacity
-for a LLS.  
-Another issue, especially with a fiber-fed spectrometer, is that
-the sky model is estimated from nearby fibers that are intentionally
-placed on `object-free' regions of the sky.  Although the SDSS
-project has worked carefully to mitigate the effects of variable
-fiber efficiency and XXX \cite{skysub},  significant misestimates 
-of the sky occur.  
-We have identified tens of objects where the extracted
-flux is significantly negative, indicating an overestimate
-in the sky model.  
-This may convert a partial LLS (with $\mtll < 1$) into
-an LLS.  By a similar token, a proper $\mtll \ge 2$ LLS may
-appear as a pLLS if the sky is underestimated.
-We proceed under the expectation that this effect
-is nearly random, i.e.\ for every underestimate of the sky there
-is a corresponding overestimate, but this has not been rigorously
-established.  
-The SDSS fibers are sufficiently wide
-(diameter of $3''$) that they will occasionally include flux
-from a projected neighbor.  These coincident objects may be
-much fainter than the quasar at redder wavelengths, but they
-could contribute all of the flux blueward of a strong LLS
-and lead to an underestimate of the LL opacity\footnote{An amusing
-(and plausible) systematic effect related to this is contamination
-by the light reflected from terestrial satellites crossing the night sky.  
-Even a brief `exposure' through the 3$''$ fiber could dominate the
-flux at the bluest wavelengths, although this should generally be
-mitigated by the fact that the SDSS team aquires 
-3 unique exposures per target.}.
-
-\section{The Absorbed Quasar Continuum}
-\label{sec:continuum}
-
-Absent any other sources of opacity, one can trivially
-estimate \tll\ from
-the quasar spectrum through measurements of the flux
-both redward and blueward of the observed Lyman limit (Equation~\ref{eqn:flux}).  
-In practice, however,
-the quasar flux is also attenuated by line opacity from the so-called
-\lya\ forest (a.k.a., the intergalactic medium; IGM).
-For example, consider a Lyman limit system at $\mzlls = 3.5$
-intervening a $\mzem = 4$ quasar.  The LLS attenuates the quasar flux
-blueward of $\mlll^{\rm LLS} = 4103$\AA.  At this wavelength,
-the quasar spectrum recorded on Earth will also include opacity
-from the \lya\ forest at 
-$z_{\rm \mlya} = (1+\mzlls)(\mlll/\lambda_{\rm Ly\alpha}) - 1$,
-\lyb\ absorption from the IGM at 
-$z_{\rm Ly\beta} = (1+\mzlls)(\mlll/\lambda_{\rm Ly\beta}) - 1$, etc.
-It is necessary, therefore, to account for these additional sources
-of opacity when estimating \tll.
-
-We can express
-the observed quasar flux $F_{\rm obs}$ in terms of
-the intrinsic flux (just) redward of the Lyman limit $F_{\rm int}$ as
-
-\begin{equation}
-F_{\rm obs} (\lambda \gtrsim \mlll) = F_{\rm int} \exp [-\mtigm(\lambda)] \cmma
-\end{equation}
-where \tigm\ is the effective opacity of the IGM from
-Lyman series line-opacity\footnote{In the following, we do not
-explicitly derive the 
-opacity from metals in the IGM, but these may be considered included in \tigm.}.
-The LLS introduces an additional, continuous opacity:
-
-\begin{equation}
-F_{\rm obs} (\lambda \le \mlll) = 
-  F_{\rm int} \exp [-\mtigm(\lambda) -\mtll(\lambda)] \perd
-\end{equation}
-A precise estimate of \tll, therefore, requires an estimation
-of the absorbed quasar flux not its intrinsic flux.  Conveniently,
-this quantity is the observed flux recorded in the spectrum at
-$\lambda \gtrsim \mlll$.  
-There are still signficant challenges because
-the IGM opacity is stochastic on both small (individual Lyman lines)
-and modest scales (many 10\AA) 
-and 
-the intrinsic quasar spectrum (both shape and normalization) varies
-from source to source.
-We now describe an automated procedure
-used to infer the absorbed continuum from each quasar spectrum.
-
-The traditional method of estimating the
-quasar continuum is to first identify
-regions of unabsorbed quasar flux and then to interpolate a continuum level
-between these regions.  For quasars at
-high redshift, this method is particularly error prone, because at
-wavelengths below \lya\ emission we expect few (and at very
-high redshift, none) of the pixels to be free
-of absorption from the IGM.   Moreover, this
-traditional method frequently requires by-hand modification,
-which is time-intensive and subjective to individual biases.
-Methods do exist to automatically generate a quasar
-continuum from emission-line characteristics \citep[e.g.][]{suzuki+05},
-but these are designed to infer the intrinsic quasar spectrum
-not the IGM-absorbed continuum.
-Our approach is to match a template model of the average absorbed
-continuum to each spectrum,
-allowing for a large-scale tilt (i.e. a unique underlying power-law slope)
-and arbitrary normalization.
-
-Our first step is to derive the templates for the average absorbed
-quasar continuum.  Because the line-density of the IGM and therefore \tigm\
-increase with redshift, we perform this analysis in small redshift intervals
-($\delta z = 0.3$ to 0.6; Figure~\ref{fig:template}). 
-For every quasar within the redshift interval,
-we shift the spectrum to the quasar rest-frame 
-using the SDSS reported \zem\ value.  
-Next, we "detilt" the spectrum by removing a power-law shape.
-This power-law is determined as follows.  We have
-constructed from the SDSS-DR3 dataset an average template spectrum,
-archived in XIDL\footnote{http://www.ucolick.org/$\sim$xavier/IDL}
-as ``full\_SDSS\_LLS.fits''.
-For each individual quasar spectrum,
-we sample quasar pixels with wavelengths greater 
-than \lya\ emission, divide by the template spectrum,
-and measure the spectral slope of the resulting spectrum.
-
-After aligning the spectra in the quasar rest-frame
-(nearest pixel), we median-combine the data in each redshift 
-interval\footnote{This stack is not optimal for deriving \lya\
-forest statistics \citep{dlw08}.}.
-The resultant template
-represents the median intrinsic quasar continuum modulated by the median
-flux decrement of the IGM.  Due to the presence of
-Lyman limit systems, the quasar templates will not be useful at
-wavelengths near and below the rest-frame Lyman limit;
-this portion of the spectrum, however, can be used to 
-constrain the mean free path to ionizing radiation \citep{pwo09}.
-For wavelengths blueward of 920\AA, therefore,
-we set the template to have the value recorded 920\AA.
-Conveniently, there are no strong emission features in the
-quasar SED at these wavelengths \citep[e.g.][]{telfer02}.
-The resultant template spectra are shown in Figure \ref{fig:template}.
-
-With the templates constucted, a model of the absorbed continuum
-for each quasar is determined as follows.
-First, we shift the observed quasar spectrum to the rest-frame
-and divide by the appropriate template spectrum (i.e.\ according to \zem).
-Second, we sample the quasar in the wavelength range 
-$950 \rm \AA < \lambda < 1800 \rm \AA$ and fit a power-law 
-(p$(\lambda)$ = A + B log[$\lambda$/\AA]) to the observed 
-flux, weighting by the inverse variance array.
-The emission lines in this spectral range may bias the fit,
-but we do review and modify these fits (see below).
-The product of this power-law with the template, when
-shifted to the observed frame, provies our model for the
-absorbed quasar continuum.  The power-law parameters derived
-in this fashion are listed in Table~\ref{tab:quasars}.
-Sample fits are shown in Figure~\ref{fig:ex_conti}.
-With these models, we can calculate the ratio of the absorbed
-continuum to the $1\sigma$-error array at the Lyman limit,
-which we denote as \sna.
-Figure~\ref{fig:snz}b shows the distribution of \sna\ values
-for the statistical survey.
-
-\section{Lyman Limit System Search and Characterization}
-\label{sec:lls}
-
-In the following, we parameterize a LLS by two quantities:
-(1) the absorption redshift \zlls\ and
-(2) the total \ion{H}{1} column density \nhi.
-Although the \ion{H}{1} Lyman series lines are sensitive to the component
-structure and the Doppler parameters (also known as $b$-values)
-of the `clouds' comprising an LLS,
-the opacity blueward of \lll\ is insensitive to the details.
-Furthermore, the SDSS spectra are generally of too poor quality
-to constrain such structure using the observed Lyman series lines.
-Therefore, our model of an LLS assumes a single cloud with a 
-Doppler parameter of $b=30 \,\mkms$.
-An implication of this parameterization is that two systems with
-small redshift separation are modeled as a single system with
-the total of the \nhi\ values.  Our tests with mock spectra ($\S$~\ref{sec:mock})
-indicate that two absorbers with $\delta z < 0.1$ are often
-indistinguishable from a single LLS.  The survey presented here,
-therefore, refers to LL absorption smoothed over a redshift
-interval of $\delta z \approx 0.1$.  We return to this point
-in our presentation and discussion of the survey results.
-
-We have developed an algorithm ({\it sdss\_findlls})
-to automatically search for
-and characterize LLS absorption in quasar spectra.
-In brief, the code generates a set of model spectra
-for the line and continuum opacity of
-a single LLS with redshifts covering 
-$z=z_0=(\lambda_0/\mlll-1)$ to (\zem+0.2) where $\lambda_0$
-is the starting redshift of the SDSS spectrum and \zem\ is the
-quasar emission redshift reported in the DR7\footnote{Modified by
-the analysis of \cite{phh08} where applicable for quasars from 
-the DR5 release.}.
-The grid of models assumes \nhi\ column densities 
-$\log \mnhi = 16.0, 16.2, 16.4, ..., 19.8$
-and a Doppler parameter $b = 30 \mkms$.  
-We implement a grid with 0.2\,dex spacing in \nhi\ because very
-few of the spectra have sufficient S/N to provide a more precise
-estimate.  Furthermore, we estimate systematic uncertainties
-(e.g.\ continuum placement, sky subtraction) to be of this order.
-These models are convolved with the SDSS instrumental
-resolution and then applied to the absorbed quasar continuum 
-($\S$~\ref{sec:continuum}).
-Finally, the code constructs a $\chi^2$ grid in \zlls\ and \nhi\
-space, identifies the minimum $\chi^2$, and records the `best-fit' values.  
-In general, the spectra provide very little constraint
-on \nhi\ for values exceeding $10^{17.5} \cm{-2}$ until the \lya\
-profile becomes damped \citep[e.g.][]{phw05}.
-Therefore, we report lower limits to \nhi\ for any LLS with 
-$\mtll \ge 2$.  This approach differs from previous methods
-which focused solely on the Lyman limit \citep[e.g.][]{sl94} or
-relied on `by-eye' analysis \citep{lzt9X}.
-
-For sightlines with a single LLS having $\mnhi > 10^{17.2} \cm{-2}$
-and good \sna\ (i.e.\ greater than 5 pix$^{-1}$ 
-at $\mlll^{em} \equiv \mlll \times [1+\mzem]$),
-we find that the automated
-algorithm is highly successful on its own.
-In practice, however, there are several aspects of the data and
-analysis that require visual inspection of the spectra
-and interactive modification to the model:
-First, many spectra have 
-such low S/N that \zlls\ and \nhi\ are poorly determined.
-In these cases, the a local minimum in $\chi^2$ can occur which
-gives a misestimate of these quantities.
-Second, the presence of multiple
-absorbers along the sightline (e.g.\ one or more pLLS with a lower
-redshift LLS) gives a spectrum that cannot be well
-modeled by a single LLS.
-Third, a non-negligible number of the spectra
-retrieved from the SDSS database purported to be high $z$
-quasars are either at a lower redshift or some other astronomical
-object altogether.  
-Fourth, we found that half of the absorbed continuum models required
-scaling to higher or lower value by greater than $10\%$.  
-Finally,  we prefer to avoid quasars with 
-with strong broad absorption line (BAL) or associated systems
-to focus the analysis on intervening LLS.
-
-Given the above complications to an automated analysis, we
-built a graphical user interface (GUI) within the IDL software
-package ({\it sdss\_chklls}; bundled within XIDL)
-that inputs the data and best-fit LLS model for each object.
-Two of the authors (JXP and JMO) used this GUI to validate
-and/or modify all of the models.  These authors 
-flagged erroneous spectra (159 examples), 
-strong BAL or associated absorption (quasars showing very strong
-\ion{C}{4}, \ion{N}{5}, and \ion{O}{6} absorption; 290 quasars), 
-or data with such low
-S/N that any analysis was deemed impossible (114 spectra).
-For the remainder of sightlines, the authors
-could modify the continuum (via a multiplicative scalar; Table~\ref{tab:quasars})
-and/or change the model of LLS absorption (i.e.\ \zlls, \nhi).
-This includes absorption due to candidate pLLS.  
-In many cases, \zlls\ was modified to correspond to the strongest,
-local \lya\ absorption line at $\lambda = (1+\mzlls) \times 1215.67$\AA,
-especially for those systems that also showed absorption at the
-expected wavelength for \lyb.
-
-After every sightline was analyzed in this manner,
-the results from the two authors were compared to assess
-consistency.  Roughly half of the spectra were reviewed
-because of conflicts in the models.
-The majority of these were associated 
-with the absorbed continuum placement which implied 
-differences in the search path of $|\Delta z| > 0.1$
-(see $\S$~\ref{sec:path}).
-In the majority of these cases, we simply averaged the
-two estimations of the continuum.  
-The second most frequent conflict was on the definition
-of strong BAL absorption, primarily because we did not adopt
-uniform or strict criteria.  In most cases, we 
-conservatively excluded the sightline.
-There were also $\approx 100$ cases where one author estimated
-$\log \mnhi = 17.4$ when the other estimated   
-$\log \mnhi = 17.6$, i.e., straddling the $\mtll=2$ boundary
-that defines our LLS search. 
-These were especially scrutinized for the presence of
-higher-order Lyman series lines. 
-Where necessary, the final best-estimate for \nhi\ was 
-deferred to the third author (GW).
-
-Tables~\ref{tab:survey} and \ref{tab:llscand} list the set of 
-Lyman limit systems identified in the SDSS-DR7 for systems
-that (respectively) influence our statistical analysis and otherwise. 
-For each system, we list our best estimate for \zlls\ and the \nhi\ value.
-Because the data offer minimal constraint on \nhi\
-for values exceeding 10$^{17.6} \cm{-2}$,
-in the statistical sample we only report a lower
-limit to \nhi\ for all systems with best-estimates of
-$\mnhi \ge 10^{17.6} \cm{-2}$. 
-For the pLLS, the typical $1\sigma$ uncertainty
-is approximately 0.2\,dex for $\mnhi \ge 10^{17} \cm{-2}$
-and is dominated by systematic error in
-the continuum placement and the stochastic nature of the IGM opacity. 
-As noted above,
-\zlls\ was frequently modified
-in the interactive analysis to correspond to strong \lya\ and
-\lyb\ lines.
-Our analysis of mock spectra indicate typical redshift
-uncertainies of $\sigma(z) < 0.02$ with occasional
-`catastrophic failures' due to line-blending or spurious
-spectra (Appendix~\ref{appx:mock}).
-No attempt was made to improve this
-estimate by searching for the presence of metal-line
-absorption (e.g.\ \ion{C}{4}) outside the \lya\ forest.
-There is a tendency, both in the automated algorithm and in 
-interactive analysis, to set \zlls\ at the highest value possible
-that can be accomodated by the data.  To this extent, we suspect
-that there is a modest bias in our \zlls\ values to slightly
-higher redshifts (less than 0.01 on average, but with
-the occasional large offset).
-
-Figure~\ref{fig:ex_conti} shows a representative sample of four quasar
-spectra, zoomed into the region blueward of \lyb, with the
-absorbed continuum and LLS models indicated. 
-We provide snapshots of the 
-LL region for all quasar spectra in the statistical sample 
-online\footnote{http://www.ucolick.org/$\sim$xavier/SDSSLLS}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Survey Path}
-\label{sec:path}
-
-Analagous to galaxy surveys where one defines a search
-volume based on the depth of imaging and spectroscopic
-follow-up, measurements of the incidence of quasar absorption line systems
-requires an estimate of the total spectral path sensitive 
-to a robust search.  This is generally referred to as the redshift
-path covered (by translating observed wavelength into redshift).
-For the survey of LLS, we have adopted the following criteria
-for including spectral regions in the search.  These are based on our 
-automated and interactive analysis of the SDSS spectra, 
-our modelling of Keck/LRIS follow-up spectra, and our analysis
-of simulated spectra ($\S$~\ref{sec:mock}, Appendix~\ref{appx:keck}):
-
-\begin{enumerate}
-\item The search path will begin at a minimum redshift of
-  $z_{\rm start} \ge 3.3$
-\item For the intervening LLS sample, the search path ends at the redshift
-  $z_{\rm end}$
-  corresponding to 3000~\kms\ (relativistic) blueward of \zem.
-\item The absorbed continuum flux must exceed twice the estimated error array, 
- i.e.\ \sna.
-\item The search path begins at a maximum offset of 
-   $\delta z = \mzem - z_{\rm start} \le 0.4$.
-\end{enumerate}
-The first criterion is motivated by the starting wavelength 
-of the SDSS spectra ($\lambda_0 \approx 3800$\AA) and the
-poorer quality of the data at the bluest wavelengths.
-For redshifts less than 3.3, there is insufficient spectral
-coverage and/or data quality to confidently assess the
-presence of an LLS.  The second criterion minimizes
-the influence of the quasar and its environment on
-the analysis.  This criterion is relaxed in the study of PLLS.
-
-The third criterion is the most subjective, yet important,
-for setting the redshift survey path of each quasar.
-Algorithmically,  we impose this constraint by identifying
-the first pixel blueward of $\mlll^{\rm em} \equiv \mlll(1+\mzem)$
-where our model of the absorbed quasar continuum falls
-below twice the median-smoothed (15 pixels) $1\sigma$ error array. 
-This pixel defines the starting redshift \zstrtt\ corresponding
-to a \sna=2 limit.  
-If the first pixel blueward of $\mlll^{\rm em}$ does not satisfy
-the S/N threshold, the quasar has zero redshift path, 
-i.e.\ $z_{\rm start} = z_{\rm end}$.
-One can, of course, define 
-starting redshifts
-corresponding to higher (or lower) \sna\ limits;  indeed, our
-fiducial choice of \sna=2 should be considered arbitrary, although 
-it is guided by our analysis of real and simulated spectra.
-And to avoid a systematic bias associated with pLLS (see $\S$~\ref{sec:pLLS}),
-one must choose the \sna\ criterion to be sufficiently high
-to discover $\mtll \ge 2$ LLS even in the presence of a 
-pLLS\footnote{Contrary to some of the earliest work 
-on LLS \citep[e.g.][]{tytler84},
-we do not use surival statistics to estimate the number of LLS
-at redshifts below any observed LLS.}.
-We investigate the impact of this choice on our results
-later in the manuscript.
-
-The starting redshift is further modified by the presence 
-of Lyman limit absorption.  In the case of a $\mtll \ge 2$ absorber,
-the quasar flux is severely depressed below $\lambda = \mlll (1+\mzlls)$
-and we terminate the search path at this wavelength.  
-Specifically, this implies $z_{\rm start} \ge \mzlls$ for all
-sightlines with an $\mtll \ge 2$ LLS.
-For sightlines where one or more pLLS are identified\footnote{Again,
-all pLLS should be considered candidates.  Some of the spectral
-features modelled as pLLS are instead due to unusual variations
-in the absorbed quasar continuum (e.g.\ highly reddened quasars).}, 
-we had originally intended to terminate the search once the absorbed 
-quasar continuum convolved with the pLLS absorption failed to satisfy
-the S/N threshold.  In our analysis of mock spectra, 
-however,  we found that this introduces a ``pLLS-bias'' where the
-incidence of $\mtll \ge 2$ LLS is overestimated.
-In part, our \sna=2 threshold is chosen so that one can 
-robustly search for $\mtll \ge 2$ LLS even along sightlines where
-one or more pLLS are present.
-
-Table~\ref{tab:survey} presents the list of quasars in SDSS-DR7
-that 
-(i) have $5 \ge \mzem \ge 3.6$, 
-(ii) were not identified to
-exhibit strong BAL signatures, and 
-(iii) have $3.3 \le \mzstrtt < \mzem$.
-There are \nstatqso\ quasars satisfying these criteria.
-For each sightline, we list the starting redshifts for
-\sna=2 and 3 limits.
-We report results for two values of the S/N threshold to
-search for data-quality biases. 
-Table~\ref{tab:survey} also lists all Lyman limit systems
-with $\mzlls \ge \mzstrtt$.  
-We do list these quantities for quasars with $\mzem < 3.6$,
-but these were not included in our final statistical analysis
-because of the bias related to SDSS targeting criteria
-previously mentioned by \citep{pwo09}.
-
-Using the values presented in Table~\ref{tab:survey}, it is
-straightforward to calculate \zend\ and the redshift search
-path for each quasar: $\Delta z_i = \mzend - \mzstrt$.  For
-a given \sna\ limit, the total search path for the full dataset is
-
-\begin{equation}
-\Delta z_{\rm TOT} = \smm \Delta z_i  \perd
-\end{equation}
-We calculate $\mztot^{S/N=2} = 96$.
-%of XX increase over the combined search paths of all previous
-%$z>2$ surveys for LLS \citep{peroux05}.
-To maintain a homogeneous sample and set of search criteria,
-we do not include previous studies in our analysis.
-We compare against previous results in $\S$~\ref{sec:discuss}.
-
-In Figure~\ref{fig:goz}, we present the sensitivity function
-\gz\ which expresses the number of SDSS quasars at redshift $z$
-where a robust search for LLS is possible.
-The several solid curves represent differing \sna\ limits for the survey.
-We also present the sensitivity function for proximate LLS (PLLS)
-which corresponds to the sample of quasar spectra that satisfy
-the $\msna \ge 2$ criterion at 3000~\kms\ blueward of \zem.
-
-With the definition of the search path 
-and the identification of the Lyman limit systems along each
-sightline ($\S$~\ref{sec:lls}),
-it is straightforward to calculate the incidence of intervening
-LLS per redshift interval, \lzlls.  
-The standard estimator is to compare the total number of LLS
-against the total survey path in discrete redshift intervals.
-We will return to evaluate \lzlls\ and discuss the values
-after exploring several sources of systematic error.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Mock Spectra and Systematic Errors}
-\label{appx:mock}
-
-With a survey the size of SDSS, one can quickly reduces the statistical
-noise in measurements to very small levels.  In this
-regime, one must carefully assess all sources of systematic
-error as these may dominate the measurement uncertainty.
-To this end, we have conducted a range of tests with mock
-spectra as described in this section.
-
-\subsection{Mock Spectra Construction}
-
-We generated a set of 800 mock SDSS quasar 
-spectra and analyzed them in the same way as the real data in 
-order to assess bias and completeness in our LLS survey. 
-The \ion{H}{1} forest absorption spectra 
-were generated via a Monte Carlo routine similar 
-to the one described in \cite{dww08}, 
-assuming that the \lya\ forest is well characterized by 
-three independent distributions: 
-(i) the \lya\
-line-incidence $\ell_\alpha (z) \propto (1+z)^\gamma$, 
-(ii) the \ion{H}{1} column density distribution $f(\mnhi) \propto \mnhi^\beta$, 
-and (iii) the Doppler parameter distribution parameterized as 
-$f(b) \propto b^{-5} \exp{-b_\sigma^4/b^4}$ \citep{hr99}. 
-Each simulated line of sight was filled with \ion{H}{1} \lya\ absorption lines at 
-$2<z<4.6$ until the \ion{H}{1} \lya\ effective optical depth was consistent with 
-\cite{fpl+08}, both in normalization and redshift evolution. We did not model the 
-$z\sim 3.2$ dip in the effective optical depth 
-measured by Faucher-Giguere et al., 
-and instead adopted a simple power-law 
-$\tau_{\rm eff}^{\alpha} =0.0011(1+z)^{4.23}$. 
-If the number of lines in a given patch of the forest is 
-Poisson-distributed, a power-law line density evolution 
-$\ell_\alpha (z) \propto (1+z)^\gamma$ yields a power-law 
-effective optical depth evolution $\tau_{\rm eff}^\alpha
-\propto (1+z)^{\gamma+1}$ \citep{zuo93}. 
-The column density distribution was modeled with a single power-law index 
-$\beta=-1.5$ for $12<\log(\mnhi)<19$, but with a 0.5\,dex break at 
-$\log(\mnhi)=14.5$ in order to account for the dearth of high column density lines, 
-consistent with observations \citep[e.g.][]{hkc+95,kim02}. 
-For the Doppler parameter distribution we set 
-$b_\sigma=24 \, \mkms$ \citep{kim+01}.
-
-Because SLLSs $(19 \le \log(\mnhi)<20.3)$ and DLAs $(\log(\mnhi) \ge 20.3$) have 
-different column density distributions and are usually excluded in 
-measurements of $\tau_{\rm eff}^\alpha$,
-these were added after the $\log(\mnhi)<19$ 
-line forest converged to the chosen $\tau_{\rm eff}^\alpha (z)$. 
-To constrain the redshift evolution of SLLSs, we combined the sample by 
-\cite{opb+07} and the lower limit given in \cite{rtn06}, 
-yielding $\ell_{\rm SLLS} (z) \sim 0.066(1+z)^{1.70}$. 
-For the SLLS column density distribution we adopted $\beta=-1.4$ 
-\citep{opb+07}. 
-The DLAs were modeled via $\ell_{\rm DLA} (z) =0.044(1+z)^{1.27}$ \citep{rtn06} 
-and $\beta=-2$ \citep{phw05}, 
-ignoring deviations in \fnhi\ from a single power law. 
-The Doppler parameter distribution was left unchanged.
-
-With the overall opacity of the modeled \lya\ forest consistent with observations, 
-and the high column density systems incorporated, we used the generated line lists to compute HI Lyman series (up to Ly30) and Lyman continuum absorption spectra.
-In total we computed 800 different lines of sight for quasars in the redshift range of our sample,
-160 each at $z=3.4, z=3.6, z=3.8, z=4.0$ and $z=4.2$, respectively. 
-From these we then generated mock SDSS spectra.
-First, the resolved \ion{H}{1} forest spectra were multiplied onto synthetic quasar SEDs generated from principal component spectra \citep{suzuki+05,suzuki06}.
-We then degraded the resolution of the mock spectra to $R=2000$ by convolving them with a Gaussian, and rebinned them to $\delta v=69 \mkms$, matching the approximate 
-resolution and pixel size of the SDSS spectra. Finally, we added Gaussian noise to the mock SDSS spectra. In each mock spectrum the S/N was normalized in the quasar continuum 
-at 1450\AA\ and varied as a function of flux and wavelength according to the throughput of the SDSS spectrograph. The sky level was approximated as a constant and readout noise was also incorporated. 
-Finally, for a subset of the mocks
-we imposed a sky subtraction error implemented by subtracting/adding
-a constant to the spectrum.
-These were generated to mimic such systematic errors
-that occasionally occur in the SDSS spectra.
-
-Four representative examples are shown in Figure~\ref{fig:mockex}.
-
-\subsection{LLS Recovery and Sky Subtraction Bias}
-
-Two of the authors (JXP,JMO) analyzed 500 of the mock spectra using
-the identical tools and procedures applied to the SDSS spectra;
-these steps were done without knowledge 
-of the mock line distribution and column densities (constructed by author GW).
-The results for the two authors were nearly identical; the following
-discussion and figures refer to the results related to JXP.
-Figure~\ref{fig:mockdz} summarizes the completeness and several biases
-uncovered by our analysis.  In the top panel, all cases where a mock
-$\mtll \ge 2$ LLS exists with $\mzabs > 3.2$ and an LLS was `observed'
-are presented; these correspond to $> 80\%$ of the cases.  
-Specifically, we plot the offset $\delta z$
-between the true and
-observed LLS absorption redshifts as a function of the \sna\ of the
-spectrum.  
-We find excellent agreement (small $\delta z$), nearly independent
-of the \sna\ of the data.
-There are, however, a number of cases with $\delta z > 0.01$, primarily
-related to the blending of absorption lines (see below).
-
-The lower panel in Figure~\ref{fig:mockdz} presents those cases
-that are false negatives (diamonds) and false positives (triangles).
-The latter are very rare. [seem too rare..]
-The former, however, did occur quite often in our analysis and can
-be divided into two classes:  
-(i) cases with $|\delta z| < 0.05$ which are proper false negatives, i.e.\
-true $\mtll \ge 2$ LLS that were modeled as pLLS;
-(ii) cases with $\delta z > 0.1$ which are sightlines where a
-higher $z$ pLLS precluded the detection of a lower $z$ LLS.
-The majority of the latter cases 
-are due to bona-fide pLLS at higher $z$ which greatly diminish
-the S/N of the spectra at shorter wavelengths and `obscure'
-the presence of a $\mtll \ge 2$ LLS.
-Almost none of these cases, however, satisfy the selection
-criteria established in $\S$~\ref{sec:survey};  either the
-data have too low \sna\ or the absorption redshift of the LLS
-gives $\mzem - \mzabs \ge 0.4$.
-
-The first class of false negatives, meanwhile,
-are almost exclusively associated with spectra
-that had systematically low estimates for the sky background.
-In these cases, a $\mtll \ge 2$ LLS has an apparent flux 
-at $\lambda < \mlll$ and therefore was modeled as a pLLS.
-This is the dominant effect of a sky subtraction bias.
-Although our mock spectra had even numbers of over and under-subtracted
-sky backgrounds, only the former
-are relatively easy to identify (large
-regions of spectra are significantly negative) and ignore.
-The net effect of a random sky subtraction error is a 
-systematic underestimate in the incidence of LLS.
-We stress, however, that the magnitude and frequency of poor
-sky subtraction in the mock spectra was intentionally elevated
-so that we could explore these effects.  The incidence of
-such effects within the SDSS spectra is much lower, an
-assertion supported by our follow-up spectra with Keck/LRIS
-(Appendix~\ref{sec:keck}).
-Therefore, we are confident that the sky subtraction bias 
-gives rise to a $<10\%$ systematic error for \lzlls.
-
-\subsection{The pLLS Bias}
-\label{sec:pLLS}
-
-Originally, we inteded to perform a search for LLS in spectra
-with \sna=1 to maximize the pathlength of the survey 
-(a nearly 4$\times$ increase over \sna=2).  Our
-tests with mock spectra and follow-up observations with 
-Keck/LRIS (Appendix~\ref{appx:lris}) indicated that we 
-could robustly identify $\mtll \ge 2$ LLS in such data.
-We also noted that many of the spectra showed
-pLLS candidates which reduced \sna\ to below 1 and made the
-search for $\mtll \ge 2$ LLS more challenging.  Our
-reaction was to redefine the search path 
-by attenuating the absorbed continuum due to
-any identified pLLS candidates and then reapply
-the \sna\ criterion for the remaining $z<z_{\rm pLLS}$
-spectral range.
-
-In princple, this modification should provide an unbiased
-search for $\mtll \ge 2$ LLS.  Our trials with mock spectra,
-however, revealed an insidiuous bias associated with this
-redefinition of the search path.  Specifically,  it is very
-difficult to identify pLLSs when they occur at a small
-redshift offset ($\delta z \lesssim 0.1$) redward
-from a $\mtll \ge 2$ LLS.
-In these cases, instead of the search being terminated at
-the redshift of the pLLS with the lower $z$ LLS ignored,
-the pLLS is ignored and the LLS is included within the
-statistical sample.   Furthermore, the redshift
-of the recovered LLS is biased to a higher value which 
-reduces the survey pathlength by a small but non-negligible
-quantity.  Together, these two effects lead to an overestimate
-of \lzlls\ by values ranging from $30-50$\%.  
-It is very difficult to precisely estimate the magnitude of this
-systematic bias for it depends sensitively on \lzlls, the 
-incidence of pLLS, and the quasar \zem\ distribution.
-In our opinion, one cannot robustly correct for 
-this systematic pLLS bias and we caution against performing
-any analysis that would be subject to it.
-For these reasons, we {\it ignore} pLLS when defining
-the survey path and performing the search for $\mtll \ge 2$ LLS.
-
-\subsection{The Blending Bias}
-
-As noted in the previous sub-section, LLS and pLLS
-that lie close to one another in redshift are very difficult
-to distinguish as individual systems.
-This is even true in the limit where one has spectra with
-exquisite S/N and resolution when $\delta z < 0.1$.
-With SDSS spectra, the limited information provided by the Lyman
-limit and the strongest Lyman series lines is insufficient
-to robustly distinguish multiple LLS from a single system.
-This leads to a ``Blending Bias'' that manifests itself in several
-ways.
-
-First, the blending bias increases the number of LLS
-observed because pairs of pLLSs blend together to give a single
-system with $\mtll \ge 2$.
-Second, the absorption redshifts of the LLSs are shifted to higher
-redshifts because one generally adopts \zlls\ from the higher
-of the pair of systems.  
-This leads to a smaller survey path and possibly a
-higher inferred incidence of LLS. 
-More importantly (see below), many LLS are shifted into the
-proximate region of the quasar. 
-This causes an underestimate of \lzlls\
-for intervening LLS and an overestimate of PLLS.
-
-We explored the quantitative effects of the blending bias with
-the following analysis.  We constructed a set of mock absorption
-lines for each quasar in the statistical survey (Table~\ref{tab:survey})
-with an incidence set to match our measurements ($\S$~\ref{sec:loz}).
-Specifically, we adopted an \nhi\ frequency distribution
-
-\begin{equation}
-f(\mnhi,z) = C \mnhi^\beta \, \ltp \frac{1+z}{1+z_*} \rtp^\gamma
-\label{eqn:fnmock}
-\end{equation}
-with $\beta = -1.3$ for $10^{16.5} \cm{-2} \le \mnhi \le 10^{19.5} \cm{-2}$
-and $\beta = -2$ for $\mnhi \ge 10^{19.5}$, $z_* = 3.7$,
-$\gamma = 5.1$ and $C=1.244 \sci{5}$.
-From the mock absorber list we identified all LLS with $\mnhi \ge 10^{17.5} \cm{-2}$.
-This formed the control sample.
-Then, we blended together all systems with $|\delta z| \le \delta z_j$
-where $\delta z_j = [0.01, 0.05, 0.1, 0.2]$ and reidentified systems
-satisfying $\mnhi \ge 10^{17.5} \cm{-2}$.  When blending two or more 
-systems together, we set \zabs\ to the maximum of all the lines.
-Finally, we then calcualted the incidence of LLS using the survey
-path and LLS for each $\delta z_j$.
-
-Figure~\ref{fig:bbias}a presents the results of the blending bias in
-terms of the enhancement/decrement of the incidence of $\mtll \ge 2$ LLS
-relative to the perfect model ($\delta z_j = 0$).
-For $\delta z_j < 0.1$, there is only a small and ignoreable effect.
-For $\delta z_j \ge 0.1$, however, we predict a systematic underestimate
-for the incidence of intervening LLS, especially at $z>4$ where
-the absolute incidence is highest.  
-This deficit in \lzlls\ runs contrary to expectation and is entirely
-due to the redshift bias where the blended LLS end up with \zlls\
-within the proximate region.  
-In turn, we predict a systematic over-estimate of \lzlls\ 
-for PLLS (Figure~\ref{fig:bbias}b).
-[JMO: Consider whether this affects any previous work]
-
-Our experiments with mock spectra indicate that we commonly blend
-together systems with $\delta z_j = 0.05$ to 0.1, with a weak dependence
-on redshift or S/N.  
-We conclude, therefore, that the effects of the blending bias
-on our SDSS analysis are $< 10\%$ for measurements of \lzlls\
-for intervening LLS.
-This is below the current level of the statistical
-error and we will ignore it in the presentation of the results and
-discussion.  For the PLLS, the effect for $\delta z_j = 0.1$ 
-ranges from $20-90\%$ and we will report our results on \lzlls\ 
-for these absorbers as upper limits, especially for $\mzabs > 4$.
-
-Before closing this section, we stress that the blending bias
-affects all previous and future LLS surveys.  In particular,
-we caution that the incidence of LLS cannot trivially be
-used to constrain the \ion{H}{1} frequency distribution \fnhi,
-because the latter assumes that every absorption system is
-a unique, identifiable line.  For the LLS in particular (but
-this is also true for the \lya\ forest), blending smears these
-lines over non-negligible redshift intervals ($\delta z \approx 0.1$)
-and this affect must be considered when comparing against 
-theoretical line densities.
-{\bf [Does this affect our f(N) estimates!!]}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Results}
-\label{sec:results}
-
-In this section, we present the results of our survey.  We
-defer extended discussion of previos work and the implications
-of our analysis to the following section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\lzlls: The Incidence of 
-Intervening $\mtll \ge 2$ LLS per Redshift Interval}
-\label{sec:loz}
-
-The incidence of LLS per redshift interval \lzlls\ 
-is a purely observational quantity, i.e.\ its value 
-is independent of any assumed cosmology.
-Consequently, \lzlls\ has limited physical meaning yet it 
-it is the proper starting point for a discussion
-of our observational survey.
-
-Following standard
-practice, we estimate \lzlls\ from the 
-ratio of the number of LLS $(N_{\rm LLS})$
-detected in a redshift interval to the total search path
-for that redshift interval (\ztot):
-
-\begin{equation}
-\mlzlls = \frac{N_{\rm LLS}}{\mztot}  \perd
-\label{eqn:loz}
-\end{equation}
-The error for \lzlls\ from this estimator is assumed to be dominated
-by the Poission uncertainty in $N_{\rm LLS}$.  Figure~\ref{fig:loz_lls}
-presents the estimates of \lzlls\ for the \sna=2 criterion in
-a set of arbitrary redshift intervals chosen to give roughly 
-constant $N_{\rm LLS}$ per bin (at least for $z<4$).
-Table~\ref{tab:llssumm} lists these values for \sna\ thresholds
-of 2 and 3, and we note no dependence with this threshold.
-
-Figure~\ref{fig:loz_lls} reveals that the incidence of $\mtll \ge 2$ LLS
-increases monotonically for $z>3.5$.
-Following previous work, we have modeled the redshift
-evolution in \lzlls\ as a power-law with the functional form:
-
-\begin{equation}
-\mlzlls = C_{\rm LLS} \ltk \frac{1+z}{1+z_*} \rtk^{\gamma_{\rm LLS}}
-\label{eqn:powlaw}
-\end{equation}
-setting $z_* \equiv 3.7$.
-Using standard maximum likelihood techniques
-\citep[e.g.][]{sim96}, we find best-fit values 
-to the data at $z \ge 3.5$ of
-%These are grabbed from running fig_loz
-$C_{\rm LLS} = \clls$ and 
-$\mglls = \alls$ (68\%\ c.l.).  The best-fit model
-is overplotted on the data in Figure~\ref{fig:loz_lls}.
-The relatively large uncertainty in $\gamma_{\rm LLS}$
-is due to the small redshift interval covered by our survey.
-Nevertheless, we conclude at high confidence ($>95\%$)
-that \lzlls\ is increasing at least as steeply as $\mglls = 2$
-at $z>3.5$.
-
-For $z <3.5$, Figure~\ref{fig:loz_lls} shows two evaluations
-of \lzlls.  The light, solid points show the \lzlls\ 
-values derived from our statistical quasar sample with
-the restriction that $\mzem \ge 3.6$.  
-These values are consistent with an extrapolation
-of the best-fit power-law. 
-The dotted points in the figure, meanwhile,
-show the values of \lzlls\ when one  also surveys
-quasars with $3.4 \le \mzem \le 3.6$.  
-In this case, we find systematically higher \lzlls\
-values which would indicate a non-physical, non-monotonic 
-evolution in \lzlls.  These results confirm the findings
-of PWO09 that the SDSS targeting criteria for quasar 
-spectroscopy biases the sample against sightlines without LLS.
-This leads to a systematically high and erroneous \lzlls.
-
-The sub-panel of Figure~\ref{fig:loz_lls} compares the cumulative number of LLS
-detected in the survey against redshift both as observed (solid)
-and as predicted (dotted) by the best-fit power-law model.  For the
-latter, we adopt the $g(z)$ curves for \sna=2 from Figure~\ref{fig:goz}.
-A one-sided Kolmogorov-Smirnov test yields a probability $P_{\rm KS} = 0.95$
-that the observed distribution is drawn from the adopted power-law
-expression.  We conclude that the power-law model is a good
-description of the observations.
-%We return to a discussion of the relatively large,
-%albeit poorly constrained, exponent in $\S$~\ref{sec:discuss}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{The Incidence of LLS in $\Lambda$CDM}
-\label{sec:lox}
-
-If one introduces a cosmological model, the
-observed incidence of LLS with redshift \lzlls\ may be translated
-into physical
-quantities.  Consider first the average distance a photon travels
-before encountering an LLS with $\mtll \ge 2$, \drlls.  
-Specifically, we define
-
-\begin{equation}
-\mdrlls \equiv \mlzlls^{-1} \frac{dr}{dz} \cmma
-\end{equation}
-where 
-\begin{equation}
-\frac{dr}{dz}  = \frac{c}{(1+z) H(z)}
-\end{equation}
-where
-\begin{equation}
-H(z) = H_0 \ltk \Omega_\Lambda + (1+z)^3 \Omega_m \rtk^{1/2} \perd
-\end{equation}
-Assuming $\Omega_\Lambda = 0.7, \Omega_m = 0.3$, and  $H_0=72 \mkms \rm Mpc^{-1}$
-\citep[e.g.][]{wmap05},
-we find \drlls\ ranges from $\approx 100$ to 40\,Mpc proper distance
-from $z=3.5$ to $z=4.4$ (Table~\ref{tab:summ}).
-This is substantially larger than the seperation of bright quasars 
-\citep[several Mpc 
-for $L_B \ge 10^{40} \rm \, erg \, s^{-1} \, Hz^{-1}$;][]{fg08b} 
-and therefore a simple restatement that 
-the universe was reionized before $z=4$.
-
-Another approach toward exploring the origin of absorption systems, 
-i.e.\ associating
-these systems to structures in the Universe (e.g.\ galaxies, filaments),
-is to compute
-the number of systems per absorption length \llls \citep[][]{bp69},
-where $\ell(X) dX = \ell(z) dz$ and
-
-\begin{equation}
-dX = \frac{H_0}{H(z)}(1+z)^2 dz  \perd
-\end{equation}
-The quantity \llls\ is defined to remain constant if \nlls\ the
-comoving number density
-of structures giving rise to $\mtll \ge 2$ LLS
-times \slls\ the average physical size of the structure 
-remains constant, i.e.\ $\mllls \propto \mnlls \mslls$.
-
-Figure~\ref{fig:complox} presents the evolution of \llls\
-for our cosmology as a function of redshift (see also
-Table~\ref{tab:llssumm}).  
-We observe a rise in \llls\ with redshift of roughly two times
-over the $\approx 1\,$Gyr from $z=3.4$ to 4.4.
-At 99\% confidence, we infer an increase in \llls\ over
-this redshift interval.
-This follows, of course, from the very steep
-redshift evolution observed for \lzlls\ ($\S$~\ref{sec:loz});
-in the $\Lambda$CDM cosmology, an \lzlls\ evolution steeper
-than $(1+z)^{1/2}$ at $z>3$ implies \llls\ is also increasing.
-We conclude
-that \nlls\ and/or \slls\ are increasing with redshift
-at $z \approx 3.5$.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{\lfnhi\ at $z \approx 3.7$}
-
-Although our observations and LLS analysis are insensitive
-to the \ion{H}{1} column densities of the LLS, 
-they do provide an integral
-constraint on the frequency distribution of \nhi\ values
-when combined with other surveys.
-Specifically, we can constrain the
-\nhi\ frequency distribution of LLS per absorption length
-\lfnhi\ at column densities
-$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$ as follows.
-Previous surveys of $z>3$ DLAs and SLLSs 
-have measured \fnhi\ at $z>3$ covering column densities 
-$\mnhi \ge 10^{19} \cm{-2}$ \citep{phw05,opb+07,pw09}.
-These authors have parameterized the
-distribution functions as single (SLLSs) and double (DLAs) power-laws
-of the following form:
-
-\begin{equation}
-\msfnhi = C_{\rm SLLS} \mnhi^{\beta_{\rm SLLS}} 
-\label{eqn:fslls}
-\end{equation}
-
-and
-
-\begin{equation}
-\mdfnhi = C_{\rm DLA} \ltp \frac{N}{N_d} \rtp^{\beta_{\rm DLA}}
-  \; {\rm where} \; \beta_{\rm DLA} =  
-\begin{cases}
-\beta_3:  N < N_d ; \quad \\ 
-\beta_4:  N \geq N_d \\
-\end{cases}
-\label{eqn:fdla}
-\end{equation}
-In Figure~\ref{fig:fn}, we present these frequency distributions
-as bands which represent the approximate $1 \sigma$ uncertainties.
-For the SLLS we have taken $\beta_{\rm SLLS} = -1.3 \pm 0.2$ and
-$C_{\rm SLLS} = 0.25 \pm 0.05$.
-These values are in reasonable agreement with other estimates
-\citep{petitjean}.
-For the DLAs, we have evaluated \fnhi\ from the SDSS-DR5 \citep{pw09}
-over the redshift interval $z=[3.4,4.0]$, giving 
-$N_d = ?$, $\beta_3 = ?$ and $C_{\rm DLA} = ?$ {\bf [FILL IN]}.
-Together, these evaluations give \fnhi\ for $\mnhi> 10^{19} \cm{-2}$
-at $z \approx 3.7$.
-
-We can estimate \fnhi\ for the interval $\mnhi = [10^{17.5}, 10^{19}]\cm{-2}$,
-which we will refer to as \lfnhi,
-under the following assumptions:
-(i) \lfnhi\ monotonically increases with decreasing \nhi\ 
-and
-(ii) \lfnhi\ has a power-law form
-
-\begin{equation}
-\mlfnhi = C_{\rm LLS} \mnhi^{\beta_{\rm LLS}}.
-\end{equation}
-We then impose the integral constraint that 
-the incidence of LLS with $\mtll \ge 2$ from our survey equals:
-
-\begin{equation}
-\ell_{\rm LLS} (X) = \intl_{10^{17.5} \cm{-2}}^\infty \mfnhi \, d\mnhi \perd
-\end{equation}
-At $z \approx 3.7$, we estimate $\mlzlls = 0.5 \pm 0.1$ (Figure~\ref{fig:complox})
-and find $\mbtlls = \blls$ and $C_{\rm LLS} = \clls$.
-
-A plot of \fnhi\ for $z \approx 3.7$ and $\mnhi \ge 10^{17.5} \cm{-2}$
-is shown in Figure~\ref{fig:fn}.
-Our analysis reveals that \fnhi\ becomes increasingly shallow
-with decreasing \nhi. This was suggested by previous authors
-based on similar analysis but with much poorer observational
-constraints on \llls\ \citep{phw05,opb+07}.
-Our results actually indicate that $\mbtlls > -1$ (95$\%$ c.l.)
-which means that the universe has a {\it higher} cross-section to 
-sightlines with $\mnhi = 10^{19} \cm{-2}$ than those 
-with $\mnhi = 10^{18} \cm{-2}$.
-
-We can extend the analysis of \fnhi\ one step further by adopting
-recent results on the mean free path to ionizing radiation
-(\lmfp; PWO09).  At $z=3.7$, PWO09 estimate 
-$\mlmfp = 47 h^{-1}_{72} \, \rm Mpc$ proper distance.
-This implies that the effective optical depth \teff\ is unity 
-for a photon travelling a redshift path
-$\delta z = \mlmfp (dz/dr) = 0.30$ (i.e., \teff=1 at $z=3.5$ for photons
-from a quasar with $\mzem = 3.8$).
-The evaluation of \teff\ follows from
-
-\begin{equation}
-\mteff(z_{912},\mzq) = \intl_{z_{912}}^{z_q} \intl_{\mnmin}^\infty f(\mnhi,z')
-   \lbrace 1 - \exp \ltk - \mnhi \sigma_{\rm ph}(z') \rtk \rbrace d\mnhi dz' 
-\label{eqn:teff}
-\end{equation}
-where $\sigma_{\rm ph}$ is the photoionization cross-section evaluated
-at the photon frequency and the results are insensitive to the
-minimum \nhi\ column density for any value 
-$\mnmin \le 10^{12} \cm{-2}$.
-
-Figure~\ref{fig:mfp} shows the \lmfp\ value at $z=3.7$ from PWO09
-as a solid horizontal band, assuming a 15\%\ error. 
-The solid curve, meanwhile, corresponds to the evaluation of
-Equation~\ref{eqn:teff} using our estimation of \fnhi\ integrated
-from $z=3.5$ to $z=3.8$ as a cumulative function of \nmin.
-At the limiting \nhi\ value of our survey ($10^{17.5} \cm{-2}$), 
-we estimate that 70\%\ of the opacity to ionizing radiation is
-contributed by $\mtll \ge 2$ LLS.  We estimate a 20\%\
-error in this evaluation (overplotted in the Figure).
-
-It is evident from Figure~\ref{fig:mfp} that systems with 
-$\mtll \le 2$ must contribute to \lmfp.
-For $\mnmin < 10^{17.5} \cm{-2}$ we continue the calculation
-by assuming that \fnhi\ follows a power-law
-
-\begin{equation}
-f_{\rm pLLS}(\mnhi < 10^{17.5} \cm{-2}, X) = 
-  C_{\rm pLLS} \mnhi^{\beta_{\rm pLLS}} 
-\label{eqn:fplls}
-\end{equation}
-constrained to match \lfnhi\ at $\mnhi = 10^{17.5} \cm{-2}$.
-We find that models with $\mbplls \ge -1$ cannot reproduce
-the \lmfp\ results.  In fact, the data favor $\mbplls \le -1.5$,
-i.e.\ a steeper power-law than inferred for the LLS and than
-that commonly observed for the \lya\ forest.  These conclusions
-do rely on our
-estimations of \llls; slopes as shallow as $-1.5$ are possible
-if one ignores constraints from the \lya\ forest.
-
-In Figure~\ref{fig:splinefN}, we make a first attempt at deriving
-the full \fnhi\ function for $\mnhi \ge 10^{12} \cm{-2}$ by integrating
-all of the constrains discussed thus far and also including the
-\lya\ forest.  
-For the latter, we assume $\myfnhi \propto \mnhi^{-1.5}$
-and we normalize this power-law at $z=3.7$ by matching to the
-effective \lya\ optical depth \lteff\ measured by \cite{fpl+08}
-assuming a $b$-value distribution
-$f(b) \propto b^{-5} \exp{-b_\sigma^4/b^4}$ \citep{hr99}. 
-Absent a physical model for \fnhi\ we take an empirical approach.
-We will evaluate \fnhi\ as a cubic spline \citep{press92}
-defined by the values of 12 spline points at 
-$\log \mnhi = [12.0, 14.0, 16.0, 17.5, 19.0, 20.3, 21.7, 22.5]$.
-The first, third, and last of these are arbitrarily defined
-while the others are taken to correspond to the following
-observational constraints:
-
-\begin{enumerate}
-\item We minimize $\chi^2$ for the binned evaluations of \fnhi\
-of the DLAs \citep{pw09} at $z=3.5$ over the interval 
-$\mnhi = [10^{20.3}, 10^{21.7}] \cm{-2}$, where the latter
-point corresponds to the `break' in \fnhi\ at high column
-densities \citep{phw05}.  This establishes the $y$-values
-of the spline points at $\log \mnhi = 20.3$ and 21.7 (Table~\ref{tab:spline}).
-For the spline point at $\log \mnhi = 22.5$, we force
-$\mfnhi \propto \mnhi^{-4}$ for $\mnhi \ge 10^{21.7} \cm{-2}$.
-This spline point has no effect on the analysis.
-
-\item The spline point at $\log \mnhi = 19$ is constrained to give
-$\mlslls = 0.2$ \citep{opb+07}.
-\item The spline point at $\log \mnhi = 17.5$ is constrained
-to give $\mllls = 0.5$ (this paper);
-\item The spline point at $\log \mnhi = 16$, whose x-value is 
-the most arbitrary, is constrained to give $\mlmfp = 47 \umfp$ (PWO09);
-\item The spline points at $\log \mnhi = 12 \; {\rm and} \; 14$
-are constrained to give $\mfnhi \propto \mnhi^{-1.5}$ and to
-give a \lya\ opacity $\mtlya =$ {\bf XX} \citep{fpl+08}.
-\end{enumerate}
-This approach has several advantages over our previous \fnhi\ evaluations
-(Figures~\ref{fig:fn}, \ref{fig:mfp}): 
-(i) introducing the \lya\ forest
-places a constraint at low \nhi\ values which implies more of an
-interpolative analysis then extrapolative;
-(ii) the resulting function is smooth in the first derivative
-and continuous in the second derivative.
-
-Table~\ref{tab:spline} lists the spline point values and
-Figure~\ref{fig:splinefN} plots the points and the resulting spline
-evaluation for \fnhi.  The slope $\beta \equiv d\ln[\mfnhi]/d\ln\mnhi$
-at each of the spline points is also given.
-Finally, we also show the \fnhi\ evaluations of the SLLS $(z>3$)
-and DLAs ($z=3.5$) from \cite{opb+07} and \cite{pw09}.
-
-We will defer a full discussion of the results to the following
-section, but offer the following observations.
-First, we again find that \fnhi\ is very shallow in the LLS
-region with $\beta > -1$ at $\mnhi = 10^{19} \cm{-2}$.
-Second, we observed that \fnhi\ becomes steeper than
-$\beta = -1.5$ (perhaps steeper than $\beta = -2$) for
-$\mnhi \approx 10^{16} \cm{-2}$.  This was first
-suggested by \cite{petit93} and subsequently argued for
-by \cite{rauch} and \cite{misawa}?
-
-[Comment on the uncertainties in all of this. Juggle the values
-about, e.g. bootstrap.  Try the shallower Petitjean slope for the SLLS
-if the dN/dX is much different]
-
-\subsection{The Incidence of Proximate LLS}
-
-The results presented thus far all refer to intervening LLS, systems
-restricted to have \zlls\ blueward of 3000\kms\ from the quasar
-emission redshift.  This restriction was imposed to isolate the
-`ambient' IGM and avoid biases related to having performed
-the analysis with bright, background quasars.
-In the space surrounding a bright quasar, one predicts at least two
-such biases:
-(1) bright, high $z$ quasars are known to cluster strongly
-\citep[$r_0 \approx ? \, h^{-1} \rm Mpc$;][]{shen07}
-suggesting these objects trace massive structures in the young universe.
-The local environment of bright quasars, therefore, has an uncommonly
-high density (at least in dark matter) which may give a higher
-incidence of LLS;
-(2) the radiation field of the quasar will ionize gas to large
-distances, reducing the incidence of LLS.
-For damped \lya\ systems, the first effect dominates
-as one observes an enhanced rate of proximate DLAs (PDLAs)
-relative to the intervening systems \citep{reb06,phh08}.
-
-Following the formalism presented in \cite{phh08}, we have estimated
-the incidence of proximate LLS (PLLS) in a series of redshift intervals.
-First, we re-measured the quasar emission redshifts for all
-systems with $\msna \ge 2$ at the Lyman limit and with 
-a $\mtll \ge 2$ LLS within 5000\kms\ of \zem.
-{\bf [Do this!]}
-The SDSS quasar redshifts reported in the standard DR7 data release
-are known to have significant systematic errors. 
-Following the prescriptions described in \cite{shen07},
-J. Hennawi has kindly remeasured the redshifts for all of the quasars.
-Second, we analyzed the quasars whose absorbed continuum at the wavelength
-of the Lyman limit corresponding (3000\kms\ blueward of \zem) is
-twice the median-smoothed, $1\sigma$ error-array.  This establishes
-the survey path.  All PLLS identified redward of this 3000\kms\ offset
-form the statistical sample (Table~\ref{tab:PLLS}).
-The incidence, \lplls, is then estimated in arbitrary redshift
-intervals assuming the same estimator for intervening 
-LLS (Equation~\ref{eqn:loz}).
-These results are presented in Figure~\ref{fig:prox} and compared
-against the incidence of interevening LLS, \lzlls.
-
-Ignoring the data at $z < 3.6$ (which we suspect to be biased high
-by the SDSS targeting criteria; PWO09), the
-incidence of PLLS roughly tracks that of intervening LLS.
-At $z<4$, however, the PLLS show an $\approx 25\%$ lower
-incidence than the intervening systems.  The inset figure
-shows the observed cumulative number of PLLS (dark curve) versus
-the predicted number (light curve) assuming the best-fit power-law
-for \lzlls\ of intervening LLS.
-A one-sided KS test yields only a 1\%\ probability that the
-two distributions are drawn from the same parent population.
-The principal implication is that $\mtll \ge 2$ LLS toward
-$i<20$\,mag quasars at $z>3.5$ suffer from a proximity effect
-of lower incidence presumably due to the ionizing radiation
-field of the quasar itself.
-Given the observed enhancement of strong LLS at $z \approx \mzem$
-along sightlines {\it transverse} to such quasars
-\citep{hpb+06}, our results lend further evidence that quasar emission
-is anisotropic \citep{hp07}.
-
-Before concluding this section, we comment that the PLLS
-analysis is subject to a potentially large systematic error.
-In performing our LLS survey, we have identified and removed
-all quasars with very strong associated absorption,
-e.g.\ BALs.  The intent of this procedure was to remove the
-signatures of absorption from gas very local 
-($<1$\,kpc) to the quasar from the analysis.  It is possible, however,
-that the associated absorption in some of these removed
-quasars is due to a PLLS at distances $\gg 1$\,kpc and not very
-local gas.
-This would lead to an underestimate of \lplls.
-Alternatively, we may not have identified all of the
-local absorbers and therefore might have overestiamted \lplls.
-In either case, we caution that a systematic error of the
-order of $10-20\%$ should be attributed to this effect.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Discussion}
-\label{sec:discuss}
 
 \begin{itemize}
-\item  Compare to previous work; include Misawa
-\item  Stack spectrum:  Compare $\tilde\mtll$
-\item  What gives rise to LLS?  Why is it only a 9x higher incidence than DLAs?
-  What is the connection to $z=0$?
-[What is dN/dX today?  How about in simulations?  Is the radius to
-17.6 only 3x larger?]
-\item  Taueff
+\item Usage of cool gas outflows to probe galactic-scale winds in
+  star-forming galaxies is now a well-established observational
+  technique
+\item Simple anlaysis focusing on the central wavelength and EW of the
+  lines
+\item \lya, MgII, NaI and (now) FeII* show emission
+\item Despite the wealth of observational diagnostics, little effor
+  hast been taken to constrain the wind properties
+\item These are some first steps by considering idealized wind
+  profiles.  Algorithms can be extended to any wind output
 \end{itemize}
 
-With an estimation of \lfnhi\ in hand, we can draw several inferences
-about the opacity of the Universe to ionizing radiation.  First,
-we can estimate the mean opacity at 1\,Ryd for all LLS having $\mtll \ge 2$
-by taking a weighted mean,
+\section{Methodology}
 
-%NOTE:  See fig_avgtaueff [actually fig_fn] for the exact f(N_HI) actually used
+\subsection{The Radiative Transitions}
 
-\subsection{Comparisons with Previous Work}
+[Neglect collisional excitation and de-excitation.  These would
+require $n_e > 10^3 \cm{-3}$.  Non-detection of FeI argues against
+this.]
 
-Surveys for Lyman limit systems have been carried out for several
-decades now \citep{tytler84,ssb89,lzt93,sl95,sl96,peroux03}.
-These have been  performed primarily at optical wavelengths on 
-heterogeneous quasar samples drawn from a diverse set of
-survey approaches: color-selection, radio detection, slitless
-spectroscopy, etc.  The authors also had differing completeness
-limits for \tll\ (ranging from 1 to 3) and differing approaches
-to establishing the pathlength that establishes \lzlls.  Almost
-no attention was given to assessing systematic error, and several
-of the effects described in $\S$~\ref{sec:mock} assuredly apply
-to the previous works.  It comes with little surprise, therefore,
-that many of the previous estiamtes of \lzlls\ are in disagreement
-with our results.
+In this paper, we will focus on two sets of radiative transitions
+associated with the Fe$^+$ and Mg$^+$ ions.  The choice of these
+specific low-ions is motivated by our own observations
+\citep{rubin10b} but (as described below) these two ions exhibit
+the dominant characteristics of the majoriy of low-ions used to study
+cool-gas outflows. [word] Therefore, the majority of our results can
+be generalized to other transitions that are freuqenly used.
 
-In Figure~\ref{fig:literature} we present estimates of \lzlls\
-from several previous studies, parameterized as in Equation~\ref{eqn:powlaw}
-(Table~\ref{tab:param} lists the parameters).  
-Tge dotted lines show estimates from \cite{ssb89} and \cite{lzt91},
-which included very few observations at $z>3.5$ and not surprisingly 
-had rather discrepant estimates for the high $z$ universe.
-The solid curves show the results from \cite{sl94} and \cite{peroux03}
-who performed surveys of LLS at $z \sim 4$ using the color-selected
-APM quasars.  All of these analyses were claimed to correspond to 
-LLS with $\mtll \ge 1$, although a careful review of the literature
-raises doubts to this assertion in several cases.  To compare against
-our $\mtll \ge 2$ results, therefore, we have boosted each of
-our \lzlls\ estimations by $8\%$ which is the correction factor
-imlied by the \fnhi\ function derived at $z = 3.7$ (Figure~\ref{fig:fnhi}).
+The Mg$^+$ ion, with a single 3s electron in the ground-state,
+exhibits an alkali doublet of transitions that are analagous to the
+\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
+we present the energy level diagram for the Mg$^+$ ion associated with
+the commonly observed \mgiid\ doublet.  In non-relativistic quantum
+mechanics, the 2p$^6$3p level is said to be split by spin-orbit
+coupling.  This doublet marks the only \ion{Mg}{2} electric-dipole transitions
+with wavelengths near 2800\AA.  Furthermore, the transtion connecting
+the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ is forbidden by several
+selection rules.  Therefore, an absorption to either of the upper
+states is followed essentially 100$\%$ of the time by a spontaneous decay to the
+ground state.
 
-Our results on \lzlls\ are somewhat lower than the values derived 
-from the APM surveys, but the values lie within
-1.5$\sigma$ of concordance.  The more important difference lies between
-the estimations at $z<4$.  All of the previous work, which relied
-almost entirely on the surveys of \cite{ssb89} and \cite{lzt93}, 
-[assumed] $\mzlls \approx 2$ at $z = 3$ giving a more shallow
-evolution for \lzlls\ than observed in the SDSS data.
-Our results suggest that the previous work at $z \sim 3$ overestimated
-the incidence of LLS.  Actually, the original survey by \cite{ssb89}
-is in fair agreement with an extrapolation of our power-law form
-for \lzlls\ to $z=3$, but the reanalysis by \cite{sl95} of still
-unpublished spectray by Steidel \& Sargent led to a higher estimate
-at this redshift.  We suspect that this later work gave \lzlls\ values
-that were too high either because of sample variance (i.e.\ small
-number statistics) or selection bias in the quasar sample 
-\citep[e.g.\ the color-selection bias 
-described in][and $\S$~\ref{sec:loz}]{pwo09}.
-On this point, we note that if we adopt the \cite{peroux03} estimation
-of $\mlzlls = 3$ at $z=3.7$, then the LLS alone predict a mean free path
-to ionizing radiation $\mlmfp = 45 \umfp$ that matches the measured
-value \citep{pwo09}.  This would mean that gas with $\mtll < 1$
-cannot contribute any to \lmfp, a physically impossible scenario.
-[It gets worse when you realize this gives a steep LLS f(N) which *must*
-monotonically hook onto the LLS.]
+The physics of the \mgiid\ doublet
+is analagous [repeating myself] to the physics of \ion{H}{1}
+\lya, and also the \naid\ doublet and many other doublets commonly
+studied in the ISM and IGM.  The key quantitative differences are in
+the wavelengths of the transitions and, for the calculations of interest
+in ths paper, their energy separations.  For \ion{H}{1} \lya, the
+separation is sufficiently small $\Delta v = c \Delta E / E \approx 1.3
+\mkms$ that most radiative transfer treatments ignore the fact that
+\lya\ is a pair of transitions.   This is justified by the fact that
+most astrophysical processes have turbulent processes that
+significnatly exceed this velocity separation and effectively mix the
+two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
+\ion{Na}{1} ($\Delta v \approx 304 \mkms$), and most other doublets
+commonly studies the separations are large and demand that the lines
+be treated separately.  In terms of the analysis of outflows, the line
+separation is especially relevant when the outflow speed matches the
+line separation.
 
-[Does the MFP evolution require strong LLS evolution?]
+Iron exhibits the most complex set of energy levels of the elements
+frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
+energy levels recorded \citep{iron} and even this is a necessarily
+incomplete list.  In this paper, we will focus on 9 of the levels
+related to the UV1 mutliplet whose wavelengths lie near 2600\AA\
+(Figure~\ref{fig:energy}).  One reason for the complexity of iron is
+that the majoriyt of energy levels exhibit fine-structure splitting.
+This includes the ground-state which has four fine-structure levels with
+excitation energies $T_{\rm ex} = \Delta E / k$ ranging from $\approx
+500-1500$\,K.  We label these according to the total angular momentum
+of each level $J$, with the ground-state having $J=9/2$.
+Transitions between these fine-structure levels are magnetic-dipole
+transitions with spontaneous decay times of several hours.  In
+principle, these levels can be populated by indirect UV pumping
+\citep[e.g][]{sv02,pcb06}, but this would require that the gas lie
+close to the source of UV photons (see $\S$~\ref{sec:pump}).  In the
+following, we will assume that only the ground-state is populated by
+electrons and therefore capable of absorbing photons.
 
-[Calculate MFP from Peroux LLS stats alone]
+[Comment on UV1 a bit more]
 
-\subsection{Redshift Evolution}
+\subsection{The Source}
 
-The redshit evolution in the incidence of LLS \lzlls\ impacts
-the evolution of the EUVB at low $z$ and the history of reionization
-at high $z$.  Previous work has debated whether \lzlls evolves
-as a singe power-law $(1+z)^\mglls$ from $z \approx 0 - 4$.
-In $\S$~\ref{sec:loz}, we modeled our observations with a 
-single power-law having $\mglls = \alls$.
-As noted in the previous sub-section, measurements of \lmfp\ also
-suggest a steep evolution in the incidence of LLS at $z<4$. 
-We now consider whether a single power-law extrapolation is
-a good description of \lzlls\ for $z < 3$.
+The majority (all?) of observational studies of cool gas outflows in
+absorption have focused on intervening, star-forming galaxies.  The
+unobscured emisison of these galaxies is a complex combination of
+stars and \ion{H}{2} regions that is then modulated by dust and gas
+within its ISM.  In terms of the spectral regions studied in this
+paper, most stars show a featureless continuum with a few spectral
+types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
+[Any emission??]  Furthermore, \ion{H}{2} regions are observed to emit
+at the \mgiid\ doublet, primarily due to recombinations in the outer
+layers.  It is beyond the scope of this paper to properly model this
+stellar absorption and \ion{H}{2} region emission, but the reader
+should be aeware that they can complicate the observed spectrum,
+independent of the effects of a galactic outflow.
+In the following, we will simply assume a flat continuum that will
+generally be normalized to unit value.
 
-Survey of other \ion{H}{1} absorption systems have demonstrated
-that a single $(1+z)^\gamma$ power-law is a poor description
-of the \lya\ forest \citep{weymann} and the damped \lya\ systems
-\citep{phh08}.  In the former case, one observes a flattening
-in the \lya\ line-density at $z \sim 1$ which has been interpreted
-to result from a corresponding decline in the intensity of 
-the EUVB \citep{weymann,dave}.  It is plausible that a similar
-effect would influence the LLS.
-
-In Figure~\ref{fig:zloz}, we present our estimates of \lzlls\
-at $z \sim 3.5$ and the estimate of \lzlls\ at $z \sim 1$
-from \cite[][see Howk et al., in prep for a new estimate]{sl95}.
-Overplotted on the data is a solid curve that shows the best-fit
-power law to the SDSS results.  The dashed curves show $2\sigma$
-departures from this model.  It is evident that none of these
-curves intersect the low redshift observation.
-[Did I remember to boost the \lzlls\ values for $\mtll 2 \to 1$?]
-We conclude, with high confidenc, that a strict $(1+z)^\mglls$
-power-law does not describe the evolution of \lzlls\ across
-all of cosmic time.   [Plot log (1+z) on the x-axis?]
-Instead, the data suggest a break in the high $z$ power-law
-at $z \sim 2$, similar to that observed for the \lya\ forest
-albeit at somewhat higher redshift.
-
-The dash-dot curve, is an attempt to model this break.  
-For $z<2.3$, we adopt the power-law form that matches
-the \lya\ forest at low redshift ($\mglls = 0.26$) and
-demand that it intersect the central value of the \cite{sl95}
-measurement.  For $z\ge 2.3$, the model breaks to a $\mglls = 2.78$
-power-law, again consistent with the high $z$ evolution of the
-\lya\ forest \citep[e.g.][]{kim02}.  This is a reasonably
-good description of the data and we conclude that a break
-in the power-law description of \lzlls\ likely occurs at $z \approx 2$.
-We will test this prediction with an (ongoing) survey for LLS
-at $z \sim 2$ in HST/ACS and WFC3 slitless spectra of 
-$z \approx 2.3$ quasars (PI: O'Meara).
-
-\subsection{The Average LLS Spectrum}
-
-To gain additional insight into the absorption properties of the
-LLS, we have constructed an average (stacked) spectrum 
-by (i) shifting each quasar spectrum containing a $\mtll \ge 2$ LLS
-to the LLS rest-frame and (ii) straight averaging the fluxed data.
-This stacked spectrum is primarily illustrative and has little 
-quantitative value.  The resulting spectrum is shown in 
-Figure~\ref{fig:stack}.  The peak in emission at 
-$\lambda_{\rm r} \approx 1280$\AA\ is from the \lya\ emission
-peak of the background quasar.  It is significantly
-offset from 1215\AA\ because the stack only includes intervening
-LLS, i.e.\ those that are offset by at least 3000 \kms from the 
-quasar emission redshift.
-
-The second strongest feature in the
-spectrum is the Lyman limit at the expected wavelength of 912\AA.
-Shortward of the Lyman limit, one observes a non-zero flux that
-extends down to $\approx 770$\AA.  In these relative
-flux units, we measure a flux at 900\AA\ of $f({\rm 900 \AA}) = 24$.  
-Estimating the absorbed continuum at 960\AA\ to be 
-$f({\rm 980 \AA}) = 810$, we calculate an average optical depth
-at the Lyman limit of $\mavtll = 3.5$.  This value may be compared
-to the average optical depth dervied from our \fnhi\ estimation:
-
-\begin{equation}
-\mavtll = - \ln \ltb
-\frac{\int \exp[-\mnhi \sigma_{LL}] \mfnhi \, d\mnhi}{\int \mfnhi \, d\mnhi}
-\rtb
-\label{eqn:avgtau}
-\end{equation}
-where the integrals are evaluated over the interval
-$\mnhi = [10^{17.5},10^{22}] \cm{-2}$.
-We find $\mavtll \approx 5$ for our assumed \fnhi\ distribution function.
-We compare this directly against the mean spectrum of our LLS sample in 
-$\S$~\ref{sec:XX}.
-
-\subsection{The Physical Nature of the LLS}
-
-Viewing the situation in the opposite sense (from high $z$ to low $z$),
-we speculate that the decrease in \llls\ results from an increasing
-number of ionizing sources that photoevaporate the structures associated
-with LLS.   
-Indeed, the number density of 
-bright quasars is observed to increase from $z=4$ to 3 \citep{qsoevol}.
-We postulate that these sources are 
-reducing \nlls\ and/or \slls.
-
-To explore this point further,  we
-decompose \llls\ into various absorption classes (each with $\mtll \ge 2$)
-using constraints from the literature.
-In Figure~\ref{fig:complox}, we present the \llls\ values (in cumulative
-form) for DLAs \citep{pw09} and super Lyman limit systems 
-\citep[SLLS, absorbers with $\mnhi = 10^{19} - 10^{20.3} \cm{-2}$;][]{opb+07}.
-For the latter, we assume $\ell_{\rm SLLS}(X) = 0.20$ at all redshifts because
-only a single estimate exists at $z>3$. 
-We have adopted a 20$\%$ lower (1$\sigma$) value than reported
-by \cite{opb+07} to crudely correct for the SDSS quasar targeting bias
-that will affect their measurement (PWO09). 
-The figure demonstrates that the DLAs (especially) and 
-the SLLSs have modest contributions to \llls.
-At $z=3.4$, they contribute roughly half of the observed incidence
-of $\mtll \ge 2$ LLS but this fraction likely decreases to
-$\approx 33\%$ by $z=4$.  This latter conclusion hinges on our asssumptions for 
-\lslls, in particular at $z \approx 4$ where the value is not
-well constrained.  But, we expect the SLLS to behave similarly
-to the DLAs, whose incidence is not increasing significantly at these
-redshifts.  We conclude that the observed evolution in \llls\
-is driven instead by systems with 
-$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$.
-By the same token, we infer that the decrease in \llls\ with 
-decreasing redshift is related to the photoionization 
-of these lower \nhi\ systems by the increasing number
-of ionizing sources.  The systems giving rise to DLAs (i.e. galaxies)
-are too optically thick to show significant effects 
-from an increasing radiation field.
-[THIS STUFF MIGHT BE BETTER LEFT TO THE DISCUSSION SECTION]
-
-It is difficult, if not impossible, to produce such an effect
-for simple cloud geometries in the influence of an ionizing
-radiation field \citep{zm0?}.
-We spectulate instead that the LLS with $\mnhi \sim 10^{19} \cm{-2}$
-arise in extended, partially collapsed structres, e.g. filaments.
-We further hypothesize that the flattening of \fnhi\ may be
-associated with the transition from
-the optically thick regime to being optically thin.
-Finally, we note that the rise in \llls\ with redshift
-(Figure~\ref{fig:complox}) implies that \btlls\ likely decreases
-(becomes steeper) with increasing redshift.
-
-\section{Summary}
+[What does MgI tell us about winds?  Why no P-Cygni?]
 
 \acknowledgments
-
-Funding for the SDSS and SDSS-II has been provided by the Alfred P. Sloan 
-Foundation, the Participating Institutions, the National Science Foundation, 
-the U.S. Department of Energy, the National Aeronautics and Space 
-Administration, the Japanese Monbukagakusho, the Max Planck Society, 
-and the Higher Education Funding Council for England. The SDSS Web Site 
-is http://www.sdss.org/.
-
-The SDSS is managed by the Astrophysical Research Consortium for the Participating Institutions.
-The Participating Institutions are the American Museum of Natural History, Astrophysical Institute Potsdam, University of Basel, University of Cambridge, Case Western Reserve University, University of Chicago, Drexel University, Fermilab, the Institute for Advanced Study, the Japan Participation Group, Johns Hopkins University, the Joint Institute for Nuclear Astrophysics, the Kavli Institute for Particle Astrophysics and Cosmology, the Korean Scientist Group, the Chinese Academy of Sciences (LAMOST), Los Alamos National Laboratory, the Max-Planck-Institute for Astronomy (MPIA), the Max-Planck-Institute for Astrophysics (MPA), New Mexico State University, Ohio State University, University of Pittsburgh, University of Portsmouth, Princeton University, the United States Naval Observatory, and the University of Washington.
 
@@
 
-\appendix
-
-\section{Comparisons with Keck+LRIS Spectra}
-\label{appx:keck}
-
-To assess uncertainties (statistical and systematic)
-of surveying LLS in the SDSS quasar spectra, we
-obtained independent, higher quality spectra using the LRIS spectrometer
-\citep{lris} on the Keck I telescope.  
-LRIS employs a dichroic to split the data into two
-spectral channels, each with its own camera.
-For our observations, we employed the d560 dichroic which splits the 
-light at $\approx 5600$\AA.
-For the blue channel, we used the 640/4000 grism
-which provides a dispersion of 0.63 \AA\ per unbinned pixel and has a nominal
-wavelength coverage of $3100 \rAA < \lambda < 5600$ \AA.  The blue channel
-data was binned by 2 in both the spatial and spectral dimensions. For the red
-channel, we used the 600/7500 grating which provides a dispersion of
-1.28 \AA\ per unbinned pixel, and which was tilted to provide a wavelength
-coverage of $5600 \rAA < \lambda < 8200$\AA.  The red channel data was unbinned.
-All observations were obtained using a 1 arcsecond slit which provides
-an $\approx 4$\,pixel FWHM corresponding to 
-$\approx 290\mkms$ and $\approx 220 \mkms$ for the blue and red
-data respectively.
-The data were obtained in good sky conditions during a 4 night
-run in October~2008 and had
-exposure times ranging from 300 to 500 seconds.
-The data were reduced using the LowRedux
-pipeline\footnote{http://www.ucolick.org/$\sim$xavier/LowRedux/} which
-bias subtracts, flat fields, optimally extracts, wavelength and flux
-calibrates the data to produce a final 1D spectrum.
-
-The SDSS targets for LRIS observations were chosen to sample a range
-of LLS, e.g., LLS with $\mtll \ge 2$, pLLS
-candidates, PLLS and spectra without apparent LLS.  Furthermore, 
-an emphaisis was placed on quasars with lower S/N SDSS spectra 
-to assess the completeness of recovering LLS. 
-In all cases, the LRIS spectra have sufficient S/N 
-to unambigously detect the presence of absorbers with $\mtll > 1$ 
-over the full SDSS wavelength range (i.e.\ $\lambda > 3800$ \AA) for
-the intervening LLS survey. 
-Particular emphasis was given 
-to determine what absorbed continuum S/N cutoff should be applied to
-the SDSS sample.  To this end, two of the authors (JXP and JMO)
-independently modeled LLS absorption in the LRIS data and 
-compared the results to similar analysis of the 
-the SDSS spectra.  The same
-codes were used to model LLS absorption.  In Table
-\ref{tab:lriscomp}, we present the results of these comparisons.  In
-Figure \ref{fig:lris} we show a representative sample of the
-LRIS data alongside their SDSS counterparts.  For the SDSS data in
-Figure \ref{fig:lris}, we also show the continuum level assigned
-to each spectrum.
-
-The LRIS/SDSS comparison illustrates that with a choice of absorbed
-continuum S/N $>1$ 
-we recover nearly 100\%\ of the LLS with  $\mtll > 2$ in the SDSS.  We see this
-explicitly in Table \ref{tab:lriscomp}, where we give the values for
-\zstrt\ in the SDSS search, where \zstrt\ is the redshift at which
-the absorbed continuum S/N crosses the value of 1.  In some cases, we
-identify LLS at redshifts lower than \zstrt\ in both the LRIS and
-SDSS data.  Although these LLS will not contribute to our results,
-they lend additional confidence in our absorbed continuum S/N cutoff.
-The only exceptions to the identification of LLS in the LRIS and 
-SDSS spectra at S/N~$\ge 1$ are for systemss with $\mtll \approx 2$.
-At this optical depth, JXP and JMO did not always
-agree, even in the LRIS results. 
-(WE NEED TO CHECK ALL THE TABLE RESULTS FOR SILLY MISTAKES).  
-This highlights the fact that our results have an inherent uncertainty
-in $\log \mnhi$ of $\approx 0.2$\,dex. 
-Most importantly, this
-disagreement does not appear to depend on the S/N of the spectrum for
-the range of S/N we could expect from the SDSS data, and thus does not
-effect our choice for the S/N threshold.
-
 \bibliographystyle{/u/xavier/paper/Bibli/apj}
@@
 
-\input{Tables/tab_subqso.tex}
-\input{Tables/tab_subsurvey.tex}
-\input{Tables/tab_subprox.tex}
-\input{Tables/tab_sub_candlls.tex}
-\input{Tables/tab_spline.tex}
-\input{Tables/tab_summ.tex}
-\input{Tables/tab_sdss_lris.tex}
-%\input{Tables/tab_lls.tex}
-%\input{Tables/tab_lls_nostat.tex}
-%\input{Tables/tab_lls_prox.tex}
+%\input{Tables/tab_subqso.tex}
 
@@
 \epsscale{0.8}
-\plotone{Figures/fig_qsohist.ps}
-\caption{Quasar historgrams
+\plotone{Figures/energy_levels.ps}
+\caption{
+Energy level diagrams for the \mgiid\ doublet and the UV1
+multiplet of \ion{Fe}{2} transitions.   Each transition shown is
+labelled by its rest wavelength (\AA) and Einstein A-coefficient
+(s$^{-1}$). Black updward arrows
+indicate the resonance-line transitions connected to the ground
+state of each ion.  The 2p$^6$3p configuration of Mg$^+$ is split into
+two energy levels that give rise to the \mgiid\ doublet.  
+Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
+are split into multiple energy levels giving rise to a series of
+electric-dipole transitions between these fine-structure levels.   
+The downward (green) arrows show the transitions connected to the
+resonance-line transitions (i.e.\ they share the same upper energy
+levels).  We also show a pair of levels (\ion{Fe}{2}~$\lamabda\lambda
+2618,2631$) that arise from even higher levels [Should we bother?]
+Based on Figure~7 from \cite{hartagan9X}.
 }
-\label{fig:snz}
+\label{fig:energy}
 \end{figure}
 
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/fig_templates.ps}
-\caption{Mean (median?) observed (not intrinsic)
-quasar spectra (detilted?) for 
-the full SDSS-DR7 (clipping?) in redshift intervals from
-top to bottom of $z=(3.4,3.7); (3.7,4.0); (4.0,4.4)$ and
-$(4.4, 5.0)$.    
-The increasing impact of the \lya\ forest is readily apparent
-at wavelengths $\lambda_{\rm rest} < 1200$\AA.
-}
-\label{fig:template}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_exmpl_conti.ps}
-\caption{Representative spectra of the quasars in the statistical sample.
-Each example shows the absorbed continuum model (dark blue, dotted)
-and the green curve indicates the model that includes LL absorption. 
-For this presentation, we have not shown the Lyman series in the model.
-The vertical dotted line indicates the Lyman limit wavelength
-in the quasar rest-frame, i.e.\ $\lambda = \lambda_{LL} (1+z_{em})$.
-}
-\label{fig:ex_conti}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_goz.ps}
-\caption{Summary of the redshift path surveyed in the SDSS-DR7
-for $\mtll \ge 2$ LLS absorption assuming a range of S/N thresholds
-(solid curves).  Specifically, $g(z)$ represents the number of 
-unique quasars in the SDSS that provide a search for LLS over
-the interval $dz$ at redshift $z$.  The dotted curve, meanwhile,
-represents the same quantity but for proximate LLS (PLLS; systems
-within $\delta v = 3000 \mkms$ of the quasar) and corresponds
-to a S/N=2 threshold.  This curves fall rapidly for $z<3.4$
-because we limit the analysis to quasars with $\mzem \ge 3.4$.
-The non-monotonic nature of $g(z)$ is due primarily to the presence
-of LLS along the quasar sightlines which abruptly truncate the search path.
-}
-\label{fig:goz}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.7}
-\plotone{Figures/mockspec_bw.eps}
-\caption{
-(a): A spectrum representative of the typical data quality 
-(S/N$\sim 2$ at the Lyman limit of the quasar). 
-There is a LLS ($z=3.88059, \log\mnhi=18.27$) that can be easily identified 
-at this S/N. 
-Two $16< \log\mnhi <18.27$ systems at higher $z$ do not yield a 
-high \tll\ before the light hits the optically thick system.
-(b): A high-S/N spectrum (S/N$\sim 6$ at the Lyman limit of the quasar), 
-rendering its partial LLS ($z=3.98387, \log\mnhi=17.24$) 
-easily visible. An additional SLLS at lower redshift 
-$(z=3.76609, \log\mnhi=19.28)$ sets the flux to zero at the Lyman limit.
-(c): A roll-off spectrum. There is a LLS $(z=3.68084, \log\mnhi=17.87)$, 
-but there are five $16 < \log \mnhi <17$ systems at higher $z$ that result 
-in a roll-off. The S/N at the Lyman limit of the quasar is quite low 
-(S/N$\sim 1.5$), the intervening systems further decrease 
-the S/N, rendering the LLS invisible.
-(d): A spectrum with strongly undersubtracted sky background. The 
-first strong system encountered is a LLS 
-$(z=3.87495, \log\mnhi=18.34)$, but the flux is above zero even 
-after hitting a DLA $(z=3.57678, \log\mnhi=20.43)$. 
-You can easily see that the sky subtraction is poor, because 
-Lyman alpha of the DLA does not saturate. 
-}
-\label{fig:mockex}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_mock_dz.ps}
-\caption{Offset in redshift $\delta z$ for the `observed' LLS and pLLS
-from the \zabs\ value of the nearest true $\mtll \ge 2$ LLS
-in our mock spectra.  The analysis is restricted to the highest
-\zabs\ LLS along each sightline.
-In the upper panel, we show the $\delta z$ value for sightlines
-where a LLS was `observed' and actually exists.  These are the majority
-of cases $(>80\%$)
-and we find small $\delta z$ values with a small, but important
-bias to $\delta z > 0.01$.
-In the lower panel, we show false negatives (diamonds) and false
-positive (triangles) detections.  The former correspond to a true LLS
-that was observed as ($\delta z < 0.1$) or hidden by a pLLS ($\delta z > 0.1$).
-The misidentifications ($\delta z < 0.1$) are dominated by the mock
-spectra with large underestimates in the sky background.  The dominant
-effect of a sky subtraction bias is an underestimate in in the incidence
-of LLS.
-}
-\label{fig:mockdz}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_both_bbias.ps}
-\caption{Blending bias (enhancement/decrement of \lzlls\ relative
-to no bias) for mock absorption line systems for 
-(upper) intervening $\mtll \ge 2$ LLS and
-(lower) proximate $\mtll \ge 2$ LLS.
-The absorption line statistics were set to roughly match the observed
-incidence. 
-Even for the blending over redshifts $\delta z_j = 0.2$, the bias
-for intervening systems is relatively small.
-In contrast, the blending bias systematically elevates \lzlls\ for PLLS,
-especially at $z>4$.
-}
-\label{fig:bbias}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_loz.ps}
-\caption{Incidence of intervening LLS with $\mtll \ge 2$ \lzlls\
-as a function of redshift.  
-The binning at $z<4$ is arbitrarily chosen to give roughly the
-same number of LLS per sample.  
-The solid (blue) line shows the best-fit power-law
-to the data at $z > 3.5$:  
-$\mlzlls = C_{\rm LLS} [(1+z)/(1+z_*)]^\alpha_{\rm LLS}$, 
-with $z_* \equiv 3.7$, $C_{\rm LLS} = \clls$, and
-$\beta_{\rm LLS} = \alls$ (68\%\ c.l.).
-The gray and solid points at $z < 3.5$ correspond to estimates
-of \lzlls\ where one restricts the analysis to quasars
-with $\mzem \ge 3.6$.  The dotted points, meanwhile, show
-\lzlls\ when one includes quasars with $3.4 \le \mzem \le 3.6$.
-These measurements are significantly biased to higher values by the
-SDSS quasar-targeting criteria (PWO09).
-In the subpanel, 
-the black (solid) curve shows the cumulative number of
-$\mtll \ge 2$ LLS detected in our survey of the SDSS-DR7
-database adopting the \sna=2 threshold.
-The blue (dotted) curve shows the predicted number of LLS assuming
-the best-fit power-law from Figure~\ref{fig:loz_lls} and adopting the
-\sna=2 $g(z)$ function from Figure~\ref{fig:goz}.  
-A one-sided KS-test does not rule out the null hypothesis that
-the model distribution is statistically different from the observations.
-}
-\label{fig:loz_lls}
-\end{figure}
-
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_cumlz.ps}
-%\caption{The black (solid) curve shows the cumulative number of
-%$\mtll \ge 2$ LLS detected in our survey of the SDSS-DR7
-%database adopting the \sna=2 threshold.
-%The blue (dotted) curve shows the predicted number of LLS assuming
-%the best-fit power-law from Figure~\ref{fig:loz_lls} and adopting the
-%\sna=2 $g(z)$ function from Figure~\ref{fig:goz}.  
-%A one-sided KS-test does not rule out the null hypothesis that
-%the model distribution is statistically different from the observations.
-%}
-%\label{fig:cumlz}
-%\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_complox.ps}
-\caption{
-The dashed lines bound our estimate of \llls\ for $\mtll \ge 2$ LLS
-as a function of redshift. The widths of the
-two lower bands (blue, red) indicate estimates of $\ell(X)$ for
-DLAs and SLLS \citep{opb+07,pw09}; see the text for details. 
-These bands are plotted on top of one another to indicate their total
-contribution to \llls\ (as indicated by the vertical arrows on the right-hand
-side of the figure).  The (top) blue band, therefore, represents the 
-estimate to \llls\ from LLS
-with $\mnhi = 10^{17.5} - 10^{19} \cm{-2}$. 
-[COMMENT MORE]
-}
-\label{fig:complox}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_fn.ps}
-\caption{\nhi\ frequency distribution \fnhi\ observed for the 
-SLLS \citep[green, $\mnhi = 10^{19} - 10^{20.3} \cm{-2}$;][]{opb+07}
-and DLAs \citep[red, $\mnhi \ge 10^{20.3} \cm{-2}$;][]{pw09}.
-The blue band is an estiamte of \fnhi\ for LLS having 
-$\mnhi = 10^{17.5} - 10^{19} \cm{-2}$ under the assumptions
-of a power-law form ($f(\mnhi,X) \propto \mnhi^{\beta_{\rm LLS}}$)
-and a monotonic increase from the SLLS, 
-and constrained by the incidence of observed $\tau \ge 2$ LLS (this paper).
-We find $\mbtlls = -1.0 \pm 0.3$ (90\%\ c.l.) at $z \approx 3.5$.
-}
-\label{fig:fN}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/fig_mfp.ps}
-\caption{This figure shows the mean free path contributed
-by absorbers with $\mnhi \ge \mnmin$. For $\mnmin \ge 10^{17.5} \cm{-2}$,
-(solid curve) which corresponds to our LLS survey, we have adopted
-the estimate of \fnhi\ from Figure~\ref{fig:fN} in the calculation.
-We estimate a 20\%\ uncertainy in the contribution of LLS to
-\lmfp, as shown in the figure.  For $\mnmin < 10^{17.5} \cm{-2}$,
-we assume \fnhi\ follows a simple power-law with exponent \bplls,
-and show a series of extrapolations (dash and dotted curves).
-The solid (red) horizontal band centered at $47 \umfp$
-indicates the measurement of \lmfp\ at $z \approx 3.7$ from PWO09.
-These results imply that LLS contribute $\approx 70\%$ of the 
-mean free path and that \bplls\ must be steeper than $-1$
-and likely steeper than $-1.5$.
-}
-\label{fig:mfp}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_splinefn.ps}
-\caption{The solid black curve shows our full estimation of
-\fnhi\ as a spline to the 7 black crosses (plus an 8th cross
-at $\log \mnhi = 22.5$ that is not shown; Table~\ref{tab:spline}).
-At each spline point, we calculate the local power-law slope
-$\beta = dlnf/dln\mnhi$.  The y-values of the
-spline points are constrained as follows: 
-(1) the points at $\log \mnhi = 20.3, 21.7$ are set to minimize
-$\chi^2$ from the binned evaluations of \fnhi\ of the DLAs
-at $z=3.5$ \citep{pw09}.  The spline point at $\log \mnhi = 22.5$ is then
-constrained to give $\mfnhi \propto \mnhi^{-4}$ for
-$\log \mnhi \ge 21.7$;
-(2) the spline point at $\log \mnhi = 19$ is placed to give
-$\mlslls = 0.2$ \citep{opb+07};
-(3) the spline point at $\log \mnhi = 17.5$ is constrained
-to give $\mllls = 0.5$ (this paper);
-(4) the spline point at $\log \mnhi = 16$, whose x-value is 
-the most arbitrary, is constrained to give $\mlmfp = 47 \umfp$ (PWO09);
-(5) the spline points at $\log \mnhi = 12 \; {\rm and} \; 14$
-are constrained to give $\mfnhi \propto \mnhi^{-1.5}$ and to
-give a \lya\ opacity $\mtlya = XX$ \citep{fpl+08}.
-}
-\label{fig:splinefN}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_prox_loz.ps}
-\caption{The solid and dark points show the incidence of
-proximate LLS per unit redshift (PLLS; LLS with $\mtll \ge 2$ that 
-occur within 3000\kms\ of the background quasar) against redshift.
-These are compared against the same quantity for intervening LLS
-(gray points).  The data point at $z<3.6$ corresponds to PLLS
-and has been dotted out because it is expected to be biased
-by the SDSS targetting criteria (PWO09).  Ignoring that last
-point, we find that the incidence of PLLS roughly follows that
-of intervening systems but is systematically lower by $\approx 25\%$
-at $z<4$.  The inset figure shows the cumulative number of 
-PLLS observed (black curve) against the predicted number using
-the power-law model for \lzlls\ ($\S$~\ref{sec:loz}) and
-the $g(z)$ curve for PLLS (Figure~\ref{fig:goz}).
-}
-\label{fig:prox}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/fig_literature.ps}
-\caption{Comparisons with the literature
-}
-\label{fig:literature}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/fig_allloz.ps}
-\caption{Redshift evolution in \lzlls
-}
-\label{fig:zloz}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/stack_lls.ps}
-\caption{Stack of LLS spectra
-}
-\label{fig:stack}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.9}
-\plotone{Figures/fig_lris_sdss.ps}
-\caption{LRIS spectra
-}
-\label{fig:lris}
-\end{figure}
-
-%\begin{figure}
-%\epsscale{0.9}
-%\plotone{Figures/fig_mock_loz.ps}
-%\caption{l(z) for the Mocks
-%}
-%\label{fig:mockloz}
-%\end{figure}
-
-%\begin{figure}
-%\epsscale{0.9}
-%\plotone{Figures/fig_loz_prox.ps}
-%\caption{$\ell(z)$ for proximate LLS with $\mtll \ge 2$
-%}
-%\label{fig:loz-lls}
-%\end{figure}
-
 \end{document}

### 2010-06-05 Winds/papers/Theory/First/Analysis/outflow_fiducial.cc

@@ -24,7 +24,7 @@ int    n_phi     =    1;      // number of phi bins
 double r_inner   =  1.0;      // inner boundary radius, in kpc
 double r_outer   = 20.0;      // outer boundary radius, in kpc
 double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_0       =  1e-1;     // number density at inner boundary
 double n_law     =    2.;      // -1*power law exponent of density law
 double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
 double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
@@ -32,11 +32,8 @@ double v_law     =    1.0;      // power law of velocity profile
 double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
-double dust_tau   = 1.;          // Optical depth of dust through the wind (r=0 to Infinity)
-double omnl = 1-n_law;
-double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
-double dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;  // Normalization to give dust_tau
-double dust_albedo = 0.0;         // ratio of scattering to absorption
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.4;         // ratio of scattering to absorption
 
 
 // line parameters
@@ -68,9 +65,6 @@ int verbose;             // output parameter
 //--------------------------------------------
 int main(int argc, char **argv)
 {
-
-  // Dust info
-    printf("# NH_COLM %.3e, dust_norm %.3e\n", nH_colm,dust_norm);
   void Run_Monte_Carlo(char*);
 
   // initialize MPI for parallelism
@@ -95,7 +89,6 @@ int main(int argc, char **argv)
   if (verbose)
     printf("# Sending %.3e photons on %d procs (%.3e total photons)\n",
 	   n_photons,n_procs,n_photons*n_procs);
-
 
 
[…]

### 2010-06-06 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4986 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\newcommand{\naid}{\ion{Na}{I}~$\lambda\lambda 5891, 5897$}
+\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
 \newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
@@
 \newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
+\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
+\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
+\newcommand{\nmg}{$n_{\rm Mg^+}$}
+\newcommand{\mnmg}{n_{\rm Mg^+}}
+\newcommand{\nfe}{$n_{\rm Fe^+}$}
+\newcommand{\mnfe}{n_{\rm Fe^+}}
 \def\hub{h_{72}^{-1}}
@@
 \section{Methodology}
+\label{sec:method}
 
@@
 In the following, we will simply assume a flat continuum that will
-generally be normalized to unit value.
+generally be normalized to unit value.  The size of the emitting
+region, however, will be allowed to vary. [and also anisotropy? if
+not, then say so]
 
 [What does MgI tell us about winds?  Why no P-Cygni?]
+
+\subsection{Monte Carlo Algorithm}
+
+\section{A Fiducial Wind Model}
+\label{sec:fiducial}
+
+In this section, we explore a simple yet illustrative wind model for
+an outflow tuned in part to yield a \ion{Mg}{2} absorption profile
+simlar to that observed toward $z<1$, star-forming galaxies
+\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
+consider the properties of this wind to be any more physically
+motivated than any other choice.
+
+We parameterize the wind through a density law
+
+\begin{equation}
+n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
+\end{equation}
+which conserves mass-flux and a velocity law
+
+\begin{equation}
+v_r (r) = v_0 r
+\end{equation}
+which corresponds to a purely radial flow.  Turbulent motions are
+characterized by a Doppler parameter $b_{\rm turb}$.  
+The wind is isotropic, dust-free, and only extends from an inner
+radius $r_{\rm inner}$ to $r_{\rm outer}$.  At the center of the wind
+is a source of continuum photons with size $r_{\rm source}$.  Lastly,
+we convert the hydrogen density $n_{\rm H}$ to the number density of
+Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
+absolute metallicity of 1/2 solar and depletion factors of 1/10 and
+1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
+and \nfe=\nmg/2.   
+These parameters and their values are summarized in
+Table~\ref{tab:fiducial}.  
+They were chosen to give a wind with a significant optical depth $\tau
+>> 1$ to \mgiia\ and a radial wind speed varying from $v_r \approx 100
+- 1000\mkms$.
+
+In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
+profiles against radius for the fiducial wind model;  
+their single power-law expressions are evident.  The figure also
+shows the optical depth for the \mgiia\ transition ($\tau_{2796}$).
+Although plotted against radius, we calcualted $\tau_{2796}$ by
+summing the opacity as a function of velocity in discrete and small radial intervals
+between $r_{\rm inner}$  and $r_{\rm outer}$.   It was then mapped
+onto radius using the radial velocity profile. 
+The curve agrees well with that derived using the Sobolev approximation.
+We emphasize that the optical depth vs.\ velocity are the primary
+factors that establish the absorption/emission profiles of the
+\ion{Mg}{2} and \ion{Fe}{2} transitions.  In this respect, the 
+parameters that establish the size of the wind (and source) are
+essentially arbitrary.   In contrast, the adopted Doppler paramter
+($b_{\rm turb} = 15 \mkms$) does have a modest impact on the optical
+depth profile, especially at large optical depths.  A larger/smaller
+value would imply ... [FILL IN]
+In turn, this would affect the resulting emission profiles.
+
+The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
+at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
+r_{\rm inner}$.  The optical depth profiles for the \mgiib\ transition
+is identicaly but scaled down by the ratio of $f\lambda$.  Similarly,
+the optcial depth profiles for the \ion{Fe}{2} resonance lines are
+scaled by $f \lambda$ and the \nfe/\nmg\ ratio.
+
+Using the methodology described in $\S$~\ref{sec:method}, we
+propogated photons from the source and through the outflow to an
+`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
+complex.  In Figure~\ref{fig:fiducial_1dspec}, we present the spectrum
+that this observer would record with the unattenuated source spectrum
+normalized to unit value.
 
@@
 
-%\input{Tables/tab_subqso.tex}
+\input{Tables/tab_fiducial.tex}
 
@@
 resonance-line transitions (i.e.\ they share the same upper energy
-levels).  We also show a pair of levels (\ion{Fe}{2}~$\lamabda\lambda
+levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
 2618,2631$) that arise from even higher levels [Should we bother?]
@@
 
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_nvtau_vs_r.ps}
+\caption{
+Density (solid; black), radial velocity (dotted; blue), and
+\mgiia\ optical depth profiles (dashed; red) for the fiducial
+wind model (see Table~\ref{tab:fiducial} for details).
+The density and velocity profiles are simple $r^{-2}$ and $r$
+power-laws.  The optical depth profile was calculated by summing
+the opacity at small and discrete radial intervals.  One notes that
+the wind is optically thick at the inner radius ($r_{\rm inner} =
+1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
+  outer} = 20$\,kpc).
+Note that the density and velocity curves have been scaled for plotting
+convenience.  
+}
+\label{fig:fiducial_nvt}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_fiducial_1d.ps}
+\caption{
+{\it Left} -- (upper) \ion{Mg}{2} profiles for the fiducial wind model
+described in Table~\ref{tab:fiducial} and
+Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
+characteritic of an outflow with significant absorption blueward of
+line center (dashed vertical lines) extending to $v = -1000\mkms$
+and signficiant emission redward of line center.  Note
+that even though the peak optical depth of the \ion{Mg}{2} transitions
+is nearly 30 at $v \approx -70 \mkms$, photons scattered off the outflow
+fill in the absorption.
+(lower) \ion{Fe}{2} absorption and emission profiles for the UV1
+multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
+show weaker absorption due to the smaller Fe$^+$ number density and
+lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
+the emission for \feiia\ is significantly weaker than that of the
+\feiib\ and \mgiid\ transitions.  This is because a majority of the
+absorbed \feiia\ photons are converted into
+\ion{Fe}{2}~$\lambda\lambda 2612, 2632$ photons as observed.
+[Mention the emission kinematics?]
+}
+\label{fig:fiducial_nvt}
+\end{figure}
+
 \end{document}

### 2010-06-06 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  2e6;    // number of photons
+double n_photons =  1e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
@@ -32,10 +32,10 @@ double v_law     =    1.0;      // power law of velocity profile
 double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
-double dust_tau   = 1.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
 double omnl = 1-n_law;
 double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
-double dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;  // Normalization to give dust_tau
+double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 
 
@@ -70,7 +70,15 @@ int main(int argc, char **argv)
 {
 
   // Dust info
-    printf("# NH_COLM %.3e, dust_norm %.3e\n", nH_colm,dust_norm);
+  // printf("# NH_COLM %.3e, dust_norm %.3e\n", nH_colm,dust_norm);
+    if(argc < 2) return 0;
+    dust_tau = atof(argv[1]);
+    dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;  // Normalization to give dust_tau
+    //    printf("# argc %d dust_norm %.3e\n",argc, dust_norm);
+
+    // Photons
+    if(argc > 2) n_photons = atof(argv[2]);
+
   void Run_Monte_Carlo(char*);
 
   // initialize MPI for parallelism

### 2010-06-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4992 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\aconfig}{a~$^6$D}
+\newcommand{\zconfig}{z~$^6$D$^0$}
+\newcommand{\mvr}{v_{\rm r}}
 \newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
@@
 \newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
+\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
 \newcommand{\nmg}{$n_{\rm Mg^+}$}
@@
 \begin{abstract}
-Blah
+\begin{itemize}
+\item Emission is a generic feature of (nearly) isotropic winds.  This
+  emission fills in absorption at $v \approx 0$, significantly
+  complicating the absorption-line analysis. 
 \end{abstract}
@@
 
-[Neglect collisional excitation and de-excitation.  These would
-require $n_e > 10^3 \cm{-3}$.  Non-detection of FeI argues against
-this.]
+[Table of $f,\lambda,A,\gamma$]
 
 In this paper, we will focus on two sets of radiative transitions
-associated with the Fe$^+$ and Mg$^+$ ions.  The choice of these
-specific low-ions is motivated by our own observations
-\citep{rubin10b} but (as described below) these two ions exhibit
-the dominant characteristics of the majoriy of low-ions used to study
-cool-gas outflows. [word] Therefore, the majority of our results can
-be generalized to other transitions that are freuqenly used.
+associated with the Fe$^+$ and Mg$^+$ ions, a choice motivated by 
+our own observations \citep{rubin10b}.  Although this is a limited
+set, the two ions and their transitions have 
+characteristics that resemble the properties for the majority of low-ions 
+observed in cool-gas outflows. [wording still stinks] Therefore, many
+of our results may be generalized to other studies.
 
 The Mg$^+$ ion, with a single 3s electron in the ground-state,
-exhibits an alkali doublet of transitions that are analagous to the
+exhibits an alkali doublet of transitions similar to the
 \lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
-we present the energy level diagram for the Mg$^+$ ion associated with
-the commonly observed \mgiid\ doublet.  In non-relativistic quantum
+we present the energy level diagram for this 
+\mgiid\ doublet.  In non-relativistic quantum
 mechanics, the 2p$^6$3p level is said to be split by spin-orbit
-coupling.  This doublet marks the only \ion{Mg}{2} electric-dipole transitions
-with wavelengths near 2800\AA.  Furthermore, the transtion connecting
-the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ is forbidden by several
-selection rules.  Therefore, an absorption to either of the upper
-states is followed essentially 100$\%$ of the time by a spontaneous decay to the
-ground state.
+coupling which produces the line doublet.  These are the only
+\ion{Mg}{2} electric-dipole transitions 
+with wavelengths near 2800\AA. Also, the transtion connecting
+the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
+selection rules.  Therefore, an absorption from
+2p$^6$^3s~$\to$~2p$^6$3p 
+is followed nearly 100$\%$ of the time by a spontaneous decay to the
+ground state and our treatment will ignore any other possibilities
+(e.g.\ absorption of a second photon).
 
 The physics of the \mgiid\ doublet
-is analagous [repeating myself] to the physics of \ion{H}{1}
-\lya, and also the \naid\ doublet and many other doublets commonly
-studied in the ISM and IGM.  The key quantitative differences are in
-the wavelengths of the transitions and, for the calculations of interest
-in ths paper, their energy separations.  For \ion{H}{1} \lya, the
-separation is sufficiently small $\Delta v = c \Delta E / E \approx 1.3
-\mkms$ that most radiative transfer treatments ignore the fact that
-\lya\ is a pair of transitions.   This is justified by the fact that
-most astrophysical processes have turbulent processes that
-significnatly exceed this velocity separation and effectively mix the
-two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
-\ion{Na}{1} ($\Delta v \approx 304 \mkms$), and most other doublets
-commonly studies the separations are large and demand that the lines
-be treated separately.  In terms of the analysis of outflows, the line
-separation is especially relevant when the outflow speed matches the
-line separation.
+is analagous to the physics of \ion{H}{1}
+\lya, the \naid\ doublet, and many other doublets commonly
+studied in the ISM and IGM.  These doublets differ only in
+the transiton wavelengths and the energy of the doublet separation. 
+For \ion{H}{1} \lya, the
+separation is sufficiently small ($\Delta v = c \Delta E / E \approx
+1.3 \mkms$) that most radiative transfer treatments actually ignore the fact that
+there are two transitions.   This is generally a justifiable
+assumption because 
+most astrophysical processes have turbulent motions that
+significantly exceed this velocity separation and effectively mix the
+two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
+\ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
+commonly studied the separations are large and the lines
+must be treated separately.  Regarding analysis of outflows, the line
+separation plays an important role when the outflow speed $\mvr
+\gtrsim \Delta v$.
 
@@
 frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
-energy levels recorded \citep{iron} and even this is a necessarily
-incomplete list.  In this paper, we will focus on 9 of the levels
-related to the UV1 mutliplet whose wavelengths lie near 2600\AA\
-(Figure~\ref{fig:energy}).  One reason for the complexity of iron is
-that the majoriyt of energy levels exhibit fine-structure splitting.
-This includes the ground-state which has four fine-structure levels with
-excitation energies $T_{\rm ex} = \Delta E / k$ ranging from $\approx
-500-1500$\,K.  We label these according to the total angular momentum
-of each level $J$, with the ground-state having $J=9/2$.
-Transitions between these fine-structure levels are magnetic-dipole
-transitions with spontaneous decay times of several hours.  In
-principle, these levels can be populated by indirect UV pumping
-\citep[e.g][]{sv02,pcb06}, but this would require that the gas lie
-close to the source of UV photons (see $\S$~\ref{sec:pump}).  In the
-following, we will assume that only the ground-state is populated by
-electrons and therefore capable of absorbing photons.
+energy levels recorded \citep{iron}, and even this is an
+incomplete list.  
+One reason for the complexity of iron is
+that the majority of its configurations exhibit fine-structure splitting.
+This includes the ground-state configuration (\aconfig) which is split
+into 5 levels with 
+excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
+$T_{\rm{ex} \approx
+500-1500$\,K.  These levels are usually labelled by the total angular momentum
+$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
+Transitions between these fine-structure levels are 
+forbidden (magnetic-dipole) with spontaneous decay times of several hours.
 
-[Comment on UV1 a bit more]
+In this paper, we will focus on transitions between the ground-state
+configuration and the levels associated with the \zconfig\
+configuration.  This set of transitions are named the
+UV1 mutliplet with wavelengths near 2600\AA.
+There are two resonance-line transitions (defined to originate in the
+true ground-state) associated with this multiplet, \feiid,
+corresponding to $\Delta J = 0, -1$.  The solid (green) downward
+arrows in Figure~\ref{fig:energy} mark the transitions that connect to
+the upper energy levels of the resonance lines.  These transitons can
+occur following the absorption of a single photon by the ion in its
+ground-state.
+
+The Figure also shows (as dashed downward arrows) two of the
+transitions that connect to higher energy levels of the \zconfig\
+configuration.  Radiatively, these can only occur after the absorption
+of two photons: one to raise the electron from the ground-state to an
+excited state and one from the excited state to one of the \zconfig\
+levels with $J \le 5/2$.  The excitation of the Fe$^+$ ion by the
+absorption of UV photons is termed indirect UV pumping
+\citep[e.g][]{sv02,pcb06} and requires the ion to lie
+near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
+following, we will assume that this does not occur and that only the 
+true ground-state is populated by electrons.
+
+Our calculations also ignore collisional
+processes\footnote{Recombination is also ignored.}, i.e.\ collisional
+excitation and de-excitation of the various levels.  For the
+fine-structure levels of the \aconfig\ configuration, the excitation
+energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
+density $n_c$ is very large.  For the \aconfig$_{9/2} \to
+$\aconfig$_{7/2}$ transition, the critical density $n_c \approx XX
+\cm{-3}$.  At these densities, one would predict significant (and
+detectable) quantities of \ion{Fe}{1} which has not yet been observed
+\citep[see also][]{pcb06}.  The strongest arguement for neglecting
+collisions is the general absence of {\it absorption} from the
+fine-structure levels of the \aconfig\ configuration.  [Does Kate see
+blue-shifted FeII* in absorption?]  This provides an empirical
+demonstration that collsioinal excitation is insignificant, and by
+inference one may neglect collisional de-excitation.  Meanwhile, the
+critical density and excitation energies for \ion{Mg}{2} are $n_c =
+??, T_{\rm ex} \approx 50,000$\,K.
 
@@
 
-The majority (all?) of observational studies of cool gas outflows in
-absorption have focused on intervening, star-forming galaxies.  The
-unobscured emisison of these galaxies is a complex combination of
+Nearly all of the absorption studies on cool-gas outflows 
+have focused on intensely, star-forming galaxies.  The
+intrinsic emisison of these galaxies is a complex combination of
 stars and \ion{H}{2} regions that is then modulated by dust and gas
-within its ISM.  In terms of the spectral regions studied in this
-paper, most stars show a featureless continuum with a few spectral
+within the galaxy's ISM.  In terms of the spectral regions studied
+here, most stars show a featureless continuum with a few spectral
 types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
-[Any emission??]  Furthermore, \ion{H}{2} regions are observed to emit
+[Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
 at the \mgiid\ doublet, primarily due to recombinations in the outer
-layers.  It is beyond the scope of this paper to properly model this
+layers [How about FeII?].  It is beyond the scope of this paper to
+properly model the 
 stellar absorption and \ion{H}{2} region emission, but the reader
-should be aeware that they can complicate the observed spectrum,
-independent of the effects of a galactic outflow.
-In the following, we will simply assume a flat continuum that will
-generally be normalized to unit value.  The size of the emitting
-region, however, will be allowed to vary. [and also anisotropy? if
-not, then say so]
+should be aware that they can complicate the observed spectrum,
+independent of a galactic outflow.
+In the following, we will simply assume a flat continuum 
+normalized to unit value.  The size of the emitting
+region $r_{\rm source}$, however, is a variable parameter.
 
@@
 
+[Describe 1D and 3D algorithms]
+
+[Put tests in an Appendix?]
+
 \section{A Fiducial Wind Model}
@@
 In this section, we explore a simple yet illustrative wind model for
-an outflow tuned in part to yield a \ion{Mg}{2} absorption profile
+a galactic-scale outflow.  The properties of this wind were tuned, in
+part, to yield a \ion{Mg}{2} absorption profile 
 simlar to that observed toward $z<1$, star-forming galaxies
 \citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
-consider the properties of this wind to be any more physically
-motivated than any other choice.
+favor this fiducial model over any other wind scenario nor are its
+properties any more physically motivated. 
+Its primary purpose is to establish a baseline for exploration.
 
-We parameterize the wind through a density law
+The fiducial wind follows a density law
 
@@
 \end{equation}
-which conserves mass-flux and a velocity law
+(mass-flux conserving) and a velocity law
 
@@
 characterized by a Doppler parameter $b_{\rm turb}$.  
-The wind is isotropic, dust-free, and only extends from an inner
-radius $r_{\rm inner}$ to $r_{\rm outer}$.  At the center of the wind
-is a source of continuum photons with size $r_{\rm source}$.  Lastly,
+The wind is isotropic, dust-free, and extends from an inner wind
+radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  At
+the center of the wind 
+is a homogenous source of continuum photons with size $r_{\rm source}$.  Lastly,
 we convert the hydrogen density $n_{\rm H}$ to the number density of
@@
 and \nfe=\nmg/2.   
-These parameters and their values are summarized in
-Table~\ref{tab:fiducial}.  
-They were chosen to give a wind with a significant optical depth $\tau
->> 1$ to \mgiia\ and a radial wind speed varying from $v_r \approx 100
-- 1000\mkms$.
+These normalizations give a wind with a peak optical depth $\tau
+>> 1$ to \mgiia\ that becomes optically thin over a velocity range
+spanning $v_r \approx 100 - 1000 \, \mkms$.  
+All of the parameters are summarized in Table~\ref{tab:fiducial}.
 
@@
 `observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
-complex.  In Figure~\ref{fig:fiducial_1dspec}, we present the spectrum
+complex.  In Figure~\ref{fig:fiducial_1d}, we present the spectrum
 that this observer would record with the unattenuated source spectrum
-normalized to unit value.
+normalized to unit value.   Consider first the \ion{Mg}{2} profiles;
+these show the canonical P-Cygni profiles that characterize a 
+source embedded within an outflow.  Strong absorption is evident at
+$v < -50 \mkms$ in both transitions and each shows emission at
+positive velocities.  For this isotropic and dust-free model, the
+total equivalent width of the doublet must be zero
+(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
+absorbed escapes the system at another energy, primarily at lower
+frequency.  The wind simply shuffles photons in frequency space.
+
+Focusing on the \ion{Mg}{2} absorption profiles, one notes they have
+similar and non-zero depth even though their $f\lambda$ values differ
+by a factor of two.  In absorption line analysis, this is generally
+the tell-tale signature of a gas that has a high optical depth (i.e.\
+saturated) but only partially covers the emitting source
+\citep[e.g.][]{hamman10}.  In this fiducial model, however, the wind
+entirely covers the source and the observed behaviour is unrelated to
+any partial covering.  Figure~\ref{fig:noemiss}, which compares the
+absorption profiles as derived and in the limit where photons are not
+re-emitted, shows this explicitly.   One notes that the no-emission
+case has a pair of strong absorption lines that absorb all photons at
+$v \approx -100 \mkms$, i.e.\ these profiles are simply $\exp(-\tau)$
+with $\tau$ given by the curve in Figure~\ref{fig:fiducial_nvt}.  
+The actual profile, meanwhile, has been `filled in' at $v \approx -100
+\mkms$ by photons scattered and re-emitted by the wind.  An
+absorption-line analysis that ignores these effects
+\citep[e.g.][]{sato} would systematically underestimate the true optical
+depth and falsely conclude partial covering.  [MORE?]
+[Dan's analytic calculation here?]
+
+One also notes that the emission profiles of the \mgiid\ doublet
+are very similar and have comparable equivalent widths.  In fact the
+flux of the \mgiib\ transition even exceeds that for \mgiia.  The
+profiles are similar because the absorption is saturated.
+Furthermore, the flux from \mgiib\ is greater than that for
+\mgiia\ because the wind speed exceeds the velocity separation
+of the doublet $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$ such
+that the \mgiib\ absorption profile absorbs the red wing of the
+\mgiia\ emission profile.  The relative strengths of these emission
+lines, therefore, is sensitive to both the optical depth and velocity
+extent of the wind.
+
+The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
+majority of the \ion{Fe}{2} UV1 transitions.  Several of these are
+shown individually in the velocity plot on the right.  The line
+profiles for \feiib\ is very similar to those of the \mgiid\ doublet;
+one observes strong absorption to negative velocities and strong
+emission at $v > 0 \mkms$ producing the P-Cygni profile.  Splitting
+the profile at $v = -50 \mkms$, we measure an equivalent width
+$W_{2600}^{\rm abs} = 1.19$\AA\ in absorption and $W_{2600}^{\rm em} =
+-0.84$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
+equivalent width of $W_{2600}^{\rm TOT} \approx 0.35$\AA.  
+[Point out that if $\tau_{2600}$ were higher, than the photons would
+likely be more trapped and more would come out as 2626.  Also a
+v=0km/s component might make quite a difference.]
+In contrast, the \feiia\ resonance line shows much weaker emission and
+a much higher total equivalent width ($W_{2586}^{\rm TOT} = XX$\AA).
+The differences related directly to Einstein coefficients for the
+transitions connecting the upper levels of \feiid\ to the 
+fine-structure levels of a~$^6$D.  In the case of \feiib, the
+\ion{Fe}{2}~2626 transition that returns to the a~$^6$D$_{7/2}$
+excited level has an $\approx 4\times$ smaller coefficient than the
+resonance line.  Therefore, the majority of photons absorbed at
+$\lambda 2600$ are re-emitted with the same energy and only scatter 
+in frequency space around the line.  For \feiia, the transitions to
+the a~$^6$D$_{7/2}$ and a~$^6$D$_{5/2}$ levels have comparable and
+even larger A coefficients than that to the ground-state.  Therefore,
+the majority of photons absorbed at $\lambda 2586$ are re-emitted 
+as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
+photons.  [Comment on total EW for 2586?]
+
+[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$?]
+
+[Update the EW values with the new FeII data]
+
+Our algorithm tracks the spatial emissivity of the source+wind
+complex as a function of frequency.  Therefore, it is straightforward
+to construct surface-brightness maps of the emission yielding a
+dataset analagous to intergral-field-unit (IFU) observations.  In
+Figure~\ref{fig:fig_fiducial_ifu_mgii}, we present the output for our
+fiducial wind model at several velocities relative to the \mgiia\
+transition. At $\mvr \le -200 \mkms$, where the wind has an optical
+depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
+the source contributes significantly to the observed flux.  
+At $\mvr=-100 \mkms$, however, the
+wind absorbs all photons from the source and the observed emission is
+entirely due to photons scattered by the wind.  This
+emission significantly exceeds that for $\mvr = -200\mkms$ which
+explains the fact that the absorption peaks at a velocity offset from
+the peak in the wind's optical depth. [word] At $v_{\rm r} \ge 0
+\mkms$,  both the source and wind contribute to the observed emission.
+
+[Spatial cut?]
+
+[FeII emission;  2600 and 2612]
+
+\section{Discussion}
+
+[Are MgII and FeII* emission strict predictions of outflows?  People
+have been so focused on absorption.]
 
@@
 \input{Tables/tab_fiducial.tex}
+\input{Tables/tab_fiducial_ew.tex}
 
@@
 }
-\label{fig:fiducial_nvt}
+\label{fig:fiducial_1d}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_noemiss.ps}
+\caption{
+The black curves show the line profiles (absorption and emission) of
+the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
+model.  These shows the canonical P-Cygni profiles of a source
+embedded within an outflow.  Overplotted (red) on each transition is
+the predicted absorption profile under the constraint that each
+absorbed photon is lost from the system, i.e.\ no scattering or
+re-emission.   It is evident that the true profiles have been `filled
+in' significantly by light scattered in the wind.  Ignoring this
+process, one would model the absorption lines with systematicall lower
+optical depth and derive a partial covering. [word]
+}
+\label{fig:noemiss}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_fiducial_ifu_mgii.ps}
+\caption{
+Surface-brightness emission maps around the \mgiia\ transition for the
+source+wind complex.  The middel panel shows the 1D spectrum with $v=0
+\mkms$ corresponding to $\lambda = 2796.35$ and the dotted vertical
+curves indicating the velocity slices for the emission maps.  The
+source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
+pixels at the center.   At $\mvr=-200 \mkms$, the wind has an optical
+depth of $\tau_{2796} \approx 1$ such that the source contributes
+significantly to the observed flux.  At $\mvr=-100 \mkms$, however, the
+wind absorbs all photons from the source and the observed emission is
+entirely due to photons scattered by the wind.  Surprisingly, this
+emission exceeds that observed at $\mvr = -200\mkms$. At $\mvr \ge 0
+\mkms$,  both the source and wind contribute to the observed emission.
+}
+\label{fig:fiducial_ifu_mgii}
 \end{figure}

### 2010-06-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4994 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \usepackage{natbib,amsmath}
+
 \special{papersize=8.5in,11in}
@@
 
-\newcommand{\aconfig}{a~$^6$D}
+\newcommand{\maconfig}{2p$^6$3s}
+\newcommand{\mbconfig}{2p$^6$3p}
+\newcommand{\aconfig}{a~$^6$D$^0$}
 \newcommand{\zconfig}{z~$^6$D$^0$}
@@
   complicating the absorption-line analysis. 
+\end{itemize}
 \end{abstract}
@@
 selection rules.  Therefore, an absorption from
-2p$^6$^3s~$\to$~2p$^6$3p 
+\maconfig~$\to$~\mbconfig\
 is followed nearly 100$\%$ of the time by a spontaneous decay to the
@@
 excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
-$T_{\rm{ex} \approx
-500-1500$\,K.  These levels are usually labelled by the total angular momentum
+$T_{\rm ex} \approx 500-1500$\,K.  These levels are usually labelled by the total angular momentum
 $J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
@@
 their single power-law expressions are evident.  The figure also
-shows the optical depth for the \mgiia\ transition ($\tau_{2796}$).
-Although plotted against radius, we calcualted $\tau_{2796}$ by
-summing the opacity as a function of velocity in discrete and small radial intervals
-between $r_{\rm inner}$  and $r_{\rm outer}$.   It was then mapped
-onto radius using the radial velocity profile. 
-The curve agrees well with that derived using the Sobolev approximation.
-We emphasize that the optical depth vs.\ velocity are the primary
-factors that establish the absorption/emission profiles of the
-\ion{Mg}{2} and \ion{Fe}{2} transitions.  In this respect, the 
-parameters that establish the size of the wind (and source) are
-essentially arbitrary.   In contrast, the adopted Doppler paramter
-($b_{\rm turb} = 15 \mkms$) does have a modest impact on the optical
-depth profile, especially at large optical depths.  A larger/smaller
-value would imply ... [FILL IN]
+shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
+This profile is what determines the observed absorption/emission lines
+for the wind.  
+Although plotted against radius, we first calculated $\tau_{2796}$ 
+as a function of velocity by summing the opacity in a series of
+discrete and small radial intervals
+between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
+$\tau_{2796}$ onto radius using the radial velocity profile and 
+checked that this profile is in good agreement with
+the Sobolev approximation.  
+The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
+at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
+r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
+is scaled down by the ratio of $f\lambda$ but otherwise identical.  Similarly,
+the optical depth profiles for the \feiid\ transitions are
+scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.  
+The adopted Doppler parameter
+(here $b_{\rm turb} = 15 \mkms$) also has a modest impact on the results,
+specially at large optical depths.  A larger/smaller
+$b$-value would imply ... [FILL IN]
 In turn, this would affect the resulting emission profiles.
 
-The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
-at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
-r_{\rm inner}$.  The optical depth profiles for the \mgiib\ transition
-is identicaly but scaled down by the ratio of $f\lambda$.  Similarly,
-the optcial depth profiles for the \ion{Fe}{2} resonance lines are
-scaled by $f \lambda$ and the \nfe/\nmg\ ratio.
+Because the results are dictated by the $\tau_{2796}$ profile and the
+Doppler parameter, the actual dimensions and density of the wind are
+essentially unimportant provided they scale together to give the same
+$\tau_{2796}$ profile.  Therefore, one may consider our choices for
+$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
+Nevertheless, we attempted to adopt values for this fiducial model
+that some astrophysical motivation.
 
@@
 `observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
-complex.  In Figure~\ref{fig:fiducial_1d}, we present the spectrum
-that this observer would record with the unattenuated source spectrum
-normalized to unit value.   Consider first the \ion{Mg}{2} profiles;
-these show the canonical P-Cygni profiles that characterize a 
+complex.  Figure~\ref{fig:fiducial_1d} presents the spectrum
+that this observer would record with the ``unattenuated'' source flux
+normalized to unit value.   The \ion{Mg}{2} profiles
+show the canonical `P-Cygni profile' that characterize a continuum
 source embedded within an outflow.  Strong absorption is evident at
@@
 (Table~\ref{tab:fiducial_EW}), i.e.\ every photon
-absorbed escapes the system at another energy, primarily at lower
-frequency.  The wind simply shuffles photons in frequency space.
+absorbed still escapes the system, primarily at lower
+energies.  The wind simply shuffles photons in frequency space.
 
-Focusing on the \ion{Mg}{2} absorption profiles, one notes they have
-similar and non-zero depth even though their $f\lambda$ values differ
-by a factor of two.  In absorption line analysis, this is generally
-the tell-tale signature of a gas that has a high optical depth (i.e.\
-saturated) but only partially covers the emitting source
-\citep[e.g.][]{hamman10}.  In this fiducial model, however, the wind
-entirely covers the source and the observed behaviour is unrelated to
-any partial covering.  Figure~\ref{fig:noemiss}, which compares the
-absorption profiles as derived and in the limit where photons are not
-re-emitted, shows this explicitly.   One notes that the no-emission
-case has a pair of strong absorption lines that absorb all photons at
-$v \approx -100 \mkms$, i.e.\ these profiles are simply $\exp(-\tau)$
-with $\tau$ given by the curve in Figure~\ref{fig:fiducial_nvt}.  
+Focusing on the \ion{Mg}{2} absorption, one notes the profiles have
+positive intensity yet similar depth even though their $f\lambda$
+values differ by a factor of two.  In standard absorption line
+analysis, this is generally 
+the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
+saturated) which only partially covers the emitting source
+\citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
+{\it entirely} covers the source; the apparent partial covering must
+be related to a different effect.
+Figure~\ref{fig:noemiss}, which compares the true
+absorption profiles against the case where absorbed photons are not
+re-emitted, further illustrates this issue.   As expected from the
+$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}, the no-emission
+case predicts a strong \mgiid\ doublet that absorbs all photons at
+$v \approx -100 \mkms$, i.e.\ $I_{2796} = \exp(-\tau_{2796}) \approx 0$.
 The actual profile, meanwhile, has been `filled in' at $v \approx -100
-\mkms$ by photons scattered and re-emitted by the wind.  An
+\mkms$ by photons scattered and re-emitted by the wind (see below).  An
 absorption-line analysis that ignores these effects
 \citep[e.g.][]{sato} would systematically underestimate the true optical
-depth and falsely conclude partial covering.  [MORE?]
-[Dan's analytic calculation here?]
+depth and falsely conclude partial covering.  We will find that this
+behaviour is a generic results for models with a high degree of
+isotropy.
+[Dan's analytic calculation here? or Appendix?]
 
@@
 flux of the \mgiib\ transition even exceeds that for \mgiia.  The
-profiles are similar because the absorption is saturated.
+emission profiles are similar because the absorption is saturated.
 Furthermore, the flux from \mgiib\ is greater than that for
 \mgiia\ because the wind speed exceeds the velocity separation
-of the doublet $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$ such
-that the \mgiib\ absorption profile absorbs the red wing of the
-\mgiia\ emission profile.  The relative strengths of these emission
+of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$, such
+that the \mgiib\ absorption profile partially absorbs the red wing of the
+\mgiia\ emission profile.  The relative strengths of the emission
 lines, therefore, is sensitive to both the optical depth and velocity
@@
 
+Now consider the \ion{Fe}{2} transitions.
 The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
-majority of the \ion{Fe}{2} UV1 transitions.  Several of these are
-shown individually in the velocity plot on the right.  The line
-profiles for \feiib\ is very similar to those of the \mgiid\ doublet;
+majority of the \ion{Fe}{2} UV1 transitions and several are
+shown in the velocity plot.  The line
+profile for \feiib\ is very similar to those for the \mgiid\ doublet;
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \mkms$ producing the P-Cygni profile.  Splitting
+emission at $v > 0 \mkms$ producing a P-Cygni profile.  Splitting
 the profile at $v = -50 \mkms$, we measure an equivalent width
-$W_{2600}^{\rm abs} = 1.19$\AA\ in absorption and $W_{2600}^{\rm em} =
--0.84$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
-equivalent width of $W_{2600}^{\rm TOT} \approx 0.35$\AA.  
+$W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
+-0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
+equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
 [Point out that if $\tau_{2600}$ were higher, than the photons would
@@
 In contrast, the \feiia\ resonance line shows much weaker emission and
-a much higher total equivalent width ($W_{2586}^{\rm TOT} = XX$\AA).
-The differences related directly to Einstein coefficients for the
-transitions connecting the upper levels of \feiid\ to the 
-fine-structure levels of a~$^6$D.  In the case of \feiib, the
-\ion{Fe}{2}~2626 transition that returns to the a~$^6$D$_{7/2}$
-excited level has an $\approx 4\times$ smaller coefficient than the
+a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA)
+even though the line has a $2 \times$ lower $f\lambda$ value.
+The difference comes the extra downward transition from the
+\zconfig$_{7/2}$ level and (more importantly) that the Einstein A
+coefficients  of the non-resonant lines match and even exceed that for
+the resonant line.  In the case of \feiib, the
+\ion{Fe}{2}~2626 transition 
+has an approximately  $4\times$ smaller coefficient than the
 resonance line.  Therefore, the majority of photons absorbed at
 $\lambda 2600$ are re-emitted with the same energy and only scatter 
-in frequency space around the line.  For \feiia, the transitions to
-the a~$^6$D$_{7/2}$ and a~$^6$D$_{5/2}$ levels have comparable and
-even larger A coefficients than that to the ground-state.  Therefore,
-the majority of photons absorbed at $\lambda 2586$ are re-emitted 
+in frequency space around the line.  For \feiia, 
+the majority of photons absorbed are re-emitted 
 as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
-photons.  [Comment on total EW for 2586?]
+photons.  
+The total equivalent width, however, of the lines connected to the
+\zconfig$_{7/2}$ upper level does vainsh (i.e.\ photons are conserved
+in this fiducial wind).
 
@@
 
-[Update the EW values with the new FeII data]
-
-Our algorithm tracks the spatial emissivity of the source+wind
-complex as a function of frequency.  Therefore, it is straightforward
-to construct surface-brightness maps of the emission yielding a
+Our 3D Monte Carlo algorithm tracks the spatial emissivity of the source+wind
+complex as a function of frequency.  From this output, we
+constructed surface-brightness maps producing a
 dataset analagous to intergral-field-unit (IFU) observations.  In
-Figure~\ref{fig:fig_fiducial_ifu_mgii}, we present the output for our
+Figure~\ref{fig:fiducial_ifu_mgii}, we present the output for our
 fiducial wind model at several velocities relative to the \mgiia\
@@
 wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  This
-emission significantly exceeds that for $\mvr = -200\mkms$ which
-explains the fact that the absorption peaks at a velocity offset from
-the peak in the wind's optical depth. [word] At $v_{\rm r} \ge 0
+entirely from photons scattered by the wind.  This scattered emission
+actually exceeds the source+wind emission at 
+$\mvr = -200\mkms$ such
+that the absorption profile reaches peak depth at a velocity that is
+negatively offset from
+the peak in optical depth.  The net result of the scattered photons is
+a weaker \ion{Mg}{2} profile that is offset fromt he true optical
+depth profile.  Clearly, this will complicate efforts to estimate the
+speed, covering fraction, and total column density of the wind.  At $v
+= 0 \, \mkms$, the wind and source have comparable total flux and the
+latter dominates at higher velocities.  
+At $v_{\rm r} \ge 0
 \mkms$,  both the source and wind contribute to the observed emission.
 
-[Spatial cut?]
+[Spatial cut? Yes]
 
-[FeII emission;  2600 and 2612]
+Similar characteristics are observed for the \ion{Fe}{2} resonance
+transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
+For transitions to fine-structure levels of the \aconfig, the source
+is unattenuated but there is also a significant contribution from the
+wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
+[Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
+and 1-20; ignoring the source]
 
@@
 Energy level diagrams for the \mgiid\ doublet and the UV1
-multiplet of \ion{Fe}{2} transitions.   Each transition shown is
+multiplet of \ion{Fe}{2} transitions   
+(based on Figure~7 from \cite{hmt+99}).
+Each transition shown is
 labelled by its rest wavelength (\AA) and Einstein A-coefficient
@@
 Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
-are split into multiple energy levels giving rise to a series of
-electric-dipole transitions between these fine-structure levels.   
+exhibit fine-structure splitting that gives rise to a series of
+electric-dipole transitions. 
 The downward (green) arrows show the transitions connected to the
@@
 levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
-2618,2631$) that arise from even higher levels [Should we bother?]
-Based on Figure~7 from \cite{hartagan9X}.
+2618,2631$) that arise from higher levels in the \zconfig\
+configuration.  These transitions have not yet been observed in
+galactic-scale outflows and are not considerd in our analysis.
 }
@@
 source+wind complex.  The middel panel shows the 1D spectrum with $v=0
-\mkms$ corresponding to $\lambda = 2796.35$ and the dotted vertical
+\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
 curves indicating the velocity slices for the emission maps.  The
@@
 
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_fiducial_ifu_feii2600.ps}
+\caption{
+Surface-brightness emission maps around the \feiib\ transition for the
+source+wind complex.  The middle panel shows the 1D spectrum with $v=0
+\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
+curves indicating the velocity slices for the emission maps.  
+The results are very similar to those observed for the \mgiid\ doublet
+(Figure~\ref{fig:fiducial_ifu_mgii}).
+}
+\label{fig:fiducial_ifu_feii2600}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
+\caption{
+Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda 2612$ transition for the
+source+wind complex.  The middle panel shows the 1D spectrum with $v=0
+\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
+curves indicating the velocity slices for the emission maps.  
+In this case, the source is unattenuated yet scattered photons from
+the wind also have a significant contribution. 
+}
+\label{fig:fiducial_ifu_feii2612}
+\end{figure}
+
 \end{document}

### 2010-06-10 Winds/Grid/Monte/transport.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4995 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,347 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "model.hh"
+#include "lines.hh"
+
+extern gsl_rng      *rangen;    // random number generator
+extern int verbose;             // output parameter
+extern MODEL model;
+extern SPECTRUM spectrum;
+extern VOIGT voigt;
+extern double D_obs[3], cos_obs[4];
+extern LINES lines;
+
+
+struct PHOTON {
+  int    ic;
+  double r[3], D[3];
+  double lam, xloc, lloc;
+  double E_p;
+  int    escaped;
+};
+
+double stepfrac = 0.7;
+
+//--------------------------------------------
+// Calculate a spectrum using Monte Carlo
+//--------------------------------------------
+void Run_Monte_Carlo(double n_photons)
+{
+  // local variables
+  int    i, scatter;
+  double tau_r, tau_x, vdotD;
+  double l_step, step, max_step;
+  double Pe, lobs, r_rot[3];
+  PHOTON p;
+
+  // functions to call
+  void MPI_Average_Array(double *, int);
+  double P_esc(double, double*);
+  void Emit(PHOTON*);
+  void Line_Scatter(PHOTON&, double);
+  void Get_Rotated_Coords(double *, double *);
+
+  // set the start timer 
+  time_t start_tp,end_tp;
+  time(&start_tp);
+
+  // send the photons
+  for (i=0;i<n_photons;i++)
+  {
+    Emit(&p);
+    // Energy per photon
+    p.E_p = model.L_tot/(1.0*n_photons); 
+
+    // add in straight light
+    Pe   = P_esc(p.lloc,p.r);
+    lobs = p.lloc*(1 - model.vdotD(p.ic,D_obs)/C_LIGHT);
+    Get_Rotated_Coords(p.r,r_rot);
+    spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe);
+
[…]

### 2010-06-10 Winds/papers/Theory/First/Analysis/Doppler/outflow_doppler_mgii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4997 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,414 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
[…]

### 2010-06-10 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc

@@ -1,0 +1,422 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "lines.hh"
+
+extern LINES lines;
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2575;     // beginning wavelength (Angstroms)
+double l_stop    =  2610;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
[…]

### 2010-06-10 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@4999 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -157,7 +157,7 @@ void Run_Monte_Carlo(char *outfile)
   double mu,phi,sin_theta;
   double tau_r, tau_x, step, r_sq;
   double vd_inc, vd_out, l_step, d_step;
-  double u0,u1,u2, R10, R11, rad, vel;
+  double u0,u1,u2, R10, R11, rad, vel, vproj;
   double uvec[3];
   double nu_d, cross_sec, dens_H;
 
@@ -245,7 +245,7 @@ void Run_Monte_Carlo(char *outfile)
       // if we line scattered, do it
       if (scatter >= 0)
       {
-	xloc = (lam_loc/lambda_0[scatter] - 1)*C_LIGHT/v_doppler;
+	xloc = (lam_loc/lines.lambda(scatter) - 1)*C_LIGHT/v_doppler;
 
 	// Get three velocity components of scatterer
  	u0 = voigt.Scatter_Velocity(xloc);
@@ -284,15 +284,39 @@ void Run_Monte_Carlo(char *outfile)
  	xloc = xloc - vd_inc + vd_out; 
 
 	// go back to wavelength
-	lam_loc = lambda_0[scatter]*(1 + xloc*v_doppler/C_LIGHT);
+	lam_loc = lines.lambda(scatter)*(1 + xloc*v_doppler/C_LIGHT);
 
 	// now get change in observer frame wavelength
 	rad = sqrt(r[0]*r[0] + r[1]*r[1] + r[2]*r[2]);
 	vel = Get_Velocity(r,rad)/C_LIGHT;
+	vproj = vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
 	if (rad > 0)
-	  lam = lam_loc/(1 + vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
+	  lam = lam_loc/(1 + vproj);
 
 	// Deal with branching lines
+	//	for (int j=0;j<lines.n_branch(scatter);j++) 
+	//	{
+	//	  lobs = lines.blam(scatter,j)*(1 - vproj); 
+	//	  Pe   = lines.bprob(scatter,j);
+	//	  spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe); 
+	//	}
+	
+	// see if photon is branched away
+	double r1 = gsl_rng_uniform(rangen);
+	if (r1 > lines.P_scat(scatter)) {
+	  // Count it
+	  count_it = 1;
[…]

### 2010-06-10 Winds/Simple/outflow.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5000 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -140,7 +140,7 @@ void Run_Monte_Carlo(char *outfile)
   double vd_inc, vd_out, l_step, d_step;
   double u0,u1,u2, R10, R11, rad, vel;
   double uvec[3];
-  double nu_d, cross_sec;
+  double nu_d, cross_sec, dens_H;
 
   // functions to call
   void MPI_Average_Array(double *, int);
@@ -182,6 +182,8 @@ void Run_Monte_Carlo(char *outfile)
       lam_loc = lam*(1 + vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
       if (rad == 0) lam_loc = lam;
 
+      dens_H = Get_Density(r,rad); 
+
       // default step size
       step = stepsize;
 
@@ -195,7 +197,8 @@ void Run_Monte_Carlo(char *outfile)
 	tau_r     =  -1.0*log(1 - gsl_rng_uniform(rangen));
 	nu_d = (C_LIGHT/lambda_0[l]/ANGS_TO_CM)*(v_doppler/C_LIGHT);
 	cross_sec = CLASSICAL_CS*f_lu[l]*voigt.Profile(xloc)/nu_d;
-	tau_x     = KPARSEC*Get_Density(r,rad)*abun[l]*metallicity*cross_sec;
+	tau_x     = KPARSEC*dens_H*abun[l]*metallicity*cross_sec;
+	// tau_x     = KPARSEC*Get_Density(r,rad)*abun[l]*metallicity*cross_sec;
 	l_step = tau_r/tau_x;
 	if (tau_x == 0) l_step = VERY_LARGE_NUMBER;
 	if (l_step < step) {step = l_step; scatter = l; }
@@ -203,7 +206,7 @@ void Run_Monte_Carlo(char *outfile)
 
       // get distance to dust scatter/absorption
       tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
-      tau_x = KPARSEC*dust_dens*dust_cs;
+      tau_x = KPARSEC*dens_H*dust_dens*dust_cs;
       d_step = tau_r/tau_x;
       if (tau_x == 0) d_step = VERY_LARGE_NUMBER;
       if (d_step < step) {step = d_step; scatter = -1; dust_scatter = 1; }

### 2010-06-10 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5001 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 #include "lines.hh"
 
-extern LINES lines;
+LINES lines;
 
 // monte carlo parameters
 double n_photons =  1e7;    // number of photons
@@ -293,19 +293,11 @@ void Run_Monte_Carlo(char *outfile)
 	if (rad > 0)
 	  lam = lam_loc/(1 + vproj);
 
-	// Deal with branching lines
-	//	for (int j=0;j<lines.n_branch(scatter);j++) 
-	//	{
-	//	  lobs = lines.blam(scatter,j)*(1 - vproj); 
-	//	  Pe   = lines.bprob(scatter,j);
-	//	  spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe); 
-	//	}
-	
 	// see if photon is branched away
 	double r1 = gsl_rng_uniform(rangen);
 	if (r1 > lines.P_scat(scatter)) {
-	  // Count it
-	  count_it = 1;
+	  // Count it  (deal with dust!!)
+	  // count_it = 1;
 	  // Find which branch
 	  double sum = lines.P_scat(scatter)
 	  for (int j=0;j<lines.n_branch(scatter);j++) 
@@ -313,7 +305,7 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
-		break;
+		sum = 9e9;  // Kludge to avoid 'break'
 	      }
 	    }
 	}

### 2010-06-10 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5002 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -81,7 +81,7 @@ int main(int argc, char **argv)
   
   // Photons
   if(argc > 2) n_photons = atof(argv[2]);
-  lines.Init('fe_uv1.lines')
+  lines.Init("fe_uv1.lines");
 
   void Run_Monte_Carlo(char*);
 
@@ -151,7 +151,7 @@ double Get_Density(double *x, double r)
 void Run_Monte_Carlo(char *outfile)
 {
   // local variables
-  int i, l, ind, scatter, dust_scatter, count_it;
+  int i,j, l, ind, scatter, dust_scatter, count_it;
   double x, lam_loc, xloc,lam;
   double r[3], D[3];
   double mu,phi,sin_theta;
@@ -215,7 +215,7 @@ void Run_Monte_Carlo(char *outfile)
 	// random optical depth to travel
 	tau_r     =  -1.0*log(1 - gsl_rng_uniform(rangen));
 	nu_d = (C_LIGHT/lines.lambda(l)/ANGS_TO_CM)*(v_doppler/C_LIGHT);
-	cross_sec = CLASSICAL_CS*lines.f_lu(l)*voigt.Profile(xloc)/nu_d;
+	cross_sec = CLASSICAL_CS*lines.fval(l)*voigt.Profile(xloc)/nu_d;
 	tau_x     = KPARSEC*dens_H*abun[l]*metallicity*cross_sec;
 	// tau_x     = KPARSEC*Get_Density(r,rad)*abun[l]*metallicity*cross_sec;
 	l_step = tau_r/tau_x;
@@ -289,7 +289,7 @@ void Run_Monte_Carlo(char *outfile)
 	// now get change in observer frame wavelength
 	rad = sqrt(r[0]*r[0] + r[1]*r[1] + r[2]*r[2]);
 	vel = Get_Velocity(r,rad)/C_LIGHT;
-	vproj = vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
+	vproj = vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad;
 	if (rad > 0)
 	  lam = lam_loc/(1 + vproj);
 
@@ -305,9 +305,10 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
[…]

### 2010-06-11 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5003 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -16,8 +16,10 @@ double n_photons =  1e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // beginning wavelength (Angstroms)
-double l_stop    =  2610;     // ending wavelength (Angstroms)
+double spec_start   =  2575;     // spectrum beginning wavelength (Angstroms)
+double spec_stop    =  2635;     // spectrum ending wavelength (Angstroms)
+double l_start   =  2575;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2610;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -174,8 +176,8 @@ void Run_Monte_Carlo(char *outfile)
   // define spectrum counter
   SPECTRUM spectrum;
   double lgrid[3];
-  lgrid[0] = l_start;
-  lgrid[1] = l_stop;
+  lgrid[0] = spec_start;
+  lgrid[1] = spec_stop;
   lgrid[2] = l_delta;
   spectrum.Init(lgrid,n_mu,n_phi);
   spectrum.Set_Name(outfile);
@@ -299,7 +301,7 @@ void Run_Monte_Carlo(char *outfile)
 	  // Count it  (deal with dust!!)
 	  // count_it = 1;
 	  // Find which branch
-	  double sum = lines.P_scat(scatter)
+	  double sum = lines.P_scat(scatter);
 	  for (int j=0;j<lines.n_branch(scatter);j++) 
 	    {
 	      sum += lines.bprob(scatter,j);
@@ -308,7 +310,6 @@ void Run_Monte_Carlo(char *outfile)
 		sum = -9e9;  // Kludge to avoid 'break'
 	      }
 	    }
-	  }
 	}
       }
 

### 2010-06-11 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5005 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -12,14 +12,12 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double spec_start   =  2575;     // spectrum beginning wavelength (Angstroms)
-double spec_stop    =  2635;     // spectrum ending wavelength (Angstroms)
 double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2610;     // photon ending wavelength (Angstroms)
+double l_stop    =  2635;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -176,8 +174,8 @@ void Run_Monte_Carlo(char *outfile)
   // define spectrum counter
   SPECTRUM spectrum;
   double lgrid[3];
-  lgrid[0] = spec_start;
-  lgrid[1] = spec_stop;
+  lgrid[0] = l_start;
+  lgrid[1] = l_stop;
   lgrid[2] = l_delta;
   spectrum.Init(lgrid,n_mu,n_phi);
   spectrum.Set_Name(outfile);

### 2010-06-11 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_feii.cc

@@ -1,0 +1,438 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "lines.hh"
+
+LINES lines;
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2575;     // beginning wavelength (Angstroms)
+double l_stop    =  2610;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
[…]

### 2010-06-11 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_mgii.cc

@@ -1,0 +1,398 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.4;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
+double lambda_0[]   = {2796.352, 2803.531};  
+// line oscillator strengths
+double f_lu[]       = {0.6123,     0.3054}; 
+// abundances of element of line
[…]

### 2010-06-11 Winds/papers/Theory/First/Analysis/outflow_fiducial.cc

@@ -1,398 +1,0 @@
-#include <mpi.h>
-#include <math.h>
-#include <stdlib.h>
-#include <stdio.h>
-#include <time.h>
-#include <gsl/gsl_rng.h>
-#include "locate_array.hh"
-#include "voigt.hh"
-#include "spectrum.hh"
-
-// monte carlo parameters
-double n_photons =  2e6;    // number of photons
-double stepsize  = 0.01;   // maximum size of photon step 
-
-// output spectrum parameters
-double l_start   =  2780;     // beginning wavelength (Angstroms)
-double l_stop    =  2820;     // ending wavelength (Angstroms)
-double l_delta   =   0.1;     // wavelength resolution (Angstroms)
-double F_cont    =    1;      // continuum flux level
-int    n_mu      =    1;      // number of theta bins
-int    n_phi     =    1;      // number of phi bins
-
-// grid parameters
-double r_inner   =  1.0;      // inner boundary radius, in kpc
-double r_outer   = 20.0;      // outer boundary radius, in kpc
-double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary
-double n_law     =    2.;      // -1*power law exponent of density law
-double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
-double v_law     =    1.0;      // power law of velocity profile
-double bipolar   =    0;      // degree of bipolarity
-
-double dust_cs     = 3.33e-24;    // dust cross-section
-double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
-double dust_albedo = 0.4;         // ratio of scattering to absorption
-
-
-// line parameters
-// --------------------------
- //number of lines to use
-int    n_lines      = 2; 
-// line center wavelengths
-double lambda_0[]   = {2796.352, 2803.531};  
-// line oscillator strengths
-double f_lu[]       = {0.6123,     0.3054}; 
-// abundances of element of line
[…]

### 2010-06-11 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5008 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -12,12 +12,12 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // beginning wavelength (Angstroms)
-double l_stop    =  2610;     // ending wavelength (Angstroms)
+double l_start   =  2575;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2635;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -72,15 +72,7 @@ int verbose;             // output parameter
 int main(int argc, char **argv)
 {
 
-  // Dust info
-  // printf("# NH_COLM %.3e, dust_norm %.3e\n", nH_colm,dust_norm);
-  // if(argc < 2) return 0;
-  // dust_tau = atof(argv[1]);
-  // dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;  // Normalization to give dust_tau
-  //    printf("# argc %d dust_norm %.3e\n",argc, dust_norm);
-  
-  // Photons
-  // if(argc > 2) n_photons = atof(argv[2]);
+  // Initialize
   lines.Init("fe_uv1.lines");
 
   void Run_Monte_Carlo(char*);
@@ -184,6 +176,9 @@ void Run_Monte_Carlo(char *outfile)
   int n_wave = (l_stop - l_start)/l_delta;
   double E_p = F_cont*n_wave*n_mu*n_phi/n_photons*l_delta;
 
+  // Zero out dust
+  dust_scatter = 0;
+
   // send the photons
   for (i=0;i<n_photons;i++)
   {
@@ -223,14 +218,6 @@ void Run_Monte_Carlo(char *outfile)
 	if (l_step < step) {step = l_step; scatter = l; }
       }
 
-      // get distance to dust scatter/absorption
-      tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
-      tau_x = KPARSEC*dens_H*dust_norm*dust_cs;
-      d_step = tau_r/tau_x;
[…]

### 2010-06-11 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5009 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -175,8 +175,6 @@ void Run_Monte_Carlo(char *outfile)
   // Energy per photon
   int n_wave = (l_stop - l_start)/l_delta;
   double E_p = F_cont*n_wave*n_mu*n_phi/n_photons*l_delta;
-
-  // Zero out dust
   dust_scatter = 0;
 
   // send the photons
@@ -218,6 +216,14 @@ void Run_Monte_Carlo(char *outfile)
 	if (l_step < step) {step = l_step; scatter = l; }
       }
 
+      // get distance to dust scatter/absorption
+//      tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
+//      tau_x = KPARSEC*dens_H*dust_norm*dust_cs;
+//      d_step = tau_r/tau_x;
+//      if (tau_x == 0) d_step = VERY_LARGE_NUMBER;
+//      if (d_step < step) {step = d_step; scatter = -1; dust_scatter = 1; }
+//      else  dust_scatter = 0;
+      
       // take the step
       r[0] += D[0]*step;
       r[1] += D[1]*step;
@@ -298,6 +304,20 @@ void Run_Monte_Carlo(char *outfile)
 	}
       }
 
+      //      if (dust_scatter)
+            //{
+	      //double z =  gsl_rng_uniform(rangen);
+	      //if (z > dust_albedo) {count_it = 0; break; }
+	      //// choose new isotropic direction
+ 	      //mu  = 1 - 2.0*gsl_rng_uniform(rangen);
+ 	      //      //phi = 2.0*PI*gsl_rng_uniform(rangen);
+ 	      //sin_theta = sqrt(1 - mu*mu);
+ 	      //D[0] = sin_theta*cos(phi);
+ 	      //D[1] = sin_theta*sin(phi);
+ 	      //D[2] = mu;
+            //}
+   }	
+ 
     // Count spectrum if needed
     double l_obs,t_obs,E_obs,m_obs,p_obs;
     if (count_it) 

### 2010-06-18 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5012 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,425 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e6;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// ISM parameters
+double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
+double n_ISM = 10.;           // Density (constant) of ISM gas (cm^-3)
+double v_ISM = 100.;           // Random (uniform) velocity of ISM
+//double ISM_doppler    =   15*1e5;              
+double ISM_doppler    =   40*1e5;              
+
+// Wind parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+double wind_doppler    =   15*1e5;              
+
+// Dust parameters
+double dust_cs     = 3.33e-24;    // dust cross-section
[…]

### 2010-06-20 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5015 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\taud}{$\tau_{\rm dust}$}
+\newcommand{\mtaud}{\tau_{\rm dust}}
 \newcommand{\maconfig}{2p$^6$3s}
@@
 \newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
+\newcommand{\feiic}{\ion{Fe}{2}$^* \; \lambda 2612$}
 \newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
@@
 
+\subsection{Dust}
+\label{sec:dust_method}
+
+\begin{itemize}
+\item Define \taud
+\item Dust scales with $n_H$
+\item No wavelength dependence
+\item Conversion to IR photons (not tracked)
+\end{itemize}
+
 \section{A Fiducial Wind Model}
@@
 
+\section{Complexity}
+
+\subsection{Anisotropic Winds}
+\label{sec:anisotropic}
+
+The fiducial model explored in the previous section assumed an
+isotropic wind with variations in velocity and density only
+along the radial dimension.  This is obviously an idealized case, but
+one that is frequently adopted in the literature
+\citep[e.g.][]{steidel+10}.   There are several reasons, however, why
+the wind might not be isotropic.  For example, the sources driving the
+wind (e.g.\ supernovae, an AGN) may be anisotropically distributed
+within the galaxy.  It is also possible that gas within the galactic
+halo preferentially suppresses the wind on one side.  [Any other
+reason?]
+
+With these considerations in mind, we reanalyzed the fiducial model
+with the 3D algorithm after setting the density to zero for $2\pi$ steradians.
+We then rotated our view of this system from $\theta = 0^\circ$ where
+we view the source directly to $\theta = 180^\circ$ where the source
+is covered by this anisotropic wind.  The resulting \ion{Mg}{2} and
+\ion{Fe}{2} profiles are compared against the fiducial model
+(isotropic wind) in Figure~\ref{fig:anisotropic}.
+
+Examining the \mgiid\ doublet first, 
+there is no attenutation of the source by the wind for $\theta =
+0^\circ$
+but one does observe significant line emission from photons scattered
+off the back side.  These, by definition, have $v \gtrsim 0 \mkms$
+relative to line-center with a modest emission at $v<0 \mkms$ related
+to turbulent motions within the wind ($b_{\rm turb} = 15 \mkms$).
+When viewed from the opposite direction ($\theta = 180^\circ$), the
+absorption lines dominate althrough there is still signficant
+line-emission at $v \approx 0 \mkms$ (at at $v < 0 \mkms$ which fills
+in the absorption) from photons that scatter through the wind.  The
+key difference from the isotropic wind is the absence of photons
+scatterd to $v > 100 \mkms$.  In this respect, the emission lines
+provide a (robust?) diagnostic for wind isotropy.  [Also note the
+greater depth of MgII 2803?]
+For $\theta = 90^\circ$, the wind covers one half of the source and
+one observes half the absorption and also emission at all velocities.
+
+The results are very similar for the \feiid\ resonance lines.  The
+\ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows clearly the
+separation in velocity for the line-emission.   [Anything else?]
+
+[Does the emission extend to +1000\kms?  Is it a good tracer of the of
+the dynamics (unlike \lya)? Good for Obs Section]
+
+\subsection{Dust}
+
+Essentially all astrophysical environments that contain both cool gas
+and metals also show signatures of dust depletion and extinction.  This includes the
+ISM of star-forming and \ion{H}{1}-selected galaxies
+\citep[e.g.][]{ss96,pw01,pcd+07}, strong \ion{Mg}{2} metal-line
+absorption systems \citep{york,menard}, and the galactic winds traced
+by low-ion transitions \citep{cb58,naI}.  Although the galactic winds
+traced by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
+demonstrated to contain dust, it is reasonable to include at this
+stage.
+
+Dust will affect our results for the line profiles in two respects.
+First, it serves as an opacity for the photons
+emitted by the source.  This will suppress the flux at all
+wavelengths by $\approx \exp{-\mtaud}$, but because we are normalizing the profiles to the
+continuum this is essentially ignored.  Second, photons that are
+scattered by the wind (once ore multiple times) into our view will travel a greater
+distance and suffer from greater extinction.  A photon that is
+trapped for many scatterings may have a high probability of absorbed
+by dust and leave the system as IR photons.  Indeed, this process is
+often the explanation given for the weak (or absent) \lya\ emission
+associated with star-forming galaxies \citep[e.g.][]{lya}.
+Section~\ref{sec:dust_method} describes our treatment of dust; we only
+remind the reader here that the opacity is assumed to scale with the
+gas density and that we normalized the extinction by the total optical
+depth $\tau_d$ that a photon would experience if it travelled from the
+source to infinity without scattering.
+
+In Figure~\ref{fig:dust} we show the \ion{Mg}{2} and \ion{Fe}{2}
+profiles of the fiducial model ($\mtaud = 0$) against a series of
+models with $\mtaud > 0$.  For the \ion{Mg}{2} transitions, the
+dominant effect is the suppression of the line emission at $v \ge 0
+\mkms$.  These `red' photons, of course, were scattered off the
+backside of the wind and must travel a longer path than the other
+photons.  This differnetial reddening with increasing wavelength (and
+velocity relative to line-center) is a natural consequence of dust
+extinction and is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
+emission profile.   Only for $\tau_d = 10$ does one observe a
+significant difference in the absorption profiles, specifically a
+greater degree of apparent absorption at $v \approx -150 \mkms$.  At
+such high levels of extinction, even the photons off the frontside of the
+wind are preferentially absorbed relative to the unabsorbed photons.
+Such a high dust opacity, however, implies the source itself is
+extinguished by 15\,magnitudes and it would never be observed. 
+Even $\mtaud = 3$ would be much larger than typically inferred for the
+star-forming galaxies that drive outflows \citep[e.g.][]{dust}.
+
+To summarize,  dust is likely to have only a modest effect on
+\ion{Mg}{2} and \ion{Fe}{2} transitions which have themselves only
+modest optical depths.  [How big would $\tau_{\rm MgII}$ have to get?]
+The dominant effect is a reduction in the flux of the emission lines
+with greater extinction at higher velocities relative to line-center.
+In these respects, this roughly mimics the behavior of the anistropic
+wind described in Section~\ref{sec:anisotropic}. [Is there a
+distinguishing factor, e.g. flux of 2612/2600??]
+
+[Do again for fiducial but with a higher $n_H$?  Do for other density
+laws, but maybe not show]
+
 \section{Discussion}
@@
 
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_asymm_spec.ps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+case (black lines) compared against an anisotropic wind blowing into
+only $2\pi$ steradians viewed from $\theta = 0^\circ$ (source
+uncovered) to $\theta = 180^\circ$ (source covered).  One detects
+significant emission for all orientations of this wind with the
+emission shifting from positive to negative velocities as $\theta$
+increases.  
+}
+\label{fig:anisotropic}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_dust_spec.ps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+model (black) against a series of models that include the effects of
+dust extinction.  The primary difference is the suppression of line
+emission relative to the continuum (again, normalized to unit value).
+A more subtle but important effect is that the redder photons in the
+emission lines (corresponding to higher velocity relative to
+line-center) suffer greater extinction.  This is most evident in the
+\feiic\ emission line and is due to the fact that these photons must
+travel further by scattering off the backside of the wind.  Note that
+the absorption lines are nearly unmodified until $\mtaud = 10$, a
+level of extinction that would preclude observing the source
+altogether.
+}
+\label{fig:dust}
+\end{figure}
+
 \end{document}

### 2010-06-20 Winds/Simple/spectrum.cc

@@ -39,6 +39,7 @@ void SPECTRUM::Init(double *t, double *l, int nmu, int nphi)
   // allocate
   click  = new double[n_elements];
   count  = new double[n_elements];
+  scatt_count  = new double[n_elements];
 
   // clear 
   Wipe();
@@ -102,6 +103,23 @@ void SPECTRUM::Count(double t, double l, double mu, double phi, double E)
   click[index]  += 1;
 }
 
+void SPECTRUM::Scatter(double t, double l, double mu, double phi, double E)
+{
+
+  // locate bin number in all dimensions
+  int t_bin = time_grid.Locate(t);
+  int l_bin = lambda_grid.Locate(l);
+  int m_bin = mu_grid.Locate(mu);
+  int p_bin = phi_grid.Locate(phi);
+
+  // if off the grids, just return without counting
+  if ((t_bin < 0)||(l_bin < 0)||(m_bin < 0)||(p_bin < 0)) return;
+  
+  // add to counters
+  int index      = Index(t_bin,l_bin,m_bin,p_bin);
+  scatt_count[index]  += E;
+}
+
 
 //***************************************************************
 //--------------------------------------------------------------
@@ -127,8 +145,8 @@ void SPECTRUM::Print_Spectrum()
 	  if (n_times > 1) fprintf(out,"%15.5e ",time_grid.Center(i));
 	  if (n_mu > 1) fprintf(out,"%15.5e ",mu_grid.Center(m));
 	  if (n_phi > 1) fprintf(out,"%15.5e ",phi_grid.Center(p));
-	  fprintf(out,"%15.5e %15.5e %15.5e\n",
-	    lambda_grid.Center(j),count[id],click[id]);
+	  fprintf(out,"%15.5e %15.5e %15.5e %15.5e\n",
+		  lambda_grid.Center(j),count[id],scatt_count[id],click[id]);
 	}
   
   fclose(out);

### 2010-06-20 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc

@@ -151,8 +151,8 @@ double Get_Density(double *x, double r)
 void Run_Monte_Carlo(char *outfile)
 {
   // local variables
-  int i,j, l, ind, scatter, dust_scatter, count_it;
-  double x, lam_loc, xloc,lam;
+  int i,j, l, ind, scatter, dust_scatter, count_it, flg_scatter;
+  double x, lam_loc, xloc,lam,lam_emit;
   double r[3], D[3];
   double mu,phi,sin_theta;
   double tau_r, tau_x, step, r_sq;
@@ -191,6 +191,8 @@ void Run_Monte_Carlo(char *outfile)
     Emit(r,D,r_emit);
     // initial wavelength
     lam = l_start + (l_stop-l_start)*gsl_rng_uniform(rangen);
+    lam_emit = lam;
+    flg_scatter = 0;
 
     // propogate until escaped
     while (1)
@@ -240,11 +242,12 @@ void Run_Monte_Carlo(char *outfile)
       r_sq = r[0]*r[0] + r[1]*r[1] + r[2]*r[2];
       if (r_sq > r_outer*r_outer) {count_it = 1; break;}
       // see if we've gone under inner boundary
-      if (r_sq < r_emit*r_emit) {count_it = 0; break; }
+      // if (r_sq < r_emit*r_emit) {count_it = 0; break; }
 
       // if we line scattered, do it
       if (scatter >= 0)
       {
+	flg_scatter = 1;
 	xloc = (lam_loc/lines.lambda(scatter) - 1)*C_LIGHT/v_doppler;
 
 	// Get three velocity components of scatterer
@@ -336,6 +339,17 @@ void Run_Monte_Carlo(char *outfile)
       p_obs = atan2(D[0],D[1]);
       if (p_obs < 0) p_obs += 2*PI;
       spectrum.Count(t_obs,l_obs,m_obs,p_obs,E_obs);
+    }
+
+    // Count un-absorbed photons
+    if (flg_scatter == 0) 
+      {
+      l_obs = lam_emit;
+      E_obs = E_p;
+      m_obs = D[2];
+      p_obs = atan2(D[0],D[1]);
+      if (p_obs < 0) p_obs += 2*PI;
+      spectrum.Scatter(t_obs,l_obs,m_obs,p_obs,E_obs);
     }
   }
   

### 2010-06-20 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
@@ -147,8 +147,8 @@ double Get_Density(double *x, double r)
 void Run_Monte_Carlo(char *outfile)
 {
   // local variables
-  int i, l, ind, scatter, dust_scatter, count_it;
-  double x, lam_loc, xloc,lam;
+  int i, l, ind, scatter, dust_scatter, count_it, flg_scatter;
+  double x, lam_loc, xloc,lam, lam_emit;
   double r[3], D[3];
   double mu,phi,sin_theta;
   double tau_r, tau_x, step, r_sq;
@@ -187,6 +187,8 @@ void Run_Monte_Carlo(char *outfile)
     Emit(r,D,r_emit);
     // initial wavelength
     lam = l_start + (l_stop-l_start)*gsl_rng_uniform(rangen);
+    lam_emit = lam;
+    flg_scatter = 0;
 
     // propogate until escaped
     while (1)
@@ -236,11 +238,12 @@ void Run_Monte_Carlo(char *outfile)
       r_sq = r[0]*r[0] + r[1]*r[1] + r[2]*r[2];
       if (r_sq > r_outer*r_outer) {count_it = 1; break;}
       // see if we've gone under inner boundary
-      if (r_sq < r_emit*r_emit) {count_it = 0; break; }
+      // if (r_sq < r_emit*r_emit) {count_it = 0; break; }
 
       // if we line scattered, do it
       if (scatter >= 0)
       {
+	flg_scatter = 1;
 	xloc = (lam_loc/lambda_0[scatter] - 1)*C_LIGHT/v_doppler;
 
 	// Get three velocity components of scatterer
@@ -314,6 +317,17 @@ void Run_Monte_Carlo(char *outfile)
       p_obs = atan2(D[0],D[1]);
       if (p_obs < 0) p_obs += 2*PI;
       spectrum.Count(t_obs,l_obs,m_obs,p_obs,E_obs);
+    }
+
+    // Count un-absorbed photons
+    if (flg_scatter == 0) 
+      {
+      l_obs = lam_emit;
+      E_obs = E_p;
+      m_obs = D[2];
[…]

### 2010-06-22 Winds/papers/Theory/First/Notes/lbg_code.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5024 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,preprint]{aastex}
\usepackage{natbib,amsmath}

\special{papersize=8.5in,11in}
\begin{document}

\newcommand{\taud}{$\tau_{\rm dust}$}
\newcommand{\mtaud}{\tau_{\rm dust}}
\newcommand{\maconfig}{2p$^6$3s}
\newcommand{\mbconfig}{2p$^6$3p}
\newcommand{\aconfig}{a~$^6$D$^0$}
\newcommand{\zconfig}{z~$^6$D$^0$}
\newcommand{\mvr}{v_{\rm r}}
\newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
\newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
\newcommand{\mgiia}{\ion{Mg}{2}~$\lambda 2796$}
\newcommand{\mgiib}{\ion{Mg}{2}~$\lambda 2803$}
\newcommand{\feiia}{\ion{Fe}{2}~$\lambda 2586$}
\newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
\newcommand{\feiic}{\ion{Fe}{2}$^* \; \lambda 2612$}
\newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
\newcommand{\nmg}{$n_{\rm Mg^+}$}
\newcommand{\mnmg}{n_{\rm Mg^+}}
\newcommand{\nfe}{$n_{\rm Fe^+}$}
\newcommand{\mnfe}{n_{\rm Fe^+}}
\def\hub{h_{72}^{-1}}
\def\umfp{{\hub \, \rm Mpc}}
\def\mzq{z_q}
\def\zabs{$z_{\rm abs}$}
\def\mzabs{z_{\rm abs}}
\def\intl{\int\limits}
\def\cmma{\;\;\; ,}
\def\perd{\;\;\; .}
\def\ltk{\left [ \,}
\def\ltp{\left ( \,}
\def\ltb{\left \{ \,}
\def\rtk{\, \right  ] }
\def\rtp{\, \right  ) }
\def\rtb{\, \right \} }
\def\sci#1{{\; \times \; 10^{#1}}}
\def \rAA {\rm \AA}
\def \zem {$z_{\rm em}$}
\def \mzem {z_{\rm em}}
\def\smm{\sum\limits}
\def \cmm  {cm$^{-2}$}
\def \cmmm {cm$^{-3}$}
\def \kms  {km~s$^{-1}$}
\def \mkms  {{\rm km~s^{-1}}}
\def \lyaf {Ly$\alpha$ forest}
\def \Lya  {Ly$\alpha$}
\def \lya  {Ly$\alpha$}
\def \mlya  {Ly\alpha}
\def \Lyb  {Ly$\beta$}
\def \lyb  {Ly$\beta$}
\def \lyg  {Ly$\gamma$}
\def \ly5  {Ly-5}
\def \ly6  {Ly-6}
\def \ly7  {Ly-7}
\def \nhi  {$N_{\rm HI}$}
\def \mnhi  {N_{\rm HI}}
\def \lnhi {$\log N_{HI}$}
\def \mlnhi {\log N_{HI}}
\def \etal {\textit{et al.}}
\def \lyaf {Lyman--$\alpha$ forest}
\def \mnmin {\mnhi^{\rm min}}
\def \nmin {$\mnhi^{\rm min}$}
\def \O {${\mathcal O}(N,X)$}
\newcommand{\cm}[1]{\, {\rm cm^{#1}}}
\def \snrlim {SNR$_{lim}$}

\title{Coding the LBG Wind (in 1D)}

\begin{abstract}
These notes summarize my thoughts on how to code the LBG wind
introduced by \cite{steidel+10} in 1D.   Am certain it can be done,
but I'd like a reasonably fast and somewhat malleable algorithm.
\end{abstract}

\author{
J. Xavier Prochaska
}

\section{LBG Model}

\cite{steidel+10} parameterized their wind
in terms of radius with two quantities the wind speed, $v_{\rm wind}(r)$,
and the covering fraction of the gas $f_c(r)$.  For the wind speed,
they use this functional form

\begin{equation}
v_{\rm wind}(r) = \ltp \frac{A}{1-\alpha} \rtp^{1/2} 
\ltp r_{\rm min}^{1-\alpha} - r^{1-\alpha} \rtp^{1/2}
\end{equation}
where $r_{\rm min} = 1$\,kpc, $\alpha \approx 1.3$ and $A$ is tuned to
give a speed of $\approx 750\mkms$ at $r \gg r_{\rm min}$.  They
parameterize the covering fraction as a simple power-law:

\begin{equation}
f_{\rm c}(r) =  f_{\rm c,max} r^{-\gamma}
\end{equation}
where $\gamma = 0.5$ and the maximum covering fraction $f_{\rm
  c,max}=0.6$ is assumed to occur at $r=r_{\rm min}$.

\section{General Idea}

\noindent These are the steps as I see them

\begin{enumerate}
\item Generate a photon at $r=r_{\rm min}$ with wavelength $\lambda =
  \lambda_\gamma$
\item Propogate it to the radius where its velocity $v_{\gamma} =
  c(\lambda_\gamma-\lambda_0)/\lambda_0$ matches the wind
\item Calculate $f_{\rm c}$ at that radius.
\item Determine if the photon was scattered ($P=f_{\rm c}$.  If not, it escapes.  
\item Decide whether the scattered photon has a chance to interact
  with the wind again (often it will not).
\item If it can, there should be two radii where it could.  
\item Calculate $f_{\rm c}$ at the first radius and see if it is
  scattered. If so, proceed as in the last few steps.  If not, carry
  it to the next radius and repeat.
\item Propogate the photon until is out.  
\end{enumerate}

It would be nice to allow for the possibilty of dust extinction as
well.

\section{Some Minutiae}

As I see it, the only challenging part is to determine whether a
scattered photon has a non-zero probability of interacting with the
wind again.  Here is one way of formalizing the problem (in 2D,
i.e. $x,y$ or $r,\theta$).

First, assume the photon has scattered at a position
$x_\gamma^0,y_\gamma^0$.  We will assume it scatters into a direction
$\hat \phi$.  Parameterizing its path by the variable $s$, we have:

\begin{align}
x_\gamma(s) &= x^0_\gamma + s \, \cos\phi \\
y_\gamma(s) &= y^0_\gamma + s \, \sin\phi
\end{align}
which translates into
\begin{align}
\theta_\gamma &= \tan^{-1}(y_\gamma/x_\gamma) \\
r_\gamma &= \ltk x_\gamma^2 + y_\gamma^2 \rtk^{1/2}
\end{align}

The idea, then, is to solve for the two values of $s$ where:

\begin{equation}
v_{\rm wind}(s) [\hat r(s) \times \hat \phi] = v_\gamma
\end{equation}
where the stuff in square brackets captures the direction of the
photon relative to the radial direction.

I had thought initially that this would be a simple quadratic to
solve, but the velocity expression for the wind is sufficiently
scary-looking that I doubt it.  Looks like the job for a fast root-finder.

\bibliographystyle{/u/xavier/paper/Bibli/apj}
\bibliography{/u/xavier/paper/Bibli/allrefs}

%\begin{figure}
%\epsscale{0.8}
%\plotone{Figures/fig_dust_spec.ps}
%\caption{
%altogether.
%}
%\label{fig:dust}
%\end{figure}

\end{document}

### 2010-06-24 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5025 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -7,14 +7,17 @@
 #include "locate_array.hh"
 #include "voigt.hh"
 #include "spectrum.hh"
+#include "lines.hh"
+
+LINES lines;
 
 // monte carlo parameters
 double n_photons =  2e6;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2780;     // beginning wavelength (Angstroms)
-double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_start   =  2575;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2635;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -51,14 +54,14 @@ double dust_albedo = 0.0;         // ratio of scattering to absorption
 // line parameters
 // --------------------------
  //number of lines to use
-int    n_lines      = 2; 
+//int    n_lines      = 2; 
 // line center wavelengths
-double lambda_0[]   = {2796.352, 2803.531};  
+//double lambda_0[]   = {2796.352, 2803.531};  
 // line oscillator strengths
-double f_lu[]       = {0.6123,     0.3054}; 
+//double f_lu[]       = {0.6123,     0.3054}; 
 // abundances of element of line
 double abun[]       = {3.4e-6, 3.4e-6};  // Solar metallicity and 1/10 down for dust
-double metallicity       = 0.5;                 // 1 = Solar
+double metallicity       = 0.5/2;                 // 1 = Solar (down 2 for Fe)
  // lines doppler velocity in cm/s
 
 // parameters describing voigt profile
@@ -77,6 +80,7 @@ int verbose;             // output parameter
 int main(int argc, char **argv)
 {
 
+  lines.Init("fe_uv1.lines");
 
   void Run_Monte_Carlo(char*);
 
[…]

### 2010-06-24 Winds/papers/Theory/First/Analysis/LBG/Sobolev/outflow_lbg_sobolev_mgii.cc

@@ -10,7 +10,7 @@
 
 // monte carlo parameters
 double n_photons =  2e6;    // number of photons
-double stepsize  = 0.01;   // maximum size of photon step 
+double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
 double l_start   =  2780;     // beginning wavelength (Angstroms)
@@ -20,30 +20,21 @@ double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins
 
-// ISM parameters
-double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
-double n_ISM = 1.;           // Density (constant) of ISM gas (cm^-3)
-double v_ISM = 100.;           // Random (uniform) velocity of ISM
-//double ISM_doppler    =   15*1e5;              
-double ISM_doppler    =   40*1e5;              
-
-// Wind parameters
-double r_inner   =  1.0;      // inner boundary radius, in kpc
-double r_outer   = 20.0;      // outer boundary radius, in kpc
-double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
-double n_law     =    2.;      // -1*power law exponent of density law
-double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
-double v_law     =    1.0;      // power law of velocity profile
+// LBG wind parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc [Should always be 1 !!]
+double r_outer   = 100.0;      // outer boundary radius, in kpc
+double r_emit    =  0.5;      // boundary to emit from
 double bipolar   =    0;      // degree of bipolarity
-double wind_doppler    =   15*1e5;              
 
-// Dust parameters
+double LBG_gamma = 0.5;  // Covering fraction parameter
+double LBG_fc = 0.6;          // Maximum covering fraction (for MgII 2796)
[…]

### 2010-06-25 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5027 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,456 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "lines.hh"
+
+LINES lines;
+
+// monte carlo parameters
+double n_photons =  1e6;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2575;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_law     =    1.0;      // power law of velocity profile
+double v_norm     =  1.;    // velocity at outer boundary (cm/s)
+double v_rval = r_inner;
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
[…]

### 2010-06-25 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_mgii.cc

@@ -1,0 +1,432 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e6;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_law     =    1.0;      // power law of velocity profile
+double v_norm     =  1.;    // velocity at outer boundary (cm/s)
+double v_rval = r_inner;
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
[…]

### 2010-07-01 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5030 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  2e6;    // number of photons
+double n_photons =  1e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
@@ -23,9 +23,8 @@ int    n_phi     =    1;      // number of phi bins
 // ISM parameters
 double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
 double n_ISM = 1.;           // Density (constant) of ISM gas (cm^-3)
-double v_ISM = 100.;           // Random (uniform) velocity of ISM
-//double ISM_doppler    =   15*1e5;              
 double ISM_doppler    =   40*1e5;              
+//double v_ISM = 100.;           // Random (uniform) velocity of ISM
 
 // Wind parameters
 double r_inner   =  1.0;      // inner boundary radius, in kpc
@@ -125,6 +124,7 @@ double Get_Velocity(double *x, double r)
   // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
   //  if (r < r_inner ) return 2*(gsl_rng_uniform(rangen)-0.5)*v_ISM;
   //      else return v_min * pow(r/r_inner, v_law);
+  if (r < r_inner) return 0.;
   return v_min * pow(r/r_inner, v_law);
 }
 
@@ -138,8 +138,8 @@ double Get_Density(double *x, double r)
   if (r < r_ISM) return 0;
   if (r < r_inner ) return n_ISM; 
   //  if (r > r_outer) return 0;
-  double mu = x[2]/r;
-  return n_0*pow(r_inner/r,n_law)*pow(mu*mu,2*bipolar);
+  //  double mu = x[2]/r;
+  return n_0*pow(r_inner/r,n_law); //*pow(mu*mu,2*bipolar);
 }
 
 //--------------------------------------------
@@ -148,7 +148,7 @@ double Get_Density(double *x, double r)
 double Get_Doppler(double r)
 {
   if (r == 0) return 0;
-  if (r < r_ISM) return ISM_doppler;
+  if (r < r_inner) return ISM_doppler;
   else return wind_doppler;
 }
 
@@ -252,6 +252,7 @@ void Run_Monte_Carlo(char *outfile)
       {
 	flg_scatter = 1;
[…]

### 2010-07-01 Winds/papers/Theory/First/Analysis/LBG/Covering/outflow_lbg_covering_feii.cc

@@ -12,8 +12,8 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
-double stepsize  = 0.01;   // maximum size of photon step 
+double n_photons =  2e6;    // number of photons
+double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
 double l_start   =  2575;     // photon beginning wavelength (Angstroms)
@@ -23,30 +23,21 @@ double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins
 
-// ISM parameters
-double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
-double n_ISM = 1.;           // Density (constant) of ISM gas (cm^-3)
-double v_ISM = 100.;           // Random (uniform) velocity of ISM
-//double ISM_doppler    =   15*1e5;              
-double ISM_doppler    =   40*1e5;              
-
-// Wind parameters
-double r_inner   =  1.0;      // inner boundary radius, in kpc
-double r_outer   = 20.0;      // outer boundary radius, in kpc
-double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
-double n_law     =    2.;      // -1*power law exponent of density law
-double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
-double v_law     =    1.0;      // power law of velocity profile
+// LBG wind parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc [Should always be 1 !!]
+double r_outer   = 100.0;      // outer boundary radius, in kpc
+double r_emit    =  0.5;      // boundary to emit from
 double bipolar   =    0;      // degree of bipolarity
-double wind_doppler    =   15*1e5;              
 
-// Dust parameters
+double LBG_gamma = 0.5;  // Covering fraction parameter
[…]

### 2010-07-01 Winds/papers/Theory/First/Analysis/LBG/Covering/outflow_lbg_covering_mgii.cc

@@ -7,46 +7,34 @@
 #include "locate_array.hh"
 #include "voigt.hh"
 #include "spectrum.hh"
-#include "lines.hh"
-
-LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
-double stepsize  = 0.01;   // maximum size of photon step 
+double n_photons =  2e6;    // number of photons
+double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
-double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins
 
-// ISM parameters
-double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
-double n_ISM = 1.;           // Density (constant) of ISM gas (cm^-3)
-double v_ISM = 100.;           // Random (uniform) velocity of ISM
-//double ISM_doppler    =   15*1e5;              
-double ISM_doppler    =   40*1e5;              
-
-// Wind parameters
-double r_inner   =  1.0;      // inner boundary radius, in kpc
-double r_outer   = 20.0;      // outer boundary radius, in kpc
-double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
-double n_law     =    2.;      // -1*power law exponent of density law
-double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
-double v_law     =    1.0;      // power law of velocity profile
+// LBG wind parameters
[…]

### 2010-07-01 Winds/papers/Theory/First/Analysis/LBG/Sobolev/outflow_lbg_sobolev_feii.cc

@@ -12,7 +12,7 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e6;    // number of photons
 double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
@@ -189,7 +189,7 @@ void Run_Monte_Carlo(char *outfile)
   // send the photons
   for (i=0;i<n_photons;i++)
   {
-    //    if ( (float(i)/1000 - i/1000) < 1e-5)  printf("photon %d \n",i);
+    // if ( (float(i)/1000 - i/1000) < 1e-5)  printf("photon %d \n",i);
     // Get initial positions and direction
     Emit(r,D,r_emit);
     // initial wavelength
@@ -209,7 +209,7 @@ void Run_Monte_Carlo(char *outfile)
       dens_H = Get_Density(r,rad);   // Actually normalized funny
 
       // Variable step size
-      if (rad < 1.0) step = 1e-4;  
+      if (rad < 2.0) step = 1e-4;  
       else {
 	if (rad > 10.0) step = 0.1; else step = 0.01;
       }

### 2010-07-01 Winds/papers/Theory/First/Analysis/LBG/Sobolev/outflow_lbg_sobolev_mgii.cc

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  1e6;    // number of photons
 double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
@@ -185,7 +185,7 @@ void Run_Monte_Carlo(char *outfile)
   // send the photons
   for (i=0;i<n_photons;i++)
   {
-    //    if ( (float(i)/1000 - i/1000) < 1e-5)  printf("photon %d \n",i);
+    // if ( (float(i)/1000 - i/1000) < 1e-5)  printf("photon %d \n",i);
     // Get initial positions and direction
     Emit(r,D,r_emit);
     // initial wavelength
@@ -205,7 +205,7 @@ void Run_Monte_Carlo(char *outfile)
       dens_H = Get_Density(r,rad);   // Actually normalized funny
 
       // Variable step size
-      if (rad < 1.0) step = 1e-4;  
+      if (rad < 2.0) step = 1e-4;  
       else {
 	if (rad > 10.0) step = 0.1; else step = 0.01;
       }

### 2010-07-06 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5030 ac11df5e-a788-c23b-a8e1-c758c323924d
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5031 ac11df5e-a788-c23b-a8e1-c758c323924d
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5032 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\feiic}{\ion{Fe}{2}$^* \; \lambda 2612$}
+\newcommand{\feiie}{\ion{Fe}{2}$^* \; \lambda 2626$}
 \newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
@@
 fiducial wind model at several velocities relative to the \mgiia\
-transition. At $\mvr \le -200 \mkms$, where the wind has an optical
+transition. At $v \le -200 \mkms$, where the wind has an optical
 depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
 the source contributes significantly to the observed flux.  
-At $\mvr=-100 \mkms$, however, the
+At $v=-100 \mkms$, however, the
 wind absorbs all photons from the source and the observed emission is
@@
 actually exceeds the source+wind emission at 
-$\mvr = -200\mkms$ such
+$v = -200\mkms$ such
 that the absorption profile reaches peak depth at a velocity that is
@@
 \subsection{Dust}
+\label{sec:dust}
 
@@
 
+\subsection{ISM}
+\label{sec:ISM}
+
+As designed, the fiducial mdoel does not include gas associated with
+the interstellar medium of the galaxy, i.e.\ material at $r \sim
+0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This placed the focus on
+properties of the wind.  In part, this decision was also motivated by
+the general absence of significant absorption at $v \approx 0 \mkms$
+in galaxies that exhibit outflows
+\citep[e.g.][]{wcp+09,steidel+10,rubin+10}.
+[Create an ISM grid for Dan]
+On the other hand, the stars and \ion{H}{2} regions that comprise our
+background sources are very likely embedded within and fueled by gas
+of the galactic ISM.
+
+Consider a modification to the fiducial model that adopts the same
+wind but also includes an ISM component with $<\mvr> = 0 \mkms$.  
+Specifically, the ISM component has $n_{\rm H} = 1 \cm{-3}$ for
+$r_{\rm ISM} \le r < r_{\rm inner}$, an average velocity of $\mvr = 0
+\mkms$, but a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
+Figure~\ref{fig:ISM} summarizes the properties of this model.
+[Comment?]
+
+In Figure~\ref{fig:ISM_spec} the solid curves show the \ion{Mg}{2} and
+\ion{Fe}{2} profiles for the ISM+wind (black) and fiducial (red)
+models. In comparison, the
+dotted curve shows the absorption profile for the ISM+wind in the (unphysical) case
+where no absorbed photons are re-emitted.   Focus first on the
+\ion{Mg}{2} doublet.  As expected, the dotted curve shows strong
+absorption at $v \approx 0 \mkms$ and blueward.  The full models,
+in contrast, show positive emission at $v \approx 0 \mkms$.  In
+fact, the ISM+wind model is nearly identical to the fiducial model
+with the only quantitiative difference being that the velocity centroid of
+the emission lines are shifted by $\approx +100 \mkms$.
+
+There are, however, several qualitiative differences between the
+ISM+wind and fiducial models for the \ion{Fe}{2} transitions.  First,
+the \feiia\ transition shows much stronger absorption at $v \approx 0$
+to $-100 \mkms$.  The difference from the \ion{Mg}{2} doublet is that
+this absorption is not filled in by scattered photons because the
+majority of photons absorbed at the \feiia\ are re-emitted as
+\ion{Fe}{2}~$^* \lambda\lambda 2612, 2632$ photons.  In fact, the
+\feiia\ profile with scattering nearly matches that withou re-emission
+(compare the solid and dotted lines) and this transition provides a
+very good description of the ISM+wind opacity.  The other key
+difference is the much higher strength ($3-10\times$) of emission from the
+transitions to the excited states of \aconfig.   There are two reasons
+for this higher emission: (1) the absorption is greater in the \feiid\
+resonance lines; (2) the high opacity of the ISM component leads to
+the increased conversion of resonance photons with $v \approx 0\mkms$
+into the non-resonance lines.  This is especially notable for the
+\feiib\ transition whose `partner' shows an equivalent width nearly
+$10\times$ stronger than for the fiducial model.  The relative
+strengths of the \feiib\ and \feiie\ lines therefore provide a direct
+diagnostic on the degree to which the resonance lines are trapped.
+[Comment:  this is a product of $\tau_{2600}$ and the velocity
+gradient]
+
+\subsection{The Lyman Break Galaxy Model}
+\label{sec:lbg}
+
+The Lyman break galaxies, UV color-selected galaxies at $z \sim 3$,
+are observerd to exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
+etc.\ transitions with maximum speeds of nearly 1000\kms\
+\citep[e.g.][]{lowenthal,pettini,steidel+10}.
+Recently, \cite{steidel+10} modeled the average absorption observed
+toward a set of XX LBGs and the average absorption in cool gas
+observed transverse to these galaxies.  Using our methodology, we have
+explored further the wind that they inferred from the observations.
+
+\cite{steidel+10} introduced a wind model parameterized by two
+quantities: a radial velocity low $\mvr(r)$ and the covering fraction of
+optically thick gas $f_c(r)$.  [Explain the origin of these better?]
+For the velocity law, the authors introduced the following functional
+form
+
+\begin{equation}
+\mvr = \ltp \frac{A_{\rm LBG}}{1-\alpha} \rtp^{1/2} \ltk r_{\rm
+  inner}^{1-\alpha} - r^{1-\alpha} \rtk^{1/2}
+\label{eqn:LBG_vlaw}
+\end{equation}
+with $A_{\rm LBG}$ a constant that sends the terminal speed,
+$r_{\inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
+$\alpha$ describes how steeply the velocity curve rises.  Their
+analysis of the LBG absorption profiles required
+a very steeply rising curve with $\alpha \approx 1.3$.
+The resulting curve is shown as a dotted line in the top panel of
+Figure~\ref{fig:LBG_Sobolev}.
+
+The covering fraction of the cold gas, meanwhile, was assumed to have
+the functional form
+
+\begin{equation}
+f_c(r) = f_{c,max} \ltp \frac{r}{r_{\rm inner}} \rtp^{-\gamma}
+\label{eqn:covering}
+\end{equation}
+with $\gamma \approx 0.5$ and $f_{c,max}$ the maximum covering
+fraction.  From this expression and the velocity law, one can recover
+an absorption profile $I(v) = 1 - f_c(r[v])$.  Inverting the velocity
+law, we derive
+
+\begin{equation}
+I_{\rm LBG}(v) = 1 - f_{c,max} \ltk r_{\rm inner}^{1-\alpha} - \ltp
+\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\frac{\gamma}{\alpha-1}}
+\perd
+\label{eqn:LBG_I}
+\end{equation}
+The resulting profile for $f_{c,max} = 0.6$, $\gamma=0.5$,
+$\alpha=1.3$, and $A_{\rm LBG} = $ is displayed in the lower panel of
+Figure~\ref{fig:LBG_Sobolev}.  
+In the following, we consider two methods to analyze the LBG wind.
+Both approaches assume isotropy and adopt the velocity law given by
+Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
+diffuse medium with a radial density profile.  We then apply 
+the methodology used for the other wind models.  In the other model,
+we modify our algorithms to more precisely mimic the model suggested
+by \cite{steidel+10}.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Sobolev}
+\label{sec:Sobolev}
+
+As demonstrated in Figure~\ref{fig:LBG_Sobolev}, the wind velocity for
+the LBG model rises very steeply with increasing radius before
+flattening at large radii.  Under these conditions, the Sobolev
+approximation can be applied to derive the density profile provided
+one has a description of the optical depth profile $\tau(v)$.
+For the latter, we take
+
+\begin{equation}
+\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk
+\label{eqn:tauLBG}
+\end{equation}
+and one can express the optical depth in terms of the radius using
+Equation~\ref{eqn:LBG_vlaw}.  Following \cite{sobolev60}, we have
+
+\begin{equation}
+n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa_\ell
+  \lambda_0}
+\label{eqn:Sobolev}
+\end{equation}
+with $\lambda_0$ the rest wavelength and $\kappa_\ell \equiv f\pi^2
+e^2/m_e c$.  The solid curve in the top panel of Figure~\ref{fig:LBG_Sobolev} shows the
+resultant density profile for Hydrogen.  [Probably show $n_{\rm
+  Mg^+}$]
+[This is a relatively extreme density profile.  From the inner radius
+of the wind (1\,kpc) to 2\,kpc, the density drops by over 2 orders of
+magnitude including approximately an order of magnitude over the first
+10\,pc.  Beyond 2\,kpc, the desnity drops even more rapidly, falling
+orders of magnitude from 2 to 100\,kpc.]
+It was derived by assuming
+that \mgiia\ transition has the optical depth profile given in
+Equation~\ref{eqn:tauLBG} (the black curve in the lower panel of
+Figure~\ref{fig:LBG_Sobolev})  and then scaling by $10^{5.77}$ which 
+corresponds to Mg depleted by a factor of 10 and a 1/2 solar
+metallicity.  [Give more detail?  Probably]
+We then verified that this density profile reproduced the correct
+absorption profile by discretizing the gas into a series of tiny
+`clouds' and calculating the integrated absorption profile.  This is
+overplotted as a dotted red curve on the lower which is an excellent
+match to the desired profile (black curve).
+For Fe$^+$, we take $n_{\rm Fe^+} = n_{\rm Mg^+}/2$ and the strength
+of all other transitions scale as $f\lambda$, i.e.\ the 
+\mgiib\ profile will be half as deep as that shown in
+Figure~\ref{fig:LBG_Sobolev}.
+
+We then generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
+using the 1D algorithm with no dust extinction; these are shown with
+the red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
+should focus on the \mgiia\ transition.  The dotted line in the Figure
+shows the intensity profile for the model when one ignores re-emission
+of absorbed photons.  By construction, it follows\footnote{Note that
+  one should not make this comparison for the other transitions in
+  this Sobolev model because these are scaled down by $f\lambda$ and
+  the reduced Fe$^+$ abundance.} the profile
+described in Equation~\ref{eqn:LBG_I}.   The full model, however,
+shows much weaker absorption especially at $v = 0$ to $-300 \mkms$.
+In this respect, the LBG-Sobolev model is an
+inaccurate description of the observations.  In addition, the model
+predicts significant emission in the \ion{Mg}{2} lines and several of
+the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
+has been observed for non-resonant \ion{Si}{2}
+transitions in LBGs \citep{cb58,shapley}.
+The \ion{Fe}{2} and \ion{Mg}{2} transitions
+  modeled here lie in the near-IR and have not yet been [explored].
+  [X-Shooter must help here]  On the other hand, there have been no 
+reported detections of significant line-emission related to resonance
+transitions in LBGs, only $z \le 1$ star-forming galaxies
+\citep{wcp+09,rubin09}.  We discuss these points further in the
+following section. [Do we?]
+
+[Does CIV scattered photons bugger up the P-Cygni analysis of Pettini
+et al. ?]
+
+[Does most of the scattering occur within the inner few kpc? Explore
+this with outflow.cc]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\subsubsection{Covering Fraction}
+\label{sec:Covering}
+
+In the previous sub-section, we described a Sobolev solution that
+reproduces the average absorption profile of LBGs in cool gas
+transitions.  We found that a full analysis of this wind model leads
+to absorption profiles that are qualitatively different from the ones
+observed.  This is due to the re-emission and scattering of photons
+within the wind itself.  We also noted that this model differed from
+the one proposed by S10.  Their model [argued for] discrete, optically
+thick clouds with a non-unity covering fraction (described by
+Equation~\ref{eqn:covering}).   In contrast, the Sobolev model assumes
+a diffuse medium with a declining density profile but a unit covering
+fraction.
+
+To more properly model the LBG wind described in S10, we 
+performed the following Monte Carlo calculation.  First, we propogated
+a photon from the source until its velocity relative to line-center
+resonates with the wind (it escapes if this never occurs).
+The photon then has a probability $P = f_c(r)$ of scattering.  If it
+scatters, we continue to track the photon until it comes into
+resonance again or escapes the system.  In this model, all of the
+resonance transitions are assumed to have identical optical depth in
+the absence of re-emission (the dotted line in
+Figure~\ref{fig:LBG_spec}).
+
 \section{Discussion}
@@
 \input{Tables/tab_fiducial_ew.tex}
+\input{Tables/tab_meas_models.tex}
+\input{Tables/tab_meas_plaws.tex}
 
@@
 
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_ism_diagn.ps}
+\caption{
+Density (solid; black), radial velocity (dotted; blue), and
+\mgiia\ optical depth profiles (dashed; red) for the ISM+wind
+model.  The wind is identical to the fiducial model
+(Figure~\ref{fig:fiducial_nvt}) but we also include an ISM component
+with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
+\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
+Note that the density and velocity curves have been scaled for plotting
+convenience.  
+}
+\label{fig:ISM}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_ism_spec.ps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
+model (black) compared against the fiducial wind model (red). 
+The dotted line traces the predicted absorption profile in the absence
+of any re-emission of absorbed photons.
+Regarding the \ion{Mg}{2}~doublet, the primary difference between the
+ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
+in the emission lines from $\mvr \approx 0 \mkms$ for the fiducial
+model to $\mvr \approx +100\mkms$ for the ISM+wind model. 
+[Discuss FeII]
+}
+\label{fig:ISM_spec}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_lbg_sobolev.ps}
+\caption{
+{\it Upper:} The dotted curve shows the velocity law for the LBG model
+of \cite{steidel+10}.  Note how rapidly the velocity rises from $r =
+1$ to 2\,kpc.  The solid curve shows the Sobolev solution required to
+match the average absorption profile of LBG galaxies (lower panel).
+The density drops off as $(r-1)^{-0.6}$ 
+{\it Lower:} Absorption profiles for the LBG model as defined by
+\cite{steidel+10} (black solid curve) and for our Sobolev approximation of
+the model (red dotted curve).  
+}
+\label{fig:LBG_Sobolev}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_lbg_spec.ps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+}
+\label{fig:LBG_spec}
+\end{figure}
+
 \end{document}

### 2010-07-10 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5033 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
   emission fills in absorption at $v \approx 0$, significantly
-  complicating the absorption-line analysis. 
+  complicating the absorption-line analysis, especially of an ISM
+  component. 
 \end{itemize}
@@
 In this paper, we will focus on two sets of radiative transitions
-associated with the Fe$^+$ and Mg$^+$ ions, a choice motivated by 
-our own observations \citep{rubin10b}.  Although this is a limited
-set, the two ions and their transitions have 
-characteristics that resemble the properties for the majority of low-ions 
-observed in cool-gas outflows. [wording still stinks] Therefore, many
-of our results may be generalized to other studies.
+associated with the Fe$^+$ and Mg$^+$ ions.
+Although a limited
+set, the two ions and their transitions are characteristic
+of the majority of low-ions 
+observed in cool-gas outflows. Therefore, many
+of our results can be generalized to studies that focus on other atoms
+and ions of cool gas.
 
@@
 mechanics, the 2p$^6$3p level is said to be split by spin-orbit
-coupling which produces the line doublet.  These are the only
+coupling; this produces the observed line doublet.  These are the only
 \ion{Mg}{2} electric-dipole transitions 
-with wavelengths near 2800\AA. Also, the transtion connecting
+with wavelengths near 2800\AA\ and the transtion connecting
 the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
@@
 \maconfig~$\to$~\mbconfig\
-is followed nearly 100$\%$ of the time by a spontaneous decay to the
-ground state and our treatment will ignore any other possibilities
-(e.g.\ absorption of a second photon).
+is followed essentially 100$\%$ of the time by a spontaneous decay to the
+ground state. Our treatment will ignore any other possibilities
+(e.g.\ absorption by a second photon when at the \mbconfig\ level).
 
@@
 studied in the ISM and IGM.  These doublets differ only in
-the transiton wavelengths and the energy of the doublet separation. 
+their wavelengths and the energy of the doublet separation. 
 For \ion{H}{1} \lya, the
 separation is sufficiently small ($\Delta v = c \Delta E / E \approx
-1.3 \mkms$) that most radiative transfer treatments actually ignore the fact that
-there are two transitions.   This is generally a justifiable
-assumption because 
+1.3 \mkms$) that most radiative transfer treatments actually ignore that
+there are two transitions.   This is generally justifiable
+because 
 most astrophysical processes have turbulent motions that
@@
 must be treated separately.  Regarding analysis of outflows, the line
-separation plays an important role when the outflow speed $\mvr
-\gtrsim \Delta v$.
+separation plays an important role when the outflow speed matches or
+exceeds $\Delta v$.
 
@@
 incomplete list.  
-One reason for the complexity of iron is
+One reason for iron's complexity is
 that the majority of its configurations exhibit fine-structure splitting.
@@
 configuration and the levels associated with the \zconfig\
-configuration.  This set of transitions are named the
-UV1 mutliplet with wavelengths near 2600\AA.
-There are two resonance-line transitions (defined to originate in the
-true ground-state) associated with this multiplet, \feiid,
+configuration.  This set of transitions (named the
+UV1 mutliplet) have wavelengths near 2600\AA.
+There are two resonance-line transitions\footnote{We adopt the
+  convention that a resonance line is connected to the ground-state.} 
+associated with this multiplet (\feiid)
 corresponding to $\Delta J = 0, -1$.  The solid (green) downward
@@
 the upper energy levels of the resonance lines.  These transitons can
-occur following the absorption of a single photon by the ion in its
+occur following the absorption of a single photon by Fe$^+$ in its
 ground-state.
@@
 excited state and one from the excited state to one of the \zconfig\
-levels with $J \le 5/2$.  The excitation of the Fe$^+$ ion by the
+levels with $J \le 5/2$.  Such excitation by the
 absorption of UV photons is termed indirect UV pumping
@@
 detectable) quantities of \ion{Fe}{1} which has not yet been observed
-\citep[see also][]{pcb06}.  The strongest arguement for neglecting
-collisions is the general absence of {\it absorption} from the
-fine-structure levels of the \aconfig\ configuration.  [Does Kate see
-blue-shifted FeII* in absorption?]  This provides an empirical
-demonstration that collsioinal excitation is insignificant, and by
-inference one may neglect collisional de-excitation.  Meanwhile, the
-critical density and excitation energies for \ion{Mg}{2} are $n_c =
-??, T_{\rm ex} \approx 50,000$\,K.
+\citep[see also][]{pcb06}.  Furthermore, observations rarely show
+{\it absorption} from the
+fine-structure levels of the \aconfig\ configuration and  none that is
+significantly blue-shifted \citep{rubin+10}.
+Empirically, collsioinal excitation is insignificant and, by
+inference, one may neglect collisional de-excitation.  
+For Mg$^+$, $n_c = ??$ and $T_{\rm ex} \approx 50,000$\,K  
+implying negligible collsiional excitation for the cool gas.
 
@@
 stars and \ion{H}{2} regions that is then modulated by dust and gas
-within the galaxy's ISM.  In terms of the spectral regions studied
+within the galaxy's ISM.  For the spectral regions studied
 here, most stars show a featureless continuum with a few spectral
@@
 should be aware that they can complicate the observed spectrum,
-independent of a galactic outflow.
+independent of a galactic outflow, especially at $v \approx 0 \mkms$.
 In the following, we will simply assume a flat continuum 
@@
 part, to yield a \ion{Mg}{2} absorption profile 
-simlar to that observed toward $z<1$, star-forming galaxies
+similar to that observed toward $z<1$, star-forming galaxies
 \citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
-favor this fiducial model over any other wind scenario nor are its
-properties any more physically motivated. 
-Its primary purpose is to establish a baseline for exploration.
+favor this fiducial model over any other wind scenario nor do its
+properties have spcial physical motivation.
+The primary purpose of the fiducial model is to establish a baseline
+for discussion.
 
@@
 \end{equation}
-(mass-flux conserving) and a velocity law
+(mass-flux conserving) and a velocity
 
 \begin{equation}
-v_r (r) = v_0 r
+\vec v = v_r (r) \hat r = v_0 r \hat r
+\label{eqn:vel}
 \end{equation}
@@
 the center of the wind 
-is a homogenous source of continuum photons with size $r_{\rm source}$.  Lastly,
+is a homogenous source of continuum photons with a size $r_{\rm source}$.  Lastly,
 we convert the hydrogen density $n_{\rm H}$ to the number density of
@@
 and \nfe=\nmg/2.   
-These normalizations give a wind with a peak optical depth $\tau
->> 1$ to \mgiia\ that becomes optically thin over a velocity range
-spanning $v_r \approx 100 - 1000 \, \mkms$.  
 All of the parameters are summarized in Table~\ref{tab:fiducial}.
@@
 shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
-This profile is what determines the observed absorption/emission lines
+This curve determines the resultant absorption/emission lines
 for the wind.  
@@
 between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
-$\tau_{2796}$ onto radius using the radial velocity profile and 
-checked that this profile is in good agreement with
-the Sobolev approximation.  
+$\tau_{2796}$ onto radius using the velocity expression
+(Equation~\ref{eqn:vel}). 
 The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
@@
 The adopted Doppler parameter
-(here $b_{\rm turb} = 15 \mkms$) also has a modest impact on the results,
-specially at large optical depths.  A larger/smaller
-$b$-value would imply ... [FILL IN]
-In turn, this would affect the resulting emission profiles.
-
-Because the results are dictated by the $\tau_{2796}$ profile and the
-Doppler parameter, the actual dimensions and density of the wind are
-essentially unimportant provided they scale together to give the same
+(here $b_{\rm turb} = 15 \mkms$) also has only a modest impact on the results.
+A larger/smaller $b$-value would imply ... [FILL IN]
+
+Because the results are dictated by the $\tau_{2796}$ profile in
+velocity space, the actual dimensions and density of the wind are
+essentially unimportant provided they scale together to give nearly the same
 $\tau_{2796}$ profile.  Therefore, one may consider our choices for
 $r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
-Nevertheless, we attempted to adopt values for this fiducial model
-that some astrophysical motivation.
+Nevertheless, we adopted values for this fiducial model with
+some astrophysical motivation (e.g. values that correspond to
+galactic dimensions).
 
@@
 that this observer would record with the ``unattenuated'' source flux
-normalized to unit value.   The \ion{Mg}{2} profiles
-show the canonical `P-Cygni profile' that characterize a continuum
+normalized to unit value.   The \ion{Mg}{2} doublet
+shows the canonical `P-Cygni profile' that characterize a continuum
 source embedded within an outflow.  Strong absorption is evident at
@@
 (Table~\ref{tab:fiducial_EW}), i.e.\ every photon
-absorbed still escapes the system, primarily at lower
-energies.  The wind simply shuffles photons in frequency space.
+absorbed eventually escapes the system, generally at lower
+energies.  The wind simply shuffles the photons in frequency space.
 
@@
 {\it entirely} covers the source; the apparent partial covering must
-be related to a different effect.
+be due to a different effect.
 Figure~\ref{fig:noemiss}, which compares the true
@@
 depth and falsely conclude partial covering.  We will find that this
-behaviour is a generic results for models with a high degree of
-isotropy.
+behaviour is a generic result of wind models, even for cases that are
+not fully isotropic.
 [Dan's analytic calculation here? or Appendix?]
@@
 One also notes that the emission profiles of the \mgiid\ doublet
-are very similar and have comparable equivalent widths.  In fact the
-flux of the \mgiib\ transition even exceeds that for \mgiia.  The
-emission profiles are similar because the absorption is saturated.
+are very similar with comparable equivalent widths.  In fact the
+flux of the \mgiib\ transition even exceeds that for \mgiia, the ratio
+is far below the $2:1 f\lambda$ ratio that one might have expected. The
+emission profiles are so similar simply because the absorption is
+highly saturated.
 Furthermore, the flux from \mgiib\ is greater than that for
@@
 \mgiia\ emission profile.  The relative strengths of the emission
-lines, therefore, is sensitive to both the optical depth and velocity
+lines, therefore, is sensitive to both the opacity and velocity
 extent of the wind.
@@
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \mkms$ producing a P-Cygni profile.  Splitting
-the profile at $v = -50 \mkms$, we measure an equivalent width
+emission at $v > 0 \, \mkms$ producing a P-Cygni profile.  Splitting
+the profile at $v = -50 \, \mkms$, we measure an equivalent width
 $W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
@@
 likely be more trapped and more would come out as 2626.  Also a
-v=0km/s component might make quite a difference.]
+v=0km/s component might make quite a difference. It does!]
 In contrast, the \feiia\ resonance line shows much weaker emission and
@@
 even though the line has a $2 \times$ lower $f\lambda$ value.
-The difference comes the extra downward transition from the
+This difference is due to the extra downward transition from the
 \zconfig$_{7/2}$ level and (more importantly) that the Einstein A
-coefficients  of the non-resonant lines match and even exceed that for
+coefficients of the non-resonant lines are comparable to and even
+exceed the Einstein A coefficient of
 the resonant line.  In the case of \feiib, the
@@
 resonance line.  Therefore, the majority of photons absorbed at
-$\lambda 2600$ are re-emitted with the same energy and only scatter 
+$\lambda 2600$ are re-emitted with nearly the same energy and only scatter 
 in frequency space around the line.  For \feiia, 
 the majority of photons absorbed are re-emitted 
-as longer wavelength \ion{Fe}{2}~$\lambda 2612$ or $\lambda 2632$
+as longer wavelength \ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda 2632$
 photons.  
 The total equivalent width, however, of the lines connected to the
-\zconfig$_{7/2}$ upper level does vainsh (i.e.\ photons are conserved
+\zconfig$_{7/2}$ upper level must vainsh (i.e.\ photons are conserved
 in this fiducial wind).
 
-[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$?]
+[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$? It
+can]
 
@@
 fiducial wind model at several velocities relative to the \mgiia\
-transition. At $v \le -200 \mkms$, where the wind has an optical
+transition. At $v -200 \, \mkms$, where the wind has an optical
 depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
 the source contributes significantly to the observed flux.  
-At $v=-100 \mkms$, however, the
+At $v=-100 \, \mkms$, however, the
 wind absorbs all photons from the source and the observed emission is
@@
 actually exceeds the source+wind emission at 
-$v = -200\mkms$ such
+$v = -200 \, \mkms$ such
 that the absorption profile reaches peak depth at a velocity that is
@@
 the peak in optical depth.  The net result of the scattered photons is
-a weaker \ion{Mg}{2} profile that is offset fromt he true optical
-depth profile.  Clearly, this will complicate efforts to estimate the
+a weaker \ion{Mg}{2} profile that is offset from the true optical
+depth profile.  Clearly, this complicates estimates of the
 speed, covering fraction, and total column density of the wind.  At $v
@@
 [Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
-and 1-20; ignoring the source]
+and 1-20; ignoring the source] {\bf [Do this!]}
 
@@
 with $A_{\rm LBG}$ a constant that sends the terminal speed,
-$r_{\inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
+$r_{inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
 $\alpha$ describes how steeply the velocity curve rises.  Their
@@
 
+The results of the full calculation are
+shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
+are very similar to the Sobolev calculation; scattered photons fill-in
+the absorption profiles at $v \approx 0 \mkms$ and yield significant
+emission lines at $v \gtrsim 0 \mkms$ in the resonance lines and at
+all velocities for the \ion{Fe}{2}$^*$ transitions.  For \feiia,
+the majority of absorbed photons have been converted to its
+fine-structure counterparts lending to very weak emission at this
+transition. In fact the absorption profile very nearly matches the
+model without re-emission indicating that this transition well
+reproduces the opacity of the wind.  [Could SiII or OI provide a
+similar angle?]
+
+[Discuss 'exact' match of Sobolev + Covering at MgII 2796]
+[Does the similarity of the two require that the density of clouds
+fall off like the Sobolev solution?]
+
+\section{Observables}
+
+Although the focus of this paper is to explore the absorption/emission
+profiles for idealized wind models, we ultimately intend to compare 
+profiles like these against observations to constrain characteristics
+of the wind (e.g.\ raidal extent, energetics).  In this section we
+consider a few observables and their dependence on the wind properties.
+
+\subsection{Absorption profiles}
+
+ \begin{enumerate}
+   \item Peak optical depth
+     \begin{itemize}
+       \item Not a robust measure of $\tau_{wind}$
+       \item Not even a good relative predictor for $\tau$
+       \item Not a robust predictor of $f_c$
+     \end{itemize}
+   \item Kinematics
+     \begin{itemize}
+       \item Nearly robust for $v<v_{min}$
+       \item But what sets $v_{min}$?
+       \item Generally get the full extent of the wind speed
+     \end{itemize}
+   \item EW
+     \begin{itemize}
+       \item Primarily set by $v_{min}(\tau \sim 1)$
+       \item $f\lambda$ matters, but so do emission channels
+     \end{itemize}
+   \item Fine-structure
+     \begin{itemize}
+       \item Distance to the source
+     \end{itemize}
+ \end{enumerate}
+
+\subsection{Emission profiles}
+
+ \begin{enumerate}
+   \item Resonant lines
+     \begin{itemize}
+       \item Kinematics of backside
+       \item Flux + relative
+    \end{itemize}
+   \item Fine-structure
+     \begin{itemize}
+       \item Flux $\propto \tau_{wind}$ + relative
+       \item Kinematics (anisotropy)
+    \end{itemize}
+ \end{enumerate}
+
 \section{Discussion}

### 2010-07-12 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5035 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\begin{itemize}
-\item Usage of cool gas outflows to probe galactic-scale winds in
-  star-forming galaxies is now a well-established observational
-  technique
-\item Simple anlaysis focusing on the central wavelength and EW of the
-  lines
-\item \lya, MgII, NaI and (now) FeII* show emission
-\item Despite the wealth of observational diagnostics, little effor
-  hast been taken to constrain the wind properties
-\item These are some first steps by considering idealized wind
-  profiles.  Algorithms can be extended to any wind output
-\end{itemize}
+Nearly all gaseous objects in astrophysics that emit light are also
+observed to drive gas away.  [word] This includes the jets of protostars, the
+strong stellar winds of massive O and B stars, the gentle Solar wind
+of our Sun, the associated absorption of bright quasars, and the
+spectacular jets of radio-loud AGN.   These gaseous outflows moderate
+the accretion of fresh material onto the object, inject energy and
+momentum into gas on large scales, and ...
+[Last line]
+
+Star-burst galaxies, whose light is dominated by \ion{H}{2} regions
+and massive stars, are also observed to drive gaseous outflows.  The
+flows are generally expected (and sometimes observed) to have multiple
+phases, with a hot and diffuse phase traced by X-ray emission
+\citep[e.g.][]{strickland,martin+k} and a cool, denser phase traced by
+H$\alpha$ emission \citep[e.g.][]{NGC891,M87}.
+
+Beyond the local universe, galactic outflows are predominatly
+revealted by UV and optical absorption lines, e.g.\ \ion{Na}{1},
+\ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
+as a backlight, one almost universally observes predominantly
+blue-shifted material indicating a galactic-scale flow of gas toward
+Earth and away from the galaxy.  These transitions are sensitive to
+the cool (\ion{Mg}{2}; $T \sim 10^4$K) and warm (\ion{C}{4}; $T \sim
+10^5$K) phases of the flow.  The incidence of cool gas outflows is
+nearly universal in star-forming galaxies;  this includes systems at $z \sim 0$
+which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
+\citep{rupke,martin,student}, $z \sim 1$ star-forming galaxies traced by
+\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin+10}, and
+$z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
+\ion{C}{2}, and \ion{O}{1} transitions \citep{lowenthal,steidel94}.
+
+Although the obsevation of metal-line absorption is a well established
+means of identifying outflows at all epochs, little effort has been
+made to compare these observations against (even idealized) wind
+models.  The focus to date has been to gelan the limited information
+affored by direct analysis of the absorption lines.  The data do yield
+robust measurements of the speed of the gas yet poorly constrain the
+optical depth, covering fraction, density, temperature, and distance
+of the gas from the emitting regions.  Constraints related to the
+mass, energetics, and momentum of the flow suffer from
+orders of magnitude uncertainty.  Both the origin and impact of the
+winds, therefore, remain open points of debate.
+
+Recent studes of $z \sim 1$ star-forming galaixes have revealed that
+the cool gas frequently exhibits significant \ion{Mg}{2} emission in
+addition to the ubiquitous blue-shifted absorption
+\citep{wcp+09,rubin+10b}.  \cite{rubin+10a} have also detected line
+emission from non-resonance \ion{Fe}{2}~$^*$ transitions and spatially
+extended \ion{Mg}{2} emission which they interpret as originating from
+photons scattered off a galactic-scale wind.  They estimate that the
+wind extends to at least 5\,kpc from the galaxy.  Line emission is
+also observed for $z \sim 3$ LBGs via the resonant \lya\ transition
+and fine-strcuture \ion{Si}{2}$^*$ transitions \citep{cb58,shapley}.
+\cite{rubin+10a} emphasize that a comprehensive analysis of these data
+(e.g.\ via integral-field-unit observations) could yield unique
+diagnostics on the morphology and density of the outflow, eventually
+yielding tigheter constrains on the energetics of the flow.  
+The crucial piece missing from this path is a radiative transfer
+treatment that properly ...
+
+In this paper, we take the first steps toward modeling the absorption
+and emission properties of cool gas outflows.  Using Monte Carlo
+radiative transfer technqiues, we study the nature of \ion{Mg}{2} and
+\ion{Fe}{2} absorption and emission for winds with a range of
+properties.  Although the winds are idealized, the results frequently
+contradict our initial intuition and caution one [word] on the
+challenges of converting the observables to (even crude) physical
+constraints.  [Add another line or two]
+
+[Outline of paper]
+
+[Point out IR emission from winds locally implies dust]
 

### 2010-07-13 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5038 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
   component. 
+\item The relative strengths of the emission
+lines, therefore, is sensitive to both the opacity and velocity
+extent of the wind.
 \end{itemize}
@@
 
+This section describes the methodology [employed] to generate
+emission/absorption profiles from simple wind models.
+
 \subsection{The Radiative Transitions}
 
-[Table of $f,\lambda,A,\gamma$]
-
-In this paper, we will focus on two sets of radiative transitions
-associated with the Fe$^+$ and Mg$^+$ ions.
-Although a limited
+In this paper, we focus on two sets of radiative transitions
+arising from Fe$^+$ and Mg$^+$ ions
+(Table~\ref{tab:atomic},Figure~\ref{fig:energy}).
+Although this is a necessarily limited
 set, the two ions and their transitions are characteristic
@@
 observed in cool-gas outflows. Therefore, many
-of our results can be generalized to studies that focus on other atoms
-and ions of cool gas.
+of the results may be generalized to observational studies that
+consider other atoms and ions of cool gas.
 
 The Mg$^+$ ion, with a single 3s electron in the ground-state,
-exhibits an alkali doublet of transitions similar to the
-\lya\ transitions of neutral hydrogen.  In Figure~\ref{fig:energy}
-we present the energy level diagram for this 
+exhibits an alkali doublet of transitions at $\lambda \approx
+2800$\AA\ similar to the
+\lya\ transitions of neutral hydrogen.  Figure~\ref{fig:energy}
+presents the energy level diagram for this 
 \mgiid\ doublet.  In non-relativistic quantum
-mechanics, the 2p$^6$3p level is said to be split by spin-orbit
-coupling; this produces the observed line doublet.  These are the only
+mechanics, the 2p$^6$3p energy level is said to be split by spin-orbit
+coupling which yields the observed line doublet.  These are the only
 \ion{Mg}{2} electric-dipole transitions 
@@
 \maconfig~$\to$~\mbconfig\
-is followed essentially 100$\%$ of the time by a spontaneous decay to the
+is followed essentially 100$\%$ of the time by a spontaneous decay
+($t_{\rm decay} \approx 4\sci{-9}$s to the
 ground state. Our treatment will ignore any other possibilities
-(e.g.\ absorption by a second photon when at the \mbconfig\ level).
+(e.g.\ absorption by a second photon when the electron is at the \mbconfig\ level).
 
@@
 \lya, the \naid\ doublet, and many other doublets commonly
-studied in the ISM and IGM.  These doublets differ only in
-their wavelengths and the energy of the doublet separation. 
+studied in the interstellar medium (ISM) of distant galaxies.  The
+doublets differ only in 
+their rest wavelengths and the energy of the doublet separation. 
 For \ion{H}{1} \lya, the
 separation is sufficiently small ($\Delta v = c \Delta E / E \approx
-1.3 \mkms$) that most radiative transfer treatments actually ignore that
-there are two transitions.   This is generally justifiable
-because 
+1.3 \, \mkms$) that most radiative transfer treatments actually ignore that
+there are two transitions.   This is generally justifiable for \lya\ because 
 most astrophysical processes have turbulent motions that
-significantly exceed this velocity separation and effectively mix the
+significantly exceed its velocity separation and effectively mix the
 two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
 \ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
-commonly studied the separations are large and the lines
-must be treated separately.  Regarding analysis of outflows, the line
+commonly observed, the separation is large and the transitions
+must be treated separately.  Regarding the analysis of outflows, the line
 separation plays an important role when the outflow speed matches or
-exceeds $\Delta v$.
-
-Iron exhibits the most complex set of energy levels of the elements
+exceeds $\Delta v$.  [Explain?]
+
+Iron exhibits the most complex set for energy levels of the elements
 frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
@@
 excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
-$T_{\rm ex} \approx 500-1500$\,K.  These levels are usually labelled by the total angular momentum
-$J$, with the ground-state having $J=9/2$ (Figure~\ref{fig:energy}).  
+$T_{\rm ex} \approx 500-1500$\,K, labelled by the total angular momentum
+$J$. The ground-state has $J=9/2$ (Figure~\ref{fig:energy}).  
 Transitions between these fine-structure levels are 
@@
 
-In this paper, we will focus on transitions between the ground-state
-configuration and the levels associated with the \zconfig\
+In this paper, we examine transitions between the ground-state
+configuration and the energy levels of the \zconfig\
 configuration.  This set of transitions (named the
@@
 There are two resonance-line transitions\footnote{We adopt the
-  convention that a resonance line is connected to the ground-state.} 
+  standard convention that a ``resonance line'' is an electric-dipole
+  transition connected to the ground-state.} 
 associated with this multiplet (\feiid)
@@
 transitions that connect to higher energy levels of the \zconfig\
-configuration.  Radiatively, these can only occur after the absorption
+configuration.  Ignoring collisions and recombinations, these
+transitions may only can only occur after the absorption
 of two photons: one to raise the electron from the ground-state to an
 excited state and one from the excited state to one of the \zconfig\
-levels with $J \le 5/2$.  Such excitation by the
-absorption of UV photons is termed indirect UV pumping
+levels with $J \le 5/2$.  The excitation of these levels by
+the absorption of UV photons is termed indirect UV pumping
 \citep[e.g][]{sv02,pcb06} and requires the ion to lie
 near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
-following, we will assume that this does not occur and that only the 
-true ground-state is populated by electrons.
+following, we will assume that this does not occur.
 
@@
 density $n_c$ is very large.  For the \aconfig$_{9/2} \to
-$\aconfig$_{7/2}$ transition, the critical density $n_c \approx XX
-\cm{-3}$.  At these densities, one would predict significant (and
-detectable) quantities of \ion{Fe}{1} which has not yet been observed
+$\aconfig$_{7/2}$ transition, the critical density $n_e^C \approx 4
+\sci{5} \cm{-3}$.  At these densities, one would predict  
+detectable quantities of \ion{Fe}{1} which has not yet been observed
+in galactic-scale outflows
 \citep[see also][]{pcb06}.  Furthermore, observations rarely show
 {\it absorption} from the
-fine-structure levels of the \aconfig\ configuration and  none that is
-significantly blue-shifted \citep{rubin+10}.
-Empirically, collsioinal excitation is insignificant and, by
+fine-structure levels of the \aconfig\ configuration and that material
+is not significantly blue-shifted \citep{rubin+10}.
+Empirically, collisional excitation is insignificant and, by
 inference, one may neglect collisional de-excitation.  
-For Mg$^+$, $n_c = ??$ and $T_{\rm ex} \approx 50,000$\,K  
-implying negligible collsiional excitation for the cool gas.
+For Mg$^+$,$T_{\rm ex} \approx 50,000$\,K  
+$n_e^C \approx 3 \sci{14} \cm{-3}$  [Maybe critical density is
+not so interesting here...]
+implying negligible collisional excitation for the cool gas.  
+This implies the gas has zero opacity to the non-resonant lines.
 
@@
 
-Nearly all of the absorption studies on cool-gas outflows 
+Nearly all the absorption studies of cool-gas outflows 
 have focused on intensely, star-forming galaxies.  The
@@
 stars and \ion{H}{2} regions that is then modulated by dust and gas
-within the galaxy's ISM.  For the spectral regions studied
-here, most stars show a featureless continuum with a few spectral
-types showing significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
+within the ISM.  For the spectral regions studied
+here, most stars show a featureless continuum but a few spectral
+types do show significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
 [Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
@@
 should be aware that they can complicate the observed spectrum,
-independent of a galactic outflow, especially at $v \approx 0 \mkms$.
+independent of the galactic outflow, especially at velocities $v \approx 0 \mkms$.
 In the following, we will simply assume a flat continuum 
 normalized to unit value.  The size of the emitting
-region $r_{\rm source}$, however, is a variable parameter.
+region $r_{\rm source}$ is a free parameter, although we tend to
+restrict its value to be smaller than the minimum radial extent of any
+gaseous component.
 
@@
 
-\begin{itemize}
-\item Define \taud
-\item Dust scales with $n_H$
-\item No wavelength dependence
-\item Conversion to IR photons (not tracked)
-\end{itemize}
-
-\section{A Fiducial Wind Model}
+For the majority of models studied in this paper, we assume no dust.
+This is an invalid assumption, espeically for material associated with
+the ISM of the galaxy.  Because absorption line analysis is performed
+on normalized spectra, the effects of dust are largely minimized.  For
+scattered and resonantly trapped photons, however, the effects of dust
+extinction can be significant.  Indeed, dust is frequently invoked to
+explain the weak (or absent) \lya\ emission from star-forming galaxies
+\citep[e.g.][]{shapley03}.  Although the transitions studied here have
+significantly lower opacity than \lya, dust may play an important role
+in the predicted profiles.
+
+In a few models, we include the absorption by dust under the following
+assumptions:
+(i) the dust opacity scales with the density of the gas (i.e.\ we
+adopt a fixed dust-to-gas ratio);
+(ii) the opacity is independent of wavelength, a reasonable
+approximation given the small spectral range analyzed;
+(iii) the photons absorbed by dust are re-emitted at IR wavelengths
+and `lost' from the system.  The dust absorption is normalized by \taud, 
+the integrated opacity of dust from the center of the system to
+infinity.  The ISM of a star-forming galaxy may be expected to exhibit
+\taud\ of a few \citep[e.g.][]{steidel98}.
+
+\section{The Fiducial Wind Model}
 \label{sec:fiducial}
 
-In this section, we explore a simple yet illustrative wind model for
+In this section, we study a simple yet illustrative wind model for
 a galactic-scale outflow.  The properties of this wind were tuned, in
@@
 favor this fiducial model over any other wind scenario nor do its
-properties have spcial physical motivation.
-The primary purpose of the fiducial model is to establish a baseline
+properties have special physical motivation.
+Its primary purpose is to establish a baseline
 for discussion.
 
-The fiducial wind follows a density law
+The fiducial wind follows a (mass-fluxing conserving) density law,
 
 \begin{equation}
-n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2}
+n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2} \;\;\; , 
+\label{eqn:density}
 \end{equation}
-(mass-flux conserving) and a velocity
+and a velocity
 
 \begin{equation}
-\vec v = v_r (r) \hat r = v_0 r \hat r
+\vec v = v_r (r) \hat r = v_0 r \hat r \;\;\; , 
 \label{eqn:vel}
 \end{equation}
-which corresponds to a purely radial flow.  Turbulent motions are
+i.e., a purely radial flow.  Turbulent motions are
 characterized by a Doppler parameter $b_{\rm turb}$.  
 The wind is isotropic, dust-free, and extends from an inner wind
-radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  At
-the center of the wind 
-is a homogenous source of continuum photons with a size $r_{\rm source}$.  Lastly,
-we convert the hydrogen density $n_{\rm H}$ to the number density of
+radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
+We scale the hydrogen density $n_{\rm H}$ to the number densities of
 Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
@@
 1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
-and \nfe=\nmg/2.   
-All of the parameters are summarized in Table~\ref{tab:fiducial}.
+and \nfe=\nmg/2. At the center of the wind is a homogenous source of
+continuum photons with a size $r_{\rm source}$. These parameters are
+summarized in Table~\ref{tab:fiducial}.
 
@@
 shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
-This curve determines the resultant absorption/emission lines
-for the wind.  
 Although plotted against radius, we first calculated $\tau_{2796}$ 
@@
 between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
-$\tau_{2796}$ onto radius using the velocity expression
+$\tau_{2796}$ onto radius using the velocity law
 (Equation~\ref{eqn:vel}). 
 The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
-at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
+with a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
 r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
-is scaled down by the ratio of $f\lambda$ but otherwise identical.  Similarly,
+is scaled down by the $f\lambda$ ratio but otherwise identical.  Similarly,
 the optical depth profiles for the \feiid\ transitions are
@@
 The adopted Doppler parameter
-(here $b_{\rm turb} = 15 \mkms$) also has only a modest impact on the results.
-A larger/smaller $b$-value would imply ... [FILL IN]
+($b_{\rm turb} = 15 \mkms$) has only a modest impact on the results.
+A larger/smaller $b$-value has minimal effect on the absorption
+profiles and only tends to modify the widths and for resonant
+transitions shifts the centroids of their emission lines.
 
@@
 essentially unimportant provided they scale together to give nearly the same
-$\tau_{2796}$ profile.  Therefore, one may consider our choices for
+$\tau_{2796}$ velocity profile.  Therefore, one may consider the choices for
 $r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
 Nevertheless, we adopted values for this fiducial model with
-some astrophysical motivation (e.g. values that correspond to
-galactic dimensions).
+some astrophysical motivation,  e.g. values that correspond to
+galactic dimensions and a normalization that gives $\tau_{2796}^{\rm
+  max} \sim 10$.
 
@@
 `observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
-complex.  Figure~\ref{fig:fiducial_1d} presents the spectrum
-that this observer would record with the ``unattenuated'' source flux
+complex.  Figure~\ref{fig:fiducial_1d} presents the 1D spectrum
+that this observer would record, with the ``unattenuated'' flux
 normalized to unit value.   The \ion{Mg}{2} doublet
-shows the canonical `P-Cygni profile' that characterize a continuum
+shows the canonical `P-Cygni profile' that characterizes a continuum
 source embedded within an outflow.  Strong absorption is evident at
-$v < -50 \mkms$ in both transitions and each shows emission at
+$v < -50 \mkms$ in both transitions (equivalent widths $W_{2796} =
+2.96$\AA\ and $W_{2803} = 1.29$\AA) and each shows emission at
 positive velocities.  For this isotropic and dust-free model, the
@@
 
-Focusing on the \ion{Mg}{2} absorption, one notes the profiles have
-positive intensity yet similar depth even though their $f\lambda$
+Focusing on the \ion{Mg}{2} absorption, one notes the profiles lie
+well above zero intensity and have similar depth even though their $f\lambda$
 values differ by a factor of two.  In standard absorption line
@@
 \citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
-{\it entirely} covers the source; the apparent partial covering must
+{\it entirely covers the source}; the apparent partial covering must
 be due to a different effect.
-Figure~\ref{fig:noemiss}, which compares the true
-absorption profiles against the case where absorbed photons are not
-re-emitted, further illustrates this issue.   As expected from the
-$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}, the no-emission
-case predicts a strong \mgiid\ doublet that absorbs all photons at
-$v \approx -100 \mkms$, i.e.\ $I_{2796} = \exp(-\tau_{2796}) \approx 0$.
-The actual profile, meanwhile, has been `filled in' at $v \approx -100
+Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
+absorption profiles from Figure~\ref{fig:fiducial_1d} against an
+artificial model where no absorbed photons are 
+re-emitted.   As expected from the
+$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), the
+`no-emission' model
+produces a strong \mgiid\ doublet that absorbs all photons at
+$v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
+  max}_{2796}) \approx 0$.
+The fiducial model, meanwhile, has been `filled in' at $v \approx -100
 \mkms$ by photons scattered and re-emitted by the wind (see below).  An
 absorption-line analysis that ignores these effects
-\citep[e.g.][]{sato} would systematically underestimate the true optical
-depth and falsely conclude partial covering.  We will find that this
-behaviour is a generic result of wind models, even for cases that are
+\citep[e.g.][]{sato} would (i) systematically underestimate the true optical
+depth and (ii) falsely conclude that the wind partially covers the
+source.  We will find that this
+behaviour is a generic result of the wind models considered, even for cases that are
 not fully isotropic.
@@
 
-One also notes that the emission profiles of the \mgiid\ doublet
-are very similar with comparable equivalent widths.  In fact the
-flux of the \mgiib\ transition even exceeds that for \mgiia, the ratio
-is far below the $2:1 f\lambda$ ratio that one might have expected. The
-emission profiles are so similar simply because the absorption is
-highly saturated.
-Furthermore, the flux from \mgiib\ is greater than that for
-\mgiia\ because the wind speed exceeds the velocity separation
-of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$, such
-that the \mgiib\ absorption profile partially absorbs the red wing of the
+Turning to the emission profiles of the \mgiid\ doublet, one notes
+that they are also and have comparable equivalent widths.  The
+flux of the \mgiib\ transition even exceeds that for \mgiia\ giving a
+line ratio that is far below the $2:1$ ratio that one may have naively
+expected. 
+[Does recombination predict 2:1??]
+The emission profiles are very similar because the gas is optically
+thick for a significant portion of the profile. 
+The flux from \mgiib\ actually exceeds the
+\mgiia\ emission because the wind speed is greater than the velocity separation
+of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
+Therefore,
+the \mgiib\ absorption profile partially absorbs the red wing of the
 \mgiia\ emission profile.  The relative strengths of the emission
 lines, therefore, is sensitive to both the opacity and velocity
-extent of the wind.
+extent of the wind.  We also emphasize that departures from a 2:1
+ratio indicate that processes other than simple recombination are
+active.  [CHECK THIS]
 
@@
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \, \mkms$ producing a P-Cygni profile.  Splitting
+emission at $v > 0 \, \mkms$ producing the characteristic P-Cygni profile of
+an outflow.  Splitting
 the profile at $v = -50 \, \mkms$, we measure an equivalent width
@@
 equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
-[Point out that if $\tau_{2600}$ were higher, than the photons would
-likely be more trapped and more would come out as 2626.  Also a
-v=0km/s component might make quite a difference. It does!]
 In contrast, the \feiia\ resonance line shows much weaker emission and
@@
 even though the line has a $2 \times$ lower $f\lambda$ value.
-This difference is due to the extra downward transition from the
-\zconfig$_{7/2}$ level and (more importantly) that the Einstein A
+The difference is entirely due to the much lower emission equivalent
+width for \feiia\ relative to \feiib.  The \feiia\ emission is reduced
+by two factors:
+(i) there is an additional downward transition from the
+\zconfig$_{7/2}$ level and 
+(ii) more importantly, the Einstein A
 coefficients of the non-resonant lines are comparable to and even
 exceed the Einstein A coefficient of
-the resonant line.  In the case of \feiib, the
-\ion{Fe}{2}~2626 transition 
+the resonant transition.  In contrast, 
+the \ion{Fe}{2}~2626 transition (associated with \feiib)
 has an approximately  $4\times$ smaller coefficient than the
 resonance line.  Therefore, the majority of photons absorbed at
-$\lambda 2600$ are re-emitted with nearly the same energy and only scatter 
-in frequency space around the line.  For \feiia, 
-the majority of photons absorbed are re-emitted 
-as longer wavelength \ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda 2632$
-photons.  
+$\lambda 2600$ are re-emitted as \feiib\ photons whereas 
+the majority of photons absorbed as \feiia\ are re-emitted 
+at longer wavelengths (\ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda
+2632$).
 The total equivalent width, however, of the lines connected to the
-\zconfig$_{7/2}$ upper level must vainsh (i.e.\ photons are conserved
-in this fiducial wind).
-
-[Does the FeII 2600 P-Cygni go away if we increase $\tau_{2600}$? It
-can]
-
-Our 3D Monte Carlo algorithm tracks the spatial emissivity of the source+wind
-complex as a function of frequency.  From this output, we
-constructed surface-brightness maps producing a
-dataset analagous to intergral-field-unit (IFU) observations.  In
-Figure~\ref{fig:fiducial_ifu_mgii}, we present the output for our
-fiducial wind model at several velocities relative to the \mgiia\
-transition. At $v -200 \, \mkms$, where the wind has an optical
+\zconfig$_{7/2}$ upper level must still vanish (hotons are conserved
+in this fiducial wind model).
+Indeed, if were increase $\tau_{2600}$ and especially if we include
+gas with $\mvr \approx 0 \mkms$ then the emission at \feiib\ is
+significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
+
+The preceding discussion emphasize the filling-in of absorption at $v
+\lesssim -50 \, \mkms$ and the generation of emission lines at $v \approx
+0 \, \mkms$ by photons scattered in the wind.  To study the spatial
+extent of this emission, we perfomed 3D calculations with the fiducial
+model.  The outpus is a set of surface-brightness maps in a series of
+frequency channels, giving a
+dataset analagous to integral-field-unit (IFU) observations.  In
+Figure~\ref{fig:fiducial_ifu_mgii}, we present the output 
+at several velocities relative to the \mgiia\
+transition. At $v = -200 \, \mkms$, where the wind has an optical
 depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
@@
 that the absorption profile reaches peak depth at a velocity that is
-negatively offset from
-the peak in optical depth.  The net result of the scattered photons is
+negatively offset from $\tau_{2796}^{\rm max}$.
+The net result of the scattered photons is
 a weaker \ion{Mg}{2} profile that is offset from the true optical
-depth profile.  Clearly, this complicates estimates of the
+depth profile.  Clearly, this complicates estimates for the
 speed, covering fraction, and total column density of the wind.  At $v
-= 0 \, \mkms$, the wind and source have comparable total flux and the
-latter dominates at higher velocities.  
-At $v_{\rm r} \ge 0
-\mkms$,  both the source and wind contribute to the observed emission.
-
-[Spatial cut? Yes]
+= 0 \, \mkms$, the wind and source have comparable total flux with the
+latter dominating at higher velocities.
 
@@
 wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
-[Show a cut and comment on the fraction of light in 1-3\,kpc, 1-10,
-and 1-20; ignoring the source] {\bf [Do this!]}
-
-\section{Complexity}
+
+We rexpress these azimuthally symmetric surface-brightness maps in
+Figure~\ref{fig:fidicual_cuts} where the emission has been collapsed
+along one spatial axis.  For the fiducial model, the majority of
+\ion{Mg}{2} emission occurs within the inner few kpc, e.g.\ $50-60\%$ integrating
+over $r = \pm 2.5$\,kpc for $v=-100$ to $+100 \, \mkms$.  The fraction
+is even more centrally concentrated for the \ion{Fe}{2} transitions.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Variations to the Fiducial Model}
+
+In this section, we investigate a series of more complex scenarios
+through modifications to the fiducial model.  These include relaxing
+the assumption of isotropy, introducing dust, and adding an ISM
+component within $r_{\rm inner}$.
 
@@
 
-The fiducial model explored in the previous section assumed an
-isotropic wind with variations in velocity and density only
-along the radial dimension.  This is obviously an idealized case, but
-one that is frequently adopted in the literature
+The fiducial model assumes an
+isotropic wind with only radial variations in velocity and density. 
+Angular isotropy is obviously an idealized case, but
+one that is frequently assumed in studies of galactic-scale outflows
 \citep[e.g.][]{steidel+10}.   There are several reasons, however, why
-the wind might not be isotropic.  For example, the sources driving the
-wind (e.g.\ supernovae, an AGN) may be anisotropically distributed
-within the galaxy.  It is also possible that gas within the galactic
-halo preferentially suppresses the wind on one side.  [Any other
-reason?]
+the wind may not be isotropic.  Firstly, galaxies are not spherically
+symmetric;  the sources driving the
+wind (e.g.\ supernovae, AGN) are very likely to be anisotropically distributed
+within the galaxy.  Secondly, the galaxy may be surrounded by a
+anisotropic gaseous halo that could preferentially [constrain] the
+wind.
 
@@
 we view the source directly to $\theta = 180^\circ$ where the source
-is covered by this anisotropic wind.  The resulting \ion{Mg}{2} and
+is covered by the anisotropic wind.  The resulting \ion{Mg}{2} and
 \ion{Fe}{2} profiles are compared against the fiducial model
@@
 
-Examining the \mgiid\ doublet first, 
+Examining the \mgiid\ doublet, 
 there is no attenutation of the source by the wind for $\theta =
@@
 but one does observe significant line emission from photons scattered
-off the back side.  These, by definition, have $v \gtrsim 0 \mkms$
-relative to line-center with a modest emission at $v<0 \mkms$ related
-to turbulent motions within the wind ($b_{\rm turb} = 15 \mkms$).
+off the back side.  These photons, by definition, have $v \gtrsim 0 \mkms$
+relative to line-center (a few have $v<0 \mkms$ because
+of turbulent motions in the wind). 
 When viewed from the opposite direction ($\theta = 180^\circ$), the
-absorption lines dominate althrough there is still signficant
-line-emission at $v \approx 0 \mkms$ (at at $v < 0 \mkms$ which fills
-in the absorption) from photons that scatter through the wind.  The
+absorption lines dominate but there is still significant
+line-emission -- at $v \approx 0 \mkms$ and at $v < 0 \mkms$ which fills
+in the absorption -- from photons that scatter through the wind.  The
 key difference from the isotropic wind is the absence of photons
-scatterd to $v > 100 \mkms$.  In this respect, the emission lines
-provide a (robust?) diagnostic for wind isotropy.  [Also note the
-greater depth of MgII 2803?]
+scatterd to $v > 100 \mkms$ (also note the greater strength of the
+\mgiib\ profile at $v \approx -100 \, \mkms$). The asymmetry in emission lines
+may therefore provide a robust diagnostic of wind isotropy.
 For $\theta = 90^\circ$, the wind covers one half of the source and
@@
 The results are very similar for the \feiid\ resonance lines.  The
-\ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows clearly the
+\ion{Fe}{2}$^* \; \lambda 2612$ line shows clearly the
 separation in velocity for the line-emission.   [Anything else?]
 
-[Does the emission extend to +1000\kms?  Is it a good tracer of the of
-the dynamics (unlike \lya)? Good for Obs Section]
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection{Dust}
@@
 by low-ion transitions \citep{cb58,naI}.  Although the galactic winds
-traced by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
-demonstrated to contain dust, it is reasonable to include at this
-stage.
-
-Dust will affect our results for the line profiles in two respects.
+traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
+demonstrated to contain dust, it is reasonable to consider its
+effects.
+
+Dust modifies the observed flux in two manners. 
 First, it serves as an opacity for the photons
-emitted by the source.  This will suppress the flux at all
-wavelengths by $\approx \exp{-\mtaud}$, but because we are normalizing the profiles to the
-continuum this is essentially ignored.  Second, photons that are
-scattered by the wind (once ore multiple times) into our view will travel a greater
+emitted by the source.  This suppresses the flux at all
+wavelengths by $\approx \exp(-\mtaud)$, but because we normalize the profiles 
+this effect is essentially ignored.  Second, photons that are
+scattered by the wind (once or multiple times) into our view will travel a greater
 distance and suffer from greater extinction.  A photon that is
-trapped for many scatterings may have a high probability of absorbed
-by dust and leave the system as IR photons.  Indeed, this process is
+trapped for many scatterings may have a high probability of being absorbed
+by dust and then exit as an IR photon.  This process is
 often the explanation given for the weak (or absent) \lya\ emission
@@
 remind the reader here that the opacity is assumed to scale with the
-gas density and that we normalized the extinction by the total optical
-depth $\tau_d$ that a photon would experience if it travelled from the
+gas density and that we normalize the extinction by the total optical
+depth \taud\ that a photon would experience if it travelled from the
 source to infinity without scattering.
 
-In Figure~\ref{fig:dust} we show the \ion{Mg}{2} and \ion{Fe}{2}
+In Figure~\ref{fig:dust}, we show the \ion{Mg}{2} and \ion{Fe}{2}
 profiles of the fiducial model ($\mtaud = 0$) against a series of
 models with $\mtaud > 0$.  For the \ion{Mg}{2} transitions, the
-dominant effect is the suppression of the line emission at $v \ge 0
-\mkms$.  These `red' photons, of course, were scattered off the
-backside of the wind and must travel a longer path than the other
+dominant effect is the suppression of line emission at $v \ge 0
+\mkms$.  These `red' photons were scattered off the
+backside of the wind and must travel a longer path than other
 photons.  This differnetial reddening with increasing wavelength (and
@@
 extinction and is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
-emission profile.   Only for $\tau_d = 10$ does one observe a
-significant difference in the absorption profiles, specifically a
-greater degree of apparent absorption at $v \approx -150 \mkms$.  At
-such high levels of extinction, even the photons off the frontside of the
-wind are preferentially absorbed relative to the unabsorbed photons.
-Such a high dust opacity, however, implies the source itself is
-extinguished by 15\,magnitudes and it would never be observed. 
-Even $\mtaud = 3$ would be much larger than typically inferred for the
+emission profile.   In terms of the absorption, the profiles are
+nearly identical for $\mtaud \le 3$; one requires a very high
+extinction to see even a modest effect at $v \approx -100 \, \mkms$.
+
+We conclude that dust is a modest factor for this fiducial model and,
+by inference, for models with moderate peak optical depth and
+significant velocity gradients with radius (i.e.\ scenarios where the
+photons scatter one to a few times before exiting).
+At $\mtaud = 10$, however, the source itself is
+extinguished by 15\,magnitudes and would never be observed. 
+Even $\mtaud = 3$ is larger than typically inferred for the
 star-forming galaxies that drive outflows \citep[e.g.][]{dust}.
-
-To summarize,  dust is likely to have only a modest effect on
-\ion{Mg}{2} and \ion{Fe}{2} transitions which have themselves only
-modest optical depths.  [How big would $\tau_{\rm MgII}$ have to get?]
 The dominant effect is a reduction in the flux of the emission lines
@@
 
-[Do again for fiducial but with a higher $n_H$?  Do for other density
-laws, but maybe not show]
+[Do for other density laws, but maybe not show]
 
@@
 
-As designed, the fiducial mdoel does not include gas associated with
+The fiducial mdoel does not include gas associated with
 the interstellar medium of the galaxy, i.e.\ material at $r \sim
-0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This placed the focus on
-properties of the wind.  In part, this decision was also motivated by
+0$\,kpc with $v_{\rm r} \approx 0 \, \mkms$.  We chose this to focus on
+properties of the wind.  [word]  The decision was also motivated by
 the general absence of significant absorption at $v \approx 0 \mkms$
@@
 \citep[e.g.][]{wcp+09,steidel+10,rubin+10}.
-[Create an ISM grid for Dan]
 On the other hand, the stars and \ion{H}{2} regions that comprise our
@@
 of the galactic ISM.  
-
-Consider a modification to the fiducial model that adopts the same
-wind but also includes an ISM component with $<\mvr> = 0 \mkms$.  
+Consider, then, a modification to the fiducial model that has the
+identical wind but also includes an ISM component. 
 Specifically, the ISM component has $n_{\rm H} = 1 \cm{-3}$ for
-$r_{\rm ISM} \le r < r_{\rm inner}$, an average velocity of $\mvr = 0
-\mkms$, but a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-Figure~\ref{fig:ISM} summarizes the properties of this model.
-[Comment?]
-
-In Figure~\ref{fig:ISM_spec} the solid curves show the \ion{Mg}{2} and
+$r_{\rm ISM} \le r < r_{\rm inner}$ with $r_{\rm ISM} = 0.5$\,kpc, 
+an average velocity of $\mvr = 0 \mkms$, and a larger turbulent velocity $b_{\rm ISM} = 40 \mkms$.
+Figure~\ref{fig:ISM} summarizes the model.
+The resultant optical depth profile $\tau_{2796}$ is identical to the
+fiducial model for $r > 2$\,kpc but has higher opacity at $r=1-2$\,kpc
+and a substantial component at $r = 0.5-1$\,kpc.
+
+In Figure~\ref{fig:ISM_spec}, the solid curves show the \ion{Mg}{2} and
 \ion{Fe}{2} profiles for the ISM+wind (black) and fiducial (red)
@@
 dotted curve shows the absorption profile for the ISM+wind in the (unphysical) case
-where no absorbed photons are re-emitted.   Focus first on the
+where none of the absorbed photons are re-emitted.   Focus first on the
 \ion{Mg}{2} doublet.  As expected, the dotted curve shows strong
 absorption at $v \approx 0 \mkms$ and blueward.  The full models,
-in contrast, show positive emission at $v \approx 0 \mkms$.  In
-fact, the ISM+wind model is nearly identical to the fiducial model
-with the only quantitiative difference being that the velocity centroid of
-the emission lines are shifted by $\approx +100 \mkms$.
-
-There are, however, several qualitiative differences between the
-ISM+wind and fiducial models for the \ion{Fe}{2} transitions.  First,
+in contrast, show non-zero flux at these velocities and even a
+normalized flux exceeding unity at $v \approx 0 \mkms$.  In
+fact, the ISM+wind model is nearly identical to the fiducial model;
+the only quantitiative difference is that the velocity centroid of
+the emission lines are shifted redward by $\approx +100 \, \mkms$.
+
+There are, however, several qualitiative differences 
+for the \ion{Fe}{2} transitions between the ISM+wind and fiducial
+models.
+First,
 the \feiia\ transition shows much stronger absorption at $v \approx 0$
-to $-100 \mkms$.  The difference from the \ion{Mg}{2} doublet is that
-this absorption is not filled in by scattered photons because the
-majority of photons absorbed at the \feiia\ are re-emitted as
+to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
+the profile is not filled in by scattered photons. Instead, 
+the majority of \feiia\ photons absorbed are re-emitted as
 \ion{Fe}{2}~$^* \lambda\lambda 2612, 2632$ photons.  In fact, the
-\feiia\ profile with scattering nearly matches that withou re-emission
-(compare the solid and dotted lines) and this transition provides a
-very good description of the ISM+wind opacity.  The other key
-difference is the much higher strength ($3-10\times$) of emission from the
+\feiia\ profile with scattering fully included nearly matches the profile without re-emission
+(compare the solid and dotted lines); this transition provides a
+very good description of the ISM+wind opacity profile.  The other key
+difference is the much higher strength ($3-10\times$) of emission from
 transitions to the excited states of \aconfig.   There are two reasons
-for this higher emission: (1) the absorption is greater in the \feiid\
+for the higher emission: (1) the absorption is greater in the \feiid\
 resonance lines; (2) the high opacity of the ISM component leads to
@@
 
+[3D discussion]
+
+[Fix the bug in the FeII* emission]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Alternate Wind Models}
+
+\subsection{Power-Law Models}
+\label{sec:power}
+
+The models investigated in the previous two sections
+assumed power-law descriptions for both the density and velocity
+expressions of the wind (Equations~\ref{eqn:density},\ref{eqn:vel}).
+The power-law exponents were arbitrarily chosen, with minimal physical
+motivation.  In this sub-section, we explore the results for a series
+of other power-law expressions.
+
+\subsection{Radiation Pressure}
+
 \subsection{The Lyman Break Galaxy Model}
@@
 The Lyman break galaxies, UV color-selected galaxies at $z \sim 3$,
-are observerd to exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
-etc.\ transitions with maximum speeds of nearly 1000\kms\
+exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
+etc.\ transitions with speeds up to 1000\kms\
 \citep[e.g.][]{lowenthal,pettini,steidel+10}.
-Recently, \cite{steidel+10} modeled the average absorption observed
-toward a set of XX LBGs and the average absorption in cool gas
-observed transverse to these galaxies.  Using our methodology, we have
-explored further the wind that they inferred from the observations.
-
-\cite{steidel+10} introduced a wind model parameterized by two
-quantities: a radial velocity low $\mvr(r)$ and the covering fraction of
-optically thick gas $f_c(r)$.  [Explain the origin of these better?]
-For the velocity law, the authors introduced the following functional
+Researchers have since invoked these winds to explain enrichment of
+the intergalactic medium \citep[e.g.][]{aguirre,evan}, the origin of the
+damped \lya\ systems \citep{nelson,joop98}, and XXX.  Although the
+presence of these outflows were established over a decade ago
+\citep{lowenthal,pettini98}, the processes driving the wind remain
+unidentified as do [precise] estimates of the mass/energetics of the
+outflow.
+
+Recently, \cite[][; hereafter S10]{steidel+10} introduced a model to
+explain jointly the average absorption they observed
+toward a set of XXX LBGs and the average absorption in cool gas
+observed transverse to these galaxies.  
+Their wind model is defined by two
+expressions: a radial velocity law $\mvr(r)$ and the covering fraction of
+optically thick gas $f_c(r)$.  For the latter, S10 envision an
+ensemble of small, optically thick clouds $(\tau \gg 1)$ that only
+partially cover the galaxy.
+For the velocity law, they adopted the following functional
 form
@@
 \end{equation}
-with $A_{\rm LBG}$ a constant that sends the terminal speed,
-$r_{inner}$ is the inner radius of the wind (taken to be 1\,kpc) and
+with $A_{\rm LBG}$ a constant that sets the terminal speed,
+$r_{inner}$ is the inner radius of the wind (taken to be 1\,kpc), and
 $\alpha$ describes how steeply the velocity curve rises.  Their
-analysis of the LBG absorption profiles required
+analysis of the LBG absorption profiles implied
 a very steeply rising curve with $\alpha \approx 1.3$.
-The resulting curve is shown as a dotted line in the top panel of
+This velocity expression is shown as a dotted line in the top panel of
 Figure~\ref{fig:LBG_Sobolev}.
 
-The covering fraction of the cold gas, meanwhile, was assumed to have
+The covering fraction of optically thick cold gas, meanwhile, was assumed to have
 the functional form
@@
 \begin{equation}
-f_c(r) = f_{c,max} \ltp \frac{r}{r_{\rm inner}} \rtp^{-\gamma}
+f_c(r) = f_{c,max} \ltp \frac{r}{r_{\rm inner}} \rtp^{-\gamma} \cmma
 \label{eqn:covering}
@@
 fraction.  From this expression and the velocity law, one can recover
-an absorption profile $I(v) = 1 - f_c(r[v])$.  Inverting the velocity
-law, we derive
+an absorption profile $I_{\rm LBG}(v) = 1 - f_c(r[v])$, written
+explicitly as
 
@@
 I_{\rm LBG}(v) = 1 - f_{c,max} \ltk r_{\rm inner}^{1-\alpha} - \ltp
-\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\frac{\gamma}{\alpha-1}}
+\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\gamma}/(\alpha-1)}
 \perd
@@
 The resulting profile for $f_{c,max} = 0.6$, $\gamma=0.5$,
-$\alpha=1.3$, and $A_{\rm LBG} = $ is displayed in the lower panel of
+$\alpha=1.3$, and $A_{\rm LBG} = -192,000 \, \rm km^2 s^{-2} kpc^{-2}$ 
+is displayed in the lower panel of
 Figure~\ref{fig:LBG_Sobolev}.
+
 In the following, we consider two methods to analyze the LBG wind.
@@
 Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
-diffuse medium with a radial density profile.  We then apply 
+diffuse medium with unit convering fraction and a radial density
+profile determined from the Sobolev approximation.  We then apply 
 the methodology used for the other wind models.  In the other model,
-we modify our algorithms to more precisely mimic the model suggested
+we modify our algorithms to more precisely mimic the concept of an
+ensemble of optically thick clouds with a partial covering fraction.
 by \cite{steidel+10}.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sobolev}
+\subsubsection{Sobolev approximation}
 \label{sec:Sobolev}
@@
 flattening at large radii.  Under these conditions, the Sobolev
-approximation can be applied to derive the density profile provided
-one has a description of the optical depth profile $\tau(v)$.
-For the latter, we take
+approximation relates the optical depth of an expanding medium to the
+density and velocity gradient of the gas.  In our case, we 
+generate the optical depth prpofile from Equation~\ref{eqn:LBG_I},
 
 \begin{equation}
-\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk
+\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk \cmma
 \label{eqn:tauLBG}
 \end{equation}
-and one can express the optical depth in terms of the radius using
-Equation~\ref{eqn:LBG_vlaw}.  Following \cite{sobolev60}, we have
+and invert the Sobolev approximation to derive the density profile.
+Following \cite{lamers+c99}, we have
 
@@
 n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa_\ell
-  \lambda_0}
+  \lambda}
 \label{eqn:Sobolev}
 \end{equation}
-with $\lambda_0$ the rest wavelength and $\kappa_\ell \equiv f\pi^2
-e^2/m_e c$.  The solid curve in the top panel of Figure~\ref{fig:LBG_Sobolev} shows the
-resultant density profile for Hydrogen.  [Probably show $n_{\rm
-  Mg^+}$]
-[This is a relatively extreme density profile.  From the inner radius
-of the wind (1\,kpc) to 2\,kpc, the density drops by over 2 orders of
-magnitude including approximately an order of magnitude over the first
-10\,pc.  Beyond 2\,kpc, the desnity drops even more rapidly, falling
-orders of magnitude from 2 to 100\,kpc.]
-It was derived by assuming
-that \mgiia\ transition has the optical depth profile given in
-Equation~\ref{eqn:tauLBG} (the black curve in the lower panel of
-Figure~\ref{fig:LBG_Sobolev})  and then scaling by $10^{5.77}$ which 
-corresponds to Mg depleted by a factor of 10 and a 1/2 solar
-metallicity.  [Give more detail?  Probably]
-We then verified that this density profile reproduced the correct
+with $\lambda$ the rest wavelength and $\kappa_\ell \equiv f\pi^2
+e^2/m_e c$.
+
+The solid curve in Figure~\ref{fig:LBG_Sobolev}a shows the
+resultant density profile for Mg^$+$ assuming that the \mgiia\ line
+follows the intensity profile drawn in Figure~\ref{fig:LBG_Sobolev}b. 
+This is a relatively extreme density profile.  From the inner radius
+of 1\,kpc to 2\,kpc, the density drops by over 2 orders of
+magnitude including nearly one order of magnitude over the first
+10\,pc.  Beyond 2\,kpc, the density drops even more rapidly, falling
+orders of magnitude from 2 to 100\,kpc.
+
+We verified that the density profile shown in
+Figure~\ref{fig:LBG_Sobolev}a
+reproduces the proper
 absorption profile by discretizing the gas into a series of tiny
-`clouds' and calculating the integrated absorption profile.  This is
-overplotted as a dotted red curve on the lower which is an excellent
+`clouds' and calculating the integrated absorption profile.  This
+calculation is shown as a dotted red curve in
+Figure~\ref{fig:LBG_Sobolev}b which is an excellent
 match to the desired profile (black curve).
-For Fe$^+$, we take $n_{\rm Fe^+} = n_{\rm Mg^+}/2$ and the strength
-of all other transitions scale as $f\lambda$, i.e.\ the 
-\mgiib\ profile will be half as deep as that shown in
-Figure~\ref{fig:LBG_Sobolev}.
-
-We then generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
-using the 1D algorithm with no dust extinction; these are shown with
-the red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
+To calculate the optical depth profiles for the other transitions, we
+assume $\mnfe = \mnmg/2$ and scale $\tau$ by $f\lambda$.
+
+We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
+using the 1D algorithm with no dust extinction; these are shown as
+red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
 should focus on the \mgiia\ transition.  The dotted line in the Figure
@@
   one should not make this comparison for the other transitions in
-  this Sobolev model because these are scaled down by $f\lambda$ and
-  the reduced Fe$^+$ abundance.} the profile
-described in Equation~\ref{eqn:LBG_I}.   The full model, however,
-shows much weaker absorption especially at $v = 0$ to $-300 \mkms$.
+  this Sobolev model because those are scaled down by $f\lambda$ and
+  (for \ion{Fe}{2}) the reduced Fe$^+$ abundance.} the profile
+described by Equation~\ref{eqn:LBG_I}.   In comparison, the full model
+shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$.
 In this respect, the LBG-Sobolev model is an
-inaccurate description of the observations.  In addition, the model
-predicts significant emission in the \ion{Mg}{2} lines and several of
+inaccurate description of the observations. The model
+also predicts significant emission in the \ion{Mg}{2} lines and several of
 the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
 has been observed for non-resonant \ion{Si}{2}
-transitions in LBGs \citep{cb58,shapley}.
-The \ion{Fe}{2} and \ion{Mg}{2} transitions
-  modeled here lie in the near-IR and have not yet been [explored].
-  [X-Shooter must help here]  On the other hand, there have been no 
+transitions in LBGs \citep{cb58,shapley}, but
+the \ion{Fe}{2} transitions
+modeled here lie in the near-IR and have not yet been investigated.
+On the other hand, there have been no 
 reported detections of significant line-emission related to resonance
-transitions in LBGs, only $z \le 1$ star-forming galaxies
-\citep{wcp+09,rubin09}.  We discuss these points further in the
-following section. [Do we?]
-
-[Does CIV scattered photons bugger up the P-Cygni analysis of Pettini
+transitions (e.g.\ \ion {Mg}{2}) in LBGs, only for $z \le 1$ star-forming galaxies
+\citep{wcp+09,rubin09}.  
+[Last line or two]
+
+[Do CIV scattered photons bugger up the P-Cygni analysis of Pettini
 et al. ?]
 
-[Does most of the scattering occur within the inner few kpc? Explore
-this with outflow.cc]
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Covering Fraction}
+\subsubsection{Partial Covering Fraction}
 \label{sec:Covering}
@@
 reproduces the average absorption profile of LBGs in cool gas
-transitions.  We found that a full analysis of this wind model leads
-to absorption profiles that are qualitatively different from the ones
-observed.  This is due to the re-emission and scattering of photons
-within the wind itself.  We also noted that this model differed from
-the one proposed by S10.  Their model [argued for] discrete, optically
-thick clouds with a non-unity covering fraction (described by
-Equation~\ref{eqn:covering}).   In contrast, the Sobolev model assumes
+transitions where scattered photons are ignored.  A proper analysis of
+this wind model predicts absorption profiles that are qualitatively
+different from the ones observed because scattered photons fill-in
+absorption and generate significant line emission, similar to the
+fiducial wind model ($\S$~\ref{sec:fiducial}).
+The LBG-Sobolev model, however, differs from
+the one proposed by S10.  They proposed an ensemble of optically
+thick clouds with the (parital) covering fraction described by
+Equation~\ref{eqn:covering}.   In contrast, the Sobolev model assumes
 a diffuse medium with a declining density profile but a unit covering
-fraction.
+fraction.  One is left to question whether this difference leads to
+the contradictory results of the model. [word]
 
@@
 a photon from the source until its velocity relative to line-center
-resonates with the wind (it escapes if this never occurs).
+resonates with the wind (the photon escapes if this never occurs).
 The photon then has a probability $P = f_c(r)$ of scattering.  If it
-scatters, we continue to track the photon until it comes into
+scatters, we track the photon until it comes into
 resonance again or escapes the system.  In this model, all of the
 resonance transitions are assumed to have identical optical depth in
-the absence of re-emission (the dotted line in
-Figure~\ref{fig:LBG_spec}).
-
-The results of the full calculation are
+the absence of re-emission.
+
+The results of the full calculation (absorption plus scattering) are
 shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
@@
 fine-structure counterparts lending to very weak emission at this
-transition. In fact the absorption profile very nearly matches the
+transition. The absorption profile very nearly matches the
 model without re-emission indicating that this transition well
-reproduces the opacity of the wind.  [Could SiII or OI provide a
-similar angle?]
-
-[Discuss 'exact' match of Sobolev + Covering at MgII 2796]
-[Does the similarity of the two require that the density of clouds
-fall off like the Sobolev solution?]
+reproduces the opacity of the wind.  
+The equivalent width of \feiia\ even exceeds that for \feiib, an
+inversion that if observed would strongly support this model.
+[Could SiII or OI do the same?]
+
+Comparing the LBG Sobolev and parital covering models in
+Figure~\ref{fig:LBG_spec} (via \mgiia), we note nearly identical
+results.  The differencs that occur for the other transitions,
+meanwhile, are only because their opacities are scaled downward in the
+Sobolev model (as required).  [Do the data prefer one to the other?
+And what if we modified the density away from Sobolev?]
+In principle, they provide a means to distinguish between the two LBG
+models.
+
+[Does most of the scattering occur within the inner few kpc? Explore
+this with outflow.cc]
 
@@
 
+\input{Tables/table_atomic.tex}
 \input{Tables/tab_fiducial.tex}
@@
 \caption{
-Surface-brightness emission maps around the \feiib\ transition for the
+(a) Surface-brightness emission maps around the \feiib\ transition for the
 source+wind complex.  The middle panel shows the 1D spectrum with $v=0
@@
 
-\begin{figure}
+\begin{figure*}
 \epsscale{0.8}
@@
 \caption{
-Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda 2612$ transition for the
+(b) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda 2612$ transition for the
 source+wind complex.  The middle panel shows the 1D spectrum with $v=0
@@
 \label{fig:fiducial_ifu_feii2612}
+\end{figure*}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_fiducial_cut.ps}
+\caption{
+Spatial cuts
+}
+\label{fig:fiducial_cuts}
 \end{figure}
@@
 
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_lbg_cumul.ps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+}
+\label{fig:LBG_cumul}
+\end{figure}
+
 \end{document}

### 2010-07-14 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5043 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\bturb}{$b_{\rm turb}$}
+\newcommand{\mbturb}{b_{\rm turb}}
 \newcommand{\taud}{$\tau_{\rm dust}$}
@@
 \def \kms  {km~s$^{-1}$}
-\def \mkms  {{\rm km~s^{-1}}}
+\def \mkms  {\, {\rm km~s^{-1}}}
 \def \lyaf {Ly$\alpha$ forest}
@@
 separation is sufficiently small ($\Delta v = c \Delta E / E \approx
-1.3 \, \mkms$) that most radiative transfer treatments actually ignore that
+1.3 \mkms$) that most radiative transfer treatments actually ignore that
 there are two transitions.   This is generally justifiable for \lya\ because 
@@
 significantly exceed its velocity separation and effectively mix the
-two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \, \mkms$),  
-\ion{Na}{1} ($\Delta v \approx 304 \, \mkms$), and most of the other doublets
+two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
+\ion{Na}{1} ($\Delta v \approx 304 \mkms$), and most of the other doublets
 commonly observed, the separation is large and the transitions
@@
 The adopted Doppler parameter
-($b_{\rm turb} = 15 \mkms$) has only a modest impact on the results.
-A larger/smaller $b$-value has minimal effect on the absorption
-profiles and only tends to modify the widths and for resonant
-transitions shifts the centroids of their emission lines.
+($\mbturb = 15 \mkms$) has only a modest impact on the results.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+The absorption profiles are insensitive to \bturb\ and this parameter 
+only tends to modify the widths and modestly
+shift the centroids of emission lines.
 
@@
 Nevertheless, we adopted values for this fiducial model with
-some astrophysical motivation,  e.g. values that correspond to
+some astrophysical motivation,  e.g., values that correspond to
 galactic dimensions and a normalization that gives $\tau_{2796}^{\rm
@@
 complex.  Figure~\ref{fig:fiducial_1d} presents the 1D spectrum
-that this observer would record, with the ``unattenuated'' flux
+that this observer would record, with the unattenuated flux
 normalized to unit value.   The \ion{Mg}{2} doublet
@@
 (Table~\ref{tab:fiducial_EW}), i.e.\ every photon
-absorbed eventually escapes the system, generally at lower
-energies.  The wind simply shuffles the photons in frequency space.
-
-Focusing on the \ion{Mg}{2} absorption, one notes the profiles lie
+absorbed eventually escapes the system, typically at lower
+energy.  The wind simply shuffles the photons in frequency space.
+
+Focusing further on the \ion{Mg}{2} absorption, one notes the profiles lie
 well above zero intensity and have similar depth even though their $f\lambda$
 values differ by a factor of two.  In standard absorption line
-analysis, this is generally 
+analysis, this is 
 the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
@@
 {\it entirely covers the source}; the apparent partial covering must
-be due to a different effect.
+be related to an alternate effect.
 Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
 absorption profiles from Figure~\ref{fig:fiducial_1d} against an
-artificial model where no absorbed photons are 
+artificial model where no absorbed photons are not
 re-emitted.   As expected from the
@@
   max}_{2796}) \approx 0$.
-The fiducial model, meanwhile, has been `filled in' at $v \approx -100
-\mkms$ by photons scattered and re-emitted by the wind (see below).  An
+The fiducial model, in contrast, has been `filled in' at $v \approx -100
+\mkms$ by photons scattered and re-emitted by the wind.  An
 absorption-line analysis that ignores these effects
@@
 not fully isotropic.
-[Dan's analytic calculation here? or Appendix?]
 
 Turning to the emission profiles of the \mgiid\ doublet, one notes
-that they are also and have comparable equivalent widths.  The
+that they are also similar and have comparable equivalent widths
+[word].  The
 flux of the \mgiib\ transition even exceeds that for \mgiia\ giving a
@@
 thick for a significant portion of the profile. 
-The flux from \mgiib\ actually exceeds the
+The ultimate outcome is a conversion of some \mgiia\ photons into
+\mgiib\ photons.
+Furthermore, the flux from \mgiib\ exceeds the
 \mgiia\ emission because the wind speed is greater than the velocity separation
@@
 lines, therefore, is sensitive to both the opacity and velocity
-extent of the wind.  We also emphasize that departures from a 2:1
-ratio indicate that processes other than simple recombination are
-active.  [CHECK THIS]
+extent of the wind.
 
@@
 shown in the velocity plot.  The line
-profile for \feiib\ is very similar to those for the \mgiid\ doublet;
+profile for \feiib\ is very similar to the \mgiid\ doublet;
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \, \mkms$ producing the characteristic P-Cygni profile of
+emission at $v > 0 \mkms$ producing the characteristic P-Cygni profile of
 an outflow.  Splitting
-the profile at $v = -50 \, \mkms$, we measure an equivalent width
+the profile at $v = -50 \mkms$, we measure an equivalent width
 $W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
@@
 In contrast, the \feiia\ resonance line shows much weaker emission and
-a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA)
+a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA),
 even though the line has a $2 \times$ lower $f\lambda$ value.
-The difference is entirely due to the much lower emission equivalent
-width for \feiia\ relative to \feiib.  The \feiia\ emission is reduced
-by two factors:
+These differences between the \ion{Fe}{2} resonance lines and with the
+\ion{Mg}{2} doublet occur because of the complex of non-resonant
+\ion{Fe}{2} transitions (Figure~\ref{fig:energy}).  Specfically,
+resonance photons absorbed at \feiid\ have a finite probability of
+being scattered as a non-resonant photon which escapes the system
+without further interaction.  The principal effects are to reduce the
+line emission of \feiid\ and produce non-resonant line-emission (e.g.\
+\feiic).
+
+The reduced \feiia\ emission relative to \feiib\ results from the
+\ion{Fe}{2}$^*$ emission.
+The \feiia\ flux is reduced by two factors:
 (i) there is an additional downward transition from the
 \zconfig$_{7/2}$ level and 
-(ii) more importantly, the Einstein A
+(ii) the Einstein A
 coefficients of the non-resonant lines are comparable to and even
@@
 the \ion{Fe}{2}~2626 transition (associated with \feiib)
-has an approximately  $4\times$ smaller coefficient than the
+has an approximately  $4\times$ smaller A coefficient than the
 resonance line.  Therefore, the majority of photons absorbed at
@@
 2632$).
+If we were to increase $\tau_{2600}$ (and especially if we include
+gas with $\mvr \approx 0 \mkms$) then the emission at \feiib\ is
+significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
 The total equivalent width, however, of the lines connected to the
-\zconfig$_{7/2}$ upper level must still vanish (hotons are conserved
+\zconfig$_{7/2}$ upper level must still vanish (photons are conserved
 in this fiducial wind model).
-Indeed, if were increase $\tau_{2600}$ and especially if we include
-gas with $\mvr \approx 0 \mkms$ then the emission at \feiib\ is
-significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
-
-The preceding discussion emphasize the filling-in of absorption at $v
-\lesssim -50 \, \mkms$ and the generation of emission lines at $v \approx
-0 \, \mkms$ by photons scattered in the wind.  To study the spatial
+
+The preceding discussion emphasizes the filling-in of resonance absorption at $v
+\lesssim -50 \mkms$ and the generation of emission lines at $v \approx
+0 \mkms$ by photons scattered in the wind.  To study the spatial
 extent of this emission, we perfomed 3D calculations with the fiducial
-model.  The outpus is a set of surface-brightness maps in a series of
-frequency channels, giving a
-dataset analagous to integral-field-unit (IFU) observations.  In
+model.  The output is a set of surface-brightness maps in a series of
+frequency channels; the
+dataset is analagous to integral-field-unit (IFU) observations.  In
 Figure~\ref{fig:fiducial_ifu_mgii}, we present the output 
 at several velocities relative to the \mgiia\
-transition. At $v = -200 \, \mkms$, where the wind has an optical
-depth $\tau_{2796} < 1$ (Figure~\ref{fig:fig_fiducial_nvt}),
-the source contributes significantly to the observed flux.  
-At $v=-100 \, \mkms$, however, the
+transition. At $v = -250 \mkms$, where the wind has an optical
+depth $\tau_{2796} < 1$ (Figure~\ref{fig:fiducial_nvt}),
+the source contributes roughly half of the observed flux.  
+At $v=-100 \mkms$, however, the
 wind absorbs all photons from the source and the observed emission is
@@
 actually exceeds the source+wind emission at 
-$v = -200 \, \mkms$ such
-that the absorption profile reaches peak depth at a velocity that is
-negatively offset from $\tau_{2796}^{\rm max}$.
+$v = -250 \mkms$ such
+that the absorption profile is
+negatively offset from the velocity where $\tau_{2796}$ is maximal
+(Figure~\ref{fig:fiducial_nvt}).
 The net result of the scattered photons is
 a weaker \ion{Mg}{2} profile that is offset from the true optical
-depth profile.  Clearly, this complicates estimates for the
+depth profile.  Clearly, the effects complicate estimates for the
 speed, covering fraction, and total column density of the wind.  At $v
-= 0 \, \mkms$, the wind and source have comparable total flux with the
+= 0 \mkms$, the wind and source have comparable total flux with the
 latter dominating at higher velocities.
 
-Similar characteristics are observed for the \ion{Fe}{2} resonance
+Similar results are observed for the \ion{Fe}{2} resonance
 transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
 For transitions to fine-structure levels of the \aconfig, the source
-is unattenuated but there is also a significant contribution from the
-wind (Figure~\ref{fig:fiducial_ifu_feii2612}).
-
-We rexpress these azimuthally symmetric surface-brightness maps in
-Figure~\ref{fig:fidicual_cuts} where the emission has been collapsed
-along one spatial axis.  For the fiducial model, the majority of
-\ion{Mg}{2} emission occurs within the inner few kpc, e.g.\ $50-60\%$ integrating
-over $r = \pm 2.5$\,kpc for $v=-100$ to $+100 \, \mkms$.  The fraction
+is unattenuated but there is a significant contribution from photons
+generated in the wind.
+
+At all velocities, the majority of emission occurs at $r \le 5$\,kpc.
+A better assessment of the radial profiles is provided by
+Figure~\ref{fig:fiducial_cuts}, where we collapse the 
+azimuthally symmetric surface-brightness maps in
+one spatial dimension.  The majority of
+\ion{Mg}{2} emission occurs within the inner few kpc, e.g.\ $50-60\%$
+of the light at $v=-100$ to $+100 \mkms$
+comes from $|r| < 3$\,kpc.
+The emission
 is even more centrally concentrated for the \ion{Fe}{2} transitions.
+These distributions are [critically important] for observations
+acquired through a slit, i.e.\ where the aperture has a limited extent
+in one or more dimensions.  A standard longslit on 10m-class
+telescopes, for examples, subtends $\approx 1''$ corresponding to
+$5-10$\,kpc for $z \sim 1$.    We return to this issue in
+$\S$~\ref{sec:obs}.
+
+[Comment that an observation like constrains the radial extent +
+density/velocity profiles of the wind]
 
@@
 
-In this section, we investigate a series of more complex scenarios
+In this section, we investigate a series of more complex wind
+scenarios
 through modifications to the fiducial model.  These include relaxing
@@
 Angular isotropy is obviously an idealized case, but
-one that is frequently assumed in studies of galactic-scale outflows
-\citep[e.g.][]{steidel+10}.   There are several reasons, however, why
-the wind may not be isotropic.  Firstly, galaxies are not spherically
+it is frequently assumed in studies of galactic-scale outflows
+\citep[e.g.][]{steidel+10}.   There are several reasons, however, to
+consider anisotropic winds.  Firstly, galaxies are not spherically
 symmetric;  the sources driving the
-wind (e.g.\ supernovae, AGN) are very likely to be anisotropically distributed
-within the galaxy.  Secondly, the galaxy may be surrounded by a
-anisotropic gaseous halo that could preferentially [constrain] the
+wind (e.g.\ supernovae, AGN) are very unlikely to be anisotropically distributed
+within the galaxy.  
+Secondly, the galactic ISM frequently has a disk-like morphology
+which will suppress the wind preferntially at low galactic latitudes,
+perhaps yielding a bi-conic morphology \citep[e.g.][]{m87}.
+Lastly, the galaxy may be surrounded by an
+anisotropic gaseous halo that would produce an irregularly shaped
 wind.
@@
 With these considerations in mind, we reanalyzed the fiducial model
-with the 3D algorithm after setting the density to zero for $2\pi$ steradians.
-We then rotated our view of this system from $\theta = 0^\circ$ where
-we view the source directly to $\theta = 180^\circ$ where the source
-is covered by the anisotropic wind.  The resulting \ion{Mg}{2} and
+with the 3D algorithm after departing from isotopy.  It is beyond the
+scope of this paper to explore a full suite of anisotropic profiles;
+the following simply assumes half of the fiducial wind, i.e.,  
+the density is set to zero for $2\pi$ steradians.
+We have viewed this system from $\theta = 0^\circ$ where
+the source is observed directly to $\theta = 180^\circ$ where the source
+is covered by this anisotropic wind.  The resulting \ion{Mg}{2} and
 \ion{Fe}{2} profiles are compared against the fiducial model
@@
 off the back side.  These photons, by definition, have $v \gtrsim 0 \mkms$
-relative to line-center (a few have $v<0 \mkms$ because
+relative to line-center (a subset have $v \lesssim 0 \mkms$ because
 of turbulent motions in the wind). 
@@
 key difference from the isotropic wind is the absence of photons
-scatterd to $v > 100 \mkms$ (also note the greater strength of the
-\mgiib\ profile at $v \approx -100 \, \mkms$). The asymmetry in emission lines
-may therefore provide a robust diagnostic of wind isotropy.
-For $\theta = 90^\circ$, the wind covers one half of the source and
-one observes half the absorption and also emission at all velocities.
+scattered to $v > 100 \mkms$;  this also implies a deeper 
+\mgiib\ absorption profile at $v \approx -100 \mkms$. The asymmetry
+shift in velocity centroid of the emission lines
+may provide a diagnostic of wind isotropy, especially when combined
+with the absorption profile [word].
 
 The results are very similar for the \feiid\ resonance lines.  The
-\ion{Fe}{2}$^* \; \lambda 2612$ line shows clearly the
-separation in velocity for the line-emission.   [Anything else?]
+\ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows most clearly the
+offset in velocity between the source unobscured ($\theta = 0^\circ$)
+and source covered ($\theta = 180^\circ$) cases.  This line [shift]
+produces the most robust constrain on wind isotropy. [Observable: dust
+is a trade-off]
 
@@
 Dust modifies the observed flux in two manners. 
-First, it serves as an opacity for the photons
-emitted by the source.  This suppresses the flux at all
+First, it is a source of opacity for all of 
+the photons.  This suppresses the flux at all
 wavelengths by $\approx \exp(-\mtaud)$, but because we normalize the profiles 
 this effect is essentially ignored.  Second, photons that are
-scattered by the wind (once or multiple times) into our view will travel a greater
+scattered by the wind will travel a greater
 distance and suffer from greater extinction.  A photon that is
 trapped for many scatterings may have a high probability of being absorbed
-by dust and then exit as an IR photon.  This process is
+by dust.  This process is
 often the explanation given for the weak (or absent) \lya\ emission
@@
 Section~\ref{sec:dust_method} describes our treatment of dust; we only
-remind the reader here that the opacity is assumed to scale with the
-gas density and that we normalize the extinction by the total optical
+remind the reader here that we assume a constant dust-to-gas ratio 
+normalized by the total optical
 depth \taud\ that a photon would experience if it travelled from the
@@
 dominant effect is the suppression of line emission at $v \ge 0
-\mkms$.  These `red' photons were scattered off the
+\mkms$.  These `red' photons have scattered off the
 backside of the wind and must travel a longer path than other
-photons.  This differnetial reddening with increasing wavelength (and
-velocity relative to line-center) is a natural consequence of dust
-extinction and is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
-emission profile.   In terms of the absorption, the profiles are
-nearly identical for $\mtaud \le 3$; one requires a very high
-extinction to see even a modest effect at $v \approx -100 \, \mkms$.
-
-We conclude that dust is a modest factor for this fiducial model and,
-by inference, for models with moderate peak optical depth and
+photons.  This creates a differential reddening that increases with wavelength (and
+velocity relative to line-center). It is a natural consequence of dust
+extinction;  the effect is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
+emission profile which is otherwise symmetrically distributed around
+$v \approx 0 \mkms$.   In terms of absorption, the profiles are
+nearly identical for $\mtaud \le 3$.  One requires a very high
+extinction to see an effect at $v \approx -100 \mkms$.
+
+% The following could go in the Discussion section
+We conclude that dust has only a modest influence on this fiducial model and,
+by inference, models with moderate peak optical depth and
 significant velocity gradients with radius (i.e.\ scenarios where the
 photons scatter one to a few times before exiting).
-At $\mtaud = 10$, however, the source itself is
-extinguished by 15\,magnitudes and would never be observed. 
+To achieve qualitative changes, one requires an extreme level of
+extinction ($\mtaud = 10$).  In this case, the source would be
+extinguished by 15\,magnitudes and could never be observed. 
 Even $\mtaud = 3$ is larger than typically inferred for the
 star-forming galaxies that drive outflows \citep[e.g.][]{dust}.
-The dominant effect is a reduction in the flux of the emission lines
-with greater extinction at higher velocities relative to line-center.
-In these respects, this roughly mimics the behavior of the anistropic
+For the emission lines,
+the dominant effect is a reduction in the flux 
+with a greater extinction at higher velocities relative to line-center.
+In these respects, dust extinction crudely mimics the behavior of the anistropic
 wind described in Section~\ref{sec:anisotropic}. [Is there a
@@
 
-[Do for other density laws, but maybe not show]
-
 \subsection{ISM}
@@
 
-The fiducial mdoel does not include gas associated with
+The fiducial model does not include gas associated with
 the interstellar medium of the galaxy, i.e.\ material at $r \sim
-0$\,kpc with $v_{\rm r} \approx 0 \, \mkms$.  We chose this to focus on
-properties of the wind.  [word]  The decision was also motivated by
-the general absence of significant absorption at $v \approx 0 \mkms$
-in galaxies that exhibit outflows
+0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
+results related solely to the wind.  The decision to ignore the ISM
+was also motivated by the general absence of significant absorption at
+$v \approx 0 \mkms$ in galaxies that exhibit outflows 
 \citep[e.g.][]{wcp+09,steidel+10,rubin+10}.
@@
 Consider, then, a modification to the fiducial model that has the
-identical wind but also includes an ISM component. 
+same wind but also includes an ISM component. 
 Specifically, the ISM component has $n_{\rm H} = 1 \cm{-3}$ for
@@
 The resultant optical depth profile $\tau_{2796}$ is identical to the
-fiducial model for $r > 2$\,kpc but has higher opacity at $r=1-2$\,kpc
-and a substantial component at $r = 0.5-1$\,kpc.
+fiducial model for $r > 2$\,kpc, a slightly higher opacity at
+$r=1-2$\,kpc, and a large opacity at $r = 0.5-1$\,kpc.
 
 In Figure~\ref{fig:ISM_spec}, the solid curves show the \ion{Mg}{2} and
-\ion{Fe}{2} profiles for the ISM+wind (black) and fiducial (red)
+\ion{Fe}{2} profiles for the ISM+wind (red) and fiducial (black)
 models. In comparison, the
 dotted curve shows the absorption profile for the ISM+wind in the (unphysical) case
-where none of the absorbed photons are re-emitted.   Focus first on the
+where none of the absorbed photons are scattered or re-emitted.   Focus first on the
 \ion{Mg}{2} doublet.  As expected, the dotted curve shows strong
@@
 the only quantitiative difference is that the velocity centroid of
-the emission lines are shifted redward by $\approx +100 \, \mkms$.
+the emission lines are shifted redward by $\approx +100 \mkms$.
 
@@
 \ion{Fe}{2}~$^* \lambda\lambda 2612, 2632$ photons.  In fact, the
-\feiia\ profile with scattering fully included nearly matches the profile without re-emission
-(compare the solid and dotted lines); this transition provides a
-very good description of the ISM+wind opacity profile.  The other key
-difference is the much higher strength ($3-10\times$) of emission from
-transitions to the excited states of \aconfig.   There are two reasons
-for the higher emission: (1) the absorption is greater in the \feiid\
+ISM+wind \feiia\ profile nearly matches the profile without re-emission 
+(compare to the dotted lines); this transition provides a
+very good description of the ISM+wind opacity profile.  
+We conclude that resonant transitions tha are coupled to (multiple)
+non-resonant, electric dipole transitions may offer the best
+diagnostic of ISM absorption.
+
+The differences in the \ion{Fe}{2} absorption profiles are reflected
+in the much higher strengths ($3-10\times$) of emission from
+transitions to the excited states of \aconfig.   This occurs because
+of : (1) the greater absorption in the \feiid\
 resonance lines; (2) the high opacity of the ISM component leads to
-the increased conversion of resonance photons with $v \approx 0\mkms$
+an enhanced conversion of resonance photons with $v \approx 0\mkms$
 into the non-resonance lines.  This is especially notable for the
@@
 $10\times$ stronger than for the fiducial model.  The relative
-strengths of the \feiib\ and \feiie\ lines therefore provide a direct
+strengths of the \feiib\ and \feiie\ lines provide a direct
 diagnostic on the degree to which the resonance lines are trapped.
@@
 [Fix the bug in the FeII* emission]
+
+\subsection{Summary Table}
+
+Table~\ref{tab:line_diag} presents a series of quantitative measures
+for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
+the fiducial model and a set of the variations.  Listed are the
+equivalent wdiths (absorption and emission), the peak optical depth
+for the absorption $\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the
+velocity where the optical depth peaks $v_\tau$, the optical
+depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv v
+\ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in
+emission, the velocity where the flux peaks $v_f$, and the
+flux-weighted velocity centroid of the emission line $v_{\bar f}$.
+
+One observes a wide range in these measures.  This emphasize the
+challenge in converting the absorption/emission data to physical
+constraints on wind schenarios.  We return to further consider these
+results in $\S$~\ref{sec:obs}.
 
@@
 
+\begin{equation}
+\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} 
+   + \ln\ltp R_0/r \rtp }
+\end{equation}
+
+\begin{equation}
+n(r) = \frac{dM_{\rm wind}/dt}{r^2 v(r)}
+\end{equation}
+
 \subsection{The Lyman Break Galaxy Model}
@@
 
-The Lyman break galaxies, UV color-selected galaxies at $z \sim 3$,
+The Lyman break galaxies (LBGs), UV color-selected galaxies at $z \sim 3$,
 exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
@@
 \citep[e.g.][]{lowenthal,pettini,steidel+10}.
-Researchers have since invoked these winds to explain enrichment of
+Researchers have invoked these winds to explain enrichment of
 the intergalactic medium \citep[e.g.][]{aguirre,evan}, the origin of the
@@
 presence of these outflows were established over a decade ago
-\citep{lowenthal,pettini98}, the processes driving the wind remain
-unidentified as do [precise] estimates of the mass/energetics of the
-outflow.
+\citep{lowenthal,pettini98}, the processes that drive them remain
+unidentified.  Similarly,  current estimates of the mass and energetics of the
+outflow suffer from orders of magnitude uncertainty.
 
@@
 explain jointly the average absorption they observed
-toward a set of XXX LBGs and the average absorption in cool gas
+toward a set of several hundred LBGs and the average absorption in cool gas
 observed transverse to these galaxies.  
 Their wind model is defined by two
-expressions: a radial velocity law $\mvr(r)$ and the covering fraction of
-optically thick gas $f_c(r)$.  For the latter, S10 envision an
+expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
+fraction of optically thick gas $f_c(r)$.  For the latter, S10
+envision an 
 ensemble of small, optically thick clouds $(\tau \gg 1)$ that only
@@
 a very steeply rising curve with $\alpha \approx 1.3$.
-This velocity expression is shown as a dotted line in the top panel of
-Figure~\ref{fig:LBG_Sobolev}.
+This velocity expression is shown as a dotted line in 
+Figure~\ref{fig:LBG_Sobolev}a.
 
@@
 I_{\rm LBG}(v) = 1 - f_{c,max} \ltk r_{\rm inner}^{1-\alpha} - \ltp
-\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\gamma}/(\alpha-1)}
+\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\gamma/(\alpha-1)}
 \perd
@@
 $\alpha=1.3$, and $A_{\rm LBG} = -192,000 \, \rm km^2 s^{-2} kpc^{-2}$ 
-is displayed in the lower panel of
-Figure~\ref{fig:LBG_Sobolev}.
+is displayed in Figure~\ref{fig:LBG_Sobolev}b.
 
@@
 ensemble of optically thick clouds with a partial covering fraction.
-by \cite{steidel+10}.
 
@@
 flattening at large radii.  Under these conditions, the Sobolev
-approximation relates the optical depth of an expanding medium to the
-density and velocity gradient of the gas.  In our case, we 
-generate the optical depth prpofile from Equation~\ref{eqn:LBG_I},
+approximation provies an accurate relation between the optical depth
+of the flowing medium to the
+density and velocity gradient ($d\mvr/dr$) of the gas.  In our case, we 
+generate the optical depth profile from Equation~\ref{eqn:LBG_I},
 
@@
 and invert the Sobolev approximation to derive the density profile.
-Following \cite{lamers+c99}, we have
+Following \cite{lamers+c99}, we have for a purely radial flow
 
@@
 n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa_\ell
-  \lambda}
+  \lambda} \cmma
 \label{eqn:Sobolev}
@@
 The solid curve in Figure~\ref{fig:LBG_Sobolev}a shows the
-resultant density profile for Mg^$+$ assuming that the \mgiia\ line
+resultant density profile for Mg$^+$ assuming that the \mgiia\ line
 follows the intensity profile drawn in Figure~\ref{fig:LBG_Sobolev}b. 
@@
 reproduces the proper
-absorption profile by discretizing the gas into a series of tiny
-`clouds' and calculating the integrated absorption profile.  This
+absorption profile by discretizing the gas into a series of layers
+and calculating the integrated absorption profile.  This
 calculation is shown as a dotted red curve in
@@
   this Sobolev model because those are scaled down by $f\lambda$ and
-  (for \ion{Fe}{2}) the reduced Fe$^+$ abundance.} the profile
-described by Equation~\ref{eqn:LBG_I}.   In comparison, the full model
-shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$.
-In this respect, the LBG-Sobolev model is an
+  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} the profile
+described by Equation~\ref{eqn:LBG_I} as plotted in
+Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
+red curve)
+shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
+due to scattered photons.
+In this respect, our LBG-Sobolev model is an
 inaccurate description of the observations. The model
@@
 the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
-has been observed for non-resonant \ion{Si}{2}
+has been observed for \ion{Si}{2}$^*$
 transitions in LBGs \citep{cb58,shapley}, but
-the \ion{Fe}{2} transitions
+the \ion{Fe}{2}$^*$ transitions
 modeled here lie in the near-IR and have not yet been investigated.
@@
 reported detections of significant line-emission related to resonance
-transitions (e.g.\ \ion {Mg}{2}) in LBGs, only for $z \le 1$ star-forming galaxies
+transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
 \citep{wcp+09,rubin09}.  
-[Last line or two]
+The principal result is that the scattering and re-emission of
+absorbed photons signficantly alters the predicted absorption profiles
+for the inputted model.  This is, of course, an unavoidable
+consequence of an isotropic, dust-free model with unit covering
+fraction.
+[Transition?]
 
@@
 transitions where scattered photons are ignored.  A proper analysis of
-this wind model predicts absorption profiles that are qualitatively
+this wind model, however, predicts line profiles that are qualitatively
 different from the ones observed because scattered photons fill-in
-absorption and generate significant line emission, similar to the
-fiducial wind model ($\S$~\ref{sec:fiducial}).
+absorption and generate significant line emission (similar to the
+fiducial wind model; $\S$~\ref{sec:fiducial}).
 The LBG-Sobolev model, however, differs from
-the one proposed by S10.  They proposed an ensemble of optically
+the one proposed by S10:  they proposed an ensemble of optically
 thick clouds with the (parital) covering fraction described by
-Equation~\ref{eqn:covering}.   In contrast, the Sobolev model assumes
+Equation~\ref{eqn:covering} whereas the Sobolev model assumes
 a diffuse medium with a declining density profile but a unit covering
-fraction.  One is left to question whether this difference leads to
-the contradictory results of the model. [word]
+fraction.  At face value, one questions whether this difference leads to
+the contradictory results of the model.
 
@@
 resonance again or escapes the system.  In this model, all of the
-resonance transitions are assumed to have identical optical depth in
-the absence of re-emission.
+resonance transitions are assumed to have identical (high) optical
+depth.
 
@@
 
+Given the essentially perfect correspondence between the Sobolev and
+partical covering models (for \mgiia), we are motivated to consider
+further the characteristics of the Sobolev model which offers a
+density profile.  It is straightforward to convert the density and
+velocity profiles into distributions of mass, energy, and momentum in
+the wind.  These are shown in cumulative form in
+Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
+two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
+assumes a very poorly constrained scalar factor of $10^{5.7}$.  One
+should give minimal weight to the absolute values for any of the
+quantities;
+(ii) the Sobolev approximation is not a proper description of the S10
+LBG wind model.
+
+The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
+majority of energy, mass, and momentum in the wind is transported by
+the outer layers ($r > 20$\,kpc).  This is surprising given that the
+density is $\approx 5$~orders of magnitude lower at these radii than
+at $r = 1$\,pc.  [Is this unphysical?  Can we conflate it to then kill
+the S10 model?]
+
 \section{Observables}
+\label{sec:obs}
 
@@
 
+[Does recombination predict 2:1 for MgII??]
+[We also emphasize that departures from a 2:1
+ratio indicate that processes other than simple recombination are
+active. ]
+
+[Profiles are modified by {\it many} factors => Difficult to derive
+robust constraints from absorption alone.]
+
+[Is one safe if there is no emission detected?]
+
 \acknowledgments
@@
 case (black lines) compared against an anisotropic wind blowing into
-only $2\pi$ steradians viewed from $\theta = 0^\circ$ (source
+only $2\pi$ steradians as viewed from $\theta = 0^\circ$ (source
 uncovered) to $\theta = 180^\circ$ (source covered).  One detects
-significant emission for all orientations of this wind with the
-emission shifting from positive to negative velocities as $\theta$
-increases.  
+significant emission for all orientations of this wind. The velocity
+centroid of this 
+emission shifts from positive to negative velocities as $\theta$
+increases.  The absorption reaches a maximum at $\theta > 100^\circ$
+and disappears for $\theta = 0^\circ$.
 }
@@
 model (black) against a series of models that include the effects of
-dust extinction.  The primary difference is the suppression of line
+dust extinction parameterized by \taud.  The primary difference is the suppression of line
 emission relative to the continuum (again, normalized to unit value).
@@
 line-center) suffer greater extinction.  This is most evident in the
-\feiic\ emission line and is due to the fact that these photons must
-travel further by scattering off the backside of the wind.  Note that
+\feiic\ emission line and occurs because these photons must
+travel further to scatter off the backside of the wind.  Note that
 the absorption lines are nearly unmodified until $\mtaud = 10$, a
@@
 \caption{
-Density (solid; black), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (dashed; red) for the ISM+wind
+Density (dashed; red), radial velocity (dotted; blue), and
+\mgiia\ optical depth profiles (solid; black) for the ISM+wind
 model.  The wind is identical to the fiducial model
-(Figure~\ref{fig:fiducial_nvt}) but we also include an ISM component
+(Figure~\ref{fig:fiducial_nvt}) but this model also includes an ISM component
 with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
@@
 \begin{figure}
-\epsscale{0.8}
+\epsscale{0.7}
 \plotone{Figures/fig_ism_spec.ps}
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
-model (black) compared against the fiducial wind model (red). 
+model (red) compared against the fiducial wind model (black). 
 The dotted line traces the predicted absorption profile in the absence
@@
 model to $\mvr \approx +100\mkms$ for the ISM+wind model. 
-[Discuss FeII]
+The \ion{Fe}{2} profiles, however, show qualitative differences from
+the ISM model.  The \feiid\ resonance transitions each exhibit much
+greater absorption at $v \approx 0 \mkms$ than the fiducial model.
+This emission associated with these lines is also substantially
+reduced, implying much higher fluxes for the non-resonant lines (e.g.\
+\feiic).  The lack of scattered \feiia\ photons results in an
+absorption profile that very nearly matches the input opacity profile.
+We conclude that fine-structure transitions may offer the best
+characterization of an ISM component.
 }
@@
 {\it Upper:} The dotted curve shows the velocity law for the LBG model
-of \cite{steidel+10}.  Note how rapidly the velocity rises from $r =
-1$ to 2\,kpc.  The solid curve shows the Sobolev solution required to
-match the average absorption profile of LBG galaxies (lower panel).
-The density drops off as $(r-1)^{-0.6}$ 
-{\it Lower:} Absorption profiles for the LBG model as defined by
-\cite{steidel+10} (black solid curve) and for our Sobolev approximation of
-the model (red dotted curve).  
+of S10.  Note how rapidly the velocity rises from $r =
+1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the gas
+density derived from 
+the average absorption profile of LBG galaxies (lower panel).
+The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
+steepends to $(r/{\rm kpc}-1)^{-1.8}$.
+{\it Lower:} Average absorption profile for LBG cool gas absorption as
+measured and defined by S10
+(black solid curve).  Overplotted on this curve is a (red) dotted line that
+shows the absorption profile dervied from the density (and velocity)
+law shown in the upper panel.  The excellent agreement confrims the
+validity of the Sobolev approximation.
 }
@@
 \caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
+LBG models considered in the text: (red) the profiles for the density
+law derived from the Sobolev approximation using the average LBG
+absorption profile and (black) a model constructed to faithfully
+correspond to the wind model advocated by S10.  The dotted line,
+meanwhile, shows the absorption profiles of the latter model where one
+ignores scattered and re-emitted photons.  Similar to the fiducial
+model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
+significantly modify the absorption profiles (especially \ion{Mg}{2})
+and produce significant emission lines.  There is remarkable agreement
+between the \mgiia\ profile for the two models. [Cast doubt on S10
+here?]
 }

### 2010-07-14 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5044 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 which will suppress the wind preferntially at low galactic latitudes,
-perhaps yielding a bi-conic morphology \citep[e.g.][]{m87}.
+perhaps yielding a bi-conic morphology \citep[e.g.][]{M87}.
 Lastly, the galaxy may be surrounded by an
@@
 \begin{equation}
-\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} 
+\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} \rtp
    + \ln\ltp R_0/r \rtp }
@@
 
+\clearpage
+
+%\bibliographystyle{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati}
+%\bibliography{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati09}
 \bibliographystyle{/u/xavier/paper/Bibli/apj}
 \bibliography{/u/xavier/paper/Bibli/allrefs}
+
+\clearpage
 
@@
 
+\clearpage
+
 \begin{figure}

### 2010-07-16 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5047 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-Nearly all gaseous objects in astrophysics that emit light are also
-observed to drive gas away.  [word] This includes the jets of protostars, the
-strong stellar winds of massive O and B stars, the gentle Solar wind
+Nearly all gaseous objects in astrophysics that shine are also
+observed to [emit] gas.  This includes the jets of protostars, the
+stellar winds of massive O and B stars, the gentle Solar wind
 of our Sun, the associated absorption of bright quasars, and the
@@
 momentum into gas on large scales, and ...
-[Last line]
-
-Star-burst galaxies, whose light is dominated by \ion{H}{2} regions
-and massive stars, are also observed to drive gaseous outflows.  The
+Developing a comprehensive model for these flows is critical to
+understanding the evolution of the source and the impact on its
+surrounding environment.
+
+Star-burst galaxies, whose luminosity is dominated by \ion{H}{2} regions
+and massive stars, are also observed to drive gaseous outflows.  These
 flows are generally expected (and sometimes observed) to have multiple
-phases, with a hot and diffuse phase traced by X-ray emission
-\citep[e.g.][]{strickland,martin+k} and a cool, denser phase traced by
-H$\alpha$ emission \citep[e.g.][]{NGC891,M87}.
-
-Beyond the local universe, galactic outflows are predominatly
-revealted by UV and optical absorption lines, e.g.\ \ion{Na}{1},
+phases, for example a hot and diffuse phase traced by X-ray emission
+\citep[e.g.][]{shc+04,km10} together with a cool, denser phase traced by
+H$\alpha$ emission \citep[e.g.][]{NGC891}.  Several spectacular
+examples in the local universe demonstrate that flows can extend to
+tens of kpc from the galaxy \citep{M87} carrying significant speed
+to escape from the gravitational potential well of the galaxy's dark
+matter halo \citep{wind_escape}.
+
+Beyond $z \sim 0$, galactic outflows are predominatly
+revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
 \ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
-as a backlight, one almost universally observes predominantly
+as a backlight, one observes predominantly
 blue-shifted material indicating a galactic-scale flow of gas toward
@@
 which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
-\citep{rupke,martin,student}, $z \sim 1$ star-forming galaxies traced by
+\citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
 \ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin+10}, and
 $z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
-\ion{C}{2}, and \ion{O}{1} transitions \citep{lowenthal,steidel94}.
-
-Although the obsevation of metal-line absorption is a well established
-means of identifying outflows at all epochs, little effort has been
-made to compare these observations against (even idealized) wind
-models.  The focus to date has been to gelan the limited information
-affored by direct analysis of the absorption lines.  The data do yield
-robust measurements of the speed of the gas yet poorly constrain the
+\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97}.
+
+The observation of metal-line absorption is now a well established
+means of identifying outflows at all epochs. Very little research,
+however,  has been directed
+to comparing the observations against (even idealized) wind
+models.  Instead, researchers have tried to glean what limited information
+is affored by direct analysis of the absorption lines.  The data do yield
+robust measurements of the speed of the gas yet they poorly constrain the
 optical depth, covering fraction, density, temperature, and distance
-of the gas from the emitting regions.  Constraints related to the
+of the flow from the galaxy.   In turn, constraints related to the
 mass, energetics, and momentum of the flow suffer from
-orders of magnitude uncertainty.  Both the origin and impact of the
-winds, therefore, remain open points of debate.
+orders of magnitude uncertainty.  Both the origin and impact of
+galactic-scale winds, therefore, remain open points of debate
+\citep{debate}.
 
 Recent studes of $z \sim 1$ star-forming galaixes have revealed that
-the cool gas frequently exhibits significant \ion{Mg}{2} emission in
-addition to the ubiquitous blue-shifted absorption
-\citep{wcp+09,rubin+10b}.  \cite{rubin+10a} have also detected line
+the cool gas often exhibits significant \ion{Mg}{2} emission in
+tandem with the nearly ubiquitous blue-shifted absorption
+\citep{wcp+09,rubin+10b}.  The resultant spectra resemble the P-Cygni
+profile characteristic of stellar winds.
+\cite{rubin+10a} have also detected line
 emission from non-resonance \ion{Fe}{2}~$^*$ transitions and spatially
-extended \ion{Mg}{2} emission which they interpret as originating from
-photons scattered off a galactic-scale wind.  They estimate that the
+extended \ion{Mg}{2} emission which they interpret as 
+photons scattered off the wind.  In one galaxy, they estimate that the
 wind extends to at least 5\,kpc from the galaxy.  Line emission is
 also observed for $z \sim 3$ LBGs via the resonant \lya\ transition
-and fine-strcuture \ion{Si}{2}$^*$ transitions \citep{cb58,shapley}.
-\cite{rubin+10a} emphasize that a comprehensive analysis of these data
-(e.g.\ via integral-field-unit observations) could yield unique
+and fine-strcuture \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
+A comprehensive analysis of these emission lines
+(e.g.\ via deep integral-field-unit observations) could yield unique
 diagnostics on the morphology and density of the outflow, eventually
-yielding tigheter constrains on the energetics of the flow.  
-The crucial piece missing from this path is a radiative transfer
-treatment that properly ...
+setting tighter constraints on the energetics of the flow.  
+Although astrnomoers are rapidly producing a wealth of observational
+datasets on galactic-scale winds, a key ingredient to a proper
+analysis is absent.
+
+[Draw analaogy to exploring SN lightcurves and spectra]
 
@@
 
-This section describes the methodology [employed] to generate
+This section describes our methodology for generating
 emission/absorption profiles from simple wind models.
@@
 arising from Fe$^+$ and Mg$^+$ ions
-(Table~\ref{tab:atomic},Figure~\ref{fig:energy}).
-Although this is a necessarily limited
-set, the two ions and their transitions are characteristic
-of the majority of low-ions 
+(Table~\ref{tab:atomic}, Figure~\ref{fig:energy}).
+This is a necessarily limited
+set, but the two ions and their transitions have characteristic
+shared by the majority of low-ions 
 observed in cool-gas outflows. Therefore, many
-of the results may be generalized to observational studies that
+of the results that follow may be generalized to observational studies that
 consider other atoms and ions of cool gas.
@@
 exhibits an alkali doublet of transitions at $\lambda \approx
-2800$\AA\ similar to the
-\lya\ transitions of neutral hydrogen.  Figure~\ref{fig:energy}
+2800$\AA\ analagous to the
+\lya\ doublet of neutral hydrogen.  Figure~\ref{fig:energy}
 presents the energy level diagram for this 
@@
 mechanics, the 2p$^6$3p energy level is said to be split by spin-orbit
-coupling which yields the observed line doublet.  These are the only
+coupling giving the observed line doublet.  These are the only
 \ion{Mg}{2} electric-dipole transitions 
@@
 \maconfig~$\to$~\mbconfig\
-is followed essentially 100$\%$ of the time by a spontaneous decay
-($t_{\rm decay} \approx 4\sci{-9}$s to the
+is followed $\approx 100\%$ of the time by a spontaneous decay
+($t_{\rm decay} \approx 4\sci{-9}$s) to the
 ground state. Our treatment will ignore any other possibilities
@@
 
-The physics of the \mgiid\ doublet
-is analagous to the physics of \ion{H}{1}
+In terms of radiative transfer, the [behaviour]
+of the \mgiid\ doublet
+is very similar to that for \ion{H}{1}
 \lya, the \naid\ doublet, and many other doublets commonly
-studied in the interstellar medium (ISM) of distant galaxies.  The
-doublets differ only in 
+studied in the interstellar medium (ISM) of distant galaxies.  
+Each of these has the ground-state connected by a pair of electric
+dipole transitions with nearly identical energy.
+The doublets differ only in 
 their rest wavelengths and the energy of the doublet separation. 
@@
 commonly observed, the separation is large and the transitions
-must be treated separately.  Regarding the analysis of outflows, the line
-separation plays an important role when the outflow speed matches or
-exceeds $\Delta v$.  [Explain?]
-
-Iron exhibits the most complex set for energy levels of the elements
+must be treated separately.
+
+Iron exhibits the most complex set of energy levels for elements
 frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
@@
 This includes the ground-state configuration (\aconfig) which is split
-into 5 levels with 
-excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
-$T_{\rm ex} \approx 500-1500$\,K, labelled by the total angular momentum
-$J$. The ground-state has $J=9/2$ (Figure~\ref{fig:energy}).  
+into 5 levels, 
+labelled by the total angular momentum $J$, 
+with excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
+$T_{\rm ex} \approx 500-1500$\,K (Figure~\ref{fig:energy}).  
 Transitions between these fine-structure levels are 
-forbidden (magnetic-dipole) with spontaneous decay times of several hours.
+forbidden (magnetic-dipole) and have spontaneous decay times of several hours.
 
@@
   standard convention that a ``resonance line'' is an electric-dipole
-  transition connected to the ground-state.} 
+  transition connected to the ground-state.  We also label
+  non-resonsant transitions with an asterisk, e.g.\ \feiic.} 
 associated with this multiplet (\feiid)
-corresponding to $\Delta J = 0, -1$.  The solid (green) downward
-arrows in Figure~\ref{fig:energy} mark the transitions that connect to
-the upper energy levels of the resonance lines.  These transitons can
+corresponding to $\Delta J = 0, -1$ indicated by upward (black) arrows
+in Figure~\ref{fig:energy}. The solid (green) downward
+arrows in Figure~\ref{fig:energy} mark the transitions that are
+connected to
+the upper energy levels of the resonance lines.  These transitons may
 occur following the absorption of a single photon by Fe$^+$ in its
@@
 of two photons: one to raise the electron from the ground-state to an
-excited state and one from the excited state to one of the \zconfig\
-levels with $J \le 5/2$.  The excitation of these levels by
+excited state and another to raise the electron from the excited state
+to one of the \zconfig\ levels with $J \le 5/2$.  The excitation of
+fine-structure levels by 
 the absorption of UV photons is termed indirect UV pumping
-\citep[e.g][]{sv02,pcb06} and requires the ion to lie
+\citep[e.g][]{silva02,pcb06} and requires the ion to lie
 near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
@@
 is not significantly blue-shifted \citep{rubin+10}.
-Empirically, collisional excitation is insignificant and, by
-inference, one may neglect collisional de-excitation.  
-For Mg$^+$,$T_{\rm ex} \approx 50,000$\,K  
-$n_e^C \approx 3 \sci{14} \cm{-3}$  [Maybe critical density is
-not so interesting here...]
-implying negligible collisional excitation for the cool gas.  
-This implies the gas has zero opacity to the non-resonant lines.
+In the following, we assume that electrons only occupy the
+ground-state, i.e.\ the gas has zero opacity to the non-resonant
+lines.
+Empirically, because collisional excitation is insignificant and
+then one may also neglect collisional de-excitation.  
+The excitation energy for Mg$^+$ ($T_{\rm ex} \approx 50,000$\,K),  
+meanwhile, is significantly higher implying 
+negligible collisional excitation.
 
@@
 
-Nearly all the absorption studies of cool-gas outflows 
+Nearly all of the absorption studies of cool-gas outflows 
 have focused on intensely, star-forming galaxies.  The
@@
 stars and \ion{H}{2} regions that is then modulated by dust and gas
-within the ISM.  For the spectral regions studied
+within the interstellar medium (ISM).  For the spectral regions studied
 here, most stars show a featureless continuum but a few spectral
@@
 normalized to unit value.  The size of the emitting
-region $r_{\rm source}$ is a free parameter, although we tend to
+region $r_{\rm source}$ is a free parameter, but we tend to
 restrict its value to be smaller than the minimum radial extent of any
@@
 
-[What does MgI tell us about winds?  Why no P-Cygni?]
-
 \subsection{Monte Carlo Algorithm}
@@
 For the majority of models studied in this paper, we assume no dust.
-This is an invalid assumption, espeically for material associated with
-the ISM of the galaxy.  Because absorption line analysis is performed
-on normalized spectra, the effects of dust are largely minimized.  For
-scattered and resonantly trapped photons, however, the effects of dust
-extinction can be significant.  Indeed, dust is frequently invoked to
+This is an invalid assumption, especially for material associated with
+the ISM of a galaxy.  
+There is also empirical evidence for dust emission from galactic-scale
+outflows from near-IR emission \citep[e.g.][]{M87_dust}.
+Because absorption line analysis is performed
+on normalized spectra, the effects of dust are largely minimized.  
+These effects are corrected for by simply rescaling the normalized
+flux.  For
+scattered and resonantly trapped photons, however, the relative effect of dust
+extinction can be much greater.  Indeed, dust is frequently invoked to
 explain the weak (or absent) \lya\ emission from star-forming galaxies
 \citep[e.g.][]{shapley03}.  Although the transitions studied here have
-significantly lower opacity than \lya, dust may play an important role
+significantly lower opacity than \lya, dust could play an important role
 in the predicted profiles.
@@
 infinity.  The ISM of a star-forming galaxy may be expected to exhibit
-\taud\ of a few \citep[e.g.][]{steidel98}.
+\taud\ values of one to a few \citep[e.g.][]{dust_again}.
 
@@
 part, to yield a \ion{Mg}{2} absorption profile 
-similar to that observed toward $z<1$, star-forming galaxies
-\citep{wcp+09,rubin10b}.  We emphasize, however, that we do not
+similar to those observed for $z \sim 1$, star-forming galaxies
+\citep{wcp+09,rubin+10b}.  We emphasize, however, that we do not
 favor this fiducial model over any other wind scenario nor do its
@@
 
-The fiducial wind follows a (mass-fluxing conserving) density law,
+The fiducial wind follows a (mass-flux conserving) density law,
 
@@
 \end{equation}
-and a velocity
+and a velocity law
 
@@
 radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
-We scale the hydrogen density $n_{\rm H}$ to the number densities of
+We convert the hydrogen density $n_{\rm H}$ to the number densities of
 Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
@@
 and \nfe=\nmg/2. At the center of the wind is a homogenous source of
-continuum photons with a size $r_{\rm source}$. These parameters are
+continuum photons with size $r_{\rm source}$. These parameters are
 summarized in Table~\ref{tab:fiducial}.
@@
 In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
-profiles against radius for the fiducial wind model;  
+laws against radius;  
 their single power-law expressions are evident.  The figure also
 shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
-Although plotted against radius, we first calculated $\tau_{2796}$ 
-as a function of velocity by summing the opacity in a series of
+Although plotted against radius, we calculated $\tau_{2796}$ first
+as a function of velocity by summing the opacity for a series of
 discrete and small radial intervals
@@
 (Equation~\ref{eqn:vel}). 
-The $\tau_{2796}$ profile peaks at $\tau_{2796}^{\rm max} \approx 30$
-with a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
+The $\tau_{2796}$ profile peaks with $\tau_{2796}^{\rm max} \approx 30$
+at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
 r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
@@
 The adopted Doppler parameter
-($\mbturb = 15 \mkms$) has only a modest impact on the results.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+($\mbturb = 15 \mkms$) has a minor impact on the results.
 The absorption profiles are insensitive to \bturb\ and this parameter 
@@
 saturated) which only partially covers the emitting source
-\citep[e.g.][]{hamman10}.  Our fiducial wind model, however, 
+\citep[e.g.][]{hamann+10}.  Our fiducial wind model, however, 
 {\it entirely covers the source}; the apparent partial covering must
@@
 absorption-line analysis that ignores these effects
-\citep[e.g.][]{sato} would (i) systematically underestimate the true optical
+\citep[e.g.][]{smn+09} would (i) systematically underestimate the true optical
 depth and (ii) falsely conclude that the wind partially covers the
@@
 \citep[e.g.][]{ss96,pw01,pcd+07}, strong \ion{Mg}{2} metal-line
-absorption systems \citep{york,menard}, and the galactic winds traced
-by low-ion transitions \citep{cb58,naI}.  Although the galactic winds
+absorption systems \citep{ykv+06,mnt+08}, and the galactic winds traced
+by low-ion transitions \citep{prs+02,rvs05b}.  Although the galactic winds
 traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
@@
 often the explanation given for the weak (or absent) \lya\ emission
-associated with star-forming galaxies \citep[e.g.][]{lya}.
+associated with star-forming galaxies. 
 Section~\ref{sec:dust_method} describes our treatment of dust; we only
@@
 $v \approx 0 \mkms$ in galaxies that exhibit outflows 
-\citep[e.g.][]{wcp+09,steidel+10,rubin+10}.
+\citep[e.g.][]{wcp+09,steidel+10,rubin+10b}.
 On the other hand, the stars and \ion{H}{2} regions that comprise our
@@
 etc.\ transitions with speeds up to 1000\kms\
-\citep[e.g.][]{lowenthal,pettini,steidel+10}.
+\citep[e.g.][]{lkg+97,pks+98,steidel+10}.
 Researchers have invoked these winds to explain enrichment of
-the intergalactic medium \citep[e.g.][]{aguirre,evan}, the origin of the
-damped \lya\ systems \citep{nelson,joop98}, and XXX.  Although the
-presence of these outflows were established over a decade ago
-\citep{lowenthal,pettini98}, the processes that drive them remain
+the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
+damped \lya\ systems \citep{nbf98,schaye01a}, and XXX.  Although the
+presence of these outflows were established over a decade ago,
+the processes that drive them remain
 unidentified.  Similarly,  current estimates of the mass and energetics of the
@@
 and invert the Sobolev approximation to derive the density profile.
-Following \cite{lamers+c99}, we have for a purely radial flow
+Following \cite{lc99}, we have for a purely radial flow
 
@@
 has been observed for \ion{Si}{2}$^*$
-transitions in LBGs \citep{cb58,shapley}, but
+transitions in LBGs \citep{prs+02,shapley03}, but
 the \ion{Fe}{2}$^*$ transitions
@@
 
+[What does MgI tell us about winds?  Why no P-Cygni?]
+
 \acknowledgments
 
-J. X. P. and J.M.O. are supported by NASA grant
-HST-GO-10878.05-A.  J.X.P and G.W. are partially supported
+J.X.P and K.R. are partially supported
 by an NSF CAREER grant (AST--0548180), and 
@@
 labelled by its rest wavelength (\AA) and Einstein A-coefficient
-(s$^{-1}$). Black updward arrows
-indicate the resonance-line transitions connected to the ground
-state of each ion.  The 2p$^6$3p configuration of Mg$^+$ is split into
+(s$^{-1}$). Black upward arrows
+indicate the resonance-line transitions, i.e.\ those connected to the ground
+state.  The 2p$^6$3p configuration of Mg$^+$ is split into
 two energy levels that give rise to the \mgiid\ doublet.  
@@
 electric-dipole transitions. 
-The downward (green) arrows show the transitions connected to the
+The downward (green) arrows show the transitions that are connected to the
 resonance-line transitions (i.e.\ they share the same upper energy
@@
 configuration.  These transitions have not yet been observed in
-galactic-scale outflows and are not considerd in our analysis.
+galactic-scale outflows and are not considered in our analysis.
 }
@@
 \caption{
-Density (solid; black), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (dashed; red) for the fiducial
+Density (dashed; red), radial velocity (dotted; blue), and
+\mgiia\ optical depth profiles (solid; black) for the fiducial
 wind model (see Table~\ref{tab:fiducial} for details).
-The density and velocity profiles are simple $r^{-2}$ and $r$
+The density and velocity laws are simple $r^{-2}$ and $r^1$
 power-laws.  The optical depth profile was calculated by summing
-the opacity at small and discrete radial intervals.  One notes that
+the opacity at small and discrete radial intervals in velocity space
+and then converted to radius with the velocity law.  One notes that
 the wind is optically thick at the inner radius ($r_{\rm inner} =
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_fiducial_1d.ps}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_fiducial_1d.ps}
 \caption{
-{\it Left} -- (upper) \ion{Mg}{2} profiles for the fiducial wind model
+{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
 described in Table~\ref{tab:fiducial} and
@@
 characteritic of an outflow with significant absorption blueward of
-line center (dashed vertical lines) extending to $v = -1000\mkms$
-and signficiant emission redward of line center.  Note
+line-center (dashed vertical lines) extending to $v = -1000\mkms$
+and significant emission redward of line-center.  Note
 that even though the peak optical depth of the \ion{Mg}{2} transitions
@@
 fill in the absorption.
-(lower) \ion{Fe}{2} absorption and emission profiles for the UV1
+(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
 multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
@@
 absorbed \feiia\ photons are converted into
-\ion{Fe}{2}~$\lambda\lambda 2612, 2632$ photons as observed.
-[Mention the emission kinematics?]
+\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
+{\it Right} -- A subset of the transitions displayed in a velocity
+plot.
 }
@@
 \caption{
-The black curves show the line profiles (absorption and emission) of
+The solid curves show the line profiles (absorption and emission) of
 the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
-model.  These shows the canonical P-Cygni profiles of a source
-embedded within an outflow.  Overplotted (red) on each transition is
-the predicted absorption profile under the constraint that each
+model.  These include the effects of scattered photons and show the
+canonical P-Cygni profiles of a source 
+embedded within an outflow.  Overplotted (dotted line) on each transition is
+the predicted absorption profile under the constraint that every
 absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission.   It is evident that the true profiles have been `filled
+re-emission occurs.   These profiles have been `filled
 in' significantly by light scattered in the wind.  Ignoring this
-process, one would model the absorption lines with systematicall lower
-optical depth and derive a partial covering. [word]
+process, one would model the absorption lines with a systematically lower
+optical depth and (incorrectly) conclude that the source is partly covered by the
+gas.  It is essential, therefore, to account for the effects of
+scattered/re-emitted photons in a proper analysis of the absorption
+profiles of cool gas outflows.
 }
@@
 Surface-brightness emission maps around the \mgiia\ transition for the
-source+wind complex.  The middel panel shows the 1D spectrum with $v=0
+source+wind complex of the fiducial model.  The middel panel shows the 1D spectrum with $v=0
 \mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
-curves indicating the velocity slices for the emission maps.  The
+curves indicate the velocity slices for the emission maps.  The
 source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
-pixels at the center.   At $\mvr=-200 \mkms$, the wind has an optical
-depth of $\tau_{2796} \approx 1$ such that the source contributes
-significantly to the observed flux.  At $\mvr=-100 \mkms$, however, the
+pixels at the center.   At $v=-250 \mkms$, the wind has an optical
+depth of $\tau_{2796} \approx 1$ and the source contributes
+roughly half of the observed flux.  At $v=-100 \mkms$ the
 wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  Surprisingly, this
-emission exceeds that observed at $\mvr = -200\mkms$. At $\mvr \ge 0
+entirely due to photons scattered by the wind.  Impressively, this
+emission exceeds the integrated flux at $v = -250\mkms$. At $v \ge 0
 \mkms$,  both the source and wind contribute to the observed emission.
+At all velocities, the majority of emission comes from the inner
+$\approx 5$\,kpc.
 }
@@
 \plotone{Figures/fig_fiducial_ifu_feii2600.ps}
+\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
 \caption{
@@
 (Figure~\ref{fig:fiducial_ifu_mgii}).
-}
-\label{fig:fiducial_ifu_feii2600}
-\end{figure}
-
-\begin{figure*}
-\epsscale{0.8}
-\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
-\caption{
-(b) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda 2612$ transition for the
+(b) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
+2612$ transition for the 
 source+wind complex.  The middle panel shows the 1D spectrum with $v=0
@@
 }
-\label{fig:fiducial_ifu_feii2612}
-\end{figure*}
+\label{fig:fiducial_ifu_feii}
+\end{figure}
 
@@
 \caption{
-Spatial cuts
+The panels show the relative emission from the wind as a function of
+radius for (a) \mgiia\ and (b) \feiib\ in a series of velocity
+channels.  With the exception of $v = -100 \mkms$ for \mgiia, the wind
+has finite transmission such that one observes the source at $r =
+0$\,kpc.  In all cases,  the majority of emission occurs at $r
+\lesssim 2.5$\,kpc, even if one ignores the source emission.
 }

### 2010-07-16 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc

@@ -1,0 +1,457 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "lines.hh"
+
+LINES lines;
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2575;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  5e-2;     // number density at inner boundary (cm^-3)
+double v_parm    =  1.0;      // power law of velocity profile
+double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
+double v_rval    = r_outer;
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+//double omnl = 1-n_law;
+//double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+//int    n_lines      = 2; 
+// line center wavelengths
[…]

### 2010-07-16 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_mgii.cc

@@ -1,0 +1,434 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  5e-2;     // number density at inner boundary (cm^-3)
+double v_parm    =  1.0;      // power law of velocity profile
+double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
+double v_rval    = r_outer;
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+//double omnl = 1-n_law;
+//double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
+double lambda_0[]   = {2796.352, 2803.531};  
+// line oscillator strengths
[…]

### 2010-07-16 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5048 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
+\newcommand{\feiis}{\ion{Fe}{2}$^*$}
 \newcommand{\nmg}{$n_{\rm Mg^+}$}
@@
 
-Nearly all gaseous objects in astrophysics that shine are also
-observed to [emit] gas.  This includes the jets of protostars, the
+Nearly all gaseous objects that shine are also
+observed to generate gaseous flows.  This includes the jets of protostars, the
 stellar winds of massive O and B stars, the gentle Solar wind
@@
 spectacular jets of radio-loud AGN.   These gaseous outflows moderate
-the accretion of fresh material onto the object, inject energy and
+the accretion of new material onto the object, inject energy and
 momentum into gas on large scales, and ...
 Developing a comprehensive model for these flows is critical to
-understanding the evolution of the source and the impact on its
+understanding the evolution of the source and its impact on the
 surrounding environment.
@@
 phases, for example a hot and diffuse phase traced by X-ray emission
-\citep[e.g.][]{shc+04,km10} together with a cool, denser phase traced by
-H$\alpha$ emission \citep[e.g.][]{NGC891}.  Several spectacular
+together with a cool, denser phase traced by H$\alpha$ emission 
+\citep[e.g.][]{shc+04,km10}. 
+Several spectacular
 examples in the local universe demonstrate that flows can extend to
@@
 
-Beyond $z \sim 0$, galactic outflows are predominatly
+Beyond $z \sim 0$, galactic outflows are 
 revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
 \ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
-as a backlight, one observes predominantly
-blue-shifted material indicating a galactic-scale flow of gas toward
+as a backlight, one observes gas that is predominantly
+blue-shifted which indicates a flow toward
 Earth and away from the galaxy.  These transitions are sensitive to
@@
 \citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
-\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin+10}, and
+\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin09}, and
 $z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
-\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97}.
+\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97,shapley03}.
 
 The observation of metal-line absorption is now a well established
-means of identifying outflows at all epochs. Very little research,
+means of identifying outflows. Very little research,
 however,  has been directed
 to comparing the observations against (even idealized) wind
-models.  Instead, researchers have tried to glean what limited information
+models.  Instead, researchers have gleaned what limited information
 is affored by direct analysis of the absorption lines.  The data do yield
@@
 orders of magnitude uncertainty.  Both the origin and impact of
-galactic-scale winds, therefore, remain open points of debate
+galactic-scale winds, therefore, remain open matters of debate
 \citep{debate}.
@@
 Recent studes of $z \sim 1$ star-forming galaixes have revealed that
-the cool gas often exhibits significant \ion{Mg}{2} emission in
+the cool gas often exhibits significant resonant-line emission (e.g.\
+\ion{Mg}{2}) in
 tandem with the nearly ubiquitous blue-shifted absorption
-\citep{wcp+09,rubin+10b}.  The resultant spectra resemble the P-Cygni
+\citep{wcp+09,rubin09,rubin+10b}.  The resultant spectra resemble the P-Cygni
 profile characteristic of stellar winds.
 \cite{rubin+10a} have also detected line
-emission from non-resonance \ion{Fe}{2}~$^*$ transitions and spatially
-extended \ion{Mg}{2} emission which they interpret as 
-photons scattered off the wind.  In one galaxy, they estimate that the
-wind extends to at least 5\,kpc from the galaxy.  Line emission is
-also observed for $z \sim 3$ LBGs via the resonant \lya\ transition
-and fine-strcuture \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
-A comprehensive analysis of these emission lines
-(e.g.\ via deep integral-field-unit observations) could yield unique
+emission from non-resonant \ion{Fe}{2}$^*$ transitions 
+Their interpretation is that the emission is the result of photons
+scattered off the wind into our sightline, analagous to P-Cygni.
+\cite{rubin+10a} also observed spatially extended \ion{Mg}{2} emission
+which they use to estimate the size of the outflow.  They infer that
+the wind extends to at least 5\,kpc from the galaxy.  Line emission is
+also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
+and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
+A comprehensive analysis of the emission lines
+related to galactic-scale outflows
+(e.g.\ via deep integral-field-unit observations) may offer unique
 diagnostics on the morphology and density of the outflow, eventually
 setting tighter constraints on the energetics of the flow.
-Although astrnomoers are rapidly producing a wealth of observational
+
+Although astronomers are rapidly producing a wealth of observational
 datasets on galactic-scale winds, a key ingredient to a proper
 analysis is absent.
-
 [Draw analaogy to exploring SN lightcurves and spectra]
@@
 properties.  Although the winds are idealized, the results frequently
-contradict our initial intuition and caution one [word] on the
-challenges of converting the observables to (even crude) physical
+contradict our intuition and 
+challenge the straightforward conversion of observables to (even crude) physical
 constraints.  [Add another line or two]
 
-[Outline of paper]
-
-[Point out IR emission from winds locally implies dust]
+The paper is organized as follows.  In $\S$~\ref{sec:method}, we
+describe the methodology of our radiative transfer algorithms.  These
+are applied to a fiducial wind model in $\S$~\ref{sec:fiducial} and
+variations of this model in $\S$~\ref{sec:variants}.  In
+$\S$~\ref{sec:alternate}, we explore wind models with a broader range
+of density and velocity laws.  Consideration of key observables is
+given in $\S$~\ref{sec:obs} and we discuss the principal results
+in $\S$~\ref{sec:discuss}.  A brief summary is given in
+$\S$~\ref{sec:summary}.
 
@@
 This is a necessarily limited
-set, but the two ions and their transitions have characteristic
-shared by the majority of low-ions 
+set, but the two ions and their transitions do have characteristics
+shared by the majority of low-ion transitions
 observed in cool-gas outflows. Therefore, many
@@
 
-In terms of radiative transfer, the [behaviour]
-of the \mgiid\ doublet
-is very similar to that for \ion{H}{1}
+In terms of radiative transfer, the 
+\mgiid\ doublet is very similar to that for \ion{H}{1}
 \lya, the \naid\ doublet, and many other doublets commonly
 studied in the interstellar medium (ISM) of distant galaxies.  
-Each of these has the ground-state connected by a pair of electric
+Each of these has the ground-state connected to a pair of electric
 dipole transitions with nearly identical energy.
@@
 separation is sufficiently small ($\Delta v = c \Delta E / E \approx
-1.3 \mkms$) that most radiative transfer treatments actually ignore that
-there are two transitions.   This is generally justifiable for \lya\ because 
+1.3 \mkms$) that most radiative transfer treatments actually ignore it
+is a doublet.
+This is generally justifiable for \lya\ because 
 most astrophysical processes have turbulent motions that
-significantly exceed its velocity separation and effectively mix the
+significantly exceed the doublet's velocity separation and effectively mix the
 two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
@@
 associated with this multiplet (\feiid)
-corresponding to $\Delta J = 0, -1$ indicated by upward (black) arrows
+corresponding to $\Delta J = 0, -1$; these are indicated by upward (black) arrows
 in Figure~\ref{fig:energy}. The solid (green) downward
@@
 
-The Figure also shows (as dashed downward arrows) two of the
-transitions that connect to higher energy levels of the \zconfig\
+The Figure also shows (as dashed, downward arrows) two of the
+\feiis\ transitions that connect to higher energy levels of the \zconfig\
 configuration.  Ignoring collisions and recombinations, these
@@
 near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
-following, we will assume that this does not occur.
+following, we will assume that this process does not occur.
 
@@
 energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
-density $n_c$ is very large.  For the \aconfig$_{9/2} \to
+density $n_c$ is large.  For the \aconfig$_{9/2} \to
 $\aconfig$_{7/2}$ transition, the critical density $n_e^C \approx 4
@@
 {\it absorption} from the
-fine-structure levels of the \aconfig\ configuration and that material
+fine-structure levels of the \aconfig\ configuration and even that material
 is not significantly blue-shifted \citep{rubin+10}.
@@
 meanwhile, is significantly higher implying 
-negligible collisional excitation.
+negligible collisional processes.
 
@@
 
-Nearly all of the absorption studies of cool-gas outflows 
+Nearly all of the absorption studies of galactic-scale outflows 
 have focused on intensely, star-forming galaxies.  The
@@
 should be aware that they can complicate the observed spectrum,
-independent of the galactic outflow, especially at velocities $v \approx 0 \mkms$.
+independent of the outflow, especially at velocities $v \approx 0 \mkms$.
 In the following, we will simply assume a flat continuum 
@@
 There is also empirical evidence for dust emission from galactic-scale
-outflows from near-IR emission \citep[e.g.][]{M87_dust}.
+outflows \citep[e.g.][]{M87_dust}.
 Because absorption line analysis is performed
-on normalized spectra, the effects of dust are largely minimized.  
-These effects are corrected for by simply rescaling the normalized
-flux.  For
+on normalized spectra, these effects of dust are largely minimized; 
+the effects are corrected by simply rescaling the normalized flux.  For
 scattered and resonantly trapped photons, however, the relative effect of dust
@@
 \citep[e.g.][]{shapley03}.  Although the transitions studied here have
-significantly lower opacity than \lya, dust could play an important role
+much lower opacity than \lya, dust could play an important role
 in the predicted profiles.
 
-In a few models, we include the absorption by dust under the following
+In a few models, we include absorption by dust under the following
 assumptions:
@@
 (iii) the photons absorbed by dust are re-emitted at IR wavelengths
-and `lost' from the system.  The dust absorption is normalized by \taud, 
+and are `lost' from the system.  The dust absorption is normalized by \taud, 
 the integrated opacity of dust from the center of the system to
@@
 \end{equation}
-and a velocity law
+and a velocity law with a purely radial flow
 
 \begin{equation}
-\vec v = v_r (r) \hat r = v_0 r \hat r \;\;\; , 
+\vec v = v_r (r) \hat r = v_0 r \hat r  \perd
 \label{eqn:vel}
 \end{equation}
-i.e., a purely radial flow.  Turbulent motions are
+Turbulent motions are
 characterized by a Doppler parameter $b_{\rm turb}$.  
@@
 r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
-is scaled down by the $f\lambda$ ratio but otherwise identical.  Similarly,
+(not plotted) is scaled down by the $f\lambda$ ratio but is otherwise identical.  Similarly,
 the optical depth profiles for the \feiid\ transitions are
@@
 ($\mbturb = 15 \mkms$) has a minor impact on the results.
-The absorption profiles are insensitive to \bturb\ and this parameter 
+The absorption profiles are insensitive to its value and varying \bturb\
 only tends to modify the widths and modestly
@@
 essentially unimportant provided they scale together to give nearly the same
-$\tau_{2796}$ velocity profile.  Therefore, one may consider the choices for
+$\tau_{2796}$ profile.  Therefore, one may consider the choices for
 $r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
@@
 source embedded within an outflow.  Strong absorption is evident at
-$v < -50 \mkms$ in both transitions (equivalent widths $W_{2796} =
-2.96$\AA\ and $W_{2803} = 1.29$\AA) and each shows emission at
+$v < -50 \mkms$ in both transitions (equivalent widths, $W_{2796} =
+3.0$\AA\ and $W_{2803} = 1.3$\AA) and each shows emission at
 positive velocities.  For this isotropic and dust-free model, the
@@
 
-Focusing further on the \ion{Mg}{2} absorption, one notes the profiles lie
+Focusing further on the \ion{Mg}{2} absorption, one notes that the profiles lie
 well above zero intensity and have similar depth even though their $f\lambda$
@@
 absorption profiles from Figure~\ref{fig:fiducial_1d} against an
-artificial model where no absorbed photons are not
+artificial model where no absorbed photons are 
 re-emitted.   As expected from the
@@
 absorption-line analysis that ignores these effects
-\citep[e.g.][]{smn+09} would (i) systematically underestimate the true optical
+would (i) systematically underestimate the true optical
 depth and (ii) falsely conclude that the wind partially covers the
@@
 Turning to the emission profiles of the \mgiid\ doublet, one notes
-that they are also similar and have comparable equivalent widths
-[word].  The
+that they are also similar with comparable equivalent widths The
 flux of the \mgiib\ transition even exceeds that for \mgiia\ giving a
@@
 thick for a significant portion of the profile. 
-The ultimate outcome is a conversion of some \mgiia\ photons into
-\mgiib\ photons.
 Furthermore, the flux from \mgiib\ exceeds the
@@
 \mgiia\ emission profile.  The relative strengths of the emission
-lines, therefore, is sensitive to both the opacity and velocity
+lines is sensitive to both the opacity and velocity
 extent of the wind.
@@
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \mkms$ producing the characteristic P-Cygni profile of
-an outflow.  Splitting
+emission at $v > 0 \mkms$ producing a characteristic P-Cygni profile. 
+Splitting
 the profile at $v = -50 \mkms$, we measure an equivalent width
@@
 \ion{Mg}{2} doublet occur because of the complex of non-resonant
-\ion{Fe}{2} transitions (Figure~\ref{fig:energy}).  Specfically,
+\ion{Fe}{2} transitions (Figure~\ref{fig:energy}).  Specifically,
 resonance photons absorbed at \feiid\ have a finite probability of
-being scattered as a non-resonant photon which escapes the system
+being re-emitted as a non-resonant photon which escapes the system
 without further interaction.  The principal effects are to reduce the
@@
 
-The reduced \feiia\ emission relative to \feiib\ results from the
-\ion{Fe}{2}$^*$ emission.
-The \feiia\ flux is reduced by two factors:
+The reduced \feiia\ emission relative to \feiib\ is related to
+two factors:
 (i) there is an additional downward transition from the
@@
 resonance line.  Therefore, the majority of photons absorbed at
-$\lambda 2600$ are re-emitted as \feiib\ photons whereas 
-the majority of photons absorbed as \feiia\ are re-emitted 
+$\lambda \approx 2600$ are re-emitted as \feiib\ photons whereas 
+the majority of photons absorbed at $\lambda \approx 2586$ are re-emitted 
 at longer wavelengths (\ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda
@@
 significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
-The total equivalent width, however, of the lines connected to the
+The total equivalent width, however, of the three lines connected to the
 \zconfig$_{7/2}$ upper level must still vanish (photons are conserved
@@
 model.  The output is a set of surface-brightness maps in a series of
-frequency channels; the
-dataset is analagous to integral-field-unit (IFU) observations.  In
+frequency channels yielding a
+dataset analagous to integral-field-unit (IFU) observations.  In
 Figure~\ref{fig:fiducial_ifu_mgii}, we present the output 
@@
 actually exceeds the source+wind emission at 
-$v = -250 \mkms$ such
-that the absorption profile is
+$v = -250 \mkms$ so that the absorption profile is
 negatively offset from the velocity where $\tau_{2796}$ is maximal
 (Figure~\ref{fig:fiducial_nvt}).
-The net result of the scattered photons is
-a weaker \ion{Mg}{2} profile that is offset from the true optical
-depth profile.  Clearly, the effects complicate estimates for the
+The net result is
+a weaker \ion{Mg}{2} absorption line peaks blueward of the peak in the
+optical depth profile.  Clearly, these effects complicate estimates for the
 speed, covering fraction, and total column density of the wind.  At $v
@@
 Similar results are observed for the \ion{Fe}{2} resonance
-transitions (Figure~\ref{fig:fiducial_ifu_feii2600}).
+transitions (Figure~\ref{fig:fiducial_ifu_feii}).
 For transitions to fine-structure levels of the \aconfig, the source
@@
 generated in the wind. 
-
-At all velocities, the majority of emission occurs at $r \le 5$\,kpc.
-A better assessment of the radial profiles is provided by
-Figure~\ref{fig:fiducial_cuts}, where we collapse the 
-azimuthally symmetric surface-brightness maps in
+The results presented in Figures~\ref{fig:fiducial_ifu_mgii} and
+\ref{fig:fiducial_ifu_feii} are sensitive to the radial extent,
+morphology, density and velocity profiles of this galactic-scale
+wind.  Consequenetly, IFU observations of line emission from low-ion
+transitions may offer the most direct constraints on galactic-scale
+wind properties.
+
+At all velocities, the majority of light comes from the inner regions
+of the wind. 
+Figure~\ref{fig:fiducial_cuts} presents the relative flux for the 
+azimuthally symmetric surface-brightness maps collapsed along
 one spatial dimension.  The majority of
@@
 is even more centrally concentrated for the \ion{Fe}{2} transitions.
-These distributions are [critically important] for observations
+A proper treatment of these
+distributions is critical to interpret observations
 acquired through a slit, i.e.\ where the aperture has a limited extent
 in one or more dimensions.  A standard longslit on 10m-class
-telescopes, for examples, subtends $\approx 1''$ corresponding to
+telescopes, for example, subtends $\approx 1''$ corresponding to
 $5-10$\,kpc for $z \sim 1$.    We return to this issue in
@@
 
-[Comment that an observation like constrains the radial extent +
-density/velocity profiles of the wind]
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Variations to the Fiducial Model}
+\label{sec:variants}
 
@@
 through modifications to the fiducial model.  These include relaxing
-the assumption of isotropy, introducing dust, and adding an ISM
-component within $r_{\rm inner}$.
+the assumption of isotropy, introducing dust, adding an ISM
+component within $r_{\rm inner}$, and varying the normalization of the
+optical depth profiles.
 
@@
 symmetric;  the sources driving the
-wind (e.g.\ supernovae, AGN) are very unlikely to be anisotropically distributed
+wind (e.g.\ supernovae, AGN) are very unlikely to be isotropically distributed
 within the galaxy.  
 Secondly, the galactic ISM frequently has a disk-like morphology
-which will suppress the wind preferntially at low galactic latitudes,
+which will suppress the wind preferentially at low galactic latitudes,
 perhaps yielding a bi-conic morphology \citep[e.g.][]{M87}.
-Lastly, the galaxy may be surrounded by an
+Lastly, a galaxy could be surrounded by an
 anisotropic gaseous halo that would produce an irregularly shaped
@@
 With these considerations in mind, we reanalyzed the fiducial model
-with the 3D algorithm after departing from isotopy.  It is beyond the
+with the 3D algorithm after departing from isotropy.  It is beyond the
 scope of this paper to explore a full suite of anisotropic profiles;
-the following simply assumes half of the fiducial wind, i.e.,  
-the density is set to zero for $2\pi$ steradians.
+the following simply assumes half of the fiducial wind by setting
+the density to zero for $2\pi$ steradians.
 We have viewed this system from $\theta = 0^\circ$ where
@@
 key difference from the isotropic wind is the absence of photons
-scattered to $v > 100 \mkms$;  this also implies a deeper 
-\mgiib\ absorption profile at $v \approx -100 \mkms$. The asymmetry
-shift in velocity centroid of the emission lines
-may provide a diagnostic of wind isotropy, especially when combined
-with the absorption profile [word].
-
-The results are very similar for the \feiid\ resonance lines.  The
+scattered to $v > 100 \mkms$;  this also implies deeper 
+\mgiib\ absorption at $v \approx -100 \mkms$. The 
+shift in velocity centroid and asymmetry of the emission lines
+serve to diagnose the degree of wind isotropy, especially in
+conjunction with analysis of the absorption profiles.
+
+The results are similar for the \feiid\ resonance lines.  The
 \ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows most clearly the
 offset in velocity between the source unobscured ($\theta = 0^\circ$)
-and source covered ($\theta = 180^\circ$) cases.  This line [shift]
-produces the most robust constrain on wind isotropy. [Observable: dust
-is a trade-off]
+and source covered ($\theta = 180^\circ$) cases.  The offset of the
+\feiis\ lines is the most significant 
+difference from the fully isotropic wind.
 
@@
 the photons.  This suppresses the flux at all
-wavelengths by $\approx \exp(-\mtaud)$, but because we normalize the profiles 
-this effect is essentially ignored.  Second, photons that are
+wavelengths by $\approx \exp(-\mtaud)$ but because we re-normalize the
+profiles, this effect is essentially ignored.  Second, photons that are
 scattered by the wind will travel a greater
-distance and suffer from greater extinction.  A photon that is
-trapped for many scatterings may have a high probability of being absorbed
+distance and therefore suffer from greater extinction.  A photon that is
+trapped for many scatterings may have a very high probability of being absorbed
 by dust.  This process is
@@
 associated with star-forming galaxies. 
-Section~\ref{sec:dust_method} describes our treatment of dust; we only
-remind the reader here that we assume a constant dust-to-gas ratio 
+Section~\ref{sec:dust_method} describes our treatment of dust; we 
+remind the reader that we assume a constant dust-to-gas ratio 
 normalized by the total optical
@@
 backside of the wind and must travel a longer path than other
-photons.  This creates a differential reddening that increases with wavelength (and
-velocity relative to line-center). It is a natural consequence of dust
-extinction;  the effect is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
-emission profile which is otherwise symmetrically distributed around
-$v \approx 0 \mkms$.   In terms of absorption, the profiles are
-nearly identical for $\mtaud \le 3$.  One requires a very high
-extinction to see an effect at $v \approx -100 \mkms$.
+photons.  Dust leads to a differential reddening that increases with wavelength (and
+velocity) relative to line-center. This is a natural consequence of dust
+extinction and is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
+emission profile which is symmetrically distributed around
+$v=0 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
+nearly identical for $\mtaud \le 3$.  One requiresvery high
+extinction to see a deepening of the profiles at $v \approx -100 \mkms$.
 
@@
 photons scatter one to a few times before exiting).
-To achieve qualitative changes, one requires an extreme level of
+For qualitative changes, one requires an extreme level of
 extinction ($\mtaud = 10$).  In this case, the source would be
@@
 $v \approx 0 \mkms$ in galaxies that exhibit outflows 
-\citep[e.g.][]{wcp+09,steidel+10,rubin+10b}.
+\citep[e.g.][]{wcp+09,rubin09,steidel+10}.
 On the other hand, the stars and \ion{H}{2} regions that comprise our
@@
 In Figure~\ref{fig:ISM_spec}, the solid curves show the \ion{Mg}{2} and
-\ion{Fe}{2} profiles for the ISM+wind (red) and fiducial (black)
+\ion{Fe}{2} profiles for the ISM+wind and fiducial 
 models. In comparison, the
@@
 There are, however, several qualitiative differences 
-for the \ion{Fe}{2} transitions between the ISM+wind and fiducial
-models.
-First,
-the \feiia\ transition shows much stronger absorption at $v \approx 0$
+for the \ion{Fe}{2} transitions. 
+First, the \feiia\ transition in the ISM+wind model
+shows much stronger absorption at $v \approx 0$
 to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
 the profile is not filled in by scattered photons. Instead, 
-the majority of \feiia\ photons absorbed are re-emitted as
+the majority of \feiia\ photons that are absorbed are re-emitted as
 \ion{Fe}{2}~$^* \lambda\lambda 2612, 2632$ photons.  In fact, the
@@
 (compare to the dotted lines); this transition provides a
-very good description of the ISM+wind opacity profile.  
+very good description of the intrinsic ISM+wind optical depth profile.  
 We conclude that resonant transitions tha are coupled to (multiple)
-non-resonant, electric dipole transitions may offer the best
+non-resonant, electric dipole transitions offer the best
 diagnostic of ISM absorption.
@@
 in the much higher strengths ($3-10\times$) of emission from
-transitions to the excited states of \aconfig.   This occurs because
-of : (1) the greater absorption in the \feiid\
+transitions to the excited states of \aconfig.   This occurs because:
+(1) there is greater absorption by the \feiid\
 resonance lines; (2) the high opacity of the ISM component leads to
 an enhanced conversion of resonance photons with $v \approx 0\mkms$
-into the non-resonance lines.  This is especially notable for the
+into \feiis\ photons.  This is especially notable for the
 \feiib\ transition whose `partner' shows an equivalent width nearly
@@
 
-[3D discussion]
+[3D discussion; Figure~\ref{fig:ISM_ifu}]
 
@@
 \section{Alternate Wind Models}
+\label{sec:alternate}
 
@@
 \section{Discussion}
+\label{sec:discuss}
 
@@
 [What does MgI tell us about winds?  Why no P-Cygni?]
+
+\section{Summary}
+\label{sec:summary}
 

### 2010-07-16 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5051 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+[Do dust too (as a green curve in Figure~\ref{fig:ISM_spec})]
+
+\subsection{Varying $n_{\rm H}^0$}
+
+[Consider a series of models with the optical depth varying]
+
 \subsection{Summary Table}
@@
 for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
-the fiducial model and a set of the variations.  Listed are the
-equivalent wdiths (absorption and emission), the peak optical depth
+the fiducial model ($\S$~\ref{sec:fiducial}) and a set of the models
+presented in this section.  Listed are the
+equivalent widths (absorption and emission), the peak optical depth
 for the absorption $\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the
 velocity where the optical depth peaks $v_\tau$, the optical
-depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv v
+depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv \, v
 \ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in
@@
 
-One observes a wide range in these measures.  This emphasize the
-challenge in converting the absorption/emission data to physical
-constraints on wind schenarios.  We return to further consider these
-results in $\S$~\ref{sec:obs}.
+One observes a wide range in these measures.  This emphasizes the
+challenges to convert 1D spectra to physical
+constraints on wind scenarios.  We consider these
+results further in $\S$~\ref{sec:obs}.
 
@@
 of other power-law expressions.
+We consider three different density laws ($n_{\rm H}(r) \propto
+r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr(r)
+\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
+(Table~\ref{tab:plaws}, Figure~\ref{fig:plaws}a).  [Comment in the Table how $\mvr$ is
+different when the velocity law is positive]  
+The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
+modified to yield an \mgiia\ optical depth profile that peaks at
+$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
+$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b).
+
+[Discuss models]
+
+[Refer to Table~\ref{tab:plaw_diag}]
 
 \subsection{Radiation Pressure}
+
+[Kate: Write the details of velocity + density law]
 
@@
 
+Figure~\ref{fig:rad_nvt}, \ref{fig:rad_spec}
+
 \subsection{The Lyman Break Galaxy Model}
@@
 exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
-etc.\ transitions with speeds up to 1000\kms\
-\citep[e.g.][]{lkg+97,pks+98,steidel+10}.
+etc.\ transitions with speeds up to 1000\,\kms\
+\citep[e.g.][]{lkg+97,pks+98}.
 Researchers have invoked these winds to explain enrichment of
@@
 explain jointly the average absorption they observed
-toward a set of several hundred LBGs and the average absorption in cool gas
+toward a set of several hundred LBGs and the average absorption in gas
 observed transverse to these galaxies.  
@@
 expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
-fraction of optically thick gas $f_c(r)$.  For the latter, S10
+fraction of optically thick `clouds' $f_c(r)$.  For the latter, S10
 envision an 
-ensemble of small, optically thick clouds $(\tau \gg 1)$ that only
-partially cover the galaxy.
+ensemble of small, optically thick $(\tau \gg 1)$ clouds that only
+partially cover a galactic-scale source (i.e.\ a few to 10\,kpc).
 For the velocity law, they adopted the following functional
@@
 
-The covering fraction of optically thick cold gas, meanwhile, was assumed to have
+The covering fraction of optically thick clouds, meanwhile, was assumed to have
 the functional form
@@
 profile determined from the Sobolev approximation.  We then apply 
-the methodology used for the other wind models.  In the other model,
+the Monte Carlo methodology used for the other wind models to predict
+\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other model,
 we modify our algorithms to more precisely mimic the concept of an
-ensemble of optically thick clouds with a partial covering fraction.
+ensemble of optically thick clouds with a partial covering fraction on
+galactic scales.
 
@@
 calculation is shown as a dotted red curve in
-Figure~\ref{fig:LBG_Sobolev}b which is an excellent
+Figure~\ref{fig:LBG_Sobolev}b; it is an excellent
 match to the desired profile (black curve).
 To calculate the optical depth profiles for the other transitions, we
-assume $\mnfe = \mnmg/2$ and scale $\tau$ by $f\lambda$.
+assume $\mnfe = \mnmg/2$ and scale $\tau$ by the $f\lambda$ product.
 
@@
 should focus on the \mgiia\ transition.  The dotted line in the Figure
-shows the intensity profile for the model when one ignores re-emission
+shows the intensity profile when one ignores re-emission
 of absorbed photons.  By construction, it follows\footnote{Note that
   one should not make this comparison for the other transitions in
-  this Sobolev model because those are scaled down by $f\lambda$ and
+  the Sobolev model because those are scaled down by $f\lambda$ and
   for \ion{Fe}{2} the reduced Fe$^+$ abundance.} the profile
@@
 [Do CIV scattered photons bugger up the P-Cygni analysis of Pettini
-et al. ?]
+et al. ? I bet they do!]
 
@@
 The LBG-Sobolev model, however, differs from
-the one proposed by S10:  they proposed an ensemble of optically
+the one proposed by S10:  these authors proposed an ensemble of optically
 thick clouds with the (parital) covering fraction described by
@@
 the absorption profiles at $v \approx 0 \mkms$ and yield significant
-emission lines at $v \gtrsim 0 \mkms$ in the resonance lines and at
-all velocities for the \ion{Fe}{2}$^*$ transitions.  For \feiia,
+emission lines at $v \gtrsim 0 \mkms$ in the resonance
+lines. Furthermore, significant emission is observed at
+all velocities for the \feiis\ transitions.  For \feiia,
 the majority of absorbed photons have been converted to its
@@
 The equivalent width of \feiia\ even exceeds that for \feiib, an
-inversion that if observed would strongly support this model.
+inversion that, if observed, would strongly support this model.
 [Could SiII or OI do the same?]
@@
 Figure~\ref{fig:LBG_spec} (via \mgiia), we note nearly identical
-results.  The differencs that occur for the other transitions,
-meanwhile, are only because their opacities are scaled downward in the
+results.  The differences that occur for the other transitions,
+meanwhile, are only because the opacities are scaled downward in the
 Sobolev model (as required).  [Do the data prefer one to the other?
@@
 partical covering models (for \mgiia), we are motivated to consider
-further the characteristics of the Sobolev model which offers a
-density profile.  It is straightforward to convert the density and
-velocity profiles into distributions of mass, energy, and momentum in
+further the characteristics of the Sobolev model which has the
+distinct advantage of producing a 
+density profile.  It is straightforward, then, to convert the density and
+velocity profiles into distributions of mass, energy, and momentum
+within
 the wind.  These are shown in cumulative form in
@@
 two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
-assumes a very poorly constrained scalar factor of $10^{5.7}$.  One
+assumes a very poorly constrained scalar factor of $10^{5.47}$.  One
 should give minimal weight to the absolute values for any of the
@@
 \begin{figure}
-\epsscale{0.8}
+\epsscale{0.95}
 \plotone{Figures/energy_levels.ps}
@@
 electric-dipole transitions. 
-The downward (green) arrows show the transitions that are connected to the
+The downward (green) arrows show the \feiis\ transitions that are connected to the
 resonance-line transitions (i.e.\ they share the same upper energy
-levels).  We also show a pair of levels (\ion{Fe}{2}~$\lambda\lambda
+levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
 2618,2631$) that arise from higher levels in the \zconfig\
@@
 the opacity at small and discrete radial intervals in velocity space
-and then converted to radius with the velocity law.  One notes that
+and was then converted to radius with the velocity law.  One notes that
 the wind is optically thick at the inner radius ($r_{\rm inner} =
@@
 that even though the peak optical depth of the \ion{Mg}{2} transitions
-is nearly 30 at $v \approx -70 \mkms$, photons scattered off the outflow
-fill in the absorption.
+is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
+photons scattered off the outflow fill in the absorption.
 (Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
@@
 absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission occurs.   These profiles have been `filled
+re-emission occurs.   The true profiles have been `filled
 in' significantly by light scattered in the wind.  Ignoring this
@@
 optical depth and (incorrectly) conclude that the source is partly covered by the
-gas.  It is essential, therefore, to account for the effects of
-scattered/re-emitted photons in a proper analysis of the absorption
-profiles of cool gas outflows.
+gas.  
 }
@@
 entirely due to photons scattered by the wind.  Impressively, this
-emission exceeds the integrated flux at $v = -250\mkms$. At $v \ge 0
+emission exceeds the integrated flux at $v = -250\mkms$ such that the
+line center is offset from the peak optical depth.  At $v \ge 0
 \mkms$,  both the source and wind contribute to the observed emission.
@@
 \epsscale{0.8}
-\plotone{Figures/fig_fiducial_ifu_feii2600.ps}
-\plotone{Figures/fig_fiducial_ifu_feii2612.ps}
-\caption{
-(a) Surface-brightness emission maps around the \feiib\ transition for the
+\plotone{Figures/fig_feii_ifu.ps}
+\caption{
+(Upper) Surface-brightness emission maps around the \feiib\ transition for the
 source+wind complex.  The middle panel shows the 1D spectrum with $v=0
@@
 (Figure~\ref{fig:fiducial_ifu_mgii}).
-(b) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
+(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
 2612$ transition for the 
@@
 uncovered) to $\theta = 180^\circ$ (source covered).  One detects
-significant emission for all orientations of this wind. The velocity
-centroid of this 
+significant emission for all orientations of this wind but significant
+absorption only for $\theta \ge 90^\circ$.
+The velocity centroid of the 
 emission shifts from positive to negative velocities as $\theta$
-increases.  The absorption reaches a maximum at $\theta > 100^\circ$
-and disappears for $\theta = 0^\circ$.
+increases and one transitions from viewing the wind to be behind the
+source to in front.  The velocity centroid of emission, therefore, may
+give a robust measure of wind isotropy.
 }
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-model (black) against a series of models that include the effects of
-dust extinction parameterized by \taud.  The primary difference is the suppression of line
-emission relative to the continuum (again, normalized to unit value).
+model (black) against a series of models that include 
+dust extinction.  The primary effect is suppression of
+the line-emission relative to the continuum. 
 A more subtle but important effect is that the redder photons in the
@@
 line-center) suffer greater extinction.  This is most evident in the
-\feiic\ emission line and occurs because these photons must
-travel further to scatter off the backside of the wind.  Note that
+\feiic\ emission line; it occurs because these photons must
+travel farther to scatter off the backside of the wind.  Note that
 the absorption lines are nearly unmodified until $\mtaud = 10$, a
@@
 \mgiia\ optical depth profiles (solid; black) for the ISM+wind
-model.  The wind is identical to the fiducial model
-(Figure~\ref{fig:fiducial_nvt}) but this model also includes an ISM component
+model.  The wind is identical to that from the fiducial model
+(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
 with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
@@
 The dotted line traces the predicted absorption profile in the absence
-of any re-emission of absorbed photons.
+of re-emission and scattering.
 Regarding the \ion{Mg}{2}~doublet, the primary difference between the
 ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
-in the emission lines from $\mvr \approx 0 \mkms$ for the fiducial
-model to $\mvr \approx +100\mkms$ for the ISM+wind model. 
-The \ion{Fe}{2} profiles, however, show qualitative differences from
+in the emission lines from $v \approx 0 \mkms$ for the fiducial
+model to $v \approx +100\mkms$ for the ISM+wind model. 
+For the ISM+wind model, 
+the \ion{Fe}{2} profiles show qualitative differences. 
 the ISM model.  The \feiid\ resonance transitions each exhibit much
 greater absorption at $v \approx 0 \mkms$ than the fiducial model.
-This emission associated with these lines is also substantially
+The resonant line-emission is also substantially
 reduced, implying much higher fluxes for the non-resonant lines (e.g.\
@@
 absorption profile that very nearly matches the input opacity profile.
-We conclude that fine-structure transitions may offer the best
+We conclude that resonance transitions that are strongly coupled to
+non-resonant lines offer the best
 characterization of an ISM component.
@@
 \label{fig:ISM_spec}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_ism_ifu.ps}
+\caption{
+Surface-brightness emission maps for ISM+wind model
+}
+\label{fig:ISM_ifu}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_vary_profiles.ps}
+\caption{
+Power-law profiles
+}
+\label{fig:plaws}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
+\caption{
+Power-law profiles spectral lines
+}
+\label{fig:plaws_spec}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_radiation_nvt.ps}
+\caption{
+Radiation diagnosed
+}
+\label{fig:rad_nvt}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_rad_spec.ps}
+\caption{
+Radiation spec
+}
+\label{fig:rad_spec}
 \end{figure}
@@
 \caption{
-{\it Upper:} The dotted curve shows the velocity law for the LBG model
+(a) The dotted curve shows the velocity law (values are labelled on the
+right side) for the LBG model
 of S10.  Note how rapidly the velocity rises from $r =
-1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the gas
+1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
+Mg$^+$ gas
 density derived from 
-the average absorption profile of LBG galaxies (lower panel).
+the average absorption profile of LBG galaxies (see below).
 The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
-steepends to $(r/{\rm kpc}-1)^{-1.8}$.
-{\it Lower:} Average absorption profile for LBG cool gas absorption as
+steepens to $(r/{\rm kpc}-1)^{-1.8}$.
+(b) Average absorption profile for LBG cool gas absorption as
 measured and defined by S10
 (black solid curve).  Overplotted on this curve is a (red) dotted line that
-shows the absorption profile dervied from the density (and velocity)
-law shown in the upper panel.  The excellent agreement confrims the
+shows the \mgiia\ absorption profile dervied from the density (and velocity)
+law shown in the upper panel.  The excellent agreement confirms the
 validity of the Sobolev approximation.
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
-LBG models considered in the text: (red) the profiles for the density
-law derived from the Sobolev approximation using the average LBG
-absorption profile and (black) a model constructed to faithfully
-correspond to the wind model advocated by S10.  The dotted line,
-meanwhile, shows the absorption profiles of the latter model where one
-ignores scattered and re-emitted photons.  Similar to the fiducial
+LBG models considered: (red) the profiles from the 
+Sobolev approximation 
+and (black) a model constructed to faithfully
+correspond to the wind model advocated by S10.  The dotted line
+shows the absorption profiles of the latter model if one were
+to neglect scattered and re-emitted photons.  Similar to the fiducial
 model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
 significantly modify the absorption profiles (especially \ion{Mg}{2})
-and produce significant emission lines.  There is remarkable agreement
+and produce significant emission lines.  
+The result, for \ion{Mg}{2} especially, is a set of profiles that do
+not match the average observed LBG absorption profile.
+Note the excellent agreement
 between the \mgiia\ profile for the two models. [Cast doubt on S10
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_lbg_cumul.ps}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_lbg_cumul.ps}
 \caption{

### 2010-07-16 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc

@@ -27,7 +27,7 @@ int    n_phi     =    1;      // number of phi bins
 double r_inner   =  1.0;      // inner boundary radius, in kpc
 double r_outer   = 20.0;      // outer boundary radius, in kpc
 double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  5e-2;     // number density at inner boundary (cm^-3)
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
 double v_parm    =  1.0;      // power law of velocity profile
 double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
 double v_rval    = r_outer;

### 2010-07-16 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_mgii.cc

@@ -24,7 +24,7 @@ int    n_phi     =    1;      // number of phi bins
 double r_inner   =  1.0;      // inner boundary radius, in kpc
 double r_outer   = 20.0;      // outer boundary radius, in kpc
 double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  5e-2;     // number density at inner boundary (cm^-3)
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
 double v_parm    =  1.0;      // power law of velocity profile
 double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
 double v_rval    = r_outer;

### 2010-07-16 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5052 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 models.  Instead, researchers have gleaned what limited information
-is affored by direct analysis of the absorption lines.  The data do yield
+is afforded by direct analysis of the absorption lines.  The data do yield
 robust measurements of the speed of the gas yet they poorly constrain the
@@
 
-Recent studes of $z \sim 1$ star-forming galaixes have revealed that
+Recent studies of $z \sim 1$ star-forming galaxies have revealed that
 the cool gas often exhibits significant resonant-line emission (e.g.\
@@
 Their interpretation is that the emission is the result of photons
-scattered off the wind into our sightline, analagous to P-Cygni.
+scattered off the wind into our sightline, analogous to P-Cygni.
 \cite{rubin+10a} also observed spatially extended \ion{Mg}{2} emission
@@
 analysis is absent.
-[Draw analaogy to exploring SN lightcurves and spectra]
+[Draw analogy to exploring SN lightcurves and spectra]
 
@@
 and emission properties of cool gas outflows.  Using Monte Carlo
-radiative transfer technqiues, we study the nature of \ion{Mg}{2} and
+radiative transfer techniques, we study the nature of \ion{Mg}{2} and
 \ion{Fe}{2} absorption and emission for winds with a range of
@@
 exhibits an alkali doublet of transitions at $\lambda \approx
-2800$\AA\ analagous to the
+2800$\AA\ analogous to the
 \lya\ doublet of neutral hydrogen.  Figure~\ref{fig:energy}
@@
 \ion{Mg}{2} electric-dipole transitions 
-with wavelengths near 2800\AA\ and the transtion connecting
+with wavelengths near 2800\AA\ and the transition connecting
 the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
@@
 into 5 levels, 
-labelled by the total angular momentum $J$, 
+labeled by the total angular momentum $J$, 
 with excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
@@
 configuration.  This set of transitions (named the
-UV1 mutliplet) have wavelengths near 2600\AA.
+UV1 multiplet) have wavelengths near 2600\AA.
 There are two resonance-line transitions\footnote{We adopt the
@@
   transition connected to the ground-state.  We also label
-  non-resonsant transitions with an asterisk, e.g.\ \feiic.} 
+  non-resonant transitions with an asterisk, e.g.\ \feiic.} 
 associated with this multiplet (\feiid)
@@
 connected to
-the upper energy levels of the resonance lines.  These transitons may
+the upper energy levels of the resonance lines.  These transitions may
 occur following the absorption of a single photon by Fe$^+$ in its
@@
 have focused on intensely, star-forming galaxies.  The
-intrinsic emisison of these galaxies is a complex combination of
+intrinsic emission of these galaxies is a complex combination of
 stars and \ion{H}{2} regions that is then modulated by dust and gas
@@
 1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
-and \nfe=\nmg/2. At the center of the wind is a homogenous source of
+and \nfe=\nmg/2. At the center of the wind is a homogeneous source of
 continuum photons with size $r_{\rm source}$. These parameters are
@@
 0 \mkms$ by photons scattered in the wind.  To study the spatial
-extent of this emission, we perfomed 3D calculations with the fiducial
+extent of this emission, we performed 3D calculations with the fiducial
 model.  The output is a set of surface-brightness maps in a series of
 frequency channels yielding a
-dataset analagous to integral-field-unit (IFU) observations.  In
+dataset analogous to integral-field-unit (IFU) observations.  In
 Figure~\ref{fig:fiducial_ifu_mgii}, we present the output 
@@
 morphology, density and velocity profiles of this galactic-scale
-wind.  Consequenetly, IFU observations of line emission from low-ion
+wind.  Consequently, IFU observations of line emission from low-ion
 transitions may offer the most direct constraints on galactic-scale
@@
 Examining the \mgiid\ doublet, 
-there is no attenutation of the source by the wind for $\theta =
+there is no attenuation of the source by the wind for $\theta =
 0^\circ$
@@
 normalized by the total optical
-depth \taud\ that a photon would experience if it travelled from the
+depth \taud\ that a photon would experience if it traveled from the
 source to infinity without scattering.
@@
 $v=0 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
-nearly identical for $\mtaud \le 3$.  One requiresvery high
+nearly identical for $\mtaud \le 3$.  One requires very high
 extinction to see a deepening of the profiles at $v \approx -100 \mkms$.
@@
 with a greater extinction at higher velocities relative to line-center.
-In these respects, dust extinction crudely mimics the behavior of the anistropic
+In these respects, dust extinction crudely mimics the behavior of the
+anisotropic
 wind described in Section~\ref{sec:anisotropic}. [Is there a
@@
 fact, the ISM+wind model is nearly identical to the fiducial model;
-the only quantitiative difference is that the velocity centroid of
+the only quantitative difference is that the velocity centroid of
 the emission lines are shifted redward by $\approx +100 \mkms$.
 
-There are, however, several qualitiative differences 
+There are, however, several qualitative differences 
 for the \ion{Fe}{2} transitions. 
@@
 Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
-diffuse medium with unit convering fraction and a radial density
+diffuse medium with unit covering fraction and a radial density
 profile determined from the Sobolev approximation.  We then apply 
@@
 The principal result is that the scattering and re-emission of
-absorbed photons signficantly alters the predicted absorption profiles
+absorbed photons significantly alters the predicted absorption profiles
 for the inputted model.  This is, of course, an unavoidable
@@
 the one proposed by S10:  these authors proposed an ensemble of optically
-thick clouds with the (parital) covering fraction described by
+thick clouds with the (partial) covering fraction described by
 Equation~\ref{eqn:covering} whereas the Sobolev model assumes
@@
 Given the essentially perfect correspondence between the Sobolev and
-partical covering models (for \mgiia), we are motivated to consider
+partial covering models (for \mgiia), we are motivated to consider
 further the characteristics of the Sobolev model which has the
@@
 profiles like these against observations to constrain characteristics
-of the wind (e.g.\ raidal extent, energetics).  In this section we
+of the wind (e.g.\ radial extent, energetics).  In this section we
 consider a few observables and their dependence on the wind properties.
@@
 Each transition shown is
-labelled by its rest wavelength (\AA) and Einstein A-coefficient
+labeled by its rest wavelength (\AA) and Einstein A-coefficient
 (s$^{-1}$). Black upward arrows
@@
 Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
-characteritic of an outflow with significant absorption blueward of
+characteristic of an outflow with significant absorption blueward of
 line-center (dashed vertical lines) extending to $v = -1000\mkms$
@@
 Surface-brightness emission maps around the \mgiia\ transition for the
-source+wind complex of the fiducial model.  The middel panel shows the 1D spectrum with $v=0
+source+wind complex of the fiducial model.  The middle panel shows the
+1D spectrum with $v=0 
 \mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
@@
 \caption{
-(a) The dotted curve shows the velocity law (values are labelled on the
+(a) The dotted curve shows the velocity law (values are labeled on the
 right side) for the LBG model
@@
 (black solid curve).  Overplotted on this curve is a (red) dotted line that
-shows the \mgiia\ absorption profile dervied from the density (and velocity)
+shows the \mgiia\ absorption profile derived from the density (and velocity)
 law shown in the upper panel.  The excellent agreement confirms the

### 2010-07-22 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5064 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -28,7 +28,7 @@ double r_ISM   =  0.5;      // inner boundary of ISM, in kpc
 double n_ISM = 1.;           // Density (constant) of ISM gas (cm^-3)
 double v_ISM = 100.;           // Random (uniform) velocity of ISM
 //double ISM_doppler    =   15*1e5;              
-double ISM_doppler    =   40*1e5;              
+double ISM_doppler    =   40*1e5;    // Doppler in the ISM region (cm/s)          
 
 // Wind parameters
 double r_inner   =  1.0;      // inner boundary radius, in kpc

### 2010-07-22 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_feii.cc

@@ -16,8 +16,8 @@ double n_photons =  1e6;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_start   =  2573;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2637;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins

### 2010-07-22 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5065 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -316,6 +316,7 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
+		lam = lam*(1 + v_doppler/C_LIGHT*(uvec[0]*D[0] + uvec[1]*D[1] + uvec[2]*D[2]));
 		sum = -9e9;  // Kludge to avoid 'break'
 	      }
 	    }

### 2010-07-22 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5066 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -12,12 +12,12 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_start   =  2573;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2637;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins

### 2010-07-22 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5067 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -313,6 +313,7 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
+		lam = lam*(1 + v_doppler/C_LIGHT*(uvec[0]*D[0] + uvec[1]*D[1] + uvec[2]*D[2]));
 		sum = -9e9;  // Kludge to avoid 'break'
 	      }
 	    }

### 2010-07-23 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5069 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -342,7 +342,7 @@ void Run_Monte_Carlo(char *outfile)
     }
 
     // Count un-absorbed photons
-    if (flg_scatter == 0) 
+    if (flg_scatter == 0 && dust_scatter == 0) 
       {
       l_obs = lam_emit;
       E_obs = E_p;

### 2010-07-23 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc

@@ -221,7 +221,7 @@ void Run_Monte_Carlo(char *outfile)
 	if (l_step < step) {step = l_step; scatter = l; }
       }
 
-      // get distance to dust scatter/absorption
+      // Calculate dust opacity and check for absorption
       tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
       tau_x = KPARSEC*dens_H*dust_norm*dust_cs;
       d_step = tau_r/tau_x;
@@ -319,8 +319,8 @@ void Run_Monte_Carlo(char *outfile)
       spectrum.Count(t_obs,l_obs,m_obs,p_obs,E_obs);
     }
 
-    // Count un-absorbed photons
-    if (flg_scatter == 0) 
+    // Count un-absorbed photons (and not dust absorbed)
+    if (flg_scatter == 0 && dust_scatter == 0) 
       {
       l_obs = lam_emit;
       E_obs = E_p;

### 2010-07-23 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_feii.cc

@@ -16,8 +16,8 @@ double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_start   =  2573;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2639;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -143,8 +143,8 @@ double Get_Density(double *x, double r)
 void Run_Monte_Carlo(char *outfile)
 {
   // local variables
-  int i,j, l, ind, scatter, dust_scatter, count_it;
-  double x, lam_loc, xloc,lam;
+  int i,j, l, ind, scatter, dust_scatter, count_it, flg_scatter;
+  double x, lam_loc, xloc,lam, lam_emit;
   double r[3], D[3];
   double mu,phi,sin_theta;
   double tau_r, tau_x, step, r_sq;
@@ -184,6 +184,8 @@ void Run_Monte_Carlo(char *outfile)
     Emit(r,D,r_emit);
     // initial wavelength
     lam = l_start + (l_stop-l_start)*gsl_rng_uniform(rangen);
+    lam_emit = lam;
+    flg_scatter = 0;
 
     // propogate until escaped
     while (1)
@@ -238,6 +240,7 @@ void Run_Monte_Carlo(char *outfile)
       // if we line scattered, do it
       if (scatter >= 0)
       {
+	flg_scatter = 1;
 	xloc = (lam_loc/lines.lambda(scatter) - 1)*C_LIGHT/v_doppler;
 
 	// Get three velocity components of scatterer
@@ -329,6 +332,17 @@ void Run_Monte_Carlo(char *outfile)
       p_obs = atan2(D[0],D[1]);
       if (p_obs < 0) p_obs += 2*PI;
       spectrum.Count(t_obs,l_obs,m_obs,p_obs,E_obs);
+    }
+
+    // Count un-absorbed photons
+    if (flg_scatter == 0) 
+      {
+      l_obs = lam_emit;
+      E_obs = E_p;
+      m_obs = D[2];
[…]

### 2010-07-23 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_mgii.cc

@@ -33,7 +33,7 @@ double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
-double dust_albedo = 0.4;         // ratio of scattering to absorption
+double dust_albedo = 0.0;         // ratio of scattering to absorption
 
 
 // line parameters
@@ -132,8 +132,8 @@ double Get_Density(double *x, double r)
 void Run_Monte_Carlo(char *outfile)
 {
   // local variables
-  int i, l, ind, scatter, dust_scatter, count_it;
-  double x, lam_loc, xloc,lam;
+  int i, l, ind, scatter, dust_scatter, count_it, flg_scatter;
+  double x, lam_loc, xloc,lam, lam_emit;
   double r[3], D[3];
   double mu,phi,sin_theta;
   double tau_r, tau_x, step, r_sq;
@@ -172,6 +172,8 @@ void Run_Monte_Carlo(char *outfile)
     Emit(r,D,r_emit);
     // initial wavelength
     lam = l_start + (l_stop-l_start)*gsl_rng_uniform(rangen);
+    lam_emit = lam;
+    flg_scatter = 0;
 
     // propogate until escaped
     while (1)
@@ -223,6 +225,7 @@ void Run_Monte_Carlo(char *outfile)
       // if we line scattered, do it
       if (scatter >= 0)
       {
+	flg_scatter = 1;
 	xloc = (lam_loc/lambda_0[scatter] - 1)*C_LIGHT/v_doppler;
 
 	// Get three velocity components of scatterer
@@ -296,6 +299,17 @@ void Run_Monte_Carlo(char *outfile)
       p_obs = atan2(D[0],D[1]);
       if (p_obs < 0) p_obs += 2*PI;
       spectrum.Count(t_obs,l_obs,m_obs,p_obs,E_obs);
+    }
+
+    // Count un-absorbed photons
+    if (flg_scatter == 0) 
+      {
+      l_obs = lam_emit;
+      E_obs = E_p;
+      m_obs = D[2];
+      p_obs = atan2(D[0],D[1]);
+      if (p_obs < 0) p_obs += 2*PI;
+      spectrum.Scatter(t_obs,l_obs,m_obs,p_obs,E_obs);
     }
   }
   

### 2010-07-23 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_feii.cc

@@ -17,7 +17,7 @@ double stepsize  = 0.01;   // maximum size of photon step
 
 // output spectrum parameters
 double l_start   =  2573;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2637;     // photon ending wavelength (Angstroms)
+double l_stop    =  2639;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -311,6 +311,7 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
+		lam = lam*(1 + v_doppler/C_LIGHT*(uvec[0]*D[0] + uvec[1]*D[1] + uvec[2]*D[2]));
 		sum = -9e9;  // Kludge to avoid 'break'
 	      }
 	    }

### 2010-07-23 Winds/papers/Theory/First/Analysis/Doppler/outflow_doppler_mgii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5070 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -234,7 +234,7 @@ void Run_Monte_Carlo(char *outfile)
       r_sq = r[0]*r[0] + r[1]*r[1] + r[2]*r[2];
       if (r_sq > r_outer*r_outer) {count_it = 1; break;}
       // see if we've gone under inner boundary
-      if (r_sq < r_emit*r_emit) {count_it = 0; break; }
+      // if (r_sq < r_emit*r_emit) {count_it = 0; break; }
 
       // if we line scattered, do it
       if (scatter >= 0)

### 2010-07-23 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_feii.cc

@@ -235,7 +235,7 @@ void Run_Monte_Carlo(char *outfile)
       r_sq = r[0]*r[0] + r[1]*r[1] + r[2]*r[2];
       if (r_sq > r_outer*r_outer) {count_it = 1; break;}
       // see if we've gone under inner boundary
-      if (r_sq < r_emit*r_emit) {count_it = 0; break; }
+      // if (r_sq < r_emit*r_emit) {count_it = 0; break; }
 
       // if we line scattered, do it
       if (scatter >= 0)

### 2010-07-23 Winds/papers/Theory/First/Analysis/Fiducial/outflow_fiducial_mgii.cc

@@ -220,7 +220,7 @@ void Run_Monte_Carlo(char *outfile)
       r_sq = r[0]*r[0] + r[1]*r[1] + r[2]*r[2];
       if (r_sq > r_outer*r_outer) {count_it = 1; break;}
       // see if we've gone under inner boundary
-      if (r_sq < r_emit*r_emit) {count_it = 0; break; }
+      // if (r_sq < r_emit*r_emit) {count_it = 0; break; }
 
       // if we line scattered, do it
       if (scatter >= 0)

### 2010-07-23 Winds/papers/Theory/First/Analysis/Normalize/outflow_norm_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5071 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,450 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+#include "lines.hh"
+
+LINES lines;
+
+// monte carlo parameters
+double n_photons =  2e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2573;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2639;     // photon ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
[…]

### 2010-07-23 Winds/papers/Theory/First/Analysis/Normalize/outflow_norm_mgii.cc

@@ -1,0 +1,417 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  1e-1;     // number density at inner boundary
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
+double lambda_0[]   = {2796.352, 2803.531};  
+// line oscillator strengths
+double f_lu[]       = {0.6123,     0.3054}; 
[…]

### 2010-07-24 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5064 ac11df5e-a788-c23b-a8e1-c758c323924d
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5072 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
        \item Not a robust predictor of $f_c$
+       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
      \end{itemize}
@@
        \item Generally get the full extent of the wind speed
+       \item Plot $v_{pk}$ vs $\tau_{pk}$
      \end{itemize}
@@
        \item $f\lambda$ matters, but so do emission channels
+       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
      \end{itemize}
@@
        \item Flux + relative
+       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
     \end{itemize}
@@
 \label{sec:discuss}
+
+1)  Emission is a generic prediction of wind models (and something
+which has been essentially ignored aside from \lya).  We can discuss
+the caveats (dust, finite slit size, intrinsic spectrum).
+
+2)  Emission complicates the analysis of absorption at v$\sim$0 km/s, especially in
+resonantly trapped transitions (e.g. MgII, NaI).   This affects tau\_pk,
+C\_f and also offsets the line centroids (e.g. FeII, MgII).  These
+are primarily negative effects.
+
+3)  Emission can be used for good!   This is largely an extension of
+your emission paper, of course.
+
+   (i)  Morphology [MgII is likely best]
+  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
+ (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
 

### 2010-07-24 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc

@@ -296,7 +296,7 @@ void Run_Monte_Carlo(char *outfile)
       {
 	double z =  gsl_rng_uniform(rangen);
 	if (z > dust_albedo) {count_it = 0; break; }
-	// choose new isotropic direction
+	// choose new isotropic direction (not used)
  	mu  = 1 - 2.0*gsl_rng_uniform(rangen);
  	phi = 2.0*PI*gsl_rng_uniform(rangen);
  	sin_theta = sqrt(1 - mu*mu);

### 2010-07-24 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_feii.cc

@@ -12,12 +12,12 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  2575;     // photon beginning wavelength (Angstroms)
-double l_stop    =  2635;     // photon ending wavelength (Angstroms)
+double l_start   =  2573;     // photon beginning wavelength (Angstroms)
+double l_stop    =  2639;     // photon ending wavelength (Angstroms)
 double l_delta   =   0.1;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
@@ -46,7 +46,9 @@ double wind_doppler    =   15*1e5;
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
 double omnl = 1-n_law;
-double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double NH_wind   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double NH_ism    =  n_ISM * (r_inner-r_ISM);
+double NH_colm   =  NH_ism + NH_wind;
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 
@@ -79,6 +81,13 @@ int verbose;             // output parameter
 //--------------------------------------------
 int main(int argc, char **argv)
 {
+
+  // Input dust (optional),  Photons are inputted two (required)
+  if(argc > 2) {
+    dust_tau = atof(argv[1]);
+    dust_norm   =  dust_tau / dust_cs /  NH_colm / KPARSEC ;
+    n_photons = atof(argv[2]);
+  }
 
   lines.Init("fe_uv1.lines");
 
@@ -198,6 +207,8 @@ void Run_Monte_Carlo(char *outfile)
   int n_wave = (l_stop - l_start)/l_delta;
[…]

### 2010-07-24 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_mgii.cc

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  1e7;    // number of photons
+double n_photons =  2e7;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
@@ -42,7 +42,9 @@ double wind_doppler    =   15*1e5;
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
 double omnl = 1-n_law;
-double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double NH_wind   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double NH_ism    =  n_ISM * (r_inner-r_ISM);
+double NH_colm   =  NH_ism + NH_wind;
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 
@@ -76,6 +78,12 @@ int verbose;             // output parameter
 int main(int argc, char **argv)
 {
 
+  // Input dust (optional),  Photons are inputted two (required)
+  if(argc > 2) {
+    dust_tau = atof(argv[1]);
+    dust_norm   =  dust_tau / dust_cs /  NH_colm / KPARSEC ;
+    n_photons = atof(argv[2]);
+  }
 
   void Run_Monte_Carlo(char*);
 
@@ -193,6 +201,7 @@ void Run_Monte_Carlo(char *outfile)
   int n_wave = (l_stop - l_start)/l_delta;
   double E_p = F_cont*n_wave*n_mu*n_phi/n_photons*l_delta;
 
+  dust_scatter = 0;
   // send the photons
   for (i=0;i<n_photons;i++)
   {
@@ -234,6 +243,16 @@ void Run_Monte_Carlo(char *outfile)
 	l_step = tau_r/tau_x;
 	if (tau_x == 0) l_step = VERY_LARGE_NUMBER;
 	if (l_step < step) {step = l_step; scatter = l; }
+      }
+
[…]

### 2010-07-24 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_feii.cc

@@ -83,6 +83,12 @@ int main(int argc, char **argv)
   // Photons
   if(argc > 5) n_photons = atof(argv[5]);
 
+  // Dust
+  if(argc > 6) {
+    dust_tau = atof(argv[1]);
+    dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;
+  }
+
   // Lines 
   lines.Init("fe_uv1.lines");
 

### 2010-07-24 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_mgii.cc

@@ -80,6 +80,13 @@ int main(int argc, char **argv)
   // Photons
   if(argc > 5) n_photons = atof(argv[5]);
 
+  // Dust
+  if(argc > 6) {
+    dust_tau = atof(argv[1]);
+    dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;
+    return 0;  // Need to deal with nH_colm properly
+  }
+
   void Run_Monte_Carlo(char*);
 
   // initialize MPI for parallelism
@@ -182,6 +189,8 @@ void Run_Monte_Carlo(char *outfile)
   int n_wave = (l_stop - l_start)/l_delta;
   double E_p = F_cont*n_wave*n_mu*n_phi/n_photons*l_delta;
 
+  dust_scatter = 0;
+
   // send the photons
   for (i=0;i<n_photons;i++)
   {
@@ -224,12 +233,14 @@ void Run_Monte_Carlo(char *outfile)
       }
 
       // get distance to dust scatter/absorption
-      tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
-      tau_x = KPARSEC*dens_H*dust_norm*dust_cs;
-      d_step = tau_r/tau_x;
-      if (tau_x == 0) d_step = VERY_LARGE_NUMBER;
-      if (d_step < step) {step = d_step; scatter = -1; dust_scatter = 1; }
-      else  dust_scatter = 0;
+      if (dust_norm > 0.) {
+	tau_r = -1.0*log(1 - gsl_rng_uniform(rangen));
+	tau_x = KPARSEC*dens_H*dust_norm*dust_cs;
+	d_step = tau_r/tau_x;
+	if (tau_x == 0) d_step = VERY_LARGE_NUMBER;
+	if (d_step < step) {step = d_step; scatter = -1; dust_scatter = 1; }
+	else  dust_scatter = 0;
+      }
       
       // take the step
       r[0] += D[0]*step;
@@ -298,7 +309,7 @@ void Run_Monte_Carlo(char *outfile)
       {
 	double z =  gsl_rng_uniform(rangen);
 	if (z > dust_albedo) {count_it = 0; break; }
-	// choose new isotropic direction
+	// choose new isotropic direction (not used)
  	mu  = 1 - 2.0*gsl_rng_uniform(rangen);
  	phi = 2.0*PI*gsl_rng_uniform(rangen);
  	sin_theta = sqrt(1 - mu*mu);
[…]

### 2010-07-30 Winds/Grid/Transfer/outflow.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5089 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,353 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e6;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2790;     // beginning wavelength (Angstroms)
+double l_stop    =  2810;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    20;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  0.1;      // inner boundary radius, in kpc
+double r_outer   =  1.0;      // outer boundary radius, in kpc
+double r_emit    =  0.1;      // boundary to emit from
+double n_0       =  1e-3;     // number density at inner boundary
+double n_law     =    2;      // -1*power law exponent of density law
+double v_max     =  3.0e7;    // velocity at outer boundary (cm/s)
+double v_law     =    1;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-22;    // dust cross-section
+double dust_dens   =  1;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.4;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
+double lambda_0[]   = {2796.352, 2803.531};  
+// line oscillator strengths
+double f_lu[]       = {0.6123,     0.3054}; 
+// abundances of element of line
+double abun[]       = {8.5e-5, 8.5e-5};
[…]

### 2010-07-30 Winds/Grid/Transfer/spectrum.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5090 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,235 @@
+#include <mpi.h>
+#include <stdio.h>
+#include <math.h>
+#include <string.h>
+#include "physical_constants.hh"
+#include "spectrum.hh"
+
+//***************************************************************
+// Constructors
+//***************************************************************
+
+SPECTRUM::SPECTRUM()
+{
+  strcpy(name,DEFAULT_NAME);
+  n_elements = 0;
+  n_escaped = 0;
+}
+
+
+void SPECTRUM::Init(double *t, double *l, int n, double xmax)
+{
+  // initalize grids
+  lambda_grid.New(l[0],l[1],l[2]);
+  time_grid.New(t[0],t[1],t[2]);
+  x_grid.Uniform_New(0,xmax/n,n);
+  y_grid.Uniform_New(0,xmax/n,n);
+  
+  n_times  = time_grid.Size();
+  n_lambda = lambda_grid.Size();
+  n_x  = x_grid.Size();
+  n_y  = y_grid.Size();
+  
+  a3 = x_grid.Size();
+  a2 = y_grid.Size()*a3;            
+  a1 = lambda_grid.Size()*a2;
+  n_elements = time_grid.Size()*a1;
+  
+  // allocate
+  click  = new double[n_elements];
+  count  = new double[n_elements];
+
+  // clear 
+  Wipe();
+}
+
+void SPECTRUM::Init(double *l, int n, double xmax)
+{
+  double t[] = {1,1,1};
+  Init(t,l,n,xmax);
+}
+
+
+void SPECTRUM::Set_Name(char *n)
+{
+  strcpy(name,n);
+}
+
+//***************************************************************
+// Functional procedure: Wipe
+//***************************************************************
+void SPECTRUM::Wipe()
+{
+  n_escaped = 0;
+  for (int i=0;i<n_elements;i++) {
+    click[i]  = 0;
+    count[i]  = 0; }
+}
+
+
+//***************************************************************
+// handles the indexing: should be called in this order
+//    time, wavelength, mu, phi
+//***************************************************************
+int SPECTRUM::Index(int t, int l, int i, int j)
+{
+  return t*a1 + l*a2 + i*a3 + j;
+}
+
+//***************************************************************
+//--------------------------------------------------------------
+//********************** COUNT FUNCTIONS ************************
[…]

### 2010-07-30 Winds/Grid/Transfer/transport.cc

@@ -1,0 +1,351 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "anvoigt.hh"
+#include "spectrum.hh"
+#include "model.hh"
+#include "lines.hh"
+#include "physical_constants.hh"
+
+extern gsl_rng      *rangen;    // random number generator
+extern int verbose;             // output parameter
+extern MODEL model;
+extern SPECTRUM spectrum;
+extern double D_obs[3], cos_obs[4];
+extern LINES lines;
+ANVOIGT voigt;
+
+
+struct PHOTON {
+  int    ic;
+  double r[3], D[3];
+  double lam, xloc, lloc;
+  double E_p;
+  int    escaped;
+};
+
+double stepfrac = 0.7;
+
+//--------------------------------------------
+// Calculate a spectrum using Monte Carlo
+//--------------------------------------------
+void Run_Monte_Carlo(double n_photons)
+{
+  // local variables
+  int    i, scatter;
+  double tau_r, tau_x, vdotD;
+  double l_step, step, max_step;
+  double Pe, lobs, r_rot[3];
+  PHOTON p;
+
+  // functions to call
+  void MPI_Average_Array(double *, int);
+  double P_esc(double, double*);
+  void Emit(PHOTON*);
+  void Line_Scatter(PHOTON&, double, double*);
+  void Get_Rotated_Coords(double *, double *);
+
+  // set the start timer 
+  time_t start_tp,end_tp;
+  time(&start_tp);
+
+  // send the photons
+  for (i=0;i<n_photons;i++)
+  {
+    Emit(&p);
+    // Energy per photon
+    p.E_p = model.L_tot/(1.0*n_photons); 
+
+    // add in straight light
+    Pe   = P_esc(p.lloc,p.r);
+    lobs = p.lloc*(1 - model.vdotD(p.ic,D_obs)/C_LIGHT);
+    Get_Rotated_Coords(p.r,r_rot);
+    spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe);
+
[…]

### 2010-07-30 Winds/Grid/Transfer/uv_transport.cc

@@ -1,0 +1,148 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "model.hh"
+#include "physical_constants.hh"
+
+
+extern gsl_rng      *rangen;    // random number generator
+extern int verbose;             // output parameter
+extern MODEL model;
+
+struct PHOTON {
+  int    ic;
+  double r[3], D[3];
+  double lam, xloc, lloc;
+  double E_p;
+  int    escaped;
+};
+
+
+//--------------------------------------------
+// Calculate a spectrum using Monte Carlo
+//--------------------------------------------
+void Run_UV_Transport(double n_photons, double L_UV, int n_iter)
+{
+  void Run_UV_MC(double, double);
+  
+  for (int i=0;i<n_iter;i++)
+  {
+    model.Wipe_J_UV();
+    model.Compute_Ionization_State();
+    model.Compute_Photo_Opacity();
+    Run_UV_MC(n_photons, L_UV);
+    model.Reduce_J_UV();
+    model.Print_J_UV();
+  }
+
+}
+
+
+void Run_UV_MC(double n_photons, double L_UV)
+{
+
+  double stepfrac = 0.3;
+
+  // local variables
+  int    i, scatter;
+  double tau_r, opac, vdotD;
+  double l_step, step, max_step;
+  double mu, phi, sin_theta;
+  PHOTON p;
+
+  // set the start timer 
+  time_t start_tp,end_tp;
+  time(&start_tp);
+
+  // send the photons
+  for (i=0;i<n_photons;i++)
+  {
+    double xcen = model.xmax/2.0;
+    // Emit the photon
+    mu  = 1 - 2.0*gsl_rng_uniform(rangen);
+    phi = 2.0*PI*gsl_rng_uniform(rangen);
+    sin_theta = sqrt(1 - mu*mu);
+    double r_emit = 0; // xcen
+    p.r[0] = xcen + r_emit*sin_theta*cos(phi);
+    p.r[1] = xcen + r_emit*sin_theta*sin(phi);
+    p.r[2] = xcen + r_emit*mu; 
+    mu  = 1 - 2.0*gsl_rng_uniform(rangen);
+    phi = 2.0*PI*gsl_rng_uniform(rangen);
+    sin_theta = sqrt(1 - mu*mu);
[…]

### 2010-08-01 Winds/Grid/Transfer/outflow_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5093 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,384 @@
+// Models surface brightness emission for our LBG model
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  2e6;    // number of photons
+double stepsize  = 0.0001;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    20;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   =  100.0;      // outer boundary radius, in kpc
+double r_emit    =  0.5;      // boundary to emit from
+double bipolar   =    0;      // degree of bipolarity
+
+double LBG_gamma = 0.5;  // Covering fraction parameter
+double LBG_fc = 0.6;          // Maximum covering fraction (for MgII 2796)
+double LBG_vmax =  800*1e5;  // cm/s
+double LBG_alpha = 1.3;     // Velocity field parameter
+double LBG_A =  LBG_vmax*LBG_vmax * (1.-LBG_alpha);  // Wind parameter
+double LBG_Aa =  sqrt(LBG_A/(1-LBG_alpha));
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+double dust_norm   =  0.;   // Normalization to give dust_tau
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 2; 
+// line center wavelengths
[…]

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5095 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\ewabs}{$W_{\rm a}$}
+\newcommand{\ewe}{$W_{\rm e}$}
+\newcommand{\rtt}{$r_{\tau = 0.2}$}
+\newcommand{\mrtt}{r_{\tau = 0.2}}
 \newcommand{\bturb}{$b_{\rm turb}$}
@@
 
-\section{Observables}
-\label{sec:obs}
-
-Although the focus of this paper is to explore the absorption/emission
-profiles for idealized wind models, we ultimately intend to compare 
-profiles like these against observations to constrain characteristics
-of the wind (e.g.\ radial extent, energetics).  In this section we
-consider a few observables and their dependence on the wind properties.
-
-\subsection{Absorption profiles}
-
- \begin{enumerate}
-   \item Peak optical depth
-     \begin{itemize}
-       \item Not a robust measure of $\tau_{wind}$
-       \item Not even a good relative predictor for $\tau$
-       \item Not a robust predictor of $f_c$
-       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
-     \end{itemize}
-   \item Kinematics
-     \begin{itemize}
-       \item Nearly robust for $v<v_{min}$
-       \item But what sets $v_{min}$?
-       \item Generally get the full extent of the wind speed
-       \item Plot $v_{pk}$ vs $\tau_{pk}$
-     \end{itemize}
-   \item EW
-     \begin{itemize}
-       \item Primarily set by $v_{min}(\tau \sim 1)$
-       \item $f\lambda$ matters, but so do emission channels
-       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
-     \end{itemize}
-   \item Fine-structure
-     \begin{itemize}
-       \item Distance to the source
-     \end{itemize}
- \end{enumerate}
-
-\subsection{Emission profiles}
-
- \begin{enumerate}
-   \item Resonant lines
-     \begin{itemize}
-       \item Kinematics of backside
-       \item Flux + relative
-       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
-    \end{itemize}
-   \item Fine-structure
-     \begin{itemize}
-       \item Flux $\propto \tau_{wind}$ + relative
-       \item Kinematics (anisotropy)
-    \end{itemize}
- \end{enumerate}
-
+%\section{Observables}
+%\label{sec:obs}
+%
+%%Although the focus of this paper is to explore the absorption/emission
+%profiles for idealized wind models, we ultimately intend to compare 
+%profiles like these against observations to constrain characteristics
+%of the wind (e.g.\ radial extent, energetics).  In this section we
+%consider a few observables and their dependence on the wind properties.
+%
+%\subsection{Absorption profiles}
+%
+% \begin{enumerate}
+%   \item Peak optical depth
+%     \begin{itemize}
+%       \item Not a robust measure of $\tau_{wind}$
+%       \item Not even a good relative predictor for $\tau$
+%       \item Not a robust predictor of $f_c$
+%       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
+%     \end{itemize}
+%   \item Kinematics
+%     \begin{itemize}
+%       \item Nearly robust for $v<v_{min}$
+%       \item But what sets $v_{min}$?
+%       \item Generally get the full extent of the wind speed
+%       \item Plot $v_{pk}$ vs $\tau_{pk}$
+%     \end{itemize}
+%   \item EW
+%     \begin{itemize}
+%       \item Primarily set by $v_{min}(\tau \sim 1)$
+%       \item $f\lambda$ matters, but so do emission channels
+%       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
+%     \end{itemize}
+%   \item Fine-structure
+%     \begin{itemize}
+%       \item Distance to the source
+%     \end{itemize}
+% \end{enumerate}
+%     
+%\subsection{Emission profiles}
+%
+% \begin{enumerate}
+%   \item Resonant lines
+%     \begin{itemize}
+%       \item Kinematics of backside
+%       \item Flux + relative
+%       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
+%    \end{itemize}
+%   \item Fine-structure
+%     \begin{itemize}
+%       \item Flux $\propto \tau_{wind}$ + relative
+%       \item Kinematics (anisotropy)
+%    \end{itemize}
+% \end{enumerate}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Discussion}
 \label{sec:discuss}
+
+The previous sections presented a series of idealized wind models for
+cool gas outflows, and explored the absorption/emission profiles of
+the \mgiid\ doublet and the \ion{Fe}{2} UV1 multiplet.  In addition to
+the ubiquitous presence of blue-shifted absorption, the wind models
+also generically predict strong line emission in both the resonance
+and non-resonance transitions.  For isotropic and dust-free scenarios,
+this is simple convservation of photon number: every photon emitted by
+the source eventually escapes the system with the wind only [slightly]
+shifting them in frequency space.  A principal result of this paper,
+therefore, is that cool gas outflows should generate detectable line
+emission.
+
+As noted in the introduction, there are several reports of line
+emission associated with star-forming galaxies that exhibit cool gas outflows.  
+[SHORTEN THE OBSERVER SUMMARY]
+[Phillips first reported?]
+Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
+reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
+and \cite{rubin+10c}.   
+\cite{wcp+09}, who
+studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
+\ion{Mg}{2} emission in a small subset of the individual galaxy
+spectra of their large sample.  These were excluded from the full
+analysis on concerns that the emission was related to AGN activity.
+The stacked spectra of the remaining galaxies, however, also indicated
+\ion{Mg}{2} emisison, both directly and when the authors modeled and
+`removed' the $v \approx 0\kms$ absorption component.  Although the
+authors suggested the emission could be related to back-scattered
+light in the wind, they also allowed that it could be related to weak
+AGN activity.   Very similar \ion{Mg}{2} emission was observed by
+\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
+of lower redshift galaxies. 
+[Did Kate see FeII* emission in her stacks? If not, why not?]
+[Are there aspects of those works that are now understood, e.g. the
+difference in FeII 2586 and FeII 2600]
+At high redshift, \ion{Si}{2}* line emission has been reported from
+the Lyman break galaxies which was suggested to be
+related to \ion{H}{2} regions within the galaxies \citep{shapley03}.
+Lastly, \ion{Na}{1} line emission has also been detected in the
+stacked spectra of $z \sim 0$ galaxies by \cite{chen}.  
+We contend that all of these incidences may be examples of line
+scattered photons in the cool gas outflows of these star-forming
+galaxies.  Indeed, our results indicate that line emission could (and
+should) be produced by all of these galaxies if the outflows (and the
+galaxy emission) are nearly isotropic.
+
+On the other hand,
+there are many examples of galaxies where blue-shifted absorption is
+detected yet the authors report no significant line emission.  This
+includes the \ion{Na}{1} flows reported by \cite{rupke} and
+\cite{martin}, the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
+ULIRGS by \cite{mb10}, and the extreme \ion{Mg}{2} outflows identified
+by \cite{tremonti}.  Similarly, there have been no reports of
+resonance line emission from the LBGs nor ... [Others]
+The multitude of non-detections stands in stark contradiction to the
+results presented in this paper.   We are motivated, therefore, to
+reassess several of the effects that may reduce the line emission
+and consider whether these may eliminate the line emission for many
+star-forming galaxies.  [If MgII emission is 'common' for HII regions,
+why don't we see it *always* when we see OII, Hbeta, etc?  Same for
+FeII*]
+
+Dust is frequently invoked to explain the suppression of line emission
+related to a resonantly trapped line (e.g.\ \lya).  Indeed, a photon
+that is trapped for many scatterings within a dust medium will be
+preferentially extincted relative to a non-resonant photon.  In
+$\S$~\ref{sec:dust}, we examined the effects of dust extinction on the
+\ion{Mg}{2} and \ion{Fe}{2} emission.  The general result was a modest
+suppression of the line flux of the order of (1+\taud)$^{-1}$ instead of
+exp(--\taud).   [Do a series of models and fit a functional form for
+the fiducial model]  Although the \ion{Mg}{2} photons are resonantly
+trapped within the outflow, they require only one to a few scatterings
+to escape the fiducial wind model and dust has only a
+modest effect.  This reflects the [modest] opacity of the \ion{Mg}{2}
+doublet (e.g.\ relative to \lya) but also the specific characteristics
+of the wind.  We have also experimented with dust in several of the
+other models (e.g.\ the ISM+wind scenario) and find similar results.
+[Dust does reduce the $v \sim 0$ emission in the ISM+wind model more,
+as it is more effectively trapped.  Discuss this somewhere..  Also
+note that the EW of the absorption is higher for an ISM model so that
+the absolute value of EW emission is higher too for FeII*]
+Another reason \ion{Mg}{2} is less susceptible than \lya\ is that the
+latter may be generated through the flourescence of an ionizing
+photon, i.e.\ via a recombination cascade.  The ionizing photons 
+would penetrate deeper into the outflow and more effectively trap the
+\lya\ photon [is this right?].
+
+We also emphasize that the \ion{Fe}{2} resonance photons, especially
+\feiia, are converted to non-resonant photons and escape the wind
+freely.  A wind model that effectively trapped \ion{Mg}{2}
+photons for many scatterings would not be expected to trap the
+\feiid\ photons.  Therefore, the effects of dust are 
+reduced for \ion{Fe}{2}* and, by inference, any other set of
+transitions that are coupled to a fine-structure level (e.g.\
+\ion{Si}{2} and \ion{Si}{2}*).  
+Although dust does reduce the line flux relative to the continuum, we
+conclude that it has only a modest effect on \ion{Mg}{2} and
+\ion{Fe}{2}* emission.
+
+Another factor that reduces the predicted line emission is a
+non-isotropic wind model,e.g.\ the flux is reduced if there is no
+backside of the wind.  To zeroth order, the line emission scales
+roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
+wind\footnote{There is also a first order dependence on the actual
+  orientation of the wind with emission maximal if the backside is
+  fully present.}.  Because we require that the wind is at least
+pointing towards us, it is difficult to reduce $\Omega$ signficantly
+below $2 \pi$.  Therefore, we expect this effect to reduce the
+emission by a factor of order unity.  
+[The notion of the source absorbing all photons that scatter into it
+is akin to removing the backside]
+
+By a similar [token], an anisotropic source could alter the predicted
+line emission.  For example, if the backside of the galaxy were
+brighter/fainter than would one predict brighter/fainter emission
+relative to the observed continuum.
+To reduce the emission, the brightest regions
+of the galaxy would need to be oriented toward Earth.  Although this would not a
+generic occurance, most spectroscopic samples are magnitude-limited
+and therefore biased to detecting galaxies at their brightest.
+
+Together, dust and non-isotropic wind models can reduce line emission
+by a factor of a few.  We suggest, however, that this would generally
+not be sufficient to reduce the emission below the typical detection
+limits.
+
+There is another, more subtle effect that in principle will
+substantially reduce the observed line emission: slit losses.  As
+described in Figures~\ref{fig:fiducial_ifu_mgii} and
+\ref{fig:ISM_ifu}, emission from the wind is spatially extended with
+at least modest surface brightness at large radii implying a
+non-negligible total luminosity from well beyond the galaxy.  
+The majority of observations of star-forming galaxies to date have
+been taken through a spectroscopic slit typically designed to cover
+the brightest continuum regions of the galaxy.  A slit with an angular
+extent of $1-1.5''$ subtends roughly $8-15$\,kpc for galaxies at $z>0.5$.
+Therefore, a slit covering a galaxy with our fiducial wind would cover
+less than half of the wind.  The result will be reduced line emission,
+especially in comparison with the galaxy continuum.
+
+We have investigated the effect of a [partial] aperture as follows.
+We model the slit as a perfect, infinte rectangle centered on the
+galaxy.  We then tabulate the equivalent width of the line emission
+through slits with a range of widths, parameterized by the radius
+where the wind has an effective optical depth in the line of $\tau =
+0.2$ (\rtt)\footnote{Specifically, we determine the
+  velocity where $\tau(v) = 0.2$ and then use the velocity law to
+  convert to a radius.}.   We expect the line emission is weak beyond
+this radius because the photons have only a low probability of
+interacting with the wind.  For the fiducial wind model, $\mrtt
+\approx 15$\,kpc for \mgiia\ (Figure~\ref{fig:fiducial_nvt}).
+
+The predicted equivalent width in emission \ewe\ relative to the absorption
+equivalent width \ewabs\ is presented in
+Figure~\ref{fig:obs_slit} for a set of transitions (black curves).
+The curves rise very steeply with increasing slit width and then
+plateau when the slit width is $\approx \mrtt$.  
+The results are comparable for other wind models considered
+in this paper (colored curves in Figure~\ref{fig:obs_slit}).
+We conclude that slit losses would be important for slits that do not
+cover a majority of the wind.   Again, the effect is of order unity
+unless the slit width is very small.   Provided the winds do not
+extend far beyond 10\,kpc, the majority of emission will be subtended
+by stnadard slit observations.  Nevertheless, the results do motivate
+the usage of extended apertures, e.g.\ integral field unit (IFU)
+instrumentation that would map the wind both spatially and spectrally.
+
+Although there are several effects that will reduce line emission
+relative to the absorption produced by the outflow, our analysis
+indicates that detectable line emission should be present for [the
+majority] of winds.  One of the principal effects of this emission is
+that it modifies the observed absorption profiles (e.g.\
+Figure~\ref{fig:noemiss}) which may lead to erroneous conclusions
+regarding characteristics of the flow.  {\it Analysis of cool gas outflows
+that ignores emission may incorrectly lead to conclusions the gas is
+partially covered, has a significantly lower peak optical depth,
+and/or that a $v \sim 0 \mkms$ ISM component (perhaps even infall) is
+absent.}  Figure~\ref{fig:obs_ew} demonstrates a simple observational
+consequence of the line emission: reduced estimates for the absorption
+equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
+which has the most affected transitions, the \ewabs\ is reduced by
+XX\% for the wind models presented in this paper.
+
+[Could they have accidentally `sky subtracted' it?  I doubt it]
+
+%%%%%%%%%%%%%%%%%
 
@@
 
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_slit.ps}
+\caption{
+Slit width effects
+}
+\label{fig:obs_slit}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_ew.ps}
+\caption{
+EW effect
+}
+\label{fig:obs_ew}
+\end{figure}
+
 \end{document}

### 2010-08-02 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_feii.cc

@@ -308,6 +308,7 @@ void Run_Monte_Carlo(char *outfile)
 	      sum += lines.bprob(scatter,j);
 	      if (r1 < sum) {
 		lam = lines.blam(scatter,j)*(1 - vproj); 
+		lam = lam*(1 + v_doppler/C_LIGHT*(uvec[0]*D[0] + uvec[1]*D[1] + uvec[2]*D[2]));
 		sum = -9e9;  // Kludge to avoid 'break'
 	      }
 	    }

### 2010-08-02 Winds/papers/Theory/First/Analysis/ISM/outflow_ISM_feii.cc

@@ -342,10 +342,20 @@ void Run_Monte_Carlo(char *outfile)
 	      }
 	    }
 	}
-
-
       }
 
+      if (dust_scatter)
+      {
+	double z =  gsl_rng_uniform(rangen);
+	if (z > dust_albedo) {count_it = 0; break; }
+	// choose new isotropic direction
+ 	mu  = 1 - 2.0*gsl_rng_uniform(rangen);
+ 	phi = 2.0*PI*gsl_rng_uniform(rangen);
+ 	sin_theta = sqrt(1 - mu*mu);
+ 	D[0] = sin_theta*cos(phi);
+ 	D[1] = sin_theta*sin(phi);
+ 	D[2] = mu;
+      }
    }	
  
     // Count spectrum if needed

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5097 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 which has the most affected transitions, the \ewabs\ is reduced by
-XX\% for the wind models presented in this paper.
+$30-50\%$ for the wind models presented in this paper.  This could
+yield a systematically lower optical depth for the wind and therefore
+a lower total mass and kinetic energy.  Although not apparent in
+Figure~\ref{fig:obs_ew}, the effects are most pronounced for wind
+scenarios where the peak optical depth occurs near $v = \mkms$.
+Simple geometric projection limits the majority of scattered photon emission to
+have $v \approx \pm 200 \mkms$ and the absorption profiles
+are filled-in primarily at these velocities.  In
+Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
+for \mgiia\ 
+versus the velocity where $\tau = \tau_{pk}$ for the various wind models (i.e.\
+$\tau_{pk}$ vs.\ $v_\tau$ from Tables~\ref{tab:line_diag},
+\ref{tab:plaw_diag}).   In every one of the models, the intrinsic peak
+optical depth exceeds 10 and occasionally exceeds 100.  For the
+majority of cases with $v_\tau < -300\mkm$, one observes $\tau_{pk} <
+2$ and would infer the wind is not even optically thick!
+The results are similar for \mgiib\ although one infers a somewhat
+higher column density because of its lower $f\lambda$ value.
+In the majority of cases, one would faslely conclude that hte wind
+partially covered the source and also estimate a peak optical depth
+lower than the intrinsic.
+
+All of these (negative) effects for \ion{Mg}{2} absorption are reduced
+for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
+is because a signficant fraction (or even a majority) of the
+\ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
+wavelengths which have no effect on the absorption profiles. [word]
+Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
+closely follow the intrinsic value, one derives more accurate peak
+optical depths, and the absorption kinematics more faithfully reflect
+the motions of the flow.  Regarding the last point, one 
+predicts a velocity offset between the peak depth of the \ion{Fe}{2}
+centroid and that for \ion{Mg}{2} (Figure~\ref{fig:obs_vtau})
+especially when the peak occurs at $v > -400 \mkms$.  One is simply
+not sensitive to opacity at $v \sim 0 \mkms$ with the \ion{Mg}{2}
+transitions.  This includes gas realted tothe ISM of the galaxy and
+also infalling material with modest speeds.  One must take careful
+consideration of line emission, therefore,  before drawing robust
+conclusions aobut the presence/absence of gas with small velocity
+offsets from systemic.
+
+We emphasize that all of these effects are heightened by the
+relatively low spectral resolution and S/N characteristic of the data
+obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
+shows one realization of the \mgiid\ doublet for the fiducial model
+convolved with the line-spread-function of the Keck/LRIS spectrometer
+(FWHM=250\kms) and an assumed S/N=7 per XX\AA\ pixel.  Both the absorption
+and emission profiles are evident, but it is evident that it will be
+very difficult to resolve the issues discussed above (e.g.\ partial
+covering, incorrect peak optical depth) with these data.  The effects
+are even more difficult to predict for spectral stacks, especially
+when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
+An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
+averaged 200 identical \ion{Mg}{2} profiles from the fiducial model
+degraded to a S/N=1\,pix$^{-1}$ and assuming a random redshift error
+$\sigma(z) = 40\mkms$.  [Check S10]
+
+[Should galaxies with strong \lya\ emission be expected to show
+low-ion emission? Perhaps not if \lya\ is produced by ionizing photons
+from SF regions.]
 
@@
 
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_peaktau.ps}
+\caption{
+EW effect
+}
+\label{fig:obs_peaktau}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_vtau.ps}
+\caption{
+Velocity offset
+}
+\label{fig:obs_vtau}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_lris.ps}
+\caption{
+Velocity offset
+}
+\label{fig:obs_lris}
+\end{figure}
+
 \end{document}

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5098 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
-shows one realization of the \mgiid\ doublet for the fiducial model
+shows one realization of the \mgiid\ doublet for the ISM+wind model
 convolved with the line-spread-function of the Keck/LRIS spectrometer
-(FWHM=250\kms) and an assumed S/N=7 per XX\AA\ pixel.  Both the absorption
+(FWHM=250\kms) and an assumed S/N=7 per (1 \AA) pixel.  Both the absorption
 and emission profiles are evident, but it is evident that it will be
@@
 An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
-averaged 200 identical \ion{Mg}{2} profiles from the fiducial model
-degraded to a S/N=1\,pix$^{-1}$ and assuming a random redshift error
-$\sigma(z) = 40\mkms$.  [Check S10]
+averaged 100 identical \ion{Mg}{2} profiles from the fiducial model
+degraded to a S/N=2\,pix$^{-1}$ and assuming a random redshift error
+$\sigma(z) = 100\mkms$.  [Check S10 error] [Note the further shift in
+MgII 2796 due to the instrument resolution]
 

### 2010-08-02 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5099 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -87,6 +87,7 @@ int main(int argc, char **argv)
   if(argc > 6) {
     dust_tau = atof(argv[1]);
     dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;
+    return 0;  // Need to deal with nH_colm properly
   }
 
   // Lines 

### 2010-08-02 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5101 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+Focuses on the observational consequences and implications if our results.
+
 The previous sections presented a series of idealized wind models for
@@
 \ion{Mg}{2} emisison, both directly and when the authors modeled and
-`removed' the $v \approx 0\kms$ absorption component.  Although the
+`removed' the $v \approx 0\mkms$ absorption component.  Although the
 authors suggested the emission could be related to back-scattered
@@
 optical depth exceeds 10 and occasionally exceeds 100.  For the
-majority of cases with $v_\tau < -300\mkm$, one observes $\tau_{pk} <
+majority of cases with $v_\tau < -300\mkms$, one observes $\tau_{pk} <
 2$ and would infer the wind is not even optically thick!
@@
 
+The previous few paragraphs sound a cautionary and largely negative
+perspective on the implications for absorption-line analysis of
+galactic-scale outflows, in the presence of (expected) significant
+line-emission.   While this does complicate [the analysis],
+observations of the line emission alone offer new and unique
+constraints on the charcteristics of the outflow.  And when coupled
+with the absorption-line data, the two sets of constraints...
+The most direct measure provided by the line emission is an estimate
+of the size and morphology of the outflow \citep[e.g.][]{rubin_emiss}.  
+Line emission is predicted to extend to radii where the Sobolev
+optical depth exceeds a few tenths [is that right?].  The principle
+challenge is to achieve sufficient sensitivity to detect the low
+surface brightness emission.
+
+As Figure~\ref{fig:obs_sb}
+demonstrates, the surface brightness at the inner wind radius of our
+fiducial wind exceeds the outer radius by several orders of magnitude.
+Nevertheless, an instrument that sampled the entire wind (e.g.\ a
+large format IFU or narrow band imager) may detect the emission in
+azimuthally averaged apertures. [Give estimate]
+[Add FeII* to the SB figure]
+
+Of the transitions considered in this paper, \ion{Mg}{2} emission is
+preferred for [this analysis] because 
+(i) it has the largest equivalent width in absorption and
+(ii) there are fewer emission channels per absorption line than for
+\ion{Fe}{2}.  This implies the highest peak and integrated fluxes
+(Figure~\ref{fig:obs_sb}).  With an IFU observation covering all of
+the \ion{Fe}{2} transitions, one could sum the together to enhance the
+signal.
+
+The kinematics of the line emission also offer insight into physical
+characteristics of the wind.
+
 %%%%%%%%%%%%%%%%%
@@
 
-\section{Summary}
-\label{sec:summary}
+\section{Concluding remarks}
+\label{sec:conclude}
+
+1. More complicated winds needed
+
+2. Cosmological context (espeicially at $z>2$)
 
@@
 
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_sb.ps}
+\caption{
+Surface brightness
+}
+\label{fig:obs_sb}
+\end{figure}
+
 \end{document}

### 2010-08-03 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/model_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5104 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,136 @@
+#include <stdlib.h>
+#include <stdio.h>
+#include <mpi.h>
+#include "model_lbg.hh"
+#include "math.h"
+#include "physical_constants.hh"
+#include "Lua.hh"
+
+void MODEL::Init(const char* fname)
+{
+  Lua lua;
+  lua.init( fname );
+
+  // Dimensions
+  model.r_inner = lua.scalar<double>("r_inner");
+  model.r_outer = lua.scalar<double>("r_outer");
+  model.r_emit = lua.scalar<double>("r_emit");
+
+  // Wind
+  model.LBG_gamma = lua.scalar<double>("LBG_gamma");
+  model.LBG_fc = lua.scalar<double>("LBG_fc");
+  model.LBG_vmax = lua.scalar<double>("LBG_vmax");
+  model.LBG_alpha = lua.scalar<double>("LBG_alpha");
+  model.vdop = lua.scalar<double>("vdoppler");
+
+  // Calcualte a few
+  model.LBG_A =  model.LBG_vmax*model.LBG_vmax * (1.-model.LBG_alpha);  // Wind parameter
+  model.LBG_Aa =  sqrt(model.LBG_A/(1-model.LBG_alpha));
+}
+
+
+
+void MODEL::Calculate_Opacities(void)
+{
+  double nu_Lya   = C_LIGHT/(LAM_LYA*ANGS_TO_CM);
+  double flu_Lya  = 0.42;
+  double Lyman_CS = CLASSICAL_CS*flu_Lya/nu_Lya;
+  double E_Lya    = 1.63422e-11;
+
+  // For your reference
+  // sigma(Lya) = CLASSICAL_CS*flu/nu_dop
+  // or sigma(Lya) = 1e-13 cm^2 (T/10^4)^(-1/2)
+  
+  
+  double N_e, N_H, Clya, this_e;
+  int ind;
+  for (int i=0;i<n_x;i++)
+    for (int j=0;j<n_x;j++)
+      for (int k=0;k<n_x;k++)
+      {
+	ind = i*n_x*n_x + j*n_x + k;
+	indx[ind] = i;
+	indy[ind] = j;
+	indz[ind] = k;
+
+	Clya = 2.41e-6*pow(temp[ind]/1e4,0.22)
+	  *exp(-10.2/K_BOLTZ_EV/temp[ind])*pow(temp[ind],-0.5);
+	
[…]

### 2010-08-03 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/transport_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5105 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,375 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "anvoigt.hh"
+#include "spectrum.hh"
+#include "model.hh"
+#include "lines.hh"
+#include "physical_constants.hh"
+
+extern gsl_rng      *rangen;    // random number generator
+extern int verbose;             // output parameter
+extern MODEL model;
+extern SPECTRUM spectrum;
+extern double D_obs[3], cos_obs[4];
+extern LINES lines;
+ANVOIGT voigt;
+
+
+struct PHOTON {
+  int    ic;
+  double r[3], D[3];
+  double lam, xloc, lloc;
+  double E_p;
+  int    escaped;
+};
+
+double stepfrac = 0.7;
+
+//--------------------------------------------
+// Calculate a spectrum using Monte Carlo
+//--------------------------------------------
+void Run_Monte_Carlo(double n_photons)
+{
+  // local variables
+  int    i, scatter;
+  double tau_r, tau_x, vdotD;
+  double l_step, step, max_step;
+  double Pe, lobs, r_rot[3];
+  PHOTON p;
+
+  // functions to call
+  void MPI_Average_Array(double *, int);
+  double P_esc(double, double*);
+  void Emit(PHOTON*);
+  void Line_Scatter(PHOTON&, double, double*);
+  void Get_Rotated_Coords(double *, double *);
+
+  // set the start timer 
+  time_t start_tp,end_tp;
+  time(&start_tp);
+
+  // send the photons
+  for (i=0;i<n_photons;i++)
+  {
+    Emit(&p, model.r_emit);
+    // Energy per photon
+    p.E_p = model.L_tot/(1.0*n_photons); 
+
+    // add in straight light
+    Pe   = P_esc(p.lloc,p.r);
+    lobs = p.lloc*(1 - model.vdotD(p.ic,D_obs)/C_LIGHT);
+    Get_Rotated_Coords(p.r,r_rot);
+    spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe);
+
[…]

### 2010-08-03 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/model_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5107 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -12,108 +12,39 @@ void MODEL::Init(const char* fname)
   lua.init( fname );
 
   // Dimensions
-  model.r_inner = lua.scalar<double>("r_inner");
-  model.r_outer = lua.scalar<double>("r_outer");
-  model.r_emit = lua.scalar<double>("r_emit");
+  r_inner = lua.scalar<double>("r_inner");
+  r_outer = lua.scalar<double>("r_outer");
+  r_emit = lua.scalar<double>("r_emit");
 
   // Wind
-  model.LBG_gamma = lua.scalar<double>("LBG_gamma");
-  model.LBG_fc = lua.scalar<double>("LBG_fc");
-  model.LBG_vmax = lua.scalar<double>("LBG_vmax");
-  model.LBG_alpha = lua.scalar<double>("LBG_alpha");
-  model.vdop = lua.scalar<double>("vdoppler");
+  LBG_gamma = lua.scalar<double>("LBG_gamma");
+  LBG_fc = lua.scalar<double>("LBG_fc");
+  LBG_vmax = lua.scalar<double>("LBG_vmax");
+  LBG_alpha = lua.scalar<double>("LBG_alpha");
+  vdop = lua.scalar<double>("vdoppler");
 
   // Calcualte a few
-  model.LBG_A =  model.LBG_vmax*model.LBG_vmax * (1.-model.LBG_alpha);  // Wind parameter
-  model.LBG_Aa =  sqrt(model.LBG_A/(1-model.LBG_alpha));
+  LBG_A =  LBG_vmax*LBG_vmax * (1.-LBG_alpha);  // Wind parameter
+  LBG_Aa =  sqrt(LBG_A/(1-LBG_alpha));
+
+  // Normalize
+  L_tot = 1;
 }
 
 
 
-void MODEL::Calculate_Opacities(void)
+double MODEL::Velocity(double r)
 {
-  double nu_Lya   = C_LIGHT/(LAM_LYA*ANGS_TO_CM);
-  double flu_Lya  = 0.42;
-  double Lyman_CS = CLASSICAL_CS*flu_Lya/nu_Lya;
-  double E_Lya    = 1.63422e-11;
+  if (r <= r_inner) return 0;
+  return LBG_Aa * sqrt(1 - pow(r,1-LBG_alpha));  // Assumes r_inner=1kpc
+}
 
-  // For your reference
[…]

### 2010-08-03 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/transport_lbg.cc

@@ -37,7 +37,8 @@ void Run_Monte_Carlo(double n_photons)
 {
   // local variables
   int    i, scatter;
-  double tau_r, tau_x, vdotD;
+  int l, flg_resonance[50];
+  double tau_r, tau_x, rad;
   double l_step, step, max_step;
   double Pe, lobs, r_rot[3];
   PHOTON p;
@@ -45,7 +46,8 @@ void Run_Monte_Carlo(double n_photons)
   // functions to call
   void MPI_Average_Array(double *, int);
   double P_esc(double, double*);
-  void Emit(PHOTON*);
+  double Get_vdotD(double,double*, double*);  // Vector only
+  void Emit(PHOTON*, double);
   void Line_Scatter(PHOTON&, double, double*);
   void Get_Rotated_Coords(double *, double *);
 
@@ -62,47 +64,54 @@ void Run_Monte_Carlo(double n_photons)
 
     // add in straight light
     Pe   = P_esc(p.lloc,p.r);
-    lobs = p.lloc*(1 - model.vdotD(p.ic,D_obs)/C_LIGHT);
+    lobs = p.lloc*(1 - Get_vdotD(model.r_emit, p.r,D_obs)/C_LIGHT);
     Get_Rotated_Coords(p.r,r_rot);
     spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe);
+
+    for (l=0;l<50;l++) flg_resonance[l] = 0;
 
     // propogate until escaped (unless nothing stands in the way)
     while (1)
     {
       // locate zone and escape if so
-      p.ic = model.Locate_Zone(p.r);
-      if (p.ic < 0) {p.escaped = 1; break; }
+      //p.ic = model.Locate_Zone(p.r);
+      //if (p.ic < 0) {p.escaped = 1; break; }
 
       // photon wavelength in local frame
-      p.lloc = p.lam/(1 - model.vdotD(p.ic, p.D)/C_LIGHT);
+      rad = sqrt(p.r[0]*p.r[0] + p.r[1]*p.r[1] + p.r[2]*p.r[2]);
+      p.lloc = p.lam/(1 - Get_vdotD(rad, p.r, p.D)/C_LIGHT);
 
-      // default step size
-      max_step = model.dx*stepfrac;
-      step = max_step;
[…]

### 2010-08-16 Winds/papers/Theory/First/wind_simple.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5128 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
-\newcommand{\feiic}{\ion{Fe}{2}$^* \; \lambda 2612$}
-\newcommand{\feiie}{\ion{Fe}{2}$^* \; \lambda 2626$}
+\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
+\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
 \newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
-\newcommand{\feiis}{\ion{Fe}{2}$^*$}
+\newcommand{\feiis}{\ion{Fe}{2}$*$}
 \newcommand{\nmg}{$n_{\rm Mg^+}$}
@@
 
-\title{Simple Wind Models}
+\title{Idealized Wind Models of Cool Gas Outflows}
 
@@
 Iron exhibits the most complex set of energy levels for elements
-frequently studied in astrophysics.  The Fe$^+$ ion alone has over XXX
-energy levels recorded \citep{iron}, and even this is an
+frequently studied in astrophysics.  The Fe$^+$ ion alone has over
+10,000 energy levels recorded \citep{iron}, and even this is an
 incomplete list.  
@@
 in Figure~\ref{fig:energy}. The solid (green) downward
-arrows in Figure~\ref{fig:energy} mark the transitions that are
-connected to
+arrows in Figure~\ref{fig:energy} mark the non-resonant \feiis\
+transitions that are connected to
 the upper energy levels of the resonance lines.  These transitions may
 occur following the absorption of a single photon by Fe$^+$ in its
-ground-state.
+ground-state.   This process may also be referred to as flourescence.
 
@@
 configuration.  Ignoring collisions and recombinations, these
-transitions may only can only occur after the absorption
+transitions may only occur after the absorption
 of two photons: one to raise the electron from the ground-state to an
@@
 \citep[e.g][]{silva02,pcb06} and requires the ion to lie
-near an intense source of UV photons (see $\S$~\ref{sec:pump}).  In the
-following, we will assume that this process does not occur.
+near an intense source of UV photons.  
+Even a bright, star-forming galaxy emits too few photons at $\lambda
+\approx 2500$\AA\ to UV-pump Fe$^+$ ions that are farther than $\sim
+100$\,pc from the stars.
+In the
+following, we will assume that emission from this process is
+negligible.
 
@@
 detectable quantities of \ion{Fe}{1} which has not yet been observed
-in galactic-scale outflows
-\citep[see also][]{pcb06}.  Furthermore, observations rarely show
+in galactic-scale outflows. Furthermore, observations rarely show
 {\it absorption} from the
-fine-structure levels of the \aconfig\ configuration and even that material
-is not significantly blue-shifted \citep{rubin+10}.
+fine-structure levels of the \aconfig\ configuration and that material
+is not significantly blue-shifted (Rubin et al., in prep). 
 In the following, we assume that electrons only occupy the
@@
 lines.
-Empirically, because collisional excitation is insignificant and
+If collisional excitation is insignificant 
 then one may also neglect collisional de-excitation.  
-The excitation energy for Mg$^+$ ($T_{\rm ex} \approx 50,000$\,K),  
-meanwhile, is significantly higher implying 
-negligible collisional processes.
+Regarding the \ion{Mg}{2} doublet, its
+excitation energy is significantly higher implying 
+negligible collisional processes at essentially any density.
 
@@
 types do show significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
-[Any emission??]  \ion{H}{2} regions, meanwhile, are observed to emit
+{\bf [Kate: Any emission??]}  \ion{H}{2} regions, meanwhile, are observed to emit
 at the \mgiid\ doublet, primarily due to recombinations in the outer
-layers [How about FeII?].  It is beyond the scope of this paper to
+layers {\bf [Kate: How about FeII?]}.  It is beyond the scope of this paper to
 properly model the 
@@
 independent of the outflow, especially at velocities $v \approx 0 \mkms$.
-In the following, we will simply assume a flat continuum 
+In the following, we assume a simple flat continuum 
 normalized to unit value.  The size of the emitting
-region $r_{\rm source}$ is a free parameter, but we tend to
-restrict its value to be smaller than the minimum radial extent of any
-gaseous component.
+region $r_{\rm source}$ is a free parameter, but we restrict its value
+to be smaller than the minimum radial extent of any gaseous
+component.
 
@@
 [Put tests in an Appendix?]
+
+\subsection{The Sobolev Approximation}
+
+For a wind with a steep velocity law (i.e.\ a large gradient $dv/dr$)
+and/or a a narrow intrinsic profile (i.e.\ a small Doppler parameter),
+Sobolev \cite{sobolev}
 

### 2010-08-16 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5129 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\mdv}{\delta v}
 \newcommand{\ewabs}{$W_{\rm a}$}
@@
 
+[Phillips first reported?]
+Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
+reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
+and \cite{rubin+10c}.   
+\cite{wcp+09}, who
+studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
+\ion{Mg}{2} emission in a small subset of the individual galaxy
+spectra of their large sample.  These were excluded from the full
+analysis on concerns that the emission was related to AGN activity.
+The stacked spectra of the remaining galaxies, however, also indicated
+\ion{Mg}{2} emisison, both directly and when the authors modeled and
+`removed' the $v \approx 0\mkms$ absorption component.  Although the
+authors suggested the emission could be related to back-scattered
+light in the wind, they also allowed that it could be related to weak
+AGN activity.   Very similar \ion{Mg}{2} emission was observed by
+\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
+of lower redshift galaxies. 
+[Did Kate see FeII* emission in her stacks? If not, why not?]
+
 Although astronomers are rapidly producing a wealth of observational
@@
 
-\subsection{The Sobolev Approximation}
-
-For a wind with a steep velocity law (i.e.\ a large gradient $dv/dr$)
-and/or a a narrow intrinsic profile (i.e.\ a small Doppler parameter),
-Sobolev \cite{sobolev}
-
 \subsection{Dust}
@@
 
-For the majority of models studied in this paper, we assume no dust.
+For the majority of models studied in this paper, we assume the gas
+contains no dust.
 This is an invalid assumption, especially for material associated with
 the ISM of a galaxy.  
-There is also empirical evidence for dust emission from galactic-scale
-outflows \citep[e.g.][]{M87_dust}.
-Because absorption line analysis is performed
-on normalized spectra, these effects of dust are largely minimized; 
-the effects are corrected by simply rescaling the normalized flux.  For
-scattered and resonantly trapped photons, however, the relative effect of dust
-extinction can be much greater.  Indeed, dust is frequently invoked to
+Extraplanar material likely associated with a galactic-scale 
+outflow has been observed to emit IR radiation characteristic of dust \citep[e.g.][]{M87_dust}.
+Essentially all astrophysical environments that contain both cool gas
+and metals also show signatures of dust depletion and extinction.  This includes the
+ISM of star-forming and \ion{H}{1}-selected galaxies
+\citep[e.g.][]{ss96,pw01,pcd+07}, strong \ion{Mg}{2} metal-line
+absorption systems \citep{ykv+06,mnt+08}, and the galactic winds traced
+by low-ion transitions \citep{prs+02,rvs05b}.  Although the galactic winds
+traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
+demonstrated to contain dust, it is reasonable to consider its
+effects.
+In addition, \cite{msf+10} have argued from a statistical analysis
+that dust is distributed to many tens kpc from $z \sim 0.1$ galaxies
+and have suggested it was transported from the galaxies by
+galactic-scale winds.  One is motivated, therefore, to consider
+models that include the effects of dust extinction.
+
+For analysis on normalized spectra, the effects of dust are largely minimized; 
+dust has a nearly constant opacity over small spectral regions and all
+features are simply scaled together.
+For scattered and resonantly trapped photons, however, the relative effect of dust
+extinction can be much greater.  
+These photons travel a much longer distance to escape the medium and
+may experience a much higher integrated opacity from dust.
+Indeed, dust is frequently invoked to
 explain the weak (or absent) \lya\ emission from star-forming galaxies
 \citep[e.g.][]{shapley03}.  Although the transitions studied here have
-much lower opacity than \lya, dust could play an important role
+much lower opacity than \lya, dust could still play an important role
 in the predicted profiles.
@@
 the integrated opacity of dust from the center of the system to
-infinity.  The ISM of a star-forming galaxy may be expected to exhibit
-\taud\ values of one to a few \citep[e.g.][]{dust_again}.
+infinity.  The ambient ISM of a star-forming galaxy may be expected to exhibit
+\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{dust_again}.
+
+\subsection{The Sobolev Approximation}
+
+For a wind with a steep velocity law (i.e.\ a large gradient $dv/dr$)
+and/or a a narrow intrinsic profile (i.e.\ a small Doppler parameter),
+\citet{sobolev60} introduced a formalism that defines the opacity of
+the wind at a given radius $\tau(r)$ in terms of the density and
+velocity gradient of the flow at that radius:
+
+\begin{equation}
+\tau^S(r) = \kappa_\ell \rho(r) \, \lambda_\ell \ltp \frac{dv}{dr}
+\rtp^{-1}
+\label{eqn:Sobolev}
+\end{equation}
+where $\kappa_\ell$ is the opacity of transition $\ell$.  The opacity
+holds for a photon with wavelength $\lambda^S
+= \lambda_\ell (1-v(r)/c)$ with the velocity evaluated at the radius.
+This is, of course, not the true opacity.
+A photon with wavelength $\lambda^S$ that travels through the wind 
+experiences a total opacity 
+$\tau_\nu = \intl_0^\infty \rho(r) \kappa_\nu dr$.  The Sobolev
+approximation is valid when the opacity the photon experiences is
+domianted by gas in a localized portion of the flow that has velocity
+$v = c(\lambda^S/\lambda^\ell - 1)$.  In this case, $\tau^S$ provides an
+excellent approximation.  We find that it applies to nearly all of the
+models presented in this paper.  [Comment on the lack of the $b$-value
+in this?]
 
@@
 similar to those observed for $z \sim 1$, star-forming galaxies
-\citep{wcp+09,rubin+10b}.  We emphasize, however, that we do not
+\citep{wcp+09,rubin+10c}.  We emphasize, however, that we do not
 favor this fiducial model over any other wind scenario nor do its
 properties have special physical motivation.
-Its primary purpose is to establish a baseline
+Its role is to establish a baseline
 for discussion.
 
-The fiducial wind follows a (mass-flux conserving) density law,
+The fiducial wind is isotropic, dust-free, and extends from an inner wind
+radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
+It follows a (mass-flux conserving) density law,
 
@@
 Turbulent motions are
-characterized by a Doppler parameter $b_{\rm turb}$.  
-The wind is isotropic, dust-free, and extends from an inner wind
-radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
+characterized by a Doppler parameter\footnote{
+  The adopted Doppler parameter
+  ($\mbturb = 15 \mkms$) has a minor impact on the results.
+  The absorption profiles are insensitive to its value and varying \bturb\
+  only tends to modify the widths and modestly
+  shift the centroids of emission lines.} 
+, $b_{\rm turb}$.  
 We convert the hydrogen density $n_{\rm H}$ to the number densities of
@@
 and \nfe=\nmg/2. At the center of the wind is a homogeneous source of
-continuum photons with size $r_{\rm source}$. These parameters are
-summarized in Table~\ref{tab:fiducial}.
+continuum photons with size $r_{\rm source}$. The parameters for the
+fiducial wind model are summarized in Table~\ref{tab:fiducial}.
 
@@
 laws against radius;  
-their single power-law expressions are evident.  The figure also
-shows the optical depth profile for the \mgiia\ transition ($\tau_{2796}$).
-Although plotted against radius, we calculated $\tau_{2796}$ first
+their simple power-law expressions are evident.  The figure also
+shows the optical depth profile for the \mgiia\ transition
+($\tau_{2796}$), estimated from the Sobolev approximation\footnote{We
+  have verified this approxmiation holds by calculating 
+  $\tau_{2796}$ first
   as a function of velocity by summing the opacity for a series of
@@
   $\tau_{2796}$ onto radius using the velocity law
-(Equation~\ref{eqn:vel}). 
+  (Equation~\ref{eqn:vel}). This optical depth profile is shown as the
+black dotted line in Figure~\ref{fig:fiducial_nvt}.}
+(Equation~\ref{eqn:Sobolev}).
+
 The $\tau_{2796}$ profile peaks with $\tau_{2796}^{\rm max} \approx 30$
-at a velocity $v \approx 65 \mkms$ corresponding to $r \approx 1.3
+at a velocity $\mvr \approx 65 \mkms$ corresponding to $r \approx 1.3
 r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
@@
 scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.
-The adopted Doppler parameter
-($\mbturb = 15 \mkms$) has a minor impact on the results.
-The absorption profiles are insensitive to its value and varying \bturb\
-only tends to modify the widths and modestly
-shift the centroids of emission lines.
-
-Because the results are dictated by the $\tau_{2796}$ profile in
-velocity space, the actual dimensions and density of the wind are
+
+Because the results are dictated by frequency dependence of the
+$\tau_{2796}$ profile, 
+the actual dimensions and density of the wind are
 essentially unimportant provided they scale together to give nearly the same
-$\tau_{2796}$ profile.  Therefore, one may consider the choices for
+optical depth. Therefore, one may consider the choices for
 $r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
@@
 source embedded within an outflow.  Strong absorption is evident at
-$v < -50 \mkms$ in both transitions (equivalent widths, $W_{2796} =
-3.0$\AA\ and $W_{2803} = 1.3$\AA) and each shows emission at
-positive velocities.  For this isotropic and dust-free model, the
-total equivalent width of the doublet must be zero
-(Table~\ref{tab:fiducial_EW}), i.e.\ every photon
+$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both transitions (equivalent widths, $W^{2796} =
+3.0$\AA\ and $W^{2803} = 1.3$\AA) and each shows emission at
+positive velocities.  For an isotropic and dust-free model, the
+total equivalent width of the doublet must be zero,
+i.e.\ every photon
 absorbed eventually escapes the system, typically at lower
 energy.  The wind simply shuffles the photons in frequency space.
+A simple summation of the absorption and emission equivalent widths
+(Table~\ref{tab:fiducial_EW}) confirms this expectation.
 
@@
 {\it entirely covers the source}; the apparent partial covering must
-be related to an alternate effect.
+be related to a different effect.
 Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
@@
 re-emitted.   As expected from the
-$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), the
-`no-emission' model
+$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), this
+`intrinsic' model
 produces a strong \mgiid\ doublet that absorbs all photons at
-$v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
+$\delta v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
   max}_{2796}) \approx 0$.
-The fiducial model, in contrast, has been `filled in' at $v \approx -100
-\mkms$ by photons scattered and re-emitted by the wind.  An
+The true model, in contrast, has been `filled in' at $\delta v \approx -100
+\mkms$ by photons scattered in the wind.  An
 absorption-line analysis that ignores these effects
@@
 source.  We will find that this
-behaviour is a generic result of the wind models considered, even for cases that are
-not fully isotropic.
+[behaviour] is a generic result, even for wind models that include
+dust and are not fully isotropic.
 
@@
 The emission profiles are very similar because the gas is optically
-thick for a significant portion of the profile. 
-Furthermore, the flux from \mgiib\ exceeds the
+thick yielding comparable total absorption. 
+Furthermore, the flux from \mgiib\ actually exceeds the
 \mgiia\ emission because the wind speed is greater than the velocity separation
 of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
-Therefore,
-the \mgiib\ absorption profile partially absorbs the red wing of the
-\mgiia\ emission profile.  The relative strengths of the emission
-lines is sensitive to both the opacity and velocity
-extent of the wind.
-
-Now consider the \ion{Fe}{2} transitions.
-The bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
+Therefore, the red wing of the
+\mgiia\ emission profile is partially absorbed by \mgiib\ and
+re-emitted at lower frequency.  We conclude that the relative
+strengths of the emission lines is sensitive to both the opacity and
+velocity extent of the wind.
+
+Now consider the \ion{Fe}{2} transitions:
+the bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
 majority of the \ion{Fe}{2} UV1 transitions and several are
@@
 one observes strong absorption to negative velocities and strong
-emission at $v > 0 \mkms$ producing a characteristic P-Cygni profile. 
+emission at $\mdv > 0 \mkms$ producing a characteristic P-Cygni profile. 
 Splitting
-the profile at $v = -50 \mkms$, we measure an equivalent width
-$W_{2600}^{\rm abs} = 1.16$\AA\ in absorption and $W_{2600}^{\rm em} =
+the profile at $\mdv = -50 \mkms$, we measure an equivalent width
+$W^{2600}_{\rm a} = 1.16$\AA\ in absorption and $W^{2600}_{\rm e} =
 -0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
-equivalent width of $W_{2600}^{\rm TOT} \approx 0.22$\AA.  
+equivalent width of $W^{2600}_{\rm TOT} \approx 0.22$\AA.  
 In contrast, the \feiia\ resonance line shows much weaker emission and
-a much higher total equivalent width ($W_{2586}^{\rm TOT} = 0.49$\AA),
+a much higher total equivalent width ($W^{2586}_{\rm TOT} = 0.49$\AA),
 even though the line has a $2 \times$ lower $f\lambda$ value.
-These differences between the \ion{Fe}{2} resonance lines and with the
-\ion{Mg}{2} doublet occur because of the complex of non-resonant
-\ion{Fe}{2} transitions (Figure~\ref{fig:energy}).  Specifically,
+These differences between the \ion{Fe}{2} resonance lines (and with the
+\ion{Mg}{2} doublet) occur because of the complex of non-resonant
+\feiis\ transitions that are coupled to the resonance lines
+(Figure~\ref{fig:energy}).  Specifically, 
 resonance photons absorbed at \feiid\ have a finite probability of
-being re-emitted as a non-resonant photon which escapes the system
+being re-emitted as a non-resonant photon which then escapes the system
 without further interaction.  The principal effects are to reduce the
-line emission of \feiid\ and produce non-resonant line-emission (e.g.\
+line emission of \feiid\ and to produce non-resonant line-emission (e.g.\
 \feiic).
@@
 (ii) the Einstein A
-coefficients of the non-resonant lines are comparable to and even
+coefficients of the non-resonant lines coupled to \feiia\ are comparable to and even
 exceed the Einstein A coefficient of
 the resonant transition.  In contrast, 
-the \ion{Fe}{2}~2626 transition (associated with \feiib)
+the \feiie\ transition (associated with \feiib)
 has an approximately  $4\times$ smaller A coefficient than the
+corresponding
 resonance line.  Therefore, the majority of photons absorbed at
-$\lambda \approx 2600$ are re-emitted as \feiib\ photons whereas 
-the majority of photons absorbed at $\lambda \approx 2586$ are re-emitted 
-at longer wavelengths (\ion{Fe}{2}$^* \; \lambda 2612$ or $\lambda
-2632$).
+$\lambda \approx 2600$\AA\ are re-emitted as \feiib\ photons whereas 
+the majority of photons absorbed at $\lambda \approx 2586$\AA\ are re-emitted 
+at longer wavelengths (\feiic\ or $\lambda 2632$).
 If we were to increase $\tau_{2600}$ (and especially if we include
-gas with $\mvr \approx 0 \mkms$) then the emission at \feiib\ is
+gas with $\mvr \approx 0 \mkms$) then the \feiib\ emission is
 significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
@@
 \zconfig$_{7/2}$ upper level must still vanish (photons are conserved
-in this fiducial wind model).
-
-The preceding discussion emphasizes the filling-in of resonance absorption at $v
-\lesssim -50 \mkms$ and the generation of emission lines at $v \approx
+in this isotropic, dust-free model).
+
+The preceding discussion emphasizes the filling-in of resonance
+absorption at $\mdv
+\lesssim -50 \mkms$ and the generation of emission lines at $\mdv \approx
 0 \mkms$ by photons scattered in the wind.  To study the spatial
-extent of this emission, we performed 3D calculations with the fiducial
-model.  The output is a set of surface-brightness maps in a series of
+extent of this emission, we mapped the emission of the fiducial
+model (see $\S$~\ref{sec:monte} for a description of the algorithm).
+The output is a set of surface-brightness maps in a series of 
 frequency channels yielding a
@@
 at several velocities relative to the \mgiia\
-transition. At $v = -250 \mkms$, where the wind has an optical
+transition. At $\mdv = -250 \mkms$, where the wind has an optical
 depth $\tau_{2796} < 1$ (Figure~\ref{fig:fiducial_nvt}),
 the source contributes roughly half of the observed flux.  
-At $v=-100 \mkms$, however, the
+At $\mdv=-100 \mkms$, however, the
 wind absorbs all photons from the source and the observed emission is
@@
 actually exceeds the source+wind emission at 
-$v = -250 \mkms$ so that the absorption profile is
+$\mdv = -250 \mkms$ such that the absorption profile is
 negatively offset from the velocity where $\tau_{2796}$ is maximal
@@
 The net result is
-a weaker \ion{Mg}{2} absorption line peaks blueward of the peak in the
-optical depth profile.  Clearly, these effects complicate estimates for the
-speed, covering fraction, and total column density of the wind.  At $v
-= 0 \mkms$, the wind and source have comparable total flux with the
+weaker \ion{Mg}{2} absorption that peaks blueward of the actual peak in the
+optical depth profile.  
+Table~\ref{tab:line_diag} reports several kinematic measurements of
+the absorption and emission features.
+Clearly, these effects complicate estimates for the
+speed, covering fraction, and total column density of the wind.  At
+$\mdv = 0 \mkms$, the wind and source have comparable total flux with the
 latter dominating at higher velocities.
@@
 of the wind. 
-Figure~\ref{fig:fiducial_cuts} presents the relative flux for the 
-azimuthally symmetric surface-brightness maps collapsed along
-one spatial dimension.  The majority of
+The majority of
 \ion{Mg}{2} emission occurs within the inner few kpc, e.g.\ $50-60\%$
-of the light at $v=-100$ to $+100 \mkms$
+of the light at $\mdv=-100$ to $+100 \mkms$
 comes from $|r| < 3$\,kpc.
@@
 $5-10$\,kpc for $z \sim 1$.    We return to this issue in
-$\S$~\ref{sec:obs}.
+$\S$~\ref{sec:discuss}.
 
@@
 perhaps yielding a bi-conic morphology \citep[e.g.][]{M87}.
-Lastly, a galaxy could be surrounded by an
-anisotropic gaseous halo that would produce an irregularly shaped
-wind.
+Lastly, the galaxy could be surrounded by an
+anisotropic gaseous halo whose interaction would produce an irregular 
+outflow.
 
@@
 with the 3D algorithm after departing from isotropy.  It is beyond the
-scope of this paper to explore a full suite of anisotropic profiles;
-the following simply assumes half of the fiducial wind by setting
-the density to zero for $2\pi$ steradians.
-We have viewed this system from $\theta = 0^\circ$ where
-the source is observed directly to $\theta = 180^\circ$ where the source
-is covered by this anisotropic wind.  The resulting \ion{Mg}{2} and
-\ion{Fe}{2} profiles are compared against the fiducial model
+scope of this paper to explore a full suite of anisotropic profiles.
+We consider two simple examples: (i) half the fiducial model, where 
+the density is set to zero for $2\pi$ steradians.  This model is
+viewed from $\phi = 0^\circ$ (source uncovered) 
+to $\phi = 180^\circ$ (source covered); and 
+(ii) a bi-conical wind where the density is set to zero for angles
+$|\theta| < \theta_b$ that and is viewed along the plane of symmetry.
+
+The resulting \ion{Mg}{2} and
+\ion{Fe}{2} profiles for the half wind are compared against the fiducial model
 (isotropic wind) in Figure~\ref{fig:anisotropic}.  
-
 Examining the \mgiid\ doublet, 
-there is no attenuation of the source by the wind for $\theta =
-0^\circ$
-but one does observe significant line emission from photons scattered
-off the back side.  These photons, by definition, have $v \gtrsim 0 \mkms$
-relative to line-center (a subset have $v \lesssim 0 \mkms$ because
+the $\phi = 0^\circ$ model only shows
+line-emission from photons scattered
+off the back side.  These photons, by definition, have $\mdv \gtrsim 0 \mkms$
+relative to line-center (a subset have $\mdv \lesssim 0 \mkms$ because
 of turbulent motions in the wind). 
-When viewed from the opposite direction ($\theta = 180^\circ$), the
+When viewed from the opposite direction ($\phi = 180^\circ$), the
 absorption lines dominate but there is still significant
-line-emission -- at $v \approx 0 \mkms$ and at $v < 0 \mkms$ which fills
-in the absorption -- from photons that scatter through the wind.  The
+line-emission, at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
+in the absorption, from photons that scatter through the wind.  The
 key difference from the isotropic wind is the absence of photons
-scattered to $v > 100 \mkms$;  this also implies deeper 
-\mgiib\ absorption at $v \approx -100 \mkms$. The 
+scattered to $\mdv > 100 \mkms$;  this also implies deeper 
+\mgiib\ absorption at $\mdv \approx -100 \mkms$. The 
 shift in velocity centroid and asymmetry of the emission lines
@@
 conjunction with analysis of the absorption profiles. 
-
 The results are similar for the \feiid\ resonance lines.  The
 \ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows most clearly the
-offset in velocity between the source unobscured ($\theta = 0^\circ$)
-and source covered ($\theta = 180^\circ$) cases.  The offset of the
+offset in velocity between the source unobscured ($\phi = 0^\circ$)
+and source covered ($\phi = 180^\circ$) cases.  The offset of the
 \feiis\ lines is the most significant 
 difference from the fully isotropic wind.
+
+[Add a paragraph on the bi-conical wind]
 
@@
 
-Essentially all astrophysical environments that contain both cool gas
-and metals also show signatures of dust depletion and extinction.  This includes the
-ISM of star-forming and \ion{H}{1}-selected galaxies
-\citep[e.g.][]{ss96,pw01,pcd+07}, strong \ion{Mg}{2} metal-line
-absorption systems \citep{ykv+06,mnt+08}, and the galactic winds traced
-by low-ion transitions \citep{prs+02,rvs05b}.  Although the galactic winds
-traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
-demonstrated to contain dust, it is reasonable to consider its
-effects.
-
-Dust modifies the observed flux in two manners. 
+As described in $\S$~\ref{sec:dust_method}, 
+one generally expects dust in astrophysical environments that contain
+cool gas and metals.  This dust 
+modifies the observed wind profiles in two manners. 
 First, it is a source of opacity for all of 
@@
 profiles, this effect is essentially ignored.  Second, photons that are
-scattered by the wind will travel a greater
-distance and therefore suffer from greater extinction.  A photon that is
+scattered by the wind must travel a greater
+distance to escape and therefore suffer from greater extinction.  A photon that is
 trapped for many scatterings may have a very high probability of being absorbed
-by dust.  This process is
-often the explanation given for the weak (or absent) \lya\ emission
-associated with star-forming galaxies. 
-Section~\ref{sec:dust_method} describes our treatment of dust; we 
-remind the reader that we assume a constant dust-to-gas ratio 
-normalized by the total optical
-depth \taud\ that a photon would experience if it traveled from the
+by dust.  
+Section~\ref{sec:dust_method} describes the details on our treatment of dust; we 
+remind the reader here that we assume a constant dust-to-gas ratio 
+that is normalized by the total optical
+depth \taud\ a photon would experience if it traveled from the
 source to infinity without scattering.
@@
 models with $\mtaud > 0$.  For the \ion{Mg}{2} transitions, the
-dominant effect is the suppression of line emission at $v \ge 0
+dominant effect is the suppression of line emission at $\mdv \ge 0
 \mkms$.  These `red' photons have scattered off the
 backside of the wind and must travel a longer path than other
-photons.  Dust leads to a differential reddening that increases with wavelength (and
-velocity) relative to line-center. This is a natural consequence of dust
-extinction and is most evident in the \ion{Fe}{2}$^* \; \lambda 2612$
+photons.  Dust leads to a differential reddening that increases with 
+velocity relative to line-center. This is a natural consequence of dust
+extinction and is most evident in the \feiic\ 
 emission profile which is symmetrically distributed around
-$v=0 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
+$\mdv= 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
 nearly identical for $\mtaud \le 3$.  One requires very high
-extinction to see a deepening of the profiles at $v \approx -100 \mkms$.
+extinction to eventually produce a deepening of the profiles at 
+$\mdv \approx -100 \mkms$.
 
@@
 0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
-results related solely to the wind.  The decision to ignore the ISM
+results related solely to a wind component.  The decision to ignore the ISM
 was also motivated by the general absence of significant absorption at
-$v \approx 0 \mkms$ in galaxies that exhibit outflows 
+$\mdv \approx 0 \mkms$ in galaxies that exhibit outflows 
 \citep[e.g.][]{wcp+09,rubin09,steidel+10}.
-On the other hand, the stars and \ion{H}{2} regions that comprise our
-background sources are very likely embedded within and fueled by gas
-of the galactic ISM.  
-Consider, then, a modification to the fiducial model that has the
-same wind but also includes an ISM component. 
-Specifically, the ISM component has $n_{\rm H} = 1 \cm{-3}$ for
+On the other hand, the stars that comprise the
+source are very likely embedded within and fueled by gas
+of the ISM.  
+Consider, then, a modification to the fiducial model that 
+includes an ISM. 
+Specifically, we assume the ISM component has density $n_{\rm H} = 1 \cm{-3}$ for
 $r_{\rm ISM} \le r < r_{\rm inner}$ with $r_{\rm ISM} = 0.5$\,kpc, 
 an average velocity of $\mvr = 0 \mkms$, and a larger turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-Figure~\ref{fig:ISM} summarizes the model.
+%Figure~\ref{fig:ISM} summarizes the model.
 The resultant optical depth profile $\tau_{2796}$ is identical to the
-fiducial model for $r > 2$\,kpc, a slightly higher opacity at
-$r=1-2$\,kpc, and a large opacity at $r = 0.5-1$\,kpc.
+fiducial model for $r > 2$\,kpc, has a slightly higher opacity at
+$r=1-2$\,kpc, and has a very large opacity at $r = 0.5-1$\,kpc.
 
@@
 models. In comparison, the
-dotted curve shows the absorption profile for the ISM+wind in the (unphysical) case
+dotted curve shows the intrinsic absorption profile for the ISM+wind
+model corresponding to the (unphysical) case
 where none of the absorbed photons are scattered or re-emitted.   Focus first on the
 \ion{Mg}{2} doublet.  As expected, the dotted curve shows strong
-absorption at $v \approx 0 \mkms$ and blueward.  The full models,
+absorption at $\mdv \approx 0 \mkms$ and blueward.  The full models,
 in contrast, show non-zero flux at these velocities and even a
-normalized flux exceeding unity at $v \approx 0 \mkms$.  In
+normalized flux exceeding unity at $\mdv \approx 0 \mkms$.  In
 fact, the ISM+wind model is nearly identical to the fiducial model;
@@
 the emission lines are shifted redward by $\approx +100 \mkms$.
+We have also examined the spatial emission of this model and note
+qualitatively similar results to the fiducial wind model
+(Figures~\ref{fig:fiducial_ifu_mgii} and \ref{fig:fiducial_ifu_feii}).
 
@@
 First, the \feiia\ transition in the ISM+wind model
-shows much stronger absorption at $v \approx 0$
+shows much stronger absorption at $\mdv \approx 0$
 to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
@@
 the majority of \feiia\ photons that are absorbed are re-emitted as
-\ion{Fe}{2}~$^* \lambda\lambda 2612, 2632$ photons.  In fact, the
-ISM+wind \feiia\ profile nearly matches the profile without re-emission 
+\feiis\~$\lambda\lambda 2612, 2632$ photons.  In fact, the
+\feiia\ profile very nearly matches the profile without re-emission 
 (compare to the dotted lines); this transition provides a
 very good description of the intrinsic ISM+wind optical depth profile.  
-We conclude that resonant transitions tha are coupled to (multiple)
+We conclude that resonant transitions that are coupled to (multiple)
 non-resonant, electric dipole transitions offer the best
-diagnostic of ISM absorption.
+diagnosis of ISM absorption.
 
@@
 resonance lines; (2) the high opacity of the ISM component leads to
-an enhanced conversion of resonance photons with $v \approx 0\mkms$
+an enhanced conversion of resonance photons with $\mdv \approx 0\mkms$
 into \feiis\ photons.  This is especially notable for the
-\feiib\ transition whose `partner' shows an equivalent width nearly
+\feiib\ transition whose coupled \feiis\ transition shows an equivalent width nearly
 $10\times$ stronger than for the fiducial model.  The relative
@@
 
-[3D discussion; Figure~\ref{fig:ISM_ifu}]
-
-[Fix the bug in the FeII* emission]
-
-[Do dust too (as a green curve in Figure~\ref{fig:ISM_spec})]
+Because of the high degree of photon trapping within the ISM
+component, this model does suffer more from dust extinction than the
+fiducial model.  We have studied the ISM+wind model including dust
+with $\mtaud=1$ (normalized to include the ISM gas).  All of the 
+emission lines are significantly reduced.  The \ion{Mg}{2} emission is
+affect most because these lines are resonantly trapped.  The \feiis\
+emission is also reduced relative to the dust-free model, but the
+absolute flux still exceeds the fiducial model
+(Table~\ref{tab:line_diag}).
+[Should I show a figure?]
 
@@
 
-[Consider a series of models with the optical depth varying]
+The final modification we applied to the fiducial model was to
+uniformly vary the normalization of the optical depth profiles.
+Specifically, we ran a series of additional models with $n_H^0$ at
+1/3, 3, and 10 times the fiducial value of $n_H^{0,f} = 0.1 \cm{-3}$.
+The resulting \ion{Mg}{2} and \ion{Fe}{2} profiles are compared
+against the fiducial model in Figure~\ref{fig:norm}.  Inspecting
+\ion{Mg}{2}, one notes that the models with 1/3 and $3 n_H^{0,f}$
+behave as expected.  Higher optical depth leads to greater \mgiia\
+absorption and stronger \mgiib\ emission such that the observed
+\mgiib\ absorption profile weakens.  In the extreme case for the
+normalization of $10 n_H^{0,f}$, the \mgiib\ absorption and \mgiia\
+emission have nearly disappeared and one primarily observes very
+strong \mgiia\ absorption and \mgiib\ emission.
+
+Similar behaviour is observed for the \ion{Fe}{2} transitions.
+Interestingly, the \feiia\ transiions never show significant emission,
+only stronger absorption with increasing $n_H^0$.  In fact, for $n_H^0
+> 2 n_H^{0,f}$ the peak optical depth of \feiia\ actually exceeds that
+for \feiib\ because the latter remains significantly filled-in by
+scattered photons.  [Is there a final point to make?]
 
@@
 for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
-the fiducial model ($\S$~\ref{sec:fiducial}) and a set of the models
-presented in this section.  Listed are the
-equivalent widths (absorption and emission), the peak optical depth
-for the absorption $\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the
+the fiducial model ($\S$~\ref{sec:fiducial}) and a subset of the models
+presented in this section.  Listed are the absorption and emission
+equivalent widths ($W_{\rm a}, W_{\rm e}$), the peak optical depth
+for the absorption $\tau_{\rm pk}$, the
 velocity where the optical depth peaks $v_\tau$, the optical
@@
 flux-weighted velocity centroid of the emission line $v_{\bar f}$.
-
-One observes a wide range in these measures.  This emphasizes the
-challenges to convert 1D spectra to physical
-constraints on wind scenarios.  We consider these
-results further in $\S$~\ref{sec:obs}.
+We discuss several of these measures in $\S$~\ref{sec:discuss}.
 
@@
 \label{sec:alternate}
-
-\subsection{Power-Law Models}
-\label{sec:power}
-
-The models investigated in the previous two sections
-assumed power-law descriptions for both the density and velocity
-expressions of the wind (Equations~\ref{eqn:density},\ref{eqn:vel}).
-The power-law exponents were arbitrarily chosen, with minimal physical
-motivation.  In this sub-section, we explore the results for a series
-of other power-law expressions.
-We consider three different density laws ($n_{\rm H}(r) \propto
-r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr(r)
-\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
-(Table~\ref{tab:plaws}, Figure~\ref{fig:plaws}a).  [Comment in the Table how $\mvr$ is
-different when the velocity law is positive]  
-The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
-modified to yield an \mgiia\ optical depth profile that peaks at
-$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
-$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b).
-
-[Discuss models]
-
-[Refer to Table~\ref{tab:plaw_diag}]
-
-\subsection{Radiation Pressure}
-
-[Kate: Write the details of velocity + density law]
-
-\begin{equation}
-\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} \rtp
-   + \ln\ltp R_0/r \rtp }
-\end{equation}
-
-\begin{equation}
-n(r) = \frac{dM_{\rm wind}/dt}{r^2 v(r)}
-\end{equation}
-
-Figure~\ref{fig:rad_nvt}, \ref{fig:rad_spec}
 
@@
 the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
-damped \lya\ systems \citep{nbf98,schaye01a}, and XXX.  Although the
+damped \lya\ systems \citep{nbf98,schaye01a}, and the formation of
+`red and dead' galaxies \citep[e.g.][]{redgal}.  Although the
 presence of these outflows were established over a decade ago,
@@
 
-Recently, \cite[][; hereafter S10]{steidel+10} introduced a model to
+Recently, \citet[][; hereafter S10]{steidel+10} introduced a model to
 explain jointly the average absorption they observed
@@
 ensemble of small, optically thick $(\tau \gg 1)$ clouds that only
-partially cover a galactic-scale source (i.e.\ a few to 10\,kpc).
+partially cover a galactic-scale source.
 For the velocity law, they adopted the following functional
@@
 \end{equation}
-with $A_{\rm LBG}$ a constant that sets the terminal speed,
-$r_{inner}$ is the inner radius of the wind (taken to be 1\,kpc), and
-$\alpha$ describes how steeply the velocity curve rises.  Their
+with $A_{\rm LBG}$ the constant that sets the terminal speed,
+$r_{inner}$ the inner radius of the wind (taken to be 1\,kpc), and
+$\alpha$ the power-law exponent that describes how steeply the velocity curve rises.  Their
 analysis of the LBG absorption profiles implied
@@
 density and velocity gradient ($d\mvr/dr$) of the gas.  In our case, we 
-generate the optical depth profile from Equation~\ref{eqn:LBG_I},
+generate the optical depth profile in velocity space using Equation~\ref{eqn:LBG_I},
 
 \begin{equation}
-\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk \cmma
+\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk \perd
 \label{eqn:tauLBG}
 \end{equation}
-and invert the Sobolev approximation to derive the density profile.
-Following \cite{lc99}, we have for a purely radial flow
+We then invert the Sobolev approximation (Equation~\ref{eqn:Sobolev})
+to derive the radial density profile:
 
@@
 
-We verified that the density profile shown in
+We verified that the Sobolev-derived density profile shown in
 Figure~\ref{fig:LBG_Sobolev}a
@@
 shows the intensity profile when one ignores re-emission
-of absorbed photons.  By construction, it follows\footnote{Note that
+of absorbed photons.  By construction, it is the exact profile\footnote{Note that
   one should not make this comparison for the other transitions in
   the Sobolev model because those are scaled down by $f\lambda$ and
-  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} the profile
-described by Equation~\ref{eqn:LBG_I} as plotted in
+  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} 
+described by Equation~\ref{eqn:LBG_I} and plotted in
 Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
@@
 On the other hand, there have been no 
-reported detections of significant line-emission related to resonance
+reported detections of significant line-emission related to low-ion resonance
 transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
@@
 fraction.
-[Transition?]
-
-[Do CIV scattered photons bugger up the P-Cygni analysis of Pettini
-et al. ? I bet they do!]
 
@@
 reproduces the average absorption profile of LBGs in cool gas
-transitions where scattered photons are ignored.  A proper analysis of
-this wind model, however, predicts line profiles that are qualitatively
-different from the ones observed because scattered photons fill-in
+transitions when scattered photons are ignored.  A proper analysis
+that includes scattered photons,
+however, predicts line-profiles that are qualitatively
+different from the observations because these scattered photons fill-in
 absorption and generate significant line emission (similar to the
 fiducial wind model; $\S$~\ref{sec:fiducial}).
-The LBG-Sobolev model, however, differs from
-the one proposed by S10:  these authors proposed an ensemble of optically
+This LBG-Sobolev model, however, differs from
+the one proposed by S10:  those authors proposed an ensemble of optically
 thick clouds with the (partial) covering fraction described by
-Equation~\ref{eqn:covering} whereas the Sobolev model assumes
+Equation~\ref{eqn:covering}, whereas the Sobolev model assumes
 a diffuse medium with a declining density profile but a unit covering
-fraction.  At face value, one questions whether this difference leads to
-the contradictory results of the model.
+fraction.  At face value, one may question whether this difference
+causes the contradictory results of the LBG-Sobolev model.
 
@@
 scatters, we track the photon until it comes into
-resonance again or escapes the system.  In this model, all of the
+resonance again\footnote{Because this wind has a monotonically
+  increasing velocity law, the photon may only interact again if a
+  longer wavelength transition is available, e.g.\ \mgiib\ for a
+  scattered \mgiia\ photon.} or escapes the system.  In this model, all of the
 resonance transitions are assumed to have identical (high) optical
@@
 The results of the full calculation (absorption plus scattering) are
-shown as the black curve in Figure~\ref{fig:LBG_spec}.  The results
-are very similar to the Sobolev calculation; scattered photons fill-in
+shown as the black curve in Figure~\ref{fig:LBG_spec}.  Remarkably, the results
+are very similar to the LBG-Sobolev calculation; scattered photons fill-in
 the absorption profiles at $v \approx 0 \mkms$ and yield significant
 emission lines at $v \gtrsim 0 \mkms$ in the resonance
-lines. Furthermore, significant emission is observed at
-all velocities for the \feiis\ transitions.  For \feiia,
-the majority of absorbed photons have been converted to its
-fine-structure counterparts lending to very weak emission at this
-transition. The absorption profile very nearly matches the
-model without re-emission indicating that this transition well
-reproduces the opacity of the wind.  
+lines. Furthermore, significant emission is observed 
+for the \feiis\ transitions, centered at $\mdv \approx 0 \mkms$.  
+In contrast to the \ion{Mg}{2} profiles, the predicted \ion{Fe}{2}
+lines (especially \feiia) much more closely resembl the intrinsic
+profiles (dotted curves).  This occurs because many of these
+absorbed photons flouresce into \feiis\ emission.
 The equivalent width of \feiia\ even exceeds that for \feiib, an
 inversion that, if observed, would strongly support this model.
-[Could SiII or OI do the same?]
-
-Comparing the LBG Sobolev and parital covering models in
-Figure~\ref{fig:LBG_spec} (via \mgiia), we note nearly identical
-results.  The differences that occur for the other transitions,
-meanwhile, are only because the opacities are scaled downward in the
-Sobolev model (as required).  [Do the data prefer one to the other?
-And what if we modified the density away from Sobolev?]
-In principle, they provide a means to distinguish between the two LBG
-models.
-
-[Does most of the scattering occur within the inner few kpc? Explore
-this with outflow.cc]
-
-Given the essentially perfect correspondence between the Sobolev and
-partial covering models (for \mgiia), we are motivated to consider
-further the characteristics of the Sobolev model which has the
-distinct advantage of producing a 
-density profile.  It is straightforward, then, to convert the density and
+
+In principle, these differences may be reduced by increasing the
+assumed abundances of \nmg\ and \nfe.  A robust conclusion of our
+analysis, however, is that these simple models cannot reproduce the
+observed profiles of resonantly trapped lines like the \ion{Mg}{2}
+doublet because of the emission from scattered photons.  In order to
+achieve a significant opacity at $\mdv \approx 0 \mkms$, one must
+either suppress the line-emission (e.g.\ with severe dust extinction) 
+or include a substantial ISM component that absorbs light at $\mdv
+\gtrsim 0 \mkms$ (e.g.\ $\S$~\ref{sec:ISM}).  As we discuss in the
+following section, it is difficult (if not impossible) to fully
+suppress the line-emission.  This is especially true for a scenario
+with partial covering.
+
+Given the essentially perfect correspondence between the LBG-Sobolev and
+LBG partial covering models (for \mgiia), we are motivated to consider
+further the characteristics of the Sobolev model which has 
+an explicit density profile.  It is straightforward, then, to convert the density and
 velocity profiles into distributions of mass, energy, and momentum
@@
 LBG wind model.
-
 The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
@@
 the S10 model?]
+
+We also caution that the \ion{C}{4} emission observed for LBGs
+\citep[e.g.][]{cb58} may result from the galactic-scale outflow, not
+only the expected stellar winds of massive stars.
+
+%%%%%%%%%%%%%%%%%%%%%%%
+\subsection{Radiation Pressure}
+
+[Kate: Write the details of velocity + density law]
+
+\begin{equation}
+\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} \rtp
+   + \ln\ltp R_0/r \rtp }
+\end{equation}
+
+\begin{equation}
+n(r) = \frac{dM_{\rm wind}/dt}{r^2 v(r)}
+\end{equation}
+Similar to the fiducial wind model, this wind has a decreasing density
+law with $n_{\rm H}$ roughly proportional to $r^{-2}$ [CHECK].
+To produce a wind whose \mgiia\ optical depth profile peaks at 
+$\tau_{2796}^{\rm max} \gtrsim 10$, we set $R_g = r_{\rm inner} =
+1\,\rm kpc$, $R_0=20\,\rm kpc$, and $\sigma = 125 \mkms$.  The density
+and velocity peak at $r=r_{\rm inner}$ where $n_{\rm H}^0 = 0.07
+\cm{-3}$ and $\mvr = 380 \mkms$.  This corresponds to a mass flow of
+$0.63 \msun\; \rm yr^{-1}$.
+
+Figure~\ref{fig:rad_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
+profiles for a radiatively-driven wind model compared against the
+fiducial wind model.
+In contrast to the fiducial model, the
+velocity of the radiation-driven model decreases with increasing
+radius such that the optical depth peaks at large velocity (here $\mdv
+\approx -400 \mkms$).  At these velocities, the absorption is not
+filled-in by scattered photons such that one recovers absorption lines
+that very nearly match the intrinsic optical depth profile (dotted
+curve).  Although the \ion{Mg}{2} absorption profiles are very
+different from the fiducial model, the \ion{Mg}{2} line-emission has
+similar peak flux and velocity centroids (see also
+Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
+equivalent width, yet the lines are much broader for the
+radiative-driven model. This reflects the fact that the peak optical
+depth occurs at $\mdv \approx -400 \mkms$.
+
+%%%%%%%%%%%%%%%%%%%%
+\subsection{Power-Law Models}
+\label{sec:power}
+
+The models investigated in the previous two sections
+assumed power-law descriptions for both the density and velocity
+laws (Equations~\ref{eqn:density},\ref{eqn:vel}).
+The power-law exponents were arbitrarily chosen, i.e.\ with little physical
+motivation.  In this sub-section, we explore the results for a series
+of other power-law expressions.
+We consider three different density laws ($n_{\rm H} \propto
+r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr
+\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
+(Table~\ref{tab:plaw_parm}, Figure~\ref{fig:plaws}a).  
+[Comment in the Table how $\mvr$ is
+different when the velocity law is positive]  
+Each of these winds extends over the same inner and outer radii as the
+fiducial model.
+The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
+modified to yield an \mgiia\ optical depth profile that peaks at
+$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
+$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b). [Use Sobolev?]
+All models assume a Doppler parameter
+$b=15\mkms$, full isotropy, and a dust-free environment.
+Lastly, the abundance of Mg$^+$ and Fe$^+$ ions scale with hydrogen as
+in the fiducial model.
+
+Figure~\ref{fig:plaws_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
+profiles for the full suite of power-law models.  Although these
+models differ qualitatively from the fiducial model in their density
+and velocity laws, the resultant profiles share many of the same
+features.  Each shows significant absorption at $\mdv < 0 \mkms$ with
+the profiles extending to the velocity where $\tau_{2796} < 0.1$
+(Figure~\ref{fig:plaws}b).  All of hte models also exhibit strong
+line-emission, primarily at velocities $\mdv \sim 0 \mkms$.  
+This emission fills-in the \ion{Mg}{2} absorption at $\mdv \gtrsim
+-100 \mkms$ such that the profiles never achieve a relative flux less
+than $\approx 0.1$ at these velocities.  [Comment on exceptions]
+Similar to the radiative driven wind ($\S$~\ref{sec:radiate}),
+however, the power-law models that have significant opacity at $\mdv <
+-300 \mkms$ have larger peak optical depths.  Another commonality is
+the weak or absent line-emission at \feiia; one instead notes strong
+\feiic\ emission that generally excees the equivalent width of the
+fiducial model.
+
+One of the few distinctions of these models from the fiducial wind is
+the higher peak optical depth of absorption in the \feiib\
+transition.  This is predominantly due to the fact that several of
+these power law models have much higher peak optical depth in all
+transitions.  [Also due to ?]
+Table~\ref{tab:plaw_diag} compares measures of the absorption and
+emission profiles against the fiducial model.
+
+[Comment that $v(r)$ has a greater effect than $n(r)$.]
 
@@
 
-The previous sections presented a series of idealized wind models for
+The previous sections presented idealized wind models for
 cool gas outflows, and explored the absorption/emission profiles of
@@
 the ubiquitous presence of blue-shifted absorption, the wind models
-also generically predict strong line emission in both the resonance
+also predict strong line-emission in both resonance
 and non-resonance transitions.  For isotropic and dust-free scenarios,
-this is simple convservation of photon number: every photon emitted by
-the source eventually escapes the system with the wind only [slightly]
-shifting them in frequency space.  A principal result of this paper,
-therefore, is that cool gas outflows should generate detectable line
-emission.
-
-As noted in the introduction, there are several reports of line
-emission associated with star-forming galaxies that exhibit cool gas outflows.  
-[SHORTEN THE OBSERVER SUMMARY]
-[Phillips first reported?]
-Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
-reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
-and \cite{rubin+10c}.   
-\cite{wcp+09}, who
-studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
-\ion{Mg}{2} emission in a small subset of the individual galaxy
-spectra of their large sample.  These were excluded from the full
-analysis on concerns that the emission was related to AGN activity.
-The stacked spectra of the remaining galaxies, however, also indicated
-\ion{Mg}{2} emisison, both directly and when the authors modeled and
-`removed' the $v \approx 0\mkms$ absorption component.  Although the
-authors suggested the emission could be related to back-scattered
-light in the wind, they also allowed that it could be related to weak
-AGN activity.   Very similar \ion{Mg}{2} emission was observed by
-\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
-of lower redshift galaxies. 
-[Did Kate see FeII* emission in her stacks? If not, why not?]
+this is a simple convservation of photons: every photon emitted by
+the source eventually escapes the system maintaining an essentially
+zero total equivalent width. A principal result of this paper,
+therefore, is that cool gas outflows should generate detectable 
+line-emission.
+
+Indeed, line-emission from low-ion transitions has been reported from 
+star-forming galaxies that exhibit cool gas outflows.  
+This includes emission related to \ion{Na}{1} \citep{phillips,chen},
+\ion{Mg}{2} emission \citep{wcp+09,rwk+10}, 
+\ion{Si}{2}* emission from LBG galaxies \citep{shapley03},
+and most recently significant \feiis\ emission \citep{rubin+10c}. 
+These authors have proposed a variety of origins for this
+line-emission including AGN activity, recombination in \ion{H}{2}
+regions, and back-scattering off the galactic-scale wind.
 [Are there aspects of those works that are now understood, e.g. the
-difference in FeII 2586 and FeII 2600]
-At high redshift, \ion{Si}{2}* line emission has been reported from
-the Lyman break galaxies which was suggested to be
-related to \ion{H}{2} regions within the galaxies \citep{shapley03}.
-Lastly, \ion{Na}{1} line emission has also been detected in the
-stacked spectra of $z \sim 0$ galaxies by \cite{chen}.  
-We contend that all of these incidences may be examples of line
-scattered photons in the cool gas outflows of these star-forming
-galaxies.  Indeed, our results indicate that line emission could (and
-should) be produced by all of these galaxies if the outflows (and the
-galaxy emission) are nearly isotropic.
+difference in FeII 2586 and FeII 2600?]
+Our results suggest that the majority of this line-emission is 
+line-scattered photons in the cool gas outflows of these star-forming
+galaxies.  Indeed, our results indicate that line emission could and
+should be produced by all of these galaxies if the outflows 
+are nearly isotropic. [Add??]
 
@@
 detected yet the authors report no significant line emission.  This
-includes the \ion{Na}{1} flows reported by \cite{rupke} and
-\cite{martin}, the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
+includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
+the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
 ULIRGS by \cite{mb10}, and the extreme \ion{Mg}{2} outflows identified
 by \cite{tremonti}.  Similarly, there have been no reports of
-resonance line emission from the LBGs nor ... [Others]
-The multitude of non-detections stands in stark contradiction to the
-results presented in this paper.   We are motivated, therefore, to
-reassess several of the effects that may reduce the line emission
-and consider whether these may eliminate the line emission for many
+resonance line-emission from low-ion transitions in the LBGs\footnote{\citet{pettini02}
+  reported and analyzed \ion{C}{4} line-emission from the lensed LBG
+  cb58, attributing this flux to stellar winds.  We caution, however,
+  that the galactic-scale wind proposed to exist for cb58 should also
+  have contributed to the \ion{C}{4} line-emission.}, and a subset of
+$z \lesssim 1$ galaxies show no detectable \ion{Mg}{2} or \ion{Fe}{2}*
+emission (Rubin et al., in prep). 
+These non-detections appear to contradict a primary conclusion of 
+this paper.   We are motivated, therefore, to
+reassess several of the effects that can reduce the line-emission
+and consider whether these could preclude its detection for many
 star-forming galaxies.  [If MgII emission is 'common' for HII regions,
-why don't we see it *always* when we see OII, Hbeta, etc?  Same for
-FeII*]
+why don't we see it *always* when we see OII, Hbeta, etc? Is it
+trapped and then extincted? Same for FeII*]
+
+%% STOPPED HERE %%
 
@@
 \input{Tables/tab_meas_models.tex}
+\input{Tables/tab_plaw_parm.tex}
 \input{Tables/tab_meas_plaws.tex}
@@
 
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_ism_diagn.ps}
-\caption{
-Density (dashed; red), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (solid; black) for the ISM+wind
-model.  The wind is identical to that from the fiducial model
-(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
-with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
-\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-Note that the density and velocity curves have been scaled for plotting
-convenience.  
-}
-\label{fig:ISM}
-\end{figure}
+%\begin{figure}
+%\epsscale{0.8}
+%\plotone{Figures/fig_ism_diagn.ps}
+%\caption{
+%Density (dashed; red), radial velocity (dotted; blue), and
+%\mgiia\ optical depth profiles (solid; black) for the ISM+wind
+%model.  The wind is identical to that from the fiducial model
+%(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
+%with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
+%\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
+%Note that the density and velocity curves have been scaled for plotting
+%convenience.  
+%}
+%\label{fig:ISM}
+%\end{figure}
 
@@
 \epsscale{0.8}
-\plotone{Figures/fig_ism_ifu.ps}
-\caption{
-Surface-brightness emission maps for ISM+wind model
-}
-\label{fig:ISM_ifu}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_vary_profiles.ps}
-\caption{
-Power-law profiles
-}
-\label{fig:plaws}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
-\caption{
-Power-law profiles spectral lines
-}
-\label{fig:plaws_spec}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_radiation_nvt.ps}
-\caption{
-Radiation diagnosed
-}
-\label{fig:rad_nvt}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_rad_spec.ps}
-\caption{
-Radiation spec
-}
-\label{fig:rad_spec}
+\plotone{Figures/fig_norm_spec.ps}
+\caption{
+Varying normalization
+}
+\label{fig:norm}
 \end{figure}
@@
 
+%%%% RADIATIVE %%%%%%
+%\begin{figure}
+%\epsscale{0.8}
+%\plotone{Figures/fig_radiation_nvt.ps}
+%\caption{
+%Radiation diagnosed
+%}
+%\label{fig:rad_nvt}
+%\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_rad_spec.ps}
+\caption{
+\ion{Mg}{2} and \ion{Fe}{2}
+profiles for a radiation-driven wind model (red) compared against the
+fiducial wind model (black).  In contrast to the fiducial model, the
+velocity of the radiation-driven model decreases with increasing
+radius such that the optical depth peaks at large velocity (here $\mdv
+\approx -400 \mkms$).  At these velocities, the absorption is not
+filled-in by scattered photons such that one recovers absorption lines
+that very nearly match the intrinsic optical depth profile (dotted
+curve).  Although the \ion{Mg}{2} absorption profiles are very
+different from the fiducial model, the \ion{Mg}{2} line-emission has
+similar peak flux and velocity centroids (see also
+Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
+equivalent width, yet the lines are much broader for the
+radiative-driven model. This reflects the fact that the peak optical
+depth occurs at $\mdv \approx -400 \mkms$.
+}
+\label{fig:rad_spec}
+\end{figure}
+
+%%%% POWER LAWS %%%%
+\begin{figure}
+\epsscale{0.8}
+\plotone{Figures/fig_vary_profiles.ps}
+\caption{
+Power-law profiles
+}
+\label{fig:plaws}
+\end{figure}
+
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
+\caption{
+Power-law profiles spectral lines
+}
+\label{fig:plaws_spec}
+\end{figure}
+
 \begin{figure}

### 2010-08-16 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5130 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 Dust is frequently invoked to explain the suppression of line emission
-related to a resonantly trapped line (e.g.\ \lya).  Indeed, a photon
-that is trapped for many scatterings within a dust medium will be
-preferentially extincted relative to a non-resonant photon.  In
-$\S$~\ref{sec:dust}, we examined the effects of dust extinction on the
+related toresonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
+that is trapped for many scatterings within a dusty medium will 
+preferentially be extincted relative to a non-resonant photon.  In
+$\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
 \ion{Mg}{2} and \ion{Fe}{2} emission.  The general result was a modest
 suppression of the line flux of the order of (1+\taud)$^{-1}$ instead of
-exp(--\taud).   [Do a series of models and fit a functional form for
-the fiducial model]  Although the \ion{Mg}{2} photons are resonantly
-trapped within the outflow, they require only one to a few scatterings
-to escape the fiducial wind model and dust has only a
-modest effect.  This reflects the [modest] opacity of the \ion{Mg}{2}
-doublet (e.g.\ relative to \lya) but also the specific characteristics
-of the wind.  We have also experimented with dust in several of the
-other models (e.g.\ the ISM+wind scenario) and find similar results.
-[Dust does reduce the $v \sim 0$ emission in the ISM+wind model more,
-as it is more effectively trapped.  Discuss this somewhere..  Also
-note that the EW of the absorption is higher for an ISM model so that
-the absolute value of EW emission is higher too for FeII*]
-Another reason \ion{Mg}{2} is less susceptible than \lya\ is that the
-latter may be generated through the flourescence of an ionizing
-photon, i.e.\ via a recombination cascade.  The ionizing photons 
-would penetrate deeper into the outflow and more effectively trap the
-\lya\ photon [is this right?].
-
+exp(--\taud). Although the \ion{Mg}{2} photons are resonantly
+trapped, they require only one to a few scatterings
+to escape the wind model and dust has only a
+modest effect.  This results from the moderate opacity of the \ion{Mg}{2}
+doublet (e.g.\ relative to \lya) and also the velocity law of the
+fiducial wind model.
+As we have discussed, in scenarios where the \ion{Mg}{2} photons are
+more effectively trapped (i.e.\ for many scatterings), dust suppresses
+the emission further.
 We also emphasize that the \ion{Fe}{2} resonance photons, especially
 \feiia, are converted to non-resonant photons and escape the wind
-freely.  A wind model that effectively trapped \ion{Mg}{2}
-photons for many scatterings would not be expected to trap the
-\feiid\ photons.  Therefore, the effects of dust are 
+freely.  Therefore, a wind model that trapped \ion{Mg}{2}
+photons for many scatterings would not similarly trap 
+\feiid\ photons.  The effects of dust are much 
 reduced for \ion{Fe}{2}* and, by inference, any other set of
 transitions that are coupled to a fine-structure level (e.g.\
-\ion{Si}{2} and \ion{Si}{2}*).  
-Although dust does reduce the line flux relative to the continuum, we
-conclude that it has only a modest effect on \ion{Mg}{2} and
-\ion{Fe}{2}* emission.
-
-Another factor that reduces the predicted line emission is a
-non-isotropic wind model,e.g.\ the flux is reduced if there is no
-backside of the wind.  To zeroth order, the line emission scales
+\ion{Si}{2} and \ion{Si}{2}*).  In summary,
+dust does reduce the line flux relative to the continuum, but we
+conclude that it has only a modest effect on the predicted \ion{Mg}{2}
+and \ion{Fe}{2}* emission.
+
+Another factor that may reduce the line-emission is a
+non-isotropic wind model. One may lower the flux, for example,  by
+removing the backside to the wind (e.g.\ the source itself could
+shadow a significant fraction of the backside).  To zeroth order, the line emission scales
 roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
 wind\footnote{There is also a first order dependence on the actual
-  orientation of the wind with emission maximal if the backside is
-  fully present.}.  Because we require that the wind is at least
-pointing towards us, it is difficult to reduce $\Omega$ signficantly
+  orientation of the wind, with maximal emission when the backside is
+  fully viewed.}.  Because we require that the wind 
+points toward us, it is difficult to reduce $\Omega$ signficantly
 below $2 \pi$.  Therefore, we expect this effect to reduce the
-emission by a factor of order unity.  
-[The notion of the source absorbing all photons that scatter into it
-is akin to removing the backside]
-
-By a similar [token], an anisotropic source could alter the predicted
-line emission.  For example, if the backside of the galaxy were
-brighter/fainter than would one predict brighter/fainter emission
+emission by at most a factor of order unity.  
+Similarly, an anisotropic source may alter the predicted
+line-emission.  For example, if the backside of the galaxy were
+brighter/fainter then would one predict brighter/fainter emission
 relative to the observed continuum.
 To reduce the emission, the brightest regions
-of the galaxy would need to be oriented toward Earth.  Although this would not a
+of the galaxy would need to be oriented toward Earth.  Although this
+would not be a
 generic occurance, most spectroscopic samples are magnitude-limited
-and therefore biased to detecting galaxies at their brightest.
-
-Together, dust and non-isotropic wind models can reduce line emission
-by a factor of a few.  We suggest, however, that this would generally
-not be sufficient to reduce the emission below the typical detection
+and therefore biased to detecting galaxies when viewed at their
+highest fluxes.
+
+Together, dust and non-isotropic wind models may reduce the line-emission
+of \ion{Mg}{2} and \ion{Fe}{2}
+by a factor of order unity.  This would generally
+not be sufficient, however, to reduce the emission below the typical detection
 limits.
 
-There is another, more subtle effect that in principle will
-substantially reduce the observed line emission: slit losses.  As
+There is another (more subtle) effect that in principle will
+substantially reduce the observed line emission: slit-loss.  As
 described in Figures~\ref{fig:fiducial_ifu_mgii} and
 \ref{fig:ISM_ifu}, emission from the wind is spatially extended with
-at least modest surface brightness at large radii implying a
-non-negligible total luminosity from well beyond the galaxy.  
+a non-zero surface brightness predicted at large radii. This implies 
+a non-negligible luminosity emitted well beyond the galaxy.  
 The majority of observations of star-forming galaxies to date have
-been taken through a spectroscopic slit typically designed to cover
-the brightest continuum regions of the galaxy.  A slit with an angular
-extent of $1-1.5''$ subtends roughly $8-15$\,kpc for galaxies at $z>0.5$.
-Therefore, a slit covering a galaxy with our fiducial wind would cover
-less than half of the wind.  The result will be reduced line emission,
-especially in comparison with the galaxy continuum.
-
-We have investigated the effect of a [partial] aperture as follows.
-We model the slit as a perfect, infinte rectangle centered on the
-galaxy.  We then tabulate the equivalent width of the line emission
-through slits with a range of widths, parameterized by the radius
-where the wind has an effective optical depth in the line of $\tau =
-0.2$ (\rtt)\footnote{Specifically, we determine the
-  velocity where $\tau(v) = 0.2$ and then use the velocity law to
-  convert to a radius.}.   We expect the line emission is weak beyond
+been taken through a spectroscopic slit designed to cover
+the brightest continuum regions of the galaxy. Slits with angular
+extents of $1-1.5''$ subtend roughly $8-15$\,kpc for galaxies at $z>0.5$.
+Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
+less than half the wind.  The result will be reduced line emission,
+even when compared to the galaxy continuum.
+
+We explore the effects of slit-loss as follows.
+We model the slit as a perfect, infinitely-long rectangle centered on the
+galaxy.  We then tabulate the equivalent width of the line-emission
+through slits with a range of widths, parameterized by twice the radius
+where the wind has a Sobolev optical depth of $\tau^S = 0.2$ (\rtt).
+The line-emission will be weak beyond
 this radius because the photons have only a low probability of
 interacting with the wind.  For the fiducial wind model, $\mrtt
-\approx 15$\,kpc for \mgiia\ (Figure~\ref{fig:fiducial_nvt}).
+\approx 15$\,kpc for the \mgiia\ transition (Figure~\ref{fig:fiducial_nvt}).
 
@@
 equivalent width \ewabs\ is presented in
-Figure~\ref{fig:obs_slit} for a set of transitions (black curves).
+Figure~\ref{fig:obs_slit} for a series of transitions for the fiducial
+wind model (black curves).
+[Add LBG, radiative]
 The curves rise very steeply with increasing slit width and then
@@
 in this paper (colored curves in Figure~\ref{fig:obs_slit}).
-We conclude that slit losses would be important for slits that do not
-cover a majority of the wind.   Again, the effect is of order unity
-unless the slit width is very small.   Provided the winds do not
-extend far beyond 10\,kpc, the majority of emission will be subtended
-by stnadard slit observations.  Nevertheless, the results do motivate
-the usage of extended apertures, e.g.\ integral field unit (IFU)
+All of the curves rise so steeply that 
+the effect is of slit-loss is of order unity
+unless the slit-width is very small.   
+Nevertheless, the results do motivate
+extended aperture observations, e.g.\ integral field unit (IFU)
 instrumentation that would map the wind both spatially and spectrally.
 
-Although there are several effects that will reduce line emission
-relative to the absorption produced by the outflow, our analysis
-indicates that detectable line emission should be present for [the
-majority] of winds.  One of the principal effects of this emission is
+Although several effects can reduce the line-emission
+relative to the absorption of the outflow, our analysis
+indicates that detectable line-emission should occur. 
+A principal effect of this emission is
 that it modifies the observed absorption profiles (e.g.\
-Figure~\ref{fig:noemiss}) which may lead to erroneous conclusions
-regarding characteristics of the flow.  {\it Analysis of cool gas outflows
-that ignores emission may incorrectly lead to conclusions the gas is
+Figure~\ref{fig:noemiss}). This may lead to erroneous conclusions
+regarding several characteristics of the flow.  {\it An anaaaalysis of cool gas outflows
+that ignores line-emission may incorrectly conclude that the gas is
 partially covered, has a significantly lower peak optical depth,
-and/or that a $v \sim 0 \mkms$ ISM component (perhaps even infall) is
-absent.}  Figure~\ref{fig:obs_ew} demonstrates a simple observational
-consequence of the line emission: reduced estimates for the absorption
+and/or that a $\mdv \sim 0 \mkms$ component is
+absent.}  Figure~\ref{fig:obs_ew} demonstrates one observational
+consequence of the line emission: reduced measurements for the absorption
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
 which has the most affected transitions, the \ewabs\ is reduced by
-$30-50\%$ for the wind models presented in this paper.  This could
-yield a systematically lower optical depth for the wind and therefore
-a lower total mass and kinetic energy.  Although not apparent in
-Figure~\ref{fig:obs_ew}, the effects are most pronounced for wind
-scenarios where the peak optical depth occurs near $v = \mkms$.
-Simple geometric projection limits the majority of scattered photon emission to
-have $v \approx \pm 200 \mkms$ and the absorption profiles
+$30-50\%$ from the intrinsic absorption.  In turn, one may derive 
+a systematically lower optical depth or velocity extent for the wind,
+and therefore a lower total mass and kinetic energy.  
+The effects are most pronounced for wind
+scenarios where the peak optical depth occurs near $\mdv = 0 \mkms$.
+Geometric projection limits the majority of scattered photon emission to
+have $|\mdv| < 200 \mkms$; therefore,  the absorption profiles
 are filled-in primarily at these velocities.  In
 Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
-for \mgiia\ 
-versus the velocity where $\tau = \tau_{pk}$ for the various wind models (i.e.\
-$\tau_{pk}$ vs.\ $v_\tau$ from Tables~\ref{tab:line_diag},
-\ref{tab:plaw_diag}).   In every one of the models, the intrinsic peak
-optical depth exceeds 10 and occasionally exceeds 100.  For the
-majority of cases with $v_\tau < -300\mkms$, one observes $\tau_{pk} <
+$tau_{\rm pk}$ for \mgiia\ 
+versus the velocity where the profile has greatest depth 
+for the various wind models (i.e.\
+$\tau_{\rm pk}$ vs.\ $v_\tau$ from Tables~\ref{tab:line_diag} and
+\ref{tab:plaw_diag}).   In every one of the models, the true peak
+optical depth $\tau_{\rm pk}^{\rm true} > 10$.  For the
+majority of cases with $v_\tau > -300\mkms$, one observes $\tau_{\rm pk} <
 2$ and would infer the wind is not even optically thick!
-The results are similar for \mgiib\ although one infers a somewhat
-higher column density because of its lower $f\lambda$ value.
-In the majority of cases, one would faslely conclude that hte wind
-partially covered the source and also estimate a peak optical depth
-lower than the intrinsic.
-
-All of these (negative) effects for \ion{Mg}{2} absorption are reduced
+This occurs because photons scattered by the wind have `filled-in' the
+absorption at velocity $\mdv \approx 0 \mkms$.  In contrast, the wind
+models with $v_\tau < -400 \mkms$ all give $\tau_{\rm pk} > 3$.  The
+results are similar for the \mgiib\ profile.  In fact, one infers a
+very similar $\tau_{\rm pk}$ for the two lines which would generally
+lead to the false conclusion of partial covering (and, correctly, a
+higher $\tau_{\rm pk}^{\rm true}$).  [Last thought?\
+
+All of these (somewhat negative) effects for \ion{Mg}{2} absorption are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
-is because a signficant fraction (or even a majority) of the
+is because a signficant fraction (even a majority) of the
 \ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
-wavelengths which have no effect on the absorption profiles. [word]
+wavelengths, which has no effect on the absorption profiles. 
 Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
@@
 optical depths, and the absorption kinematics more faithfully reflect
-the motions of the flow.  Regarding the last point, one 
-predicts a velocity offset between the peak depth of the \ion{Fe}{2}
-centroid and that for \ion{Mg}{2} (Figure~\ref{fig:obs_vtau})
-especially when the peak occurs at $v > -400 \mkms$.  One is simply
-not sensitive to opacity at $v \sim 0 \mkms$ with the \ion{Mg}{2}
-transitions.  This includes gas realted tothe ISM of the galaxy and
-also infalling material with modest speeds.  One must take careful
+the motions of the flow.  Regarding the last point, one also
+predicts a velocity offset between the \ion{Fe}{2} and \ion{Mg}{2}
+centroids (Figure~\ref{fig:obs_vtau}).
+One is simply
+less sensitive to absorption at $v \sim 0 \mkms$ with the \ion{Mg}{2}
+transitions.  This includes gas realted to the ISM of the galaxy and
+also material infalling at a modest speed.  One must take careful
 consideration of line emission, therefore,  before drawing robust
 conclusions aobut the presence/absence of gas with small velocity
-offsets from systemic.
+offsets from systemic. [Comment on MgII moving too fast]
 
@@
 characteristics of the wind.
+
+[Relative strengths of MgII 2796 and 2803 speak to $\tau$ and
+$v_r^{max}$]
 

### 2010-08-17 Winds/papers/Theory/First/wind_simple.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5132 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\tpk}{$\tau_{\rm pk}$}
+\newcommand{\mtpk}{\tau_{\rm pk}}
 \newcommand{\mdv}{\delta v}
@@
 \subsection{Radiation Pressure}
+\label{sec:radiative}
 
@@
 
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_fiducial_cut.ps}
-\caption{
-The panels show the relative emission from the wind as a function of
-radius for (a) \mgiia\ and (b) \feiib\ in a series of velocity
-channels.  With the exception of $v = -100 \mkms$ for \mgiia, the wind
-has finite transmission such that one observes the source at $r =
-0$\,kpc.  In all cases,  the majority of emission occurs at $r
-\lesssim 2.5$\,kpc, even if one ignores the source emission.
-}
-\label{fig:fiducial_cuts}
-\end{figure}
+%\begin{figure}
+%\epsscale{0.8}
+%\plotone{Figures/fig_fiducial_cut.ps}
+%\caption{
+%The panels show the relative emission from the wind as a function of
+%radius for (a) \mgiia\ and (b) \feiib\ in a series of velocity
+%channels.  With the exception of $v = -100 \mkms$ for \mgiia, the wind
+%has finite transmission such that one observes the source at $r =
+%0$\,kpc.  In all cases,  the majority of emission occurs at $r
+%\lesssim 2.5$\,kpc, even if one ignores the source emission.
+%}
+%\label{fig:fiducial_cuts}
+%\end{figure}
 
@@
 case (black lines) compared against an anisotropic wind blowing into
-only $2\pi$ steradians as viewed from $\theta = 0^\circ$ (source
-uncovered) to $\theta = 180^\circ$ (source covered).  One detects
+only $2\pi$ steradians as viewed from $\phi = 0^\circ$ (source
+uncovered) to $\phi = 180^\circ$ (source covered).  One detects
 significant emission for all orientations of this wind but significant
-absorption only for $\theta \ge 90^\circ$.
+absorption only for $\phi \ge 90^\circ$.
 The velocity centroid of the 
-emission shifts from positive to negative velocities as $\theta$
+emission shifts from positive to negative velocities as $\phi$
 increases and one transitions from viewing the wind to be behind the
@@
 \caption{
-Power-law profiles spectral lines
+\ion{Mg}{2} and \ion{Fe}{2} profiles for a series of power-law wind
+models described in Table~\ref{tab:plaw_parm}.  These panels reveal
+the diversity of absorption and emission that result from a set of
+intrinsic optical depth profiles that have relatively modest
+differences (Figure~\ref{fig:plaws}b).  As designed, all of the models
+show significant absorption blueward of systemic velocity.  As
+important, each shows strong line-emission at $\mdv \sim 0 \mkms$,
+with the flux proportional to the degree of absorption.
 }
@@
 \caption{
-Slit width effects
+Emission equivalent width ($W_{\rm e}$) relative to the observed
+absorption equivalent width ($W_{\rm a}$) for a series of transitions:
+(solid -- \mgiia; dotted -- \mgiiab; dashed -- \feiib).  The
+\ewe/\ewabs\ ratio is plottd as a function of slit width relative to
+twice the radius \rtt, defined to be where the Sobolev optical depth 
+$\tau^S = 0.2$.  The black curves correspond to the fiducial wind
+model ($\S$~\ref{sec:fiducial}), the red curves are for the
+LBG-partial covering scenario ($\S$~\ref{sec:Covering}), and the
+radiative-driven wind ($\S$~\ref{sec:radiative}) has blue curves.
+For all of the wind models, the \ewe/\ewabs\ ratio rises very steeply
+with slit width and plataeus at $\approx \mrtt$.  [Add?]
 }
@@
 \caption{
-EW effect
+Difference between the `observed' absorption equivalent width \ewabs\
+which includes the flux of scattered photons and the intrinsic
+equivalent width $W_{\rm i}$ that ignores photon scattering.  The
+dashed (dotted) curves trace a 50\%\ (10\%) reduction in \ewabs\
+relative to $W_{\rm i}$.  One notes a reduction in \ewabs by $\approx
+30-50\%$ for the \mgiia\ transition (the effect is generally larger
+for \mgiib).  The effects of scattered photons are reduced for the
+\ion{Fe}{2} transitions because a fraction (in fact a majority for
+\feiia) of the absorbed photons flourecse as \feiis\ emission at
+longer wavelengths and do not `fill-in' the absorption profiles.
 }
@@
 \caption{
-EW effect
+The observed peak optical depth $\tau_{\rm pk} \equiv -\ln [I_{\rm
+  min}]$ for \mgiia\ profiles of the wind models studied in this paper
+(Tables~\ref{tab:line_diag}, \ref{tab:plaw_diag}) with $I_{\rm min}$
+the minimum normalized intensity of the absorption profile.  Cases
+where \tpk\ exceeds 3 are presented as lower limits.  The \tpk\ values
+are plotted against the velocity $v_\tau$ where $I(v) = I_{\rm min}$.  In all
+of the models, the true peak optical depth $\mtpk^{\rm true} > 10$.
+The much lower `observed' values occur because scattered \mgiia\
+photons have filled-in the absorption profiels at velocities $\mdv
+\gtrsim -400 \mkms$.  Therefore, the effects are greates for wind
+models where the optical depth peaks near $\mdv \sim 0 \mkms$.
+Indeed, models with $v_\tau < -400 \mkms$ all show $\mtkp > 3$.
 }
@@
 \caption{
-Velocity offset
+Comparison of the velocities where the \feiia\ and \mgiia\ absorption
+profiles have observed peak optical depth.  Results for all the models
+studied in this paper are presented (Tables~\ref{tab:line_diag},
+\ref{tab:plaw_diag}).  The dashsed curve traces the one-to-one line.
+It is evident that for wind models have a peak optical depth near the
+systemic velocity, the \mgiib\ absorption profile is shifted blueward
+by one to several hundred \kms.  One may therefore falesly conclude
+that (i) the majority of mass in the wind is travelling at a higher
+velocity; and (ii) there is no gas with $\mdv \sim 0 \mkms$.
 }

### 2010-08-17 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc

@@ -12,7 +12,7 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  2e7;    // number of photons
+double n_photons =  1e8;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters

### 2010-08-17 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5133 ac11df5e-a788-c23b-a8e1-c758c323924d

--- 2010-08-17 Winds/papers/Theory/First/wind_simple.tex
@@
 
+\newcommand{\msun}{M_\odot}
 \newcommand{\tpk}{$\tau_{\rm pk}$}
@@
 \citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
-\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin09}, and
+\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rwk+10}, and
 $z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
@@
 tandem with the nearly ubiquitous blue-shifted absorption
-\citep{wcp+09,rubin09,rubin+10b}.  The resultant spectra resemble the P-Cygni
+\citep{wcp+09,rwk+10}.  The resultant spectra resemble the P-Cygni
 profile characteristic of stellar winds.
-\cite{rubin+10a} have also detected line
+\cite{rubin+10c} have also detected line
 emission from non-resonant \ion{Fe}{2}$^*$ transitions 
@@
 scattered off the wind into our sightline, analogous to P-Cygni.
-\cite{rubin+10a} also observed spatially extended \ion{Mg}{2} emission
+\cite{rubin+10c} also observed spatially extended \ion{Mg}{2} emission
 which they use to estimate the size of the outflow.  They infer that
@@
 Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
-reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
-and \cite{rubin+10c}.   
+reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
+and Rubin et al.\ 2011 (in prep).
 \cite{wcp+09}, who
@@
 AGN activity.   Very similar \ion{Mg}{2} emission was observed by
-\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
+\cite{rwk+10} who repeated the analysis of \cite{wcp+09} on a set
 of lower redshift galaxies. 
@@
 saturated) which only partially covers the emitting source
-\citep[e.g.][]{hamann+10}.  Our fiducial wind model, however, 
+\citep[e.g.][]{hammann+10}.  Our fiducial wind model, however, 
 {\it entirely covers the source}; the apparent partial covering must
@@
 $\mdv \approx 0 \mkms$ in galaxies that exhibit outflows 
-\citep[e.g.][]{wcp+09,rubin09,steidel+10}.
+\citep[e.g.][]{wcp+09,rwk+10,steidel+10}.
 On the other hand, the stars that comprise the
@@
 the majority of \feiia\ photons that are absorbed are re-emitted as
-\feiis\~$\lambda\lambda 2612, 2632$ photons.  In fact, the
+\feiis$\lambda\lambda 2612, 2632$ photons.  In fact, the
 \feiia\ profile very nearly matches the profile without re-emission 
@@
 transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
-\citep{wcp+09,rubin09}.  
+\citep{wcp+09,rwk+10}.  
 The principal result is that the scattering and re-emission of
@@
 We also caution that the \ion{C}{4} emission observed for LBGs
-\citep[e.g.][]{cb58} may result from the galactic-scale outflow, not
+\citep[e.g.][]{prs+02} may result from the galactic-scale outflow, not
 only the expected stellar winds of massive stars.
@@
 the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
-ULIRGS by \cite{mb10}, and the extreme \ion{Mg}{2} outflows identified
-by \cite{tremonti}.  Similarly, there have been no reports of
-resonance line-emission from low-ion transitions in the LBGs\footnote{\citet{pettini02}
+ULIRGS by \cite{mb09}, and the extreme \ion{Mg}{2} outflows identified
+by \cite{tmd07}.  Similarly, there have been no reports of
+resonance line-emission from low-ion transitions in the
+LBGs\footnote{\citet{psa+00}
   reported and analyzed \ion{C}{4} line-emission from the lensed LBG
@@
 substantially reduce the observed line emission: slit-loss.  As
-described in Figures~\ref{fig:fiducial_ifu_mgii} and
-\ref{fig:ISM_ifu}, emission from the wind is spatially extended with
+described in Figure~\ref{fig:fiducial_ifu_mgii}, 
+emission from the wind is spatially extended with
 a non-zero surface brightness predicted at large radii. This implies 
@@
 The most direct measure provided by the line emission is an estimate
-of the size and morphology of the outflow \citep[e.g.][]{rubin_emiss}.  
+of the size and morphology of the outflow \citep[e.g.][]{rubin+10c}.  
 Line emission is predicted to extend to radii where the Sobolev
@@
 
-\input{Tables/table_atomic.tex}
-\input{Tables/tab_fiducial.tex}
-\input{Tables/tab_fiducial_ew.tex}
-\input{Tables/tab_meas_models.tex}
-\input{Tables/tab_plaw_parm.tex}
-\input{Tables/tab_meas_plaws.tex}
+\input{../Tables/table_atomic.tex}
+\input{../Tables/tab_fiducial.tex}
+\input{../Tables/tab_fiducial_ew.tex}
+\input{../Tables/tab_meas_models.tex}
+\input{../Tables/tab_plaw_parm.tex}
+\input{../Tables/tab_meas_plaws.tex}
 
@@
 \epsscale{0.95}
-\plotone{Figures/energy_levels.ps}
+\plotone{../Figures/energy_levels.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_nvtau_vs_r.ps}
+\plotone{../Figures/fig_nvtau_vs_r.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_fiducial_1d.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_noemiss.ps}
+\plotone{../Figures/fig_noemiss.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_fiducial_ifu_mgii.ps}
+\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_feii_ifu.ps}
+\plotone{../Figures/fig_feii_ifu.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_asymm_spec.ps}
+\plotone{../Figures/fig_asymm_spec.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_dust_spec.ps}
+\plotone{../Figures/fig_dust_spec.ps}
 \caption{
@@
 \epsscale{0.7}
-\plotone{Figures/fig_ism_spec.ps}
+\plotone{../Figures/fig_ism_spec.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_norm_spec.ps}
+\plotone{../Figures/fig_norm_spec.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_lbg_sobolev.ps}
+\plotone{../Figures/fig_lbg_sobolev.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_lbg_spec.ps}
+\plotone{../Figures/fig_lbg_spec.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_lbg_cumul.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_rad_spec.ps}
+\plotone{../Figures/fig_rad_spec.ps}
 \caption{
@@
 \epsscale{0.8}
-\plotone{Figures/fig_vary_profiles.ps}
+\plotone{../Figures/fig_vary_profiles.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_slit.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
 \caption{
@@
 absorption equivalent width ($W_{\rm a}$) for a series of transitions:
-(solid -- \mgiia; dotted -- \mgiiab; dashed -- \feiib).  The
+(solid -- \mgiia; dotted -- \mgiib; dashed -- \feiib).  The
 \ewe/\ewabs\ ratio is plottd as a function of slit width relative to
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_ew.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_peaktau.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
 \caption{
@@
 models where the optical depth peaks near $\mdv \sim 0 \mkms$.
-Indeed, models with $v_\tau < -400 \mkms$ all show $\mtkp > 3$.
+Indeed, models with $v_\tau < -400 \mkms$ all show $\mtpk > 3$.
 }
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_vtau.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_lris.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_sb.ps}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
 \caption{

### 2010-08-18 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5137 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\nhn}{$n_{\rm H}^0$}
+\newcommand{\mnhn}{n_{\rm H}^0}
 \newcommand{\msun}{M_\odot}
@@
 \newcommand{\feiib}{\ion{Fe}{2}~$\lambda 2600$}
-\newcommand{\feiic}{\ion{Fe}{2}$* \; \lambda 2612$}
-\newcommand{\feiie}{\ion{Fe}{2}$* \; \lambda 2626$}
+\newcommand{\feiic}{\ion{Fe}{2}*$ \; \lambda 2612$}
+\newcommand{\feiie}{\ion{Fe}{2}*$ \; \lambda 2626$}
 \newcommand{\feiid}{\ion{Fe}{2}~$\lambda\lambda 2586, 2600$}
-\newcommand{\feiis}{\ion{Fe}{2}$*$}
+\newcommand{\feiis}{\ion{Fe}{2}*}
 \newcommand{\nmg}{$n_{\rm Mg^+}$}
@@
 the wind at a given radius $\tau(r)$ in terms of the density and
-velocity gradient of the flow at that radius:
+velocity gradient of the flow at that radius;
 
 \begin{equation}
-\tau^S(r) = \kappa_\ell \rho(r) \, \lambda_\ell \ltp \frac{dv}{dr}
-\rtp^{-1}
+\tau^S(r) = \kappa^\ell \rho(r) \, \lambda^\ell \ltp \frac{dv}{dr} 
+\rtp^{-1}  \cmma
 \label{eqn:Sobolev}
 \end{equation}
-where $\kappa_\ell$ is the opacity of transition $\ell$.  The opacity
-holds for a photon with wavelength $\lambda^S
-= \lambda_\ell (1-v(r)/c)$ with the velocity evaluated at the radius.
-This is, of course, not the true opacity.
-A photon with wavelength $\lambda^S$ that travels through the wind 
+where $\kappa^\ell$ is the opacity of transition $\ell$.  This opacity
+applies to a photon with wavelength $\lambda^S
+\equiv \lambda^\ell (1-v(r)/c)$.
+This is, of course, not the true opacity;
+a photon with wavelength $\lambda^S$ that travels through the wind 
 experiences a total opacity 
-$\tau_\nu = \intl_0^\infty \rho(r) \kappa_\nu dr$.  The Sobolev
+$\tau_\nu^\ell = \intl_0^\infty \rho(r) \kappa_\nu^\ell dr$.  The Sobolev
 approximation is valid when the opacity the photon experiences is
-domianted by gas in a localized portion of the flow that has velocity
-$v = c(\lambda^S/\lambda^\ell - 1)$.  In this case, $\tau^S$ provides an
-excellent approximation.  We find that it applies to nearly all of the
-models presented in this paper.  [Comment on the lack of the $b$-value
-in this?]
+domianted by gas in a localized portion of the flow.
+We find that it applies to nearly all of the
+models presented in this paper and therefore provides a convenient
+approach to estimating $\tau^\ell_\nu$.
 
@@
 
-The final modification we applied to the fiducial model was to
+The final modification to the fiducial model considered was to
 uniformly vary the normalization of the optical depth profiles.
-Specifically, we ran a series of additional models with $n_H^0$ at
-1/3, 3, and 10 times the fiducial value of $n_H^{0,f} = 0.1 \cm{-3}$.
+Specifically, we ran a series of additional models with $n_{\rm H}^0$ at
+1/3, 3, and 10 times the fiducial value of $n_{\rm H}^{0,f} = 0.1 \cm{-3}$.
 The resulting \ion{Mg}{2} and \ion{Fe}{2} profiles are compared
 against the fiducial model in Figure~\ref{fig:norm}.  Inspecting
-\ion{Mg}{2}, one notes that the models with 1/3 and $3 n_H^{0,f}$
-behave as expected.  Higher optical depth leads to greater \mgiia\
-absorption and stronger \mgiib\ emission such that the observed
-\mgiib\ absorption profile weakens.  In the extreme case for the
-normalization of $10 n_H^{0,f}$, the \mgiib\ absorption and \mgiia\
+\ion{Mg}{2}, one notes that the models with 1/3 and $3 n_{\rm H}^{0,f}$
+behave as expected.  Higher/lower optical depths lead to
+greater/weaker \mgiia\ absorption and stronger/weaker \mgiib\ emission
+In the extreme case of
+$n_{\rm H}^0 = 10 n_{\rm H}^{0,f}$, the \mgiib\ absorption and \mgiia\
 emission have nearly disappeared and one primarily observes very
 strong \mgiia\ absorption and \mgiib\ emission.
+In essence, this wind has converted all of the photons absorbed by the
+\ion{Mg}{2} doublet into \mgiib\ emission.
 
@@
 Interestingly, the \feiia\ transiions never show significant emission,
-only stronger absorption with increasing $n_H^0$.  In fact, for $n_H^0
-> 2 n_H^{0,f}$ the peak optical depth of \feiia\ actually exceeds that
+only stronger absorption with increasing $n_{\rm H}^0$.  In fact, for $n_{\rm H}^0
+> 2 n_{\rm H}^{0,f}$ the peak optical depth of \feiia\ actually exceeds that
 for \feiib\ because the latter remains significantly filled-in by
-scattered photons.  [Is there a final point to make?]
+scattered photons.  By the same token, the flux of the \feiic\
+emission increases with \nhn.
 
@@
 
+This section presents several additional wind scenarios that differ
+significantly from the fiducial model explored in the previous
+sections.  In each case, we maintain the simple assumption of
+isotropy.
+
 \subsection{The Lyman Break Galaxy Model}
@@
 Researchers have invoked these winds to explain enrichment of
-the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
+the intergalactic medium \citep[e.g.][]{ahs+01,spa+06}, the origin of the
 damped \lya\ systems \citep{nbf98,schaye01a}, and the formation of
@@
 explain jointly the average absorption they observed
-toward a set of several hundred LBGs and the average absorption in gas
+along the sightlines to several hundred LBGs and the average absorption in gas
 observed transverse to these galaxies.  
@@
 ensemble of small, optically thick $(\tau \gg 1)$ clouds that only
-partially cover a galactic-scale source.
+partially cover the galaxies.
 For the velocity law, they adopted the following functional
@@
 with $A_{\rm LBG}$ the constant that sets the terminal speed,
-$r_{inner}$ the inner radius of the wind (taken to be 1\,kpc), and
+$r_{\rm inner}$ the inner radius of the wind (taken to be 1\,kpc), and
 $\alpha$ the power-law exponent that describes how steeply the velocity curve rises.  Their
@@
 fraction.  From this expression and the velocity law, one can recover
-an absorption profile $I_{\rm LBG}(v) = 1 - f_c(r[v])$, written
+an absorption profile $I_{\rm LBG}(v) = 1 - f_c[r(v)]$, written
 explicitly as
@@
 The resulting profile for $f_{c,max} = 0.6$, $\gamma=0.5$,
-$\alpha=1.3$, and $A_{\rm LBG} = -192,000 \, \rm km^2 s^{-2} kpc^{-2}$ 
+$\alpha=1.3$, and $A_{\rm LBG} = -192,000 \, \rm km^2 \, s^{-2} \, kpc^{-2}$ 
 is displayed in Figure~\ref{fig:LBG_Sobolev}b.
@@
 In the following, we consider two methods to analyze the LBG wind.
-Both approaches assume isotropy and adopt the velocity law given by
+Both approaches assume an isotropic wind and adopt the velocity law given by
 Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
@@
 the Monte Carlo methodology used for the other wind models to predict
-\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other model,
+\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other LBG model,
 we modify our algorithms to more precisely mimic the concept of an
@@
 \begin{equation}
-n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa_\ell
-  \lambda} \cmma
-\label{eqn:Sobolev}
+n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa^\ell
+  \lambda^\ell} \cmma
+\label{eqn:nSobolev}
 \end{equation}
-with $\lambda$ the rest wavelength and $\kappa_\ell \equiv f\pi^2
-e^2/m_e c$.
+with $\lambda^\ell$ the rest wavelength and $\kappa^\ell \equiv f^\ell
+\pi^2 e^2/m_e c$.
 
@@
 shows the intensity profile when one ignores re-emission
-of absorbed photons.  By construction, it is the exact profile\footnote{Note that
+of absorbed photons.  By construction, it is the same profile\footnote{Note that
   one should not make this comparison for the other transitions in
@@
 shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
-due to scattered photons.
+because scattered photons fill in the absorption profile.
 In this respect, our LBG-Sobolev model is an
@@
 \citep{wcp+09,rwk+10}.  
-The principal result is that the scattering and re-emission of
+The principal result of the LBG-Sobolev model is that the scattering and re-emission of
 absorbed photons significantly alters the predicted absorption profiles
@@
 fraction.
+
+Because we have explicit velocity and densities profiles for the LBG-Sobolev
+model, it is straightforward to calculate the radial
+distributions of mass, energy, and momentum of
+the wind.  These are shown in cumulative form in
+Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
+two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
+assumes a very poorly constrained scalar factor of $10^{5.47}$.  One
+should give minimal weight to the absolute values for any of the
+quantities;
+(ii) the Sobolev approximation is not a proper description of the S10
+LBG wind model (see the following sub-section).
+The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
+majority of energy, mass, and momentum in the wind is transported by
+the outer layers ($r > 20$\,kpc).  This is surprising given that the
+density is $\approx 5$~orders of magnitude lower at these radii than
+at $r = 1$\,pc.
 
@@
 however, predicts line-profiles that are qualitatively
-different from the observations because these scattered photons fill-in
-absorption and generate significant line emission (similar to the
+different from the observations because scattered photons fill-in
+absorption and generate significant line-emission (similar to the
 fiducial wind model; $\S$~\ref{sec:fiducial}).
@@
 the one proposed by S10:  those authors proposed an ensemble of optically
-thick clouds with the (partial) covering fraction described by
-Equation~\ref{eqn:covering}, whereas the Sobolev model assumes
+thick clouds with a partial covering fraction described by
+Equation~\ref{eqn:covering}.  In contrast, the Sobolev model assumes
 a diffuse medium with a declining density profile but a unit covering
 fraction.  At face value, one may question whether this difference
-causes the contradictory results of the LBG-Sobolev model.
+leads to the contradictory results of the LBG-Sobolev model.
 
 To more properly model the LBG wind described in S10, we 
-performed the following Monte Carlo calculation.  First, we propogated
+performed the following Monte Carlo calculation.  First, we propogate
 a photon from the source until its velocity relative to line-center
@@
   scattered \mgiia\ photon.} or escapes the system.  In this model, all of the
-resonance transitions are assumed to have identical (high) optical
-depth.
+resonance transitions are assumed to have identical (infinite) optical
+depth at line center.
 
@@
 In contrast to the \ion{Mg}{2} profiles, the predicted \ion{Fe}{2}
-lines (especially \feiia) much more closely resembl the intrinsic
+lines (especially \feiia) much more closely resemble the intrinsic
 profiles (dotted curves).  This occurs because many of these
@@
 
-In principle, these differences may be reduced by increasing the
-assumed abundances of \nmg\ and \nfe.  A robust conclusion of our
-analysis, however, is that these simple models cannot reproduce the
+A robust conclusion of our
+analysis is that these simple models cannot reproduce the
 observed profiles of resonantly trapped lines like the \ion{Mg}{2}
@@
 following section, it is difficult (if not impossible) to fully
-suppress the line-emission.  This is especially true for a scenario
-with partial covering.
-
-Given the essentially perfect correspondence between the LBG-Sobolev and
-LBG partial covering models (for \mgiia), we are motivated to consider
-further the characteristics of the Sobolev model which has 
-an explicit density profile.  It is straightforward, then, to convert the density and
-velocity profiles into distributions of mass, energy, and momentum
-within
-the wind.  These are shown in cumulative form in
-Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
-two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
-assumes a very poorly constrained scalar factor of $10^{5.47}$.  One
-should give minimal weight to the absolute values for any of the
-quantities;
-(ii) the Sobolev approximation is not a proper description of the S10
-LBG wind model.
-The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
-majority of energy, mass, and momentum in the wind is transported by
-the outer layers ($r > 20$\,kpc).  This is surprising given that the
-density is $\approx 5$~orders of magnitude lower at these radii than
-at $r = 1$\,pc.  [Is this unphysical?  Can we conflate it to then kill
-the S10 model?]
-
-We also caution that the \ion{C}{4} emission observed for LBGs
-\citep[e.g.][]{prs+02} may result from the galactic-scale outflow, not
+suppress the line-emission,  especially for scenarios that invoke
+partial covering.  We conclude, therefore, that the LBG model
+introduced by S10 is not a valid description of the data.
+
+Lastly, we caution that resonant line-emission observed for LBGs
+\citep[e.g.\ \ion{C}{4};][]{prs+02} may result from the galactic-scale outflow, not
 only the expected stellar winds of massive stars.
+A proper treatment of these radiative transfer effects is required to
+quantitatively analyze these features.
 
@@
 Similar to the fiducial wind model, this wind has a decreasing density
-law with $n_{\rm H}$ roughly proportional to $r^{-2}$ [CHECK].
+law with $n_{\rm H}$ roughly proportional to $r^{-2}$. 
 To produce a wind whose \mgiia\ optical depth profile peaks at 
@@
 \cm{-3}$ and $\mvr = 380 \mkms$.  This corresponds to a mass flow of
-$0.63 \msun\; \rm yr^{-1}$.
+$dM_{\rm wind}/dt = 0.63 \msun\; \rm yr^{-1}$.
 
 Figure~\ref{fig:rad_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
-profiles for a radiatively-driven wind model compared against the
+profiles for this radiation-driven wind model compared against the
 fiducial wind model.
@@
 Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
-equivalent width, yet the lines are much broader for the
-radiative-driven model. This reflects the fact that the peak optical
+equivalent width, yet the lines of the radiation-driven model are much
+broader. This reflects the fact that the peak optical
 depth occurs at $\mdv \approx -400 \mkms$.
+[Last point]
 
@@
 
-The models investigated in the previous two sections
-assumed power-law descriptions for both the density and velocity
+The fiducial model assumed power-law descriptions for both the density and velocity
 laws (Equations~\ref{eqn:density},\ref{eqn:vel}).
@@
 motivation.  In this sub-section, we explore the results for a series
-of other power-law expressions.
+of other power-law expressions, also arbitarily defined.
 We consider three different density laws ($n_{\rm H} \propto
@@
 (Table~\ref{tab:plaw_parm}, Figure~\ref{fig:plaws}a).  
-[Comment in the Table how $\mvr$ is
-different when the velocity law is positive]  
 Each of these winds extends over the same inner and outer radii as the
@@
 modified to yield an \mgiia\ optical depth profile that peaks at
-$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
-$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b). [Use Sobolev?]
+$\tau_{2796}^{\rm max} \approx 10-10^3$ and then usually decreases to
+$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b). 
 All models assume a Doppler parameter
@@
 Lastly, the abundance of Mg$^+$ and Fe$^+$ ions scale with hydrogen as
-in the fiducial model.
+in the fiducial model ($\S$~\ref{sec:fiducial}).
 
@@
 the profiles extending to the velocity where $\tau_{2796} < 0.1$
-(Figure~\ref{fig:plaws}b).  All of hte models also exhibit strong
+(Figure~\ref{fig:plaws}b).  All of the models also exhibit strong
 line-emission, primarily at velocities $\mdv \sim 0 \mkms$.  
 This emission fills-in the \ion{Mg}{2} absorption at $\mdv \gtrsim
--100 \mkms$ such that the profiles never achieve a relative flux less
-than $\approx 0.1$ at these velocities.  [Comment on exceptions]
+-100 \mkms$ such that the profiles rarely achieve a relative flux less
+than $\approx 0.1$ at these velocities. 
 Similar to the radiative driven wind ($\S$~\ref{sec:radiate}),
@@
 the weak or absent line-emission at \feiia; one instead notes strong
-\feiic\ emission that generally excees the equivalent width of the
+\feiic\ emission that generally exceeds the equivalent width of the
 fiducial model.
 
-One of the few distinctions of these models from the fiducial wind is
+One of the few obvious distinctions of these models from the fiducial wind is
 the higher peak optical depth of absorption in the \feiib\
-transition.  This is predominantly due to the fact that several of
-these power law models have much higher peak optical depth in all
-transitions.  [Also due to ?]
+transition.  This is predominantly due to the 
+higher peak optical depth of this transition. 
 Table~\ref{tab:plaw_diag} compares measures of the absorption and
 emission profiles against the fiducial model.
-
-[Comment that $v(r)$ has a greater effect than $n(r)$.]
-
-%\section{Observables}
-%\label{sec:obs}
-%
-%%Although the focus of this paper is to explore the absorption/emission
-%profiles for idealized wind models, we ultimately intend to compare 
-%profiles like these against observations to constrain characteristics
-%of the wind (e.g.\ radial extent, energetics).  In this section we
-%consider a few observables and their dependence on the wind properties.
-%
-%\subsection{Absorption profiles}
-%
-% \begin{enumerate}
-%   \item Peak optical depth
-%     \begin{itemize}
-%       \item Not a robust measure of $\tau_{wind}$
-%       \item Not even a good relative predictor for $\tau$
-%       \item Not a robust predictor of $f_c$
-%       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
-%     \end{itemize}
-%   \item Kinematics
-%     \begin{itemize}
-%       \item Nearly robust for $v<v_{min}$
-%       \item But what sets $v_{min}$?
-%       \item Generally get the full extent of the wind speed
-%       \item Plot $v_{pk}$ vs $\tau_{pk}$
-%     \end{itemize}
-%   \item EW
-%     \begin{itemize}
-%       \item Primarily set by $v_{min}(\tau \sim 1)$
-%       \item $f\lambda$ matters, but so do emission channels
-%       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
-%     \end{itemize}
-%   \item Fine-structure
-%     \begin{itemize}
-%       \item Distance to the source
-%     \end{itemize}
-% \end{enumerate}
-%     
-%\subsection{Emission profiles}
-%
-% \begin{enumerate}
-%   \item Resonant lines
-%     \begin{itemize}
-%       \item Kinematics of backside
-%       \item Flux + relative
-%       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
-%    \end{itemize}
-%   \item Fine-structure
-%     \begin{itemize}
-%       \item Flux $\propto \tau_{wind}$ + relative
-%       \item Kinematics (anisotropy)
-%    \end{itemize}
-% \end{enumerate}
-
+In detail, the line profiles do differ in their peak optical depths,
+the velocity centroids of absorption, and the total equivalent widths.
+We find that most of these differences are driven by differences in
+the velocity laws, i.e.\ the kinematics of the outflow.
+[Last point]
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Focuses on the observational consequences and implications if our results.
+We now discuss the principal results of our analysis and comment on
+the observational consequences and implications.
 

### 2010-08-20 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/model_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5142 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -40,6 +40,7 @@ double MODEL::Velocity(double r)
 }
 
 double MODEL::Covering(double r)
+{
   if (r <= r_inner) return 0.;
   return LBG_fc * pow(r/r_inner, -1*LBG_gamma);
 }

### 2010-08-20 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/transport_lbg.cc

@@ -7,7 +7,7 @@
 #include "locate_array.hh"
 #include "anvoigt.hh"
 #include "spectrum.hh"
-#include "model.hh"
+#include "model_lbg.hh"
 #include "lines.hh"
 #include "physical_constants.hh"
 
@@ -36,16 +36,16 @@ double stepfrac = 0.7;
 void Run_Monte_Carlo(double n_photons)
 {
   // local variables
-  int    i, scatter;
+  int    i, scatter, l_scat;
   int l, flg_resonance[50];
-  double tau_r, tau_x, rad;
+  double tau_r, tau_x, rad, r_sq, cover;
   double l_step, step, max_step;
   double Pe, lobs, r_rot[3];
   PHOTON p;
 
   // functions to call
   void MPI_Average_Array(double *, int);
-  double P_esc(double, double*);
+  double P_esc(double, double*, int);
   double Get_vdotD(double,double*, double*);  // Vector only
   void Emit(PHOTON*, double);
   void Line_Scatter(PHOTON&, double, double*);
@@ -63,11 +63,16 @@ void Run_Monte_Carlo(double n_photons)
     p.E_p = model.L_tot/(1.0*n_photons); 
 
     // add in straight light
-    Pe   = P_esc(p.lloc,p.r);  // This one need not be unity
+    Pe   = P_esc(p.lloc,p.r, -1);  // This one need not be unity
     lobs = p.lloc*(1 - Get_vdotD(model.r_emit, p.r,D_obs)/C_LIGHT);
     Get_Rotated_Coords(p.r,r_rot);
-    spectrum.Count(1,lobs,r_rot[0],r_rot[1],p.E_p*Pe);
+    spectrum.Count(1,lobs,abs(r_rot[0]),abs(r_rot[1]),p.E_p*Pe);
 
+    // Did we escape right out?
+    if (Pe > 0.99999) continue;
+    // printf("# Got here \n");
+
+    // Reset the flag
     for (l=0;l<50;l++) flg_resonance[l] = 0;
 
     // propogate until escaped (unless nothing stands in the way)
@@ -89,9 +94,10 @@ void Run_Monte_Carlo(double n_photons)
       max_step = step;
 
       scatter = -1;
+      l_scat = -1;
 
[…]

### 2010-08-21 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5142 ac11df5e-a788-c23b-a8e1-c758c323924d
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5144 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\mnhn}{n_{\rm H}^0}
+\newcommand{\mnhf}{n_{\rm H}^{0,f}}
 \newcommand{\msun}{M_\odot}
@@
 ground-state.   This process may also be referred to as flourescence.
+Note that two of these transitions (\feiis$\; \lambda\lambda 2626, 2632$) are
+close enough in energy that their line profiles can overlap.
 
@@
 ground-state, i.e.\ the gas has zero opacity to the non-resonant
-lines.
-If collisional excitation is insignificant 
+lines.  If collisional excitation is insignificant 
 then one may also neglect collisional de-excitation.  
@@
 to be smaller than the minimum radial extent of any gaseous
-component.
+component.   Lastly, the source does not absorb any scattered or
+emitted photons.
 
@@
 emission profile which is symmetrically distributed around
-$\mdv= 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
+$\mdv= 0 \mkms$ in the $\mtaud=0$ model.   
+The degree of suppression of the line-emission is relatively modest,
+however.  Specifically, we find that the flux is reduced by a factor 
+of the order of (1+\taud)$^{-1}$ (Figure~\ref{fig:dust_tau},
+instead of the factor
+exp(--\taud) that one may have naively predicted. 
+Although the \ion{Mg}{2} photons are resonantly
+In terms of absorption, the profiles are
 nearly identical for $\mtaud \le 3$.  One requires very high
@@
 and non-resonance transitions.  For isotropic and dust-free scenarios,
-this is a simple convservation of photons: every photon emitted by
-the source eventually escapes the system maintaining an essentially
+this is a simple conservation of photons: every photon emitted by
+the source eventually escapes the system maintaining 
 zero total equivalent width. A principal result of this paper,
@@
 \ion{Si}{2}* emission from LBG galaxies \citep{shapley03},
-and most recently significant \feiis\ emission \citep{rubin+10c}. 
-These authors have proposed a variety of origins for this
+and, most recently, significant \feiis\ emission \citep{rubin+10c}. 
+A variety of origins have been proposed for this
 line-emission including AGN activity, recombination in \ion{H}{2}
@@
 Our results suggest that the majority of this line-emission is 
-line-scattered photons in the cool gas outflows of these star-forming
+from scattered photons in the cool gas outflows of these star-forming
 galaxies.  Indeed, our results indicate that line emission could and
-should be produced by all of these galaxies if the outflows 
-are nearly isotropic. [Add??]
+should be produced by all of galaxies driving a wind.
 
@@
 includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
-the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
-ULIRGS by \cite{mb09}, and the extreme \ion{Mg}{2} outflows identified
+\ion{Mg}{2} and \ion{Fe}{2} absorption in
+ULIRGS \citep{mb09}, and the extreme \ion{Mg}{2} outflows identified
 by \cite{tmd07}.  Similarly, there have been no reports of
@@
   that the galactic-scale wind proposed to exist for cb58 should also
-  have contributed to the \ion{C}{4} line-emission.}, and a subset of
+  have contributed to the \ion{C}{4} line-emission.}, and many
 $z \lesssim 1$ galaxies show no detectable \ion{Mg}{2} or \ion{Fe}{2}*
-emission (Rubin et al., in prep). 
+emission despite significant blue-shifted absorption (Rubin et al., in prep). 
 These non-detections appear to contradict a primary conclusion of 
@@
 Dust is frequently invoked to explain the suppression of line emission
-related toresonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
+related to resonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
 that is trapped for many scatterings within a dusty medium will 
@@
 $\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
-\ion{Mg}{2} and \ion{Fe}{2} emission.  The general result was a modest
-suppression of the line flux of the order of (1+\taud)$^{-1}$ instead of
+\ion{Mg}{2} and \ion{Fe}{2} emission.  The general result
+(Figure~\ref{fig:dust_tau}) is the modest
+suppression of line flux that scales with (1+\taud)$^{-1}$ instead of
 exp(--\taud). Although the \ion{Mg}{2} photons are resonantly
@@
 to escape the wind model and dust has only a
-modest effect.  This results from the moderate opacity of the \ion{Mg}{2}
+modest effect.  This reflects the moderate opacity of the \ion{Mg}{2}
 doublet (e.g.\ relative to \lya) and also the velocity law of the
@@
 As we have discussed, in scenarios where the \ion{Mg}{2} photons are
-more effectively trapped (i.e.\ for many scatterings), dust suppresses
-the emission further.
-We also emphasize that the \ion{Fe}{2} resonance photons, especially
-\feiia, are converted to non-resonant photons and escape the wind
-freely.  Therefore, a wind model that trapped \ion{Mg}{2}
+more effectively trapped, dust further suppresses
+the emission (e.g.\ the ISM+wind model from $\S$~\ref{sec:ISM}).
+In contrast to \ion{Mg}{2}, 
+the \ion{Fe}{2} resonance photons may be
+converted to non-resonant photons that freely escape the wind.
+Therefore, a wind model that trapped \ion{Mg}{2}
 photons for many scatterings would not similarly trap 
 \feiid\ photons.  The effects of dust are much 
-reduced for \ion{Fe}{2}* and, by inference, any other set of
+reduced and, by inference, the same holds for any other set of
 transitions that are coupled to a fine-structure level (e.g.\
-\ion{Si}{2} and \ion{Si}{2}*).  In summary,
-dust does reduce the line flux relative to the continuum, but we
-conclude that it has only a modest effect on the predicted \ion{Mg}{2}
-and \ion{Fe}{2}* emission.
+\ion{Si}{2}/\ion{Si}{2}*).  In summary,
+dust does reduce the line flux relative to the continuum, but 
+often has only a modest effect on the predicted \ion{Mg}{2}
+emission and always a minor effect on \feiis\ emission.
 
 Another factor that may reduce the line-emission is a
-non-isotropic wind model. One may lower the flux, for example,  by
-removing the backside to the wind (e.g.\ the source itself could
-shadow a significant fraction of the backside).  To zeroth order, the line emission scales
+non-isotropic wind model. The flux is lower, for example, if one
+eliminates the backside to the wind (e.g.\ the source itself could
+shadow a significant fraction of the backside).  To zeroth order, the
+line-emission scales 
 roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
@@
   fully viewed.}.  Because we require that the wind 
-points toward us, it is difficult to reduce $\Omega$ signficantly
-below $2 \pi$.  Therefore, we expect this effect to reduce the
-emission by at most a factor of order unity.  
+points toward us, it is difficult to reduce $\Omega$ much
+below $2 \pi$ and, therefore, anisotropic winds reduce the
+emission by a factor of order unity.  
 Similarly, an anisotropic source may alter the predicted
@@
 of the galaxy would need to be oriented toward Earth.  Although this
-would not be a
+hould not be a
 generic occurance, most spectroscopic samples are magnitude-limited
-and therefore biased to detecting galaxies when viewed at their
-highest fluxes.
+and biased towards detecting galaxies when observed from their
+brightest viewpoint.  In principle, this might imply a further
+reduction of order unity.
 
@@
 
-There is another (more subtle) effect that in principle will
-substantially reduce the observed line emission: slit-loss.  As
+There is another (more subtle) effect that could
+greatly reduce the observed line emission: slit-loss.  As
 described in Figure~\ref{fig:fiducial_ifu_mgii}, 
@@
 Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
-less than half the wind.  The result will be reduced line emission,
-even when compared to the galaxy continuum.
+less than half the wind.  The result is reduced line-emission,
+when compared to the galaxy continuum.
 
@@
 this radius because the photons have only a low probability of
-interacting with the wind.  For the fiducial wind model, $\mrtt
-\approx 15$\,kpc for the \mgiia\ transition (Figure~\ref{fig:fiducial_nvt}).
+interacting with the wind.  For the fiducial wind model, 
+the \mgiia\ transition has $\mrtt \approx 15$\,kpc 
+(Figure~\ref{fig:fiducial_nvt}).
 
@@
 wind model (black curves).
-[Add LBG, radiative]
-The curves rise very steeply with increasing slit width and then
-plateau when the slit width is $\approx \mrtt$.  
+[Add LBG, radiative models]
+The \ewe/\ewabs\ curves rise very steeply with increasing slit width and then
+plateau when the slit width reaches $\approx \mrtt$.  
 The results are comparable for other wind models considered
@@
 All of the curves rise so steeply that 
-the effect is of slit-loss is of order unity
+the effects of slit-loss is of order unity
 unless the slit-width is very small.   
@@
 relative to the absorption of the outflow, our analysis
-indicates that detectable line-emission should occur. 
-A principal effect of this emission is
-that it modifies the observed absorption profiles (e.g.\
+indicates that detectable line-emission should occur frequently. 
+Furthermore, the line-emission could be suppressed so as not to exceed
+the galaxy continum yet still (partially) fill-in the absorption
+profiles. Indeed, dust and anisotropic winds preferentially suppress
+line-emission at $\mdv > 0 \mkms$
+(Figures~\ref{fig:dust},\ref{fig:anisotropic}).
+The emission would still 
+modify the observed absorption profiles (e.g.\
 Figure~\ref{fig:noemiss}). This may lead to erroneous conclusions
-regarding several characteristics of the flow.  {\it An anaaaalysis of cool gas outflows
-that ignores line-emission may incorrectly conclude that the gas is
+regarding several characteristics of the flow.  {\it An analysis of cool gas outflows
+that entirely ignores line-emission may incorrectly conclude that the gas is
 partially covered, has a significantly lower peak optical depth,
 and/or that a $\mdv \sim 0 \mkms$ component is
-absent.}  Figure~\ref{fig:obs_ew} demonstrates one observational
-consequence of the line emission: reduced measurements for the absorption
+absent.}  
+We now consider several quantitative effects of the line-emission.
+
+Figure~\ref{fig:obs_ew} demonstrates one observational
+consequence: reduced measurements for the absorption
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
@@
 have $|\mdv| < 200 \mkms$; therefore,  the absorption profiles
-are filled-in primarily at these velocities.  In
-Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
-$tau_{\rm pk}$ for \mgiia\ 
+are filled-in primarily at these velocities.
+
+Another (related) consequence is the reduction of peak depth of the
+absorption.
+In Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
+$\tau_{\rm pk}$ for \mgiia\ 
 versus the velocity where the profile has greatest depth 
@@
 This occurs because photons scattered by the wind have `filled-in' the
-absorption at velocity $\mdv \approx 0 \mkms$.  In contrast, the wind
-models with $v_\tau < -400 \mkms$ all give $\tau_{\rm pk} > 3$.  The
+absorption at velocity $\mdv \approx 0 \mkms$.  In contrast, wind
+models with $v_\tau < -400 \mkms$ all yield $\tau_{\rm pk} > 3$.  The
 results are similar for the \mgiib\ profile.  In fact, one infers a
 very similar $\tau_{\rm pk}$ for the two lines which would generally
-lead to the false conclusion of partial covering (and, correctly, a
-higher $\tau_{\rm pk}^{\rm true}$).  [Last thought?\
-
-All of these (somewhat negative) effects for \ion{Mg}{2} absorption are reduced
+lead to the false conclusion of partial covering. 
+[Last point]
+
+Tf these negative effects for \ion{Mg}{2} absorption are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
@@
 predicts a velocity offset between the \ion{Fe}{2} and \ion{Mg}{2}
-centroids (Figure~\ref{fig:obs_vtau}).
-One is simply
-less sensitive to absorption at $v \sim 0 \mkms$ with the \ion{Mg}{2}
-transitions.  This includes gas realted to the ISM of the galaxy and
+centroids (Figure~\ref{fig:obs_vtau}) because scattered photons
+preferentially fill-in
+absorption at $v \sim 0 \mkms$ for the \ion{Mg}{2}
+transitions.  This affects gas related to the ISM of the galaxy and
 also material infalling at a modest speed.  One must take careful
 consideration of line emission, therefore,  before drawing robust
-conclusions aobut the presence/absence of gas with small velocity
-offsets from systemic. [Comment on MgII moving too fast]
+conclusions about the presence/absence of gas with small velocity
+offsets from systemic. Figure~\ref{fig:obs_vtau} also emphasizes that
+the \ion{Mg}{2} profiles may misrepresent the kinematics of the bulk of
+the gas.  Analysis of these lines, without consideration of
+line-emission, would lead to incorrect conclusions on the energetics
+and mass flux of the wind.
 
@@
 convolved with the line-spread-function of the Keck/LRIS spectrometer
-(FWHM=250\kms) and an assumed S/N=7 per (1 \AA) pixel.  Both the absorption
-and emission profiles are evident, but it is evident that it will be
-very difficult to resolve the issues discussed above (e.g.\ partial
-covering, incorrect peak optical depth) with these data.  The effects
-are even more difficult to predict for spectral stacks, especially
-when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
-An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
+(a Gaussian with FWHM=250\kms) and an assumed signal-to-noise of
+S/N=7 per (1 \AA) pixel.  Both the absorption
+and emission are well detected, but it would be
+difficult to resolve the issues discussed above (e.g.\ partial
+covering, peak optical depth) with these data.  
+One also notes several sysmetaic effects of the lower spectral
+resolution, e.g.\ reduced peak flux in the line-emission and a
+systematics shift of \mgiia\ absorption to more negative velocity.
+We have also modelled an observation of the fiducial model as a
+stacked of the galaxy spectra (Figure~\ref{fig:obs_lris}b) [word].
+Specifically, we
 averaged 100 identical \ion{Mg}{2} profiles from the fiducial model
 degraded to a S/N=2\,pix$^{-1}$ and assuming a random redshift error
-$\sigma(z) = 100\mkms$.  [Check S10 error] [Note the further shift in
-MgII 2796 due to the instrument resolution]
+$\sigma(z) = 100\mkms$.  
+This treatment is meant to illustrate the
+implications of stacking galaxy spectra to sutdy outflows
+\citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the
+single galaxy observation shown in panel (a) is the smearing of
+line-emission and absorption that reduces the height/depth of each.
+The effects would be even more pronounced if one studied spectra with
+a diversity of \ion{Mg}{2} profiles.    [{\bf Kate}: try stacking your set
+of observed LRIS data]
 
@@
 
-[Could they have accidentally `sky subtracted' it?  I doubt it]
-
 The previous few paragraphs sound a cautionary and largely negative
 perspective on the implications for absorption-line analysis of
-galactic-scale outflows, in the presence of (expected) significant
-line-emission.   While this does complicate [the analysis],
-observations of the line emission alone offer new and unique
+galactic-scale outflows in the presence of (expected) significant
+line-emission.   While this is a necessary complication, analysis of
+detected line-emission does offer new and unique
 constraints on the charcteristics of the outflow.  And when coupled
-with the absorption-line data, the two sets of constraints...
+with the absorption-line data, the two sets of constraints may break
+various degeneracies on the physical characteristics of the outflow.
+
 The most direct measure provided by the line emission is an estimate
-of the size and morphology of the outflow \citep[e.g.][]{rubin+10c}.  
+of the size and morphology of the outflow \citep]{rubin+10c}.  
 Line emission is predicted to extend to radii where the Sobolev
@@
 surface brightness emission.  
-
 As Figure~\ref{fig:obs_sb}
 demonstrates, the surface brightness at the inner wind radius of our
-fiducial wind exceeds the outer radius by several orders of magnitude.
+fiducial wind exceeds that at the outer radius by several orders of magnitude.
 Nevertheless, an instrument that sampled the entire wind (e.g.\ a
@@
 
-1)  Emission is a generic prediction of wind models (and something
-which has been essentially ignored aside from \lya).  We can discuss
-the caveats (dust, finite slit size, intrinsic spectrum).
-
-2)  Emission complicates the analysis of absorption at v$\sim$0 km/s, especially in
-resonantly trapped transitions (e.g. MgII, NaI).   This affects tau\_pk,
-C\_f and also offsets the line centroids (e.g. FeII, MgII).  These
-are primarily negative effects.
-
 3)  Emission can be used for good!   This is largely an extension of
@@
  (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
-
-[Are MgII and FeII* emission strict predictions of outflows?  People
-have been so focused on absorption.]
 
@@
 
-\section{Concluding remarks}
+\section{Summary}
 \label{sec:conclude}
@@
 
-2. Cosmological context (espeicially at $z>2$)
+2. Line-profiles can be explained by both increasing and decreasing
+velocity laws.
 
@@
 
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_ism_diagn.ps}
-%\caption{
-%Density (dashed; red), radial velocity (dotted; blue), and
-%\mgiia\ optical depth profiles (solid; black) for the ISM+wind
-%model.  The wind is identical to that from the fiducial model
-%(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
-%with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
-%\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-%Note that the density and velocity curves have been scaled for plotting
-%convenience.  
-%}
-%\label{fig:ISM}
-%\end{figure}
+\begin{figure}
+\epsscale{0.8}
+\plotone{../Figures/fig_taud_vs_we.ps}
+\caption{
+Attenuation by dust
+}
+\label{fig:dust_tau}
+\end{figure}
 
@@
 \caption{
-Varying normalization
+\ion{Mg}{2} and \ion{Fe}{2} profiles for the fiducial model with
+varying normalization, parameterized by \nhn.  As expected, the
+strength of absorption increases with increasing \nhn\ which also
+results in stronger line-emission.  Note that the \feiia\ emission is
+always weak; only its absorption varies with \nhn\ actually exceeding
+the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
+\ion{Mg}{2} doublet, meanwhile, always falls below a relative flux of
+0.3 while the emission rises steadily with \nhn.
 }
@@
 \caption{
-Velocity offset
+`Observations' of the \ion{Mg}{2} profiles for the fiducial wind
+model.  
+(a) The true profile (dotted lines) have been convolved with a
+Gaussian line-spread-function (FWHM~$= 250 \mkms$) and noise has been
+added to give a S/N=7 per pixel.  Note the suppressed peak in the
+line-emission; one may even infer the flux of \mgiia\ exceeds that of
+\mgiia.  One also finds that the \mgiia\ absorption is shifted to
+shorted wavelength (a greater velocity offset from systemic).  
+(b) The solid curve shows a stack of 100 spectra of the fiducial
+profile, each degraded to a S/N=2 per pixel, and offset from systemic
+by a normal deviate of $\sigma = 100 \mkms$ to mimic uncercainty in
+the redshift of the galaxy.  
+This treatment is meant to illustrate the
+implications of stacking galaxy spectra to sutdy outflows
+\citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the
+single galaxy observation shown in panel (a) is the smearing of
+line-emission and absorption that reduces the height/depth of each.
+The effects would be even more pronounced if one studied spectra with
+a diversity of \ion{Mg}{2} profiles.    
 }

### 2010-08-21 Winds/papers/Theory/First/Notes/lbg_clumps.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5145 ac11df5e-a788-c23b-a8e1-c758c323924d

\documentclass[12pt,letterpaper]{article}

%\font\bfit = cmbxti10 scaled \magstephalf

\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{ulem}
\usepackage{fancyheadings}
\usepackage[usenames]{color}

\pretolerance=10000
\textwidth=6.7in
\textheight=8.9in
\topmargin=-0.6in
\headheight=.15in
\hoffset = -0.2in
\headsep=.35in
\oddsidemargin=0in
\evensidemargin=0in
\parindent=2em
\parskip=0.2ex

\input{/u/xavier/bin/defs}
\input{/u/xavier/bin/latex}

\newcommand{\nc}{$\mathcal{N}$}
\newcommand{\mnc}{\mathcal{N}}
\newcommand{\mvr}{v_{\rm r}}

\newenvironment{my_enumerate}{
\begin{enumerate}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{enumerate}
}

\newenvironment{my_itemize}{
\begin{itemize}
  \setlength{\itemsep}{1pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}}{\end{itemize}
}

\pagestyle{empty}

\special{papersize=8.5in,11in}

\begin{document}

\begin{center}
{\Large Simple Exploration of the LBG Clump Model (Steidel+10)}
\end{center}

Here are some definitions of key quantities:

\begin{my_itemize}
\item \nc: Number of clumps in a given shell of width $\Delta r$
\item $d_c$: Size of the clump (assumed to be cubes)
\item $\sigma$: Cross-section of the clump ($d_c^2$)
\item $n_c$: Number density of a clump (Hydrogen)
\item $m_c$: Mass of a clump, i.e. $m_p n_c d_c^3$
\item $A$: Total area of clumps, i.e. $\mnc \sigma$
\item $f_c$: Covering fraction of clumps at radius $r$
\end{my_itemize}

In the S10 model, the clumps have covering fraction

\begin{equation}
f_c(r) = f_{c,max} \ltp \frac{r}{r_{\rm inner}} \rtp^{-\gamma} \cmma
\label{eqn:covering}
\end{equation}

with $\gamma \approx 0.5$ and velocity

\begin{equation}
\mvr = \ltp \frac{A_{\rm LBG}}{1-\alpha} \rtp^{1/2} \ltk r_{\rm
  inner}^{1-\alpha} - r^{1-\alpha} \rtk^{1/2} \perd
\label{eqn:LBG_vlaw}
\end{equation}
with $\alpha \approx 1.3$.

Consider a shell of width $\Delta r$ at radius $r$.  The surface area
of this shell is $4\pi r^2$.  To achieve a covering fraction $f_c$,
one requires

\begin{equation}
\mnc(r) = \frac{4 \pi r^2}{\sigma} \cdot f_c(r) = 
\frac{4 \pi f_{c,max}}{\sigma \, (\rm kpc^{1/2})} \cdot r^{3/2}
\end{equation}
clumps within the shell.  It is evident that the number of clumps
increases rather steeply with radius.  [Note: we could allow for
varying clump size by doing the calculation in terms of $A$ but I
don't think it would matter much.]

Now consider the mass profile of this clumpy wind.  Again, assuming
identical clumps at all radii, we have the mass per shell of

\begin{equation}
M_{\Delta r} = m_c \mnc 
\end{equation}
Normalizing to the mass in the first shell ($r = 1 - 2$\,kpc), we get
the cumulative mass profile shown in Figure~\ref{fig:mass}.
We find that there is 10000$\times$ more mass in the wind beyond that
in the innermost shell!

\clearpage

\begin{figure}[ht]
\begin{center}
\includegraphics[width=4.5in,angle=180]{../Figures/fig_lbg_clump_mass.pdf}
\end{center}
  \caption{Cumulative mass profile, normalized to the mass within
    $r=1-2$\,kpc, for identical clumps.  There is over 10000$\times$
    more mass beyond 2\,kpc than within that first shell. 
}
  \label{fig:mass}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=4.5in,angle=180]{../Figures/fig_lbg_clump_eandp.pdf}
\end{center}
  \caption{Cumulative energy and momentum profiles.
}
  \label{fig:eandp}
\end{figure}

Figure~\ref{fig:eandp} shows the energy and momentum
profiles, again relative to that in the inner most shell assuming
$E_{\Delta r} = M_{\Delta r} v^2$ and $P = M_{\Delta r} v$.  The
results are similar to the mass profile because the velocity curve
rises so steeply at small radii.

\vskip 0.2in

Now consider an estimation of the absolute value for the mass.  I'll
begin by assuming a size for the clump of $d_c = 100$\,pc.  If we
desire this clump to be optically thick for SiII~1526, then we need a
Si$^+$ number density $n_{\rm Si^+} = 10^{14} \cm{-2} / d_c$.  Lastly,
I will assume solar abundance, i.e. $n_H = 10^{4.5} n_{\rm Si^+}$.
This gives a number density $n_H \approx 0.01 \cm{-3}$.  I think it
might be hard to have much lower number density. Each clump,
then, has a mass $m_c = 253 \msol$. To
get a 80\%\ covering fraction at 2\,kpc, we will need $\mnc \approx
4000$ clumps or a total of $\approx 10^6 \msol$.  Finally, we estimate
that the total mass in the wind is $10^{10} \msol$ with $\sim 90\%$ of
that mass beyond 30\,kpc.  All of this material is travelling at
800\,\kms.

\vskip 0.1in

So, is this at all plausible?  And, if not, can one monkey with the
size of my clumps etc.\ to make a plausible scenario?

\end{document}

IDL> c = x_constants()
IDL> dc = 100*c.pc
IDL> nSi = 1d14 / dc
IDL> nH = 10.^(4.5)*nSi
IDL> print, nH
     0.010248243

### 2010-08-23 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5146 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 extent of the wind.
+\item  One must take careful
+consideration of line emission, therefore,  before drawing robust
+conclusions about the presence/absence of gas with small velocity
+offsets from systemic. 
 \end{itemize}
@@
 
-Recently, \citet[][; hereafter S10]{steidel+10} introduced a model to
+Recently, \citet[][hereafter S10]{steidel+10} introduced a model to
 explain jointly the average absorption they observed
@@
 flattening at large radii.  Under these conditions, the Sobolev
-approximation provies an accurate relation between the optical depth
-of the flowing medium to the
-density and velocity gradient ($d\mvr/dr$) of the gas.  In our case, we 
-generate the optical depth profile in velocity space using Equation~\ref{eqn:LBG_I},
+approximation provides an accurate description of the optical depth
+for the flowing medium. 
+In our case, the optical depth profile is actually provided by 
+Equation~\ref{eqn:LBG_I},
 
@@
 \end{equation}
-We then invert the Sobolev approximation (Equation~\ref{eqn:Sobolev})
-to derive the radial density profile:
+Therefore, we may invert the Sobolev approximation (Equation~\ref{eqn:Sobolev})
+to derive the radial density profile,
 
@@
 reproduces the proper
-absorption profile by discretizing the gas into a series of layers
+absorption profile by discretizing a wind into a series of layers
 and calculating the integrated absorption profile.  This
@@
 match to the desired profile (black curve).
-To calculate the optical depth profiles for the other transitions, we
-assume $\mnfe = \mnmg/2$ and scale $\tau$ by the $f\lambda$ product.
-
-We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
+To calculate the optical depth profiles for the other \ion{Mg}{2} and
+\ion{Fe}{2} transitions, we
+assume $\mnfe = \mnmg/2$ and also scale $\tau$ by the $f\lambda$ product.
+
+We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this LBG-Sobolev
+wind
 using the 1D algorithm with no dust extinction; these are shown as
@@
 shows the intensity profile when one ignores re-emission
-of absorbed photons.  By construction, it is the same profile\footnote{Note that
-  one should not make this comparison for the other transitions in
-  the Sobolev model because those are scaled down by $f\lambda$ and
+of absorbed photons.  By construction, it is the same profile\footnote{
+  The other transitions in
+  the LBG-Sobolev model are signficantly weaker than the input model
+  because these are scaled down by $f\lambda$ and 
   for \ion{Fe}{2} the reduced Fe$^+$ abundance.} 
@@
 distributions of mass, energy, and momentum of
-the wind.  These are shown in cumulative form in
+this wind.  These are shown in cumulative form in
 Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
@@
 LBG wind model (see the following sub-section).
-The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
-majority of energy, mass, and momentum in the wind is transported by
-the outer layers ($r > 20$\,kpc).  This is surprising given that the
-density is $\approx 5$~orders of magnitude lower at these radii than
-at $r = 1$\,pc.
+This issues aside, we may inspect Figure~\ref{fig:LBG_cumul} to reveal
+global properties of this LBG-Sobolev wind.
+One obvious result is that all of the curves rise very steeply at
+small radii.  We find, for example, that $\approx 10\%$ of the mass is
+contained within the inner 2\,kpc.  All of the curves continue to
+rise, however, such that the majority of energy, mass, and momentum in
+the wind is transported by its outermost layers (i.e., $r > 20$\,kpc).
+This is somewhat surprising given that the density is $\approx
+5$~orders of magnitude lower at these radii than at $r = 1$\,pc.
+More importantly, we question wheter any physical process could
+produce a wind with such extreme properties.
 
@@
 fiducial wind model; $\S$~\ref{sec:fiducial}).
-This LBG-Sobolev model, however, differs from
-the one proposed by S10:  those authors proposed an ensemble of optically
+We also argued that the implied mass, energy, and momentum
+distributions of this wind (Figure~\ref{fig:LBG_cumul} were too
+extreme. 
+This LBG-Sobolev model, however, is not precisely
+the one proposed by S10;  those authors proposed an ensemble of optically
 thick clouds with a partial covering fraction described by
-Equation~\ref{eqn:covering}.  In contrast, the Sobolev model assumes
+Equation~\ref{eqn:covering}.  In contrast, the LBG-Sobolev model assumes
 a diffuse medium with a declining density profile but a unit covering
-fraction.  At face value, one may question whether this difference
-leads to the contradictory results of the LBG-Sobolev model.
+fraction.  One may question, therefore,  whether the differences
+lead to the failures of the LBG-Sobolev model.
 
@@
 resonance again\footnote{Because this wind has a monotonically
-  increasing velocity law, the photon may only interact again if a
+  increasing velocity law, the photon may only scatter again if a
   longer wavelength transition is available, e.g.\ \mgiib\ for a
@@
 shown as the black curve in Figure~\ref{fig:LBG_spec}.  Remarkably, the results
-are very similar to the LBG-Sobolev calculation; scattered photons fill-in
+are essentially identical to the LBG-Sobolev calculation for the
+\mgiia\ transition; scattered photons fill-in
 the absorption profiles at $v \approx 0 \mkms$ and yield significant
-emission lines at $v \gtrsim 0 \mkms$ in the resonance
-lines. Furthermore, significant emission is observed 
+emission lines at $v \gtrsim 0 \mkms$. 
+Similar results are observed for th eother resonance lines and  
+significant emission is observed 
 for the \feiis\ transitions, centered at $\mdv \approx 0 \mkms$.  
-In contrast to the \ion{Mg}{2} profiles, the predicted \ion{Fe}{2}
-lines (especially \feiia) much more closely resemble the intrinsic
-profiles (dotted curves).  This occurs because many of these
+In contrast to the \ion{Mg}{2} profiles, the 
+\feiia\ line much more closely resembles its intrinsic
+profile (dotted curves).  This occurs because most of these
 absorbed photons flouresce into \feiis\ emission.
@@
 or include a substantial ISM component that absorbs light at $\mdv
-\gtrsim 0 \mkms$ (e.g.\ $\S$~\ref{sec:ISM}).  As we discuss in the
-following section, it is difficult (if not impossible) to fully
-suppress the line-emission,  especially for scenarios that invoke
-partial covering.  We conclude, therefore, that the LBG model
+\gtrsim 0 \mkms$ (e.g.\ $\S$~\ref{sec:ISM}).  
+Absent such corrections (which may be insufficient),
+we conclude that the LBG model
 introduced by S10 is not a valid description of the data.
 
-Lastly, we caution that resonant line-emission observed for LBGs
-\citep[e.g.\ \ion{C}{4};][]{prs+02} may result from the galactic-scale outflow, not
-only the expected stellar winds of massive stars.
+The resonant line-emission predicted for \ion{Mg}{2} should also arise
+in other transitions.  Indeed, we caution that hte \ion{C}{4}
+line-emission observed in LBG spectra
+\citep[e.g.][]{prs+02} may result from the galactic-scale outflow, not
+only the stellar winds of massive stars.
 A proper treatment of these radiative transfer effects is required to
@@
 law with $n_{\rm H}$ roughly proportional to $r^{-2}$. 
+In contrast to the fiducial model, the velocity law is nearly
+constant  with radius before decreasing sharply as r approaches $R_0$.
 To produce a wind whose \mgiia\ optical depth profile peaks at 
@@
 fiducial wind model.
-In contrast to the fiducial model, the
-velocity of the radiation-driven model decreases with increasing
-radius such that the optical depth peaks at large velocity (here $\mdv
-\approx -400 \mkms$).  At these velocities, the absorption is not
-filled-in by scattered photons such that one recovers absorption lines
-that very nearly match the intrinsic optical depth profile (dotted
-curve).  Although the \ion{Mg}{2} absorption profiles are very
-different from the fiducial model, the \ion{Mg}{2} line-emission has
-similar peak flux and velocity centroids (see also
+In contrast to the fiducial model, 
+the optical depth peaks at much larger velocity (here $\mdv
+\approx -350 \mkms$).  At these velocities, the absorption is not
+filled-in by scattered photons and one recovers absorption lines
+that more closely follows the intrinsic optical depth profile (dotted
+curve). The \ion{Mg}{2} line-emission, meanwhile, has
+similar peak flux and velocity centroids to the fiducial model (see also
 Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
 equivalent width, yet the lines of the radiation-driven model are much
-broader. This reflects the fact that the peak optical
-depth occurs at $\mdv \approx -400 \mkms$.
-[Last point]
+broader. This reflects the fact that the majority of absorption
+occurs at $\mdv \approx -350 \mkms$.
+The kinematics of \feiis\ line-emission, therfore, independently
+diagnoses the intrinsihc optical depth profile of the flow.
 
@@
 The power-law exponents were arbitrarily chosen, i.e.\ with little physical
-motivation.  In this sub-section, we explore the results for a series
+motivation.  In this sub-section, we cursorily explore the results for a series
 of other power-law expressions, also arbitarily defined.
+Our intention is to illustrate the diversity of \ion{Mg}{2} and
+\ion{Fe}{2} profiles that may result from modifications to the density
+and velocity laws.
 We consider three different density laws ($n_{\rm H} \propto
 r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr
-\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
+\propto r^{-2}, r^{-1}, r^{0.5}$) for nine wind models
 (Table~\ref{tab:plaw_parm}, Figure~\ref{fig:plaws}a).  
@@
 $b=15\mkms$, full isotropy, and a dust-free environment.
-Lastly, the abundance of Mg$^+$ and Fe$^+$ ions scale with hydrogen as
-in the fiducial model ($\S$~\ref{sec:fiducial}).
+Lastly, the abundances of Mg$^+$ and Fe$^+$ scale with hydrogen as
+in the fiducial model (Table~\ref{tab:fiducial}).
 
@@
 and velocity laws, the resultant profiles share many of the same
-features.  Each shows significant absorption at $\mdv < 0 \mkms$ with
-the profiles extending to the velocity where $\tau_{2796} < 0.1$
+characteristics.  Each shows significant absorption at $\mdv < 0
+\mkms$, extending to the velocity where $\tau_{2796}$ drops below 0.1
 (Figure~\ref{fig:plaws}b).  All of the models also exhibit strong
@@
 than $\approx 0.1$ at these velocities. 
-Similar to the radiative driven wind ($\S$~\ref{sec:radiate}),
-however, the power-law models that have significant opacity at $\mdv <
--300 \mkms$ have larger peak optical depths.  Another commonality is
+Similar to the radiative driven wind ($\S$~\ref{sec:radiative}),
+the power-law models that have significant opacity at $\mdv <
+-300 \mkms$ tend to have larger peak optical depths.  Another commonality is
 the weak or absent line-emission at \feiia; one instead notes strong
 \feiic\ emission that generally exceeds the equivalent width of the
-fiducial model.
-
+fiducial model.  One also notes that the width of the \feiis\ emission
+is systematically higher for models where the optical depth in
+absorption peaks at large velocity from the systemic.
 One of the few obvious distinctions of these models from the fiducial wind is
 the higher peak optical depth of absorption in the \feiib\
-transition.  This is predominantly due to the 
-higher peak optical depth of this transition. 
+transition.  This is primarily because these models have 
+higher intrinsic optical depths (e.g.\ higher $n_{\rm Fe^+}$ values).
+
 Table~\ref{tab:plaw_diag} compares measures of the absorption and
@@
 the velocity centroids of absorption, and the total equivalent widths.
-We find that most of these differences are driven by differences in
+We find that many of the differences are driven by differences in
 the velocity laws, i.e.\ the kinematics of the outflow.
 [Last point]
+
+[Comment that decreasing opacity can be produced by $v \propto
+r^{-1}$]
 
@@
 and non-resonance transitions.  For isotropic and dust-free scenarios,
-this is a simple conservation of photons: every photon emitted by
-the source eventually escapes the system maintaining 
+this is simple conservation of photons: every photon emitted by
+the source eventually escapes the system to maintain
 zero total equivalent width. A principal result of this paper,
-therefore, is that cool gas outflows should generate detectable 
-line-emission.
+therefore, is that galaxies with observed cool gas outflows should
+also generate detectable line-emission.
 
@@
 difference in FeII 2586 and FeII 2600?]
-Our results suggest that the majority of this line-emission is 
+Our results suggest that the majority of the observed line-emission is 
 from scattered photons in the cool gas outflows of these star-forming
-galaxies.  Indeed, our results indicate that line emission could and
-should be produced by all of galaxies driving a wind.
+galaxies.  Indeed, our results indicate that line-emission may
+be produced by all of galaxies driving a wind.
 
@@
 detected yet the authors report no significant line emission.  This
-includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
+includes \ion{Na}{1} flows \cite{rvs05a,martin,smn+09}, 
 \ion{Mg}{2} and \ion{Fe}{2} absorption in
@@
 reassess several of the effects that can reduce the line-emission
-and consider whether these could preclude its detection for many
-star-forming galaxies.  [If MgII emission is 'common' for HII regions,
-why don't we see it *always* when we see OII, Hbeta, etc? Is it
-trapped and then extincted? Same for FeII*]
-
-%% STOPPED HERE %%
-
-Dust is frequently invoked to explain the suppression of line emission
-related to resonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
+and consider whether these could prevent its detection for many
+star-forming galaxies.
+
+Dust is frequently invoked to explain the suppression of line-emission
+of resonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
 that is trapped for many scatterings within a dusty medium will 
@@
 \ion{Mg}{2} and \ion{Fe}{2} emission.  The general result
-(Figure~\ref{fig:dust_tau}) is the modest
-suppression of line flux that scales with (1+\taud)$^{-1}$ instead of
+(Figure~\ref{fig:dust_tau}) is a modest
+reduction in flux that scales as (1+\taud)$^{-1}$ instead of
 exp(--\taud). Although the \ion{Mg}{2} photons are resonantly
 trapped, they require only one to a few scatterings
-to escape the wind model and dust has only a
-modest effect.  This reflects the moderate opacity of the \ion{Mg}{2}
+to escape the wind model limiting the effects of
+dust.  This reflects the moderate opacity of the \ion{Mg}{2}
 doublet (e.g.\ relative to \lya) and also the velocity law of the
@@
 As we have discussed, in scenarios where the \ion{Mg}{2} photons are
-more effectively trapped, dust further suppresses
+more effectively trapped dust further suppresses
 the emission (e.g.\ the ISM+wind model from $\S$~\ref{sec:ISM}).
@@
 dust does reduce the line flux relative to the continuum, but 
-often has only a modest effect on the predicted \ion{Mg}{2}
+it generally has only a modest effect on the predicted \ion{Mg}{2}
 emission and always a minor effect on \feiis\ emission.
 
-Another factor that may reduce the line-emission is a
+Another factor that may reduce line-emission is a
 non-isotropic wind model. The flux is lower, for example, if one
@@
 points toward us, it is difficult to reduce $\Omega$ much
-below $2 \pi$ and, therefore, anisotropic winds reduce the
-emission by a factor of order unity.  
+below $2 \pi$ and, therefore, anisotropy likely reduces the
+emission by at most a factor of order unity.  
 Similarly, an anisotropic source may alter the predicted
@@
 of the galaxy would need to be oriented toward Earth.  Although this
-hould not be a
-generic occurance, most spectroscopic samples are magnitude-limited
+would not be a
+generic orientation, most spectroscopic samples are magnitude-limited
 and biased towards detecting galaxies when observed from their
@@
 
-Together, dust and non-isotropic wind models may reduce the line-emission
+Together, dust and anisotropic models may reduce the line-emission
 of \ion{Mg}{2} and \ion{Fe}{2}
-by a factor of order unity.  This would generally
+by one or two factors of order unity.  This would generally
 not be sufficient, however, to reduce the emission below the typical detection
@@
 There is another (more subtle) effect that could
-greatly reduce the observed line emission: slit-loss.  As
+greatly reduce the observed line-emission: slit-loss.  As
 described in Figure~\ref{fig:fiducial_ifu_mgii}, 
@@
 Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
-less than half the wind.  The result is reduced line-emission,
+less than half the full wind.  The result is reduced line-emission,
 when compared to the galaxy continuum.
@@
 (Figure~\ref{fig:fiducial_nvt}).  
-
 The predicted equivalent width in emission \ewe\ relative to the absorption
@@
 plateau when the slit width reaches $\approx \mrtt$.  
+For this model, the emission is concentrated toward the source; this
+derives from the density and velocity profiles but is also a simple
+consequence of geometric projection.
 The results are comparable for other wind models considered
 in this paper (colored curves in Figure~\ref{fig:obs_slit}).
-All of the curves rise so steeply that 
-the effects of slit-loss is of order unity
+All of the curves rise steeply enough that 
+the effects of slit-loss are minor (order unity)
 unless the slit-width is very small.   
@@
 relative to the absorption of the outflow, our analysis
-indicates that detectable line-emission should occur frequently. 
+indicates that detectable line-emission should frequently occur. 
 Furthermore, the line-emission could be suppressed so as not to exceed
@@
 line-emission at $\mdv > 0 \mkms$
-(Figures~\ref{fig:dust},\ref{fig:anisotropic}).
+(Figures~\ref{fig:anisotropic},\ref{fig:dust}).
 The emission would still 
 modify the observed absorption profiles (e.g.\
-Figure~\ref{fig:noemiss}). This may lead to erroneous conclusions
-regarding several characteristics of the flow.  {\it An analysis of cool gas outflows
+Figure~\ref{fig:noemiss}) and may lead to erroneous conclusions
+regarding characteristics of the flow.  {\it An analysis of cool gas outflows
 that entirely ignores line-emission may incorrectly conclude that the gas is
@@
 absent.}  
-We now consider several quantitative effects of the line-emission.
+We now examine several quantitative effects of line-emission.
 
@@
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
-which has the most affected transitions, the \ewabs\ is reduced by
-$30-50\%$ from the intrinsic absorption.  In turn, one may derive 
+which has the most affected transitions, \ewabs\ is reduced by
+$30-50\%$ from the intrinsic equivalent width.  In turn, one may derive 
 a systematically lower optical depth or velocity extent for the wind,
@@
 models with $v_\tau < -400 \mkms$ all yield $\tau_{\rm pk} > 3$.  The
-results are similar for the \mgiib\ profile.  In fact, one infers a
-very similar $\tau_{\rm pk}$ for the two lines which would generally
-lead to the false conclusion of partial covering. 
-[Last point]
-
-Tf these negative effects for \ion{Mg}{2} absorption are reduced
+results are similar for the \mgiib\ profile.  In fact, one generally
+measures similar $\tau_{\rm pk}$ for the two \ion{Mg}{2} lines and would 
+falsely conclude that the source is partially covered. 
+In the case of \ion{Fe}{2}, one may even observe a (non-physical)
+inversion in the apparent optical depths of \feiia\ and \feiib\ (e.g.\
+Figure~\ref{fig:norm}).
+
+These negative effects for \ion{Mg}{2} absorption are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
@@
 \ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
-wavelengths, which has no effect on the absorption profiles. 
+wavelengths, which does not effect the absorption profiles. 
 Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
@@
 predicts a velocity offset between the \ion{Fe}{2} and \ion{Mg}{2}
-centroids (Figure~\ref{fig:obs_vtau}) because scattered photons
-preferentially fill-in
-absorption at $v \sim 0 \mkms$ for the \ion{Mg}{2}
-transitions.  This affects gas related to the ISM of the galaxy and
+centroids (Figure~\ref{fig:obs_vtau}).
+%because scattered photons
+%preferentially fill-in
+%absorption at $v \sim 0 \mkms$ for the \ion{Mg}{2} transitions.  
+This affects analysis of gas related to the ISM of the galaxy and
 also material infalling at a modest speed.  One must take careful
@@
 relatively low spectral resolution and S/N characteristic of the data
-obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
+commonly acquired for $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
 shows one realization of the \mgiid\ doublet for the ISM+wind model
@@
 resolution, e.g.\ reduced peak flux in the line-emission and a
-systematics shift of \mgiia\ absorption to more negative velocity.
-We have also modelled an observation of the fiducial model as a
-stacked of the galaxy spectra (Figure~\ref{fig:obs_lris}b) [word].
+systematic shift of \mgiia\ absorption to more negative velocity.
+We have also modelled an observation of the ISM+wind model using
+a stacked galaxy spectrum (Figure~\ref{fig:obs_lris}b).
 Specifically, we
 averaged 100 identical \ion{Mg}{2} profiles from the fiducial model
-degraded to a S/N=2\,pix$^{-1}$ and assuming a random redshift error
-$\sigma(z) = 100\mkms$.  
-This treatment is meant to illustrate the
-implications of stacking galaxy spectra to sutdy outflows
+degraded to a S/N=2\,pix$^{-1}$ and shifted by a random velocity
+offset with $\sigma = 100\mkms$.  
+This treatment illustrates the effects of using stacked galaxy 
+spectra to study outflows
 \citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the
@@
 The effects would be even more pronounced if one studied spectra with
-a diversity of \ion{Mg}{2} profiles.    [{\bf Kate}: try stacking your set
-of observed LRIS data]
+a diversity of \ion{Mg}{2} profiles.    
+Special care is required to interpret properties of the wind (and
+ISM) from such spectral analysis.
+[Emphasize that the ISM component has *no chance* of being revealed]
+[{\bf Kate}: try stacking your set of observed LRIS data]
 
@@
 galactic-scale outflows in the presence of (expected) significant
-line-emission.   While this is a necessary complication, analysis of
-detected line-emission does offer new and unique
-constraints on the charcteristics of the outflow.  And when coupled
+line-emission.   While this is a necessary complication, direct analysis of
+the line-emission does offer new and unique
+constraints on the charcteristics of the outflow.  And, when coupled
 with the absorption-line data, the two sets of constraints may break
 various degeneracies on the physical characteristics of the outflow.
-
-The most direct measure provided by the line emission is an estimate
-of the size and morphology of the outflow \citep]{rubin+10c}.  
+We now consider a few examples.
+
+The most obvious measures provided by line-emission analysis are
+estimates
+of the size and morphology of the outflow \citep{rubin+10c}.  
 Line emission is predicted to extend to radii where the Sobolev
-optical depth exceeds a few tenths [is that right?].  The principle
-challenge is to achieve sufficient sensitivity to detect the low
-surface brightness emission.  
-As Figure~\ref{fig:obs_sb}
+optical depth exceeds a few tenths.  The principle
+challenge is to achieve sufficient sensitivity to detect low
+surface brightness emission. As Figure~\ref{fig:obs_sb}
 demonstrates, the surface brightness at the inner wind radius of our
@@
 [Add FeII* to the SB figure]
-
 Of the transitions considered in this paper, \ion{Mg}{2} emission is
-preferred for [this analysis] because 
+preferred for this analysis because 
 (i) it has the largest equivalent width in absorption and
 (ii) there are fewer emission channels per absorption line than for
-\ion{Fe}{2}.  This implies the highest peak and integrated fluxes
-(Figure~\ref{fig:obs_sb}).  With an IFU observation covering all of
-the \ion{Fe}{2} transitions, one could sum the together to enhance the
-signal.
+\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiia) has the
+highest peak and integrated fluxes 
+(Figure~\ref{fig:obs_sb}).
 
@@
 
+[\feiis\ width!!]
+
+[Centroid of \ion{Mg}{2} $-->$ dust, isotropy]
+
 [Relative strengths of MgII 2796 and 2803 speak to $\tau$ and
 $v_r^{max}$]
+
+[If MgII emission is 'common' for HII regions,
+why don't we see it *always* when we see OII, Hbeta, etc? Is it
+trapped and then extincted? Same for FeII*]
 
@@
 
-1. More complicated winds needed
-
-2. Line-profiles can be explained by both increasing and decreasing
+\begin{enumerate}
+\item Line-profiles can be explained by both increasing and decreasing
 velocity laws.
 
+\item We conclude that resonance transitions that are strongly coupled to
+non-resonant lines offer the best
+characterization of an ISM component.
+\end{enumerate}
+
 \acknowledgments
 
+We acknowledge valuable conversations with D. Koo, J. Hennawi, 
 J.X.P and K.R. are partially supported
@@
 levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
-2618,2631$) that arise from higher levels in the \zconfig\
+2618,2631$; red and dashed lines) that arise from higher levels in the \zconfig\
 configuration.  These transitions have not yet been observed in
@@
 Density (dashed; red), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (solid; black) for the fiducial
+\mgiia\ optical depth profiles (solid and dotted; black) for the fiducial
 wind model (see Table~\ref{tab:fiducial} for details).
 The density and velocity laws are simple $r^{-2}$ and $r^1$
-power-laws.  The optical depth profile was calculated by summing
+power-laws; these curves have been scaled for plotting
+convenience.  
+The optical depth profile was calculated two ways: (i) using the
+Sobolev approximation (Equation~\ref{eqn:Sobolev}; solid black curve)
+and (ii) summing
 the opacity at small and discrete radial intervals in velocity space
-and was then converted to radius with the velocity law.  One notes that
+and then converting to radius with the velocity law.  These give
+very similar results. One notes that
 the wind is optically thick at the inner radius ($r_{\rm inner} =
@@
   outer} = 20$\,kpc).
-Note that the density and velocity curves have been scaled for plotting
-convenience.  
 }
@@
 is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
-photons scattered off the outflow fill in the absorption.
+photons scattered off the outflow significantly fill-in the absorption.
 (Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
@@
 lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
-the emission for \feiia\ is significantly weaker than that of the
+the emission for \feiia\ is much weaker than that for the
 \feiib\ and \mgiid\ transitions.  This is because a majority of the
-absorbed \feiia\ photons are converted into
+absorbed \feiia\ photons flouresce into
 \ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
@@
 canonical P-Cygni profiles of a source 
-embedded within an outflow.  Overplotted (dotted line) on each transition is
+embedded within an outflow.  Overplotted on each transition (dotted line) is
 the predicted absorption profile under the constraint that every
 absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission occurs.   The true profiles have been `filled
-in' significantly by light scattered in the wind.  Ignoring this
+re-emission occurs.   The true profiles have been `filled-in' 
+significantly by light scattered in the wind.  Ignoring this
 process, one would model the absorption lines with a systematically lower
@@
 source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
-pixels at the center.   At $v=-250 \mkms$, the wind has an optical
+pixels at the center of each map.   At $v=-250 \mkms$, the wind has an optical
 depth of $\tau_{2796} \approx 1$ and the source contributes
@@
 emission exceeds the integrated flux at $v = -250\mkms$ such that the
-line center is offset from the peak optical depth.  At $v \ge 0
+\mgiia\ line center is offset from the (intrinsic) peak in optical depth.  At $v \ge 0
 \mkms$,  both the source and wind contribute to the observed emission.
@@
 (Upper) Surface-brightness emission maps around the \feiib\ transition for the
-source+wind complex.  The middle panel shows the 1D spectrum with $v=0
-\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
-curves indicating the velocity slices for the emission maps.  
+source+wind complex.  
+%The middle panel shows the 1D spectrum with $v=0
+%\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
+%curves indicating the velocity slices for the emission maps.  
 The results are very similar to those observed for the \mgiid\ doublet
@@
 2612$ transition for the 
-source+wind complex.  The middle panel shows the 1D spectrum with $v=0
-\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
-curves indicating the velocity slices for the emission maps.  
+source+wind complex.  %The middle panel shows the 1D spectrum with $v=0
+%\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
+%curves indicating the velocity slices for the emission maps.  
 In this case, the source is unattenuated yet scattered photons from
-the wind also have a significant contribution. 
+the wind also make a significant contribution. 
+[Is this figure superfluous??]
 }
@@
 \caption{
-Attenuation by dust
+Predicted line-emission equivalent widths for \mgiib\ from the
+fiducial wind model, as attenuated by dust with a range of \taud\
+values.  
+It is obvious that the equivalent widths (i.e., the flux relative to
+the continuum) do not scale as $\exp(\tau_d)$.
+The black (solid) curve shows the model predictions while the
+dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
+\cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
+representation of the radiative transfer results.   
 }
@@
 model to $v \approx +100\mkms$ for the ISM+wind model. 
-For the ISM+wind model, 
-the \ion{Fe}{2} profiles show qualitative differences. 
-the ISM model.  The \feiid\ resonance transitions each exhibit much
+The \ion{Fe}{2} profiles, meanwhile, show several qualitative differences. 
+The \feiid\ resonance transitions each exhibit much
 greater absorption at $v \approx 0 \mkms$ than the fiducial model.
@@
 reduced, implying much higher fluxes for the non-resonant lines (e.g.\
-\feiic).  The lack of scattered \feiia\ photons results in an
+\feiic,2626).  The lack of scattered \feiia\ photons results in an
 absorption profile that very nearly matches the input opacity profile.
@@
 results in stronger line-emission.  Note that the \feiia\ emission is
-always weak; only its absorption varies with \nhn\ actually exceeding
+always weak; only its absorption increases with \nhn\ and actually exceeds
 the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
 \ion{Mg}{2} doublet, meanwhile, always falls below a relative flux of
-0.3 while the emission rises steadily with \nhn.
+0.3 while the \mgiib\ emission rises steadily with \nhn.
 }
@@
 steepens to $(r/{\rm kpc}-1)^{-1.8}$.
-(b) Average absorption profile for LBG cool gas absorption as
+(b) The average profile for LBG cool gas absorption as
 measured and defined by S10
@@
 shows the \mgiia\ absorption profile derived from the density (and velocity)
-law shown in the upper panel.  The excellent agreement confirms the
-validity of the Sobolev approximation.
+law shown in the upper panel.  
 }
@@
 model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
-significantly modify the absorption profiles (especially \ion{Mg}{2})
+significantly modify the absorption profiles (especially \ion{Mg}{2}
+and \feiib)
 and produce significant emission lines.  
@@
 not match the average observed LBG absorption profile.
-Note the excellent agreement
-between the \mgiia\ profile for the two models. [Cast doubt on S10
-here?]
 }
@@
 \caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+The upper left panel shows the density (solid) and velocity (dotted)
+laws for the LBG-Sobolev wind model (Figure~\ref{fig:LBG_Sobolev}).
+The remaining panels show the cumulative mass, energy, and momentum of
+this flow.  All of the curves rise very steeply at small radii and
+then rise steadily to large radii.  The principal result is that the
+majority of mass, energy, and momentum in the wind are contained at
+large radii.
 }
@@
 radius such that the optical depth peaks at large velocity (here $\mdv
-\approx -400 \mkms$).  At these velocities, the absorption is not
-filled-in by scattered photons such that one recovers absorption lines
-that very nearly match the intrinsic optical depth profile (dotted
+\approx -350 \mkms$).  At these velocities, the absorption is not
+filled-in by scattered photons and one recovers absorption lines
+that closely resemble the intrinsic optical depth profile (dotted
 curve).  Although the \ion{Mg}{2} absorption profiles are very
 different from the fiducial model, the \ion{Mg}{2} line-emission has
-similar peak flux and velocity centroids (see also
-Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
+similar peak flux and velocity centroids 
+The \feiis\ emisison also has a simiar
 equivalent width, yet the lines are much broader for the
-radiative-driven model. This reflects the fact that the peak optical
-depth occurs at $\mdv \approx -400 \mkms$.
+radiative-driven model. 
 }
@@
 \caption{
-Power-law profiles
+In panel (a) we illustrate the density (gray curves; dashed -- $\mnhn
+\propto r^0$, dotted -- $\mnhn \propto r^{-3}$, dot-dash -- $\mnhn
+\propto r^{-2}$) and velocity laws (colored; green -- $v \propto
+r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$).  For
+comparison we also plot the velocity and density laws for the fiducial
+model (thin, black curves).  See Table~\ref{tab:plaw_parm} for further
+details.
+Panel (b) plots the optical depth profiles of the \mgiia\ line for
+the nine models build from the density and velocity laws of panel (a).
 }
@@
 \ion{Mg}{2} and \ion{Fe}{2} profiles for a series of power-law wind
-models described in Table~\ref{tab:plaw_parm}.  These panels reveal
+models (see Table~\ref{tab:plaw_parm} for details).  These panels reveal
 the diversity of absorption and emission that result from a set of
@@
 with the flux proportional to the degree of absorption.
+We also note that the width of the \feiic\ emission scales with the
+velocity offset of peak optical depth for the \feiia\ absorption.
+Threefore, the emission kinematics trace the intrinsic
+optical depth profile.
 }
@@
 Difference between the `observed' absorption equivalent width \ewabs\
-which includes the flux of scattered photons and the intrinsic
+which includes the flux of scattered photons and the `intrinsic'
 equivalent width $W_{\rm i}$ that ignores photon scattering.  The
@@
 \ion{Fe}{2} transitions because a fraction (in fact a majority for
-\feiia) of the absorbed photons flourecse as \feiis\ emission at
+\feiia) of the absorbed photons flouresce as \feiis\ emission at
 longer wavelengths and do not `fill-in' the absorption profiles.
@@
 \caption{
-`Observations' of the \ion{Mg}{2} profiles for the fiducial wind
-model.  
+`Observations' of the \ion{Mg}{2} profiles for the ISM+wind model.  
 (a) The true profile (dotted lines) have been convolved with a
@@
 shorted wavelength (a greater velocity offset from systemic).  
-(b) The solid curve shows a stack of 100 spectra of the fiducial
+(b) The solid curve shows a stack of 100 spectra of the ISM+wind
 profile, each degraded to a S/N=2 per pixel, and offset from systemic

### 2010-08-24 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5147 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 The stacked spectra of the remaining galaxies, however, also indicated
-\ion{Mg}{2} emisison, both directly and when the authors modeled and
+\ion{Mg}{2} emission, both directly and when the authors modeled and
 `removed' the $v \approx 0\mkms$ absorption component.  Although the
@@
 occur following the absorption of a single photon by Fe$^+$ in its
-ground-state.   This process may also be referred to as flourescence.
+ground-state.   This process may also be referred to as fluorescence.
 Note that two of these transitions (\feiis$\; \lambda\lambda 2626, 2632$) are
@@
 approximation is valid when the opacity the photon experiences is
-domianted by gas in a localized portion of the flow.
+dominated by gas in a localized portion of the flow.
 We find that it applies to nearly all of the
@@
 ($\tau_{2796}$), estimated from the Sobolev approximation\footnote{We
-  have verified this approxmiation holds by calculating 
+  have verified this approximation holds by calculating 
   $\tau_{2796}$ first
@@
 Using the methodology described in $\S$~\ref{sec:method}, we
-propogated photons from the source and through the outflow to an
+propagated photons from the source and through the outflow to an
 `observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
@@
 source.  We will find that this
-[behaviour] is a generic result, even for wind models that include
+[behavior] is a generic result, even for wind models that include
 dust and are not fully isotropic.
@@
 
-Similar behaviour is observed for the \ion{Fe}{2} transitions.
-Interestingly, the \feiia\ transiions never show significant emission,
+Similar behavior is observed for the \ion{Fe}{2} transitions.
+Interestingly, the \feiia\ transitions never show significant emission,
 only stronger absorption with increasing $n_{\rm H}^0$.  In fact, for $n_{\rm H}^0
@@
   The other transitions in
-  the LBG-Sobolev model are signficantly weaker than the input model
+  the LBG-Sobolev model are significantly weaker than the input model
   because these are scaled down by $f\lambda$ and 
@@
 5$~orders of magnitude lower at these radii than at $r = 1$\,pc.
-More importantly, we question wheter any physical process could
+More importantly, we question whether any physical process could
 produce a wind with such extreme properties.
@@
 To more properly model the LBG wind described in S10, we 
-performed the following Monte Carlo calculation.  First, we propogate
+performed the following Monte Carlo calculation.  First, we propagate
 a photon from the source until its velocity relative to line-center
@@
 emission lines at $v \gtrsim 0 \mkms$. 
-Similar results are observed for th eother resonance lines and  
+Similar results are observed for the other resonance lines and  
 significant emission is observed 
@@
 profile (dotted curves).  This occurs because most of these
-absorbed photons flouresce into \feiis\ emission.
+absorbed photons fluoresce into \feiis\ emission.
 The equivalent width of \feiia\ even exceeds that for \feiib, an
@@
 The resonant line-emission predicted for \ion{Mg}{2} should also arise
-in other transitions.  Indeed, we caution that hte \ion{C}{4}
+in other transitions.  Indeed, we caution that the \ion{C}{4}
 line-emission observed in LBG spectra
@@
 similar peak flux and velocity centroids to the fiducial model (see also
-Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
+Table~\ref{tab:plaw_diag}).  The \feiis\ emission also has a similar
 equivalent width, yet the lines of the radiation-driven model are much
@@
 occurs at $\mdv \approx -350 \mkms$.
-The kinematics of \feiis\ line-emission, therfore, independently
-diagnoses the intrinsihc optical depth profile of the flow.
+The kinematics of \feiis\ line-emission, therefore, independently
+diagnoses the intrinsic optical depth profile of the flow.
 
@@
 motivation.  In this sub-section, we cursorily explore the results for a series
-of other power-law expressions, also arbitarily defined.
+of other power-law expressions, also arbitrarily defined.
 Our intention is to illustrate the diversity of \ion{Mg}{2} and
@@
 that is trapped for many scatterings within a dusty medium will 
-preferentially be extincted relative to a non-resonant photon.  In
+preferentially be  relative to a non-resonant photon.  In
 $\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
@@
 Furthermore, the line-emission could be suppressed so as not to exceed
-the galaxy continum yet still (partially) fill-in the absorption
+the galaxy continuum yet still (partially) fill-in the absorption
 profiles. Indeed, dust and anisotropic winds preferentially suppress
@@
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
-is because a signficant fraction (even a majority) of the
+is because a significant fraction (even a majority) of the
 \ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
@@
 covering, peak optical depth) with these data.  
-One also notes several sysmetaic effects of the lower spectral
+One also notes several systematic effects of the lower spectral
 resolution, e.g.\ reduced peak flux in the line-emission and a
@@
 the line-emission does offer new and unique
-constraints on the charcteristics of the outflow.  And, when coupled
+constraints on the characteristics of the outflow.  And, when coupled
 with the absorption-line data, the two sets of constraints may break
@@
 \feiib\ and \mgiid\ transitions.  This is because a majority of the
-absorbed \feiia\ photons flouresce into
+absorbed \feiia\ photons fluoresce into
 \ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
@@
 similar peak flux and velocity centroids 
-The \feiis\ emisison also has a simiar
+The \feiis\ emission also has a similar
 equivalent width, yet the lines are much broader for the
@@
 velocity offset of peak optical depth for the \feiia\ absorption.
-Threefore, the emission kinematics trace the intrinsic
+Therefore, the emission kinematics trace the intrinsic
 optical depth profile.
@@
 (solid -- \mgiia; dotted -- \mgiib; dashed -- \feiib).  The
-\ewe/\ewabs\ ratio is plottd as a function of slit width relative to
+\ewe/\ewabs\ ratio is plotted as a function of slit width relative to
 twice the radius \rtt, defined to be where the Sobolev optical depth 
@@
 For all of the wind models, the \ewe/\ewabs\ ratio rises very steeply
-with slit width and plataeus at $\approx \mrtt$.  [Add?]
+with slit width and plateaus at $\approx \mrtt$.  [Add?]
 }
@@
 \ion{Fe}{2} transitions because a fraction (in fact a majority for
-\feiia) of the absorbed photons flouresce as \feiis\ emission at
+\feiia) of the absorbed photons fluoresce as \feiis\ emission at
 longer wavelengths and do not `fill-in' the absorption profiles.
@@
 of the models, the true peak optical depth $\mtpk^{\rm true} > 10$.
-The much lower `observed' values occur because scattered \mgiia\
-photons have filled-in the absorption profiels at velocities $\mdv
-\gtrsim -400 \mkms$.  Therefore, the effects are greates for wind
+The much lower `observed' \tpk\ values occur because scattered \mgiia\
+photons have filled-in the absorption profiles at velocities $\mdv
+\gtrsim -400 \mkms$.  Therefore, the effects are greatest for wind
 models where the optical depth peaks near $\mdv \sim 0 \mkms$.
@@
 Comparison of the velocities where the \feiia\ and \mgiia\ absorption
-profiles have observed peak optical depth.  Results for all the models
+profiles have greatest depth.  Results for all the models
 studied in this paper are presented (Tables~\ref{tab:line_diag},
-\ref{tab:plaw_diag}).  The dashsed curve traces the one-to-one line.
-It is evident that for wind models have a peak optical depth near the
-systemic velocity, the \mgiib\ absorption profile is shifted blueward
-by one to several hundred \kms.  One may therefore falesly conclude
+\ref{tab:plaw_diag}).  
+It is evident that wind models with a peak optical depth near the
+systemic velocity have a \mgiib\ absorption profile shifted blueward
+by one to several hundred \kms.  Analysis of such profiles may lead to
+the false conclusion 
 that (i) the majority of mass in the wind is travelling at a higher
 velocity; and (ii) there is no gas with $\mdv \sim 0 \mkms$.
+The dashed curve traces the one-to-one line.
 }
@@
 Gaussian line-spread-function (FWHM~$= 250 \mkms$) and noise has been
-added to give a S/N=7 per pixel.  Note the suppressed peak in the
+added to give a S/N=7 per pixel.  Note the suppressed peak in 
 line-emission; one may even infer the flux of \mgiia\ exceeds that of
-\mgiia.  One also finds that the \mgiia\ absorption is shifted to
-shorted wavelength (a greater velocity offset from systemic).  
+\mgiib.  One also finds that the \mgiia\ absorption is shifted to
+shorter wavelength (a greater velocity offset from systemic).  
 (b) The solid curve shows a stack of 100 spectra of the ISM+wind
 profile, each degraded to a S/N=2 per pixel, and offset from systemic
-by a normal deviate of $\sigma = 100 \mkms$ to mimic uncercainty in
+by a normal deviate of $\sigma = 100 \mkms$ to mimic uncertainty in
 the redshift of the galaxy.  
 This treatment is meant to illustrate the
-implications of stacking galaxy spectra to sutdy outflows
+implications of stacking galaxy spectra to study outflows
 \citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the

### 2010-08-28 Winds/papers/Theory/First/Notes/lbg_clumps.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5153 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \begin{center}
-{\Large Simple Exploration of the LBG Clump Model (Steidel+10)}
+{\Large Simple Exploration of the LBG Clump Model (Steidel+10): v2}
 \end{center}
@@
 \item \nc: Number of clumps in a given shell of width $\Delta r$
+\item $\Delta v_c$: Internal velocity dispersion of the clump (e.g.\
+  10 km/s)
+\item $\Delta r$: Width of the shell. This will relate to the internal
+  velocity dispersion of the clumps.
+\item $n$: Number density of clumps at radius $r$
 \item $d_c$: Size of the clump (assumed to be cubes)
@@
 \item $m_c$: Mass of a clump, i.e. $m_p n_c d_c^3$
-\item $A$: Total area of clumps, i.e. $\mnc \sigma$
+%\item $A$: Total area of clumps in $\Delta r$, i.e. $\mnc \sigma$
 \item $f_c$: Covering fraction of clumps at radius $r$
@@
 \end{equation}
-
 with $\gamma \approx 0.5$ and velocity
@@
 
-Consider a shell of width $\Delta r$ at radius $r$.  The surface area
-of this shell is $4\pi r^2$.  To achieve a covering fraction $f_c$,
-one requires
+Consider a shell of width $\Delta r$ at radius $r$.   The number of
+clumps in this shell is:
 
 \begin{equation}
-\mnc(r) = \frac{4 \pi r^2}{\sigma} \cdot f_c(r) = 
-\frac{4 \pi f_{c,max}}{\sigma \, (\rm kpc^{1/2})} \cdot r^{3/2}
+\mnc = n \cdot \Delta r \cdot 4 \pi r^2
 \end{equation}
-clumps within the shell.  It is evident that the number of clumps
-increases rather steeply with radius.  [Note: we could allow for
-varying clump size by doing the calculation in terms of $A$ but I
-don't think it would matter much.]
-
-Now consider the mass profile of this clumpy wind.  Again, assuming
-identical clumps at all radii, we have the mass per shell of
+And the covering fraction will be
 
 \begin{equation}
-M_{\Delta r} = m_c \mnc 
+f_c = \frac{\sigma \mnc}{4 \pi r^2} = n \sigma \Delta r
 \end{equation}
-Normalizing to the mass in the first shell ($r = 1 - 2$\,kpc), we get
-the cumulative mass profile shown in Figure~\ref{fig:mass}.
-We find that there is 10000$\times$ more mass in the wind beyond that
-in the innermost shell!
+Lastly, the thickness of a given shell relates to the overlap of the
+clumps in velocity space.  Given an internal velocity dispersion $\Delta
+v_c$ for each clump, we have:
 
-\clearpage
+\begin{equation}
+\Delta r = \Delta v_c \ltp \frac{dv}{dr} \rtp^{-1}  \perd
+\end{equation}
+This starts to look like the Sobolev equations, but not quite.  The
+key issue here is that $\Delta r$ varies with radius.  Because the LBG
+velocity curve flattens, $\Delta r$ increases quite rapidly with $r$.
 
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=4.5in,angle=180]{../Figures/fig_lbg_clump_mass.pdf}
-\end{center}
-  \caption{Cumulative mass profile, normalized to the mass within
-    $r=1-2$\,kpc, for identical clumps.  There is over 10000$\times$
-    more mass beyond 2\,kpc than within that first shell. 
-}
-  \label{fig:mass}
-\end{figure}
+If we like, we can rewrite these equations in terms of the density of
+the clumps
 
-\begin{figure}[ht]
-\begin{center}
-\includegraphics[width=4.5in,angle=180]{../Figures/fig_lbg_clump_eandp.pdf}
-\end{center}
-  \caption{Cumulative energy and momentum profiles.
-}
-  \label{fig:eandp}
-\end{figure}
+\begin{equation}
+n(r) = \frac{f_c(r)}{\sigma} \frac{1}{\Delta r} \cmma
+\end{equation}
+the mass of a shell of $\Delta r$
 
-Figure~\ref{fig:eandp} shows the energy and momentum
-profiles, again relative to that in the inner most shell assuming
-$E_{\Delta r} = M_{\Delta r} v^2$ and $P = M_{\Delta r} v$.  The
-results are similar to the mass profile because the velocity curve
-rises so steeply at small radii.
-
-\vskip 0.2in
+\begin{equation}
+M_{\Delta r} = \frac{f}{\sigma} \cdot 4 \pi r^2 \cdot m_c
+\end{equation}
+We see (as in v1 of this write-up) that the mass in each shell goes as
+$r^{3/2}$ given the functional form of the covering fraction.  But the
+mistake I had made is that the thickness of the shells ($\Delta r$) is
+increasing with radius.  So the cumulative mass doesn't increase as
+rapidly.
 
@@
 might be hard to have much lower number density. Each clump,
-then, has a mass $m_c = 253 \msol$. To
-get a 80\%\ covering fraction at 2\,kpc, we will need $\mnc \approx
-4000$ clumps or a total of $\approx 10^6 \msol$.  Finally, we estimate
-that the total mass in the wind is $10^{10} \msol$ with $\sim 90\%$ of
-that mass beyond 30\,kpc.  All of this material is travelling at
-800\,\kms.
+then, has a mass $m_c = 253 \msol$.
 
-\vskip 0.1in
+With this clump size and mass, we get the density, mass, and flux
+profiles shown in Figure~\ref{fig:aclump}.  Each of these curves start
+at $r = 2$\,kpc because at smaller radii the clumps overlap.  Again,
+the mass approaches $10^{10} \msol$ and most of the mass lies at the
+outer radii.  The clump density drops very rapidly with radius such
+that the clump flux is nearly constant.  I think this is by design
+given the shells have thickness $\Delta r \propto (dv/dr)^{-1}$, but
+I'm not sure.
 
 So, is this at all plausible?  And, if not, can one monkey with the
-size of my clumps etc.\ to make a plausible scenario?
+size or $\Delta v_c$ of my clumps etc.\ to make a plausible scenario?
+
+\begin{figure}[ht]
+\begin{center}
+\includegraphics[width=5.5in]{../Figures/fig_lbg_aclump.pdf}
+\end{center}
+  \caption{$\Delta r$, density, mass, and flux profiles for the LBG
+    wind model assuming $\Delta v_c = 10 \mkms$ and that the clump has
+    $d_c = 100$\,pc and $m_c = 250 \msol$.
+}
+  \label{fig:aclump}
+\end{figure}
 

### 2010-08-28 Winds/papers/Theory/First/Notes/lbg_clumps.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5154 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
-\documentclass[12pt,letterpaper]{article}
+\documentclass[11pt,letterpaper]{article}
 
@@
 
-So, is this at all plausible?  And, if not, can one monkey with the
-size or $\Delta v_c$ of my clumps etc.\ to make a plausible scenario?
-
 \begin{figure}[ht]
@@
 
+So, is this at all plausible?  And, if not, can one monkey with the
+size or $\Delta v_c$ of my clumps etc.\ to make a plausible scenario?
+It is evident that $M_{\rm TOT} \propto m_c / (\sigma \Delta v_c)$
+where the $\Delta v_c$ comes in because that sets the size of each
+shell.  I had worried that $(m_c / \sigma) \propto d_c$ but we are
+demanding that each cloud is optically thick, i.e.\ $n_c d_c = {\rm
+  Const}$.  Therefore, $m_c / \sigma = {\rm Const}$.  So all the
+dependence is in $\Delta v_c$ and I don't see raising that by more
+than a factor of a few.
+
 \end{document}

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/model_lbg.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5156 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -39,6 +39,13 @@ double MODEL::Velocity(double r)
   return LBG_Aa * sqrt(1 - pow(r,1-LBG_alpha));  // Assumes r_inner=1kpc
 }
 
+double MODEL::DvDr(double r)  // cm/s per kpc
+{
+  if (r <= r_inner) return 0;
+  double dvdr = LBG_Aa * 0.5 / sqrt(1-pow(r,1-LBG_alpha)) * (LBG_alpha-1) * pow(r,-1*LBG_alpha);
+  return dvdr;
+}
+
 double MODEL::Covering(double r)
 {
   if (r <= r_inner) return 0.;

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/transport_lbg.cc

@@ -230,6 +230,8 @@ void Line_Scatter(PHOTON &p, double lam, double *uvec)
 
   p.xloc = (p.lloc/lam - 1)*C_LIGHT/model.v_doppler();
 
+  // Offset in radius (only proper along radial, but hopefully close enough)
+
   // get three velocity components of scatterer
   double temp = 0.5*M_PROTON*pow(model.v_doppler(),2)/K_BOLTZ;
   double apar = 4.7e-3*sqrt(1e4/temp);
@@ -296,6 +298,8 @@ double P_esc(double lloc, double *r, int l_scat)
   int n_lines = lines.n();
 
   TOT_ESC = 1.;
+
+  // See if we escape in this line (Doppler allows for multiple scatterings)
 
   // See if there is a transition to the red
   flg = 0;

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/outflow_lbg_covering_feii.cc

@@ -12,7 +12,7 @@
 LINES lines;
 
 // monte carlo parameters
-double n_photons =  2e6;    // number of photons
+double n_photons =  1e7;    // number of photons
 double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
@@ -54,7 +54,8 @@ double dust_albedo = 0.0;         // ratio of scattering to absorption
 double abun       = 3.4e-6;
 double metallicity       = 0.5/2;                 // 1 = Solar
  // lines doppler velocity in cm/s
-double v_doppler    =   5*1e5;              
+double v_interact    =  1*1e5;              // Condition to scatter
+double v_doppler    =   10*1e5;           // 10 km/s (internal)
 
 // parameters describing voigt profile
 double voigt_a   = 0.1;
@@ -145,6 +146,19 @@ double Get_Velocity(double *x, double r)
   return LBG_Aa * sqrt(1 - pow(r,1-LBG_alpha));  // Assumes r_inner=1kpc
 }
 
+//--------------------------------------------
+// Function returns dv/dr at a given a radius (in cm/s per kpc)
+//     This is only valid along the radial direction
+//--------------------------------------------
+double Get_DvDr(double r)
+{
+  //  return v_max*pow(r/r_outer,v_law);
+  // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
+  if (r <= r_inner) return 0;
+  double dvdr = LBG_Aa * 0.5 / sqrt(1-pow(r,1-LBG_alpha)) * (LBG_alpha-1) * pow(r,-1*LBG_alpha);
+  return dvdr;
+}
+
 
 //--------------------------------------------
 // Function returns the density proxy given a radius (in kpc)
@@ -175,7 +189,7 @@ void Run_Monte_Carlo(char *outfile)
   double vd_inc, vd_out, l_step, d_step;
   double u0,u1,u2, R10, R11, rad, vel, vproj;
   double uvec[3];
-  double nu_d, cross_sec, dens_H, cover;
+  double nu_d, cross_sec, dens_H, cover, dvdr;
 
   // functions to call
   void MPI_Average_Array(double *, int);
[…]

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/outflow_lbg_covering_mgii.cc

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  2e6;    // number of photons
+double n_photons =  1e7;    // number of photons
 double stepsize  = 0.0001;   // maximum size of photon step  (kpc)
 
 // output spectrum parameters
@@ -51,7 +51,8 @@ double f_lu[]       = {0.6123,     0.3054};
 double abun       = 3.4e-6;
 double metallicity       = 0.5;                 // 1 = Solar
  // lines doppler velocity in cm/s
-double v_doppler    =   5*1e5;              
+double v_interact    =  1*1e5;              // Condition to scatter
+double v_doppler    =   10*1e5;           // 10 km/s (internal)
 
 // parameters describing voigt profile
 double voigt_a   = 0.1;
@@ -139,6 +140,19 @@ double Get_Velocity(double *x, double r)
   return LBG_Aa * sqrt(1 - pow(r,1-LBG_alpha));  // Assumes r_inner=1kpc
 }
 
+//--------------------------------------------
+// Function returns dv/dr at a given a radius (in cm/s per kpc)
+//     This is only valid along the radial direction
+//--------------------------------------------
+double Get_DvDr(double r)
+{
+  //  return v_max*pow(r/r_outer,v_law);
+  // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
+  if (r <= r_inner) return 0;
+  double dvdr = LBG_Aa * 0.5 / sqrt(1-pow(r,1-LBG_alpha)) * (LBG_alpha-1) * pow(r,-1*LBG_alpha);
+  return dvdr;
+}
+
 
 //--------------------------------------------
 // Function returns the density proxy given a radius (in kpc)
@@ -169,7 +183,7 @@ void Run_Monte_Carlo(char *outfile)
   double vd_inc, vd_out, l_step, d_step;
   double u0,u1,u2, R10, R11, rad, vel;
   double uvec[3];
-  double nu_d, cross_sec, dens_H, cover;
+  double nu_d, cross_sec, dens_H, cover, dvdr;
 
   // functions to call
   void MPI_Average_Array(double *, int);
@@ -177,6 +191,7 @@ void Run_Monte_Carlo(char *outfile)
[…]

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/main_lbg.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5157 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,123 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "Lua.hh"
+#include "locate_array.hh"
+#include "spectrum.hh"
+#include "model_lbg.hh"
+#include "lines.hh"
+
+
+// globals
+gsl_rng  *rangen;    // random number generator
+double   n_photons;
+int      verbose;     
+MODEL    model;
+SPECTRUM spectrum;
+double   D_obs[3], cos_obs[4];
+LINES    lines;
+
+
+//--------------------------------------------
+// the main program
+//--------------------------------------------
+int main(int argc, char **argv)
+{
+
+  void Run_Monte_Carlo(double);
+  void Run_UV_Transport(double, double, int);
+
+  // initialize MPI for parallelism
+  int my_rank, n_procs;
+  MPI_Init( &argc, &argv );
+  MPI_Comm_rank( MPI_COMM_WORLD, &my_rank );
+  MPI_Comm_size( MPI_COMM_WORLD, &n_procs );
+  if (my_rank == 0) verbose = 1; else verbose = 0;
+  if (verbose) printf("# Using %d processors\n",n_procs);
+
+  // setup and seed random number generator
+  const gsl_rng_type * TypeR;
+  gsl_rng_env_setup();
+  gsl_rng_default_seed = (unsigned int)time(NULL) + my_rank;
+  TypeR = gsl_rng_default;
+  rangen = gsl_rng_alloc (TypeR);
+  
+   // open up the lua parameter file
+  Lua lua;
+  std::string script_file = "param.lua";  // This default is *not* functional
+  if( argc > 1 ) script_file = std::string( argv[ 1 ] ); else return 0;
+  lua.init( script_file );
+
+  // Photons and viewing angle
+  n_photons =  lua.scalar<double>("n_photons");
+  double O_theta = lua.scalar<double>("O_theta"); 
+  double O_phi   = lua.scalar<double>("O_phi");
+  D_obs[0]  = sin(O_theta/180.0*PI)*cos(O_phi/180.0*PI);
+  D_obs[1]  = sin(O_theta/180.0*PI)*sin(O_phi/180.0*PI);
+  D_obs[2]  = cos(O_theta/180.0*PI);
+  cos_obs[0] = cos(O_theta/180.0*PI);
[…]

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/model_lbg.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5161 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -22,6 +22,7 @@ void MODEL::Init(const char* fname)
   LBG_vmax = lua.scalar<double>("LBG_vmax");
   LBG_alpha = lua.scalar<double>("LBG_alpha");
   vdop = lua.scalar<double>("vdoppler");
+  vinteract = lua.scalar<double>("vinteract");
 
   // Calcualte a few
   LBG_A =  LBG_vmax*LBG_vmax * (1.-LBG_alpha);  // Wind parameter

### 2010-08-30 Winds/papers/Theory/First/Analysis/LBG/Covering/3D/transport_lbg.cc

@@ -64,9 +64,12 @@ void Run_Monte_Carlo(double n_photons)
 
     // add in straight light
     Pe   = P_esc(p.lloc,p.r, -1);  // This one need not be unity
+    // printf(" \n", i);
     lobs = p.lloc*(1 - Get_vdotD(model.r_emit, p.r,D_obs)/C_LIGHT);
     Get_Rotated_Coords(p.r,r_rot);
     spectrum.Count(1,lobs,abs(r_rot[0]),abs(r_rot[1]),p.E_p*Pe);
+
+    // if ((i % 5000) == 0)  printf("i = %d \n", i);
 
     // Did we escape right out?
     if (Pe > 0.99999) continue;
@@ -102,7 +105,7 @@ void Run_Monte_Carlo(double n_photons)
       	//int l_scat = 0;
 	for (int j=0;j<lines.n();j++)
 	  {
-	    p.xloc = (p.lloc/lines.lambda(j) - 1)*C_LIGHT/model.v_doppler();
+	    p.xloc = (p.lloc/lines.lambda(j) - 1)*C_LIGHT/model.v_interact();
 	    // In resonance
 	    if ((p.xloc*p.xloc) <  1 && flg_resonance[j] == 0) {
 	      cover = model.Covering(rad);
@@ -133,6 +136,7 @@ void Run_Monte_Carlo(double n_photons)
 	// count scattered light
 	lobs = p.lloc*(1 - Get_vdotD(rad, p.r,D_obs)/C_LIGHT);
 	Pe   = P_esc(p.lloc,p.r,l_scat)*lines.P_scat(l_scat);  // Check to come into resonance with redder lines
+
 	Get_Rotated_Coords(p.r,r_rot);
 	spectrum.Count(1,lobs,abs(r_rot[0]),abs(r_rot[1]),p.E_p*Pe); 
 
@@ -228,9 +232,17 @@ void Line_Scatter(PHOTON &p, double lam, double *uvec)
 {
   double u0,u1,u2, R10, R11;
 
-  p.xloc = (p.lloc/lam - 1)*C_LIGHT/model.v_doppler();
+  p.xloc = (p.lloc/lam - 1)*C_LIGHT/model.v_interact();
 
   // Offset in radius (only proper along radial, but hopefully close enough)
+  double rad = sqrt(p.r[0]*p.r[0] + p.r[1]*p.r[1] + p.r[2]*p.r[2]);
+  double dvdr = model.DvDr(rad);
[…]

### 2010-09-03 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5149 ac11df5e-a788-c23b-a8e1-c758c323924d
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5174 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \section{Introduction}
+\label{sec:intro}
 
@@
 of our Sun, the associated absorption of bright quasars, and the
-spectacular jets of radio-loud AGN.   These gaseous outflows moderate
-the accretion of new material onto the object, inject energy and
-momentum into gas on large scales, and ...
+spectacular jets of radio-loud AGN.   These gaseous outflows 
+%%KHRR
+regulate the metal and dust content and distribution within the 
+objects and its surroundings, 
+%%
+moderate the accretion of new material, and %onto the object, 
+inject energy and momentum into gas on large scales. %, and ...
 Developing a comprehensive model for these flows is critical to
@@
 
-Star-burst galaxies, whose luminosity is dominated by \ion{H}{2} regions
+Starburst galaxies, whose luminosity is dominated by \ion{H}{2} regions
 and massive stars, are also observed to drive gaseous outflows.  These
@@
 together with a cool, denser phase traced by H$\alpha$ emission 
-\citep[e.g.][]{shc+04,km10}. 
+%% KHRR -- added refs
+\citep[e.g.][]{ham90,martin99,shc+04,km10}. 
 Several spectacular
 examples in the local universe demonstrate that flows can extend to
-tens of kpc from the galaxy \citep{M87} carrying significant speed
+up to $\sim 10$ kpc
+%tens of kpc 
+from the galaxy \citep{M87,lhw99,wsg08,vsr+03} carrying significant speed
 to escape from the gravitational potential well of the galaxy's dark
-matter halo \citep{wind_escape}.
-
-Beyond $z \sim 0$, galactic outflows are 
+matter halo \citep{wind_escape,sh09}.
+
+%Beyond $z \sim 0$, 
+Galactic outflows are also
 revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
@@
 the cool (\ion{Mg}{2}; $T \sim 10^4$K) and warm (\ion{C}{4}; $T \sim
-10^5$K) phases of the flow.  The incidence of cool gas outflows is
-nearly universal in star-forming galaxies;  this includes systems at $z \sim 0$
+10^5$K) phases of the flow.  
+The incidence of cool gas outflows is
+nearly universal in 
+%% KHRR added:
+vigorously
+%%
+star-forming galaxies;  this includes systems at $z \sim 0$
 which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
-\citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
+\citep{rvs05a,martin05,smn+09,mb09,cth+10}, 
+$z \sim 1$ star-forming galaxies traced by
 \ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rwk+10}, and
@@
 
-The observation of metal-line absorption is now a well established
-means of identifying outflows. Very little research,
-however,  has been directed
-to comparing the observations against (even idealized) wind
-models.  Instead, researchers have gleaned what limited information
+The observation of metal-line absorption is now a well-established
+means of identifying outflows.  Furthermore, because the X-ray and
+H$\alpha$ emission generated by winds is faint, absorption-line
+analyses have traditionally been the only way to probe outflows in
+distant galaxies. However, very little research
+has been directed
+toward comparing the observations against (even idealized) wind
+models (although see \citealt{fmm+09}).  
+Instead, researchers have gleaned what limited information
 is afforded by direct analysis of the absorption lines.  The data do yield
-robust measurements of the speed of the gas yet they poorly constrain the
+robust measurements of the speed of the gas (is this really true?), 
+yet they poorly constrain the
 optical depth, covering fraction, density, temperature, and distance
@@
 galactic-scale winds, therefore, remain open matters of debate
-\citep{debate}.
-
-Recent studies of $z \sim 1$ star-forming galaxies have revealed that
-the cool gas often exhibits significant resonant-line emission (e.g.\
-\ion{Mg}{2}) in
+\citep{debate,mqt05,sdr08,sh09,ssr02,od06,kkd+09}.
+
+Recent studies of $z \lesssim 1$ star-forming galaxies have revealed that
+the cool outflowing gas often exhibits significant resonant-line emission (e.g.\
+\ion{Mg}{2}, \ion{Na}{1}) in
 tandem with the nearly ubiquitous blue-shifted absorption
-\citep{wcp+09,rwk+10}.  The resultant spectra resemble the P-Cygni
+\citep{wcp+09,rwk+10,cth+10}.  The resultant spectra resemble the P-Cygni
 profile characteristic of stellar winds.
-\cite{rubin+10c} have also detected line
-emission from non-resonant \ion{Fe}{2}$^*$ transitions 
-Their interpretation is that the emission is the result of photons
-scattered off the wind into our sightline, analogous to P-Cygni.
-\cite{rubin+10c} also observed spatially extended \ion{Mg}{2} emission
-which they use to estimate the size of the outflow.  They infer that
-the wind extends to at least 5\,kpc from the galaxy.  Line emission is
-also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
-and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
-A comprehensive analysis of the emission lines
-related to galactic-scale outflows
-(e.g.\ via deep integral-field-unit observations) may offer unique
-diagnostics on the morphology and density of the outflow, eventually
-setting tighter constraints on the energetics of the flow.
-
-[Phillips first reported?]
-Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
-reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
-and Rubin et al.\ 2011 (in prep).
-\cite{wcp+09}, who
+This phenomenon was first reported by \citet{phillips93}, who observed 
+blue-shifted absorption and red-shifted emission in the \ion{Na}{1}
+transition in the spectrum of the local starburst galaxy NGC 1808.
+More recently, \cite{wcp+09}, who
 studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
@@
 of lower redshift galaxies.
-[Did Kate see FeII* emission in her stacks? If not, why not?]
+
+Bright \ion{Mg}{2} line emission has also been
+reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
+and Rubin et al.\ 2011 (in prep).
+In their analysis of a single galaxy spectrum, \cite{rubin+10c}
+further demonstrated that the \ion{Mg}{2} line emission is spatially
+extended, and used the size of the emission to infer that the wind 
+extends to at least 7\,kpc from the galaxy.
+These authors additionally detected line
+emission from non-resonant \ion{Fe}{2}$^*$ transitions, and attribute
+the emission to fluorescence powered by \ion{Fe}{2} resonant
+absorption.  In other words, these photons are re-emitted by the wind
+into our sightline, and are analogous to the emitted photons in a P
+Cygni profile.
+%Their interpretation is that the emission is the result of photons
+%scattered off the wind into our sightline, analogous to P-Cygni.
+%\cite{rubin+10c} also observed spatially extended \ion{Mg}{2} emission
+%which they use to estimate the size of the outflow.  They infer that
+%the wind extends to at least 7\,kpc from the galaxy.  
+Line emission is
+also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
+and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
+We emphasize that this emission arises from a completely different
+physical process than those generating X-ray and H$\alpha$ emission
+(e.g., shocks), and presumably probes both the cool gas at the base of
+the wind and the outskirts of the flow (i.e., wherever a given
+transition is optically thick).
+A comprehensive analysis of the %emission lines
+scattered and fluorescent emission
+related to galactic-scale outflows
+(e.g.\ via deep integral-field-unit [IFU] observations,
+\citealt{ssb+05,wsg08}) 
+may offer unique
+diagnostics on the spatial extent, morphology, and density of the outflow 
+from distant galaxies,
+eventually
+setting tighter constraints on the energetics of the flow.
+
+%[Phillips first reported?]
+%Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
+%reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
+%and Rubin et al.\ 2011 (in prep).
+%\cite{wcp+09}, who
+%studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
+%\ion{Mg}{2} emission in a small subset of the individual galaxy
+%spectra of their large sample.  These were excluded from the full
+%analysis on concerns that the emission was related to AGN activity.
+%The stacked spectra of the remaining galaxies, however, also indicated
+%\ion{Mg}{2} emission, both directly and when the authors modeled and
+%`removed' the $v \approx 0\mkms$ absorption component.  Although the
+%authors suggested the emission could be related to back-scattered
+%light in the wind, they also allowed that it could be related to weak
+%AGN activity.   Very similar \ion{Mg}{2} emission was observed by
+%\cite{rwk+10} who repeated the analysis of \cite{wcp+09} on a set
+%of lower redshift galaxies. 
+%[Did Kate see FeII* emission in her stacks? If not, why not?]
 
@@
 datasets on galactic-scale winds, a key ingredient to a proper
-analysis is absent.
-[Draw analogy to exploring SN lightcurves and spectra]
-
+analysis is absent.  Just as comparisons between observed supernova 
+lightcurves and spectra and radiative transfer calculations of
+of SNe models have provided crucial insight into the physics driving,
+e.g., standard candle relationships for both Type Ia and IIP SNe 
+\citep{kw07,kw09}, modeling of the observable signatures of galactic
+outflows is necessary for understanding the physical
+properties of the gas and ultimately the physics driving the flows. 
+%[Draw analogy to exploring SN lightcurves and spectra]
 In this paper, we take the first steps toward modeling the absorption
-and emission properties of cool gas outflows.  Using Monte Carlo
+and emission properties of cool gas outflows as observed in one
+dimensional spectra and by IFUs.  Using Monte Carlo
 radiative transfer techniques, we study the nature of \ion{Mg}{2} and
 \ion{Fe}{2} absorption and emission for winds with a range of
-properties.  Although the winds are idealized, the results frequently
+properties, accounting for the effects of resonant scattering and
+fluorescence for the first time.  
+Although the winds are idealized, the results frequently
 contradict our intuition and 
 challenge the straightforward conversion of observables to (even crude) physical
-constraints.  [Add another line or two]
+constraints.  We caution that these findings have a direct bearing on
+recent and upcoming surveys of galactic outflows, particularly those
+which make use of \ion{Mg}{2} and \ion{Fe}{2} transitions to probe
+outflow properties.
+%[Add another line or two]
 
@@
 $\S$~\ref{sec:alternate}, we explore wind models with a broader range
-of density and velocity laws.  Consideration of key observables is
-given in $\S$~\ref{sec:obs} and we discuss the principal results
-in $\S$~\ref{sec:discuss}.  A brief summary is given in
-$\S$~\ref{sec:summary}.
+of density and velocity laws. We discuss the principal results and
+connect to observations in $\S$~\ref{sec:discuss}.  A brief summary is
+given in $\S$~\ref{sec:summary}.
 
@@
 within the interstellar medium (ISM).  For the spectral regions studied
-here, most stars show a featureless continuum but a few spectral
+here, most stars show a featureless continuum, but a few spectral
 types do show significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
-{\bf [Kate: Any emission??]}  \ion{H}{2} regions, meanwhile, are observed to emit
+In addition, asymmetric and/or blue-shifted absorption is exhibited in these
+transitions in A and F stars driving stellar winds \citep{sll+94}.
+\ion{Mg}{2} P Cygni profiles are observed in a handful of F stars by \cite{sll+94}, who
+attribute the emission to chromospheric activity rather than mass-loss effects.
+%{\bf [Kate: Any emission??]}  
+\ion{H}{2} regions, meanwhile, are observed to emit weakly
 at the \mgiid\ doublet, primarily due to recombinations in the outer
-layers {\bf [Kate: How about FeII?]}.  It is beyond the scope of this paper to
+layers \citep{kbc+93} {\bf [Kate: How about FeII?  X: I don't know of any examples of this.]}.  
+It is beyond the scope of this paper to
 properly model the 
@@
 \subsection{Monte Carlo Algorithm}
+\label{sec:monte}
 
@@
 Extraplanar material likely associated with a galactic-scale 
-outflow has been observed to emit IR radiation characteristic of dust \citep[e.g.][]{M87_dust}.
+outflow has been observed to emit IR radiation characteristic of dust 
+\citep[e.g.][]{M87_dust,hrg90,adb99,rkl01}.
 Essentially all astrophysical environments that contain both cool gas
@@
 infinity.  The ambient ISM of a star-forming galaxy may be expected to exhibit
-\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{dust_again}.
+\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{dust_again,cf00}.
 
@@
 For a wind with a steep velocity law (i.e.\ a large gradient $dv/dr$)
-and/or a a narrow intrinsic profile (i.e.\ a small Doppler parameter),
+and/or a narrow intrinsic profile (i.e.\ a small Doppler parameter),
 \citet{sobolev60} introduced a formalism that defines the opacity of
@@
 saturated) which only partially covers the emitting source
-\citep[e.g.][]{hammann+10}.  Our fiducial wind model, however, 
+\citep[e.g.][]{rvs05a,hammann+10}.  Our fiducial wind model, however, 
 {\it entirely covers the source}; the apparent partial covering must
@@
 
+%%% KHRR edited this-- no content change intended, just tried to
+%%% remove repetition
 Turning to the emission profiles of the \mgiid\ doublet, one notes
-that they are also similar with comparable equivalent widths The
-flux of the \mgiib\ transition even exceeds that for \mgiia\ giving a
-line ratio that is far below the $2:1$ ratio that one may have naively
-expected. 
-[Does recombination predict 2:1??]
-The emission profiles are very similar because the gas is optically
-thick yielding comparable total absorption. 
-Furthermore, the flux from \mgiib\ actually exceeds the
-\mgiia\ emission because the wind speed is greater than the velocity separation
+that they are quite similar with comparable equivalent widths.
+This is because the gas is optically
+thick yielding comparable total absorption. The
+flux of the \mgiib\ transition even exceeds that for \mgiia\ 
+because the wind speed is greater than the velocity separation
 of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
@@
 \mgiia\ emission profile is partially absorbed by \mgiib\ and
-re-emitted at lower frequency.  We conclude that the relative
+re-emitted at lower frequency.
+This yields a
+line ratio that is far below the $2:1$ ratio that one may have naively
+expected, and leads us to conclude that the relative
 strengths of the emission lines is sensitive to both the opacity and
 velocity extent of the wind. 
+[Does recombination predict 2:1??  The simple HII region Cloudy model
+produces nearly a 2:1 ratio, though not exactly. (Kate)]
+%The emission profiles are very similar because the gas is optically
+%thick yielding comparable total absorption. 
+%Furthermore, the flux from \mgiib\ actually exceeds the
+%\mgiia\ emission because the wind speed is greater than the velocity separation
+%of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
+%Therefore, the red wing of the
+%\mgiia\ emission profile is partially absorbed by \mgiib\ and
+%re-emitted at lower frequency.  We conclude that the relative
+%strengths of the emission lines is sensitive to both the opacity and
+%velocity extent of the wind.
 
@@
 which will suppress the wind preferentially at low galactic latitudes,
-perhaps yielding a bi-conic morphology \citep[e.g.][]{M87}.
+perhaps yielding a bi-conic morphology \citep[e.g.][]{ham90,wws02}.
 Lastly, the galaxy could be surrounded by an
@@
 (ii) a bi-conical wind where the density is set to zero for angles
-$|\theta| < \theta_b$ that and is viewed along the plane of symmetry.
+$|\theta| < \theta_b$ and that is viewed along the plane of symmetry.
 
@@
 however.  Specifically, we find that the flux is reduced by a factor 
-of the order of (1+\taud)$^{-1}$ (Figure~\ref{fig:dust_tau},
+of the order of (1+\taud)$^{-1}$ (Figure~\ref{fig:dust_tau}),
 instead of the factor
 exp(--\taud) that one may have naively predicted. 
-Although the \ion{Mg}{2} photons are resonantly
+%Although the \ion{Mg}{2} photons are resonantly
 In terms of absorption, the profiles are
@@
 
-[Kate: Write the details of velocity + density law]
-
+%[Kate: Write the details of velocity + density law]
+As discussed in $\S$~\ref{sec:intro}, the importance of various physical mechanisms
+in driving these ubiquitous galactic outflows remains an open
+question.  Several studies advocate a primarily energy-driven
+wind scenario, in which the hot wind produced by the thermalized
+energy from SNe ejecta entrains cool clouds via ram pressure \citep[e.g.][]{cc85,ham90,sh09}.
+Alternatively, momentum deposition by photons emitted by luminous star clusters onto
+dust grains in the ISM may also play an integral role in driving
+large-scale outflows \citep[e.g.][]{mqt05,mmt10}.  Both of these
+mechanisms likely contribute more or less significantly in a given
+galaxy; however, the latter (radiation-pressure driving) has the added
+advantage that it does not destroy cool gas clouds as it acts.  Here
+we explore the line profiles produced by a radiation-pressure driven
+wind model as described by \cite{mqt05}.
+
+These authors start by assuming the galaxy is an isothermal sphere
+with mass profile $M_{gal}(r) = 2\sigma^2r/G$, where $\sigma$ is the
+velocity dispersion, and with luminosity $L$.  The gas mass profile is
+simply $M_g(r) = f_g M_{gal}(r)$, with $f_g$ a constant gas fraction.  
+The dust has opacity $\kappa$ and is optically thin, such that the force per unit mass of wind
+material due to radiation is $\frac{\kappa L}{4\pi c r^2}$.
+Ignoring gas pressure, and assuming a steady state for the flow (i.e.,
+the mass outflow rate, $dM_{\rm wind}/dt$, is constant), the momentum
+equation for the wind is 
+\begin{equation}
+\mvr \frac{d\mvr}{dr} = -\frac{GM_{gal}(r)}{r^2} + \frac{\kappa L}{4\pi c r^2}.
+\end{equation}
+Substituting $2\sigma^2 r/G$ for $M_{gal}(r)$ and solving for $\mvr$,
+\citet{mqt05} find
 \begin{equation}
@@
 \end{equation}
-
+(their Equ. 26),
+where $\mvr = 0$ at $R_0$ and $R_g = \frac{\kappa L}{8\pi c \sigma^2}$.
+The corresponding density profile for the gas is given by
 \begin{equation}
-n(r) = \frac{dM_{\rm wind}/dt}{r^2 v(r)}
+n(r) = \frac{dM_{\rm wind}/dt}{m_p r^2 v(r)}, 
 \end{equation}
+with $m_p$ the mass of the hydrogen atom.
 Similar to the fiducial wind model, this wind has a decreasing density
@@
 star-forming galaxies that exhibit cool gas outflows.  
-This includes emission related to \ion{Na}{1} \citep{phillips,chen},
+This includes emission related to \ion{Na}{1} \citep{phillips93,cth+10},
 \ion{Mg}{2} emission \citep{wcp+09,rwk+10}, 
@@
 galaxies.  Indeed, our results indicate that line-emission may
-be produced by all of galaxies driving a wind.
+be produced by all %of 
+galaxies driving a wind.
 
@@
 detected yet the authors report no significant line emission.  This
-includes \ion{Na}{1} flows \cite{rvs05a,martin,smn+09}, 
+includes \ion{Na}{1} flows \cite{rvs05a,martin05,smn+09}, 
 \ion{Mg}{2} and \ion{Fe}{2} absorption in
@@
 that is trapped for many scatterings within a dusty medium will 
-preferentially be  relative to a non-resonant photon.  In
+preferentially be lost (???) relative to a non-resonant photon.  In
 $\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
@@
 spectra to study outflows
-\citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the
+\citep[e.g.][]{wcp+09,smn+09,rwk+10}.   The main difference from the
 single galaxy observation shown in panel (a) is the smearing of
@@
 \section{Summary}
-\label{sec:conclude}
+\label{sec:summary}
 
@@
 implications of stacking galaxy spectra to study outflows
-\citep[e.g.][]{wcp+09,sato+,rkc+10}.   The main difference from the
+\citep[e.g.][]{wcp+09,smn+09,rwk+10}.   The main difference from the
 single galaxy observation shown in panel (a) is the smearing of

### 2010-09-09 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5179 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 %tens of kpc 
-from the galaxy \citep{M87,lhw99,wsg08,vsr+03} carrying significant speed
+from the galaxy \citep{lhw99,wsg08,vsr+03} carrying significant speed
 to escape from the gravitational potential well of the galaxy's dark
-matter halo \citep{wind_escape,sh09}.
+matter halo \citep[e.g.][]{sh09}.
 
@@
 Instead, researchers have gleaned what limited information
-is afforded by direct analysis of the absorption lines.  The data do yield
-robust measurements of the speed of the gas (is this really true?), 
+is afforded by direct analysis of the absorption lines.  The data
+diagnose the speed of the gas relative to the galaxy, 
 yet they poorly constrain the
@@
 galactic-scale winds, therefore, remain open matters of debate
-\citep{debate,mqt05,sdr08,sh09,ssr02,od06,kkd+09}.
+\citep{mqt05,sdr08,sh09,ssr02,od06,kkd+09}.
 
@@
 Bright \ion{Mg}{2} line emission has also been
-reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10c}
-and Rubin et al.\ 2011 (in prep).
+reported for individual galaxies at $z \sim 0.7$ by \cite[][see also
+Rubin et al\ 2011, in prep.]{rubin+10c}.
 In their analysis of a single galaxy spectrum, \cite{rubin+10c}
@@
 absorption.  In other words, these photons are re-emitted by the wind
-into our sightline, and are analogous to the emitted photons in a P
-Cygni profile.
+into our sightline, and are analogous to the emitted photons in a P-Cygni profile.
 %Their interpretation is that the emission is the result of photons
@@
 %the wind extends to at least 7\,kpc from the galaxy.  
-Line emission is
+Line-emission is
 also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
@@
 properties, accounting for the effects of resonant scattering and
-fluorescence for the first time.  
+fluorescence. 
 Although the winds are idealized, the results frequently
@@
 \subsection{The Radiative Transitions}
+
+[JXP:  This needs to be re-run and revised following Kate's update.
+Will do so in the next few days (hopefully tomorrow)]
 
@@
 would (i) systematically underestimate the true optical
-depth and (ii) falsely conclude that the wind partially covers the
-source.  We will find that this
-[behavior] is a generic result, even for wind models that include
+depth and/or (ii) falsely conclude that the wind partially covers the
+source.  We will find that these are
+generic results, even for wind models that include
 dust and are not fully isotropic.
@@
 
-[Add a paragraph on the bi-conical wind]
+[Add a paragraph on the bi-conical wind once we are confident in the
+results.  This is may be a rather big effect.]
+
+[Consider showing a 2D model for biconical]
 
@@
 absolute flux still exceeds the fiducial model
-(Table~\ref{tab:line_diag}).
-[Should I show a figure?]
+(Table~\ref{tab:line_diag}).  At large negative velocity offset from
+systemic, the two profiles are nearly identical.
 
@@
 regions, and back-scattering off the galactic-scale wind.
-[Are there aspects of those works that are now understood, e.g. the
-difference in FeII 2586 and FeII 2600?]
 Our results suggest that the majority of the observed line-emission is 
 from scattered photons in the cool gas outflows of these star-forming
-galaxies.  Indeed, our results indicate that line-emission may
-be produced by all %of 
+galaxies.  Indeed, line-emission should be generated by all 
 galaxies driving a wind.
@@
 detected yet the authors report no significant line emission.  This
-includes \ion{Na}{1} flows \cite{rvs05a,martin05,smn+09}, 
+includes \ion{Na}{1} flows \citep{rvs05a,martin05,smn+09}, 
 \ion{Mg}{2} and \ion{Fe}{2} absorption in
@@
 reassess several of the effects that can reduce the line-emission
-and consider whether these could prevent its detection for many
+and consider whether these prevent its detection for many
 star-forming galaxies.
@@
 Dust is frequently invoked to explain the suppression of line-emission
-of resonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
+for resonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
 that is trapped for many scatterings within a dusty medium will 
-preferentially be lost (???) relative to a non-resonant photon.  In
+be preferentially extincted relative to a non-resonant photon.  In
 $\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
@@
 trapped, they require only one to a few scatterings
-to escape the wind model limiting the effects of
+to escape the wind which limits the effects of
 dust.  This reflects the moderate opacity of the \ion{Mg}{2}
@@
 converted to non-resonant photons that freely escape the wind.
-Therefore, a wind model that trapped \ion{Mg}{2}
-photons for many scatterings would not similarly trap 
+Therefore, a wind model that traps \ion{Mg}{2}
+photons for many scatterings does not similarly trap 
 \feiid\ photons.  The effects of dust are much 
@@
 Another factor that may reduce line-emission is a
-non-isotropic wind model. The flux is lower, for example, if one
+non-isotropic (e.g.\ biconical) wind model. The flux is lower, for example, if one
 eliminates the backside to the wind (e.g.\ the source itself could
-shadow a significant fraction of the backside).  To zeroth order, the
-line-emission scales 
+shadow a significant fraction of the backside).  
+For our fiducial model, many of the photons scattered into our
+sightline arise nearly normal to the sightline such that a biconicial
+wind has signficantly lower line emission
+($\S$~\ref{sec:anisotropic}). 
+For the anisotropic winds explored in this paper,
+the line-emission scales 
 roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
@@
 points toward us, it is difficult to reduce $\Omega$ much
-below $2 \pi$ and, therefore, anisotropy likely reduces the
-emission by at most a factor of order unity.  
-Similarly, an anisotropic source may alter the predicted
+below $2 \pi$ and, therefore, anisotropy reduces the
+emission by a factor of order unity.  
+Similarly, an anisotropicly emitting source would modify the predicted
 line-emission.  For example, if the backside of the galaxy were
@@
 of \ion{Mg}{2} and \ion{Fe}{2}
-by one or two factors of order unity.  This would generally
-not be sufficient, however, to reduce the emission below the typical detection
-limits.
+by one to a few factors of order unity.  For some galaxies, these
+effects may help to explain the absence of significant line-emission,
+but we suspect these would generally
+not be sufficient to reduce it below the detection limit.
 
@@
 galaxy.  We then tabulate the equivalent width of the line-emission
-through slits with a range of widths, parameterized by twice the radius
-where the wind has a Sobolev optical depth of $\tau^S = 0.2$ (\rtt).
+through slits with a range of widths, parameterized by \rtt: twice the radius
+where the wind has a Sobolev optical depth of $\tau^S = 0.2$. 
 The line-emission will be weak beyond
 this radius because the photons have only a low probability of
-interacting with the wind.  For the fiducial wind model, 
+being scattered.  For the fiducial wind model, 
 the \mgiia\ transition has $\mrtt \approx 15$\,kpc 
@@
 wind model (black curves).
-[Add LBG, radiative models]
+[Add radiative model]
 The \ewe/\ewabs\ curves rise very steeply with increasing slit width and then
 plateau when the slit width reaches $\approx \mrtt$.  
-For this model, the emission is concentrated toward the source; this
+For the fiducial model, the emission is concentrated toward the source; this
 derives from the density and velocity profiles but is also a simple
@@
 The results are comparable for other wind models considered
-in this paper (colored curves in Figure~\ref{fig:obs_slit}).
+in this paper. 
 All of the curves rise steeply enough that 
@@
 relative to the absorption of the outflow, our analysis
-indicates that detectable line-emission should frequently occur. 
+indicates that detectable line-emission should occur frequently. 
 Furthermore, the line-emission could be suppressed so as not to exceed
@@
 
-These negative effects for \ion{Mg}{2} absorption are reduced
+These effects for \ion{Mg}{2} absorption are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
@@
 \ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
-wavelengths, which does not effect the absorption profiles. 
+wavelengths which does not affect the absorption profiles. 
 Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
-closely follow the intrinsic value, one derives more accurate peak
+closely follow the intrinsic values, one derives more accurate peak
 optical depths, and the absorption kinematics more faithfully reflect
@@
 predicts a velocity offset between the \ion{Fe}{2} and \ion{Mg}{2}
-centroids (Figure~\ref{fig:obs_vtau}).
+absorption-line centroids (Figure~\ref{fig:obs_vtau}).
 %because scattered photons
@@
 %absorption at $v \sim 0 \mkms$ for the \ion{Mg}{2} transitions.  
-This affects analysis of gas related to the ISM of the galaxy and
-also material infalling at a modest speed.  One must take careful
-consideration of line emission, therefore,  before drawing robust
-conclusions about the presence/absence of gas with small velocity
-offsets from systemic. Figure~\ref{fig:obs_vtau} also emphasizes that
+This affects the analysis of gas related to the ISM of the galaxy and
+also material infalling at a modest speed.  
+Figure~\ref{fig:obs_vtau} also emphasizes that
 the \ion{Mg}{2} profiles may misrepresent the kinematics of the bulk of
@@
 spectra to study outflows
-\citep[e.g.][]{wcp+09,smn+09,rwk+10}.   The main difference from the
+\citep[e.g.][; S10]{wcp+09,rwk+10}.   The main difference from the
 single galaxy observation shown in panel (a) is the smearing of
@@
 a diversity of \ion{Mg}{2} profiles.    
-Special care is required to interpret properties of the wind (and
+Special care is required, therefore, to interpret properties of the wind (and
 ISM) from such spectral analysis.
-[Emphasize that the ISM component has *no chance* of being revealed]
-[{\bf Kate}: try stacking your set of observed LRIS data]
 
@@
 large format IFU or narrow band imager) may detect the emission in
-azimuthally averaged apertures. [Give estimate]
-[Add FeII* to the SB figure]
+azimuthally averaged apertures. {\bf [JXP: Give estimate]
+[JXP: Add FeII* to the SB figure]}
 Of the transitions considered in this paper, \ion{Mg}{2} emission is
@@
 (ii) there are fewer emission channels per absorption line than for
-\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiia) has the
-highest peak and integrated fluxes 
-(Figure~\ref{fig:obs_sb}).
-
-The kinematics of the line emission also offer insight into physical
+\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiib) frequently has the
+highest peak and integrated fluxes (Figure~\ref{fig:obs_sb}).  
+On the other hand, the \ion{Mg}{2} transitions are more susceptible to
+the effects of dust extinction and for some galaxies \feiis\ emission
+will be dominant.  [Last comment]
+
+The kinematics of the line-emission also offer insight into physical
 characteristics of the wind.
-
-[\feiis\ width!!]
-
-[Centroid of \ion{Mg}{2} $-->$ dust, isotropy]
+In $\S$~\ref{sec:dust}, we emphasized that dust extinction
+preferentially suppresses photons scattered off the backside of the
+wind (e.g.\ with $\mdv > 0 \mkms$) so that the centroid is shifted to
+negative velocities.  Similarly, anisotropic models with reduced
+emission off the backside yield emission lines that are centered
+blueward of the galaxy's systemic redshift.  These effects are mos
+prominent in the \feiis\ emission.  The centroids of the \ion{Mg}{2}
+lines, meanwhile, may be modififed by absorption, e.g.\ a wind with
+speeds exceeding 600\kms\ will have \mgiib\ scatter \mgiia\ photons.
+Therefore, the line centroids are sensitive to the optical depth
+profile of the wind.
+
+We also find that the emission-line widths trace specific
+characteristics of the wind.  For the \feiis\ emission, the widths are
+most sensitive to the optical depth at large velocities from
+systemic.  This is illustrated in Figure~\ref{fig:edelv} which plots
+the 90\%\ velocity width $\Delta v_e$ of \feiic\ versus the velocity
+where the wind optical depth is maximal ($v_\tau$).  It is evident
+that $\Delta v_e$ increases with $v_\tau$; a large measured width for
+\feiis\ emission requires a wind profile with large optical depths at
+$\mdv < 200 \mkms$.
+
+Lastly, the line ratios of paris of transitions (e.g.\ \mgiia/\mgiib,
+\feiic/\feiid) are sensitive to several characteristics of the wind.
+These include dust extinction, the relative abundances of Mg/Fe, and
+...
 
@@
 
-[If MgII emission is 'common' for HII regions,
-why don't we see it *always* when we see OII, Hbeta, etc? Is it
-trapped and then extincted? Same for FeII*]
+[Discuss why there can be cases with $v_\tau \sim 0$ and high
+$\tau_{pk}$, if I can figure it out!]
 
@@
 
-   (i)  Morphology [MgII is likely best]
-  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
+%   (i)  Morphology [MgII is likely best]
+%  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
  (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
 
-[Does recombination predict 2:1 for MgII??]
-[We also emphasize that departures from a 2:1
-ratio indicate that processes other than simple recombination are
-active. ]
-
-[Profiles are modified by {\it many} factors => Difficult to derive
-robust constraints from absorption alone.]
-
-[Is one safe if there is no emission detected?]
-
-[What does MgI tell us about winds?  Why no P-Cygni?]
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section{Summary}
@@
 $\tau^S = 0.2$.  The black curves correspond to the fiducial wind
-model ($\S$~\ref{sec:fiducial}), the red curves are for the
-LBG-partial covering scenario ($\S$~\ref{sec:Covering}), and the
-radiative-driven wind ($\S$~\ref{sec:radiative}) has blue curves.
+model ($\S$~\ref{sec:fiducial}; $\mrtt \approx 15$\,kpc), the red curves are for the
+LBG-partial covering scenario ($\S$~\ref{sec:Covering}; $\mrtt \approx
+8$\,kpc), and the
+radiative-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
 For all of the wind models, the \ewe/\ewabs\ ratio rises very steeply
-with slit width and plateaus at $\approx \mrtt$.  [Add?]
+with slit width and then plateaus at $\approx \mrtt$.  
+Therefore, a slit that exceeds $\approx 0.5 \mrtt$ will admit nearlly
+all of the photons scattered to our sightilne.
 }
@@
 dashed (dotted) curves trace a 50\%\ (10\%) reduction in \ewabs\
-relative to $W_{\rm i}$.  One notes a reduction in \ewabs by $\approx
+relative to $W_{\rm i}$.  One notes a reduction in \ewabs\ by $\approx
 30-50\%$ for the \mgiia\ transition (the effect is generally larger
@@
 photons have filled-in the absorption profiles at velocities $\mdv
-\gtrsim -400 \mkms$.  Therefore, the effects are greatest for wind
-models where the optical depth peaks near $\mdv \sim 0 \mkms$.
+\gtrsim -400 \mkms$. The effects are greatest for wind
+models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
+the majority of scattered photons have this realtive velocity.
 Indeed, models with $v_\tau < -400 \mkms$ all show $\mtpk > 3$.
@@
 \caption{
-Comparison of the velocities where the \feiia\ and \mgiia\ absorption
-profiles have greatest depth.  Results for all the models
+Comparison of the velocities for which the \feiia\ and \mgiia\ absorption
+profiles have greatest depth.  Results for all of the models
 studied in this paper are presented (Tables~\ref{tab:line_diag},
@@
 It is evident that wind models with a peak optical depth near the
-systemic velocity have a \mgiib\ absorption profile shifted blueward
+systemic velocity have a \mgiia\ absorption profile shifted blueward
 by one to several hundred \kms.  Analysis of such profiles may lead to
@@
 \mgiib.  One also finds that the \mgiia\ absorption is shifted to
-shorter wavelength (a greater velocity offset from systemic).  
+shorter wavelengths (a greater velocity offset from systemic).  
 (b) The solid curve shows a stack of 100 spectra of the ISM+wind
@@
 line-emission and absorption that reduces the height/depth of each.
-The effects would be even more pronounced if one studied spectra with
+The effects may be even more pronounced if one studied spectra with
 a diversity of \ion{Mg}{2} profiles.    
@@
 \caption{
-Surface brightness
+Surface brightness profiles of the fiducial wind model for the \mgiia\
+(solid) and \feiic\ (dotted) transitions.  Both profiles peak at small
+radii and decrease by several orders of magnitude before reaching the
+outer edge of the wind.  The profiles are sufficiently shallow,
+however, that the azimuthally integrated flux declines by only a
+factor of XXX from $r = 1$\,kpc to $r=10$\,kpc.  Therefore, a
+sensitive IFU observation could map the emission (and, in principle,
+the kinematics) from $r_{\rm inner}$ to $r_{\rm outer}$.
 }
@@
 
+\begin{figure}
+\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
+\caption{
+Width of \feiis.
+}
+\label{fig:obs_edelv}
+\end{figure}
+
 \end{document}

### 2010-09-10 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5191 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 J. Xavier Prochaska\altaffilmark{1}, 
-Others
-%John M. O'Meara\altaffilmark{2}, 
-%Gabor Worseck\altaffilmark{1} 
-%\& Scott Burles\altaffilmark{3}
+Daniel Kasen\altaffilmark{1,2,3}, 
+Kate Rubin\altaffilmark{1} 
 }
 \altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of California, 1156 High Street, Santa Cruz, CA 95064}
-%\altaffiltext{2}{Department of Chemistry and Physics, Saint Michael's College.
-%One Winooski Park, Colchester, VT 05439}
+\altaffiltext{2}{UCB?}
+\altaffiltext{3}{Hubble Fellow}
 
@@
 sightline arise nearly normal to the sightline such that a biconicial
-wind has signficantly lower line emission
+wind has significantly lower line emission
 ($\S$~\ref{sec:anisotropic}). 
@@
 emission by a factor of order unity.  
-Similarly, an anisotropicly emitting source would modify the predicted
+Similarly, an anisotropically emitting source would modify the predicted
 line-emission.  For example, if the backside of the galaxy were
@@
 large format IFU or narrow band imager) may detect the emission in
-azimuthally averaged apertures. {\bf [JXP: Give estimate]
-[JXP: Add FeII* to the SB figure]}
+azimuthally averaged apertures. {\bf [JXP: Give estimate]}
 Of the transitions considered in this paper, \ion{Mg}{2} emission is
@@
 prominent in the \feiis\ emission.  The centroids of the \ion{Mg}{2}
-lines, meanwhile, may be modififed by absorption, e.g.\ a wind with
+lines, meanwhile, may be modified by absorption, e.g.\ a wind with
 speeds exceeding 600\kms\ will have \mgiib\ scatter \mgiia\ photons.
@@
 most sensitive to the optical depth at large velocities from
-systemic.  This is illustrated in Figure~\ref{fig:edelv} which plots
+systemic.  This is illustrated in Figure~\ref{fig:obs_edelv} which plots
 the 90\%\ velocity width $\Delta v_e$ of \feiic\ versus the velocity
@@
 with slit width and then plateaus at $\approx \mrtt$.  
-Therefore, a slit that exceeds $\approx 0.5 \mrtt$ will admit nearlly
-all of the photons scattered to our sightilne.
+Therefore, a slit that exceeds $\approx 0.5 \mrtt$ will admit nearly
+all of the photons scattered to our sightline.
 }
@@
 models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
-the majority of scattered photons have this realtive velocity.
+the majority of scattered photons have this relative velocity.
 Indeed, models with $v_\tau < -400 \mkms$ all show $\mtpk > 3$.
@@
 Surface brightness profiles of the fiducial wind model for the \mgiia\
-(solid) and \feiic\ (dotted) transitions.  Both profiles peak at small
+(solid) and \feiid\ (dotted) transitions.  Both profiles peak at small
 radii and decrease by several orders of magnitude before reaching the
@@
 however, that the azimuthally integrated flux declines by only a
-factor of XXX from $r = 1$\,kpc to $r=10$\,kpc.  Therefore, a
+factor of $\approx 10$ from $r = 1$\,kpc to $r=10$\,kpc.  Therefore, a
 sensitive IFU observation could map the emission (and, in principle,
@@
 \caption{
-Width of \feiis.
+Plot of the 90\%\ velocity width ($\Delta v_e$) of \feiic\ emission versus the
+velocity where the resonance lines achieve peak optical depth
+$v_\tau$ in absorption.  The $\Delta v_e$ values rise steadily with
+increasing offset of $v_\tau$ from systemic.  The width of the \feiic\
+emission line, therefore, offers an independent diagnostic of the wind
+speed.
 }

### 2010-09-10 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_mgii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5203 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -22,12 +22,12 @@ int    n_phi     =    1;      // number of phi bins
 
 // grid parameters
 double r_inner   =  1.0;      // inner boundary radius, in kpc
-double r_outer   = 20.0;      // outer boundary radius, in kpc
+double r_outer   = 50.0;      // outer boundary radius, in kpc
 double r_emit    =  0.2;      // boundary to emit from
-double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
-double v_parm    =  1.0;      // power law of velocity profile
+double n_0       =  3e-2;     // number density at inner boundary (cm^-3)
+double r_g    =  4.0;      // Wind parameter (kpc)
 double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
-double v_rval    = r_outer;
+double r_0    = 1.;      // Launch radius (kpc)
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
@@ -125,7 +125,7 @@ double Get_Velocity(double r)
   //  return v_max*pow(r/r_outer,v_law);
   // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
   if(r < r_inner) return 0.;
-  return v_norm * sqrt( v_parm * (1./v_rval - 1./r) + log(v_rval/r) );
+  return v_norm * sqrt( r_g * (1./r_0 - 1./r) + log(r_0/r) );
 }
 
 

### 2010-09-11 Winds/papers/Theory/First/Analysis/Radiation/outflow_rad_feii.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5204 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -28,9 +28,9 @@ double r_inner   =  1.0;      // inner boundary radius, in kpc
 double r_outer   = 20.0;      // outer boundary radius, in kpc
 double r_emit    =  0.2;      // boundary to emit from
 double n_0       =  1e-1;     // number density at inner boundary (cm^-3)
-double v_parm    =  1.0;      // power law of velocity profile
+double r_g    =  4.0;      // Wind parameter (kpc)
 double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
-double v_rval    = r_outer;
+double r_0    = 1.;      // Launch radius (kpc)
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
@@ -131,7 +131,7 @@ double Get_Velocity(double r)
   //  return v_max*pow(r/r_outer,v_law);
   // return v_min + (r-r_inner)/(r_outer-r_inner) * (v_max-v_min);
   if(r < r_inner) return 0.;
-  return v_norm * sqrt( v_parm * (1./v_rval - 1./r) + log(v_rval/r) );
+  return v_norm * sqrt( r_g * (1./r_0 - 1./r) + log(r_0/r) );
 }
 
 

### 2010-09-11 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5205 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-%[Kate: Write the details of velocity + density law]
-As discussed in $\S$~\ref{sec:intro}, the importance of various physical mechanisms
-in driving these ubiquitous galactic outflows remains an open
+As discussed in the Introduction, the importance of various physical mechanisms
+in driving galactic outflows remains an open
 question.  Several studies advocate a primarily energy-driven
@@
 In contrast to the fiducial model, the velocity law is nearly
-constant with radius before decreasing sharply as r approaches $R_0$.
+constant with radius before decreasing sharply at large radii.
 To produce a wind whose \mgiia\ optical depth profile peaks at 
-$\tau_{2796}^{\rm max} \gtrsim 10$, we set $R_g = r_{\rm inner} =
-1\,\rm kpc$, $R_0=20\,\rm kpc$, and $\sigma = 125 \mkms$.  The density
-and velocity peak at $r=r_{\rm inner}$ where $n_{\rm H}^0 = 0.07
-\cm{-3}$ and $\mvr = 380 \mkms$.  This corresponds to a mass flow of
-$dM_{\rm wind}/dt = 0.63 \msun\; \rm yr^{-1}$.
+$\tau_{2796}^{\rm max} \gtrsim 10$, we set $R_0 = r_{\rm inner} =
+1\,\rm kpc$, $R_g=4\,\rm kpc$, and $\sigma = 125 \mkms$.  The density
+peaks at $r=r_{\rm inner}$ where $n_{\rm H}^0 = 0.03
+\cm{-3}$.  The velocity, meanwhile, peaks at $r=R_g$ with $\mvr
+\approx 400 \mkms$.  This corresponds to a mass flow of
+$dM_{\rm wind}/dt \approx 0.2 \msun\; \rm yr^{-1}$.
 
@@
 the optical depth peaks at much larger velocity (here $\mdv
-\approx -350 \mkms$).  At these velocities, the absorption is not
+\approx -400 \mkms$).  At these velocities, the absorption is not
 filled-in by scattered photons and one recovers absorption lines
@@
 broader. This reflects the fact that the majority of absorption
-occurs at $\mdv \approx -350 \mkms$.
+occurs at $\mdv \ll 0 \mkms$.
 The kinematics of \feiis\ line-emission, therefore, independently

### 2010-09-16 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5214 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-[Describe 1D and 3D algorithms]
-
-[Put tests in an Appendix?]
+We calculated spectra using a 3D Monte Carlo radiation transport code originally designed for supernova outflows  \cite{Kasen_2006} but  modified to treat resonant line transport  on a galactic scale \cite{Kasen_lyman}.
+Our methods are similar to those used in several other codes \citep[e.g.,][]{Zheng_2002,Dijkstra_2006,Verhame_2006,Laursen_2009}, except that here we include the effects of multiple line scattering and fluorescence.
+
+For our 3-dimensional calculations, the  wind properties (density, temperature and velocity) were descritized on a $300^3$ Cartesian grid (for certain 1-D calculations, the wind properties were simply computed on the fly from analytic formulae).
+The radiation field was represented by $N$ photon packets (typically $N \sim 10^7$) which were initially emitted isotropically and uniformly throughout the source region ($r < r_{\rm source}$).
+The wavelengths of the packets were sampled from a flat spectral energy distribution.
+
+Photon packets were tracked through randomized scattering and absorption events until they escaped the computational domain.
+The distance to the next packet interaction event was determined by Doppler shifting packets to the comoving frame and sampling the mean free path to each resonance line, as well to dust.
+The resonant line opacity followed a Voigt profile which was determined using the analytic fits of  \cite{Tomi_2006}.
+Non-resonant lines were assumed to be completely optically thin, and the dust opacity was assumed to be wavelength independent and completely absorbing (right X?).
+Because of the relatively low optical depths encountered in these models, no ``core-skipping'' scheme was applied to accelerate the resonant line transport,  and recoil effects were ignored.
+
+In a resonant line interaction, a photon excites an atom from the ground state to an excited level.
+The end result is either scattering (i.e., de-excitation back to the ground state) or fluorescence (de-excitation to another excited  level).
+The probability that the atom de-excites to lower level $x$ is  $p_{x} = A_{ux} / \sum_i A_{ui}$, where the $A_{ui}$ are the Einstein spontaneous emission coefficients and the sum runs over all levels accessible from the upper state $u$.
+For each interaction event, a random number was drawn to sample the final state from this probability distribution.
+If the result was a scattering, the process was assumed to be coherent in the comoving frame.
+If the result was fluorescence, the packet was  reemitted at the line center wavelength of the new transition.
+Natural line broadening in fluorescence was ignored given the high velocity gradients in our models.
+In all cases, the angular redistribution was  assumed to be isotropic.
+
+%Spatially averaged spectra of the models were constructed by collecting all packets which escaped in a given (observer-frame) wavelength bin.   
+To generate multi-dimensional images and spectra of the system, an escape probability method was used.
+At the initiation of a packet, and at every subsequent interaction event, we calculated the probability $P_x = e^{-\tau_{ux}} p_{ux}$,  that the packet de-excited into state $x$ and escaped the domain in some pre-specified direction.
+Here
+$\tau_{ux}$ is the optical depth to infinity, which was  constructed  by integration along the path to escape, taking into account the relevant Doppler shifts and possible absorption by lines or dust.
+The contribution of the packet to the final spectrum was than added in for every possible final state, each shifted to the proper observer-frame wavelength and weighted by the probability $P_x$.
+
+To validate the monte carlo code, we calculated a series of test problems consisting of a point source embedded in a spherical, homogenous medium of varying resonant line optical depth.
+The resulting resonant line profiles  \citep[see][]{kasen_lyman} were
+found to be in good agreement with the standard analytic solutions \citep{Harrington_1973,Neufeld_1990,Dijkstra_2006}.
+As a further test, we calculated line profiles for the case of an extended spherical source embedded in a homologously expanding wind with large velocity gradient.
+These model spectra (Figure~\ref{fig:oneline_test}) are in good agreement with ones determined by direct numerical integration of the radiation transport equation under the Sobolev approximation [e.g.,][]\citep{Jeffery_Branch}.
 
@@
 saturated) which only partially covers the emitting source
-\citep[e.g.][]{rvs05a,hammann+10}.  Our fiducial wind model, however, 
+\citep[e.g.][]{rvs05a,hkp+10}.  Our fiducial wind model, however, 
 {\it entirely covers the source}; the apparent partial covering must
@@
 \epsscale{0.8}
+\plotone{../Figures/oneline_test.eps}
+\caption{
+Line profiles of a test problem calculated using the monte carlo code (solid) and by direct numerical integration of the transport equation under the Sobolev approximation (dashed lines).
+The configuration was  spherical and consisted of a homologously expanding wind  with density profile $n \propto r^{-2}$  lying above an opaque emitting surface at velocity coordinate 100~km~s$^{-1}$.
+The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and $\tau = 100$ (blue lines).
+Discrepancies in the $\tau = 100$ case are likely due to the breakdown of the Sobolev approximation at high optical depth.
+}
+\label{fig:oneline_test}
+\end{figure}
+
+\begin{figure}
+\epsscale{0.8}
 \plotone{../Figures/fig_nvtau_vs_r.ps}

### 2010-09-17 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5216 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -33,8 +33,6 @@ double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
-double omnl = 1-n_law;
-double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 

### 2010-09-17 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_mgii.cc

@@ -83,8 +83,9 @@ int main(int argc, char **argv)
   // Dust
   if(argc > 6) {
     dust_tau = atof(argv[1]);
+    double omnl = 1-n_law;
+    double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
     dust_norm   =  dust_tau / dust_cs /  nH_colm / KPARSEC ;
-    return 0;  // Need to deal with nH_colm properly
   }
 
   void Run_Monte_Carlo(char*);

### 2010-09-17 Winds/papers/Theory/First/Analysis/Dust/outflow_dust_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5218 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -32,6 +32,8 @@ double v_law     =    1.0;      // power law of velocity profile
 double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
+double omnl = 1-n_law;
+double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption

### 2010-09-17 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_mgii.cc

@@ -32,8 +32,8 @@ double v_rval = r_inner;
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
-double omnl = 1-n_law;
-double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+//double omnl = 1-n_law;
+//double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 

### 2010-09-17 Winds/papers/Theory/First/Analysis/PowLaws/outflow_plaw_mgii.cc
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5219 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -32,8 +32,6 @@ double v_rval = r_inner;
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
-//double omnl = 1-n_law;
-//double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
 double dust_norm   =  0.;   // Normalization to give dust_tau
 double dust_albedo = 0.0;         // ratio of scattering to absorption
 

### 2010-09-30 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5251 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 J. Xavier Prochaska\altaffilmark{1}, 
-Daniel Kasen\altaffilmark{1,2,3}, 
+Daniel Kasen\altaffilmark{2,3}, 
 Kate Rubin\altaffilmark{1} 
@@
 \altaffiltext{1}{Department of Astronomy and Astrophysics, UCO/Lick Observatory, University of California, 1156 High Street, Santa Cruz, CA 95064}
-\altaffiltext{2}{UCB?}
-\altaffiltext{3}{Hubble Fellow}
+\altaffiltext{2}{Departments of Physics and Astronomy, University of California, Berkeley, 366 LeConte Hall, Berkeley CA, 94720}
+\altaffiltext{3}{Nuclear Science Division, Lawrence Berkeley National Laboratory, 1 Cyclotron Rd, Berkeley, CA, 94720}
 
@@
 Iron exhibits the most complex set of energy levels for elements
-frequently studied in astrophysics.  The Fe$^+$ ion alone has over
-10,000 energy levels recorded \citep{iron}, and even this is an
+frequently studied in astrophysics.  The Fe$^+$ ion alone has 
+millions of energy levels recorded \citep{kurucz_cd1}, and even this is an
 incomplete list.  
@@
 
+A photon propagating through a differentially expanding medium
+interacts with a line only when
+it's comoving frame wavelength is Doppler shifted into near resonance with the line center rest wavelength. 
 For a wind with a steep velocity law  (i.e.\ a large gradient $dv/dr$)
-and/or a narrow intrinsic profile (i.e.\ a small Doppler parameter),
-\citet{sobolev60} introduced a formalism that defines the opacity of
-the wind at a given radius $\tau(r)$ in terms of the density and
-velocity gradient of the flow at that radius;
-
+and/or a narrow intrinsic profile (i.e.\ a small Doppler parameter), the 
+spatial extent of the region of resonance
+may by much smaller than the length scale of the
+wind itself.  The interaction can then 
+be considered to occur at  a point.
+In this case, \citet{sobolev60} introduced a formalism that gives the line optical depth $\tau(r)$ at  
+a given point in terms of the density and
+velocity gradient of the flow at that radius.  For a wind in homologous expansion,
+this optical depth is independent of the direction of propagation and given by
 \begin{equation}
-\tau^S(r) = \kappa^\ell \rho(r) \, \lambda^\ell \ltp \frac{dv}{dr} 
-\rtp^{-1}  \cmma
+\tau^S(r) = K^\ell   \lambda_0^\ell | dv/dr |^{-1} \cmma
 \label{eqn:Sobolev}
 \end{equation}
-where $\kappa^\ell$ is the opacity of transition $\ell$.  This opacity
-applies to a photon with wavelength $\lambda^S
-\equiv \lambda^\ell (1-v(r)/c)$.
-This is, of course, not the true opacity;
-a photon with wavelength $\lambda^S$ that travels through the wind 
-experiences a total opacity 
-$\tau_\nu^\ell = \intl_0^\infty \rho(r) \kappa_\nu^\ell dr$.  The Sobolev
-approximation is valid when the opacity the photon experiences is
-dominated by gas in a localized portion of the flow.
-We find that it applies to nearly all of the
-models presented in this paper and therefore provides a convenient
-approach to estimating $\tau^\ell_\nu$.
+where 
+\begin{equation}
+K^\ell = \frac{\pi e^2}{m_e c} f^\ell n^\ell(r)
+\end{equation}
+is the integrated line opacity, $\lambda_0^\ell$ the rest center wavelength,
+$f^\ell$ the oscillator strength and
+$n^\ell$ the density in the lower level of the transition.   We have
+neglected corrections for stimulated emission.   This optical
+depth applies to a photon with wavelength $\lambda^S
+\equiv \lambda^\ell (1- v(r)~\hat{r}  \cdot \hat{d} /c)$ where $\hat{d}$ is the 
+direction of propagation.  The probability that such a photon
+is scattered/absorbed at the point of resonance is simply $1 - \exp[-\tau^S(r)]$.
+We find that the Sobolev approximation applies for nearly all of the
+models presented in this paper, and therefore provides a convenient
+approach to estimating the optical depth.
 
@@
 \begin{equation}
-n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2} \;\;\; , 
+n_{\rm H} (r) = n^0_{\rm H} \biggl( \frac{r_{\rm inner}}{r}  \biggr)^2\;\;\; , 
 \label{eqn:density}
@@
 \begin{equation}
-\vec v = v_r (r) \hat r = v_0 r \hat r  \perd
+\vec v = v_r (r) \hat r = \frac{v_0 r}{r_{\rm outer}} \hat r  \perd
 \label{eqn:vel}
 \end{equation}
-Turbulent motions are
+For the fiducial case,  the hydrogen density at
+the inner radius is $n_{\rm H}^0 = 0.1~{\rm cm}^{-3}$ and the
+velocity at the outer radius is $v_0 = 1,000$~\kms. Turbulent motions are
 characterized by a Doppler parameter\footnote{
   The adopted Doppler parameter
-  ($\mbturb = 15 \mkms$) has a minor impact on the results.
+ has a minor impact on the results.
   The absorption profiles are insensitive to its value and varying \bturb\
@@
   shift the centroids of emission lines.} 
-, $b_{\rm turb}$.  
+$b_{\rm turb} = 15 \mkms$.  
 We convert the hydrogen density $n_{\rm H}$ to the number densities of
@@
 
-Because the results are dictated by frequency dependence of the
-$\tau_{2796}$ profile, 
-the actual dimensions and density of the wind are
-essentially unimportant provided they scale together to give nearly the same
+%Because the results are dictated by frequency dependence of the
+% $\tau_{2796}$ profile
+%  I don't understand this sentence so I commented it out -- ? -- Dan 
+For the spatial integrated (i.e., 1D) spectra, the actual dimensions and density of the wind are
+unimportant provided they scale together to give nearly the same
 optical depth. Therefore, one may consider the choices for
@@
 symmetric;  the sources driving the
-wind (e.g.\ supernovae, AGN) are very unlikely to be isotropically distributed
+wind (e.g.\ supernovae, AGN) are very unlikely to be spherically distributed
 within the galaxy.  
@@
 Lastly, the galaxy could be surrounded by an
-anisotropic gaseous halo whose interaction would produce an irregular 
+aspherical gaseous halo whose interaction would produce an irregular 
 outflow.
@@
 strengths of the \feiib\ and \feiie\ lines provide a direct
-diagnostic on the degree to which the resonance lines are trapped.
+diagnostic on the degree to which the resonance line photons are trapped.
 [Comment:  this is a product of $\tau_{2600}$ and the velocity
@@
 Both approaches assume an isotropic wind and adopt the velocity law given by
-Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
+Equation~\ref{eqn:LBG_vlaw}.  In the first model, we treat the cool gas as a
 diffuse medium with unit covering fraction and a radial density
@@
 the Monte Carlo methodology used for the other wind models to predict
-\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other LBG model,
+\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the second LBG model,
 we modify our algorithms to more precisely mimic the concept of an
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sobolev approximation}
+\subsubsection{Sobolev Inversion}
 \label{sec:Sobolev}
@@
 for the flowing medium. 
-In our case, the optical depth profile is actually provided by 
-Equation~\ref{eqn:LBG_I},
-
+The Sobolev line optical depth profile can be derived from
+the absorption profile (Equation~\ref{eqn:LBG_I}), 
 \begin{equation}
@@
 \end{equation}
-Therefore, we may invert the Sobolev approximation (Equation~\ref{eqn:Sobolev})
-to derive the radial density profile,
-
+This simple expression assumes that the source size is small compared the wind dimensions
+and neglects the effects of light scattered in the wind (for more general inversion
+formulae that do not make these assumptions, see \citet{Kasen_2002}).
+The Sobolev approximation (Equation~\ref{eqn:Sobolev}) provides a simple expression for the optical
+depth at each radius in terms of the local density and velocity gradient.  In general, the velocity 
+ gradient must be taken along the direction of propagation of a photon, however
+in this model the central source is of relatively small  and the radiation
+field is therefore primarily radially directed.  In this 
+case the velocity gradient in the radial direction, $d\mvr/dr$, is the relevant quantity, and 
+we may use Equation~\ref{eqn:Sobolev}  to invert
+the optical depth and determine the density profile,
 \begin{equation}
-n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa^\ell
-  \lambda^\ell} \cmma
+n_{\rm LBG}(r) =  \tau_{\rm LBG}(r)  \frac{ |d\mvr/dr |}{f^\ell  \lambda_0^\ell}
+\biggl( \frac{ m_e c}{\pi e^2} \biggl)
+ \cmma
 \label{eqn:nSobolev}
 \end{equation}
-with $\lambda^\ell$ the rest wavelength and $\kappa^\ell \equiv f^\ell
-\pi^2 e^2/m_e c$.
 
@@
 
-In the previous sub-section, we described a Sobolev solution that
+In the previous sub-section, we described a Sobolev inversion that
 reproduces the average absorption profile of LBGs in cool gas
@@
 We also argued that the implied mass, energy, and momentum
-distributions of this wind (Figure~\ref{fig:LBG_cumul} were too
+distributions of this wind (Figure~\ref{fig:LBG_cumul}) were too
 extreme. 

### 2010-10-06 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5257 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\ewe}{$W_{\rm e}$}
-\newcommand{\rtt}{$r_{\tau = 0.2}$}
-\newcommand{\mrtt}{r_{\tau = 0.2}}
+\newcommand{\rtt}{$r_{\tau_S = 0.2}$}
+\newcommand{\mrtt}{r_{\tau_S = 0.2}}
 \newcommand{\bturb}{$b_{\rm turb}$}
@@
 
-\title{Idealized Wind Models of Cool Gas Outflows}
+\title{Diagnosing Simple Wind Models of Cool Gas Outflows through
+  Metal-Line Absorption and Emission}
 
@@
 \begin{abstract}
-\begin{itemize}
-\item Emission is a generic feature of (nearly) isotropic winds.  This
-  emission fills in absorption at $v \approx 0$, significantly
-  complicating the absorption-line analysis, especially of an ISM
-  component. 
-\item The relative strengths of the emission
-lines, therefore, is sensitive to both the opacity and velocity
-extent of the wind.
-\item  One must take careful
-consideration of line emission, therefore,  before drawing robust
-conclusions about the presence/absence of gas with small velocity
-offsets from systemic. 
-\end{itemize}
+We analyze the absorption and emission-line profiles produced by a set
+of simple, cool gas wind models motivated by galactic-scale outflow
+observations.  We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
+multiplet at $\lambda \approx 2600$\AA, but the results are applicable
+to most other transitions used to study outflows (e.g.\ \ion{Na}{1},
+\ion{H}{1} \lya, \ion{Si}{2}).   We implement monte carlo radiative
+transfer techniques to properly track the propogation of scattered and
+flourescent photons to [produce] 1D spectra and 2D spectral images.
+[Should we make the codes publically available?  Upon request?]
+[Mention fiducial model here?]
+By design, the \ion{Mg}{2} doublet exhibits strong, blue-shifted
+absorption but also comparably strong line-emission at roughly
+systemic velocity.  This line-emission `fills-in' the absorption at
+velocieties near systemic, significantly reducing the inferred
+opacity. Analysis of cool gas outflows that entirely ignores this
+line-emission may incorrectly conclude that the gas is partially
+covered, has a significantly lower peak optical depth, and/or that a
+gas with velocities near systemic (e.g.\ from the ISM or even
+an infalling component) is absent.   
+The \ion{Fe}{2} resonance lines show similar behaviour, however 
+these lines are connected to fine-structure levels that are optically
+thin to the medium.  As a result, the resonant line-emission is
+reduced (at the `expense' of significant fine-structure emission) and
+the absorption lines more faithfully reproduce the intrinsic opacity
+of the wind.   [Together these results naturally explain the
+absorption and emission-line characteristics observed for star-forming
+galaies at $z<1$.]  
+We examine outflows with a range of power-law density and velocity
+profiles and a radiative-driven wind model.  The resultant \ion{Mg}{2}
+and \ion{Fe}{2} profiles show a diverse complexity of absorption and
+emission characteristics but overall have qualitatively similar
+features.  We also study a scenario purported to describe the outflows
+of $z \sim 3$ Lyman break galaxies and argue this model fails to
+reproduce the observations when (previously ignored0 scattered photons
+are properly considered.   Strong line-emission from metal-line
+transitions is a generic prediction of wind models, even in the
+presence of dust and anisotropic configurations.  We calculate the
+surface brightness profiles of this emission which motivates
+spatially-extended spectroscopic observations with current and
+next-generation integral-field-unit instruments.
+
 \end{abstract}
@@
 toward comparing the observations against (even idealized) wind
-models (although see \citealt{fmm+09}).  
+models \citep[e.g.][]{fmm+09}.  
 Instead, researchers have gleaned what limited information
@@
 This phenomenon was first reported by \citet{phillips93}, who observed 
-blue-shifted absorption and red-shifted emission in the \ion{Na}{1}
+blue-shifted absorption and red-shifted emission for the \ion{Na}{1}
 transition in the spectrum of the local starburst galaxy NGC 1808.
@@
 \ion{Mg}{2} emission, both directly and when the authors modeled and
-`removed' the $v \approx 0\mkms$ absorption component.  Although the
+`removed' the $v \approx 0\mkms$ absorption component.  The
 authors suggested the emission could be related to back-scattered
-light in the wind, they also allowed that it could be related to weak
+light in the wind, but presumed that it was related to weak
 AGN activity.   Very similar \ion{Mg}{2} emission was observed by
@@
 also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
-and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
+and non-resonant \ion{Si}{2}$^*$ transitions\footnote{See also
+  \cite{france10} for a new example at $z \sim 0$.} \citep{prs+02,shapley03}.
 We emphasize that this emission arises from a completely different
@@
 challenge the straightforward conversion of observables to (even crude) physical
-constraints.  We caution that these findings have a direct bearing on
+constraints.  These findings have a direct bearing on
 recent and upcoming surveys of galactic outflows, particularly those
@@
 \subsection{The Radiative Transitions}
-
-[JXP:  This needs to be re-run and revised following Kate's update.
-Will do so in the next few days (hopefully tomorrow)]
 
@@
 frequently studied in astrophysics.  The Fe$^+$ ion alone has 
-millions of energy levels recorded \citep{kurucz_cd1}, and even this is an
+millions of energy levels recorded \citep{kurucz05}, and even this is an
 incomplete list.  
@@
 attribute the emission to chromospheric activity rather than mass-loss effects.
-%{\bf [Kate: Any emission??]}  
 \ion{H}{2} regions, meanwhile, are observed to emit weakly
 at the \mgiid\ doublet, primarily due to recombinations in the outer
-layers \citep{kbc+93} {\bf [Kate: How about FeII?  X: I don't know of any examples of this.]}.  
+layers \citep{kbc+93}.
 It is beyond the scope of this paper to
@@
 should be aware that they can complicate the observed spectrum,
-independent of the outflow, especially at velocities $v \approx 0 \mkms$.
+independently of any outflow, especially at velocities $v \approx 0 \mkms$.
 In the following, we assume a simple flat continuum 
@@
 
-We calculated spectra using a 3D Monte Carlo radiation transport code originally designed for supernova outflows  \cite{Kasen_2006} but  modified to treat resonant line transport  on a galactic scale \cite{Kasen_lyman}.
-Our methods are similar to those used in several other codes \citep[e.g.,][]{Zheng_2002,Dijkstra_2006,Verhame_2006,Laursen_2009}, except that here we include the effects of multiple line scattering and fluorescence.
+We calculated spectra using a 3D Monte Carlo radiation transport code
+originally designed for supernova outflows  \citep{Kasen_2006} but
+modified to treat resonant line transport  on a galactic scale
+\citep{Kasen_lyman}.  Our methods are similar to those used in several
+other codes which focus on \lya\
+\citep[e.g.,][]{Zheng_2002,Dijkstra_2006,Verhame_2006,Laursen_2009},
+except that here we include the effects of multiple line scattering
+and fluorescence.
 
@@
 
-Photon packets were tracked through randomized scattering and absorption events until they escaped the computational domain.
-The distance to the next packet interaction event was determined by Doppler shifting packets to the comoving frame and sampling the mean free path to each resonance line, as well to dust.
-The resonant line opacity followed a Voigt profile which was determined using the analytic fits of  \cite{Tomi_2006}.
-Non-resonant lines were assumed to be completely optically thin, and the dust opacity was assumed to be wavelength independent and completely absorbing (right X?).
-Because of the relatively low optical depths encountered in these models, no ``core-skipping'' scheme was applied to accelerate the resonant line transport,  and recoil effects were ignored.
+Photon packets were tracked through randomized scattering and
+absorption events until they escaped the computational domain.  The
+distance to the next packet interaction event was determined by
+Doppler shifting packets to the comoving frame and sampling the mean
+free path to each resonance line (and dust, if present).  The resonant
+line opacity followed a Voigt profile which was determined using the
+analytic fits of  \cite{Tomi_2006}.      Non-resonant lines were
+assumed to be completely optically thin, and the dust opacity was
+assumed to be wavelength independent and completely absorbing
+($\S$~\ref{sec:dust_method}).
+Because of the relatively low optical depths encountered in
+these models, no ``core-skipping'' scheme was applied to accelerate
+the resonant line transport,  and recoil effects were ignored.
 
@@
 To validate the monte carlo code, we calculated a series of test problems consisting of a point source embedded in a spherical, homogenous medium of varying resonant line optical depth.
-The resulting resonant line profiles  \citep[see][]{kasen_lyman} were
-found to be in good agreement with the standard analytic solutions \citep{Harrington_1973,Neufeld_1990,Dijkstra_2006}.
-As a further test, we calculated line profiles for the case of an extended spherical source embedded in a homologously expanding wind with large velocity gradient.
-These model spectra (Figure~\ref{fig:oneline_test}) are in good agreement with ones determined by direct numerical integration of the radiation transport equation under the Sobolev approximation [e.g.,][]\citep{Jeffery_Branch}.
+The resulting resonant line profiles  \citep[see][]{Kasen_lyman} were
+found to be in good agreement with the standard analytic solutions
+\citep{Harrington_1973,Neufeld_1990,Dijkstra_2006}.  As a further
+test, we calculated line profiles for the case of an extended
+spherical source embedded in a homologously expanding wind with large
+velocity gradient.  These model spectra
+(Figure~\ref{fig:oneline_test}) are in good agreement with ones
+determined by direct numerical integration of the radiation transport
+equation under the Sobolev approximation \citep[e.g.,][]{Jeffery_Branch}.
 
@@
 the ISM of a galaxy.  
-Extraplanar material likely associated with a galactic-scale 
-outflow has been observed to emit IR radiation characteristic of dust 
-\citep[e.g.][]{M87_dust,hrg90,adb99,rkl01}.
 Essentially all astrophysical environments that contain both cool gas
@@
 absorption systems \citep{ykv+06,mnt+08}, and the galactic winds traced
-by low-ion transitions \citep{prs+02,rvs05b}.  Although the galactic winds
-traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
-demonstrated to contain dust, it is reasonable to consider its
-effects.
+by low-ion transitions \citep{prs+02,rvs05b}.  
+Extraplanar material likely associated with a galactic-scale 
+outflow has been observed to emit IR radiation characteristic of dust 
+\citep[e.g.][]{hrg90,adb99,rkl01}.
 In addition, \cite{msf+10} have argued from a statistical analysis
@@
 and have suggested it was transported from the galaxies by
-galactic-scale winds.  One is motivated, therefore, to consider
-models that include the effects of dust extinction.
-
-For analysis on normalized spectra, the effects of dust are largely minimized; 
+galactic-scale winds.  
+Although the galactic winds
+traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
+demonstrated to contain dust, it is reasonable to consider its effects.
+
+For analysis on normalized spectra (i.e.\ absorption lines), the effects of dust are largely minimized; 
 dust has a nearly constant opacity over small spectral regions and all
@@
 approximation given the small spectral range analyzed;
-(iii) the photons absorbed by dust are re-emitted at IR wavelengths
+(iii) dust absorbs but does not scatter photons;
+(iv) the photons absorbed by dust are re-emitted at IR wavelengths
 and are `lost' from the system.  The dust absorption is normalized by \taud, 
@@
 infinity.  The ambient ISM of a star-forming galaxy may be expected to exhibit
-\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{dust_again,cf00}.
+\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{cf00}.
 
@@
 spatial extent of the region of resonance
-may by much smaller than the length scale of the
+may be much smaller than the length scale of the
 wind itself.  The interaction can then 
@@
 velocity gradient of the flow at that radius.  For a wind in homologous expansion,
-this optical depth is independent of the direction of propagation and given by
+this optical depth is independent of the direction of propagation and
+is given by
 \begin{equation}
-\tau^S(r) = K^\ell   \lambda_0^\ell | dv/dr |^{-1} \cmma
+\tau_S(r) = K_\ell   \lambda^0_\ell | dv/dr |^{-1} \cmma
 \label{eqn:Sobolev}
@@
 \begin{equation}
-K^\ell = \frac{\pi e^2}{m_e c} f^\ell n^\ell(r)
+K_\ell = \frac{\pi e^2}{m_e c} f_\ell n_\ell(r)
 \end{equation}
-is the integrated line opacity, $\lambda_0^\ell$ the rest center wavelength,
-$f^\ell$ the oscillator strength and
-$n^\ell$ the density in the lower level of the transition.   We have
+is the integrated line opacity, $\lambda^0_\ell$ the rest center wavelength,
+$f_\ell$ the oscillator strength and
+$n_\ell$ the density in the lower level of the transition.   We have
 neglected corrections for stimulated emission.   This optical
-depth applies to a photon with wavelength $\lambda^S
-\equiv \lambda^\ell (1- v(r)~\hat{r}  \cdot \hat{d} /c)$ where $\hat{d}$ is the 
+depth applies to a photon with wavelength $\lambda_S
+\equiv \lambda_\ell (1- v(r)~\hat{r}  \cdot \hat{d} /c)$ where $\hat{d}$ is the 
 direction of propagation.  The probability that such a photon
-is scattered/absorbed at the point of resonance is simply $1 - \exp[-\tau^S(r)]$.
+is scattered/absorbed at the point of resonance is simply $1 - \exp[-\tau_S(r)]$.
 We find that the Sobolev approximation applies for nearly all of the
@@
 (Equation~\ref{eqn:Sobolev}). 
-
 The $\tau_{2796}$ profile peaks with $\tau_{2796}^{\rm max} \approx 30$
@@
 
-%Because the results are dictated by frequency dependence of the
-% $\tau_{2796}$ profile
-%  I don't understand this sentence so I commented it out -- ? -- Dan 
-For the spatial integrated (i.e., 1D) spectra, the actual dimensions and density of the wind are
+For the spatially integrated (i.e., 1D) spectra, the actual dimensions and density of the wind are
 unimportant provided they scale together to give nearly the same
 optical depth. Therefore, one may consider the choices for
-$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
+$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as largely arbitrary.
 Nevertheless, we adopted values for this fiducial model with
@@
 well above zero intensity and have similar depth even though their $f\lambda$
-values differ by a factor of two.  In standard absorption line
+values differ by a factor of two.  In standard absorption-line
 analysis, this is 
@@
 
-%%% KHRR edited this-- no content change intended, just tried to
-%%% remove repetition
 Turning to the emission profiles of the \mgiid\ doublet, one notes
@@
 line ratio that is far below the $2:1$ ratio that one may have naively
-expected, and leads us to conclude that the relative
+expected (e..g.\ if the line-emission resulted from recombinations),
+and leads us to conclude that the relative 
 strengths of the emission lines is sensitive to both the opacity and
 velocity extent of the wind.
-[Does recombination predict 2:1??  The simple HII region Cloudy model
-produces nearly a 2:1 ratio, though not exactly. (Kate)]
-%The emission profiles are very similar because the gas is optically
-%thick yielding comparable total absorption. 
-%Furthermore, the flux from \mgiib\ actually exceeds the
-%\mgiia\ emission because the wind speed is greater than the velocity separation
-%of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
-%Therefore, the red wing of the
-%\mgiia\ emission profile is partially absorbed by \mgiib\ and
-%re-emitted at lower frequency.  We conclude that the relative
-%strengths of the emission lines is sensitive to both the opacity and
-%velocity extent of the wind.
 
@@
 transitions (Figure~\ref{fig:fiducial_ifu_feii}).
-For transitions to fine-structure levels of the \aconfig, the source
+For transitions to fine-structure levels of the \aconfig\
+configuration, the source
 is unattenuated but there is a significant contribution from photons
@@
 [Add a paragraph on the bi-conical wind once we are confident in the
-results.  This is may be a rather big effect.]
+results.  This may be a rather big effect.]
 
@@
 significant velocity gradients with radius (i.e.\ scenarios where the
-photons scatter one to a few times before exiting).
+photons scatter only one to a few times before exiting).
 For qualitative changes, one requires an extreme level of
@@
 Even $\mtaud = 3$ is larger than typically inferred for the
-star-forming galaxies that drive outflows \citep[e.g.][]{dust}.
+star-forming galaxies that drive outflows \citep[e.g.][]{cf00}.
 For the emission lines,
@@
 anisotropic
-wind described in Section~\ref{sec:anisotropic}. [Is there a
-distinguishing factor, e.g. flux of 2612/2600??]
+wind described in Section~\ref{sec:anisotropic}.
 
@@
 in the much higher strengths ($3-10\times$) of emission from
-transitions to the excited states of \aconfig.   This occurs because:
+transitions to the excited states of the \aconfig\ configuration.   This occurs because:
 (1) there is greater absorption by the \feiid\
@@
 strengths of the \feiib\ and \feiie\ lines provide a direct
-diagnostic on the degree to which the resonance line photons are trapped.
-[Comment:  this is a product of $\tau_{2600}$ and the velocity
-gradient]
+diagnostic on the degree to which the resonance line photons are
+trapped, i.e.\ the peak opitcal depth of \ion{Fe}{2}~2600 and
+the velocity gradient of the wind.
 
@@
 systemic, the two profiles are nearly identical.
+We conclude that a dusty ISM model could show significant absorption
+at $\delta v \approx 0 \mkms$ in resonance lines (including
+\ion{Mg}{2}) with strong line-emission in the \feiis\
+transitions.
 
@@
 damped \lya\ systems \citep{nbf98,schaye01a}, and the formation of
-`red and dead' galaxies \citep[e.g.][]{redgal}.  Although the
+`red and dead' galaxies \citep[e.g.][]{spf01}.  Although the
 presence of these outflows were established over a decade ago,
@@
  gradient must be taken along the direction of propagation of a photon, however
-in this model the central source is of relatively small  and the radiation
+in this model the central source is relatively small  and the radiation
 field is therefore primarily radially directed.  In this 
@@
 \begin{equation}
-n_{\rm LBG}(r) =  \tau_{\rm LBG}(r)  \frac{ |d\mvr/dr |}{f^\ell  \lambda_0^\ell}
+n_{\rm LBG}(r) =  \tau_{\rm LBG}(r)  \frac{ |d\mvr/dr |}{f_\ell  \lambda^0_\ell}
 \biggl( \frac{ m_e c}{\pi e^2} \biggl)
@@
 reproduces the proper
-absorption profile by discretizing a wind into a series of layers
+absorption profile by discretizing the wind into a series of layers
 and calculating the integrated absorption profile.  This
@@
 This LBG-Sobolev model, however, is not precisely
-the one proposed by S10;  those authors proposed an ensemble of optically
+the one introduced by S10;  those authors proposed an ensemble of optically
 thick clouds with a partial covering fraction described by
@@
 achieve a significant opacity at $\mdv \approx 0 \mkms$, one must
-either suppress the line-emission (e.g.\ with severe dust extinction) 
+either suppress the line-emission (e.g.\ with severe dust extinction
+or anisotropic winds) 
 or include a substantial ISM component that absorbs light at $\mdv
@@
 we conclude that the LBG model
-introduced by S10 is not a valid description of the data.
+introduced by S10 is not a valid description of the data.  Also,
+similar to our LBG-Sobolev calculation (Figure~\ref{fig:LBG_Sobolev}),
+this clump predicts the majority of mass, energy, and momentum are
+carried in the outer 
+In fact, for clumps that are optical thick to strong metal-line
+transitions (e.g.\ \ion{Si}{2}~1526) we estimate that the wind would
+carry nearly a total mass of $\approx 10^{10} \msun$!  We question
+whether this is a plausible result from star-formation driven
+feedback.
 
@@
 question.  Several studies advocate a primarily energy-driven
-wind scenario, in which the hot wind produced by the thermalized
+wind scenario, in which the hot wind is produced by the thermalized
 energy from SNe ejecta entrains cool clouds via ram pressure \citep[e.g.][]{cc85,ham90,sh09}.
@@
 advantage that it does not destroy cool gas clouds as it acts.  Here
-we explore the line profiles produced by a radiation-pressure driven
+we explore the line-profiles produced by a radiation-pressure driven
 wind model as described by \cite{mqt05}.
@@
 diagnoses the intrinsic optical depth profile of the flow.
+We conclude that the radiative-driven model has characteristics that
+are qualitatively similar to the fiducial model (e.g.\ strong
+blue-shifted absorption and significant line-emission) with a few
+quantitative differences that, in principle, could distinguish them
+with high fidelity observations.
 
@@
 $\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b). 
+This choice of normalization was observationally driven to yield
+significant absorption lines.
 All models assume a Doppler parameter
@@
 transition.  This is primarily because these models have 
-higher intrinsic optical depths (e.g.\ higher $n_{\rm Fe^+}$ values).
-
+higher intrinsic optical depths (i.e.\ higher $n_{\rm Fe^+}$ values).
+
+While there is commonality amongst between models, the specific
+characteristics of the absorption/emission profiles do exhibit
+significant diversity.
 Table~\ref{tab:plaw_diag} compares measures of the absorption and
 emission profiles against the fiducial model.
-In detail, the line profiles do differ in their peak optical depths,
+In detail, the line profiles differ in their peak optical depths,
 the velocity centroids of absorption, and the total equivalent widths.
@@
 the velocity laws, i.e.\ the kinematics of the outflow.
-[Last point]
-
-[Comment that decreasing opacity can be produced by $v \propto
-r^{-1}$]
+At the same time, models with very different density/velocity laws can
+produce rather similar results.  For example, profiles that have declining
+opacity with increasing velocity offset from systemic can be obtained
+with a radial velocity law that increases (e.g.\ the fiducial model)
+or decreases (model~D).  The implication is that absorption profiles
+alone are likely insufficient to fully characterize the physical
+characteristics of the outflow.
 
@@
 it generally has only a modest effect on the predicted \ion{Mg}{2}
-emission and always a minor effect on \feiis\ emission.
+emission and a minor effect on \feiis\ emission.
 
 Another factor that may reduce line-emission is a
-non-isotropic (e.g.\ biconical) wind model. The flux is lower, for example, if one
+non-isotropic wind model. The flux is lower, for example, if one
 eliminates the backside to the wind (e.g.\ the source itself could
@@
 reduction of order unity.
+{\bf [Put comments on biconical here]}
 
@@
 effects may help to explain the absence of significant line-emission,
-but we suspect these would generally
-not be sufficient to reduce it below the detection limit.
+but these would generally
+not be sufficient to preclude the detection.
 
@@
 Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
-less than half the full wind.  The result is reduced line-emission,
+less than half the full wind.  The result is reduced line-emission
 when compared to the galaxy continuum.
@@
 through slits with a range of widths, parameterized by \rtt: twice the radius
-where the wind has a Sobolev optical depth of $\tau^S = 0.2$. 
+where the wind has a Sobolev optical depth of $\tau_S = 0.2$. 
 The line-emission will be weak beyond
@@
 consequence of geometric projection.
-The results are comparable for other wind models considered
-in this paper. 
+Figure~\ref{fig:obs_slit} reveals similar results for other wind
+models.
 All of the curves rise steeply enough that 
@@
 
-Another (related) consequence is the reduction of peak depth of the
+Another (related) consequence is the reduction of the peak depth of 
 absorption.
@@
 results are similar for the \mgiib\ profile.  In fact, one generally
-measures similar $\tau_{\rm pk}$ for the two \ion{Mg}{2} lines and would 
+measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and would 
 falsely conclude that the source is partially covered. 
@@
 (a Gaussian with FWHM=250\kms) and an assumed signal-to-noise of
-S/N=7 per (1 \AA) pixel.  Both the absorption
+S/N=7 per 1 \AA\ pixel.  Both the absorption
 and emission are well detected, but it would be
@@
 spectra to study outflows
-\citep[e.g.][; S10]{wcp+09,rwk+10}.   The main difference from the
+\citep[e.g.][S10]{wcp+09,rwk+10}.   The main difference from the
 single galaxy observation shown in panel (a) is the smearing of
@@
 
-[Should galaxies with strong \lya\ emission be expected to show
-low-ion emission? Perhaps not if \lya\ is produced by ionizing photons
-from SF regions.]
+%[Should galaxies with strong \lya\ emission be expected to show
+%low-ion emission? Perhaps not if \lya\ is produced by ionizing photons
+%from SF regions.]
 
@@
 optical depth exceeds a few tenths.  The principle
-challenge is to achieve sufficient sensitivity to detect low
+challenge is to achieve sufficient sensitivity to detect the predicted
+low
 surface brightness emission. As Figure~\ref{fig:obs_sb}
@@
 large format IFU or narrow band imager) may detect the emission in
-azimuthally averaged apertures. {\bf [JXP: Give estimate]}
+azimuthally averaged apertures. 
+For the fiducial wind model, for example, the azimuthally integrated
+flux falls by only a factor of 10 from $r = 1$ to 15\,kpc.
 Of the transitions considered in this paper, \ion{Mg}{2} emission is
@@
 the effects of dust extinction and for some galaxies \feiis\ emission
-will be dominant.  [Last comment]
-
-The kinematics of the line-emission also offer insight into physical
+could be dominant.  In either case, the study of spatially-extended
+line-emission from photons scattred by the galactic-scale wind offers
+an direct means to study the morphology and radial extent of these
+phenomena.  The next generaly of large-format optical and infrared
+integral-field-units are well suited to this scientific endeavor
+(e.g.\ KCWI on Keck, MUSE on the VLT).
+
+The kinematic characteristics of the line-emission also offer insight into physical
 characteristics of the wind.
@@
 preferentially suppresses photons scattered off the backside of the
-wind (e.g.\ with $\mdv > 0 \mkms$) so that the centroid is shifted to
+wind (e.g.\ $\mdv > 0 \mkms$) so that the line-centroid is shifted to
 negative velocities.  Similarly, anisotropic models with reduced
 emission off the backside yield emission lines that are centered
-blueward of the galaxy's systemic redshift.  These effects are mos
+blueward of the galaxy's systemic redshift.  These effects are most
 prominent in the \feiis\ emission.  The centroids of the \ion{Mg}{2}
@@
 Therefore, the line centroids are sensitive to the optical depth
-profile of the wind.
-
-We also find that the emission-line widths trace specific
-characteristics of the wind.  For the \feiis\ emission, the widths are
-most sensitive to the optical depth at large velocities from
+profile of the wind.  Although these effects are modest (tens of
+\kms), they can be [recorded] by modern resolution spectroscopy.
+
+We also find that the emission-line widths reveal
+characteristics of the wind.  In particular, the \feiis\ emission-line 
+widths are
+sensitive to the optical depth of the wind at large velocities from
 systemic.  This is illustrated in Figure~\ref{fig:obs_edelv} which plots
@@
 \feiis\ emission requires a wind profile with large optical depths at
-$\mdv < 200 \mkms$.
-
-Lastly, the line ratios of paris of transitions (e.g.\ \mgiia/\mgiib,
-\feiic/\feiid) are sensitive to several characteristics of the wind.
-These include dust extinction, the relative abundances of Mg/Fe, and
-...
-
-[Relative strengths of MgII 2796 and 2803 speak to $\tau$ and
-$v_r^{max}$]
-
-[Discuss why there can be cases with $v_\tau \sim 0$ and high
-$\tau_{pk}$, if I can figure it out!]
-
-%%%%%%%%%%%%%%%%%
-
-3)  Emission can be used for good!   This is largely an extension of
-your emission paper, of course.
-
-%   (i)  Morphology [MgII is likely best]
-%  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
- (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
+$\mdv < -200 \mkms$.  The broadening of \feiis\ emission occurs
+because this emission is dominated by single scatterings 
+which trace all components of the wind.  {\bf [Also the optical depth profile of
+  FeII]}
+
+Lastly, the line flux ratios of pairs of transitions 
+are sensitive to characteristics of the wind.
+The most obvious example is the relative emisison of the \mgiid\
+doublet.  Specifically, an outflow whose velocity exceeds the doublet
+spacing ($\Delta v \approx 770 \mkms$) will convert \mgiia\ photons
+into \mgiib\ emission resulting in a flux ratio that is inverted
+relative to the intrinsic optical depth profiles (e.g.\
+Figure~\ref{fig:norm}).  Another important example is the relative
+flux of \feiis\ emission relative to \ion{Mg}{2}.  
+A dusty medium with velocity near systemic (e.g.\ an
+ISM component) may significantly suppress \ion{Mg}{2} emission yet
+have a significant \feiis\ line flux because the latter is not
+resonantly trapped.  [One last example?]
 
@@
 
+In this paper, we have explored the predicted absorption and
+emission-line profiles of a set of simple galactic-scale outflow
+models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
+multiple of rest-frame UV transitions, but the results translate to
+most other lines thus far used to probe these phenomna.  Our primary
+findings are summarized as follows:
+
 \begin{enumerate}
-\item Line-profiles can be explained by both increasing and decreasing
-velocity laws.
-
-\item We conclude that resonance transitions that are strongly coupled to
-non-resonant lines offer the best
-characterization of an ISM component.
+
+\item Isotropic, dust-free wind models conserve photon flux.
+  Therefore, the blue-shifted absorption-line profiles commonly
+  observed in star-forming galaxies are predicted to be accompanied by
+  emission-lines with similar equivalent width.
+
+\item The line-emission occurs preferentially at the systemic velocity
+  of the galaxy and `fills-in' the absorption profiles at velocity
+  offsets $|\mdv| < 200 \mkms$ from systemic.  For transitions that
+  are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
+  \ion{Na}{1}), one predicts this emission to significantly fill-in
+  the absorption near systemic.
+
+\item Analysis of cool gas outflows that entirely ignores this
+line-emission may incorrectly conclude that the gas is partially
+covered, has a significantly lower peak optical depth, and/or that a
+gas with velocities near systemic (e.g.\ from the ISM or even
+an infalling component) is absent.
+
+\item Resonance transitions that are strongly coupled to
+non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) offer the best
+characterization of the opacity of the wind and also any component
+with velocity near systemic.  The emission will be domianted by the
+optically-thin, fine-structure transitions.
+
+\item  Dust extinction has only modest effects on the profiles
+  in models where one to only a few scatterings are predicted.  Models
+  with high opacity at small radii and at systemic velocity (e.g.\ an
+  optically thick, ISM component)  can effecitvely extinguish
+  resonantly trapped emission (\ion{Mg}{2}) but have more modest
+  effect on non-resonant lines (\feiis).
+
+\item We examined two scenarios designed to mimic the wind model
+  proposed by S10 for $z \sim 3$ Lyman break galaxies.  These models
+  predict substantial line-emission from scattered photons that
+  greatly modify the predicted line-profiles.  As such, 
+  these models do not reproduce the observed line-profiles.
+
+\item In fact, the
+\feiia\ profile very nearly matches the profile without re-emission 
+(compare to the dotted lines); this transition provides a
+very good description of the intrinsic ISM+wind optical depth profile.  
+We conclude that resonant transitions that are coupled to (multiple)
+non-resonant, electric dipole transitions offer the best
+diagnosis of ISM absorption.
+
+\item The kinematics and flux ratios of the emission lines 
+  constrain the wind speed, opacity, dust extinction, and XXX of the
+  wind.
+
+\item Biconical?
+
+\item Significant line-emission is a generic prediction of simple wind
+  models, even in the presence of dust, anisotropic flows, and when
+  viewed through finite apertures.  We have explored the 2D emission
+  maps (Figure~\ref{fig:ifu}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
+  the winds.  Sensitive, spatially-extended observations will map the
+  morphology and radial extent of the outflows.  These data afford the
+  best opportunity to estimate the energetics and mass-flux of
+  galactic-scale outflows.
+
 \end{enumerate}
@@
 
-We acknowledge valuable conversations with D. Koo, J. Hennawi, 
+We acknowledge valuable conversations with D. Koo, J. Hennawi, and ... 
 J.X.P and K.R. are partially supported

### 2010-10-11 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5263 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\title{Diagnosing Simple Wind Models of Cool Gas Outflows through
+\title{Diagnosing Simple Wind Models of Cool Gas Outflows as Viewed by
   Metal-Line Absorption and Emission}
@@
 of simple, cool gas wind models motivated by galactic-scale outflow
-observations.  We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
+observations.  
+We examine outflows with a range of power-law density and velocity
+profiles and a radiative-driven wind model.  
+We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
 multiplet at $\lambda \approx 2600$\AA, but the results are applicable
-to most other transitions used to study outflows (e.g.\ \ion{Na}{1},
+to other transitions that trace outflows (e.g.\ \ion{Na}{1},
 \ion{H}{1} \lya, \ion{Si}{2}).   We implement monte carlo radiative
-transfer techniques to properly track the propogation of scattered and
-flourescent photons to [produce] 1D spectra and 2D spectral images.
+transfer techniques that track the propogation of scattered and
+flourescent photons to generate 1D spectra and 2D spectral images.
 [Should we make the codes publically available?  Upon request?]
 [Mention fiducial model here?]
-By design, the \ion{Mg}{2} doublet exhibits strong, blue-shifted
-absorption but also comparably strong line-emission at roughly
-systemic velocity.  This line-emission `fills-in' the absorption at
-velocieties near systemic, significantly reducing the inferred
-opacity. Analysis of cool gas outflows that entirely ignores this
-line-emission may incorrectly conclude that the gas is partially
-covered, has a significantly lower peak optical depth, and/or that a
-gas with velocities near systemic (e.g.\ from the ISM or even
-an infalling component) is absent.   
+As expected, the \ion{Mg}{2} doublet exhibits strong, blue-shifted
+absorption but one also predicts strong line-emission at roughly
+the systemic velocity.  This line-emission `fills-in' the absorption, 
+significantly reducing the effective
+opacity near systemic. Analysis of cool gas outflows that entirely ignores this
+line-emission may incorrectly infer that the gas is partially
+covered, measure a significantly lower peak optical depth, and/or
+conclude that gas at systemic velocity is absent   
+(e.g.\ an ISM or slowly infalling component). 
 The \ion{Fe}{2} resonance lines show similar behaviour, however 
-these lines are connected to fine-structure levels that are optically
-thin to the medium.  As a result, the resonant line-emission is
-reduced (at the `expense' of significant fine-structure emission) and
-the absorption lines more faithfully reproduce the intrinsic opacity
-of the wind.   [Together these results naturally explain the
+these lines are connected to optically thin transitions to
+fine-structure levels. As such, the \ion{Fe}{2} 
+absorption lines more faithfully reproduce the intrinsic opacity
+of the wind.   Together these results naturally explain the
 absorption and emission-line characteristics observed for star-forming
-galaies at $z<1$.]  
-We examine outflows with a range of power-law density and velocity
-profiles and a radiative-driven wind model.  The resultant \ion{Mg}{2}
-and \ion{Fe}{2} profiles show a diverse complexity of absorption and
-emission characteristics but overall have qualitatively similar
-features.  We also study a scenario purported to describe the outflows
+galaies at $z<1$.
+We also study a scenario purported to describe the outflows
 of $z \sim 3$ Lyman break galaxies and argue this model fails to
-reproduce the observations when (previously ignored0 scattered photons
-are properly considered.   Strong line-emission from metal-line
-transitions is a generic prediction of wind models, even in the
-presence of dust and anisotropic configurations.  We calculate the
-surface brightness profiles of this emission which motivates
-spatially-extended spectroscopic observations with current and
-next-generation integral-field-unit instruments.
+reproduce the observations when (previously ignored) scattered photons
+are properly considered.   
+%Strong line-emission from metal-line
+%transitions is a generic prediction of wind models, even in the
+%presence of dust and anisotropic configurations.  
+The surface brightness profiles of emission from metal-line
+transitions offers a unique means of assessing the morphology and size
+of galactic-scale winds motivating deep,
+spatially-extended spectroscopic observations.
 
@@
 galaxies.  Indeed, line-emission should be generated by all 
-galaxies driving a wind.
+galaxies driving a cool gas outflow.
 
@@
 reassess several of the effects that can reduce the line-emission
-and consider whether these prevent its detection for many
+and consider whether these prevent its detection in many
 star-forming galaxies.
@@
 fiducial wind model.
-As we have discussed, in scenarios where the \ion{Mg}{2} photons are
-more effectively trapped dust further suppresses
+In scenarios where the \ion{Mg}{2} photons are
+more effectively trapped, dust does suppress
 the emission (e.g.\ the ISM+wind model from $\S$~\ref{sec:ISM}).
@@
 it generally has only a modest effect on the predicted \ion{Mg}{2}
-emission and a minor effect on \feiis\ emission.
+emission and a relatively minor effect on \feiis\ emission.
 
@@
 sightline arise nearly normal to the sightline such that a biconicial
-wind has significantly lower line emission
+wind has significantly lower line-emission
 ($\S$~\ref{sec:anisotropic}). 
@@
 by one to a few factors of order unity.  For some galaxies, these
-effects may help to explain the absence of significant line-emission,
+effects may explain the absence of significant line-emission,
 but these would generally
-not be sufficient to preclude the detection.
+not be sufficient to preclude detection.
 
@@
 a non-zero surface brightness predicted at large radii. This implies 
-a non-negligible luminosity emitted well beyond the galaxy.  
+a non-negligible luminosity emitted beyond the angular extent of the galaxy.  
 The majority of observations of star-forming galaxies to date have
 been taken through a spectroscopic slit designed to cover
-the brightest continuum regions of the galaxy. Slits with angular
+the brightest continuum regions. Slits with angular
 extents of $1-1.5''$ subtend roughly $8-15$\,kpc for galaxies at $z>0.5$.
 Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
-less than half the full wind.  The result is reduced line-emission
+less than half the wind.  The result is reduced line-emission
 when compared to the galaxy continuum.
@@
 wind model (black curves).
-[Add radiative model]
+{\bf [Add radiative model]}
 The \ewe/\ewabs\ curves rise very steeply with increasing slit width and then
@@
 Figure~\ref{fig:obs_slit} reveals similar results for other wind
-models.
-All of the curves rise steeply enough that 
+models. The curves rise so steeply that 
 the effects of slit-loss are minor (order unity)
@@
 extended aperture observations, e.g.\ integral field unit (IFU)
-instrumentation that would map the wind both spatially and spectrally.
+instrumentation, that would map the wind both spatially and spectrally.
 
@@
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
-which has the most affected transitions, \ewabs\ is reduced by
+which has the most effected transitions, \ewabs\ is reduced by
 $30-50\%$ from the intrinsic equivalent width.  In turn, one may derive 
@@
 This affects the analysis of gas related to the ISM of the galaxy and
-also material infalling at a modest speed.  
+also material infalling at modest speeds.  
 Figure~\ref{fig:obs_vtau} also emphasizes that
@@
 
-The most obvious measures provided by line-emission analysis are
+The most obvious measures provided by the line-emission are
 estimates
@@
 For the fiducial wind model, for example, the azimuthally integrated
-flux falls by only a factor of 10 from $r = 1$ to 15\,kpc.
+flux falls by only a factor of 10 for projected radii of 1 to 15\,kpc.
 Of the transitions considered in this paper, \ion{Mg}{2} emission is
@@
 an direct means to study the morphology and radial extent of these
-phenomena.  The next generaly of large-format optical and infrared
-integral-field-units are well suited to this scientific endeavor
+phenomena.  The next generation of large-format optical and infrared
+integral-field-units are well-suited to this scientific endeavor
 (e.g.\ KCWI on Keck, MUSE on the VLT).
@@
 prominent in the \feiis\ emission.  The centroids of the \ion{Mg}{2}
-lines, meanwhile, may be modified by absorption, e.g.\ a wind with
-speeds exceeding 600\kms\ will have \mgiib\ scatter \mgiia\ photons.
-Therefore, the line centroids are sensitive to the optical depth
-profile of the wind.  Although these effects are modest (tens of
-\kms), they can be [recorded] by modern resolution spectroscopy.
-
-We also find that the emission-line widths reveal
+lines, meanwhile, are sensitive to the optical depth
+profile of the wind.   For example, a wind with flows exceeding
+$\approx 600 \mkms$ will shift the \mgiia\ centroid to bluer
+wavelengths (e.g.\ Figure~\ref{fig:norm}).
+Although these effects are modest (tens of
+\kms), they may be resolved by moderate resolution spectroscopy.
+
+The emission-line velocity widths also reveal
 characteristics of the wind.  In particular, the \feiis\ emission-line 
@@
 the 90\%\ velocity width $\Delta v_e$ of \feiic\ versus the velocity
-where the wind optical depth is maximal ($v_\tau$).  It is evident
-that $\Delta v_e$ increases with $v_\tau$; a large measured width for
+where the wind optical depth is maximal ($v_\tau$).  We find that
+$\Delta v_e$ increases with $v_\tau$ such that a large width for
 \feiis\ emission requires a wind profile with large optical depths at
@@
 have a significant \feiis\ line flux because the latter is not
-resonantly trapped.  [One last example?]
+resonantly trapped.
 
@@
 multiple of rest-frame UV transitions, but the results translate to
-most other lines thus far used to probe these phenomna.  Our primary
+most other transitions used to probe cool gas.  Our primary
 findings are summarized as follows:
@@
   observed in star-forming galaxies are predicted to be accompanied by
-  emission-lines with similar equivalent width.
+  emission-lines with similar equivalent width.  This is even true for
+  anisotropic and dust-extincted scenarios.
 
@@
   are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
-  \ion{Na}{1}), one predicts this emission to significantly fill-in
-  the absorption near systemic.
+  \ion{Na}{1}). The observed absorption profiles may be significantly
+  different from the intrinsic optical depth profile.
 
@@
 non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) offer the best
-characterization of the opacity of the wind and also any component
-with velocity near systemic.  The emission will be domianted by the
+characterization of the opacity of the wind and also material 
+with velocities near systemic.  The emission will generally be dominated by the
 optically-thin, fine-structure transitions.
 
-\item  Dust extinction has only modest effects on the profiles
-  in models where one to only a few scatterings are predicted.  Models
+\item  Dust extinction has only modest effects 
+  in models which predict only a few scatterings.  Models
   with high opacity at small radii and at systemic velocity (e.g.\ an
-  optically thick, ISM component)  can effecitvely extinguish
+  optically thick, ISM component)  can effectively extinguish
   resonantly trapped emission (\ion{Mg}{2}) but have more modest
@@
   predict substantial line-emission from scattered photons that
-  greatly modify the predicted line-profiles.  As such, 
-  these models do not reproduce the observed line-profiles.
-
-\item In fact, the
-\feiia\ profile very nearly matches the profile without re-emission 
-(compare to the dotted lines); this transition provides a
-very good description of the intrinsic ISM+wind optical depth profile.  
-We conclude that resonant transitions that are coupled to (multiple)
-non-resonant, electric dipole transitions offer the best
-diagnosis of ISM absorption.
+  greatly modify the predicted line-profiles.  
+  These models do not reproduce the observed line-profiles.
+
+%\item In fact, the
+%\feiia\ profile very nearly matches the profile without re-emission 
+%(compare to the dotted lines); this transition provides a
+%very good description of the intrinsic ISM+wind optical depth profile.  
+%We conclude that resonant transitions that are coupled to (multiple)
+%non-resonant, electric dipole transitions offer the best
+%diagnosis of ISM absorption.
 

### 2010-10-11 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5267 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\title{Diagnosing Simple Wind Models of Cool Gas Outflows as Viewed by
+\title{Simple Wind Models of Cool Gas Outflows as Viewed by
   Metal-Line Absorption and Emission}
@@
 
-[Add a paragraph on the bi-conical wind once we are confident in the
-results.  This may be a rather big effect.]
-
-[Consider showing a 2D model for biconical]
+We have also analyzed the predicted profiles for a series of biconical
+winds with $\theta = 10-60^\circ$, each viewed along the axis of
+asymmetry with the wind covering the source.
+Table~\ref{tab:line_diag} summarizes the results for two cases.  For
+modest opening angles $\theta < 20^\circ$, the results are
+qualitatively similar to the fiducial model;  the profiles show
+similar equivalent widths for absorption and emission.  The key
+quantitative difference is that the \feiis\ line-emission is
+suppressed at $\delta v \approx 0 \mkms$ because the portion of the
+wind with that projected velocity has been removed.  For
+$\theta>45^\circ$, enough of the wind has been removed that the
+line-emission is several times weaker than the fiducial model.
+Similarly, the absorption-line profiles more closely track the
+intrinsic optical depth of the outflow.   Of course, these same models
+when viewed `sideways' would show no absorption yet significant
+line-emission.  Such events are sufficiently rare (Rubin et
+al., in prep) that we consider this level of anisotropy to be of minor
+importance.
 
@@
   viewed through finite apertures.  We have explored the 2D emission
-  maps (Figure~\ref{fig:ifu}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
+  maps (Figure~\ref{fig:fiducial_ifu_mgii}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
   the winds.  Sensitive, spatially-extended observations will map the
@@
 and then converting to radius with the velocity law.  These give
-very similar results. One notes that
-the wind is optically thick at the inner radius ($r_{\rm inner} =
-1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
-  outer} = 20$\,kpc).
+very similar results. 
+The wind parameters were set to give an optically thick medium at the
+inner radius ($r_{\rm inner} = 1$\,kpc) that becomes optically thin at
+the outer radius ($r_{\rm outer} = 20$\,kpc). 
 }
@@
 re-emission occurs.   The true profiles have been `filled-in' 
-significantly by light scattered in the wind.  Ignoring this
+significantly with photons scattered by the wind into our sightline.  Ignoring this
 process, one would model the absorption lines with a systematically lower
@@
 wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  Impressively, this
+entirely due to photons scattered by the wind.  Amazingly, this
 emission exceeds the integrated flux at $v = -250\mkms$ such that the
@@
 the wind also make a significant contribution. 
-[Is this figure superfluous??]
 }
@@
 uncovered) to $\phi = 180^\circ$ (source covered).  One detects
-significant emission for all orientations of this wind but significant
+significant emission for all orientations but significant
 absorption only for $\phi \ge 90^\circ$.
@@
 emission shifts from positive to negative velocities as $\phi$
-increases and one transitions from viewing the wind to be behind the
-source to in front.  The velocity centroid of emission, therefore, may
-give a robust measure of wind isotropy.
+increases and one transitions from viewing the wind as lying behind the
+source to in front of it.  The velocity centroid of emission, therefore,
+diagnoses the degree of anisotropy for the wind.
 }
@@
 model (black) against a series of models that include 
-dust extinction.  The primary effect is suppression of
+dust extinction, parameterize by the integrated dust opacity from
+source to infinity (\taud).  The primary effect of dust is to suppress 
 the line-emission relative to the continuum. 
 A more subtle but important effect is that the redder photons in the
-emission lines (corresponding to higher velocity relative to
-line-center) suffer greater extinction.  This is most evident in the
-\feiic\ emission line; it occurs because these photons must
-travel farther to scatter off the backside of the wind.  Note that
+emission lines (corresponding to positive velocity offsets relative to
+line-center) suffer greater extinction.  
+This occurs because the `redder' photons that we view have travelled 
+farther to scatter off the backside of the wind.  Note that
 the absorption lines are nearly unmodified until $\mtaud = 10$, a
@@
 \caption{
-Predicted line-emission equivalent widths for \mgiib\ from the
+Predicted equivalent widths for \mgiib\ line-emission from the
 fiducial wind model, as attenuated by dust with a range of \taud\
@@
 the continuum) do not scale as $\exp(\tau_d)$.
-The black (solid) curve shows the model predictions while the
+The black (solid) curve shows the model results while the
 dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
 \cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
-representation of the radiative transfer results.   
+representation of the results for our radiative transfer calculations.   
 }
@@
 reduced, implying much higher fluxes for the non-resonant lines (e.g.\
-\feiic,2626).  The lack of scattered \feiia\ photons results in an
-absorption profile that very nearly matches the input opacity profile.
-We conclude that resonance transitions that are strongly coupled to
-non-resonant lines offer the best
-characterization of an ISM component.
+\feiic,2626).  
+Lastly, we note that the \feiia\ absorption profile provides a good
+(albeit imperfect) representation of the wind opacity and therefore
+offers the best characterization of an ISM component.
 }
@@
 varying normalization, parameterized by \nhn.  As expected, the
-strength of absorption increases with increasing \nhn\ which also
+strength of absorption increases with increasing \nhn; this also
 results in stronger line-emission.  Note that the \feiia\ emission is
-always weak; only its absorption increases with \nhn\ and actually exceeds
+always weak. Only its absorption increases with \nhn\ and actually exceeds
 the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
@@
 \caption{
-(a) The dotted curve shows the velocity law (values are labeled on the
-right side) for the LBG model
-of S10.  Note how rapidly the velocity rises from $r =
+(a) The dotted curve shows the velocity law (labeled on the
+right axis) for the LBG model
+of S10 plotted against $(r/{\rm kpc} -1)$ to highlight the evolution
+in the quantities at small radii.  For example,  note how rapidly the velocity rises from $r =
 1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
@@
 the average absorption profile of LBG galaxies (see below).
-The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
+The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
 steepens to $(r/{\rm kpc}-1)^{-1.8}$.
@@
 and (black) a model constructed to faithfully
-correspond to the wind model advocated by S10.  The dotted line
+represent the wind model advocated by S10.  The dotted line
 shows the absorption profiles of the latter model if one were
@@
 and \feiib)
-and produce significant emission lines.  
+and produce strong emission lines.  
 The result, for \ion{Mg}{2} especially, is a set of profiles that do
@@
 majority of mass, energy, and momentum in the wind are contained at
-large radii.
+large radii.  We derive similar results for the LBG-partial covering model
+if we assume the wind is composed of identical clouds optically thick
+to strong metal-line transitions (e.g.\ \ion{Si}{2}~1526).  The
+energy and momemtum in the outer regions of the outflow may be very
+difficult to generate with standard galactic-scale wind scenarios.
 }
@@
 fiducial wind model (black).  In contrast to the fiducial model, the
-velocity of the radiation-driven model decreases with increasing
-radius such that the optical depth peaks at large velocity (here $\mdv
+optical depth peaks at large velocity (here $\mdv
 \approx -350 \mkms$).  At these velocities, the absorption is not
@@
 The \feiis\ emission also has a similar
-equivalent width, yet the lines are much broader for the
+equivalent width, yet the lines are much broader in the
 radiative-driven model. 
@@
 \propto r^{-2}$) and velocity laws (colored; green -- $v \propto
-r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$).  For
+r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$) for a
+series of power-law models (Table~\ref{tab:plaw_parm}).  For
 comparison we also plot the velocity and density laws for the fiducial
-model (thin, black curves).  See Table~\ref{tab:plaw_parm} for further
-details.
+model (thin, black curves).  
 Panel (b) plots the optical depth profiles of the \mgiia\ line for
-the nine models build from the density and velocity laws of panel (a).
+the nine models built from the density and velocity laws of panel (a).
+Each of these were normalised to have peak optical depths of 10 to
+1000 and to be optically thin at small or large velocity.
 }
@@
 \caption{
-Emission equivalent width ($W_{\rm e}$) relative to the observed
+Absolute emission equivalent width ($|W_{\rm e}|$) relative to the observed
 absorption equivalent width ($W_{\rm a}$) for a series of transitions:
@@
 twice the radius \rtt, defined to be where the Sobolev optical depth 
-$\tau^S = 0.2$.  The black curves correspond to the fiducial wind
+$\tau_S = 0.2$.  The black curves correspond to the fiducial wind
 model ($\S$~\ref{sec:fiducial}; $\mrtt \approx 15$\,kpc), the red curves are for the
@@
 radiative-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
-For all of the wind models, the \ewe/\ewabs\ ratio rises very steeply
+For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
 with slit width and then plateaus at $\approx \mrtt$.  
@@
 photons have filled-in the absorption profiles at velocities $\mdv
-\gtrsim -400 \mkms$. The effects are greatest for wind
+\gtrsim -400 \mkms$. These effects, therefore, are greatest for wind
 models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
@@
 line-emission; one may even infer the flux of \mgiia\ exceeds that of
-\mgiib.  One also finds that the \mgiia\ absorption is shifted to
-shorter wavelengths (a greater velocity offset from systemic).  
+\mgiib.  The \mgiia\ absorption is also shifted to
+shorter wavelengths, i.e.\ to a greater velocity offset from systemic.  
 (b) The solid curve shows a stack of 100 spectra of the ISM+wind
 profile, each degraded to a S/N=2 per pixel, and offset from systemic
-by a normal deviate of $\sigma = 100 \mkms$ to mimic uncertainty in
+by a normal deviate with $\sigma = 100 \mkms$ to mimic uncertainty in
 the redshift of the galaxy.  
@@
 line-emission and absorption that reduces the height/depth of each.
-The effects may be even more pronounced if one studied spectra with
+The effects would likely be even more pronounced if one studied spectra with
 a diversity of \ion{Mg}{2} profiles.    
@@
 Surface brightness profiles of the fiducial wind model for the \mgiia\
-(solid) and \feiid\ (dotted) transitions.  Both profiles peak at small
+(solid) and \feiie\ (dotted) transitions.  Both profiles peak at small
 radii and decrease by several orders of magnitude before reaching the
@@
 sensitive IFU observation could map the emission (and, in principle,
-the kinematics) from $r_{\rm inner}$ to $r_{\rm outer}$.
+the kinematics) from $r_{\rm inner}$ to approximately $r_{\rm outer}$.
 }

### 2010-10-12 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5268 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 observations.  
-We examine outflows with a range of power-law density and velocity
-profiles and a radiative-driven wind model.  
+We implement monte carlo radiative
+transfer techniques that track the propogation of scattered and
+flourescent photons to generate 1D spectra and 2D spectral images.
+{\bf [Should we make the codes publically available?  Upon request?]}
+%We examine outflows with a range of power-law density and velocity
+%profiles and a radiative-driven wind model.  
 We focus on the \mgiid\ doublet and \ion{Fe}{2} UV1
@@
 to other transitions that trace outflows (e.g.\ \ion{Na}{1},
-\ion{H}{1} \lya, \ion{Si}{2}).   We implement monte carlo radiative
-transfer techniques that track the propogation of scattered and
-flourescent photons to generate 1D spectra and 2D spectral images.
-[Should we make the codes publically available?  Upon request?]
-[Mention fiducial model here?]
-As expected, the \ion{Mg}{2} doublet exhibits strong, blue-shifted
-absorption but one also predicts strong line-emission at roughly
-the systemic velocity.  This line-emission `fills-in' the absorption, 
-significantly reducing the effective
-opacity near systemic. Analysis of cool gas outflows that entirely ignores this
+\ion{H}{1} \lya, \ion{Si}{2}).   
+By design, the resonance transitions show lue-shifted
+absorption but one also predicts strong resonance and fine-structure line-emission at roughly
+the systemic velocity.  This line-emission `fills-in' the absorption
+reducing the equivalent width by up to $50\%$, shifting the centroid
+by tens of \kms, and severely
+reducing the effective
+opacity near systemic.  Analysis of cool gas outflows that ignores this
 line-emission may incorrectly infer that the gas is partially
@@
 conclude that gas at systemic velocity is absent   
-(e.g.\ an ISM or slowly infalling component). 
-The \ion{Fe}{2} resonance lines show similar behaviour, however 
-these lines are connected to optically thin transitions to
-fine-structure levels. As such, the \ion{Fe}{2} 
-absorption lines more faithfully reproduce the intrinsic opacity
+(e.g.\ an interstellar or slowly infalling component). 
+Because the \ion{Fe}{2} lines
+are connected by optically-thin transitions to
+fine-structure levels, their profiles
+more closely reproduce the intrinsic opacity
 of the wind.   Together these results naturally explain the
 absorption and emission-line characteristics observed for star-forming
-galaies at $z<1$.
+galaxies at $z<1$.
 We also study a scenario purported to describe the outflows
 of $z \sim 3$ Lyman break galaxies and argue this model fails to
-reproduce the observations when (previously ignored) scattered photons
-are properly considered.   
+reproduce the observations when radiative transfer of scattered photons
+is properly considered.   
 %Strong line-emission from metal-line
@@
 %presence of dust and anisotropic configurations.  
-The surface brightness profiles of emission from metal-line
-transitions offers a unique means of assessing the morphology and size
-of galactic-scale winds motivating deep,
+Although line-emission complicates the analysis of absorption-line
+profiles, the 
+surface brightness profiles 
+offers a unique means of assessing the morphology and size
+of galactic-scale winds.  Furthermore, the kinematics and line-ratios
+offer powerful diagnostics of outflows,  motivating deep,
 spatially-extended spectroscopic observations.
@@
 
-Another factor that may reduce line-emission is a
-non-isotropic wind model. The flux is lower, for example, if one
+Another factor that may reduce line-emission is an
+anisotropic wind model. The flux is lower, for example, if one
 eliminates the backside to the wind (e.g.\ the source itself could
 shadow a significant fraction of the backside).  
-For our fiducial model, many of the photons scattered into our
-sightline arise nearly normal to the sightline such that a biconicial
-wind has significantly lower line-emission
+Similarly, 
+many of the scattered photons of the fiducial 
+model arise nearly normal to the sightline such that a biconicial
+wind can have significantly lower line-emission
 ($\S$~\ref{sec:anisotropic}). 
@@
 generic orientation, most spectroscopic samples are magnitude-limited
-and biased towards detecting galaxies when observed from their
-brightest viewpoint.  In principle, this might imply a further
+and biased towards detecting galaxies when observed at their
+brightest.  In principle, this might imply a further
 reduction of order unity.
-{\bf [Put comments on biconical here]}
 
@@
 because this emission is dominated by single scatterings 
-which trace all components of the wind.  {\bf [Also the optical depth profile of
-  FeII]}
+which trace all components of the wind.
 
@@
 models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
-multiple of rest-frame UV transitions, but the results translate to
-most other transitions used to probe cool gas.  Our primary
+multiple of rest-frame UV transitions, but the results transfer to
+most other lines used to probe cool gas.  Our primary
 findings are summarized as follows:
@@
   observed in star-forming galaxies are predicted to be accompanied by
-  emission-lines with similar equivalent width.  This is even true for
-  anisotropic and dust-extincted scenarios.
+  emission-lines with similar equivalent width.  This even holds for
+  non-extreme anisotropic and dust-extincted scenarios.
 
@@
   are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
-  \ion{Na}{1}). The observed absorption profiles may be significantly
-  different from the intrinsic optical depth profile.
+  \ion{Na}{1}),  this implies much lower equivalent widths (up to
+  $50\%$) and also velocity profiles that are significantly offset
+  from the intrinsic optical depth profile.
 
@@
 \item Resonance transitions that are strongly coupled to
-non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) offer the best
-characterization of the opacity of the wind and also material 
-with velocities near systemic.  The emission will generally be dominated by the
-optically-thin, fine-structure transitions.
-
-\item  Dust extinction has only modest effects 
-  in models which predict only a few scatterings.  Models
+non-resonant lines (e.g.\ \ion{Fe}{2}, \ion{Si}{2}) 
+produce emission dominated by the
+optically-thin, fine-structure transitions.  As such, the resonance
+absorption lines offer the best
+characterization of the opacity of the wind and also of material 
+with velocities near systemic.
+
+\item  Dust extinction modestly affects 
+  models where resonance photons are trapped for only a few scatterings.  Models
   with high opacity at small radii and at systemic velocity (e.g.\ an
@@
   predict substantial line-emission from scattered photons that
-  greatly modify the predicted line-profiles.  
-  These models do not reproduce the observed line-profiles.
+  greatly modify the predicted line-profiles so that  
+  these models do not reproduce the observed line-profiles.
 
@@
 
-\item The kinematics and flux ratios of the emission lines 
-  constrain the wind speed, opacity, dust extinction, and XXX of the
-  wind.
-
-\item Biconical?
-
 \item Significant line-emission is a generic prediction of simple wind
@@
   viewed through finite apertures.  We have explored the 2D emission
-  maps (Figure~\ref{fig:fiducial_ifu_mgii}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
+  maps (Figure~\ref{fig:fiducial_ifu_mgii}) and surface brightness 
+  profiles (Figure~\ref{fig:obs_sb}) of
   the winds.  Sensitive, spatially-extended observations will map the
@@
   galactic-scale outflows.
+
+\item The kinematics and flux ratios of the emission lines 
+  constrain the wind speed, opacity, dust extinction, and morphology of the
+  wind.
 

### 2010-10-12 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5269 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 We implement monte carlo radiative
-transfer techniques that track the propogation of scattered and
-flourescent photons to generate 1D spectra and 2D spectral images.
-{\bf [Should we make the codes publically available?  Upon request?]}
+transfer techniques that track the propagation of scattered and
+fluorescent photons to generate 1D spectra and 2D spectral images.
+{\bf [Should we make the codes publicly available?  Upon request?]}
 %We examine outflows with a range of power-law density and velocity
@@
 \ion{H}{1} \lya, \ion{Si}{2}).   
-By design, the resonance transitions show lue-shifted
+By design, the resonance transitions show blue-shifted
 absorption but one also predicts strong resonance and fine-structure line-emission at roughly
@@
 
-For our 3-dimensional calculations, the  wind properties (density, temperature and velocity) were descritized on a $300^3$ Cartesian grid (for certain 1-D calculations, the wind properties were simply computed on the fly from analytic formulae).
+For our 3-dimensional calculations, the  wind properties (density, temperature and velocity) were discretized on a $300^3$ Cartesian grid (for certain 1-D calculations, the wind properties were simply computed on the fly from analytic formulae).
 The radiation field was represented by $N$ photon packets (typically $N \sim 10^7$) which were initially emitted isotropically and uniformly throughout the source region ($r < r_{\rm source}$).
@@
 diagnostic on the degree to which the resonance line photons are
-trapped, i.e.\ the peak opitcal depth of \ion{Fe}{2}~2600 and
+trapped, i.e.\ the peak optical depth of \ion{Fe}{2}~2600 and
 the velocity gradient of the wind.
@@
 many of the scattered photons of the fiducial 
-model arise nearly normal to the sightline such that a biconicial
+model arise nearly normal to the sightline such that a biconical
 wind can have significantly lower line-emission
@@
 could be dominant.  In either case, the study of spatially-extended
-line-emission from photons scattred by the galactic-scale wind offers
+line-emission from photons scattered by the galactic-scale wind offers
 an direct means to study the morphology and radial extent of these
@@
 are sensitive to characteristics of the wind.
-The most obvious example is the relative emisison of the \mgiid\
+The most obvious example is the relative emission of the \mgiid\
 doublet.  Specifically, an outflow whose velocity exceeds the doublet
@@
 
-We acknowledge valuable conversations with D. Koo, J. Hennawi, and ... 
+We acknowledge valuable conversations with D. Koo, J. Hennawi, and
+A. Wolfe. 
 J.X.P and K.R. are partially supported
@@
 to strong metal-line transitions (e.g.\ \ion{Si}{2}~1526).  The
-energy and momemtum in the outer regions of the outflow may be very
+energy and momentum in the outer regions of the outflow may be very
 difficult to generate with standard galactic-scale wind scenarios.
@@
 the nine models built from the density and velocity laws of panel (a).
-Each of these were normalised to have peak optical depths of 10 to
+Each of these were normalized to have peak optical depths of 10 to
 1000 and to be optically thin at small or large velocity.

### 2010-10-21 Winds/papers/Theory/First/Preprint/windsimple_prpt.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5288 ac11df5e-a788-c23b-a8e1-c758c323924d

--- 2010-10-11 Winds/papers/Theory/First/Submit/ms.tex
@@
-\documentclass[12pt,preprint]{aastex}
+\documentclass[]{emulateapj}
+%\documentclass[12pt,preprint]{aastex}
 \usepackage{natbib,amsmath}
@@
 
-\title{Simple Wind Models of Cool Gas Outflows as Viewed by
+\title{Diagnosing Simple Wind Models of Cool Gas Outflows as Viewed by
   Metal-Line Absorption and Emission}
@@
 
-We have also analyzed the predicted profiles for a series of biconical
-winds with $\theta = 10-60^\circ$, each viewed along the axis of
-asymmetry with the wind covering the source.
-Table~\ref{tab:line_diag} summarizes the results for two cases.  For
-modest opening angles $\theta < 20^\circ$, the results are
-qualitatively similar to the fiducial model;  the profiles show
-similar equivalent widths for absorption and emission.  The key
-quantitative difference is that the \feiis\ line-emission is
-suppressed at $\delta v \approx 0 \mkms$ because the portion of the
-wind with that projected velocity has been removed.  For
-$\theta>45^\circ$, enough of the wind has been removed that the
-line-emission is several times weaker than the fiducial model.
-Similarly, the absorption-line profiles more closely track the
-intrinsic optical depth of the outflow.   Of course, these same models
-when viewed `sideways' would show no absorption yet significant
-line-emission.  Such events are sufficiently rare (Rubin et
-al., in prep) that we consider this level of anisotropy to be of minor
-importance.
+[Add a paragraph on the bi-conical wind once we are confident in the
+results.  This may be a rather big effect.]
+
+[Consider showing a 2D model for biconical]
 
@@
   viewed through finite apertures.  We have explored the 2D emission
-  maps (Figure~\ref{fig:fiducial_ifu_mgii}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
+  maps (Figure~\ref{fig:ifu}) and surface brightness profiles (Figure~\ref{fig:obs_sb}) of
   the winds.  Sensitive, spatially-extended observations will map the
@@
 
-%\bibliographystyle{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati}
-%\bibliography{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati09}
-\bibliographystyle{/u/xavier/paper/Bibli/apj}
-\bibliography{/u/xavier/paper/Bibli/allrefs}
-
-\clearpage
-
-\input{../Tables/table_atomic.tex}
-\input{../Tables/tab_fiducial.tex}
-\input{../Tables/tab_fiducial_ew.tex}
-\input{../Tables/tab_meas_models.tex}
-\input{../Tables/tab_plaw_parm.tex}
-\input{../Tables/tab_meas_plaws.tex}
-
-\begin{figure}
-\epsscale{0.95}
-\plotone{../Figures/energy_levels.ps}
+\begin{figure}[ht]
+%\epsscale{0.95}
+%\plotone{../Figures/energy_levels.ps}
+\centering
+\includegraphics[width=3.5in]{../Figures/energy_levels.ps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/oneline_test.eps}
+\centering
+\includegraphics[width=3.5in]{../Figures/oneline_test.eps}
+%\epsscale{0.8}
+%\plotone{../Figures/oneline_test.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_nvtau_vs_r.ps}
+%\epsscale{0.8}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_nvtau_vs_r.ps}
 \caption{
@@
 and then converting to radius with the velocity law.  These give
-very similar results. 
-The wind parameters were set to give an optically thick medium at the
-inner radius ($r_{\rm inner} = 1$\,kpc) that becomes optically thin at
-the outer radius ($r_{\rm outer} = 20$\,kpc). 
+very similar results. One notes that
+the wind is optically thick at the inner radius ($r_{\rm inner} =
+1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
+  outer} = 20$\,kpc).
 }
@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
@@
 \label{fig:fiducial_1d}
-\end{figure}
+\end{figure*}
 
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_noemiss.ps}
+%\epsscale{0.8}
+\includegraphics[width=3.5in]{../Figures/fig_noemiss.ps}
 \caption{
@@
 re-emission occurs.   The true profiles have been `filled-in' 
-significantly with photons scattered by the wind into our sightline.  Ignoring this
+significantly by light scattered in the wind.  Ignoring this
 process, one would model the absorption lines with a systematically lower
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
+%\epsscale{0.8}
+\includegraphics[width=3.5in]{../Figures/fig_fiducial_ifu_mgii.ps}
 \caption{
@@
 wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  Amazingly, this
+entirely due to photons scattered by the wind.  Impressively, this
 emission exceeds the integrated flux at $v = -250\mkms$ such that the
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_feii_ifu.ps}
+\includegraphics[width=3.5in]{../Figures/fig_feii_ifu.ps}
 \caption{
@@
 the wind also make a significant contribution. 
+[Is this figure superfluous??]
 }
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_asymm_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_asymm_spec.ps}
 \caption{
@@
 uncovered) to $\phi = 180^\circ$ (source covered).  One detects
-significant emission for all orientations but significant
+significant emission for all orientations of this wind but significant
 absorption only for $\phi \ge 90^\circ$.
@@
 emission shifts from positive to negative velocities as $\phi$
-increases and one transitions from viewing the wind as lying behind the
-source to in front of it.  The velocity centroid of emission, therefore,
-diagnoses the degree of anisotropy for the wind.
+increases and one transitions from viewing the wind to be behind the
+source to in front.  The velocity centroid of emission, therefore, may
+give a robust measure of wind isotropy.
 }
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_dust_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_dust_spec.ps}
 \caption{
@@
 model (black) against a series of models that include 
-dust extinction, parameterize by the integrated dust opacity from
-source to infinity (\taud).  The primary effect of dust is to suppress 
+dust extinction.  The primary effect is suppression of
 the line-emission relative to the continuum. 
 A more subtle but important effect is that the redder photons in the
-emission lines (corresponding to positive velocity offsets relative to
-line-center) suffer greater extinction.  
-This occurs because the `redder' photons that we view have travelled 
-farther to scatter off the backside of the wind.  Note that
+emission lines (corresponding to higher velocity relative to
+line-center) suffer greater extinction.  This is most evident in the
+\feiic\ emission line; it occurs because these photons must
+travel farther to scatter off the backside of the wind.  Note that
 the absorption lines are nearly unmodified until $\mtaud = 10$, a
@@
 \epsscale{0.8}
-\plotone{../Figures/fig_taud_vs_we.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_taud_vs_we.ps}
 \caption{
-Predicted equivalent widths for \mgiib\ line-emission from the
+Predicted line-emission equivalent widths for \mgiib\ from the
 fiducial wind model, as attenuated by dust with a range of \taud\
@@
 the continuum) do not scale as $\exp(\tau_d)$.
-The black (solid) curve shows the model results while the
+The black (solid) curve shows the model predictions while the
 dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
 \cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
-representation of the results for our radiative transfer calculations.   
+representation of the radiative transfer results.   
 }
@@
 \begin{figure}
-\epsscale{0.7}
-\plotone{../Figures/fig_ism_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_ism_spec.ps}
 \caption{
@@
 reduced, implying much higher fluxes for the non-resonant lines (e.g.\
-\feiic,2626).  
-Lastly, we note that the \feiia\ absorption profile provides a good
-(albeit imperfect) representation of the wind opacity and therefore
-offers the best characterization of an ISM component.
+\feiic,2626).  The lack of scattered \feiia\ photons results in an
+absorption profile that very nearly matches the input opacity profile.
+We conclude that resonance transitions that are strongly coupled to
+non-resonant lines offer the best
+characterization of an ISM component.
 }
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_norm_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_norm_spec.ps}
 \caption{
@@
 varying normalization, parameterized by \nhn.  As expected, the
-strength of absorption increases with increasing \nhn; this also
+strength of absorption increases with increasing \nhn\ which also
 results in stronger line-emission.  Note that the \feiia\ emission is
-always weak. Only its absorption increases with \nhn\ and actually exceeds
+always weak; only its absorption increases with \nhn\ and actually exceeds
 the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_sobolev.ps}
+\includegraphics[width=3.5in]{../Figures/fig_lbg_sobolev.ps}
 \caption{
-(a) The dotted curve shows the velocity law (labeled on the
-right axis) for the LBG model
-of S10 plotted against $(r/{\rm kpc} -1)$ to highlight the evolution
-in the quantities at small radii.  For example,  note how rapidly the velocity rises from $r =
+(a) The dotted curve shows the velocity law (values are labeled on the
+right side) for the LBG model
+of S10.  Note how rapidly the velocity rises from $r =
 1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
@@
 the average absorption profile of LBG galaxies (see below).
-The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
+The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
 steepens to $(r/{\rm kpc}-1)^{-1.8}$.
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_lbg_spec.ps}
 \caption{
@@
 and (black) a model constructed to faithfully
-represent the wind model advocated by S10.  The dotted line
+correspond to the wind model advocated by S10.  The dotted line
 shows the absorption profiles of the latter model if one were
@@
 and \feiib)
-and produce strong emission lines.  
+and produce significant emission lines.  
 The result, for \ion{Mg}{2} especially, is a set of profiles that do
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_lbg_cumul.ps}
 \caption{
@@
 majority of mass, energy, and momentum in the wind are contained at
-large radii.  We derive similar results for the LBG-partial covering model
-if we assume the wind is composed of identical clouds optically thick
-to strong metal-line transitions (e.g.\ \ion{Si}{2}~1526).  The
-energy and momemtum in the outer regions of the outflow may be very
-difficult to generate with standard galactic-scale wind scenarios.
+large radii.
 }
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_rad_spec.ps}
+\includegraphics[width=3.5in]{../Figures/fig_rad_spec.ps}
 \caption{
@@
 fiducial wind model (black).  In contrast to the fiducial model, the
-optical depth peaks at large velocity (here $\mdv
+velocity of the radiation-driven model decreases with increasing
+radius such that the optical depth peaks at large velocity (here $\mdv
 \approx -350 \mkms$).  At these velocities, the absorption is not
@@
 The \feiis\ emission also has a similar
-equivalent width, yet the lines are much broader in the
+equivalent width, yet the lines are much broader for the
 radiative-driven model. 
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_vary_profiles.ps}
+\includegraphics[width=3.5in]{../Figures/fig_vary_profiles.ps}
 \caption{
@@
 \propto r^{-2}$) and velocity laws (colored; green -- $v \propto
-r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$) for a
-series of power-law models (Table~\ref{tab:plaw_parm}).  For
+r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$).  For
 comparison we also plot the velocity and density laws for the fiducial
-model (thin, black curves).  
+model (thin, black curves).  See Table~\ref{tab:plaw_parm} for further
+details.
 Panel (b) plots the optical depth profiles of the \mgiia\ line for
-the nine models built from the density and velocity laws of panel (a).
-Each of these were normalised to have peak optical depths of 10 to
-1000 and to be optically thin at small or large velocity.
+the nine models build from the density and velocity laws of panel (a).
 }
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_plaw_spec.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_slit.ps}
 \caption{
-Absolute emission equivalent width ($|W_{\rm e}|$) relative to the observed
+Emission equivalent width ($W_{\rm e}$) relative to the observed
 absorption equivalent width ($W_{\rm a}$) for a series of transitions:
@@
 twice the radius \rtt, defined to be where the Sobolev optical depth 
-$\tau_S = 0.2$.  The black curves correspond to the fiducial wind
+$\tau^S = 0.2$.  The black curves correspond to the fiducial wind
 model ($\S$~\ref{sec:fiducial}; $\mrtt \approx 15$\,kpc), the red curves are for the
@@
 radiative-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
-For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
+For all of the wind models, the \ewe/\ewabs\ ratio rises very steeply
 with slit width and then plateaus at $\approx \mrtt$.  
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_ew.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_peaktau.ps}
 \caption{
@@
 photons have filled-in the absorption profiles at velocities $\mdv
-\gtrsim -400 \mkms$. These effects, therefore, are greatest for wind
+\gtrsim -400 \mkms$. The effects are greatest for wind
 models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_vtau.ps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_lris.ps}
 \caption{
@@
 line-emission; one may even infer the flux of \mgiia\ exceeds that of
-\mgiib.  The \mgiia\ absorption is also shifted to
-shorter wavelengths, i.e.\ to a greater velocity offset from systemic.  
+\mgiib.  One also finds that the \mgiia\ absorption is shifted to
+shorter wavelengths (a greater velocity offset from systemic).  
 (b) The solid curve shows a stack of 100 spectra of the ISM+wind
 profile, each degraded to a S/N=2 per pixel, and offset from systemic
-by a normal deviate with $\sigma = 100 \mkms$ to mimic uncertainty in
+by a normal deviate of $\sigma = 100 \mkms$ to mimic uncertainty in
 the redshift of the galaxy.  
@@
 line-emission and absorption that reduces the height/depth of each.
-The effects would likely be even more pronounced if one studied spectra with
+The effects may be even more pronounced if one studied spectra with
 a diversity of \ion{Mg}{2} profiles.    
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_sb.ps}
 \caption{
 Surface brightness profiles of the fiducial wind model for the \mgiia\
-(solid) and \feiie\ (dotted) transitions.  Both profiles peak at small
+(solid) and \feiid\ (dotted) transitions.  Both profiles peak at small
 radii and decrease by several orders of magnitude before reaching the
@@
 sensitive IFU observation could map the emission (and, in principle,
-the kinematics) from $r_{\rm inner}$ to approximately $r_{\rm outer}$.
+the kinematics) from $r_{\rm inner}$ to $r_{\rm outer}$.
 }
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
+\includegraphics[height=3.5in,angle=90]{../Figures/fig_obs_edelv.ps}
 \caption{
@@
 
+\clearpage
+
+\input{../Tables/table_atomic.tex}
+\input{../Tables/tab_fiducial.tex}
+\input{../Tables/tab_fiducial_ew.tex}
+\input{../Tables/tab_meas_models_nor.tex}
+\input{../Tables/tab_plaw_parm.tex}
+\input{../Tables/tab_meas_plaws_nor.tex}
+
+\clearpage
+
+%\bibliographystyle{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati}
+%\bibliography{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati09}
+\bibliographystyle{/u/xavier/paper/Bibli/apj}
+\bibliography{/u/xavier/paper/Bibli/allrefs}
+
+\clearpage
+
 \end{document}

### 2010-11-15 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5406 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 surface brightness profiles 
-offers a unique means of assessing the morphology and size
+offer a unique means of assessing the morphology and size
 of galactic-scale winds.  Furthermore, the kinematics and line-ratios
@@
 regulate the metal and dust content and distribution within the 
-objects and its surroundings, 
+objects and their surroundings, 
 %%
@@
 %tens of kpc 
-from the galaxy \citep{lhw99,wsg08,vsr+03} carrying significant speed
+from the galaxy \citep{lhw99,vsr+03,wsg08} carrying significant speed
 to escape from the gravitational potential well of the galaxy's dark
@@
 These authors additionally detected line
-emission from non-resonant \ion{Fe}{2}$^*$ transitions, and attribute
+emission from non-resonant \ion{Fe}{2}$^*$ transitions, and attributed
 the emission to fluorescence powered by \ion{Fe}{2} resonant
@@
 $\tau_{ux}$ is the optical depth to infinity, which was  constructed  by integration along the path to escape, taking into account the relevant Doppler shifts and possible absorption by lines or dust.
-The contribution of the packet to the final spectrum was than added in for every possible final state, each shifted to the proper observer-frame wavelength and weighted by the probability $P_x$.
+The contribution of the packet to the final spectrum was then added in for every possible final state, each shifted to the proper observer-frame wavelength and weighted by the probability $P_x$.
 
@@
 In addition, \cite{msf+10} have argued from a statistical analysis
-that dust is distributed to many tens kpc from $z \sim 0.1$ galaxies
+that dust is distributed to many tens of kpc from $z \sim 0.1$ galaxies
 and have suggested it was transported from the galaxies by
@@
 interacts with a line only when
-it's comoving frame wavelength is Doppler shifted into near resonance with the line center rest wavelength. 
+its comoving frame wavelength is Doppler-shifted into near resonance with the line center rest wavelength. 
 For a wind with a steep velocity law  (i.e.\ a large gradient $dv/dr$)
@@
 optical depth. Therefore, one may consider the choices for
-$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as largely arbitrary.
+$r_{\rm inner}, r_{\rm outer}$, and $n_{\rm H}^0$ as largely arbitrary.
 Nevertheless, we adopted values for this fiducial model with
@@
 propagated photons from the source and through the outflow to an
-`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
+`observer' at $r \gg r_{\rm outer}$ who views the entire wind+source
 complex.  Figure~\ref{fig:fiducial_1d} presents the 1D spectrum
@@
 source embedded within an outflow.  Strong absorption is evident at
-$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both transitions (equivalent widths, $W^{2796} =
+$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both
+transitions (with equivalent widths $W^{2796} =
 3.0$\AA\ and $W^{2803} = 1.3$\AA) and each shows emission at
@@
 line ratio that is far below the $2:1$ ratio that one may have naively
-expected (e..g.\ if the line-emission resulted from recombinations),
+expected (e.g.\ if the line-emission resulted from recombinations),
 and leads us to conclude that the relative 
-strengths of the emission lines is sensitive to both the opacity and
+strengths of the emission lines are sensitive to both the opacity and
 velocity extent of the wind.
@@
 (Figure~\ref{fig:energy}).  Specifically, 
-resonance photons absorbed at \feiid\ have a finite probability of
+a resonance photon absorbed at \feiid\ has a finite probability of
 being re-emitted as a non-resonant photon which then escapes the system
@@
 resonance line.  Therefore, the majority of photons absorbed at
-$\lambda \approx 2600$\AA\ are re-emitted as \feiib\ photons whereas 
+$\lambda \approx 2600$\AA\ are re-emitted as \feiib\ photons, whereas 
 the majority of photons absorbed at $\lambda \approx 2586$\AA\ are re-emitted 
 at longer wavelengths (\feiic\ or $\lambda 2632$).
-If we were to increase $\tau_{2600}$ (and especially if we include
+If we %were to 
+increase $\tau_{2600}$ (and especially if we include
 gas with $\mvr \approx 0 \mkms$) then the \feiib\ emission is
@@
 When viewed from the opposite direction ($\phi = 180^\circ$), the
-absorption lines dominate but there is still significant
-line-emission, at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
-in the absorption, from photons that scatter through the wind.  The
-key difference from the isotropic wind is the absence of photons
+absorption lines dominate, but there is still significant
+line-emission at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
+in the absorption from photons that scatter through the wind.  The
+key difference between this and the isotropic wind is the absence of photons
 scattered to $\mdv > 100 \mkms$;  this also implies deeper 
 \mgiib\ absorption at $\mdv \approx -100 \mkms$. The 
-shift in velocity centroid and asymmetry of the emission lines
+shifts in velocity centroid and asymmetry of the emission lines
 serve to diagnose the degree of wind isotropy, especially in
@@
 cool gas and metals.  This dust 
-modifies the observed wind profiles in two manners. 
+modifies the observed wind profiles in two ways. 
 First, it is a source of opacity for all of 
@@
 distance to escape and therefore suffer from greater extinction.  A photon that is
-trapped for many scatterings may have a very high probability of being absorbed
+trapped for many scatterings %may have a very high 
+has an increased 
+probability of being absorbed
 by dust.  
-Section~\ref{sec:dust_method} describes the details on our treatment of dust; we 
+Section~\ref{sec:dust_method} describes the details of our treatment of dust; we 
 remind the reader here that we assume a constant dust-to-gas ratio 
@@
 nearly identical for $\mtaud \le 3$.  One requires very high
-extinction to eventually produce a deepening of the profiles at 
+extinction to %eventually 
+produce a deepening of the profiles at 
 $\mdv \approx -100 \mkms$.
@@
 We conclude that dust has only a modest influence on this fiducial model and,
-by inference, models with moderate peak optical depth and
-significant velocity gradients with radius (i.e.\ scenarios where the
+by inference, on models with moderate peak optical depths and
+significant velocity gradients with radius (i.e.\ scenarios in which the
 photons scatter only one to a few times before exiting).
@@
 The fiducial model does not include gas associated with
-the interstellar medium of the galaxy, i.e.\ material at $r \sim
+the ISM %interstellar medium 
+of the galaxy, i.e.\ material at $r \sim
 0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
@@
 source are very likely embedded within and fueled by gas
-of the ISM.  
+from the ISM.  
 Consider, then, a modification to the fiducial model that 
@@
 fact, the ISM+wind model is nearly identical to the fiducial model;
-the only quantitative difference is that the velocity centroid of
+the only quantitative difference is that the velocity centroids of
 the emission lines are shifted redward by $\approx +100 \mkms$.
-We have also examined the spatial emission of this model and note
-qualitatively similar results to the fiducial wind model
+We have also examined the spatial distribution of emission from 
+this model and find results
+qualitatively similar to the fiducial wind model
 (Figures~\ref{fig:fiducial_ifu_mgii} and \ref{fig:fiducial_ifu_feii}).
@@
 (1) there is greater absorption by the \feiid\
-resonance lines; (2) the high opacity of the ISM component leads to
+resonance lines; and (2) the high opacity of the ISM component leads to
 an enhanced conversion of resonance photons with $\mdv \approx 0\mkms$
@@
 strengths of the \feiib\ and \feiie\ lines provide a direct
-diagnostic on the degree to which the resonance line photons are
+diagnostic of the degree to which the resonance line photons are
 trapped, i.e.\ the peak optical depth of \ion{Fe}{2}~2600 and
@@
 emission lines are significantly reduced.  The \ion{Mg}{2} emission is
-affect most because these lines are resonantly trapped.  The \feiis\
+affected most because these lines are resonantly trapped.  The \feiis\
 emission is also reduced relative to the dust-free model, but the
 absolute flux still exceeds the fiducial model
-(Table~\ref{tab:line_diag}).  At large negative velocity offset from
+(Table~\ref{tab:line_diag}).  At large negative velocity offsets from
 systemic, the two profiles are nearly identical.
@@
 
-The final modification to the fiducial model considered was to
-uniformly vary the normalization of the optical depth profiles.
+The final modification to the fiducial model considered was %to
+%uniformly vary 
+a uniform variation of
+the normalization of the optical depth profiles.
 Specifically, we ran a series of additional models with $n_{\rm H}^0$ at
@@
 behave as expected.  Higher/lower optical depths lead to
-greater/weaker \mgiia\ absorption and stronger/weaker \mgiib\ emission
+greater/weaker \mgiia\ absorption and stronger/weaker \mgiib\ emission.
 In the extreme case of
@@
 Table~\ref{tab:line_diag} presents a series of quantitative measures
-for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
+of the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
 the fiducial model ($\S$~\ref{sec:fiducial}) and a subset of the models
@@
 `red and dead' galaxies \citep[e.g.][]{spf01}.  Although the
-presence of these outflows were established over a decade ago,
+presence of these outflows was established over a decade ago,
 the processes that drive them remain
 unidentified.  Similarly,  current estimates of the mass and energetics of the
-outflow suffer from orders of magnitude uncertainty.
+outflows suffer from orders of magnitude uncertainty.
 
@@
 For the velocity law, they adopted the following functional
-form
+form:
 
@@
 
-In the following, we consider two methods to analyze the LBG wind.
+In the following, we consider two methods for analyzing the LBG wind.
 Both approaches assume an isotropic wind and adopt the velocity law given by
@@
 \biggl( \frac{ m_e c}{\pi e^2} \biggl)
- \cmma
+ %\cmma
+ \perd
 \label{eqn:nSobolev}
@@
 absorbed photons significantly alters the predicted absorption profiles
-for the inputted model.  This is, of course, an unavoidable
+for the input %ted 
+model.  This is, of course, an unavoidable
 consequence of an isotropic, dust-free model with unit covering
@@
 
-Because we have explicit velocity and densities profiles for the LBG-Sobolev
+Because we have explicit velocity and density profiles for the LBG-Sobolev
 model, it is straightforward to calculate the radial
@@
 LBG wind model (see the following sub-section).
-This issues aside, we may inspect Figure~\ref{fig:LBG_cumul} to reveal
+These issues aside, we may inspect Figure~\ref{fig:LBG_cumul} to reveal
 global properties of this LBG-Sobolev wind.
@@
 carried in the outer 
-In fact, for clumps that are optical thick to strong metal-line
+In fact, for clumps that are optically thick to strong metal-line
 transitions (e.g.\ \ion{Si}{2}~1526) we estimate that the wind would
@@
 question.  Several studies advocate a primarily energy-driven
-wind scenario, in which the hot wind is produced by the thermalized
+wind scenario, in which the hot wind produced by the thermalized
 energy from SNe ejecta entrains cool clouds via ram pressure \citep[e.g.][]{cc85,ham90,sh09}.
@@
 
-These authors start by assuming the galaxy is an isothermal sphere
+These authors start by assuming the galaxy has luminosity $L$ and is an isothermal sphere
 with mass profile $M_{gal}(r) = 2\sigma^2r/G$, where $\sigma$ is the
-velocity dispersion, and with luminosity $L$.  The gas mass profile is
+velocity dispersion.  The gas mass profile is
 simply $M_g(r) = f_g M_{gal}(r)$, with $f_g$ a constant gas fraction.  
@@
 \begin{equation}
-n(r) = \frac{dM_{\rm wind}/dt}{m_p r^2 v(r)}, 
+n_{\rm H}(r) = \frac{dM_{\rm wind}/dt}{m_p r^2 v(r)}, 
 \end{equation}
@@
 filled-in by scattered photons and one recovers absorption lines
-that more closely follows the intrinsic optical depth profile (dotted
+that more closely follow the intrinsic optical depth profile (dotted
 curve). The \ion{Mg}{2} line-emission, meanwhile, has
@@
 The kinematics of \feiis\ line-emission, therefore, independently
-diagnoses the intrinsic optical depth profile of the flow.
-We conclude that the radiative-driven model has characteristics that
+diagnose the intrinsic optical depth profile of the flow.
+We conclude that the radiation-driven model has characteristics that
 are qualitatively similar to the fiducial model (e.g.\ strong
@@
 The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
-modified to yield an \mgiia\ optical depth profile that peaks at
+modified to yield a \mgiia\ optical depth profile that peaks at
 $\tau_{2796}^{\rm max} \approx 10-10^3$ and then usually decreases to
@@
 than $\approx 0.1$ at these velocities. 
-Similar to the radiative driven wind ($\S$~\ref{sec:radiative}),
+Similar to the radiation-driven wind ($\S$~\ref{sec:radiative}),
 the power-law models that have significant opacity at $\mdv <
@@
 absorption peaks at large velocity from the systemic.
-One of the few obvious distinctions of these models from the fiducial wind is
+One of the few obvious distinctions between these models and the fiducial wind is
 the higher peak optical depth of absorption in the \feiib\
-transition.  This is primarily because these models have 
+transition.  This occurs primarily because these models have 
 higher intrinsic optical depths (i.e.\ higher $n_{\rm Fe^+}$ values).
 
-While there is commonality amongst between models, the specific
+While there is commonality between models, the specific
 characteristics of the absorption/emission profiles do exhibit
@@
 and non-resonance transitions.  For isotropic and dust-free scenarios,
-this is simple conservation of photons: every photon emitted by
+this is 
+due to the 
+simple conservation of photons: every photon emitted by
 the source eventually escapes the system to maintain
@@
 \ion{Mg}{2} emission \citep{wcp+09,rwk+10}, 
-\ion{Si}{2}* emission from LBG galaxies \citep{shapley03},
+\ion{Si}{2}* emission from LBGs \citep{shapley03},
 and, most recently, significant \feiis\ emission \citep{rubin+10c}. 
@@
 more effectively trapped, dust does suppress
-the emission (e.g.\ the ISM+wind model from $\S$~\ref{sec:ISM}).
+the emission (e.g.\ in the ISM+wind model from $\S$~\ref{sec:ISM}).
 In contrast to \ion{Mg}{2}, 
@@
 
-Another factor that may reduce line-emission is an
-anisotropic wind model. The flux is lower, for example, if one
+Another factor that may reduce line-emission is %an
+%anisotropic 
+wind %model
+anisotropy. The flux is lower, for example, if one
 eliminates the backside to the wind (e.g.\ the source itself could
@@
 Similarly, 
-many of the scattered photons of the fiducial 
+many of the scattered photons in the fiducial 
 model arise nearly normal to the sightline such that a biconical
@@
 effects may explain the absence of significant line-emission,
-but these would generally
+but they would generally
 not be sufficient to preclude detection.
@@
 indicates that detectable line-emission should occur frequently. 
-Furthermore, the line-emission could be suppressed so as not to exceed
-the galaxy continuum yet still (partially) fill-in the absorption
+Furthermore, the line-emission could be suppressed so %as not to 
+that it does not
+exceed
+the galaxy continuum yet still (partially) fills-in the absorption
 profiles. Indeed, dust and anisotropic winds preferentially suppress
@@
 regarding characteristics of the flow.  {\it An analysis of cool gas outflows
-that entirely ignores line-emission may incorrectly conclude that the gas is
-partially covered, has a significantly lower peak optical depth,
+that entirely ignores line-emission may incorrectly conclude that the source is
+partially covered, that the gas has a significantly lower peak optical depth,
 and/or that a $\mdv \sim 0 \mkms$ component is
@@
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
-which has the most effected transitions, \ewabs\ is reduced by
+which has the most strongly affected transitions, \ewabs\ is reduced by
 $30-50\%$ from the intrinsic equivalent width.  In turn, one may derive 
@@
 results are similar for the \mgiib\ profile.  In fact, one generally
-measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and would 
+measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and %would 
+may 
 falsely conclude that the source is partially covered. 
@@
 
-These effects for \ion{Mg}{2} absorption are reduced
+These effects %for \ion{Mg}{2} absorption 
+are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
@@
 spectra to study outflows
-\citep[e.g.][S10]{wcp+09,rwk+10}.   The main difference from the
+\citep[e.g.][S10]{wcp+09,rwk+10}.   The main difference %from 
+between this and 
+the
 single galaxy observation shown in panel (a) is the smearing of
@@
 with the absorption-line data, the two sets of constraints may break
-various degeneracies on the physical characteristics of the outflow.
+various degeneracies in the physical characteristics of the outflow.
 We now consider a few examples.
 
-The most obvious measures provided by the line-emission are
-estimates
-of the size and morphology of the outflow \citep{rubin+10c}.  
+The most obvious %measures provided 
+characteristics probed 
+by the line-emission are
+%estimates
+%of 
+the size and morphology of the outflow \citep{rubin+10c}.  
 Line emission is predicted to extend to radii where the Sobolev
@@
 large format IFU or narrow band imager) may detect the emission in
-azimuthally averaged apertures. 
+azimuthally-averaged apertures. 
 For the fiducial wind model, for example, the azimuthally integrated
@@
 (ii) there are fewer emission channels per absorption line than for
-\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiib) frequently has the
+\ion{Fe}{2}.  The \ion{Mg}{2} lines (especially \mgiib) frequently have the
 highest peak and integrated fluxes (Figure~\ref{fig:obs_sb}).  
@@
 could be dominant.  In either case, the study of spatially-extended
-line-emission from photons scattered by the galactic-scale wind offers
-an direct means to study the morphology and radial extent of these
+line-emission from photons scattered by a galactic-scale wind offers
+a direct means to study the morphology and radial extent of these
 phenomena.  The next generation of large-format optical and infrared
@@
 
-The kinematic characteristics of the line-emission also offer insight into physical
+The kinematic measurements of the line-emission also offer insight into physical
 characteristics of the wind.
@@
 widths are
-sensitive to the optical depth of the wind at large velocities from
+sensitive to the optical depth of the wind at large velocity offsets from
 systemic.  This is illustrated in Figure~\ref{fig:obs_edelv} which plots
@@
 models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
-multiple of rest-frame UV transitions, but the results transfer to
+multiplet of rest-frame UV transitions, but the results transfer to
 most other lines used to probe cool gas.  Our primary
@@
   are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
-  \ion{Na}{1}),  this implies much lower equivalent widths (up to
+  \ion{Na}{1}),  this implies much lower equivalent widths (by up to
   $50\%$) and also velocity profiles that are significantly offset
@@
 \item Analysis of cool gas outflows that entirely ignores this
-line-emission may incorrectly conclude that the gas is partially
-covered, has a significantly lower peak optical depth, and/or that a
+line-emission may incorrectly conclude that the source is partially
+covered, that the gas has a significantly lower peak optical depth, and/or that 
 gas with velocities near systemic (e.g.\ from the ISM or even
@@
 produce emission dominated by the
-optically-thin, fine-structure transitions.  As such, the resonance
+optically-thin, fine-structure transitions.  As such, these resonance
 absorption lines offer the best
@@
   models where resonance photons are trapped for only a few scatterings.  Models
-  with high opacity at small radii and at systemic velocity (e.g.\ an
+  with high opacity at small radii and at systemic velocity (e.g.\
+  with an
   optically thick, ISM component)  can effectively extinguish
@@
 \item The kinematics and flux ratios of the emission lines 
-  constrain the wind speed, opacity, dust extinction, and morphology of the
+  constrain the %wind 
+  speed, opacity, dust extinction, and morphology of the
   wind.
@@
 resonance-line transitions (i.e.\ they share the same upper energy
-levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
+levels).  We also show a pair of transitions (\ion{Fe}{2}$^* \lambda\lambda
 2618,2631$; red and dashed lines) that arise from higher levels in the \zconfig\
@@
 canonical P-Cygni profiles of a source 
-embedded within an outflow.  Overplotted on each transition (dotted line) is
+embedded within an outflow.  Overplotted on each transition (dotted
+red line) is
 the predicted absorption profile under the constraint that every
@@
 process, one would model the absorption lines with a systematically lower
-optical depth and (incorrectly) conclude that the source is partly covered by the
+optical depth and/or (incorrectly) conclude that the source is partly covered by the
 gas.  
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-model (black) against a series of models that include 
+model (black) compared against a series of models that include 
 dust extinction, parameterize by the integrated dust opacity from
@@
 the average absorption profile of LBG galaxies (see below).
-The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
+The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ and then
 steepens to $(r/{\rm kpc}-1)^{-1.8}$.
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
-LBG models considered: (red) the profiles from the 
+LBG models considered: (red) the profiles predicted using the 
 Sobolev approximation 
@@
 equivalent width, yet the lines are much broader in the
-radiative-driven model. 
+radiation-driven model. 
 }
@@
 \propto r^0$, dotted -- $\mnhn \propto r^{-3}$, dot-dash -- $\mnhn
-\propto r^{-2}$) and velocity laws (colored; green -- $v \propto
+\propto r^{2}$) and velocity laws (colored; green -- $v \propto
 r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$) for a
@@
 models (see Table~\ref{tab:plaw_parm} for details).  These panels reveal
-the diversity of absorption and emission that result from a set of
+the diversity of absorption and emission that results from a set of
 intrinsic optical depth profiles that have relatively modest
@@
 8$\,kpc), and the
-radiative-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
+radiation-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
 For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
@@
 where \tpk\ exceeds 3 are presented as lower limits.  The \tpk\ values
-are plotted against the velocity $v_\tau$ where $I(v) = I_{\rm min}$.  In all
+are plotted against the velocity $v_\tau$ where $I(v_\tau) = I_{\rm min}$.  In all
 of the models, the true peak optical depth $\mtpk^{\rm true} > 10$.
@@
 `Observations' of the \ion{Mg}{2} profiles for the ISM+wind model.  
-(a) The true profile (dotted lines) have been convolved with a
+(a) The true profile (dotted lines) has been convolved with a
 Gaussian line-spread-function (FWHM~$= 250 \mkms$) and noise has been
@@
 by a normal deviate with $\sigma = 100 \mkms$ to mimic uncertainty in
-the redshift of the galaxy.  
+the redshift of the galaxies.  
 This treatment is meant to illustrate the
 implications of stacking galaxy spectra to study outflows
-\citep[e.g.][]{wcp+09,smn+09,rwk+10}.   The main difference from the
+\citep[e.g.][S10]{wcp+09,rwk+10}.   The main difference from the
 single galaxy observation shown in panel (a) is the smearing of

### 2010-11-17 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5413 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\title{Simple Wind Models of Cool Gas Outflows as Viewed by
-  Metal-Line Absorption and Emission}
+\title{Simple Models of Metal-Line Absorption and Emission from
+Cool Gas Outflows}
 
@@
 galaxies at $z<1$.
-We also study a scenario purported to describe the outflows
+We also study a scenario promoted to describe the outflows
 of $z \sim 3$ Lyman break galaxies and argue this model fails to
@@
 
-\keywords{absorption lines -- intergalactic medium -- Lyman limit systems -- SDSS}
+\keywords{galaxies: formation -- galaxies: starbust}
 
@@
 spectacular jets of radio-loud AGN.   These gaseous outflows 
-%%KHRR
 regulate the metal and dust content and distribution within the 
 objects and their surroundings, 
-%%
 moderate the accretion of new material, and %onto the object, 
@@
 together with a cool, denser phase traced by H$\alpha$ emission 
-%% KHRR -- added refs
 \citep[e.g.][]{ham90,martin99,shc+04,km10}. 
@@
 up to $\sim 10$ kpc
-%tens of kpc 
 from the galaxy \citep{lhw99,vsr+03,wsg08} carrying significant speed
@@
 
-%Beyond $z \sim 0$, 
 Galactic outflows are also
@@
 The incidence of cool gas outflows is
-nearly universal in 
-%% KHRR added:
-vigorously
-%%
-star-forming galaxies;  this includes systems at $z \sim 0$
+nearly universal in vigorously
+star-forming galaxies;  this includes systems at low $z$
 which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
 \citep{rvs05a,martin05,smn+09,mb09,cth+10}, 
-$z \sim 1$ star-forming galaxies traced by
+$z \sim 1$ star-forming galaxies with winds traced by
 \ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rwk+10}, and
@@
 %the wind extends to at least 7\,kpc from the galaxy.  
-Line-emission is
+Line-emission that may be related to outflows is
 also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
@@
   \cite{france10} for a new example at $z \sim 0$.} \citep{prs+02,shapley03}.
-We emphasize that this emission arises from a completely different
+This emission likely arises from a completely different
 physical process than those generating X-ray and H$\alpha$ emission
@@
 of the results that follow may be generalized to observational studies that
-consider other atoms and ions of cool gas.
+consider other atoms and ions tracing cool gas.
 
@@
 detectable quantities of \ion{Fe}{1} which has not yet been observed
-in galactic-scale outflows. Furthermore, observations rarely show
+in galactic-scale outflows. 
+If collisional excitation is insignificant 
+then one may also neglect collisional de-excitation.  
+Furthermore, observations rarely show
 {\it absorption} from the
@@
 ground-state, i.e.\ the gas has zero opacity to the non-resonant
-lines.  If collisional excitation is insignificant 
-then one may also neglect collisional de-excitation.  
+lines.  
 Regarding the \ion{Mg}{2} doublet, its
@@
 intrinsic emission of these galaxies is a complex combination of
-stars and \ion{H}{2} regions that is then modulated by dust and gas
-within the interstellar medium (ISM).  For the spectral regions studied
-here, most stars show a featureless continuum, but a few spectral
+light from stars and \ion{H}{2} regions that is then modulated by dust and gas
+within the ISM.  For the spectral regions studied
+here, the hottest stars show a featureless continuum, but later spectral
 types do show significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
@@
 determined by direct numerical integration of the radiation transport
-equation under the Sobolev approximation \citep[e.g.,][]{Jeffery_Branch}.
+equation under the Sobolev approximation
+\citep[$\S$~\ref{sec:Sobolev}; e.g.,][]{Jeffery_Branch}.
 
@@
 \end{equation}
-is the integrated line opacity, $\lambda^0_\ell$ the rest center wavelength,
+is the integrated line opacity, $\lambda^0_\ell$ the line-center rest wavelength,
 $f_\ell$ the oscillator strength and
@@
 $\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both
-transitions (with equivalent widths $W^{2796} =
-3.0$\AA\ and $W^{2803} = 1.3$\AA) and each shows emission at
+transitions (with equivalent widths $W^{2796}_a =
+3.0$\AA\ and $W^{2803}_a = 1.3$\AA) and each shows emission at
 positive velocities.  For an isotropic and dust-free model, the
@@
 the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
-saturated) which only partially covers the emitting source
+is saturated) which only partially covers the emitting source
 \citep[e.g.][]{rvs05a,hkp+10}.  Our fiducial wind model, however, 
@@
 even though the line has a $2 \times$ lower $f\lambda$ value.
-These differences between the \ion{Fe}{2} resonance lines (and with the
-\ion{Mg}{2} doublet) occur because of the complex of non-resonant
+These differences between the \ion{Fe}{2} resonance lines (and between
+\ion{Fe}{2} and \ion{Mg}{2}) occur because of the complex of non-resonant
 \feiis\ transitions that are coupled to the resonance lines
@@
 \lesssim -50 \mkms$ and the generation of emission lines at $\mdv \approx
-0 \mkms$ by photons scattered in the wind.  To study the spatial
-extent of this emission, we mapped the emission of the fiducial
-model (see $\S$~\ref{sec:monte} for a description of the algorithm).
+0 \mkms$ by photons scattered in the wind.  We also
+mapped the emission of the fiducial
+model to sudy its spatial extent (see $\S$~\ref{sec:monte} for a description of the algorithm).
 The output is a set of surface-brightness maps in a series of 
@@
 generated in the wind.
-The results presented in Figures~\ref{fig:fiducial_ifu_mgii} and
-\ref{fig:fiducial_ifu_feii} are sensitive to the radial extent,
-morphology, density and velocity profiles of this galactic-scale
-wind.  Consequently, IFU observations of line emission from low-ion
-transitions may offer the most direct constraints on galactic-scale
-wind properties.
 
@@
 A proper treatment of these
-distributions is critical to interpret observations
+distributions is critical for interpreting observations
 acquired through a slit, i.e.\ where the aperture has a limited extent
@@
 $\S$~\ref{sec:discuss}.
+
+The results presented in Figures~\ref{fig:fiducial_ifu_mgii} and
+\ref{fig:fiducial_ifu_feii} are sensitive to the radial extent,
+morphology, density and velocity profiles of this galactic-scale
+wind.  Consequently, IFU observations of line emission from low-ion
+transitions may offer the most direct constraints on galactic-scale
+wind properties.
 
@@
 (ii) a bi-conical wind where the density is set to zero for angles
-$|\theta| < \theta_b$ and that is viewed along the plane of symmetry.
+$|\theta| < \theta_b$ and that is viewed along the axis of rotational
+symmetry ($\theta = 90^\circ$ is defined to be along our sightline).
 
@@
 absorption lines dominate, but there is still significant
-line-emission at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
-in the absorption from photons that scatter through the wind.  The
-key difference between this and the isotropic wind is the absence of photons
+line-emission at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ 
+from photons that scatter through the wind
+which fills in the absorption. 
+The key difference between this and the isotropic wind is the absence of photons
 scattered to $\mdv > 100 \mkms$;  this also implies deeper 
@@
 winds with $\theta = 10-60^\circ$, each viewed along the axis of
-asymmetry with the wind covering the source.
-Table~\ref{tab:line_diag} summarizes the results for two cases.  For
-modest opening angles $\theta < 20^\circ$, the results are
-qualitatively similar to the fiducial model;  the profiles show
+rotational asymmetry with the wind covering the
+source. Figure~\ref{fig:biconical} and
+Table~\ref{tab:line_diag} summarizes the results for several cases.  For
+$\theta_b = 10^\circ$, the results are
+very similar to the fiducial model;  the profiles show
 similar equivalent widths for absorption and emission.  The key
@@
 wind with that projected velocity has been removed.  For
-$\theta>45^\circ$, enough of the wind has been removed that the
+$\theta_b>45^\circ$, enough of the wind has been removed that the
 line-emission is several times weaker than the fiducial model.
@@
 line-emission.  Such events are sufficiently rare (Rubin et
-al., in prep) that we consider this level of anisotropy to be of minor
-importance.
+al., in prep) that we consider this level of anisotropy to be
+uncommon.
 
@@
 that is normalized by the total optical
-depth \taud\ a photon would experience if it traveled from the
+depth \taud\ photons would experience if they traveled from the
 source to infinity without scattering.
@@
 similar to our LBG-Sobolev calculation (Figure~\ref{fig:LBG_Sobolev}),
-this clump predicts the majority of mass, energy, and momentum are
-carried in the outer 
+this clump model predicts the majority of mass, energy, and momentum are
+carried in the outer regions of the wind. 
 In fact, for clumps that are optically thick to strong metal-line
@@
 Figure~\ref{fig:plaws_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
-profiles for the full suite of power-law models.  Although these
+profiles for the full suite of power-law models (see also
+Table~\ref{tab:plaw_diag}).  Although these
 models differ qualitatively from the fiducial model in their density
@@
 In detail, the line profiles differ in their peak optical depths,
-the velocity centroids of absorption, and the total equivalent widths.
+the velocity centroids of absorption/emission, and their equivalent widths.
 We find that many of the differences are driven by differences in
@@
 shadow a significant fraction of the backside).  
-Similarly, 
-many of the scattered photons in the fiducial 
-model arise nearly normal to the sightline such that a biconical
-wind can have significantly lower line-emission
+Similarly, a biconical
+wind can have significantly lower line-emission for the fiducial model
 ($\S$~\ref{sec:anisotropic}). 
@@
 wind model (black curves).
-{\bf [Add radiative model]}
 The \ewe/\ewabs\ curves rise very steeply with increasing slit width and then
@@
 (Figures~\ref{fig:anisotropic},\ref{fig:dust}).
-The emission would still 
+The remaining emission would still 
 modify the observed absorption profiles (e.g.\
@@
 emission-line profiles of a set of simple galactic-scale outflow
-models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
+models.  {\bf [Add what is new, e.g. Monte Carlo radiative transfer]}
+Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
 multiplet of rest-frame UV transitions, but the results transfer to
@@
   are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
-  \ion{Na}{1}),  this implies much lower equivalent widths (by up to
+  \ion{Na}{1}),  this implies much lower, absorption-line equivalent widths (by up to
   $50\%$) and also velocity profiles that are significantly offset
@@
 \item We examined two scenarios designed to mimic the wind model
-  proposed by S10 for $z \sim 3$ Lyman break galaxies.  These models
-  predict substantial line-emission from scattered photons that
-  greatly modify the predicted line-profiles so that  
-  these models do not reproduce the observed line-profiles.
+  proposed by \cite{steidel10} for $z \sim 3$ Lyman break galaxies.  Our
+  implementation of this model genreates substantial line-emission
+  from scattered photons that greatly modifies the predicted
+  line-profiles so that this model does not reproduce the observed
+  line-profiles.
 
@@
 
-We acknowledge valuable conversations with D. Koo, J. Hennawi, and
-A. Wolfe. 
+We acknowledge valuable conversations with D. Koo, J. Hennawi,
+A. Coil, and A. Wolfe. 
 J.X.P and K.R. are partially supported
@@
 \begin{figure}
-\epsscale{0.95}
-\plotone{../Figures/energy_levels.ps}
+%\epsscale{0.95}
+%\plotone{../Figures/energy_levels.ps}
+\includegraphics[width=6in]{f1.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/oneline_test.eps}
+%\epsscale{0.8}
+%\plotone{../Figures/oneline_test.eps}
+\includegraphics[width=6in]{f2.eps}
 \caption{
@@
 The configuration was  spherical and consisted of a homologously expanding wind  with density profile $n \propto r^{-2}$  lying above an opaque emitting surface at velocity coordinate 100~km~s$^{-1}$.
-The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and $\tau = 100$ (blue lines).
-Discrepancies in the $\tau = 100$ case are likely due to the breakdown of the Sobolev approximation at high optical depth.
+The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth
+had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and
+$\tau = 100$ (blue lines).    Discrepancies in the $\tau = 100$ case
+are likely due to the breakdown of the Sobolev approximation
+($\S$~\ref{sec:Sobolev}) at high optical depth. 
 }
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_nvtau_vs_r.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_nvtau_vs_r.ps}
+\includegraphics[width=5in]{f3.eps}
 \caption{
@@
 the opacity at small and discrete radial intervals in velocity space
-and then converting to radius with the velocity law.  These give
+and then converting to radius with the velocity law (doted black
+curve).  These give
 very similar results. 
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
+\includegraphics[scale=0.6,angle=90]{f4.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_noemiss.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_noemiss.ps}
+\includegraphics[width=5.5in]{f5.eps}
 \caption{
@@
 the predicted absorption profile under the constraint that every
-absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission occurs.   The true profiles have been `filled-in' 
+absorbed photon is lost from the system (referred to as the
+intrinsic profile), i.e.\ no scattering or
+re-emission occurs.   The intrinsic profiles have been `filled-in' 
 significantly with photons scattered by the wind into our sightline.  Ignoring this
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
+\includegraphics[width=6in]{f6.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_feii_ifu.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_feii_ifu.ps}
+\includegraphics[width=5.5in]{f7.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_asymm_spec.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_asymm_spec.ps}
+\includegraphics[width=5.5in]{f8.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_dust_spec.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_asymm_spec.ps}
+\includegraphics[width=5.5in]{f9.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+case (black lines) compared against a biconical wind with varying
+opening angle ($\theta_b = 0^\circ$ is a full wind).  For modest angles, one
+observes similar results to the fiducial model but larger angles
+($\theta_b > 45^\circ$) the emission is significantly suppressed at
+all velocities.  
+}
+\label{fig:biconical}
+\end{figure}
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_dust_spec.ps}
+\includegraphics[width=5.5in]{f10.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_taud_vs_we.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_taud_vs_we.ps}
+\includegraphics[width=5.5in]{f11.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.7}
-\plotone{../Figures/fig_ism_spec.ps}
+%\epsscale{0.7}
+%\plotone{../Figures/fig_ism_spec.ps}
+\includegraphics[width=5in]{f12.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_norm_spec.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_norm_spec.ps}
+\includegraphics[width=5.5in]{f13.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_sobolev.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_lbg_sobolev.ps}
+\includegraphics[width=5.5in]{f14.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_spec.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_lbg_spec.ps}
+\includegraphics[width=5.5in]{f15.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
+\includegraphics[scale=0.6,angle=90]{f16.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_rad_spec.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_rad_spec.ps}
+\includegraphics[width=5.5in]{f17.eps}
 \caption{
@@
 \begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_vary_profiles.ps}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_vary_profiles.ps}
+\includegraphics[width=5.5in]{f18.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
+\includegraphics[scale=0.6,angle=90]{f19.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
+\includegraphics[scale=0.6,angle=90]{f20.eps}
 \caption{
@@
 8$\,kpc), and the
-radiation-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
+radiation-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = 40$kpc) has blue curves.
 For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
+\includegraphics[scale=0.6,angle=90]{f21.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
+\includegraphics[scale=0.6,angle=90]{f22.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
+\includegraphics[scale=0.6,angle=90]{f23.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
+\includegraphics[scale=0.6,angle=90]{f24.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
+\includegraphics[scale=0.6,angle=90]{f25.eps}
 \caption{
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
+\includegraphics[scale=0.6,angle=90]{f26.eps}
 \caption{

### 2010-11-17 Winds/papers/Theory/First/Submit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5416 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 fluorescent photons to generate 1D spectra and 2D spectral images.
-{\bf [Should we make the codes publicly available?  Upon request?]}
+%{\bf [Should we make the codes publicly available?  Upon request?]}
 %We examine outflows with a range of power-law density and velocity
@@
 
-In a resonant line interaction, a photon excites an atom from the ground state to an excited level.
-The end result is either scattering (i.e., de-excitation back to the ground state) or fluorescence (de-excitation to another excited  level).
-The probability that the atom de-excites to lower level $x$ is  $p_{x} = A_{ux} / \sum_i A_{ui}$, where the $A_{ui}$ are the Einstein spontaneous emission coefficients and the sum runs over all levels accessible from the upper state $u$.
-For each interaction event, a random number was drawn to sample the final state from this probability distribution.
-If the result was a scattering, the process was assumed to be coherent in the comoving frame.
-If the result was fluorescence, the packet was  reemitted at the line center wavelength of the new transition.
-Natural line broadening in fluorescence was ignored given the high velocity gradients in our models.
-In all cases, the angular redistribution was  assumed to be isotropic.
+In a resonant line interaction, a photon excites an atom from the
+ground state to an excited level.  The end result is either scattering
+(i.e., de-excitation back to the ground state) or fluorescence
+(de-excitation to another excited  level).  The probability that the
+atom de-excites to lower level $x$ is  $p_{ux} = A_{ux} / \sum_i A_{ui}$, where the $A_{ui}$ are the Einstein spontaneous emission coefficients and the sum runs over all levels accessible from the upper state $u$.
+For each interaction event, a random number was drawn to sample the
+final state from this probability distribution.    If the result was a
+scattering, the process was assumed to be coherent in the comoving
+frame.  If the result was fluorescence, the packet was  reemitted at
+the line center wavelength of the new transition.  Natural line
+broadening in fluorescence was ignored given the high velocity
+gradients in our models.  In all cases, the angular redistribution was
+assumed to be isotropic.
 
@@
 Here
-$\tau_{ux}$ is the optical depth to infinity, which was  constructed  by integration along the path to escape, taking into account the relevant Doppler shifts and possible absorption by lines or dust.
-The contribution of the packet to the final spectrum was then added in for every possible final state, each shifted to the proper observer-frame wavelength and weighted by the probability $P_x$.
-
-To validate the monte carlo code, we calculated a series of test problems consisting of a point source embedded in a spherical, homogenous medium of varying resonant line optical depth.
-The resulting resonant line profiles  \citep[see][]{Kasen_lyman} were
+$\tau_{ux}$ is the optical depth to infinity, which was  constructed
+by integration along the path to escape, taking into account the
+relevant Doppler shifts and possible absorption by lines or dust.  The
+contribution of the packet to the final spectrum was then added in for
+every possible final state, each shifted to the proper observer-frame
+wavelength and weighted by the probability $P_x$.
+
+To validate the monte carlo code, we calculated a series of test
+problems consisting of a point source embedded in a spherical,
+homogenous medium of varying resonant line optical depth.  The
+resulting resonant line profiles  \citep[see][]{Kasen_lyman} were 
 found to be in good agreement with the standard analytic solutions
@@
 to $\phi = 180^\circ$ (source covered); and 
-(ii) a bi-conical wind where the density is set to zero for angles
-$|\theta| < \theta_b$ and that is viewed along the axis of rotational
-symmetry ($\theta = 90^\circ$ is defined to be along our sightline).
+(ii) a bi-conical wind which fills 
+$|\theta| < \theta_b$ into and out of the plane of the sky and that is
+viewed along the axis of rotational symmetry ($\theta = 0^\circ$ is
+defined to be along this axis)..
 
@@
 
-We have also analyzed the predicted profiles for a series of biconical
-winds with $\theta = 10-60^\circ$, each viewed along the axis of
+We have also analyzed the predicted profiles for a series of bi-conical
+winds with $\theta_b = 30-80^\circ$, each viewed along the axis of
 rotational asymmetry with the wind covering the
@@
 Table~\ref{tab:line_diag} summarizes the results for several cases.  For
-$\theta_b = 10^\circ$, the results are
+$\theta_b = 80^\circ$, the results are
 very similar to the fiducial model;  the profiles show
@@
 wind with that projected velocity has been removed.  For
-$\theta_b>45^\circ$, enough of the wind has been removed that the
+more highly collimated winds
+$\theta_b<45^\circ$, however, the
 line-emission is several times weaker than the fiducial model.
@@
 intrinsic optical depth of the outflow.   Of course, these same models
-when viewed `sideways' would show no absorption yet significant
+when viewed `sideways' would show no absorption but strong
 line-emission.  Such events are sufficiently rare (Rubin et
@@
 shadow a significant fraction of the backside).  
-Similarly, a biconical
+Similarly, a bi-conical
 wind can have significantly lower line-emission for the fiducial model
@@
 which has the most strongly affected transitions, \ewabs\ is reduced by
-$30-50\%$ from the intrinsic equivalent width.  In turn, one may derive 
+$30-50\%$ from the intrinsic equivalent width (the equivalent width
+one would measure in the absence of scattered photons).  In turn, one may derive 
 a systematically lower optical depth or velocity extent for the wind,
@@
   \ion{Na}{1}),  this implies much lower, absorption-line equivalent widths (by up to
-  $50\%$) and also velocity profiles that are significantly offset
+  $50\%$) and observed absorption profiles that are significantly offset in velocity
   from the intrinsic optical depth profile.
@@
   models where resonance photons are trapped for only a few scatterings.  Models
-  with high opacity at small radii and at systemic velocity (e.g.\
-  with an
+  with high opacity at small radii and at systemic velocity (e.g.\ with an
   optically thick, ISM component)  can effectively extinguish
@@
 \item We examined two scenarios designed to mimic the wind model
-  proposed by \cite{steidel10} for $z \sim 3$ Lyman break galaxies.  Our
+  proposed by \cite{steidel+10} for $z \sim 3$ Lyman break galaxies.  Our
   implementation of this model genreates substantial line-emission
@@
 Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-case (black lines) compared against a biconical wind with varying
+case (black lines) compared against a bi-conical wind with varying
 opening angle ($\theta_b = 0^\circ$ is a full wind).  For modest angles, one
@@
 longer wavelengths and do not `fill-in' the absorption profiles.
+The figure shows results for all of the models presented in
+Tables~\ref{tab:line_diag} and \ref{tab:plaw_diag}.
 }

### 2010-11-18 Winds/papers/Theory/First/Submit/ms.tex
blah
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5418 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 the systemic velocity.  This line-emission `fills-in' the absorption
-reducing the equivalent width by up to $50\%$, shifting the centroid
-by tens of \kms, and severely
-reducing the effective
+reducing the equivalent width by up to $50\%$, shift the
+absorption-lin centroid by tens of \kms, and 
+reduce the effective
 opacity near systemic.  Analysis of cool gas outflows that ignores this
@@
 We also study a scenario promoted to describe the outflows
-of $z \sim 3$ Lyman break galaxies and argue this model fails to
-reproduce the observations when radiative transfer of scattered photons
-is properly considered.   
+of $z \sim 3$ Lyman break galaxies and 
+find prfiles inconsistent with the observations due to scattered
+photon emission.
+%argue this model fails to
+%reproduce the observations when radiative transfer of scattered photons
+%is properly considered.   
 %Strong line-emission from metal-line
@@
 We consider two simple examples: (i) half the fiducial model, where 
-the density is set to zero for $2\pi$ steradians.  This model is
+the wind density is set to zero for $2\pi$ steradians.  This model is
 viewed from $\phi = 0^\circ$ (source uncovered) 
@@
 (ii) a bi-conical wind which fills 
-$|\theta| < \theta_b$ into and out of the plane of the sky and that is
+$|\theta| < \theta_b$ both into and out of the plane of the sky and that is
 viewed along the axis of rotational symmetry ($\theta = 0^\circ$ is
-defined to be along this axis)..
+defined along this axis).
 
@@
 quantitative difference is that the \feiis\ line-emission is
-suppressed at $\delta v \approx 0 \mkms$ because the portion of the
+modestly suppressed at $\delta v \approx 0 \mkms$ because the portion of the
 wind with that projected velocity has been removed.  For
@@
 al., in prep) that we consider this level of anisotropy to be
-uncommon.
+uncommon.  Nevertheless, the results for a bi-conic clearly have
+important implications for the nature of absorption and line-emission
+in our fiducial model.
 
@@
 Their wind model is defined by two
-expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
+expressions: (i) a radial velocity law $\mvr(r)$; and (ii) the covering
 fraction of optically thick `clouds' $f_c(r)$.  For the latter, S10
@@
 a diffuse medium with a declining density profile but a unit covering
-fraction.  One may question, therefore,  whether the differences
+fraction.  One may question, therefore,  whether these differences
 lead to the failures of the LBG-Sobolev model.
@@
   cb58, attributing this flux to stellar winds.  We caution, however,
-  that the galactic-scale wind proposed to exist for cb58 should also
+  that the galactic-scale wind proposed for cb58 should also
   have contributed to the \ion{C}{4} line-emission.}, and many
@@
 trapped, they require only one to a few scatterings
-to escape the wind which limits the effects of
+to escape the wind thereby limiting the effects of
 dust.  This reflects the moderate opacity of the \ion{Mg}{2}
@@
 it generally has only a modest effect on the predicted \ion{Mg}{2}
-emission and a relatively minor effect on \feiis\ emission.
+emission and a minor effect on \feiis\ emission.
 
@@
 Similarly, a bi-conical
-wind can have significantly lower line-emission for the fiducial model
-($\S$~\ref{sec:anisotropic}). 
+wind can have significantly lower line-emission, at 
+least for the fiducial model ($\S$~\ref{sec:anisotropic}). 
 For the anisotropic winds explored in this paper,
@@
 effects may explain the absence of significant line-emission,
-but they would generally
-not be sufficient to preclude detection.
+but they may not be sufficient to preclude its detection.
 
@@
 modify the observed absorption profiles (e.g.\
-Figure~\ref{fig:noemiss}) and may lead to erroneous conclusions
+Figure~\ref{fig:noemiss}) and may complicate conclusions
 regarding characteristics of the flow.  {\it An analysis of cool gas outflows
@@
 measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and %would 
-may 
-falsely conclude that the source is partially covered. 
+may incorrectly conclude that the source is partially covered. 
 In the case of \ion{Fe}{2}, one may even observe a (non-physical)
@@
 the gas.  Analysis of these lines, without consideration of
-line-emission, would lead to incorrect conclusions on the energetics
+line-emission, may lead to incorrect conclusions on the energetics
 and mass flux of the wind.
@@
 
-The previous few paragraphs sound a cautionary and largely negative
+The previous few paragraphs sounded a cautionary 
 perspective on the implications for absorption-line analysis of
 galactic-scale outflows in the presence of (expected) significant
-line-emission.   While this is a necessary complication, direct analysis of
-the line-emission does offer new and unique
+line-emission.   While this is a necessary complication, 
+we emphasize that such analysis remains one of the few observational
+techniques at our disposal to study outflows.  Furthermore,
+direct analysis of
+the line-emission offers new and unique
 constraints on the characteristics of the outflow.  And, when coupled
@@
 
-The most obvious %measures provided 
-characteristics probed 
-by the line-emission are
-%estimates
-%of 
+The most obvious characteristics probed by the line-emission are
 the size and morphology of the outflow \citep{rubin+10c}.  
@@
 optical depth exceeds a few tenths.  The principle
-challenge is to achieve sufficient sensitivity to detect the predicted
-low
-surface brightness emission. As Figure~\ref{fig:obs_sb}
+challenge is to achieve sufficient sensitivity to detect the
+predicted,
+low surface-brightness emission. As Figure~\ref{fig:obs_sb}
 demonstrates, the surface brightness at the inner wind radius of our
@@
 emission-line profiles of a set of simple galactic-scale outflow
-models.  {\bf [Add what is new, e.g. Monte Carlo radiative transfer]}
-Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
-multiplet of rest-frame UV transitions, but the results transfer to
+models.  This analysis implemented Monte Carlo radiative transfer
+techniques to propogate resonant photons through an expanding medium,
+allowing for their conversion to non-resonant photons (e.g.\ \feiis).
+Our work focused on the \mgiid\ and \ion{Fe}{2} UV1
+multiplet of rest-frame UV transitions, but the results apply to
 most other lines used to probe cool gas.  Our primary
@@
   observed in star-forming galaxies are predicted to be accompanied by
-  emission-lines with similar equivalent width.  This even holds for
+  emission-lines with similar equivalent width.  This holds even for
   non-extreme anisotropic and dust-extincted scenarios.
@@
   absorption lines offer the best
-  characterization of the opacity of the wind and also of material 
+  characterization of the opacity of the wind and also of gas 
   with velocities near systemic.
@@
   optically thick, ISM component)  can effectively extinguish
-  resonantly trapped emission (\ion{Mg}{2}) but have more modest
+  resonantly trapped emission (\ion{Mg}{2}) but have weaker
   effect on non-resonant lines (\feiis).
@@
   speed, opacity, dust extinction, and morphology of the
-  wind.
+  wind.  When combined with absorption-line analysis, one may develop
+  yet tighter constraints on these characteristics.
 
@@
 %\bibliography{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati09}
-\bibliographystyle{/u/xavier/paper/Bibli/apj}
-\bibliography{/u/xavier/paper/Bibli/allrefs}
+%\bibliographystyle{/u/xavier/paper/Bibli/apj}
+%\bibliography{/u/xavier/paper/Bibli/allrefs}
+
+\begin{thebibliography}{74}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Aguirre} {et~al.}(2001){Aguirre}, {Hernquist}, {Schaye}, {Weinberg},
+  {Katz}, \& {Gardner}}]{ahs+01}
+{Aguirre}, A., {Hernquist}, L., {Schaye}, J., {Weinberg}, D.~H., {Katz}, N., \&
+  {Gardner}, J. 2001, \apj, 560, 599
+
+\bibitem[{{Alton} {et~al.}(1999){Alton}, {Davies}, \& {Bianchi}}]{adb99}
+{Alton}, P.~B., {Davies}, J.~I., \& {Bianchi}, S. 1999, \aap, 343, 51
+
+\bibitem[{{Charlot} \& {Fall}(2000)}]{cf00}
+{Charlot}, S., \& {Fall}, S.~M. 2000, \apj, 539, 718
+
+\bibitem[{{Chen} {et~al.}(2010){Chen}, {Tremonti}, {Heckman}, {Kauffmann},
+  {Weiner}, {Brinchmann}, \& {Wang}}]{cth+10}
+{Chen}, Y., {Tremonti}, C.~A., {Heckman}, T.~M., {Kauffmann}, G., {Weiner},
+  B.~J., {Brinchmann}, J., \& {Wang}, J. 2010, \aj, 140, 445
+
+\bibitem[{{Chevalier} \& {Clegg}(1985)}]{cc85}
+{Chevalier}, R.~A., \& {Clegg}, A.~W. 1985, \nat, 317, 44
+
+\bibitem[{{Dijkstra} {et~al.}(2006){Dijkstra}, {Haiman}, \&
+  {Spaans}}]{Dijkstra_2006}
+{Dijkstra}, M., {Haiman}, Z., \& {Spaans}, M. 2006, \apj, 649, 14
+
+\bibitem[{{France} {et~al.}(2010){France}, {Nell}, {Green}, \&
+  {Leitherer}}]{france10}
+{France}, K., {Nell}, N., {Green}, J.~C., \& {Leitherer}, C. 2010, \apjl, 722,
+  L80
+
+\bibitem[{{Fujita} {et~al.}(2009){Fujita}, {Martin}, {Mac Low}, {New}, \&
+  {Weaver}}]{fmm+09}
+{Fujita}, A., {Martin}, C.~L., {Mac Low}, M., {New}, K.~C.~B., \& {Weaver}, R.
+  2009, \apj, 698, 693
+
+\bibitem[{{Hamann} {et~al.}(2010){Hamann}, {Kanekar}, {Prochaska}, {Murphy},
+  {Ellison}, {Malec}, {Milutinovic}, \& {Ubachs}}]{hkp+10}
+{Hamann}, F., {Kanekar}, N., {Prochaska}, J.~X., {Murphy}, M.~T., {Ellison},
+  S., {Malec}, A.~L., {Milutinovic}, N., \& {Ubachs}, W. 2010, ArXiv e-prints
+
+\bibitem[{{Harrington}(1973)}]{Harrington_1973}
+{Harrington}, J.~P. 1973, \mnras, 162, 43
+
+\bibitem[{{Hartigan} {et~al.}(1999){Hartigan}, {Morse}, {Tumlinson}, {Raymond},
+  \& {Heathcote}}]{hmt+99}
+{Hartigan}, P., {Morse}, J.~A., {Tumlinson}, J., {Raymond}, J., \& {Heathcote},
+  S. 1999, \apj, 512, 901
+
+\bibitem[{{Heckman} {et~al.}(1990){Heckman}, {Armus}, \& {Miley}}]{ham90}
+{Heckman}, T.~M., {Armus}, L., \& {Miley}, G.~K. 1990, \apjs, 74, 833
+
+\bibitem[{{Hughes} {et~al.}(1990){Hughes}, {Robson}, \& {Gear}}]{hrg90}
+{Hughes}, D.~H., {Robson}, E.~I., \& {Gear}, W.~K. 1990, \mnras, 244, 759
+
+\bibitem[{{Jeffery} \& {Branch}(1990)}]{Jeffery_Branch}
+{Jeffery}, D.~J., \& {Branch}, D. 1990, in Supernovae, Jerusalem Winter School
+  for Theoretical Physics, ed. {J.~C.~Wheeler, T.~Piran, \& S.~Weinberg},
+  149--+
+
+\bibitem[{{Kasen} {et~al.}(2002){Kasen}, {Branch}, {Baron}, \&
+  {Jeffery}}]{Kasen_2002}
+{Kasen}, D., {Branch}, D., {Baron}, E., \& {Jeffery}, D. 2002, \apj, 565, 380
+
+\bibitem[{{Kasen} {et~al.}(2006){Kasen}, {Thomas}, \& {Nugent}}]{Kasen_2006}
+{Kasen}, D., {Thomas}, R.~C., \& {Nugent}, P. 2006, \apj, 651, 366
+
+\bibitem[{{Kasen} \& {Woosley}(2007)}]{kw07}
+{Kasen}, D., \& {Woosley}, S.~E. 2007, \apj, 656, 661
+
+\bibitem[{{Kasen} \& {Woosley}(2009)}]{kw09}
+---. 2009, \apj, 703, 2205
+
+\bibitem[{{Kasen} {et~al.}(2010)}]{Kasen_lyman}
+{Kasen}, D., {et~al.} 2010, ApJ in preparation
+
+\bibitem[{{Kere{\v s}} {et~al.}(2009){Kere{\v s}}, {Katz}, {Dav{\'e}},
+  {Fardal}, \& {Weinberg}}]{kkd+09}
+{Kere{\v s}}, D., {Katz}, N., {Dav{\'e}}, R., {Fardal}, M., \& {Weinberg},
+  D.~H. 2009, \mnras, 396, 2332
+
+\bibitem[{{Kinney} {et~al.}(1993){Kinney}, {Bohlin}, {Calzetti}, {Panagia}, \&
+  {Wyse}}]{kbc+93}
+{Kinney}, A.~L., {Bohlin}, R.~C., {Calzetti}, D., {Panagia}, N., \& {Wyse},
+  R.~F.~G. 1993, \apjs, 86, 5
+
+\bibitem[{{Kobulnicky} \& {Martin}(2010)}]{km10}
+{Kobulnicky}, H.~A., \& {Martin}, C.~L. 2010, \apj, 718, 724
+
+\bibitem[{{Kurucz}(2005)}]{kurucz05}
+{Kurucz}, R.~L. 2005, Memorie della Societa Astronomica Italiana Supplementi,
+  8, 14
+
+\bibitem[{{Laursen} {et~al.}(2009){Laursen}, {Razoumov}, \&
+  {Sommer-Larsen}}]{Laursen_2009}
+{Laursen}, P., {Razoumov}, A.~O., \& {Sommer-Larsen}, J. 2009, \apj, 696, 853
+
+\bibitem[{{Lehnert} {et~al.}(1999){Lehnert}, {Heckman}, \& {Weaver}}]{lhw99}
+{Lehnert}, M.~D., {Heckman}, T.~M., \& {Weaver}, K.~A. 1999, \apj, 523, 575
+
+\bibitem[{{Lowenthal} {et~al.}(1997){Lowenthal}, {Koo}, {Guzman}, {Gallego},
+  {Phillips}, {Faber}, {Vogt}, {Illingworth}, \& {Gronwall}}]{lkg+97}
+{Lowenthal}, J.~D., {et~al.} 1997, \apj, 481, 673
+
+\bibitem[{{Martin}(1999)}]{martin99}
+{Martin}, C.~L. 1999, \apj, 513, 156
+
+\bibitem[{{Martin}(2005)}]{martin05}
+---. 2005, \apj, 621, 227
+
+\bibitem[{{Martin} \& {Bouch{\'e}}(2009)}]{mb09}
+{Martin}, C.~L., \& {Bouch{\'e}}, N. 2009, \apj, 703, 1394
+
+\bibitem[{{M{\'e}nard} {et~al.}(2008){M{\'e}nard}, {Nestor}, {Turnshek},
+  {Quider}, {Richards}, {Chelouche}, \& {Rao}}]{mnt+08}
+{M{\'e}nard}, B., {Nestor}, D., {Turnshek}, D., {Quider}, A., {Richards}, G.,
+  {Chelouche}, D., \& {Rao}, S. 2008, \mnras, 385, 1053
+
+\bibitem[{{M{\'e}nard} {et~al.}(2010){M{\'e}nard}, {Scranton}, {Fukugita}, \&
+  {Richards}}]{msf+10}
+{M{\'e}nard}, B., {Scranton}, R., {Fukugita}, M., \& {Richards}, G. 2010,
+  \mnras, 405, 1025
+
+\bibitem[{{Morton}(2003)}]{morton03}
+{Morton}, D.~C. 2003, \apjs, 149, 205
+
+\bibitem[{{Murray} {et~al.}(2010){Murray}, {M{\'e}nard}, \& {Thompson}}]{mmt10}
+{Murray}, N., {M{\'e}nard}, B., \& {Thompson}, T.~A. 2010, ArXiv e-prints
+
+\bibitem[{{Murray} {et~al.}(2005){Murray}, {Quataert}, \& {Thompson}}]{mqt05}
+{Murray}, N., {Quataert}, E., \& {Thompson}, T.~A. 2005, \apj, 618, 569
+
+\bibitem[{{Neufeld}(1990)}]{Neufeld_1990}
+{Neufeld}, D.~A. 1990, \apj, 350, 216
+
+\bibitem[{{Nulsen} {et~al.}(1998){Nulsen}, {Barcons}, \& {Fabian}}]{nbf98}
+{Nulsen}, P.~E.~J., {Barcons}, X., \& {Fabian}, A.~C. 1998, \mnras, 301, 168
+
+\bibitem[{{Oppenheimer} \& {Dav{\'e}}(2006)}]{od06}
+{Oppenheimer}, B.~D., \& {Dav{\'e}}, R. 2006, \mnras, 373, 1265
+
+\bibitem[{{Pettini} {et~al.}(1998){Pettini}, {Kellogg}, {Steidel}, {Dickinson},
+  {Adelberger}, \& {Giavalisco}}]{pks+98}
+{Pettini}, M., {Kellogg}, M., {Steidel}, C.~C., {Dickinson}, M., {Adelberger},
+  K.~L., \& {Giavalisco}, M. 1998, \apj, 508, 539
+
+\bibitem[{{Pettini} {et~al.}(2002){Pettini}, {Rix}, {Steidel}, {Adelberger},
+  {Hunt}, \& {Shapley}}]{prs+02}
+{Pettini}, M., {Rix}, S.~A., {Steidel}, C.~C., {Adelberger}, K.~L., {Hunt},
+  M.~P., \& {Shapley}, A.~E. 2002, \apj, 569, 742
+
+\bibitem[{{Pettini} {et~al.}(2000){Pettini}, {Steidel}, {Adelberger},
+  {Dickinson}, \& {Giavalisco}}]{psa+00}
+{Pettini}, M., {Steidel}, C.~C., {Adelberger}, K.~L., {Dickinson}, M., \&
+  {Giavalisco}, M. 2000, \apj, 528, 96
+
+\bibitem[{{Phillips}(1993)}]{phillips93}
+{Phillips}, A.~C. 1993, \aj, 105, 486
+
+\bibitem[{{Prochaska} {et~al.}(2006){Prochaska}, {Chen}, \& {Bloom}}]{pcb06}
+{Prochaska}, J.~X., {Chen}, H.-W., \& {Bloom}, J.~S. 2006, \apj, 648, 95
+
+\bibitem[{{Prochaska} {et~al.}(2007){Prochaska}, {Chen}, {Dessauges-Zavadsky},
+  \& {Bloom}}]{pcd+07}
+{Prochaska}, J.~X., {Chen}, H.-W., {Dessauges-Zavadsky}, M., \& {Bloom}, J.~S.
+  2007, \apj, 666, 267
+
+\bibitem[{{Prochaska} \& {Wolfe}(2001)}]{pw01}
+{Prochaska}, J.~X., \& {Wolfe}, A.~M. 2001, \apjl, 560, L33
+
+\bibitem[{{Radovich} {et~al.}(2001){Radovich}, {Kahanp{\"a}{\"a}}, \&
+  {Lemke}}]{rkl01}
+{Radovich}, M., {Kahanp{\"a}{\"a}}, J., \& {Lemke}, D. 2001, \aap, 377, 73
+
+\bibitem[{{Rubin} {et~al.}(2010{\natexlab{a}}){Rubin}, {Prochaska},
+  {M{\'e}nard}, {Murray}, {Kasen}, {Koo}, \& {Phillips}}]{rubin+10c}
+{Rubin}, K.~H.~R., {Prochaska}, J.~X., {M{\'e}nard}, B., {Murray}, N., {Kasen},
+  D., {Koo}, D.~C., \& {Phillips}, A.~C. 2010{\natexlab{a}}, ArXiv e-prints
+
+\bibitem[{{Rubin} {et~al.}(2010{\natexlab{b}}){Rubin}, {Weiner}, {Koo},
+  {Martin}, {Prochaska}, {Coil}, \& {Newman}}]{rwk+10}
+{Rubin}, K.~H.~R., {Weiner}, B.~J., {Koo}, D.~C., {Martin}, C.~L., {Prochaska},
+  J.~X., {Coil}, A.~L., \& {Newman}, J.~A. 2010{\natexlab{b}}, \apj, 719, 1503
+
+\bibitem[{{Rupke} {et~al.}(2005{\natexlab{a}}){Rupke}, {Veilleux}, \&
+  {Sanders}}]{rvs05a}
+{Rupke}, D.~S., {Veilleux}, S., \& {Sanders}, D.~B. 2005{\natexlab{a}}, \apjs,
+  160, 87
+
+\bibitem[{{Rupke} {et~al.}(2005{\natexlab{b}}){Rupke}, {Veilleux}, \&
+  {Sanders}}]{rvs05b}
+---. 2005{\natexlab{b}}, \apjs, 160, 115
+
+\bibitem[{{Sato} {et~al.}(2009){Sato}, {Martin}, {Noeske}, {Koo}, \&
+  {Lotz}}]{smn+09}
+{Sato}, T., {Martin}, C.~L., {Noeske}, K.~G., {Koo}, D.~C., \& {Lotz}, J.~M.
+  2009, \apj, 696, 214
+
+\bibitem[{{Savage} \& {Sembach}(1996)}]{ss96}
+{Savage}, B.~D., \& {Sembach}, K.~R. 1996, \araa, 34, 279
+
+\bibitem[{{Scannapieco} {et~al.}(2006){Scannapieco}, {Pichon}, {Aracil},
+  {Petitjean}, {Thacker}, {Pogosyan}, {Bergeron}, \& {Couchman}}]{spa+06}
+{Scannapieco}, E., {Pichon}, C., {Aracil}, B., {Petitjean}, P., {Thacker},
+  R.~J., {Pogosyan}, D., {Bergeron}, J., \& {Couchman}, H.~M.~P. 2006, \mnras,
+  365, 615
+
+\bibitem[{{Schaye}(2001)}]{schaye01a}
+{Schaye}, J. 2001, \apjl, 559, L1
+
+\bibitem[{{Shapley} {et~al.}(2003){Shapley}, {Steidel}, {Pettini}, \&
+  {Adelberger}}]{shapley03}
+{Shapley}, A.~E., {Steidel}, C.~C., {Pettini}, M., \& {Adelberger}, K.~L. 2003,
+  \apj, 588, 65
+
+\bibitem[{{Silva} \& {Viegas}(2002)}]{silva02}
+{Silva}, A.~I., \& {Viegas}, S.~M. 2002, \mnras, 329, 135
+
+\bibitem[{{Simcoe} {et~al.}(2002){Simcoe}, {Sargent}, \& {Rauch}}]{ssr02}
+{Simcoe}, R.~A., {Sargent}, W.~L.~W., \& {Rauch}, M. 2002, \apj, 578, 737
+
+\bibitem[{{Snow} {et~al.}(1994){Snow}, {Lamers}, {Lindholm}, \&
+  {Odell}}]{sll+94}
+{Snow}, T.~P., {Lamers}, H.~J.~G.~L.~M., {Lindholm}, D.~M., \& {Odell}, A.~P.
+  1994, \apjs, 95, 163
+
+\bibitem[{{Sobolev}(1960)}]{sobolev60}
+{Sobolev}, V.~V. 1960, {Moving envelopes of stars}
+
+\bibitem[{{Socrates} {et~al.}(2008){Socrates}, {Davis}, \&
+  {Ramirez-Ruiz}}]{sdr08}
+{Socrates}, A., {Davis}, S.~W., \& {Ramirez-Ruiz}, E. 2008, \apj, 687, 202
+
+\bibitem[{{Somerville} {et~al.}(2001){Somerville}, {Primack}, \&
+  {Faber}}]{spf01}
+{Somerville}, R.~S., {Primack}, J.~R., \& {Faber}, S.~M. 2001, \mnras, 320, 504
+
+\bibitem[{{Steidel} {et~al.}(2010){Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}, \& {Rakic}}]{steidel+10}
+{Steidel}, C.~C., {Erb}, D.~K., {Shapley}, A.~E., {Pettini}, M., {Reddy}, N.,
+  {Bogosavljevi{\'c}}, M., {Rudie}, G.~C., \& {Rakic}, O. 2010, \apj, 717, 289
+
+\bibitem[{{Steidel} {et~al.}(1996){Steidel}, {Giavalisco}, {Pettini},
+  {Dickinson}, \& {Adelberger}}]{sgp+96}
+{Steidel}, C.~C., {Giavalisco}, M., {Pettini}, M., {Dickinson}, M., \&
+  {Adelberger}, K.~L. 1996, \apjl, 462, L17+
+
+\bibitem[{{Strickland} \& {Heckman}(2009)}]{sh09}
+{Strickland}, D.~K., \& {Heckman}, T.~M. 2009, \apj, 697, 2030
+
+\bibitem[{{Strickland} {et~al.}(2004){Strickland}, {Heckman}, {Colbert},
+  {Hoopes}, \& {Weaver}}]{shc+04}
+{Strickland}, D.~K., {Heckman}, T.~M., {Colbert}, E.~J.~M., {Hoopes}, C.~G., \&
+  {Weaver}, K.~A. 2004, \apj, 606, 829
+
+\bibitem[{{Swinbank} {et~al.}(2005){Swinbank}, {Smail}, {Bower}, {Borys},
+  {Chapman}, {Blain}, {Ivison}, {Howat}, {Keel}, \& {Bunker}}]{ssb+05}
+{Swinbank}, A.~M., {et~al.} 2005, \mnras, 359, 401
+
+\bibitem[{{Tasitsiomi}(2006)}]{Tomi_2006}
+{Tasitsiomi}, A. 2006, \apj, 645, 792
+
+\bibitem[{{Tremonti} {et~al.}(2007){Tremonti}, {Moustakas}, \&
+  {Diamond-Stanic}}]{tmd07}
+{Tremonti}, C.~A., {Moustakas}, J., \& {Diamond-Stanic}, A.~M. 2007, \apjl,
+  663, L77
+
+\bibitem[{{Veilleux} {et~al.}(2003){Veilleux}, {Shopbell}, {Rupke},
+  {Bland-Hawthorn}, \& {Cecil}}]{vsr+03}
+{Veilleux}, S., {Shopbell}, P.~L., {Rupke}, D.~S., {Bland-Hawthorn}, J., \&
+  {Cecil}, G. 2003, \aj, 126, 2185
+
+\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
+  {Maselli}}]{Verhame_2006}
+{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
+
+\bibitem[{{Walter} {et~al.}(2002){Walter}, {Weiss}, \& {Scoville}}]{wws02}
+{Walter}, F., {Weiss}, A., \& {Scoville}, N. 2002, \apjl, 580, L21
+
+\bibitem[{{Weiner} {et~al.}(2009){Weiner}, {Coil}, {Prochaska}, {Newman},
+  {Cooper}, {Bundy}, {Conselice}, {Dutton}, {Faber}, {Koo}, {Lotz}, {Rieke}, \&
+  {Rubin}}]{wcp+09}
+{Weiner}, B.~J., {et~al.} 2009, \apj, 692, 187
+
+\bibitem[{{Westmoquette} {et~al.}(2008){Westmoquette}, {Smith}, \&
+  {Gallagher}}]{wsg08}
+{Westmoquette}, M.~S., {Smith}, L.~J., \& {Gallagher}, J.~S. 2008, \mnras, 383,
+  864
+
+\bibitem[{{York} {et~al.}(2006){York}, {Khare}, {Vanden Berk}, {Kulkarni},
+  {Crotts}, {Lauroesch}, {Richards}, {Schneider}, {Welty}, {Alsayyad}, {Kumar},
+  {Lundgren}, {Shanidze}, {Smith}, {Vanlandingham}, {Baugher}, {Hall},
+  {Jenkins}, {Menard}, {Rao}, {Tumlinson}, {Turnshek}, {Yip}, \&
+  {Brinkmann}}]{ykv+06}
+{York}, D.~G., {et~al.} 2006, \mnras, 367, 945
+
+\bibitem[{{Zheng} \& {Miralda-Escud{\'e}}(2002)}]{Zheng_2002}
+{Zheng}, Z., \& {Miralda-Escud{\'e}}, J. 2002, \apj, 578, 33
+
+\end{thebibliography}
 
@@
 
-\input{../Tables/table_atomic.tex}
-\input{../Tables/tab_fiducial.tex}
-\input{../Tables/tab_fiducial_ew.tex}
-\input{../Tables/tab_meas_models.tex}
-\input{../Tables/tab_plaw_parm.tex}
-\input{../Tables/tab_meas_plaws.tex}
+%\input{../Tables/table_atomic.tex}
+%\input{../Tables/tab_fiducial.tex}
+%\input{../Tables/tab_fiducial_ew.tex}
+%\input{../Tables/tab_meas_models.tex}
+%\input{../Tables/tab_plaw_parm.tex}
+%\input{../Tables/tab_meas_plaws.tex}
+
+\begin{deluxetable}{lcccccc}
+\tabletypesize{\footnotesize}
+\tablecolumns{11}
+\tablecaption{\ion{Mg}{2} and \ion{Fe}{2} Transitions Considered \label{tab:atomic}}
+\tablewidth{0pt}
+\tablehead{\colhead{} & \colhead{$\rm E_{high}$} & \colhead{$\rm E_{low}$} & \colhead{$J_{\rm high}$} & \colhead{$J_{\rm low}$} & \colhead{$\lambda$} & \colhead{$A$} \\
+ & \colhead{($\rm cm^{-1}$)} & \colhead{($\rm cm^{-1}$)} &&& \colhead{(\AA)} & \colhead{($\rm s^{-1}$)} } 
+\startdata
+\ion{Fe}{2} UV1 & 38458.98 &     0.00 &   9/2 & 9/2 & 2600.173 &
+2.36E+08  \\
+           & 38458.98 &   384.79 &   9/2 & 7/2 & 2626.451 & 3.41E+07 \\
+           & 38660.04 &     0.00 &   7/2 & 9/2 & 2586.650 & 8.61E+07 \\
+           & 38660.04 &   384.79 &   7/2 & 7/2 & 2612.654 & 1.23E+08 \\
+           & 38660.04 &   667.68 &   7/2 & 5/2 & 2632.108 & 6.21E+07 \\
+           & 38858.96 &   667.68 &   5/2 & 5/2 & 2618.399 & 4.91E+07 \\
+           & 38858.96 &   862.62 &   5/2 & 3/2 & 2631.832 & 8.39E+07 \\
+\tableline \\ [-1.5ex]
+\ion{Mg}{2}& 35760.89 &     0.00 &   3/2 &   0 & 2796.351 & 2.63E+08\\
+           & 35669.34 &     0.00 &   1/2 &   0 & 2803.528 & 2.60E+08\\
+\enddata
+\tablecomments{Atomic data from \citet{morton03}.}
+\end{deluxetable}
+
+\begin{deluxetable}{ccl}
+\tablewidth{0pc}
+\tablecaption{Wind Parameters: Fiducial Model\label{tab:fiducial}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Property} & \colhead{Parameter} & \colhead{Value} } 
+\startdata
+Density law  & $n(r)$ & $\propto r^{-2}$ \\
+Velocity law  & $v_r$ & $ \propto r$ \\
+Inner Radius & $r_{\rm inner}$ & 1\,kpc \\
+Outer Radius & $r_{\rm outer}$ & 20\,kpc \\
+Source size  & $r_{\rm source}$ & 0.5\,kpc \\
+Density Normalization & $n^0_{\rm H}$ & $0.1\cm{-3}$ at $r_{\rm inner}$ \\
+Velocity Normalization & $v_0$ & 1000\kms at $r_{\rm outer}$ \\
+Turbulence   & $b_{\rm turb}$  & 15 \kms \\
+Mg$^+$ Normalization & \nmg\ & $10^{-5.47} n_{\rm H}$ \\
+Fe$^+$ Normalization & \nfe\ & \nmg/2 \\
+\enddata
+%\tablecomments{Unless specified otherwise, all quantities refer to the \sna=2 threshold.  The cosmology assumed has $\Omega_\Lambda = 0.7, \Omega_m = 0.3$, and $H_0 = 72 \mkms \rm Mpc^{-1}$.}
+%\tablenotetext{a}{Total redshift survey path for the \sna=2 criterion.}
+
+\end{deluxetable}
+
+\begin{deluxetable}{ccr}
+\tablewidth{0pc}
+\tablecaption{Equivalent Widths for the Fiducial Model\label{tab:fiducial_EW}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Transition} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\lambda}^b$} \\ 
+& (\kms) & (\AA) }
+\startdata
+  MgII 2796  &[$-1030,-65$]& 2.96\\
+&[$-65,311$]&$-1.75$\\
+  MgII 2803  &[$-458,-57$]& 1.29\\
+&[$-57,692$]&$-2.34$\\
+  FeII 2586  &[$-365,-46$]& 0.59\\
+&[$-46,186$]&$-0.10$\\
+  FeII 2600  &[$-626,-78$]& 1.16\\
+&[$-49,470$]&$-0.94$\\
+  FeII* 2612 &[$-219,183$]&$-0.33$\\
+  FeII* 2626 &[$-194,177$]&$-0.27$\\
+  FeII* 2632 &[$-155,130$]&$-0.16$\\
+\enddata
+\tablenotetext{a}{Velocity interval over which the equivalent width is calculated.}
+\tablenotetext{b}{Negative values indicate line-emission.}
+\end{deluxetable}
+
+\begin{deluxetable}{ccrccccccccccc}
+\rotate
+\tablewidth{0pc}
+\tablecaption{Line Diagnostics for the Fiducial Model and Variants
+\label{tab:line_diag}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Transition} & \colhead{Model} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\rm i}$} & \colhead{$W_{\rm a}$} & \colhead{$\tau_{\rm pk}$} & \colhead{$v_\tau$} 
+& \colhead{$v_{\bar \tau}$}
+& \colhead{$v_{\rm int}^e$} & \colhead{$W_{\rm e}$} & \colhead{$f_{\rm pk}$} & \colhead{$v_f$} 
+& \colhead{$v_{\bar f}$} & \colhead{$\Delta v_{\rm e}$}
+\\
+&& (\kms) & (\AA) & (\AA) && (\kms) & (\kms) & (\kms) & (\AA) & & (\kms) & (\kms) & (\kms)}
+\startdata
+  MgII 2796  \\
+&Fiducial&[$-1009,-43$]& 4.78& 2.83&0.94&$ -215$&$ -372$&[$-32,311$]&$-1.77$& 2.48&$   32$&$  117$& 215\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-145,606$]&$-2.34$& 2.10&$   70$&$  208$& 483\\
+&$\phi=180^\circ$&[$-1030,-65$]& 4.78& 2.98&1.03&$ -199$&$ -369$&[$-65,70$]&$-0.51$& 1.78&$  -11$&$    6$& 107\\
+&$\theta_b=80^\circ$&[$-1030,-65$]& 4.78& 3.55&0.91&$ -306$&$ -442$&[$-65,257$]&$-1.03$& 1.78&$   43$&$   93$& 215\\
+&$\theta_b=45^\circ$&[$-1003,-11$]& 4.78& 4.79&2.19&$  -91$&$ -332$&[$16,96$]&$-0.04$& 1.07&$   43$&$   55$&  54\\
+&\taud=1&[$-1009,-32$]& 4.77& 2.94&0.95&$ -215$&$ -360$&[$-32,257$]&$-0.95$& 1.90&$   32$&$  101$& 193\\
+&\taud=3&[$-998,-32$]& 4.78& 3.07&1.03&$ -193$&$ -342$&[$-22,182$]&$-0.40$& 1.48&$   43$&$   76$& 150\\
+&ISM&[$-1009,-65$]& 6.36& 2.67&0.90&$ -204$&$ -390$&[$-54,311$]&$-1.60$& 2.36&$  118$&$  125$& 236\\
+&ISM+dust&[$-998,150$]& 6.42& 4.06&1.06&$ -193$&$ -270$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+  MgII 2803  \\
+&Fiducial&[$-437,-41$]& 3.29& 1.19&0.76&$ -148$&$ -193$&[$-41,676$]&$-2.24$& 2.55&$   34$&$  269$& 449\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-84,665$]&$-1.86$& 1.93&$   77$&$  257$& 482\\
+&$\phi=180^\circ$&[$-538,-57$]& 3.29& 1.82&0.97&$ -137$&$ -232$&[$-57,104$]&$-0.59$& 1.81&$   -3$&$   22$& 107\\
+&$\theta_b=80^\circ$&[$-485,-57$]& 3.29& 1.33&0.65&$ -217$&$ -237$&[$-57,746$]&$-2.30$& 2.12&$   23$&$  303$& 535\\
+&$\theta_b=45^\circ$&[$-538,-57$]& 3.29& 2.60&1.74&$  -84$&$ -217$&[$-30,692$]&$-0.72$& 1.33&$   23$&$  320$& 562\\
+&\taud=1&[$-479,-41$]& 3.28& 1.41&0.83&$ -137$&$ -195$&[$-41,591$]&$-1.30$& 1.95&$   34$&$  247$& 417\\
+&\taud=3&[$-533,-30$]& 3.26& 1.67&0.94&$ -116$&$ -195$&[$-30,484$]&$-0.66$& 1.50&$   34$&$  213$& 375\\
+&ISM&[$-426,-62$]& 6.49& 1.03&0.67&$ -169$&$ -206$&[$-51,655$]&$-2.09$& 2.57&$   98$&$  265$& 439\\
+&ISM+dust&[$-554,130$]& 6.51& 2.59&1.02&$ -137$&$ -143$&[$173,195$]&$-0.01$& 1.03&$  184$&$  184$&  21\\
+  FeII 2586  \\
+&Fiducial&[$-348,-35$]& 0.82& 0.61&1.01&$  -70$&$ -119$&[$-35,128$]&$-0.10$& 1.11&$   35$&$   47$& 128\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-104,186$]&$-0.10$& 1.06&$   70$&$   41$& 232\\
+&$\phi=180^\circ$&[$-365,-46$]& 0.82& 0.60&1.01&$  -75$&$ -133$&[$-46,70$]&$-0.03$& 1.06&$  -17$&$   12$&  87\\
+&$\theta_b=80^\circ$&[$-481,-46$]& 0.82& 0.96&1.57&$  -75$&$ -148$&[$-46,186$]&$-0.10$& 1.09&$   41$&$   71$& 203\\
+&$\theta_b=45^\circ$&[$-481,-46$]& 0.82& 1.03&1.88&$  -75$&$ -143$&[$41,99$]&$-0.02$& 1.03&$   41$&$   69$&  58\\
+&\taud=1&[$-348,-35$]& 0.82& 0.61&1.04&$  -70$&$ -118$&[$-35,116$]&$-0.05$& 1.06&$   23$&$   41$& 116\\
+&\taud=3&[$-313,-35$]& 0.94& 0.60&1.06&$  -70$&$ -113$&[$-23,46$]&$-0.02$& 1.04&$  -12$&$   12$&  58\\
+&ISM&[$-348,104$]& 1.90& 1.60&2.75&$    0$&$  -29$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+&ISM+dust&[$-313,116$]& 1.84& 1.63&2.96&$   23$&$  -25$&[$278,290$]&$-0.00$& 1.03&$  278$&$  284$&  12\\
+  FeII 2600  \\
+&Fiducial&[$-580,-37$]& 1.87& 1.18&1.08&$  -83$&$ -181$&[$-37,459$]&$-0.83$& 1.70&$   32$&$  191$& 312\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-135,442$]&$-0.78$& 1.46&$   67$&$  144$& 346\\
+&$\phi=180^\circ$&[$-597,-49$]& 1.87& 1.18&1.31&$  -78$&$ -188$&[$-49,95$]&$-0.25$& 1.39&$  -20$&$   22$&  87\\
+&$\theta_b=80^\circ$&[$-856,-49$]& 1.87& 1.72&1.07&$ -106$&$ -249$&[$-49,557$]&$-0.77$& 1.49&$   38$&$  241$& 404\\
+&$\theta_b=45^\circ$&[$-856,-49$]& 1.87& 2.12&2.71&$  -78$&$ -204$&[$-20,413$]&$-0.24$& 1.15&$   38$&$  194$& 346\\
+&\taud=1&[$-591,-37$]& 1.87& 1.20&1.14&$  -83$&$ -176$&[$-37,332$]&$-0.50$& 1.45&$   32$&$  138$& 265\\
+&\taud=3&[$-580,-37$]& 1.95& 1.25&1.31&$  -72$&$ -169$&[$-37,228$]&$-0.23$& 1.22&$   44$&$   93$& 196\\
+&ISM&[$-568,90$]& 3.12& 1.88&1.19&$  -72$&$  -99$&[$101,378$]&$-0.19$& 1.15&$  113$&$  237$& 242\\
+&ISM+dust&[$-603,101$]& 3.06& 2.12&1.40&$   44$&$  -93$&[$182,194$]&$-0.00$& 1.02&$  182$&$  188$&  12\\
+  FeII* 2612 \\
+&Fiducial&&&&&&&[$-173,183$]&$-0.34$& 1.24&$  -23$&$    5$& 241\\
+&$\phi=0^\circ$&&&&&&&[$-46,183$]&$-0.16$& 1.22&$   11$&$   67$& 172\\
+&$\phi=180^\circ$&&&&&&&[$-190,68$]&$-0.16$& 1.21&$  -46$&$  -61$& 172\\
+&$\theta_b=80^\circ$&&&&&&&[$-276,241$]&$-0.46$& 1.29&$  -46$&$  -17$& 316\\
+&$\theta_b=45^\circ$&&&&&&&[$-18,155$]&$-0.07$& 1.10&$   40$&$   68$& 144\\
+&\taud=1&&&&&&&[$-173,114$]&$-0.23$& 1.21&$  -46$&$  -28$& 207\\
+&\taud=3&&&&&&&[$-150,91$]&$-0.14$& 1.16&$  -46$&$  -30$& 184\\
+&ISM&&&&&&&[$-184,160$]&$-1.10$& 2.66&$    0$&$   -9$& 138\\
+&ISM+dust&&&&&&&[$-138,137$]&$-0.45$& 1.53&$    0$&$   -1$& 161\\
+  FeII* 2626 \\
+&Fiducial&&&&&&&[$-171,183$]&$-0.39$& 1.29&$  -46$&$    5$& 217\\
+&$\phi=0^\circ$&&&&&&&[$-52,177$]&$-0.13$& 1.16&$   34$&$   62$& 171\\
+&$\phi=180^\circ$&&&&&&&[$-194,63$]&$-0.13$& 1.16&$  -52$&$  -66$& 143\\
+&$\theta_b=80^\circ$&&&&&&&[$-280,234$]&$-0.58$& 1.41&$  -52$&$  -22$& 314\\
+&$\theta_b=45^\circ$&&&&&&&[$6,148$]&$-0.08$& 1.14&$   34$&$   76$& 114\\
+&\taud=1&&&&&&&[$-160,126$]&$-0.25$& 1.23&$  -46$&$  -17$& 194\\
+&\taud=3&&&&&&&[$-171,68$]&$-0.14$& 1.17&$  -46$&$  -51$& 194\\
+&ISM&&&&&&&[$-194,194$]&$-1.76$& 4.10&$    0$&$    0$& 103\\
+&ISM+dust&&&&&&&[$-160,114$]&$-0.47$& 1.70&$    0$&$  -21$& 137\\
+  FeII* 2632 \\
+&Fiducial&&&&&&&[$-132,119$]&$-0.16$& 1.12&$   16$&$   -6$& 194\\
+&$\phi=0^\circ$&&&&&&&[$-41,130$]&$-0.08$& 1.09&$   45$&$   44$& 142\\
+&$\phi=180^\circ$&&&&&&&[$-155,16$]&$-0.08$& 1.11&$  -41$&$  -69$& 142\\
+&$\theta_b=80^\circ$&&&&&&&[$-212,159$]&$-0.23$& 1.14&$   16$&$  -26$& 285\\
+&$\theta_b=45^\circ$&&&&&&&[$-639,102$]&$-0.18$& 1.14&$ -611$&$ -271$& 684\\
+&\taud=1&&&&&&&[$-121,85$]&$-0.11$& 1.10&$  -52$&$  -18$& 160\\
+&\taud=3&&&&&&&[$-98,16$]&$-0.05$& 1.08&$  -41$&$  -41$& 103\\
+&ISM&&&&&&&[$-121,130$]&$-0.55$& 1.81&$    5$&$    4$& 137\\
+&ISM+dust&&&&&&&[$-121,107$]&$-0.22$& 1.30&$    5$&$   -6$& 148\\
+\enddata
+\tablecomments{{L}isted are the equivalent widths (intrinsic, absorption, and emission), the peak optical depth for the absorption
+$\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the velocity where the optical depth peaks $v_\tau$, the optical depth-weighted velocity centroid 
+$v_{\bar \tau} \equiv \int dv \, v \ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in emission, the velocity where the flux peaks 
+$v_f$, the flux-weighted velocity centroid of the emission line $v_{\bar f}$ (occasionally affected by blends with neighboring emission lines), and the $90\%$ width $\Delta v_{\rm e}$.
+The $v^a_{\rm int}$ and $v^e_{\rm int}$ columns give the velocity range used to calculate the absorption and emission characteristics, respecitvely.
+These were defined by the velcoities where the profile crossed 0.95 in the normalized flux.}
+\end{deluxetable}
+
+\begin{deluxetable}{cccccc}
+\tablewidth{0pc}
+\tablecaption{Wind Parameters: Power-law Models\label{tab:plaw_parm}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Label} & \colhead{$n(r)$} & \colhead{$n_{\rm
+      H}^0$} & \colhead{$v(r)$} & \colhead{$v^0$} &
+  \colhead{$\log \tau_{2796}^{\rm max}$} }
+\startdata
+A & $r^{-3}$& 0.4000 & $r^{-2.0}$&   2.0 & 0.8 \\ 
+B & $r^{-3}$& 0.5000 & $r^{-1.0}$&  50.0 & 1.1 \\ 
+C & $r^{-3}$& 0.3000 & $r^{ 0.5}$& 100.0 & 1.8 \\ 
+D & $r^{ 0}$& 0.0100 & $r^{-2.0}$&   2.0 & 2.1 \\ 
+E & $r^{ 0}$& 0.0100 & $r^{-1.0}$&  50.0 & 1.7 \\ 
+F & $r^{ 0}$& 0.0200 & $r^{ 0.5}$& 100.0 & 1.6 \\ 
+G & $r^{ 2}$& 0.0100 & $r^{-2.0}$&   2.0 & 4.4 \\ 
+H & $r^{ 2}$& 0.0010 & $r^{-1.0}$&  50.0 & 3.2 \\ 
+I & $r^{ 2}$& 0.0001 & $r^{ 0.5}$& 100.0 & 1.8 \\ 
+\enddata
+\tablecomments{For velocity laws that decrease with radius, the
+normalization $v^0$ refers to the velocity at $r=r_{\rm outer}$
+instead of $r=r_{\rm inner}$.  All models assume a Doppler parameter
+$b=15\mkms$, full isotropy, and a dust-free environment.}
+
+\end{deluxetable}
+
+\begin{deluxetable}{ccrccccccccccc}
+\rotate
+\tablewidth{0pc}
+\tablecaption{Line Diagnostics for the Fiducial Model and Variants
+\label{tab:plaw_diag}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Transition} & \colhead{Model} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\rm i}$} & \colhead{$W_{\rm a}$} & \colhead{$\tau_{\rm pk}$} & \colhead{$v_\tau$} 
+& \colhead{$v_{\bar \tau}$}
+& \colhead{$v_{\rm int}^e$} & \colhead{$W_{\rm e}$} & \colhead{$f_{\rm pk}$} & \colhead{$v_f$} 
+& \colhead{$v_{\bar f}$} & \colhead{$\Delta v_{\rm e}$}
+\\
+&& (\kms) & (\AA) & (\AA) && (\kms) & (\kms) & (\kms) & (\AA) & & (\kms) & (\kms) & (\kms)}
+\startdata
+  MgII 2796  \\
+&Fiducial&[$-1009,-43$]& 4.78& 2.83&0.94&$ -215$&$ -372$&[$-32,311$]&$-1.77$& 2.48&$   32$&$  117$& 215\\
+&LBG Sobolev&[$-687,-86$]& 2.62& 1.35&0.45&$ -247$&$ -347$&[$-65,257$]&$-1.02$& 1.84&$   21$&$   90$& 193\\
+&LBG Covering&[$-698,-65$]& 2.67& 1.40&0.41&$ -258$&$ -344$&[$-54,214$]&$-0.93$& 2.23&$    0$&$   72$& 172\\
+&Radiation&[$-365,-65$]& 2.86& 1.72&3.00&$ -301$&$ -250$&[$-54,322$]&$-1.74$& 2.13&$   53$&$  119$& 236\\
+&A&[$-848,-22$]& 9.29& 5.02&2.92&$ -773$&$ -499$&[$-22,171$]&$-1.34$& 3.30&$   21$&$   64$& 118\\
+&B&[$-1084,-65$]&11.08& 7.54&3.00&$ -976$&$ -589$&[$-65,193$]&$-1.83$& 2.89&$    0$&$   50$& 172\\
+&C&[$-451,-65$]& 2.54& 1.82&1.86&$ -204$&$ -200$&[$-65,332$]&$-1.79$& 2.09&$    0$&$  116$& 247\\
+&D&[$-794,21$]& 4.21& 2.14&1.11&$  -11$&$ -276$&[$32,311$]&$-1.57$& 3.58&$   43$&$  141$& 172\\
+&E&[$-1009,-22$]& 6.37& 4.81&1.95&$ -183$&$ -343$&[$-22,279$]&$-3.23$& 3.59&$   43$&$  101$& 193\\
+&F&[$-622,-97$]& 4.10& 3.00&3.00&$ -451$&$ -336$&[$-86,289$]&$-2.60$& 2.19&$   64$&$   90$& 290\\
+&G&[$-794,118$]& 6.88& 2.81&3.00&$   11$&$ -165$&[$129,375$]&$-1.71$& 2.30&$  236$&$  248$& 150\\
+&H&[$-837,43$]& 5.94& 4.15&3.00&$  -32$&$ -205$&[$53,365$]&$-3.33$& 3.09&$  150$&$  190$& 204\\
+&I&[$-622,-172$]& 3.33& 2.53&3.00&$ -451$&$ -365$&[$-161,289$]&$-2.10$& 1.67&$   86$&$   62$& 343\\
+  MgII 2803  \\
+&Fiducial&[$-437,-41$]& 3.29& 1.19&0.76&$ -148$&$ -193$&[$-41,676$]&$-2.24$& 2.55&$   34$&$  269$& 449\\
+&LBG Sobolev&[$-426,-73$]& 1.53& 0.46&0.24&$ -244$&$ -244$&[$-62,387$]&$-0.80$& 1.58&$   23$&$  154$& 332\\
+&LBG Covering&[$-533,-73$]& 2.56& 0.98&0.37&$ -233$&$ -285$&[$-51,558$]&$-1.48$& 2.35&$    2$&$  227$& 396\\
+&Radiation&[$-362,-84$]& 2.32& 1.29&2.65&$ -308$&$ -256$&[$-73,323$]&$-1.31$& 1.86&$   45$&$  115$& 246\\
+&A&[$-554,-41$]& 7.06& 1.98&0.78&$ -330$&$ -293$&[$-41,805$]&$-5.72$& 5.03&$   13$&$  304$& 610\\
+&B&[$-554,-169$]& 5.74& 1.80&1.27&$ -372$&$ -359$&[$-84,1008$]&$-7.34$& 4.20&$    2$&$  338$& 749\\
+&C&[$-405,-73$]& 2.17& 1.49&1.85&$ -169$&$ -179$&[$-73,355$]&$-1.52$& 1.94&$   77$&$  122$& 246\\
+&D&[$-30,13$]& 3.69& 0.19&0.77&$   -9$&$   -1$&[$23,558$]&$-1.48$& 3.33&$   34$&$  251$& 332\\
+&E&[$-479,-30$]& 4.42& 2.40&1.70&$ -158$&$ -195$&[$-30,815$]&$-3.96$& 3.71&$   23$&$  302$& 428\\
+&F&[$-479,-94$]& 3.85& 2.59&2.50&$ -383$&$ -318$&[$-84,484$]&$-3.02$& 2.15&$   77$&$  163$& 385\\
+&G&[$-105,88$]& 9.09& 1.12&3.00&$   -9$&$   -2$&[$98,441$]&$-2.15$& 2.52&$  184$&$  250$& 235\\
+&H&[$-405,13$]& 6.43& 2.67&3.00&$  -30$&$ -143$&[$23,526$]&$-3.50$& 3.10&$  109$&$  228$& 300\\
+&I&[$-490,-191$]& 2.85& 1.96&2.35&$ -394$&$ -354$&[$-84,473$]&$-2.16$& 1.61&$   77$&$  174$& 417\\
+  FeII 2586  \\
+&Fiducial&[$-348,-35$]& 0.82& 0.61&1.01&$  -70$&$ -119$&[$-35,128$]&$-0.10$& 1.11&$   35$&$   47$& 128\\
+&LBG Sobolev&[$-151,-46$]& 0.18& 0.04&0.07&$ -139$&$  -99$&[$-12,35$]&$-0.01$& 1.05&$    0$&$   12$&  35\\
+&LBG Covering&[$-684,-12$]& 2.38& 1.93&0.65&$ -162$&$ -276$&[$-12,360$]&$-0.34$& 1.33&$   12$&$  170$& 313\\
+&Radiation&[$0,0$]& 1.00& 0.00&0.02&$    0$&$    0$&[$12,255$]&$-0.11$& 1.09&$   35$&$  132$& 220\\
+&A&[$-812,-12$]& 1.88& 1.66&0.33&$ -742$&$ -422$&[$-12,232$]&$-0.12$& 1.12&$   23$&$  109$& 197\\
+&B&[$-1009,-186$]& 2.20& 1.97&0.60&$ -951$&$ -694$&[$-93,418$]&$-0.24$& 1.09&$   12$&$  161$& 429\\
+&C&[$-278,-81$]& 0.79& 0.71&2.51&$ -116$&$ -132$&[$-70,162$]&$-0.10$& 1.08&$   93$&$   46$& 174\\
+&D&[$-209,23$]& 0.88& 0.68&3.00&$  -12$&$  -26$&[$35,70$]&$-0.01$& 1.03&$   46$&$   52$&  35\\
+&E&[$-476,-35$]& 1.33& 1.10&2.25&$  -70$&$ -129$&[$-23,174$]&$-0.12$& 1.13&$   23$&$   74$& 162\\
+&F&[$-476,-104$]& 2.24& 2.02&1.98&$ -418$&$ -318$&[$-93,371$]&$-0.34$& 1.14&$    0$&$  136$& 371\\
+&G&[$-464,406$]& 3.31& 3.24&3.00&$  -46$&$  -27$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+&H&[$-418,23$]& 2.13& 1.92&3.00&$  -46$&$ -112$&[$70,209$]&$-0.04$& 1.06&$  116$&$  139$& 116\\
+&I&[$-487,-220$]& 1.34& 1.26&3.00&$ -429$&$ -387$&[$-162,383$]&$-0.22$& 1.06&$    0$&$  110$& 464\\
+  FeII 2600  \\
+&Fiducial&[$-580,-37$]& 1.87& 1.18&1.08&$  -83$&$ -181$&[$-37,459$]&$-0.83$& 1.70&$   32$&$  191$& 312\\
+&LBG Sobolev&[$-453,-72$]& 0.55& 0.24&0.11&$ -187$&$ -263$&[$-26,228$]&$-0.21$& 1.23&$   20$&$   99$& 208\\
+&LBG Covering&[$-695,-60$]& 2.43& 1.38&0.44&$ -360$&$ -336$&[$-49,493$]&$-1.12$& 2.02&$    9$&$  203$& 381\\
+&Radiation&[$-360,-26$]& 2.21& 1.44&3.00&$ -303$&$ -247$&[$-26,320$]&$-0.84$& 1.59&$   44$&$  138$& 242\\
+&A&[$-822,-26$]& 4.61& 3.51&1.05&$ -753$&$ -455$&[$-26,793$]&$-1.78$& 2.34&$    9$&$  347$& 612\\
+&B&[$-1018,-199$]& 5.10& 4.20&1.88&$ -960$&$ -701$&[$-176,1001$]&$-2.84$& 1.86&$   -3$&$  371$& 935\\
+&C&[$-360,-72$]& 1.34& 1.09&2.04&$ -141$&$ -154$&[$-72,228$]&$-0.62$& 1.43&$   78$&$   75$& 219\\
+&D&[$-430,20$]& 1.68& 1.13&3.00&$  -14$&$  -58$&[$32,309$]&$-0.31$& 1.47&$   44$&$  163$& 219\\
+&E&[$-787,-37$]& 2.68& 2.16&3.00&$  -72$&$ -183$&[$-37,493$]&$-1.16$& 1.84&$    9$&$  205$& 346\\
+&F&[$-510,-106$]& 3.22& 2.65&3.00&$ -430$&$ -320$&[$-95,459$]&$-1.67$& 1.65&$   67$&$  159$& 381\\
+&G&[$-603,274$]& 4.81& 3.66&3.00&$  -14$&$  -55$&[$447,493$]&$-0.02$& 1.07&$  459$&$  470$&  35\\
+&H&[$-556,20$]& 3.27& 2.61&3.00&$  -49$&$ -138$&[$32,470$]&$-0.83$& 1.56&$  113$&$  234$& 300\\
+&I&[$-522,-210$]& 2.06& 1.79&3.00&$ -430$&$ -373$&[$-187,436$]&$-1.16$& 1.30&$  147$&$  118$& 473\\
+  FeII* 2612 \\
+&Fiducial&&&&&&&[$-173,183$]&$-0.34$& 1.24&$  -23$&$    5$& 241\\
+&LBG Sobolev&&&&&&&[$-69,57$]&$-0.04$& 1.07&$    0$&$   -6$& 115\\
+&LBG Covering&&&&&&&[$-356,436$]&$-1.04$& 1.79&$    0$&$   35$& 563\\
+&Radiation&&&&&&&[$-299,298$]&$-0.50$& 1.26&$    0$&$   -1$& 425\\
+&A&&&&&&&[$-402,574$]&$-0.88$& 1.35&$    0$&$   80$& 735\\
+&B&&&&&&&[$-402,597$]&$-0.88$& 1.14&$   34$&$   94$& 873\\
+&C&&&&&&&[$-184,172$]&$-0.40$& 1.20&$  -81$&$   -6$& 241\\
+&D&&&&&&&[$-115,114$]&$-0.47$& 2.37&$    0$&$   -1$& 103\\
+&E&&&&&&&[$-265,275$]&$-0.65$& 1.38&$   11$&$    5$& 310\\
+&F&&&&&&&[$-402,424$]&$-1.12$& 1.27&$   45$&$   10$& 597\\
+&G&&&&&&&[$-196,218$]&$-2.15$& 7.63&$    0$&$    7$& 126\\
+&H&&&&&&&[$-230,241$]&$-1.24$& 1.80&$  -12$&$    4$& 264\\
+&I&&&&&&&[$-402,424$]&$-0.70$& 1.13&$   34$&$   11$& 677\\
+  FeII* 2626 \\
+&Fiducial&&&&&&&[$-171,183$]&$-0.39$& 1.29&$  -46$&$    5$& 217\\
+&LBG Sobolev&&&&&&&[$-23,46$]&$-0.03$& 1.06&$   23$&$   11$&  57\\
+&LBG Covering&&&&&&&[$-251,274$]&$-0.28$& 1.22&$    0$&$   11$& 434\\
+&Radiation&&&&&&&[$-286,263$]&$-0.60$& 1.42&$    0$&$  -11$& 343\\
+&A&&&&&&&[$-663,320$]&$-1.60$& 1.71&$    0$&$ -152$& 720\\
+&B&&&&&&&[$-891,320$]&$-1.45$& 1.22&$    0$&$ -270$&1039\\
+&C&&&&&&&[$-171,160$]&$-0.46$& 1.24&$   57$&$   -5$& 217\\
+&D&&&&&&&[$-160,148$]&$-0.87$& 3.53&$    0$&$   -5$& 103\\
+&E&&&&&&&[$-251,240$]&$-0.96$& 1.58&$   23$&$   -5$& 263\\
+&F&&&&&&&[$-411,320$]&$-0.97$& 1.23&$    0$&$  -40$& 571\\
+&G&&&&&&&[$-229,228$]&$-3.69$&11.76&$    0$&$    0$& 126\\
+&H&&&&&&&[$-274,263$]&$-1.80$& 2.05&$  -12$&$   -4$& 263\\
+&I&&&&&&&[$-457,320$]&$-0.65$& 1.13&$  240$&$  -64$& 640\\
+  FeII* 2632 \\
+&Fiducial&&&&&&&[$-132,119$]&$-0.16$& 1.12&$   16$&$   -6$& 194\\
+&LBG Sobolev&&&&&&&[$-29,16$]&$-0.01$& 1.07&$   -7$&$   -7$&  46\\
+&LBG Covering&&&&&&&[$-292,301$]&$-0.53$& 1.36&$    5$&$    4$& 479\\
+&Radiation&&&&&&&[$-235,210$]&$-0.23$& 1.12&$    5$&$  -12$& 353\\
+&A&&&&&&&[$-326,370$]&$-0.59$& 1.19&$   -7$&$   15$& 581\\
+&B&&&&&&&[$-326,563$]&$-0.78$& 1.17&$ -314$&$  108$& 741\\
+&C&&&&&&&[$-143,153$]&$-0.19$& 1.10&$   62$&$    5$& 228\\
+&D&&&&&&&[$-86,96$]&$-0.23$& 1.63&$    5$&$    4$&  91\\
+&E&&&&&&&[$-212,187$]&$-0.32$& 1.19&$   28$&$  -12$& 262\\
+&F&&&&&&&[$-326,392$]&$-0.59$& 1.14&$   73$&$   30$& 581\\
+&G&&&&&&&[$-189,187$]&$-1.09$& 4.03&$    5$&$   -1$& 125\\
+&H&&&&&&&[$-212,221$]&$-0.63$& 1.41&$  -18$&$    4$& 251\\
+&I&&&&&&&[$-326,381$]&$-0.39$& 1.13&$ -326$&$   24$& 627\\
+\enddata
+\tablecomments{{L}isted are the equivalent widths (intrinsic, absorption, and emission), the peak optical depth for the absorption
+$\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the velocity where the optical depth peaks $v_\tau$, the optical depth-weighted velocity centroid 
+$v_{\bar \tau} \equiv \int dv \, v \ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in emission, the velocity where the flux peaks 
+$v_f$, the flux-weighted velocity centroid of the emission line $v_{\bar f}$ (occasionally affected by blends with neighboring emission lines), and the $90\%$ width $\Delta v_{\rm e}$.
+The $v^a_{\rm int}$ and $v^e_{\rm int}$ columns give the velocity range used to calculate the absorption and emission characteristics, respecitvely.
+These were defined by the velcoities where the profile crossed 0.95 in the normalized flux.}
+\end{deluxetable}
 

### 2011-02-04 Winds/papers/Theory/First/Resubmit/ms.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5618 ac11df5e-a788-c23b-a8e1-c758c323924d

--- 2010-11-18 Winds/papers/Theory/First/Submit/ms.tex
@@
 radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
-It follows a (mass-flux conserving) density law,
+%It follows a (mass-flux conserving) density law,
+It follows a density law,
 
@@
 In this respect, our LBG-Sobolev model is an
-inaccurate description of the observations. The model
+inaccurate description of the observations which show more uniform
+equivalent widths among differing transitions (S10). The model
 also predicts significant emission in the \ion{Mg}{2} lines and several of
@@
 More importantly, we question whether any physical process could
-produce a wind with such extreme properties.
+produce a wind with such extreme profiles.
 
@@
 analysis is that these simple models cannot reproduce the
-observed profiles of resonantly trapped lines like the \ion{Mg}{2}
-doublet because of the emission from scattered photons.  In order to
+observed profiles of resonantly trapped lines (like the \ion{Mg}{2}
+doublet) because of the emission from scattered photons.  
+In particular, the observations show much greater opacity at
+velocities within $\approx 100 \mkms$ of systemic (S10).
+In order to
 achieve a significant opacity at $\mdv \approx 0 \mkms$, one must
@@
 In fact, for clumps that are optically thick to strong metal-line
-transitions (e.g.\ \ion{Si}{2}~1526) we estimate that the wind would
-carry nearly a total mass of $\approx 10^{10} \msun$!  We question
-whether this is a plausible result from star-formation driven
-feedback.
+transitions (e.g.\ \ion{Si}{2}~1526) we estimate\footnote{Note that
+  this estimate differs from the LBG-Sobolev calculation shown in
+  Figure~\ref{fig:LBG_cumul} because the latter assumes a diffuse
+  medium with unit filling factor.}
+that the wind would
+carry nearly a total mass of $\approx 10^{10} \msun$, with the
+majority at large radii.
+%We question whether this is a plausible result from star-formation driven
+%feedback.
 
@@
 %\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
-\includegraphics[width=6in]{f6.eps}
+\includegraphics[width=5in]{f6.eps}
 \caption{
@@
 values.  
+The black (solid) curve shows the model results.
+The dashed (green) curve shows
+$W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0) \cdot \exp(-\tau_d)$.
 It is obvious that the equivalent widths (i.e., the flux relative to
-the continuum) do not scale as $\exp(\tau_d)$.
-The black (solid) curve shows the model results while the
-dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
-\cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
+the continuum) do not follow this scaling.
+The dotted (red) line, meanwhile, plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
+\cdot (1+\tau_d)^{-1}$. 
+This simple approximation is a good
 representation of the results for our radiative transfer calculations.   

### 2011-02-16 Winds/papers/Theory/First/Preprint/windsimple_prpt.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5644 ac11df5e-a788-c23b-a8e1-c758c323924d

--- 2010-10-12 Winds/papers/Theory/First/Submit/ms.tex
@@
-\documentclass[12pt,preprint]{aastex}
+\documentclass[]{emulateapj}
 \usepackage{natbib,amsmath}
@@
 \special{papersize=8.5in,11in}
+\shorttitle{Simple Models of Cool Gas Outflows} 
+\shortauthors{Prochaska, Kasen, \& Rubin}
+
 \begin{document}
@@
 galaxies at $z<1$.
-We also study a scenario purported to describe the outflows
-of $z \sim 3$ Lyman break galaxies and argue this model fails to
-reproduce the observations when radiative transfer of scattered photons
-is properly considered.   
+We also study a scenario promoted to describe the outflows
+of $z \sim 3$ Lyman break galaxies and 
+find prfiles inconsistent with the observations due to scattered
+photon emission.
+%argue this model fails to
+%reproduce the observations when radiative transfer of scattered photons
+%is properly considered.   
 %Strong line-emission from metal-line
@@
 spectacular jets of radio-loud AGN.   These gaseous outflows 
-%%KHRR
 regulate the metal and dust content and distribution within the 
-objects and its surroundings, 
-%%
+objects and their surroundings, 
 moderate the accretion of new material, and %onto the object, 
@@
 up to $\sim 10$ kpc
-%tens of kpc 
-from the galaxy \citep{lhw99,wsg08,vsr+03} carrying significant speed
+from the galaxy \citep{lhw99,vsr+03,wsg08} carrying significant speed
 to escape from the gravitational potential well of the galaxy's dark
@@
 tandem with the nearly ubiquitous blue-shifted absorption
-\citep{wcp+09,rwk+10,cth+10}.  The resultant spectra resemble the P-Cygni
+\citep{wcp+09,mb09,rwk+10,cth+10}.  The resultant spectra resemble the P-Cygni
 profile characteristic of stellar winds.
@@
 
+\begin{deluxetable}{lcccccc}
+\tabletypesize{\footnotesize}
+\tablecolumns{11}
+\tablecaption{\ion{Mg}{2} and \ion{Fe}{2} Transitions Considered \label{tab:atomic}}
+\tablewidth{0pt}
+\tablehead{\colhead{} & \colhead{$\rm E_{high}$} & \colhead{$\rm E_{low}$} & \colhead{$J_{\rm high}$} & \colhead{$J_{\rm low}$} & \colhead{$\lambda$} & \colhead{$A$} \\
+ & \colhead{($\rm cm^{-1}$)} & \colhead{($\rm cm^{-1}$)} &&& \colhead{(\AA)} & \colhead{($\rm s^{-1}$)} } 
+\startdata
+\ion{Fe}{2} UV1 & 38458.98 &     0.00 &   9/2 & 9/2 & 2600.173 &
+2.36E+08  \\
+           & 38458.98 &   384.79 &   9/2 & 7/2 & 2626.451 & 3.41E+07 \\
+           & 38660.04 &     0.00 &   7/2 & 9/2 & 2586.650 & 8.61E+07 \\
+           & 38660.04 &   384.79 &   7/2 & 7/2 & 2612.654 & 1.23E+08 \\
+           & 38660.04 &   667.68 &   7/2 & 5/2 & 2632.108 & 6.21E+07 \\
+           & 38858.96 &   667.68 &   5/2 & 5/2 & 2618.399 & 4.91E+07 \\
+           & 38858.96 &   862.62 &   5/2 & 3/2 & 2631.832 & 8.39E+07 \\
+\tableline \\ [-1.5ex]
+\ion{Mg}{2}& 35760.89 &     0.00 &   3/2 &   0 & 2796.351 & 2.63E+08\\
+           & 35669.34 &     0.00 &   1/2 &   0 & 2803.528 & 2.60E+08\\
+\enddata
+\tablecomments{Atomic data from \citet{morton03}.}
+\end{deluxetable}
+
+\begin{figure}
+%\epsscale{0.95}
+%\plotone{../Figures/energy_levels.ps}
+\includegraphics[width=3.5in]{f1.eps}
+\caption{
+Energy level diagrams for the \mgiid\ doublet and the UV1
+multiplet of \ion{Fe}{2} transitions   
+(based on Figure~7 from \cite{hmt+99}).
+Each transition shown is
+labeled by its rest wavelength (\AA) and Einstein A-coefficient
+(s$^{-1}$). Black upward arrows
+indicate the resonance-line transitions, i.e.\ those connected to the ground
+state.  The 2p$^6$3p configuration of Mg$^+$ is split into
+two energy levels that give rise to the \mgiid\ doublet.  
+Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
+exhibit fine-structure splitting that gives rise to a series of
+electric-dipole transitions. 
+The downward (green) arrows show the \feiis\ transitions that are connected to the
+resonance-line transitions (i.e.\ they share the same upper energy
+levels).  We also show a pair of transitions (\ion{Fe}{2}$^* \lambda\lambda
+2618,2631$; red and dashed lines) that arise from higher levels in the \zconfig\
+configuration.  These transitions have not yet been observed in
+galactic-scale outflows and are not considered in our analysis.
+}
+\label{fig:energy}
+\end{figure}
+
 \subsection{The Radiative Transitions}
@@
 Here
-$\tau_{ux}$ is the optical depth to infinity, which was  constructed  by integration along the path to escape, taking into account the relevant Doppler shifts and possible absorption by lines or dust.
-The contribution of the packet to the final spectrum was than added in for every possible final state, each shifted to the proper observer-frame wavelength and weighted by the probability $P_x$.
-
-To validate the monte carlo code, we calculated a series of test problems consisting of a point source embedded in a spherical, homogenous medium of varying resonant line optical depth.
-The resulting resonant line profiles  \citep[see][]{Kasen_lyman} were
+$\tau_{ux}$ is the optical depth to infinity, which was  constructed
+by integration along the path to escape, taking into account the
+relevant Doppler shifts and possible absorption by lines or dust.  The
+contribution of the packet to the final spectrum was then added in for
+every possible final state, each shifted to the proper observer-frame
+wavelength and weighted by the probability $P_x$.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/oneline_test.eps}
+\includegraphics[width=3.5in]{f2.eps}
+\caption{
+Line profiles of a test problem calculated using the monte carlo code (solid) and by direct numerical integration of the transport equation under the Sobolev approximation (dashed lines).
+The configuration was  spherical and consisted of a homologously expanding wind  with density profile $n \propto r^{-2}$  lying above an opaque emitting surface at velocity coordinate 100~km~s$^{-1}$.
+The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth
+had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and
+$\tau = 100$ (blue lines).    Discrepancies in the $\tau = 100$ case
+are likely due to the breakdown of the Sobolev approximation
+($\S$~\ref{sec:Sobolev}) at high optical depth. 
+}
+\label{fig:oneline_test}
+\end{figure}
+
+To validate the monte carlo code, we calculated a series of test
+problems consisting of a point source embedded in a spherical,
+homogenous medium of varying resonant line optical depth.  The
+resulting resonant line profiles  \citep[see][]{Kasen_lyman} were 
 found to be in good agreement with the standard analytic solutions
@@
 
+\begin{deluxetable}{ccl}
+\tablewidth{0pc}
+\tablecaption{Wind Parameters: Fiducial Model\label{tab:fiducial}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Property} & \colhead{Parameter} & \colhead{Value} } 
+\startdata
+Density law  & $n(r)$ & $\propto r^{-2}$ \\
+Velocity law  & $v_r$ & $ \propto r$ \\
+Inner Radius & $r_{\rm inner}$ & 1\,kpc \\
+Outer Radius & $r_{\rm outer}$ & 20\,kpc \\
+Source size  & $r_{\rm source}$ & 0.5\,kpc \\
+Density Normalization & $n^0_{\rm H}$ & $0.1\cm{-3}$ at $r_{\rm inner}$ \\
+Velocity Normalization & $v_0$ & 1000\kms at $r_{\rm outer}$ \\
+Turbulence   & $b_{\rm turb}$  & 15 \kms \\
+Mg$^+$ Normalization & \nmg\ & $10^{-5.47} n_{\rm H}$ \\
+Fe$^+$ Normalization & \nfe\ & \nmg/2 \\
+\enddata
+%\tablecomments{Unless specified otherwise, all quantities refer to the \sna=2 threshold.  The cosmology assumed has $\Omega_\Lambda = 0.7, \Omega_m = 0.3$, and $H_0 = 72 \mkms \rm Mpc^{-1}$.}
+%\tablenotetext{a}{Total redshift survey path for the \sna=2 criterion.}
+
+\end{deluxetable}
+
 In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
@@
 
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_nvtau_vs_r.ps}
+\includegraphics[height=3.5in,angle=90]{f3.eps}
+\caption{
+Density (dashed; red), radial velocity (dotted; blue), and
+\mgiia\ optical depth profiles (solid and dotted; black) for the fiducial
+wind model (see Table~\ref{tab:fiducial} for details).
+The density and velocity laws are simple $r^{-2}$ and $r^1$
+power-laws; these curves have been scaled for plotting
+convenience.  
+The optical depth profile was calculated two ways: (i) using the
+Sobolev approximation (Equation~\ref{eqn:Sobolev}; solid black curve)
+and (ii) summing
+the opacity at small and discrete radial intervals in velocity space
+and then converting to radius with the velocity law (doted black
+curve).  These give
+very similar results. 
+The wind parameters were set to give an optically thick medium at the
+inner radius ($r_{\rm inner} = 1$\,kpc) that becomes optically thin at
+the outer radius ($r_{\rm outer} = 20$\,kpc). 
+}
+\label{fig:fiducial_nvt}
+\end{figure}
+
+\begin{deluxetable}{ccr}
+\tablewidth{0pc}
+\tablecaption{Equivalent Widths for the Fiducial Model\label{tab:fiducial_EW}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Transition} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\lambda}^b$} \\ 
+& (\kms) & (\AA) }
+\startdata
+  MgII 2796  &[$-1030,-65$]& 2.96\\
+&[$-65,311$]&$-1.75$\\
+  MgII 2803  &[$-458,-57$]& 1.29\\
+&[$-57,692$]&$-2.34$\\
+  FeII 2586  &[$-365,-46$]& 0.59\\
+&[$-46,186$]&$-0.10$\\
+  FeII 2600  &[$-626,-78$]& 1.16\\
+&[$-49,470$]&$-0.94$\\
+  FeII* 2612 &[$-219,183$]&$-0.33$\\
+  FeII* 2626 &[$-194,177$]&$-0.27$\\
+  FeII* 2632 &[$-155,130$]&$-0.16$\\
+\enddata
+\tablenotetext{a}{Velocity interval over which the equivalent width is calculated.}
+\tablenotetext{b}{Negative values indicate line-emission.}
+\end{deluxetable}
+
+\begin{figure*}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
+\includegraphics[height=7.0in,angle=90]{f4.eps}
+\caption{
+{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
+described in Table~\ref{tab:fiducial} and
+Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
+characteristic of an outflow with significant absorption blueward of
+line-center (dashed vertical lines) extending to $v = -1000\mkms$
+and significant emission redward of line-center.  Note
+that even though the peak optical depth of the \ion{Mg}{2} transitions
+is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
+photons scattered off the outflow significantly fill-in the absorption.
+(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
+multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
+show weaker absorption due to the smaller Fe$^+$ number density and
+lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
+the emission for \feiia\ is much weaker than that for the
+\feiib\ and \mgiid\ transitions.  This is because a majority of the
+absorbed \feiia\ photons fluoresce into
+\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
+{\it Right} -- A subset of the transitions displayed in a velocity
+plot.
+}
+\label{fig:fiducial_1d}
+\end{figure*}
+
 Using the methodology described in $\S$~\ref{sec:method}, we
 propagated photons from the source and through the outflow to an
-`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
+`observer' at $r \gg r_{\rm outer}$ who views the entire wind+source
 complex.  Figure~\ref{fig:fiducial_1d} presents the 1D spectrum
@@
 source embedded within an outflow.  Strong absorption is evident at
-$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both transitions (equivalent widths, $W^{2796} =
-3.0$\AA\ and $W^{2803} = 1.3$\AA) and each shows emission at
+$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both
+transitions (with equivalent widths $W^{2796}_a =
+3.0$\AA\ and $W^{2803}_a = 1.3$\AA) and each shows emission at
 positive velocities.  For an isotropic and dust-free model, the
@@
 
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_noemiss.ps}
+\includegraphics[width=3.5in]{f5.eps}
+\caption{
+The solid curves show the line profiles (absorption and emission) of
+the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
+model.  These include the effects of scattered photons and show the
+canonical P-Cygni profiles of a source 
+embedded within an outflow.  Overplotted on each transition (dotted
+red line) is
+the predicted absorption profile under the constraint that every
+absorbed photon is lost from the system (referred to as the
+intrinsic profile), i.e.\ no scattering or
+re-emission occurs.   The intrinsic profiles have been `filled-in' 
+significantly with photons scattered by the wind into our sightline.  Ignoring this
+process, one would model the absorption lines with a systematically lower
+optical depth and/or (incorrectly) conclude that the source is partly covered by the
+gas.  
+}
+\label{fig:noemiss}
+\end{figure}
+
 Focusing further on the \ion{Mg}{2} absorption, one notes that the profiles lie
@@
 even though the line has a $2 \times$ lower $f\lambda$ value.
-These differences between the \ion{Fe}{2} resonance lines (and with the
-\ion{Mg}{2} doublet) occur because of the complex of non-resonant
+These differences between the \ion{Fe}{2} resonance lines (and between
+\ion{Fe}{2} and \ion{Mg}{2}) occur because of the complex of non-resonant
 \feiis\ transitions that are coupled to the resonance lines
 (Figure~\ref{fig:energy}).  Specifically, 
-resonance photons absorbed at \feiid\ have a finite probability of
+a resonance photon absorbed at \feiid\ has a finite probability of
 being re-emitted as a non-resonant photon which then escapes the system
@@
 
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
+\includegraphics[width=3.5in]{f6.eps}
+\caption{
+Surface-brightness emission maps around the \mgiia\ transition for the
+source+wind complex of the fiducial model.  The middle panel shows the
+1D spectrum with $v=0 
+\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
+curves indicate the velocity slices for the emission maps.  The
+source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
+pixels at the center of each map.   At $v=-250 \mkms$, the wind has an optical
+depth of $\tau_{2796} \approx 1$ and the source contributes
+roughly half of the observed flux.  At $v=-100 \mkms$ the
+wind absorbs all photons from the source and the observed emission is
+entirely due to photons scattered by the wind.  Amazingly, this
+emission exceeds the integrated flux at $v = -250\mkms$ such that the
+\mgiia\ line center is offset from the (intrinsic) peak in optical depth.  At $v \ge 0
+\mkms$,  both the source and wind contribute to the observed emission.
+At all velocities, the majority of emission comes from the inner
+$\approx 5$\,kpc.
+}
+\label{fig:fiducial_ifu_mgii}
+\end{figure}
+
 The preceding discussion emphasizes the filling-in of resonance
@@
 
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_feii_ifu.ps}
+\includegraphics[width=3.5in]{f7.eps}
+\caption{
+(Upper) Surface-brightness emission maps around the \feiib\ transition for the
+source+wind complex.  
+%The middle panel shows the 1D spectrum with $v=0
+%\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
+%curves indicating the velocity slices for the emission maps.  
+The results are very similar to those observed for the \mgiid\ doublet
+(Figure~\ref{fig:fiducial_ifu_mgii}).
+(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
+2612$ transition for the 
+source+wind complex.  %The middle panel shows the 1D spectrum with $v=0
+%\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
+%curves indicating the velocity slices for the emission maps.  
+In this case, the source is unattenuated yet scattered photons from
+the wind also make a significant contribution. 
+}
+\label{fig:fiducial_ifu_feii}
+\end{figure}
+
 Similar results are observed for the \ion{Fe}{2} resonance
@@
 $\S$~\ref{sec:discuss}.
+
+The results presented in Figures~\ref{fig:fiducial_ifu_mgii} and
+\ref{fig:fiducial_ifu_feii} are sensitive to the radial extent,
+morphology, density and velocity profiles of this galactic-scale
+wind.  Consequently, IFU observations of line emission from low-ion
+transitions may offer the most direct constraints on galactic-scale
+wind properties.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_asymm_spec.ps}
+\includegraphics[width=3.5in]{f8.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+case (black lines) compared against an anisotropic wind blowing into
+only $2\pi$ steradians as viewed from $\phi = 0^\circ$ (source
+uncovered) to $\phi = 180^\circ$ (source covered).  One detects
+significant emission for all orientations but significant
+absorption only for $\phi \ge 90^\circ$.
+The velocity centroid of the 
+emission shifts from positive to negative velocities as $\phi$
+increases and one transitions from viewing the wind as lying behind the
+source to in front of it.  The velocity centroid of emission, therefore,
+diagnoses the degree of anisotropy for the wind.
+}
+\label{fig:anisotropic}
+\end{figure}
 
@@
 We consider two simple examples: (i) half the fiducial model, where 
-the density is set to zero for $2\pi$ steradians.  This model is
+the wind density is set to zero for $2\pi$ steradians (i.e.\ a
+hemispherical wind).  This model is
 viewed from $\phi = 0^\circ$ (source uncovered) 
 to $\phi = 180^\circ$ (source covered); and 
-(ii) a bi-conical wind where the density is set to zero for angles
-$|\theta| < \theta_b$ and that is viewed along the plane of symmetry.
+(ii) a bi-conical wind which fills 
+$|\theta| < \theta_b$ both into and out of the plane of the sky and that is
+viewed along the axis of rotational symmetry ($\theta = 0^\circ$ is
+defined along this axis).
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_asymm_spec.ps}
+\includegraphics[width=3.5in]{f9.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+case (black lines) compared against a bi-conical wind with varying
+opening angle ($\theta_b = 0^\circ$ is a full wind).  For modest angles, one
+observes similar results to the fiducial model but larger angles
+($\theta_b > 45^\circ$) the emission is significantly suppressed at
+all velocities.  
+}
+\label{fig:biconical}
+\end{figure}
 
@@
 When viewed from the opposite direction ($\phi = 180^\circ$), the
-absorption lines dominate but there is still significant
-line-emission, at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
-in the absorption, from photons that scatter through the wind.  The
-key difference from the isotropic wind is the absence of photons
+absorption lines dominate, but there is still significant
+line-emission at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ 
+from photons that scatter through the wind
+which fills in the absorption. 
+The key difference between this and the isotropic wind is the absence of photons
 scattered to $\mdv > 100 \mkms$;  this also implies deeper 
 \mgiib\ absorption at $\mdv \approx -100 \mkms$. The 
-shift in velocity centroid and asymmetry of the emission lines
+shifts in velocity centroid and asymmetry of the emission lines
 serve to diagnose the degree of wind isotropy, especially in
@@
 
-We have also analyzed the predicted profiles for a series of biconical
-winds with $\theta = 10-60^\circ$, each viewed along the axis of
-asymmetry with the wind covering the source.
-Table~\ref{tab:line_diag} summarizes the results for two cases.  For
-modest opening angles $\theta < 20^\circ$, the results are
-qualitatively similar to the fiducial model;  the profiles show
+We have also analyzed the predicted profiles for a series of bi-conical
+winds with $\theta_b = 30-80^\circ$, each viewed along the axis of
+rotational asymmetry with the wind covering the
+source. Figure~\ref{fig:biconical} and
+Table~\ref{tab:line_diag} summarizes the results for several cases.  For
+$\theta_b = 80^\circ$, the results are
+very similar to the fiducial model;  the profiles show
 similar equivalent widths for absorption and emission.  The key
 quantitative difference is that the \feiis\ line-emission is
-suppressed at $\delta v \approx 0 \mkms$ because the portion of the
+modestly suppressed at $\delta v \approx 0 \mkms$ because the portion of the
 wind with that projected velocity has been removed.  For
-$\theta>45^\circ$, enough of the wind has been removed that the
+more highly collimated winds
+$\theta_b<45^\circ$, however, the
 line-emission is several times weaker than the fiducial model.
@@
 intrinsic optical depth of the outflow.   Of course, these same models
-when viewed `sideways' would show no absorption yet significant
+when viewed `sideways' would show no absorption but strong
 line-emission.  Such events are sufficiently rare (Rubin et
-al., in prep) that we consider this level of anisotropy to be of minor
-importance.
+al., in prep) that we consider this level of anisotropy to be
+uncommon.  Nevertheless, the results for a bi-conic clearly have
+important implications for the nature of absorption and line-emission
+in our fiducial model.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_dust_spec.ps}
+\includegraphics[width=3.5in]{f10.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
+model (black) compared against a series of models that include 
+dust extinction, parameterize by the integrated dust opacity from
+source to infinity (\taud).  The primary effect of dust is to suppress 
+the line-emission relative to the continuum. 
+A more subtle but important effect is that the redder photons in the
+emission lines (corresponding to positive velocity offsets relative to
+line-center) suffer greater extinction.  
+This occurs because the `redder' photons that we view have travelled 
+farther to scatter off the backside of the wind.  Note that
+the absorption lines are nearly unmodified until $\mtaud = 10$, a
+level of extinction that would preclude observing the source
+altogether.
+}
+\label{fig:dust}
+\end{figure}
 
@@
 distance to escape and therefore suffer from greater extinction.  A photon that is
-trapped for many scatterings may have a very high probability of being absorbed
+trapped for many scatterings %may have a very high 
+has an increased 
+probability of being absorbed
 by dust.  
-Section~\ref{sec:dust_method} describes the details on our treatment of dust; we 
+Section~\ref{sec:dust_method} describes the details of our treatment of dust; we 
 remind the reader here that we assume a constant dust-to-gas ratio 
 that is normalized by the total optical
-depth \taud\ a photon would experience if it traveled from the
+depth \taud\ photons would experience if they traveled from the
 source to infinity without scattering.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_taud_vs_we.ps}
+\includegraphics[height=3.5in,angle=90]{f11.eps}
+\caption{
+Predicted equivalent widths for \mgiib\ line-emission from the
+fiducial wind model, as attenuated by dust with a range of \taud\
+values.  
+The black (solid) curve shows the model results.
+The dashed (green) curve shows
+$W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0) \cdot \exp(-\tau_d)$.
+It is obvious that the equivalent widths (i.e., the flux relative to
+the continuum) do not follow this scaling.
+The dotted (red) line, meanwhile, plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
+\cdot (1+\tau_d)^{-1}$. 
+This simple approximation is a good
+representation of the results for our radiative transfer calculations.   
+}
+\label{fig:dust_tau}
+\end{figure}
 
@@
 
+\begin{figure}
+%\epsscale{0.7}
+%\plotone{../Figures/fig_ism_spec.ps}
+\includegraphics[width=3.5in]{f12.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
+model (red) compared against the fiducial wind model (black). 
+The dotted line traces the predicted absorption profile in the absence
+of re-emission and scattering.
+Regarding the \ion{Mg}{2}~doublet, the primary difference between the
+ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
+in the emission lines from $v \approx 0 \mkms$ for the fiducial
+model to $v \approx +100\mkms$ for the ISM+wind model. 
+The \ion{Fe}{2} profiles, meanwhile, show several qualitative differences. 
+The \feiid\ resonance transitions each exhibit much
+greater absorption at $v \approx 0 \mkms$ than the fiducial model.
+The resonant line-emission is also substantially
+reduced, implying much higher fluxes for the non-resonant lines (e.g.\
+\feiic,2626).  
+Lastly, we note that the \feiia\ absorption profile provides a good
+(albeit imperfect) representation of the wind opacity and therefore
+offers the best characterization of an ISM component.
+}
+\label{fig:ISM_spec}
+\end{figure}
+
 \subsection{ISM}
@@
 
+\begin{figure}[ht]
+%\epsscale{0.8}
+%\plotone{../Figures/fig_norm_spec.ps}
+\includegraphics[width=3.5in]{f13.eps}
+\caption{
+\ion{Mg}{2} and \ion{Fe}{2} profiles for the fiducial model with
+varying normalization, parameterized by \nhn.  As expected, the
+strength of absorption increases with increasing \nhn; this also
+results in stronger line-emission.  Note that the \feiia\ emission is
+always weak. Only its absorption increases with \nhn\ and actually exceeds
+the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
+\ion{Mg}{2} doublet, meanwhile, always falls below a relative flux of
+0.3 while the \mgiib\ emission rises steadily with \nhn.
+}
+\label{fig:norm}
+\end{figure}
+
+\begin{deluxetable*}{ccrccccccccccc}
+%\rotate
+\tablewidth{0pc}
+\tablecaption{Line Diagnostics for the Fiducial Model and Variants
+\label{tab:line_diag}}
+\tabletypesize{\scriptsize}
+\tablehead{\colhead{Transition} & \colhead{Model} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\rm i}$} & \colhead{$W_{\rm a}$} & \colhead{$\tau_{\rm pk}$} & \colhead{$v_\tau$} 
+& \colhead{$v_{\bar \tau}$}
+& \colhead{$v_{\rm int}^e$} & \colhead{$W_{\rm e}$} & \colhead{$f_{\rm pk}$} & \colhead{$v_f$} 
+& \colhead{$v_{\bar f}$} & \colhead{$\Delta v_{\rm e}$}
+\\
+&& (\kms) & (\AA) & (\AA) && (\kms) & (\kms) & (\kms) & (\AA) & & (\kms) & (\kms) & (\kms)}
+\startdata
+  MgII 2796  \\
+&Fiducial&[$-1009,-43$]& 4.78& 2.83&0.94&$ -215$&$ -372$&[$-32,311$]&$-1.77$& 2.48&$   32$&$  117$& 215\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-145,606$]&$-2.34$& 2.10&$   70$&$  208$& 483\\
+&$\phi=180^\circ$&[$-1030,-65$]& 4.78& 2.98&1.03&$ -199$&$ -369$&[$-65,70$]&$-0.51$& 1.78&$  -11$&$    6$& 107\\
+&$\theta_b=80^\circ$&[$-1030,-65$]& 4.78& 3.55&0.91&$ -306$&$ -442$&[$-65,257$]&$-1.03$& 1.78&$   43$&$   93$& 215\\
+&$\theta_b=45^\circ$&[$-1003,-11$]& 4.78& 4.79&2.19&$  -91$&$ -332$&[$16,96$]&$-0.04$& 1.07&$   43$&$   55$&  54\\
+&\taud=1&[$-1009,-32$]& 4.77& 2.94&0.95&$ -215$&$ -360$&[$-32,257$]&$-0.95$& 1.90&$   32$&$  101$& 193\\
+&\taud=3&[$-998,-32$]& 4.78& 3.07&1.03&$ -193$&$ -342$&[$-22,182$]&$-0.40$& 1.48&$   43$&$   76$& 150\\
+&ISM&[$-1009,-65$]& 6.36& 2.67&0.90&$ -204$&$ -390$&[$-54,311$]&$-1.60$& 2.36&$  118$&$  125$& 236\\
+&ISM+dust&[$-998,150$]& 6.42& 4.06&1.06&$ -193$&$ -270$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+  MgII 2803  \\
+&Fiducial&[$-437,-41$]& 3.29& 1.19&0.76&$ -148$&$ -193$&[$-41,676$]&$-2.24$& 2.55&$   34$&$  269$& 449\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-84,665$]&$-1.86$& 1.93&$   77$&$  257$& 482\\
+&$\phi=180^\circ$&[$-538,-57$]& 3.29& 1.82&0.97&$ -137$&$ -232$&[$-57,104$]&$-0.59$& 1.81&$   -3$&$   22$& 107\\
+&$\theta_b=80^\circ$&[$-485,-57$]& 3.29& 1.33&0.65&$ -217$&$ -237$&[$-57,746$]&$-2.30$& 2.12&$   23$&$  303$& 535\\
+&$\theta_b=45^\circ$&[$-538,-57$]& 3.29& 2.60&1.74&$  -84$&$ -217$&[$-30,692$]&$-0.72$& 1.33&$   23$&$  320$& 562\\
+&\taud=1&[$-479,-41$]& 3.28& 1.41&0.83&$ -137$&$ -195$&[$-41,591$]&$-1.30$& 1.95&$   34$&$  247$& 417\\
+&\taud=3&[$-533,-30$]& 3.26& 1.67&0.94&$ -116$&$ -195$&[$-30,484$]&$-0.66$& 1.50&$   34$&$  213$& 375\\
+&ISM&[$-426,-62$]& 6.49& 1.03&0.67&$ -169$&$ -206$&[$-51,655$]&$-2.09$& 2.57&$   98$&$  265$& 439\\
+&ISM+dust&[$-554,130$]& 6.51& 2.59&1.02&$ -137$&$ -143$&[$173,195$]&$-0.01$& 1.03&$  184$&$  184$&  21\\
+  FeII 2586  \\
+&Fiducial&[$-348,-35$]& 0.82& 0.61&1.01&$  -70$&$ -119$&[$-35,128$]&$-0.10$& 1.11&$   35$&$   47$& 128\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-104,186$]&$-0.10$& 1.06&$   70$&$   41$& 232\\
+&$\phi=180^\circ$&[$-365,-46$]& 0.82& 0.60&1.01&$  -75$&$ -133$&[$-46,70$]&$-0.03$& 1.06&$  -17$&$   12$&  87\\
+&$\theta_b=80^\circ$&[$-481,-46$]& 0.82& 0.96&1.57&$  -75$&$ -148$&[$-46,186$]&$-0.10$& 1.09&$   41$&$   71$& 203\\
+&$\theta_b=45^\circ$&[$-481,-46$]& 0.82& 1.03&1.88&$  -75$&$ -143$&[$41,99$]&$-0.02$& 1.03&$   41$&$   69$&  58\\
+&\taud=1&[$-348,-35$]& 0.82& 0.61&1.04&$  -70$&$ -118$&[$-35,116$]&$-0.05$& 1.06&$   23$&$   41$& 116\\
+&\taud=3&[$-313,-35$]& 0.94& 0.60&1.06&$  -70$&$ -113$&[$-23,46$]&$-0.02$& 1.04&$  -12$&$   12$&  58\\
+&ISM&[$-348,104$]& 1.90& 1.60&2.75&$    0$&$  -29$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+&ISM+dust&[$-313,116$]& 1.84& 1.63&2.96&$   23$&$  -25$&[$278,290$]&$-0.00$& 1.03&$  278$&$  284$&  12\\
+  FeII 2600  \\
+&Fiducial&[$-580,-37$]& 1.87& 1.18&1.08&$  -83$&$ -181$&[$-37,459$]&$-0.83$& 1.70&$   32$&$  191$& 312\\
+&$\phi=0^\circ$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&[$-135,442$]&$-0.78$& 1.46&$   67$&$  144$& 346\\
+&$\phi=180^\circ$&[$-597,-49$]& 1.87& 1.18&1.31&$  -78$&$ -188$&[$-49,95$]&$-0.25$& 1.39&$  -20$&$   22$&  87\\
+&$\theta_b=80^\circ$&[$-856,-49$]& 1.87& 1.72&1.07&$ -106$&$ -249$&[$-49,557$]&$-0.77$& 1.49&$   38$&$  241$& 404\\
+&$\theta_b=45^\circ$&[$-856,-49$]& 1.87& 2.12&2.71&$  -78$&$ -204$&[$-20,413$]&$-0.24$& 1.15&$   38$&$  194$& 346\\
+&\taud=1&[$-591,-37$]& 1.87& 1.20&1.14&$  -83$&$ -176$&[$-37,332$]&$-0.50$& 1.45&$   32$&$  138$& 265\\
+&\taud=3&[$-580,-37$]& 1.95& 1.25&1.31&$  -72$&$ -169$&[$-37,228$]&$-0.23$& 1.22&$   44$&$   93$& 196\\
+&ISM&[$-568,90$]& 3.12& 1.88&1.19&$  -72$&$  -99$&[$101,378$]&$-0.19$& 1.15&$  113$&$  237$& 242\\
+&ISM+dust&[$-603,101$]& 3.06& 2.12&1.40&$   44$&$  -93$&[$182,194$]&$-0.00$& 1.02&$  182$&$  188$&  12\\
+  FeII* 2612 \\
+&Fiducial&&&&&&&[$-173,183$]&$-0.34$& 1.24&$  -23$&$    5$& 241\\
+&$\phi=0^\circ$&&&&&&&[$-46,183$]&$-0.16$& 1.22&$   11$&$   67$& 172\\
+&$\phi=180^\circ$&&&&&&&[$-190,68$]&$-0.16$& 1.21&$  -46$&$  -61$& 172\\
+&$\theta_b=80^\circ$&&&&&&&[$-276,241$]&$-0.46$& 1.29&$  -46$&$  -17$& 316\\
+&$\theta_b=45^\circ$&&&&&&&[$-18,155$]&$-0.07$& 1.10&$   40$&$   68$& 144\\
+&\taud=1&&&&&&&[$-173,114$]&$-0.23$& 1.21&$  -46$&$  -28$& 207\\
+&\taud=3&&&&&&&[$-150,91$]&$-0.14$& 1.16&$  -46$&$  -30$& 184\\
+&ISM&&&&&&&[$-184,160$]&$-1.10$& 2.66&$    0$&$   -9$& 138\\
+&ISM+dust&&&&&&&[$-138,137$]&$-0.45$& 1.53&$    0$&$   -1$& 161\\
+  FeII* 2626 \\
+&Fiducial&&&&&&&[$-171,183$]&$-0.39$& 1.29&$  -46$&$    5$& 217\\
+&$\phi=0^\circ$&&&&&&&[$-52,177$]&$-0.13$& 1.16&$   34$&$   62$& 171\\
+&$\phi=180^\circ$&&&&&&&[$-194,63$]&$-0.13$& 1.16&$  -52$&$  -66$& 143\\
+&$\theta_b=80^\circ$&&&&&&&[$-280,234$]&$-0.58$& 1.41&$  -52$&$  -22$& 314\\
+&$\theta_b=45^\circ$&&&&&&&[$6,148$]&$-0.08$& 1.14&$   34$&$   76$& 114\\
+&\taud=1&&&&&&&[$-160,126$]&$-0.25$& 1.23&$  -46$&$  -17$& 194\\
+&\taud=3&&&&&&&[$-171,68$]&$-0.14$& 1.17&$  -46$&$  -51$& 194\\
+&ISM&&&&&&&[$-194,194$]&$-1.76$& 4.10&$    0$&$    0$& 103\\
+&ISM+dust&&&&&&&[$-160,114$]&$-0.47$& 1.70&$    0$&$  -21$& 137\\
+  FeII* 2632 \\
+&Fiducial&&&&&&&[$-132,119$]&$-0.16$& 1.12&$   16$&$   -6$& 194\\
+&$\phi=0^\circ$&&&&&&&[$-41,130$]&$-0.08$& 1.09&$   45$&$   44$& 142\\
+&$\phi=180^\circ$&&&&&&&[$-155,16$]&$-0.08$& 1.11&$  -41$&$  -69$& 142\\
+&$\theta_b=80^\circ$&&&&&&&[$-212,159$]&$-0.23$& 1.14&$   16$&$  -26$& 285\\
+&$\theta_b=45^\circ$&&&&&&&[$-639,102$]&$-0.18$& 1.14&$ -611$&$ -271$& 684\\
+&\taud=1&&&&&&&[$-121,85$]&$-0.11$& 1.10&$  -52$&$  -18$& 160\\
+&\taud=3&&&&&&&[$-98,16$]&$-0.05$& 1.08&$  -41$&$  -41$& 103\\
+&ISM&&&&&&&[$-121,130$]&$-0.55$& 1.81&$    5$&$    4$& 137\\
+&ISM+dust&&&&&&&[$-121,107$]&$-0.22$& 1.30&$    5$&$   -6$& 148\\
+\enddata
+\tablecomments{{L}isted are the equivalent widths (intrinsic, absorption, and emission), the peak optical depth for the absorption
+$\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the velocity where the optical depth peaks $v_\tau$, the optical depth-weighted velocity centroid 
+$v_{\bar \tau} \equiv \int dv \, v \ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in emission, the velocity where the flux peaks 
+$v_f$, the flux-weighted velocity centroid of the emission line $v_{\bar f}$ (occasionally affected by blends with neighboring emission lines), and the $90\%$ width $\Delta v_{\rm e}$.
+The $v^a_{\rm int}$ and $v^e_{\rm int}$ columns give the velocity range used to calculate the absorption and emission characteristics, respecitvely.
+These were defined by the velcoities where the profile crossed 0.95 in the normalized flux.}
+\end{deluxetable*}
+
 \subsection{Varying $n_{\rm H}^0$}
 
-The final modification to the fiducial model considered was to
-uniformly vary the normalization of the optical depth profiles.
+The final modification to the fiducial model considered was %to
+%uniformly vary 
+a uniform variation of
+the normalization of the optical depth profiles.
 Specifically, we ran a series of additional models with $n_{\rm H}^0$ at
@@
 galactic scales.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_lbg_sobolev.ps}
+\includegraphics[width=3.5in]{f14.eps}
+\caption{
+(a) The dotted curve shows the velocity law (labeled on the
+right axis) for the LBG model
+of S10 plotted against $(r/{\rm kpc} -1)$ to highlight the evolution
+in the quantities at small radii.  For example,  note how rapidly the velocity rises from $r =
+1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
+Mg$^+$ gas
+density derived from 
+the average absorption profile of LBG galaxies (see below).
+The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ and then
+steepens to $(r/{\rm kpc}-1)^{-1.8}$.
+(b) The average profile for LBG cool gas absorption as
+measured and defined by S10
+(black solid curve).  Overplotted on this curve is a (red) dotted line that
+shows the \mgiia\ absorption profile derived from the density (and velocity)
+law shown in the upper panel.  
+}
+\label{fig:LBG_Sobolev}
+\end{figure}
 
@@
 assume $\mnfe = \mnmg/2$ and also scale $\tau$ by the $f\lambda$ product.
+
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_lbg_spec.ps}
+\includegraphics[width=3.5in]{f15.eps}
+\caption{
+Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
+LBG models considered: (red) the profiles predicted using the 
+Sobolev approximation 
+and (black) a model constructed to faithfully
+represent the wind model advocated by S10.  The dotted line
+shows the absorption profiles of the latter model if one were
+to neglect scattered and re-emitted photons.  Similar to the fiducial
+model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
+significantly modify the absorption profiles (especially \ion{Mg}{2}
+and \feiib)
+and produce strong emission lines.  
+The result, for \ion{Mg}{2} especially, is a set of profiles that do
+not match the average observed LBG absorption profile.
+}
+\label{fig:LBG_spec}
+\end{figure}
 
@@
 
-Because we have explicit velocity and densities profiles for the LBG-Sobolev
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
+\includegraphics[height=3.5in,angle=90]{f16.eps}
+\caption{
+The upper left panel shows the density (solid) and velocity (dotted)
+laws for the LBG-Sobolev wind model (Figure~\ref{fig:LBG_Sobolev}).
+The remaining panels show the cumulative mass, energy, and momentum of
+this flow.  All of the curves rise very steeply at small radii and
+then rise steadily to large radii.  The principal result is that the
+majority of mass, energy, and momentum in the wind are contained at
+large radii.  We derive similar results for the LBG-partial covering model
+if we assume the wind is composed of identical clouds optically thick
+to strong metal-line transitions (e.g.\ \ion{Si}{2}~1526).  The
+energy and momentum in the outer regions of the outflow may be very
+difficult to generate with standard galactic-scale wind scenarios.
+}
+\label{fig:LBG_cumul}
+\end{figure}
+
+Because we have explicit velocity and density profiles for the LBG-Sobolev
 model, it is straightforward to calculate the radial
@@
 similar to our LBG-Sobolev calculation (Figure~\ref{fig:LBG_Sobolev}),
-this clump predicts the majority of mass, energy, and momentum are
-carried in the outer 
-In fact, for clumps that are optical thick to strong metal-line
-transitions (e.g.\ \ion{Si}{2}~1526) we estimate that the wind would
-carry nearly a total mass of $\approx 10^{10} \msun$!  We question
-whether this is a plausible result from star-formation driven
-feedback.
+this clump model predicts the majority of mass, energy, and momentum are
+carried in the outer regions of the wind. 
+In fact, for clumps that are optically thick to strong metal-line
+transitions (e.g.\ \ion{Si}{2}~1526) we estimate\footnote{Note that
+  this estimate differs from the LBG-Sobolev calculation shown in
+  Figure~\ref{fig:LBG_cumul} because the latter assumes a diffuse
+  medium with unit filling factor.}
+that the wind would
+carry nearly a total mass of $\approx 10^{10} \msun$, with the
+majority at large radii.
+%We question whether this is a plausible result from star-formation driven
+%feedback.
 
@@
 
-These authors start by assuming the galaxy is an isothermal sphere
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_rad_spec.ps}
+\includegraphics[width=3.5in]{f17.eps}
+\caption{
+\ion{Mg}{2} and \ion{Fe}{2}
+profiles for a radiation-driven wind model (red) compared against the
+fiducial wind model (black).  In contrast to the fiducial model, the
+optical depth peaks at large velocity (here $\mdv
+\approx -350 \mkms$).  At these velocities, the absorption is not
+filled-in by scattered photons and one recovers absorption lines
+that closely resemble the intrinsic optical depth profile (dotted
+curve).  Although the \ion{Mg}{2} absorption profiles are very
+different from the fiducial model, the \ion{Mg}{2} line-emission has
+similar peak flux and velocity centroids 
+The \feiis\ emission also has a similar
+equivalent width, yet the lines are much broader in the
+radiation-driven model. 
+}
+\label{fig:rad_spec}
+\end{figure}
+
+These authors start by assuming the galaxy has luminosity $L$ and is an isothermal sphere
 with mass profile $M_{gal}(r) = 2\sigma^2r/G$, where $\sigma$ is the
-velocity dispersion, and with luminosity $L$.  The gas mass profile is
+velocity dispersion.  The gas mass profile is
 simply $M_g(r) = f_g M_{gal}(r)$, with $f_g$ a constant gas fraction.  
@@
 
+\begin{figure}
+%\epsscale{0.8}
+%\plotone{../Figures/fig_vary_profiles.ps}
+\includegraphics[width=3.5in]{f18.eps}
+\caption{
+In panel (a) we illustrate the density (gray curves; dashed -- $\mnhn
+\propto r^0$, dotted -- $\mnhn \propto r^{-3}$, dot-dash -- $\mnhn
+\propto r^{2}$) and velocity laws (colored; green -- $v \propto
+r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$) for a
+series of power-law models (Table~\ref{tab:plaw_parm}).  For
+comparison we also plot the velocity and density laws for the fiducial
+model (thin, black curves).  
+Panel (b) plots the optical depth profiles of the \mgiia\ line for
+the nine models built from the density and velocity laws of panel (a).
+Each of these were normalized to have peak optical depths of 10 to
+1000 and to be optically thin at small or large velocity.
+}
+\label{fig:plaws}
+\end{figure}
+
+\begin{deluxetable}{cccccc}
+\tablewidth{0pc}
+\tablecaption{Wind Parameters: Power-law Models\label{tab:plaw_parm}}
+\tabletypesize{\footnotesize}
+\tablehead{\colhead{Label} & \colhead{$n(r)$} & \colhead{$n_{\rm
+      H}^0$} & \colhead{$v(r)$} & \colhead{$v^0$} &
+  \colhead{$\log \tau_{2796}^{\rm max}$} }
+\startdata
+A & $r^{-3}$& 0.4000 & $r^{-2.0}$&   2.0 & 0.8 \\ 
+B & $r^{-3}$& 0.5000 & $r^{-1.0}$&  50.0 & 1.1 \\ 
+C & $r^{-3}$& 0.3000 & $r^{ 0.5}$& 100.0 & 1.8 \\ 
+D & $r^{ 0}$& 0.0100 & $r^{-2.0}$&   2.0 & 2.1 \\ 
+E & $r^{ 0}$& 0.0100 & $r^{-1.0}$&  50.0 & 1.7 \\ 
+F & $r^{ 0}$& 0.0200 & $r^{ 0.5}$& 100.0 & 1.6 \\ 
+G & $r^{ 2}$& 0.0100 & $r^{-2.0}$&   2.0 & 4.4 \\ 
+H & $r^{ 2}$& 0.0010 & $r^{-1.0}$&  50.0 & 3.2 \\ 
+I & $r^{ 2}$& 0.0001 & $r^{ 0.5}$& 100.0 & 1.8 \\ 
+\enddata
+\tablecomments{For velocity laws that decrease with radius, the
+normalization $v^0$ refers to the velocity at $r=r_{\rm outer}$
+instead of $r=r_{\rm inner}$.  All models assume a Doppler parameter
+$b=15\mkms$, full isotropy, and a dust-free environment.}
+
+\end{deluxetable}
+
 Figure~\ref{fig:plaws_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
-profiles for the full suite of power-law models.  Although these
+profiles for the full suite of power-law models (see also
+Table~\ref{tab:plaw_diag}).  Although these
 models differ qualitatively from the fiducial model in their density
@@
 absorption peaks at large velocity from the systemic.
-One of the few obvious distinctions of these models from the fiducial wind is
+One of the few obvious distinctions between these models and the fiducial wind is
 the higher peak optical depth of absorption in the \feiib\
-transition.  This is primarily because these models have 
+transition.  This occurs primarily because these models have 
 higher intrinsic optical depths (i.e.\ higher $n_{\rm Fe^+}$ values).
 
-While there is commonality amongst between models, the specific
+\begin{deluxetable*}{ccrccccccccccc}
+%\rotate
+\tablewidth{0pc}
+\tablecaption{Line Diagnostics for the Fiducial Model and Variants
+\label{tab:plaw_diag}}
+\tabletypesize{\scriptsize}
+\tablehead{\colhead{Transition} & \colhead{Model} & \colhead{$v_{\rm int}^a$} & \colhead{$W_{\rm i}$} & \colhead{$W_{\rm a}$} & \colhead{$\tau_{\rm pk}$} & \colhead{$v_\tau$} 
+& \colhead{$v_{\bar \tau}$}
+& \colhead{$v_{\rm int}^e$} & \colhead{$W_{\rm e}$} & \colhead{$f_{\rm pk}$} & \colhead{$v_f$} 
+& \colhead{$v_{\bar f}$} & \colhead{$\Delta v_{\rm e}$}
+\\
+&& (\kms) & (\AA) & (\AA) && (km/s) & (km/s) & (km/s) & (\AA) & & (km/s) & (km/s) & (km/s)}
+\startdata
+  MgII 2796  \\
+&Fiducial&[$-1009,-43$]& 4.78& 2.83&0.94&$ -215$&$ -372$&[$-32,311$]&$-1.77$& 2.48&$   32$&$  117$& 215\\
+&LBG Sob.&[$-687,-86$]& 2.62& 1.35&0.45&$ -247$&$ -347$&[$-65,257$]&$-1.02$& 1.84&$   21$&$   90$& 193\\
+&LBG Cov.&[$-698,-65$]& 2.67& 1.40&0.41&$ -258$&$ -344$&[$-54,214$]&$-0.93$& 2.23&$    0$&$   72$& 172\\
+&Radiation&[$-365,-65$]& 2.86& 1.72&3.00&$ -301$&$ -250$&[$-54,322$]&$-1.74$& 2.13&$   53$&$  119$& 236\\
+&A&[$-848,-22$]& 9.29& 5.02&2.92&$ -773$&$ -499$&[$-22,171$]&$-1.34$& 3.30&$   21$&$   64$& 118\\
+&B&[$-1084,-65$]&11.08& 7.54&3.00&$ -976$&$ -589$&[$-65,193$]&$-1.83$& 2.89&$    0$&$   50$& 172\\
+&C&[$-451,-65$]& 2.54& 1.82&1.86&$ -204$&$ -200$&[$-65,332$]&$-1.79$& 2.09&$    0$&$  116$& 247\\
+&D&[$-794,21$]& 4.21& 2.14&1.11&$  -11$&$ -276$&[$32,311$]&$-1.57$& 3.58&$   43$&$  141$& 172\\
+%&E&[$-1009,-22$]& 6.37& 4.81&1.95&$ -183$&$ -343$&[$-22,279$]&$-3.23$& 3.59&$   43$&$  101$& 193\\
+%&F&[$-622,-97$]& 4.10& 3.00&3.00&$ -451$&$ -336$&[$-86,289$]&$-2.60$& 2.19&$   64$&$   90$& 290\\
+%&G&[$-794,118$]& 6.88& 2.81&3.00&$   11$&$ -165$&[$129,375$]&$-1.71$& 2.30&$  236$&$  248$& 150\\
+%&H&[$-837,43$]& 5.94& 4.15&3.00&$  -32$&$ -205$&[$53,365$]&$-3.33$& 3.09&$  150$&$  190$& 204\\
+%&I&[$-622,-172$]& 3.33& 2.53&3.00&$ -451$&$ -365$&[$-161,289$]&$-2.10$& 1.67&$   86$&$   62$& 343\\
+  MgII 2803  \\
+&Fiducial&[$-437,-41$]& 3.29& 1.19&0.76&$ -148$&$ -193$&[$-41,676$]&$-2.24$& 2.55&$   34$&$  269$& 449\\
+&LBG Sob.&[$-426,-73$]& 1.53& 0.46&0.24&$ -244$&$ -244$&[$-62,387$]&$-0.80$& 1.58&$   23$&$  154$& 332\\
+&LBG Cov.&[$-533,-73$]& 2.56& 0.98&0.37&$ -233$&$ -285$&[$-51,558$]&$-1.48$& 2.35&$    2$&$  227$& 396\\
+&Radiation&[$-362,-84$]& 2.32& 1.29&2.65&$ -308$&$ -256$&[$-73,323$]&$-1.31$& 1.86&$   45$&$  115$& 246\\
+&A&[$-554,-41$]& 7.06& 1.98&0.78&$ -330$&$ -293$&[$-41,805$]&$-5.72$& 5.03&$   13$&$  304$& 610\\
+&B&[$-554,-169$]& 5.74& 1.80&1.27&$ -372$&$ -359$&[$-84,1008$]&$-7.34$& 4.20&$    2$&$  338$& 749\\
+&C&[$-405,-73$]& 2.17& 1.49&1.85&$ -169$&$ -179$&[$-73,355$]&$-1.52$& 1.94&$   77$&$  122$& 246\\
+&D&[$-30,13$]& 3.69& 0.19&0.77&$   -9$&$   -1$&[$23,558$]&$-1.48$& 3.33&$   34$&$  251$& 332\\
+%&E&[$-479,-30$]& 4.42& 2.40&1.70&$ -158$&$ -195$&[$-30,815$]&$-3.96$& 3.71&$   23$&$  302$& 428\\
+%&F&[$-479,-94$]& 3.85& 2.59&2.50&$ -383$&$ -318$&[$-84,484$]&$-3.02$& 2.15&$   77$&$  163$& 385\\
+%&G&[$-105,88$]& 9.09& 1.12&3.00&$   -9$&$   -2$&[$98,441$]&$-2.15$& 2.52&$  184$&$  250$& 235\\
+%&H&[$-405,13$]& 6.43& 2.67&3.00&$  -30$&$ -143$&[$23,526$]&$-3.50$& 3.10&$  109$&$  228$& 300\\
+%&I&[$-490,-191$]& 2.85& 1.96&2.35&$ -394$&$ -354$&[$-84,473$]&$-2.16$& 1.61&$   77$&$  174$& 417\\
+  FeII 2586  \\
+&Fiducial&[$-348,-35$]& 0.82& 0.61&1.01&$  -70$&$ -119$&[$-35,128$]&$-0.10$& 1.11&$   35$&$   47$& 128\\
+&LBG Sob.&[$-151,-46$]& 0.18& 0.04&0.07&$ -139$&$  -99$&[$-12,35$]&$-0.01$& 1.05&$    0$&$   12$&  35\\
+&LBG Cov.&[$-684,-12$]& 2.38& 1.93&0.65&$ -162$&$ -276$&[$-12,360$]&$-0.34$& 1.33&$   12$&$  170$& 313\\
+&Radiation&[$0,0$]& 1.00& 0.00&0.02&$    0$&$    0$&[$12,255$]&$-0.11$& 1.09&$   35$&$  132$& 220\\
+&A&[$-812,-12$]& 1.88& 1.66&0.33&$ -742$&$ -422$&[$-12,232$]&$-0.12$& 1.12&$   23$&$  109$& 197\\
+&B&[$-1009,-186$]& 2.20& 1.97&0.60&$ -951$&$ -694$&[$-93,418$]&$-0.24$& 1.09&$   12$&$  161$& 429\\
+&C&[$-278,-81$]& 0.79& 0.71&2.51&$ -116$&$ -132$&[$-70,162$]&$-0.10$& 1.08&$   93$&$   46$& 174\\
+&D&[$-209,23$]& 0.88& 0.68&3.00&$  -12$&$  -26$&[$35,70$]&$-0.01$& 1.03&$   46$&$   52$&  35\\
+%&E&[$-476,-35$]& 1.33& 1.10&2.25&$  -70$&$ -129$&[$-23,174$]&$-0.12$& 1.13&$   23$&$   74$& 162\\
+%&F&[$-476,-104$]& 2.24& 2.02&1.98&$ -418$&$ -318$&[$-93,371$]&$-0.34$& 1.14&$    0$&$  136$& 371\\
+%&G&[$-464,406$]& 3.31& 3.24&3.00&$  -46$&$  -27$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$&$\dots$\\
+%&H&[$-418,23$]& 2.13& 1.92&3.00&$  -46$&$ -112$&[$70,209$]&$-0.04$& 1.06&$  116$&$  139$& 116\\
+%&I&[$-487,-220$]& 1.34& 1.26&3.00&$ -429$&$ -387$&[$-162,383$]&$-0.22$& 1.06&$    0$&$  110$& 464\\
+  FeII 2600  \\
+&Fiducial&[$-580,-37$]& 1.87& 1.18&1.08&$  -83$&$ -181$&[$-37,459$]&$-0.83$& 1.70&$   32$&$  191$& 312\\
+&LBG Sob.&[$-453,-72$]& 0.55& 0.24&0.11&$ -187$&$ -263$&[$-26,228$]&$-0.21$& 1.23&$   20$&$   99$& 208\\
+&LBG Cov.&[$-695,-60$]& 2.43& 1.38&0.44&$ -360$&$ -336$&[$-49,493$]&$-1.12$& 2.02&$    9$&$  203$& 381\\
+&Radiation&[$-360,-26$]& 2.21& 1.44&3.00&$ -303$&$ -247$&[$-26,320$]&$-0.84$& 1.59&$   44$&$  138$& 242\\
+&A&[$-822,-26$]& 4.61& 3.51&1.05&$ -753$&$ -455$&[$-26,793$]&$-1.78$& 2.34&$    9$&$  347$& 612\\
+&B&[$-1018,-199$]& 5.10& 4.20&1.88&$ -960$&$ -701$&[$-176,1001$]&$-2.84$& 1.86&$   -3$&$  371$& 935\\
+&C&[$-360,-72$]& 1.34& 1.09&2.04&$ -141$&$ -154$&[$-72,228$]&$-0.62$& 1.43&$   78$&$   75$& 219\\
+&D&[$-430,20$]& 1.68& 1.13&3.00&$  -14$&$  -58$&[$32,309$]&$-0.31$& 1.47&$   44$&$  163$& 219\\
+%&E&[$-787,-37$]& 2.68& 2.16&3.00&$  -72$&$ -183$&[$-37,493$]&$-1.16$& 1.84&$    9$&$  205$& 346\\
+%&F&[$-510,-106$]& 3.22& 2.65&3.00&$ -430$&$ -320$&[$-95,459$]&$-1.67$& 1.65&$   67$&$  159$& 381\\
+%&G&[$-603,274$]& 4.81& 3.66&3.00&$  -14$&$  -55$&[$447,493$]&$-0.02$& 1.07&$  459$&$  470$&  35\\
+%&H&[$-556,20$]& 3.27& 2.61&3.00&$  -49$&$ -138$&[$32,470$]&$-0.83$& 1.56&$  113$&$  234$& 300\\
+%&I&[$-522,-210$]& 2.06& 1.79&3.00&$ -430$&$ -373$&[$-187,436$]&$-1.16$& 1.30&$  147$&$  118$& 473\\
+  FeII* 2612 \\
+&Fiducial&&&&&&&[$-173,183$]&$-0.34$& 1.24&$  -23$&$    5$& 241\\
+&LBG Sob.&&&&&&&[$-69,57$]&$-0.04$& 1.07&$    0$&$   -6$& 115\\
+&LBG Cov.&&&&&&&[$-356,436$]&$-1.04$& 1.79&$    0$&$   35$& 563\\
+&Radiation&&&&&&&[$-299,298$]&$-0.50$& 1.26&$    0$&$   -1$& 425\\
+&A&&&&&&&[$-402,574$]&$-0.88$& 1.35&$    0$&$   80$& 735\\
+&B&&&&&&&[$-402,597$]&$-0.88$& 1.14&$   34$&$   94$& 873\\
+&C&&&&&&&[$-184,172$]&$-0.40$& 1.20&$  -81$&$   -6$& 241\\
+&D&&&&&&&[$-115,114$]&$-0.47$& 2.37&$    0$&$   -1$& 103\\
+%&E&&&&&&&[$-265,275$]&$-0.65$& 1.38&$   11$&$    5$& 310\\
+%&F&&&&&&&[$-402,424$]&$-1.12$& 1.27&$   45$&$   10$& 597\\
+%&G&&&&&&&[$-196,218$]&$-2.15$& 7.63&$    0$&$    7$& 126\\
+%&H&&&&&&&[$-230,241$]&$-1.24$& 1.80&$  -12$&$    4$& 264\\
+%&I&&&&&&&[$-402,424$]&$-0.70$& 1.13&$   34$&$   11$& 677\\
+  FeII* 2626 \\
+&Fiducial&&&&&&&[$-171,183$]&$-0.39$& 1.29&$  -46$&$    5$& 217\\
+&LBG Sob.&&&&&&&[$-23,46$]&$-0.03$& 1.06&$   23$&$   11$&  57\\
+&LBG Cov.&&&&&&&[$-251,274$]&$-0.28$& 1.22&$    0$&$   11$& 434\\
+&Radiation&&&&&&&[$-286,263$]&$-0.60$& 1.42&$    0$&$  -11$& 343\\
+&A&&&&&&&[$-663,320$]&$-1.60$& 1.71&$    0$&$ -152$& 720\\
+&B&&&&&&&[$-891,320$]&$-1.45$& 1.22&$    0$&$ -270$&1039\\
+&C&&&&&&&[$-171,160$]&$-0.46$& 1.24&$   57$&$   -5$& 217\\
+&D&&&&&&&[$-160,148$]&$-0.87$& 3.53&$    0$&$   -5$& 103\\
+%&E&&&&&&&[$-251,240$]&$-0.96$& 1.58&$   23$&$   -5$& 263\\
+%&F&&&&&&&[$-411,320$]&$-0.97$& 1.23&$    0$&$  -40$& 571\\
+%&G&&&&&&&[$-229,228$]&$-3.69$&11.76&$    0$&$    0$& 126\\
+%&H&&&&&&&[$-274,263$]&$-1.80$& 2.05&$  -12$&$   -4$& 263\\
+%&I&&&&&&&[$-457,320$]&$-0.65$& 1.13&$  240$&$  -64$& 640\\
+  FeII* 2632 \\
+&Fiducial&&&&&&&[$-132,119$]&$-0.16$& 1.12&$   16$&$   -6$& 194\\
+&LBG Sob.&&&&&&&[$-29,16$]&$-0.01$& 1.07&$   -7$&$   -7$&  46\\
+&LBG Cov.&&&&&&&[$-292,301$]&$-0.53$& 1.36&$    5$&$    4$& 479\\
+&Radiation&&&&&&&[$-235,210$]&$-0.23$& 1.12&$    5$&$  -12$& 353\\
+&A&&&&&&&[$-326,370$]&$-0.59$& 1.19&$   -7$&$   15$& 581\\
+&B&&&&&&&[$-326,563$]&$-0.78$& 1.17&$ -314$&$  108$& 741\\
+&C&&&&&&&[$-143,153$]&$-0.19$& 1.10&$   62$&$    5$& 228\\
+&D&&&&&&&[$-86,96$]&$-0.23$& 1.63&$    5$&$    4$&  91\\
+%&E&&&&&&&[$-212,187$]&$-0.32$& 1.19&$   28$&$  -12$& 262\\
+%&F&&&&&&&[$-326,392$]&$-0.59$& 1.14&$   73$&$   30$& 581\\
+%&G&&&&&&&[$-189,187$]&$-1.09$& 4.03&$    5$&$   -1$& 125\\
+%&H&&&&&&&[$-212,221$]&$-0.63$& 1.41&$  -18$&$    4$& 251\\
+%&I&&&&&&&[$-326,381$]&$-0.39$& 1.13&$ -326$&$   24$& 627\\
+\enddata
+\tablecomments{{L}isted are the equivalent widths (intrinsic, absorption, and emission), the peak optical depth for the absorption
+$\tau_{\rm pk} \equiv -\ln(I_{\rm min})$, the velocity where the optical depth peaks $v_\tau$, the optical depth-weighted velocity centroid 
+$v_{\bar \tau} \equiv \int dv \, v \ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in emission, the velocity where the flux peaks 
+$v_f$, the flux-weighted velocity centroid of the emission line $v_{\bar f}$ (occasionally affected by blends with neighboring emission lines), and the $90\%$ width $\Delta v_{\rm e}$.
+The $v^a_{\rm int}$ and $v^e_{\rm int}$ columns give the velocity
+range used to calculate the absorption and emission characteristics,
+respecitvely.  These were defined by the velcoities where the profile
+crossed 0.95 in the normalized flux. [See the electronic version for
+the complete Table].}
+\end{deluxetable*}
+
+While there is commonality between models, the specific
 characteristics of the absorption/emission profiles do exhibit
@@
 
+\begin{figure*}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
+\includegraphics[height=7.0in,angle=90]{f19.eps}
+\caption{
+\ion{Mg}{2} and \ion{Fe}{2} profiles for a series of power-law wind
+models (see Table~\ref{tab:plaw_parm} for details).  These panels reveal
+the diversity of absorption and emission that results from a set of
+intrinsic optical depth profiles that have relatively modest
+differences (Figure~\ref{fig:plaws}b).  As designed, all of the models
+show significant absorption blueward of systemic velocity.  As
+important, each shows strong line-emission at $\mdv \sim 0 \mkms$,
+with the flux proportional to the degree of absorption.
+We also note that the width of the \feiic\ emission scales with the
+velocity offset of peak optical depth for the \feiia\ absorption.
+Therefore, the emission kinematics trace the intrinsic
+optical depth profile.
+}
+\label{fig:plaws_spec}
+\end{figure*}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 it generally has only a modest effect on the predicted \ion{Mg}{2}
-emission and a relatively minor effect on \feiis\ emission.
-
-Another factor that may reduce line-emission is an
-anisotropic wind model. The flux is lower, for example, if one
+emission and a minor effect on \feiis\ emission.
+
+Another factor that may reduce line-emission is %an
+%anisotropic 
+wind %model
+anisotropy. The flux is lower, for example, if one
 eliminates the backside to the wind (e.g.\ the source itself could
 shadow a significant fraction of the backside).  
-Similarly, 
-many of the scattered photons of the fiducial 
-model arise nearly normal to the sightline such that a biconical
-wind can have significantly lower line-emission
-($\S$~\ref{sec:anisotropic}). 
+Similarly, a bi-conical
+wind can have significantly lower line-emission, at 
+least for the fiducial model ($\S$~\ref{sec:anisotropic}). 
 For the anisotropic winds explored in this paper,
@@
 effects may explain the absence of significant line-emission,
-but these would generally
-not be sufficient to preclude detection.
+but they may not be sufficient to preclude its detection.
 
@@
 when compared to the galaxy continuum.
+
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
+\includegraphics[height=3.5in,angle=90]{f20.eps}
+\caption{
+Absolute emission equivalent width ($|W_{\rm e}|$) relative to the observed
+absorption equivalent width ($W_{\rm a}$) for a series of transitions:
+(solid -- \mgiia; dotted -- \mgiib; dashed -- \feiib).  The
+\ewe/\ewabs\ ratio is plotted as a function of slit width relative to
+twice the radius \rtt, defined to be where the Sobolev optical depth 
+$\tau_S = 0.2$.  The black curves correspond to the fiducial wind
+model ($\S$~\ref{sec:fiducial}; $\mrtt \approx 15$\,kpc), the red curves are for the
+LBG-partial covering scenario ($\S$~\ref{sec:Covering}; $\mrtt \approx
+8$\,kpc), and the
+radiation-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = 40$kpc) has blue curves.
+For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
+with slit width and then plateaus at $\approx \mrtt$.  
+Therefore, a slit that exceeds $\approx 0.5 \mrtt$ will admit nearly
+all of the photons scattered to our sightline.
+}
+\label{fig:obs_slit}
+\end{figure}
 
@@
 (Figures~\ref{fig:anisotropic},\ref{fig:dust}).
-The emission would still 
+The remaining emission would still 
 modify the observed absorption profiles (e.g.\
-Figure~\ref{fig:noemiss}) and may lead to erroneous conclusions
+Figure~\ref{fig:noemiss}) and may complicate conclusions
 regarding characteristics of the flow.  {\it An analysis of cool gas outflows
-that entirely ignores line-emission may incorrectly conclude that the gas is
-partially covered, has a significantly lower peak optical depth,
+that entirely ignores line-emission may incorrectly conclude that the source is
+partially covered, that the gas has a significantly lower peak optical depth,
 and/or that a $\mdv \sim 0 \mkms$ component is
@@
 
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
+\includegraphics[height=3.5in,angle=90]{f21.eps}
+\caption{
+Difference between the `observed' absorption equivalent width \ewabs\
+which includes the flux of scattered photons and the `intrinsic'
+equivalent width $W_{\rm i}$ that ignores photon scattering.  The
+dashed (dotted) curves trace a 50\%\ (10\%) reduction in \ewabs\
+relative to $W_{\rm i}$.  One notes a reduction in \ewabs\ by $\approx
+30-50\%$ for the \mgiia\ transition (the effect is generally larger
+for \mgiib).  The effects of scattered photons are reduced for the
+\ion{Fe}{2} transitions because a fraction (in fact a majority for
+\feiia) of the absorbed photons fluoresce as \feiis\ emission at
+longer wavelengths and do not `fill-in' the absorption profiles.
+The figure shows results for all of the models presented in
+Tables~\ref{tab:line_diag} and \ref{tab:plaw_diag}.
+}
+\label{fig:obs_ew}
+\end{figure}
+
 Figure~\ref{fig:obs_ew} demonstrates one observational
@@
 equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
-which has the most effected transitions, \ewabs\ is reduced by
-$30-50\%$ from the intrinsic equivalent width.  In turn, one may derive 
+which has the most strongly affected transitions, \ewabs\ is reduced by
+$30-50\%$ from the intrinsic equivalent width (the equivalent width
+one would measure in the absence of scattered photons).  In turn, one may derive 
 a systematically lower optical depth or velocity extent for the wind,
@@
 are filled-in primarily at these velocities.
+
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
+\includegraphics[height=3.5in,angle=90]{f22.eps}
+\caption{
+The observed peak optical depth $\tau_{\rm pk} \equiv -\ln [I_{\rm
+  min}]$ for \mgiia\ profiles of the wind models studied in this paper
+(Tables~\ref{tab:line_diag}, \ref{tab:plaw_diag}) with $I_{\rm min}$
+the minimum normalized intensity of the absorption profile.  Cases
+where \tpk\ exceeds 3 are presented as lower limits.  The \tpk\ values
+are plotted against the velocity $v_\tau$ where $I(v_\tau) = I_{\rm min}$.  In all
+of the models, the true peak optical depth $\mtpk^{\rm true} > 10$.
+The much lower `observed' \tpk\ values occur because scattered \mgiia\
+photons have filled-in the absorption profiles at velocities $\mdv
+\gtrsim -400 \mkms$. These effects, therefore, are greatest for wind
+models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
+the majority of scattered photons have this relative velocity.
+Indeed, models with $v_\tau < -400 \mkms$ all show $\mtpk > 3$.
+}
+\label{fig:obs_peaktau}
+\end{figure}
 
@@
 results are similar for the \mgiib\ profile.  In fact, one generally
-measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and would 
-falsely conclude that the source is partially covered. 
+measures a similar $\tau_{\rm pk}$ for each \ion{Mg}{2} line and %would 
+may incorrectly conclude that the source is partially covered. 
 In the case of \ion{Fe}{2}, one may even observe a (non-physical)
@@
 
-These effects for \ion{Mg}{2} absorption are reduced
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
+\includegraphics[height=3.5in,angle=90]{f23.eps}
+\caption{
+Comparison of the velocities for which the \feiia\ and \mgiia\ absorption
+profiles have greatest depth.  Results for all of the models
+studied in this paper are presented (Tables~\ref{tab:line_diag},
+\ref{tab:plaw_diag}).  
+It is evident that wind models with a peak optical depth near the
+systemic velocity have a \mgiia\ absorption profile shifted blueward
+by one to several hundred \kms.  Analysis of such profiles may lead to
+the false conclusion 
+that (i) the majority of mass in the wind is travelling at a higher
+velocity; and (ii) there is no gas with $\mdv \sim 0 \mkms$.
+The dashed curve traces the one-to-one line.
+}
+\label{fig:obs_vtau}
+\end{figure}
+
+These effects %for \ion{Mg}{2} absorption 
+are reduced
 for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
@@
 the gas.  Analysis of these lines, without consideration of
-line-emission, would lead to incorrect conclusions on the energetics
+line-emission, may lead to incorrect conclusions on the energetics
 and mass flux of the wind.
+
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
+\includegraphics[height=3.5in,angle=90]{f24.eps}
+\caption{
+`Observations' of the \ion{Mg}{2} profiles for the ISM+wind model.  
+(a) The true profile (dotted lines) has been convolved with a
+Gaussian line-spread-function (FWHM~$= 250 \mkms$) and noise has been
+added to give a S/N=7 per pixel.  Note the suppressed peak in 
+line-emission; one may even infer the flux of \mgiia\ exceeds that of
+\mgiib.  The \mgiia\ absorption is also shifted to
+shorter wavelengths, i.e.\ to a greater velocity offset from systemic.  
+(b) The solid curve shows a stack of 100 spectra of the ISM+wind
+profile, each degraded to a S/N=2 per pixel, and offset from systemic
+by a normal deviate with $\sigma = 100 \mkms$ to mimic uncertainty in
+the redshift of the galaxies.  
+This treatment is meant to illustrate the
+implications of stacking galaxy spectra to study outflows
+\citep[e.g.][S10]{wcp+09,rwk+10}.   The main difference from the
+single galaxy observation shown in panel (a) is the smearing of
+line-emission and absorption that reduces the height/depth of each.
+The effects would likely be even more pronounced if one studied spectra with
+a diversity of \ion{Mg}{2} profiles.    
+}
+\label{fig:obs_lris}
+\end{figure}
 
@@
 
-The previous few paragraphs sound a cautionary and largely negative
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
+%\includegraphics[scale=0.6,angle=90]{f25.eps}
+\includegraphics[height=3.5in,angle=90]{f25.eps}
+\caption{
+Surface brightness profiles of the fiducial wind model for the \mgiia\
+(solid) and \feiie\ (dotted) transitions.  Both profiles peak at small
+radii and decrease by several orders of magnitude before reaching the
+outer edge of the wind.  The profiles are sufficiently shallow,
+however, that the azimuthally integrated flux declines by only a
+factor of $\approx 10$ from $r = 1$\,kpc to $r=10$\,kpc.  Therefore, a
+sensitive IFU observation could map the emission (and, in principle,
+the kinematics) from $r_{\rm inner}$ to approximately $r_{\rm outer}$.
+}
+\label{fig:obs_sb}
+\end{figure}
+
+The previous few paragraphs sounded a cautionary 
 perspective on the implications for absorption-line analysis of
 galactic-scale outflows in the presence of (expected) significant
-line-emission.   While this is a necessary complication, direct analysis of
-the line-emission does offer new and unique
+line-emission.   While this is a necessary complication, 
+we emphasize that such analysis remains one of the few observational
+techniques at our disposal to study outflows.  Furthermore,
+direct analysis of
+the line-emission offers new and unique
 constraints on the characteristics of the outflow.  And, when coupled
 with the absorption-line data, the two sets of constraints may break
-various degeneracies on the physical characteristics of the outflow.
+various degeneracies in the physical characteristics of the outflow.
 We now consider a few examples.
 
-The most obvious measures provided by the line-emission are
-estimates
-of the size and morphology of the outflow \citep{rubin+10c}.  
+The most obvious characteristics probed by the line-emission are
+the size and morphology of the outflow \citep{rubin+10c}.  
 Line emission is predicted to extend to radii where the Sobolev
 optical depth exceeds a few tenths.  The principle
-challenge is to achieve sufficient sensitivity to detect the predicted
-low
-surface brightness emission. As Figure~\ref{fig:obs_sb}
+challenge is to achieve sufficient sensitivity to detect the
+predicted,
+low surface-brightness emission. As Figure~\ref{fig:obs_sb}
 demonstrates, the surface brightness at the inner wind radius of our
@@
 
+\begin{figure}
+%\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
+\includegraphics[height=3.5in,angle=90]{f26.eps}
+\caption{
+Plot of the 90\%\ velocity width ($\Delta v_e$) of \feiic\ emission versus the
+velocity where the resonance lines achieve peak optical depth
+$v_\tau$ in absorption.  The $\Delta v_e$ values rise steadily with
+increasing offset of $v_\tau$ from systemic.  The width of the \feiic\
+emission line, therefore, offers an independent diagnostic of the wind
+speed.
+}
+\label{fig:obs_edelv}
+\end{figure}
+
 The emission-line velocity widths also reveal
@@
 emission-line profiles of a set of simple galactic-scale outflow
-models.  Our analysis focused on the \mgiid\ and \ion{Fe}{2} UV1
-multiple of rest-frame UV transitions, but the results transfer to
+models.  This analysis implemented Monte Carlo radiative transfer
+techniques to propogate resonant photons through an expanding medium,
+allowing for their conversion to non-resonant photons (e.g.\ \feiis).
+Our work focused on the \mgiid\ and \ion{Fe}{2} UV1
+multiplet of rest-frame UV transitions, but the results apply to
 most other lines used to probe cool gas.  Our primary
@@
   are only coupled to the ground-state (e.g.\ \ion{Mg}{2}, \lya,
-  \ion{Na}{1}),  this implies much lower equivalent widths (up to
-  $50\%$) and also velocity profiles that are significantly offset
+  \ion{Na}{1}),  this implies much lower, absorption-line equivalent widths (by up to
+  $50\%$) and observed absorption profiles that are significantly offset in velocity
   from the intrinsic optical depth profile.
@@
 \item Analysis of cool gas outflows that entirely ignores this
-line-emission may incorrectly conclude that the gas is partially
-covered, has a significantly lower peak optical depth, and/or that a
+  line-emission may incorrectly conclude that the source is partially
+  covered, that the gas has a significantly lower peak optical depth, and/or that 
   gas with velocities near systemic (e.g.\ from the ISM or even
@@
   produce emission dominated by the
-optically-thin, fine-structure transitions.  As such, the resonance
+  optically-thin, fine-structure transitions.  As such, these resonance
   absorption lines offer the best
-characterization of the opacity of the wind and also of material 
+  characterization of the opacity of the wind and also of gas 
   with velocities near systemic.
@@
   models where resonance photons are trapped for only a few scatterings.  Models
-  with high opacity at small radii and at systemic velocity (e.g.\ an
+  with high opacity at small radii and at systemic velocity (e.g.\ with an
   optically thick, ISM component)  can effectively extinguish
-  resonantly trapped emission (\ion{Mg}{2}) but have more modest
+  resonantly trapped emission (\ion{Mg}{2}) but have weaker
   effect on non-resonant lines (\feiis).
@@
 \item We examined two scenarios designed to mimic the wind model
-  proposed by S10 for $z \sim 3$ Lyman break galaxies.  These models
-  predict substantial line-emission from scattered photons that
-  greatly modify the predicted line-profiles so that  
-  these models do not reproduce the observed line-profiles.
+  proposed by \cite{steidel+10} for $z \sim 3$ Lyman break galaxies.  Our
+  implementation of this model genreates substantial line-emission
+  from scattered photons that greatly modifies the predicted
+  line-profiles so that this model does not reproduce the observed
+  line-profiles.
 
@@
 \item The kinematics and flux ratios of the emission lines 
-  constrain the wind speed, opacity, dust extinction, and morphology of the
-  wind.
+  constrain the %wind 
+  speed, opacity, dust extinction, and morphology of the
+  wind.  When combined with absorption-line analysis, one may develop
+  yet tighter constraints on these characteristics.
 
@@
 
-\clearpage
-
 %\bibliographystyle{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati}
 %\bibliography{/u/xavier/NSF/SASIR/SASIR-ATI/prop2009/Text/nsfati09}
-\bibliographystyle{/u/xavier/paper/Bibli/apj}
-\bibliography{/u/xavier/paper/Bibli/allrefs}
-
-\clearpage
-
-\input{../Tables/table_atomic.tex}
-\input{../Tables/tab_fiducial.tex}
-\input{../Tables/tab_fiducial_ew.tex}
-\input{../Tables/tab_meas_models.tex}
-\input{../Tables/tab_plaw_parm.tex}
-\input{../Tables/tab_meas_plaws.tex}
-
-\begin{figure}
-\epsscale{0.95}
-\plotone{../Figures/energy_levels.ps}
-\caption{
-Energy level diagrams for the \mgiid\ doublet and the UV1
-multiplet of \ion{Fe}{2} transitions   
-(based on Figure~7 from \cite{hmt+99}).
-Each transition shown is
-labeled by its rest wavelength (\AA) and Einstein A-coefficient
-(s$^{-1}$). Black upward arrows
-indicate the resonance-line transitions, i.e.\ those connected to the ground
-state.  The 2p$^6$3p configuration of Mg$^+$ is split into
-two energy levels that give rise to the \mgiid\ doublet.  
-Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
-exhibit fine-structure splitting that gives rise to a series of
-electric-dipole transitions. 
-The downward (green) arrows show the \feiis\ transitions that are connected to the
-resonance-line transitions (i.e.\ they share the same upper energy
-levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
-2618,2631$; red and dashed lines) that arise from higher levels in the \zconfig\
-configuration.  These transitions have not yet been observed in
-galactic-scale outflows and are not considered in our analysis.
-}
-\label{fig:energy}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/oneline_test.eps}
-\caption{
-Line profiles of a test problem calculated using the monte carlo code (solid) and by direct numerical integration of the transport equation under the Sobolev approximation (dashed lines).
-The configuration was  spherical and consisted of a homologously expanding wind  with density profile $n \propto r^{-2}$  lying above an opaque emitting surface at velocity coordinate 100~km~s$^{-1}$.
-The wind extended to 2,000 km~s$^{-1}$ and the Sobolev optical depth had values of  $\tau = 1$ (black lines), $\tau = 10$ (red lines), and $\tau = 100$ (blue lines).
-Discrepancies in the $\tau = 100$ case are likely due to the breakdown of the Sobolev approximation at high optical depth.
-}
-\label{fig:oneline_test}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_nvtau_vs_r.ps}
-\caption{
-Density (dashed; red), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (solid and dotted; black) for the fiducial
-wind model (see Table~\ref{tab:fiducial} for details).
-The density and velocity laws are simple $r^{-2}$ and $r^1$
-power-laws; these curves have been scaled for plotting
-convenience.  
-The optical depth profile was calculated two ways: (i) using the
-Sobolev approximation (Equation~\ref{eqn:Sobolev}; solid black curve)
-and (ii) summing
-the opacity at small and discrete radial intervals in velocity space
-and then converting to radius with the velocity law.  These give
-very similar results. 
-The wind parameters were set to give an optically thick medium at the
-inner radius ($r_{\rm inner} = 1$\,kpc) that becomes optically thin at
-the outer radius ($r_{\rm outer} = 20$\,kpc). 
-}
-\label{fig:fiducial_nvt}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_fiducial_1d.ps}
-\caption{
-{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
-described in Table~\ref{tab:fiducial} and
-Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
-characteristic of an outflow with significant absorption blueward of
-line-center (dashed vertical lines) extending to $v = -1000\mkms$
-and significant emission redward of line-center.  Note
-that even though the peak optical depth of the \ion{Mg}{2} transitions
-is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
-photons scattered off the outflow significantly fill-in the absorption.
-(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
-multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
-show weaker absorption due to the smaller Fe$^+$ number density and
-lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
-the emission for \feiia\ is much weaker than that for the
-\feiib\ and \mgiid\ transitions.  This is because a majority of the
-absorbed \feiia\ photons fluoresce into
-\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
-{\it Right} -- A subset of the transitions displayed in a velocity
-plot.
-}
-\label{fig:fiducial_1d}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_noemiss.ps}
-\caption{
-The solid curves show the line profiles (absorption and emission) of
-the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
-model.  These include the effects of scattered photons and show the
-canonical P-Cygni profiles of a source 
-embedded within an outflow.  Overplotted on each transition (dotted line) is
-the predicted absorption profile under the constraint that every
-absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission occurs.   The true profiles have been `filled-in' 
-significantly with photons scattered by the wind into our sightline.  Ignoring this
-process, one would model the absorption lines with a systematically lower
-optical depth and (incorrectly) conclude that the source is partly covered by the
-gas.  
-}
-\label{fig:noemiss}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_fiducial_ifu_mgii.ps}
-\caption{
-Surface-brightness emission maps around the \mgiia\ transition for the
-source+wind complex of the fiducial model.  The middle panel shows the
-1D spectrum with $v=0 
-\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
-curves indicate the velocity slices for the emission maps.  The
-source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
-pixels at the center of each map.   At $v=-250 \mkms$, the wind has an optical
-depth of $\tau_{2796} \approx 1$ and the source contributes
-roughly half of the observed flux.  At $v=-100 \mkms$ the
-wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  Amazingly, this
-emission exceeds the integrated flux at $v = -250\mkms$ such that the
-\mgiia\ line center is offset from the (intrinsic) peak in optical depth.  At $v \ge 0
-\mkms$,  both the source and wind contribute to the observed emission.
-At all velocities, the majority of emission comes from the inner
-$\approx 5$\,kpc.
-}
-\label{fig:fiducial_ifu_mgii}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_feii_ifu.ps}
-\caption{
-(Upper) Surface-brightness emission maps around the \feiib\ transition for the
-source+wind complex.  
-%The middle panel shows the 1D spectrum with $v=0
-%\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
-%curves indicating the velocity slices for the emission maps.  
-The results are very similar to those observed for the \mgiid\ doublet
-(Figure~\ref{fig:fiducial_ifu_mgii}).
-(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
-2612$ transition for the 
-source+wind complex.  %The middle panel shows the 1D spectrum with $v=0
-%\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
-%curves indicating the velocity slices for the emission maps.  
-In this case, the source is unattenuated yet scattered photons from
-the wind also make a significant contribution. 
-}
-\label{fig:fiducial_ifu_feii}
-\end{figure}
-
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_fiducial_cut.ps}
-%\caption{
-%The panels show the relative emission from the wind as a function of
-%radius for (a) \mgiia\ and (b) \feiib\ in a series of velocity
-%channels.  With the exception of $v = -100 \mkms$ for \mgiia, the wind
-%has finite transmission such that one observes the source at $r =
-%0$\,kpc.  In all cases,  the majority of emission occurs at $r
-%\lesssim 2.5$\,kpc, even if one ignores the source emission.
-%}
-%\label{fig:fiducial_cuts}
-%\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_asymm_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-case (black lines) compared against an anisotropic wind blowing into
-only $2\pi$ steradians as viewed from $\phi = 0^\circ$ (source
-uncovered) to $\phi = 180^\circ$ (source covered).  One detects
-significant emission for all orientations but significant
-absorption only for $\phi \ge 90^\circ$.
-The velocity centroid of the 
-emission shifts from positive to negative velocities as $\phi$
-increases and one transitions from viewing the wind as lying behind the
-source to in front of it.  The velocity centroid of emission, therefore,
-diagnoses the degree of anisotropy for the wind.
-}
-\label{fig:anisotropic}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_dust_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-model (black) against a series of models that include 
-dust extinction, parameterize by the integrated dust opacity from
-source to infinity (\taud).  The primary effect of dust is to suppress 
-the line-emission relative to the continuum. 
-A more subtle but important effect is that the redder photons in the
-emission lines (corresponding to positive velocity offsets relative to
-line-center) suffer greater extinction.  
-This occurs because the `redder' photons that we view have travelled 
-farther to scatter off the backside of the wind.  Note that
-the absorption lines are nearly unmodified until $\mtaud = 10$, a
-level of extinction that would preclude observing the source
-altogether.
-}
-\label{fig:dust}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_taud_vs_we.ps}
-\caption{
-Predicted equivalent widths for \mgiib\ line-emission from the
-fiducial wind model, as attenuated by dust with a range of \taud\
-values.  
-It is obvious that the equivalent widths (i.e., the flux relative to
-the continuum) do not scale as $\exp(\tau_d)$.
-The black (solid) curve shows the model results while the
-dotted (red) line plots $W_{\rm e}(\tau_d) = W_{\rm e}(\tau_d = 0)
-\cdot (1+\tau_d)^{-1}$.  This simple approximation is a good
-representation of the results for our radiative transfer calculations.   
-}
-\label{fig:dust_tau}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.7}
-\plotone{../Figures/fig_ism_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
-model (red) compared against the fiducial wind model (black). 
-The dotted line traces the predicted absorption profile in the absence
-of re-emission and scattering.
-Regarding the \ion{Mg}{2}~doublet, the primary difference between the
-ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
-in the emission lines from $v \approx 0 \mkms$ for the fiducial
-model to $v \approx +100\mkms$ for the ISM+wind model. 
-The \ion{Fe}{2} profiles, meanwhile, show several qualitative differences. 
-The \feiid\ resonance transitions each exhibit much
-greater absorption at $v \approx 0 \mkms$ than the fiducial model.
-The resonant line-emission is also substantially
-reduced, implying much higher fluxes for the non-resonant lines (e.g.\
-\feiic,2626).  
-Lastly, we note that the \feiia\ absorption profile provides a good
-(albeit imperfect) representation of the wind opacity and therefore
-offers the best characterization of an ISM component.
-}
-\label{fig:ISM_spec}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_norm_spec.ps}
-\caption{
-\ion{Mg}{2} and \ion{Fe}{2} profiles for the fiducial model with
-varying normalization, parameterized by \nhn.  As expected, the
-strength of absorption increases with increasing \nhn; this also
-results in stronger line-emission.  Note that the \feiia\ emission is
-always weak. Only its absorption increases with \nhn\ and actually exceeds
-the depth of \feiib\ for $\mnhn > \mnhf$.  The depth of the
-\ion{Mg}{2} doublet, meanwhile, always falls below a relative flux of
-0.3 while the \mgiib\ emission rises steadily with \nhn.
-}
-\label{fig:norm}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_sobolev.ps}
-\caption{
-(a) The dotted curve shows the velocity law (labeled on the
-right axis) for the LBG model
-of S10 plotted against $(r/{\rm kpc} -1)$ to highlight the evolution
-in the quantities at small radii.  For example,  note how rapidly the velocity rises from $r =
-1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
-Mg$^+$ gas
-density derived from 
-the average absorption profile of LBG galaxies (see below).
-The density falls off initially as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
-steepens to $(r/{\rm kpc}-1)^{-1.8}$.
-(b) The average profile for LBG cool gas absorption as
-measured and defined by S10
-(black solid curve).  Overplotted on this curve is a (red) dotted line that
-shows the \mgiia\ absorption profile derived from the density (and velocity)
-law shown in the upper panel.  
-}
-\label{fig:LBG_Sobolev}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_lbg_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
-LBG models considered: (red) the profiles from the 
-Sobolev approximation 
-and (black) a model constructed to faithfully
-represent the wind model advocated by S10.  The dotted line
-shows the absorption profiles of the latter model if one were
-to neglect scattered and re-emitted photons.  Similar to the fiducial
-model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
-significantly modify the absorption profiles (especially \ion{Mg}{2}
-and \feiib)
-and produce strong emission lines.  
-The result, for \ion{Mg}{2} especially, is a set of profiles that do
-not match the average observed LBG absorption profile.
-}
-\label{fig:LBG_spec}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_lbg_cumul.ps}
-\caption{
-The upper left panel shows the density (solid) and velocity (dotted)
-laws for the LBG-Sobolev wind model (Figure~\ref{fig:LBG_Sobolev}).
-The remaining panels show the cumulative mass, energy, and momentum of
-this flow.  All of the curves rise very steeply at small radii and
-then rise steadily to large radii.  The principal result is that the
-majority of mass, energy, and momentum in the wind are contained at
-large radii.  We derive similar results for the LBG-partial covering model
-if we assume the wind is composed of identical clouds optically thick
-to strong metal-line transitions (e.g.\ \ion{Si}{2}~1526).  The
-energy and momentum in the outer regions of the outflow may be very
-difficult to generate with standard galactic-scale wind scenarios.
-}
-\label{fig:LBG_cumul}
-\end{figure}
+%\bibliographystyle{/u/xavier/paper/Bibli/apj}
+%\bibliography{/u/xavier/paper/Bibli/allrefs}
+
+\begin{thebibliography}{74}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Aguirre} {et~al.}(2001){Aguirre}, {Hernquist}, {Schaye}, {Weinberg},
+  {Katz}, \& {Gardner}}]{ahs+01}
+{Aguirre}, A., {Hernquist}, L., {Schaye}, J., {Weinberg}, D.~H., {Katz}, N., \&
+  {Gardner}, J. 2001, \apj, 560, 599
+
+\bibitem[{{Alton} {et~al.}(1999){Alton}, {Davies}, \& {Bianchi}}]{adb99}
+{Alton}, P.~B., {Davies}, J.~I., \& {Bianchi}, S. 1999, \aap, 343, 51
+
+\bibitem[{{Charlot} \& {Fall}(2000)}]{cf00}
+{Charlot}, S., \& {Fall}, S.~M. 2000, \apj, 539, 718
+
+\bibitem[{{Chen} {et~al.}(2010){Chen}, {Tremonti}, {Heckman}, {Kauffmann},
+  {Weiner}, {Brinchmann}, \& {Wang}}]{cth+10}
+{Chen}, Y., {Tremonti}, C.~A., {Heckman}, T.~M., {Kauffmann}, G., {Weiner},
+  B.~J., {Brinchmann}, J., \& {Wang}, J. 2010, \aj, 140, 445
+
+\bibitem[{{Chevalier} \& {Clegg}(1985)}]{cc85}
+{Chevalier}, R.~A., \& {Clegg}, A.~W. 1985, \nat, 317, 44
+
+\bibitem[{{Dijkstra} {et~al.}(2006){Dijkstra}, {Haiman}, \&
+  {Spaans}}]{Dijkstra_2006}
+{Dijkstra}, M., {Haiman}, Z., \& {Spaans}, M. 2006, \apj, 649, 14
+
+\bibitem[{{France} {et~al.}(2010){France}, {Nell}, {Green}, \&
+  {Leitherer}}]{france10}
+{France}, K., {Nell}, N., {Green}, J.~C., \& {Leitherer}, C. 2010, \apjl, 722,
+  L80
+
+\bibitem[{{Fujita} {et~al.}(2009){Fujita}, {Martin}, {Mac Low}, {New}, \&
+  {Weaver}}]{fmm+09}
+{Fujita}, A., {Martin}, C.~L., {Mac Low}, M., {New}, K.~C.~B., \& {Weaver}, R.
+  2009, \apj, 698, 693
+
+\bibitem[{{Hamann} {et~al.}(2010){Hamann}, {Kanekar}, {Prochaska}, {Murphy},
+  {Ellison}, {Malec}, {Milutinovic}, \& {Ubachs}}]{hkp+10}
+{Hamann}, F., {Kanekar}, N., {Prochaska}, J.~X., {Murphy}, M.~T., {Ellison},
+  S., {Malec}, A.~L., {Milutinovic}, N., \& {Ubachs}, W. 2010, ArXiv e-prints
+
+\bibitem[{{Harrington}(1973)}]{Harrington_1973}
+{Harrington}, J.~P. 1973, \mnras, 162, 43
+
+\bibitem[{{Hartigan} {et~al.}(1999){Hartigan}, {Morse}, {Tumlinson}, {Raymond},
+  \& {Heathcote}}]{hmt+99}
+{Hartigan}, P., {Morse}, J.~A., {Tumlinson}, J., {Raymond}, J., \& {Heathcote},
+  S. 1999, \apj, 512, 901
+
+\bibitem[{{Heckman} {et~al.}(1990){Heckman}, {Armus}, \& {Miley}}]{ham90}
+{Heckman}, T.~M., {Armus}, L., \& {Miley}, G.~K. 1990, \apjs, 74, 833
+
+\bibitem[{{Hughes} {et~al.}(1990){Hughes}, {Robson}, \& {Gear}}]{hrg90}
+{Hughes}, D.~H., {Robson}, E.~I., \& {Gear}, W.~K. 1990, \mnras, 244, 759
+
+\bibitem[{{Jeffery} \& {Branch}(1990)}]{Jeffery_Branch}
+{Jeffery}, D.~J., \& {Branch}, D. 1990, in Supernovae, Jerusalem Winter School
+  for Theoretical Physics, ed. {J.~C.~Wheeler, T.~Piran, \& S.~Weinberg},
+  149--+
+
+\bibitem[{{Kasen} {et~al.}(2002){Kasen}, {Branch}, {Baron}, \&
+  {Jeffery}}]{Kasen_2002}
+{Kasen}, D., {Branch}, D., {Baron}, E., \& {Jeffery}, D. 2002, \apj, 565, 380
+
+\bibitem[{{Kasen} {et~al.}(2006){Kasen}, {Thomas}, \& {Nugent}}]{Kasen_2006}
+{Kasen}, D., {Thomas}, R.~C., \& {Nugent}, P. 2006, \apj, 651, 366
+
+\bibitem[{{Kasen} \& {Woosley}(2007)}]{kw07}
+{Kasen}, D., \& {Woosley}, S.~E. 2007, \apj, 656, 661
+
+\bibitem[{{Kasen} \& {Woosley}(2009)}]{kw09}
+---. 2009, \apj, 703, 2205
+
+\bibitem[{{Kasen} {et~al.}(2010)}]{Kasen_lyman}
+{Kasen}, D., {et~al.} 2010, ApJ in preparation
+
+\bibitem[{{Kere{\v s}} {et~al.}(2009){Kere{\v s}}, {Katz}, {Dav{\'e}},
+  {Fardal}, \& {Weinberg}}]{kkd+09}
+{Kere{\v s}}, D., {Katz}, N., {Dav{\'e}}, R., {Fardal}, M., \& {Weinberg},
+  D.~H. 2009, \mnras, 396, 2332
+
+\bibitem[{{Kinney} {et~al.}(1993){Kinney}, {Bohlin}, {Calzetti}, {Panagia}, \&
+  {Wyse}}]{kbc+93}
+{Kinney}, A.~L., {Bohlin}, R.~C., {Calzetti}, D., {Panagia}, N., \& {Wyse},
+  R.~F.~G. 1993, \apjs, 86, 5
+
+\bibitem[{{Kobulnicky} \& {Martin}(2010)}]{km10}
+{Kobulnicky}, H.~A., \& {Martin}, C.~L. 2010, \apj, 718, 724
+
+\bibitem[{{Kurucz}(2005)}]{kurucz05}
+{Kurucz}, R.~L. 2005, Memorie della Societa Astronomica Italiana Supplementi,
+  8, 14
+
+\bibitem[{{Laursen} {et~al.}(2009){Laursen}, {Razoumov}, \&
+  {Sommer-Larsen}}]{Laursen_2009}
+{Laursen}, P., {Razoumov}, A.~O., \& {Sommer-Larsen}, J. 2009, \apj, 696, 853
+
+\bibitem[{{Lehnert} {et~al.}(1999){Lehnert}, {Heckman}, \& {Weaver}}]{lhw99}
+{Lehnert}, M.~D., {Heckman}, T.~M., \& {Weaver}, K.~A. 1999, \apj, 523, 575
+
+\bibitem[{{Lowenthal} {et~al.}(1997){Lowenthal}, {Koo}, {Guzman}, {Gallego},
+  {Phillips}, {Faber}, {Vogt}, {Illingworth}, \& {Gronwall}}]{lkg+97}
+{Lowenthal}, J.~D., {et~al.} 1997, \apj, 481, 673
+
+\bibitem[{{Martin}(1999)}]{martin99}
+{Martin}, C.~L. 1999, \apj, 513, 156
+
+\bibitem[{{Martin}(2005)}]{martin05}
+---. 2005, \apj, 621, 227
+
+\bibitem[{{Martin} \& {Bouch{\'e}}(2009)}]{mb09}
+{Martin}, C.~L., \& {Bouch{\'e}}, N. 2009, \apj, 703, 1394
+
+\bibitem[{{M{\'e}nard} {et~al.}(2008){M{\'e}nard}, {Nestor}, {Turnshek},
+  {Quider}, {Richards}, {Chelouche}, \& {Rao}}]{mnt+08}
+{M{\'e}nard}, B., {Nestor}, D., {Turnshek}, D., {Quider}, A., {Richards}, G.,
+  {Chelouche}, D., \& {Rao}, S. 2008, \mnras, 385, 1053
+
+\bibitem[{{M{\'e}nard} {et~al.}(2010){M{\'e}nard}, {Scranton}, {Fukugita}, \&
+  {Richards}}]{msf+10}
+{M{\'e}nard}, B., {Scranton}, R., {Fukugita}, M., \& {Richards}, G. 2010,
+  \mnras, 405, 1025
+
+\bibitem[{{Morton}(2003)}]{morton03}
+{Morton}, D.~C. 2003, \apjs, 149, 205
+
+\bibitem[{{Murray} {et~al.}(2010){Murray}, {M{\'e}nard}, \& {Thompson}}]{mmt10}
+{Murray}, N., {M{\'e}nard}, B., \& {Thompson}, T.~A. 2010, ArXiv e-prints
+
+\bibitem[{{Murray} {et~al.}(2005){Murray}, {Quataert}, \& {Thompson}}]{mqt05}
+{Murray}, N., {Quataert}, E., \& {Thompson}, T.~A. 2005, \apj, 618, 569
+
+\bibitem[{{Neufeld}(1990)}]{Neufeld_1990}
+{Neufeld}, D.~A. 1990, \apj, 350, 216
+
+\bibitem[{{Nulsen} {et~al.}(1998){Nulsen}, {Barcons}, \& {Fabian}}]{nbf98}
+{Nulsen}, P.~E.~J., {Barcons}, X., \& {Fabian}, A.~C. 1998, \mnras, 301, 168
+
+\bibitem[{{Oppenheimer} \& {Dav{\'e}}(2006)}]{od06}
+{Oppenheimer}, B.~D., \& {Dav{\'e}}, R. 2006, \mnras, 373, 1265
+
+\bibitem[{{Pettini} {et~al.}(1998){Pettini}, {Kellogg}, {Steidel}, {Dickinson},
+  {Adelberger}, \& {Giavalisco}}]{pks+98}
+{Pettini}, M., {Kellogg}, M., {Steidel}, C.~C., {Dickinson}, M., {Adelberger},
+  K.~L., \& {Giavalisco}, M. 1998, \apj, 508, 539
+
+\bibitem[{{Pettini} {et~al.}(2002){Pettini}, {Rix}, {Steidel}, {Adelberger},
+  {Hunt}, \& {Shapley}}]{prs+02}
+{Pettini}, M., {Rix}, S.~A., {Steidel}, C.~C., {Adelberger}, K.~L., {Hunt},
+  M.~P., \& {Shapley}, A.~E. 2002, \apj, 569, 742
+
+\bibitem[{{Pettini} {et~al.}(2000){Pettini}, {Steidel}, {Adelberger},
+  {Dickinson}, \& {Giavalisco}}]{psa+00}
+{Pettini}, M., {Steidel}, C.~C., {Adelberger}, K.~L., {Dickinson}, M., \&
+  {Giavalisco}, M. 2000, \apj, 528, 96
+
+\bibitem[{{Phillips}(1993)}]{phillips93}
+{Phillips}, A.~C. 1993, \aj, 105, 486
+
+\bibitem[{{Prochaska} {et~al.}(2006){Prochaska}, {Chen}, \& {Bloom}}]{pcb06}
+{Prochaska}, J.~X., {Chen}, H.-W., \& {Bloom}, J.~S. 2006, \apj, 648, 95
+
+\bibitem[{{Prochaska} {et~al.}(2007){Prochaska}, {Chen}, {Dessauges-Zavadsky},
+  \& {Bloom}}]{pcd+07}
+{Prochaska}, J.~X., {Chen}, H.-W., {Dessauges-Zavadsky}, M., \& {Bloom}, J.~S.
+  2007, \apj, 666, 267
+
+\bibitem[{{Prochaska} \& {Wolfe}(2001)}]{pw01}
+{Prochaska}, J.~X., \& {Wolfe}, A.~M. 2001, \apjl, 560, L33
+
+\bibitem[{{Radovich} {et~al.}(2001){Radovich}, {Kahanp{\"a}{\"a}}, \&
+  {Lemke}}]{rkl01}
+{Radovich}, M., {Kahanp{\"a}{\"a}}, J., \& {Lemke}, D. 2001, \aap, 377, 73
+
+\bibitem[{{Rubin} {et~al.}(2010{\natexlab{a}}){Rubin}, {Prochaska},
+  {M{\'e}nard}, {Murray}, {Kasen}, {Koo}, \& {Phillips}}]{rubin+10c}
+{Rubin}, K.~H.~R., {Prochaska}, J.~X., {M{\'e}nard}, B., {Murray}, N., {Kasen},
+  D., {Koo}, D.~C., \& {Phillips}, A.~C. 2010{\natexlab{a}}, ArXiv e-prints
+
+\bibitem[{{Rubin} {et~al.}(2010{\natexlab{b}}){Rubin}, {Weiner}, {Koo},
+  {Martin}, {Prochaska}, {Coil}, \& {Newman}}]{rwk+10}
+{Rubin}, K.~H.~R., {Weiner}, B.~J., {Koo}, D.~C., {Martin}, C.~L., {Prochaska},
+  J.~X., {Coil}, A.~L., \& {Newman}, J.~A. 2010{\natexlab{b}}, \apj, 719, 1503
+
+\bibitem[{{Rupke} {et~al.}(2005{\natexlab{a}}){Rupke}, {Veilleux}, \&
+  {Sanders}}]{rvs05a}
+{Rupke}, D.~S., {Veilleux}, S., \& {Sanders}, D.~B. 2005{\natexlab{a}}, \apjs,
+  160, 87
+
+\bibitem[{{Rupke} {et~al.}(2005{\natexlab{b}}){Rupke}, {Veilleux}, \&
+  {Sanders}}]{rvs05b}
+---. 2005{\natexlab{b}}, \apjs, 160, 115
+
+\bibitem[{{Sato} {et~al.}(2009){Sato}, {Martin}, {Noeske}, {Koo}, \&
+  {Lotz}}]{smn+09}
+{Sato}, T., {Martin}, C.~L., {Noeske}, K.~G., {Koo}, D.~C., \& {Lotz}, J.~M.
+  2009, \apj, 696, 214
+
+\bibitem[{{Savage} \& {Sembach}(1996)}]{ss96}
+{Savage}, B.~D., \& {Sembach}, K.~R. 1996, \araa, 34, 279
+
+\bibitem[{{Scannapieco} {et~al.}(2006){Scannapieco}, {Pichon}, {Aracil},
+  {Petitjean}, {Thacker}, {Pogosyan}, {Bergeron}, \& {Couchman}}]{spa+06}
+{Scannapieco}, E., {Pichon}, C., {Aracil}, B., {Petitjean}, P., {Thacker},
+  R.~J., {Pogosyan}, D., {Bergeron}, J., \& {Couchman}, H.~M.~P. 2006, \mnras,
+  365, 615
+
+\bibitem[{{Schaye}(2001)}]{schaye01a}
+{Schaye}, J. 2001, \apjl, 559, L1
+
+\bibitem[{{Shapley} {et~al.}(2003){Shapley}, {Steidel}, {Pettini}, \&
+  {Adelberger}}]{shapley03}
+{Shapley}, A.~E., {Steidel}, C.~C., {Pettini}, M., \& {Adelberger}, K.~L. 2003,
+  \apj, 588, 65
+
+\bibitem[{{Silva} \& {Viegas}(2002)}]{silva02}
+{Silva}, A.~I., \& {Viegas}, S.~M. 2002, \mnras, 329, 135
+
+\bibitem[{{Simcoe} {et~al.}(2002){Simcoe}, {Sargent}, \& {Rauch}}]{ssr02}
+{Simcoe}, R.~A., {Sargent}, W.~L.~W., \& {Rauch}, M. 2002, \apj, 578, 737
+
+\bibitem[{{Snow} {et~al.}(1994){Snow}, {Lamers}, {Lindholm}, \&
+  {Odell}}]{sll+94}
+{Snow}, T.~P., {Lamers}, H.~J.~G.~L.~M., {Lindholm}, D.~M., \& {Odell}, A.~P.
+  1994, \apjs, 95, 163
+
+\bibitem[{{Sobolev}(1960)}]{sobolev60}
+{Sobolev}, V.~V. 1960, {Moving envelopes of stars}
+
+\bibitem[{{Socrates} {et~al.}(2008){Socrates}, {Davis}, \&
+  {Ramirez-Ruiz}}]{sdr08}
+{Socrates}, A., {Davis}, S.~W., \& {Ramirez-Ruiz}, E. 2008, \apj, 687, 202
+
+\bibitem[{{Somerville} {et~al.}(2001){Somerville}, {Primack}, \&
+  {Faber}}]{spf01}
+{Somerville}, R.~S., {Primack}, J.~R., \& {Faber}, S.~M. 2001, \mnras, 320, 504
+
+\bibitem[{{Steidel} {et~al.}(2010){Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}, \& {Rakic}}]{steidel+10}
+{Steidel}, C.~C., {Erb}, D.~K., {Shapley}, A.~E., {Pettini}, M., {Reddy}, N.,
+  {Bogosavljevi{\'c}}, M., {Rudie}, G.~C., \& {Rakic}, O. 2010, \apj, 717, 289
+
+\bibitem[{{Steidel} {et~al.}(1996){Steidel}, {Giavalisco}, {Pettini},
+  {Dickinson}, \& {Adelberger}}]{sgp+96}
+{Steidel}, C.~C., {Giavalisco}, M., {Pettini}, M., {Dickinson}, M., \&
+  {Adelberger}, K.~L. 1996, \apjl, 462, L17+
+
+\bibitem[{{Strickland} \& {Heckman}(2009)}]{sh09}
+{Strickland}, D.~K., \& {Heckman}, T.~M. 2009, \apj, 697, 2030
+
+\bibitem[{{Strickland} {et~al.}(2004){Strickland}, {Heckman}, {Colbert},
+  {Hoopes}, \& {Weaver}}]{shc+04}
+{Strickland}, D.~K., {Heckman}, T.~M., {Colbert}, E.~J.~M., {Hoopes}, C.~G., \&
+  {Weaver}, K.~A. 2004, \apj, 606, 829
+
+\bibitem[{{Swinbank} {et~al.}(2005){Swinbank}, {Smail}, {Bower}, {Borys},
+  {Chapman}, {Blain}, {Ivison}, {Howat}, {Keel}, \& {Bunker}}]{ssb+05}
+{Swinbank}, A.~M., {et~al.} 2005, \mnras, 359, 401
+
+\bibitem[{{Tasitsiomi}(2006)}]{Tomi_2006}
+{Tasitsiomi}, A. 2006, \apj, 645, 792
+
+\bibitem[{{Tremonti} {et~al.}(2007){Tremonti}, {Moustakas}, \&
+  {Diamond-Stanic}}]{tmd07}
+{Tremonti}, C.~A., {Moustakas}, J., \& {Diamond-Stanic}, A.~M. 2007, \apjl,
+  663, L77
+
+\bibitem[{{Veilleux} {et~al.}(2003){Veilleux}, {Shopbell}, {Rupke},
+  {Bland-Hawthorn}, \& {Cecil}}]{vsr+03}
+{Veilleux}, S., {Shopbell}, P.~L., {Rupke}, D.~S., {Bland-Hawthorn}, J., \&
+  {Cecil}, G. 2003, \aj, 126, 2185
+
+\bibitem[{{Verhamme} {et~al.}(2006){Verhamme}, {Schaerer}, \&
+  {Maselli}}]{Verhame_2006}
+{Verhamme}, A., {Schaerer}, D., \& {Maselli}, A. 2006, \aap, 460, 397
+
+\bibitem[{{Walter} {et~al.}(2002){Walter}, {Weiss}, \& {Scoville}}]{wws02}
+{Walter}, F., {Weiss}, A., \& {Scoville}, N. 2002, \apjl, 580, L21
+
+\bibitem[{{Weiner} {et~al.}(2009){Weiner}, {Coil}, {Prochaska}, {Newman},
+  {Cooper}, {Bundy}, {Conselice}, {Dutton}, {Faber}, {Koo}, {Lotz}, {Rieke}, \&
+  {Rubin}}]{wcp+09}
+{Weiner}, B.~J., {et~al.} 2009, \apj, 692, 187
+
+\bibitem[{{Westmoquette} {et~al.}(2008){Westmoquette}, {Smith}, \&
+  {Gallagher}}]{wsg08}
+{Westmoquette}, M.~S., {Smith}, L.~J., \& {Gallagher}, J.~S. 2008, \mnras, 383,
+  864
+
+\bibitem[{{York} {et~al.}(2006){York}, {Khare}, {Vanden Berk}, {Kulkarni},
+  {Crotts}, {Lauroesch}, {Richards}, {Schneider}, {Welty}, {Alsayyad}, {Kumar},
+  {Lundgren}, {Shanidze}, {Smith}, {Vanlandingham}, {Baugher}, {Hall},
+  {Jenkins}, {Menard}, {Rao}, {Tumlinson}, {Turnshek}, {Yip}, \&
+  {Brinkmann}}]{ykv+06}
+{York}, D.~G., {et~al.} 2006, \mnras, 367, 945
+
+\bibitem[{{Zheng} \& {Miralda-Escud{\'e}}(2002)}]{Zheng_2002}
+{Zheng}, Z., \& {Miralda-Escud{\'e}}, J. 2002, \apj, 578, 33
+
+\end{thebibliography}
+
+%\input{../Tables/table_atomic.tex}
+%\input{../Tables/tab_fiducial.tex}
+%\input{../Tables/tab_fiducial_ew.tex}
+%\input{../Tables/tab_meas_models.tex}
+%\input{../Tables/tab_plaw_parm.tex}
+%\input{../Tables/tab_meas_plaws.tex}
 
 %%%% RADIATIVE %%%%%%
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_radiation_nvt.ps}
-%\caption{
-%Radiation diagnosed
-%}
-%\label{fig:rad_nvt}
-%\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_rad_spec.ps}
-\caption{
-\ion{Mg}{2} and \ion{Fe}{2}
-profiles for a radiation-driven wind model (red) compared against the
-fiducial wind model (black).  In contrast to the fiducial model, the
-optical depth peaks at large velocity (here $\mdv
-\approx -350 \mkms$).  At these velocities, the absorption is not
-filled-in by scattered photons and one recovers absorption lines
-that closely resemble the intrinsic optical depth profile (dotted
-curve).  Although the \ion{Mg}{2} absorption profiles are very
-different from the fiducial model, the \ion{Mg}{2} line-emission has
-similar peak flux and velocity centroids 
-The \feiis\ emission also has a similar
-equivalent width, yet the lines are much broader in the
-radiative-driven model. 
-}
-\label{fig:rad_spec}
-\end{figure}
 
 %%%% POWER LAWS %%%%
-\begin{figure}
-\epsscale{0.8}
-\plotone{../Figures/fig_vary_profiles.ps}
-\caption{
-In panel (a) we illustrate the density (gray curves; dashed -- $\mnhn
-\propto r^0$, dotted -- $\mnhn \propto r^{-3}$, dot-dash -- $\mnhn
-\propto r^{-2}$) and velocity laws (colored; green -- $v \propto
-r^{0.5}$, red -- $v \propto r^{-1}$, blue -- $v \propto r^{-2}$) for a
-series of power-law models (Table~\ref{tab:plaw_parm}).  For
-comparison we also plot the velocity and density laws for the fiducial
-model (thin, black curves).  
-Panel (b) plots the optical depth profiles of the \mgiia\ line for
-the nine models built from the density and velocity laws of panel (a).
-Each of these were normalized to have peak optical depths of 10 to
-1000 and to be optically thin at small or large velocity.
-}
-\label{fig:plaws}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_plaw_spec.ps}
-\caption{
-\ion{Mg}{2} and \ion{Fe}{2} profiles for a series of power-law wind
-models (see Table~\ref{tab:plaw_parm} for details).  These panels reveal
-the diversity of absorption and emission that result from a set of
-intrinsic optical depth profiles that have relatively modest
-differences (Figure~\ref{fig:plaws}b).  As designed, all of the models
-show significant absorption blueward of systemic velocity.  As
-important, each shows strong line-emission at $\mdv \sim 0 \mkms$,
-with the flux proportional to the degree of absorption.
-We also note that the width of the \feiic\ emission scales with the
-velocity offset of peak optical depth for the \feiia\ absorption.
-Therefore, the emission kinematics trace the intrinsic
-optical depth profile.
-}
-\label{fig:plaws_spec}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_slit.ps}
-\caption{
-Absolute emission equivalent width ($|W_{\rm e}|$) relative to the observed
-absorption equivalent width ($W_{\rm a}$) for a series of transitions:
-(solid -- \mgiia; dotted -- \mgiib; dashed -- \feiib).  The
-\ewe/\ewabs\ ratio is plotted as a function of slit width relative to
-twice the radius \rtt, defined to be where the Sobolev optical depth 
-$\tau_S = 0.2$.  The black curves correspond to the fiducial wind
-model ($\S$~\ref{sec:fiducial}; $\mrtt \approx 15$\,kpc), the red curves are for the
-LBG-partial covering scenario ($\S$~\ref{sec:Covering}; $\mrtt \approx
-8$\,kpc), and the
-radiative-driven wind ($\S$~\ref{sec:radiative}; $\mrtt = XXX$) has blue curves.
-For all of the wind models, the $|W_{\rm e}|$/\ewabs\ ratio rises very steeply
-with slit width and then plateaus at $\approx \mrtt$.  
-Therefore, a slit that exceeds $\approx 0.5 \mrtt$ will admit nearly
-all of the photons scattered to our sightline.
-}
-\label{fig:obs_slit}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_ew.ps}
-\caption{
-Difference between the `observed' absorption equivalent width \ewabs\
-which includes the flux of scattered photons and the `intrinsic'
-equivalent width $W_{\rm i}$ that ignores photon scattering.  The
-dashed (dotted) curves trace a 50\%\ (10\%) reduction in \ewabs\
-relative to $W_{\rm i}$.  One notes a reduction in \ewabs\ by $\approx
-30-50\%$ for the \mgiia\ transition (the effect is generally larger
-for \mgiib).  The effects of scattered photons are reduced for the
-\ion{Fe}{2} transitions because a fraction (in fact a majority for
-\feiia) of the absorbed photons fluoresce as \feiis\ emission at
-longer wavelengths and do not `fill-in' the absorption profiles.
-}
-\label{fig:obs_ew}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_peaktau.ps}
-\caption{
-The observed peak optical depth $\tau_{\rm pk} \equiv -\ln [I_{\rm
-  min}]$ for \mgiia\ profiles of the wind models studied in this paper
-(Tables~\ref{tab:line_diag}, \ref{tab:plaw_diag}) with $I_{\rm min}$
-the minimum normalized intensity of the absorption profile.  Cases
-where \tpk\ exceeds 3 are presented as lower limits.  The \tpk\ values
-are plotted against the velocity $v_\tau$ where $I(v) = I_{\rm min}$.  In all
-of the models, the true peak optical depth $\mtpk^{\rm true} > 10$.
-The much lower `observed' \tpk\ values occur because scattered \mgiia\
-photons have filled-in the absorption profiles at velocities $\mdv
-\gtrsim -400 \mkms$. These effects, therefore, are greatest for wind
-models where the optical depth peaks near $\mdv \sim 0 \mkms$ because
-the majority of scattered photons have this relative velocity.
-Indeed, models with $v_\tau < -400 \mkms$ all show $\mtpk > 3$.
-}
-\label{fig:obs_peaktau}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_vtau.ps}
-\caption{
-Comparison of the velocities for which the \feiia\ and \mgiia\ absorption
-profiles have greatest depth.  Results for all of the models
-studied in this paper are presented (Tables~\ref{tab:line_diag},
-\ref{tab:plaw_diag}).  
-It is evident that wind models with a peak optical depth near the
-systemic velocity have a \mgiia\ absorption profile shifted blueward
-by one to several hundred \kms.  Analysis of such profiles may lead to
-the false conclusion 
-that (i) the majority of mass in the wind is travelling at a higher
-velocity; and (ii) there is no gas with $\mdv \sim 0 \mkms$.
-The dashed curve traces the one-to-one line.
-}
-\label{fig:obs_vtau}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_lris.ps}
-\caption{
-`Observations' of the \ion{Mg}{2} profiles for the ISM+wind model.  
-(a) The true profile (dotted lines) have been convolved with a
-Gaussian line-spread-function (FWHM~$= 250 \mkms$) and noise has been
-added to give a S/N=7 per pixel.  Note the suppressed peak in 
-line-emission; one may even infer the flux of \mgiia\ exceeds that of
-\mgiib.  The \mgiia\ absorption is also shifted to
-shorter wavelengths, i.e.\ to a greater velocity offset from systemic.  
-(b) The solid curve shows a stack of 100 spectra of the ISM+wind
-profile, each degraded to a S/N=2 per pixel, and offset from systemic
-by a normal deviate with $\sigma = 100 \mkms$ to mimic uncertainty in
-the redshift of the galaxy.  
-This treatment is meant to illustrate the
-implications of stacking galaxy spectra to study outflows
-\citep[e.g.][]{wcp+09,smn+09,rwk+10}.   The main difference from the
-single galaxy observation shown in panel (a) is the smearing of
-line-emission and absorption that reduces the height/depth of each.
-The effects would likely be even more pronounced if one studied spectra with
-a diversity of \ion{Mg}{2} profiles.    
-}
-\label{fig:obs_lris}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_sb.ps}
-\caption{
-Surface brightness profiles of the fiducial wind model for the \mgiia\
-(solid) and \feiie\ (dotted) transitions.  Both profiles peak at small
-radii and decrease by several orders of magnitude before reaching the
-outer edge of the wind.  The profiles are sufficiently shallow,
-however, that the azimuthally integrated flux declines by only a
-factor of $\approx 10$ from $r = 1$\,kpc to $r=10$\,kpc.  Therefore, a
-sensitive IFU observation could map the emission (and, in principle,
-the kinematics) from $r_{\rm inner}$ to approximately $r_{\rm outer}$.
-}
-\label{fig:obs_sb}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{../Figures/fig_obs_edelv.ps}
-\caption{
-Plot of the 90\%\ velocity width ($\Delta v_e$) of \feiic\ emission versus the
-velocity where the resonance lines achieve peak optical depth
-$v_\tau$ in absorption.  The $\Delta v_e$ values rise steadily with
-increasing offset of $v_\tau$ from systemic.  The width of the \feiic\
-emission line, therefore, offers an independent diagnostic of the wind
-speed.
-}
-\label{fig:obs_edelv}
-\end{figure}
 

### 2011-03-29 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5794 ac11df5e-a788-c23b-a8e1-c758c323924d

--- 2010-08-16 Winds/papers/Theory/First/wind_simple.tex
@@
 
-\title{Idealized Wind Models of Cool Gas Outflows}
+\title{The Emperor Has No Clothes}
 
@@
 \begin{abstract}
-\begin{itemize}
-\item Emission is a generic feature of (nearly) isotropic winds.  This
-  emission fills in absorption at $v \approx 0$, significantly
-  complicating the absorption-line analysis, especially of an ISM
-  component. 
-\item The relative strengths of the emission
-lines, therefore, is sensitive to both the opacity and velocity
-extent of the wind.
-\end{itemize}
+We consider the observed \lya\ emission from Lyman Break Galaxies
+(LBGs) and their surrounding environment in the context of the LBG
+clump model proposed by \cite{steidel10}.  This model does not
+reproduce the observations: the systematic redshift of \lya\ is not a
+natural prediction of a clumpy wind and the clump model has too low
+covering fraction and velocity graident to yield significant scattered
+emission at large impact parameter.  We also consider the mass, mass
+flux, energy, and power of this wind model and find that one requires
+extreme quantities.  [Mention Lya emission here?]
+[Mention most of the mass in the wind accounts for very little EW in
+the down-the-barell observations]
+We argue that this model is an inaccurate description of the CGM
+surrounding high-$z$ star-forming galaxies, and that the observed
+outflow is likely confined to $r \lesssim 10$\,kpc.
 \end{abstract}
@@
 
-Nearly all gaseous objects that shine are also
-observed to generate gaseous flows.  This includes the jets of protostars, the
-stellar winds of massive O and B stars, the gentle Solar wind
-of our Sun, the associated absorption of bright quasars, and the
-spectacular jets of radio-loud AGN.   These gaseous outflows moderate
-the accretion of new material onto the object, inject energy and
-momentum into gas on large scales, and ...
-Developing a comprehensive model for these flows is critical to
-understanding the evolution of the source and its impact on the
-surrounding environment.
+Spectroscopic observations of star-forming galaxies reveal that 
+systems at all redshifts experience outflows of cool, diffuse gas
+\citep[e.g.][]{rupke,weiner,shapley03,rubin}.  The indisputable
+signature is the preponderence of significant low-ion absorption
+(e.g.\ \ion{Na}{1}, \ion{Mg}{2}, \ion{Si}{2}) that is
+blueshifted with respect to the galaxy's stars and nebular regions.
+These data characterize the kinematics of the outflow and may place
+constraints on the optical depth and/or covering fraction of the
+material.  These ``down-the-barrel'' observations, however, provide
+very weak constraints on the distance of the gas from the galaxy.
+Therefore, the mass, energy, and power of the wind and its subsequent
+affect on the so-called circumgalactic medium of the galaxy remain
+open and compelling questions.
 
-Star-burst galaxies, whose luminosity is dominated by \ion{H}{2} regions
-and massive stars, are also observed to drive gaseous outflows.  These
-flows are generally expected (and sometimes observed) to have multiple
-phases, for example a hot and diffuse phase traced by X-ray emission
-together with a cool, denser phase traced by H$\alpha$ emission 
-\citep[e.g.][]{shc+04,km10}. 
-Several spectacular
-examples in the local universe demonstrate that flows can extend to
-tens of kpc from the galaxy \citep{M87} carrying significant speed
-to escape from the gravitational potential well of the galaxy's dark
-matter halo \citep{wind_escape}.
+At $z\sim 3$, the most extensively observed poplution of star-forming
+galaxies is the Lyman Break Galaxies (LBGs), named for their
+characteristic dip in flux from absorption by the intergalactic medium
+(IGM).  For the past $\sim 15$ years, the group led by C. Steidel has
+amassed the largest spectroscopic and imaging datasets on these
+galaxies \citep{steidel96,shapley03,reddyXX}.  These earlier works
+demonstrated nearly ubiquitous absorption from low and high-ion
+transitions that is systematically blue-shifted relative to the
+galaxy's stars and nebular emission.  These same spectra also revealed
+a diversity of \lya\ emission lines whose properties correlate with galaxy photometric
+and spectroscopic properties \citep{shapley08,cooke08}.  Irrespective
+of the \lya\ equivalent widths \wlya\, however, the line is uniformly
+shifted redward of systemic.  This has been interpted by numerous
+authors as yet another signature of the outflow
+\citep[e.g.][]{pettini,verhamme}.
 
-Beyond $z \sim 0$, galactic outflows are 
-revealed by UV and optical absorption lines, e.g.\ \ion{Na}{1},
-\ion{Mg}{2}, \ion{Si}{2} and \ion{C}{4} transitions.  With the galaxy
-as a backlight, one observes gas that is predominantly
-blue-shifted which indicates a flow toward
-Earth and away from the galaxy.  These transitions are sensitive to
-the cool (\ion{Mg}{2}; $T \sim 10^4$K) and warm (\ion{C}{4}; $T \sim
-10^5$K) phases of the flow.  The incidence of cool gas outflows is
-nearly universal in star-forming galaxies;  this includes systems at $z \sim 0$
-which exhibit \ion{Na}{1} and \ion{Mg}{2} absorption
-\citep{rvs05a,martin05,smn+09}, $z \sim 1$ star-forming galaxies traced by
-\ion{Fe}{2} and \ion{Mg}{2} transitions \citep{wcp+09,rubin09}, and
-$z>2$ Lyman break galaxies (LBGs) that show blue-shifted \ion{Si}{2},
-\ion{C}{2}, and \ion{O}{1} transitions \citep{sgp+96,lkg+97,shapley03}.
+Recently, their
+collaboration has published two papers that offer new insight into the
+CGM surrounding LBGs.   In one experiment \citep[][hereafter
+S+10]{steidel+10}, the authors have stacked low S/N, moderate
+resolution ($R \sim XX$) spectra of background galaxies at the
+rest-wavelengths of foreground LBGs with impact parameters $\rho \sim
+10-100$\,kpc.  This analysis revealed that LBGs are surrounded by a
+CGM that gives rise to \ion{H}{1}, low-ion (e.g.\ \ion{C}{2}~1334,
+\ion{Si}{2}), and high-ion (e.g.\ \ion{C}{4}) absorption from $\rho
+\approx 0-100$\,kpc.  S+10 modeled the blue-shifted absorption
+observed down-the-barrel with the extended absorption detected to
+large impact parameter as a clumpy, galactic-scale wind with speeds of
+$v \sim 800 \, \mkms$ and radial extend $r \sim 100$\,kpc.  Although
+this wind model is not a unique interpretation of the extend
+\ion{H}{1} absorption \citep{fpk+11}, it appears to satisify the key
+absorption observations.
 
-The observation of metal-line absorption is now a well established
-means of identifying outflows. Very little research,
-however,  has been directed
-to comparing the observations against (even idealized) wind
-models.  Instead, researchers have gleaned what limited information
-is afforded by direct analysis of the absorption lines.  The data do yield
-robust measurements of the speed of the gas yet they poorly constrain the
-optical depth, covering fraction, density, temperature, and distance
-of the flow from the galaxy.   In turn, constraints related to the
-mass, energetics, and momentum of the flow suffer from
-orders of magnitude uncertainty.  Both the origin and impact of
-galactic-scale winds, therefore, remain open matters of debate
-\citep{debate}.
-
-Recent studies of $z \sim 1$ star-forming galaxies have revealed that
-the cool gas often exhibits significant resonant-line emission (e.g.\
-\ion{Mg}{2}) in
-tandem with the nearly ubiquitous blue-shifted absorption
-\citep{wcp+09,rubin09,rubin+10b}.  The resultant spectra resemble the P-Cygni
-profile characteristic of stellar winds.
-\cite{rubin+10a} have also detected line
-emission from non-resonant \ion{Fe}{2}$^*$ transitions 
-Their interpretation is that the emission is the result of photons
-scattered off the wind into our sightline, analogous to P-Cygni.
-\cite{rubin+10a} also observed spatially extended \ion{Mg}{2} emission
-which they use to estimate the size of the outflow.  They infer that
-the wind extends to at least 5\,kpc from the galaxy.  Line emission is
-also observed for $z \sim 3$ LBGs in the resonant \lya\ transition
-and non-resonant \ion{Si}{2}$^*$ transitions \citep{prs+02,shapley03}.
-A comprehensive analysis of the emission lines
-related to galactic-scale outflows
-(e.g.\ via deep integral-field-unit observations) may offer unique
-diagnostics on the morphology and density of the outflow, eventually
-setting tighter constraints on the energetics of the flow.
-
-[Phillips first reported?]
-Bright \ion{Mg}{2} and \ion{Fe}{2}* line emission has also been
-reported for individual galaxies at $z \sim 0.7$ by \cite{rubin+10b}
-and \cite{rubin+10c}.   
-\cite{wcp+09}, who
-studied \ion{Mg}{2} absorption in $z \sim 1.4$ galaxies, reported
-\ion{Mg}{2} emission in a small subset of the individual galaxy
-spectra of their large sample.  These were excluded from the full
-analysis on concerns that the emission was related to AGN activity.
-The stacked spectra of the remaining galaxies, however, also indicated
-\ion{Mg}{2} emisison, both directly and when the authors modeled and
-`removed' the $v \approx 0\mkms$ absorption component.  Although the
-authors suggested the emission could be related to back-scattered
-light in the wind, they also allowed that it could be related to weak
-AGN activity.   Very similar \ion{Mg}{2} emission was observed by
-\cite{rubin+10b} who repeated the analysis of \cite{wcp+09} on a set
-of lower redshift galaxies. 
-[Did Kate see FeII* emission in her stacks? If not, why not?]
-
-Although astronomers are rapidly producing a wealth of observational
-datasets on galactic-scale winds, a key ingredient to a proper
-analysis is absent.
-[Draw analogy to exploring SN lightcurves and spectra]
-
-In this paper, we take the first steps toward modeling the absorption
-and emission properties of cool gas outflows.  Using Monte Carlo
-radiative transfer techniques, we study the nature of \ion{Mg}{2} and
-\ion{Fe}{2} absorption and emission for winds with a range of
-properties.  Although the winds are idealized, the results frequently
-contradict our intuition and 
-challenge the straightforward conversion of observables to (even crude) physical
-constraints.  [Add another line or two]
-
-The paper is organized as follows.  In $\S$~\ref{sec:method}, we
-describe the methodology of our radiative transfer algorithms.  These
-are applied to a fiducial wind model in $\S$~\ref{sec:fiducial} and
-variations of this model in $\S$~\ref{sec:variants}.  In
-$\S$~\ref{sec:alternate}, we explore wind models with a broader range
-of density and velocity laws.  Consideration of key observables is
-given in $\S$~\ref{sec:obs} and we discuss the principal results
-in $\S$~\ref{sec:discuss}.  A brief summary is given in
-$\S$~\ref{sec:summary}.
-
-\section{Methodology}
-\label{sec:method}
-
-This section describes our methodology for generating
-emission/absorption profiles from simple wind models.
-
-\subsection{The Radiative Transitions}
-
-In this paper, we focus on two sets of radiative transitions
-arising from Fe$^+$ and Mg$^+$ ions
-(Table~\ref{tab:atomic}, Figure~\ref{fig:energy}).
-This is a necessarily limited
-set, but the two ions and their transitions do have characteristics
-shared by the majority of low-ion transitions
-observed in cool-gas outflows. Therefore, many
-of the results that follow may be generalized to observational studies that
-consider other atoms and ions of cool gas.
-
-The Mg$^+$ ion, with a single 3s electron in the ground-state,
-exhibits an alkali doublet of transitions at $\lambda \approx
-2800$\AA\ analogous to the
-\lya\ doublet of neutral hydrogen.  Figure~\ref{fig:energy}
-presents the energy level diagram for this 
-\mgiid\ doublet.  In non-relativistic quantum
-mechanics, the 2p$^6$3p energy level is said to be split by spin-orbit
-coupling giving the observed line doublet.  These are the only
-\ion{Mg}{2} electric-dipole transitions 
-with wavelengths near 2800\AA\ and the transition connecting
-the $\rm {}^2P_{3/2}$ and $\rm {}^2P_{1/2}$ states is forbidden by several
-selection rules.  Therefore, an absorption from
-\maconfig~$\to$~\mbconfig\
-is followed $\approx 100\%$ of the time by a spontaneous decay
-($t_{\rm decay} \approx 4\sci{-9}$s) to the
-ground state. Our treatment will ignore any other possibilities
-(e.g.\ absorption by a second photon when the electron is at the \mbconfig\ level).
-
-In terms of radiative transfer, the 
-\mgiid\ doublet is very similar to that for \ion{H}{1}
-\lya, the \naid\ doublet, and many other doublets commonly
-studied in the interstellar medium (ISM) of distant galaxies.  
-Each of these has the ground-state connected to a pair of electric
-dipole transitions with nearly identical energy.
-The doublets differ only in 
-their rest wavelengths and the energy of the doublet separation. 
-For \ion{H}{1} \lya, the
-separation is sufficiently small ($\Delta v = c \Delta E / E \approx
-1.3 \mkms$) that most radiative transfer treatments actually ignore it
-is a doublet.
-This is generally justifiable for \lya\ because 
-most astrophysical processes have turbulent motions that
-significantly exceed the doublet's velocity separation and effectively mix the
-two transitions.  For \ion{Mg}{2} ($\Delta v \approx 770 \mkms$),  
-\ion{Na}{1} ($\Delta v \approx 304 \mkms$), and most of the other doublets
-commonly observed, the separation is large and the transitions
-must be treated separately.
-
-Iron exhibits the most complex set of energy levels for elements
-frequently studied in astrophysics.  The Fe$^+$ ion alone has over
-10,000 energy levels recorded \citep{iron}, and even this is an
-incomplete list.  
-One reason for iron's complexity is
-that the majority of its configurations exhibit fine-structure splitting.
-This includes the ground-state configuration (\aconfig) which is split
-into 5 levels, 
-labeled by the total angular momentum $J$, 
-with excitation energies $T_{\rm ex} \equiv \Delta E / k$ ranging from
-$T_{\rm ex} \approx 500-1500$\,K (Figure~\ref{fig:energy}).  
-Transitions between these fine-structure levels are 
-forbidden (magnetic-dipole) and have spontaneous decay times of several hours.
-
-In this paper, we examine transitions between the ground-state
-configuration and the energy levels of the \zconfig\
-configuration.  This set of transitions (named the
-UV1 multiplet) have wavelengths near 2600\AA.
-There are two resonance-line transitions\footnote{We adopt the
-  standard convention that a ``resonance line'' is an electric-dipole
-  transition connected to the ground-state.  We also label
-  non-resonant transitions with an asterisk, e.g.\ \feiic.} 
-associated with this multiplet (\feiid)
-corresponding to $\Delta J = 0, -1$; these are indicated by upward (black) arrows
-in Figure~\ref{fig:energy}. The solid (green) downward
-arrows in Figure~\ref{fig:energy} mark the non-resonant \feiis\
-transitions that are connected to
-the upper energy levels of the resonance lines.  These transitions may
-occur following the absorption of a single photon by Fe$^+$ in its
-ground-state.   This process may also be referred to as flourescence.
-
-The Figure also shows (as dashed, downward arrows) two of the
-\feiis\ transitions that connect to higher energy levels of the \zconfig\
-configuration.  Ignoring collisions and recombinations, these
-transitions may only occur after the absorption
-of two photons: one to raise the electron from the ground-state to an
-excited state and another to raise the electron from the excited state
-to one of the \zconfig\ levels with $J \le 5/2$.  The excitation of
-fine-structure levels by 
-the absorption of UV photons is termed indirect UV pumping
-\citep[e.g][]{silva02,pcb06} and requires the ion to lie
-near an intense source of UV photons.  
-Even a bright, star-forming galaxy emits too few photons at $\lambda
-\approx 2500$\AA\ to UV-pump Fe$^+$ ions that are farther than $\sim
-100$\,pc from the stars.
-In the
-following, we will assume that emission from this process is
-negligible.
-
-Our calculations also ignore collisional
-processes\footnote{Recombination is also ignored.}, i.e.\ collisional
-excitation and de-excitation of the various levels.  For the
-fine-structure levels of the \aconfig\ configuration, the excitation
-energies are modest ($T_{\rm ex} \sim 1000$\,K) but the critical
-density $n_c$ is large.  For the \aconfig$_{9/2} \to
-$\aconfig$_{7/2}$ transition, the critical density $n_e^C \approx 4
-\sci{5} \cm{-3}$.  At these densities, one would predict  
-detectable quantities of \ion{Fe}{1} which has not yet been observed
-in galactic-scale outflows. Furthermore, observations rarely show
-{\it absorption} from the
-fine-structure levels of the \aconfig\ configuration and that material
-is not significantly blue-shifted (Rubin et al., in prep). 
-In the following, we assume that electrons only occupy the
-ground-state, i.e.\ the gas has zero opacity to the non-resonant
-lines.
-If collisional excitation is insignificant 
-then one may also neglect collisional de-excitation.  
-Regarding the \ion{Mg}{2} doublet, its
-excitation energy is significantly higher implying 
-negligible collisional processes at essentially any density.
-
-\subsection{The Source}
-
-Nearly all of the absorption studies of galactic-scale outflows 
-have focused on intensely, star-forming galaxies.  The
-intrinsic emission of these galaxies is a complex combination of
-stars and \ion{H}{2} regions that is then modulated by dust and gas
-within the interstellar medium (ISM).  For the spectral regions studied
-here, most stars show a featureless continuum but a few spectral
-types do show significant \ion{Mg}{2} and \ion{Fe}{2} absorption.
-{\bf [Kate: Any emission??]}  \ion{H}{2} regions, meanwhile, are observed to emit
-at the \mgiid\ doublet, primarily due to recombinations in the outer
-layers {\bf [Kate: How about FeII?]}.  It is beyond the scope of this paper to
-properly model the 
-stellar absorption and \ion{H}{2} region emission, but the reader
-should be aware that they can complicate the observed spectrum,
-independent of the outflow, especially at velocities $v \approx 0 \mkms$.
-In the following, we assume a simple flat continuum 
-normalized to unit value.  The size of the emitting
-region $r_{\rm source}$ is a free parameter, but we restrict its value
-to be smaller than the minimum radial extent of any gaseous
-component.
-
-\subsection{Monte Carlo Algorithm}
-
-[Describe 1D and 3D algorithms]
-
-[Put tests in an Appendix?]
-
-\subsection{Dust}
-\label{sec:dust_method}
-
-For the majority of models studied in this paper, we assume the gas
-contains no dust.
-This is an invalid assumption, especially for material associated with
-the ISM of a galaxy.  
-Extraplanar material likely associated with a galactic-scale 
-outflow has been observed to emit IR radiation characteristic of dust \citep[e.g.][]{M87_dust}.
-Essentially all astrophysical environments that contain both cool gas
-and metals also show signatures of dust depletion and extinction.  This includes the
-ISM of star-forming and \ion{H}{1}-selected galaxies
-\citep[e.g.][]{ss96,pw01,pcd+07}, strong \ion{Mg}{2} metal-line
-absorption systems \citep{ykv+06,mnt+08}, and the galactic winds traced
-by low-ion transitions \citep{prs+02,rvs05b}.  Although the galactic winds
-traced specifically by \ion{Mg}{2} and \ion{Fe}{2} transitions have not (yet) been
-demonstrated to contain dust, it is reasonable to consider its
-effects.
-In addition, \cite{msf+10} have argued from a statistical analysis
-that dust is distributed to many tens kpc from $z \sim 0.1$ galaxies
-and have suggested it was transported from the galaxies by
-galactic-scale winds.  One is motivated, therefore, to consider
-models that include the effects of dust extinction.
-
-For analysis on normalized spectra, the effects of dust are largely minimized; 
-dust has a nearly constant opacity over small spectral regions and all
-features are simply scaled together.
-For scattered and resonantly trapped photons, however, the relative effect of dust
-extinction can be much greater.  
-These photons travel a much longer distance to escape the medium and
-may experience a much higher integrated opacity from dust.
-Indeed, dust is frequently invoked to
-explain the weak (or absent) \lya\ emission from star-forming galaxies
-\citep[e.g.][]{shapley03}.  Although the transitions studied here have
-much lower opacity than \lya, dust could still play an important role
-in the predicted profiles.
-
-In a few models, we include absorption by dust under the following
-assumptions:
-(i) the dust opacity scales with the density of the gas (i.e.\ we
-adopt a fixed dust-to-gas ratio);
-(ii) the opacity is independent of wavelength, a reasonable
-approximation given the small spectral range analyzed;
-(iii) the photons absorbed by dust are re-emitted at IR wavelengths
-and are `lost' from the system.  The dust absorption is normalized by \taud, 
-the integrated opacity of dust from the center of the system to
-infinity.  The ambient ISM of a star-forming galaxy may be expected to exhibit
-\taud\ values of one to a few at $\lambda \sim 3000$\AA\ \citep[e.g.][]{dust_again}.
-
-\subsection{The Sobolev Approximation}
-
-For a wind with a steep velocity law (i.e.\ a large gradient $dv/dr$)
-and/or a a narrow intrinsic profile (i.e.\ a small Doppler parameter),
-\citet{sobolev60} introduced a formalism that defines the opacity of
-the wind at a given radius $\tau(r)$ in terms of the density and
-velocity gradient of the flow at that radius:
-
-\begin{equation}
-\tau^S(r) = \kappa_\ell \rho(r) \, \lambda_\ell \ltp \frac{dv}{dr}
-\rtp^{-1}
-\label{eqn:Sobolev}
-\end{equation}
-where $\kappa_\ell$ is the opacity of transition $\ell$.  The opacity
-holds for a photon with wavelength $\lambda^S
-= \lambda_\ell (1-v(r)/c)$ with the velocity evaluated at the radius.
-This is, of course, not the true opacity.
-A photon with wavelength $\lambda^S$ that travels through the wind 
-experiences a total opacity 
-$\tau_\nu = \intl_0^\infty \rho(r) \kappa_\nu dr$.  The Sobolev
-approximation is valid when the opacity the photon experiences is
-domianted by gas in a localized portion of the flow that has velocity
-$v = c(\lambda^S/\lambda^\ell - 1)$.  In this case, $\tau^S$ provides an
-excellent approximation.  We find that it applies to nearly all of the
-models presented in this paper.  [Comment on the lack of the $b$-value
-in this?]
-
-\section{The Fiducial Wind Model}
-\label{sec:fiducial}
-
-In this section, we study a simple yet illustrative wind model for
-a galactic-scale outflow.  The properties of this wind were tuned, in
-part, to yield a \ion{Mg}{2} absorption profile 
-similar to those observed for $z \sim 1$, star-forming galaxies
-\citep{wcp+09,rubin+10c}.  We emphasize, however, that we do not
-favor this fiducial model over any other wind scenario nor do its
-properties have special physical motivation.
-Its role is to establish a baseline
-for discussion.
-
-The fiducial wind is isotropic, dust-free, and extends from an inner wind
-radius $r_{\rm inner}$ to an outer wind radius $r_{\rm outer}$.  
-It follows a (mass-flux conserving) density law,
-
-\begin{equation}
-n_{\rm H} (r) = \frac{n^0_{\rm H}}{r^2} \;\;\; , 
-\label{eqn:density}
-\end{equation}
-and a velocity law with a purely radial flow
-
-\begin{equation}
-\vec v = v_r (r) \hat r = v_0 r \hat r  \perd
-\label{eqn:vel}
-\end{equation}
-Turbulent motions are
-characterized by a Doppler parameter\footnote{
-  The adopted Doppler parameter
-  ($\mbturb = 15 \mkms$) has a minor impact on the results.
-  The absorption profiles are insensitive to its value and varying \bturb\
-  only tends to modify the widths and modestly
-  shift the centroids of emission lines.} 
-, $b_{\rm turb}$.  
-We convert the hydrogen density $n_{\rm H}$ to the number densities of
-Mg$^+$ and Fe$^+$ ions by assuming solar relative abundances with an
-absolute metallicity of 1/2 solar and depletion factors of 1/10 and
-1/20 for Mg and Fe respectively, i.e.\  $\mnmg = 10^{-5.47} n_{\rm H}$ 
-and \nfe=\nmg/2. At the center of the wind is a homogeneous source of
-continuum photons with size $r_{\rm source}$. The parameters for the
-fiducial wind model are summarized in Table~\ref{tab:fiducial}.
-
-In Figure~\ref{fig:fiducial_nvt} we plot the density and velocity
-laws against radius;  
-their simple power-law expressions are evident.  The figure also
-shows the optical depth profile for the \mgiia\ transition
-($\tau_{2796}$), estimated from the Sobolev approximation\footnote{We
-  have verified this approxmiation holds by calculating 
-  $\tau_{2796}$ first
-  as a function of velocity by summing the opacity for a series of
-  discrete and small radial intervals
-  between $r_{\rm inner}$  and $r_{\rm outer}$.   We then mapped
-  $\tau_{2796}$ onto radius using the velocity law
-  (Equation~\ref{eqn:vel}). This optical depth profile is shown as the
-black dotted line in Figure~\ref{fig:fiducial_nvt}.}
-(Equation~\ref{eqn:Sobolev}).
-
-The $\tau_{2796}$ profile peaks with $\tau_{2796}^{\rm max} \approx 30$
-at a velocity $\mvr \approx 65 \mkms$ corresponding to $r \approx 1.3
-r_{\rm inner}$.  The optical depth profile for the \mgiib\ transition
-(not plotted) is scaled down by the $f\lambda$ ratio but is otherwise identical.  Similarly,
-the optical depth profiles for the \feiid\ transitions are
-scaled down by $f \lambda$ and the \nfe/\nmg\ ratio.
-
-Because the results are dictated by frequency dependence of the
-$\tau_{2796}$ profile, 
-the actual dimensions and density of the wind are
-essentially unimportant provided they scale together to give nearly the same
-optical depth. Therefore, one may consider the choices for
-$r_{\rm inner}, r_{\rm outer}, n_{\rm H}^0$ as arbitrary.
-Nevertheless, we adopted values for this fiducial model with
-some astrophysical motivation,  e.g., values that correspond to
-galactic dimensions and a normalization that gives $\tau_{2796}^{\rm
-  max} \sim 10$.
-
-Using the methodology described in $\S$~\ref{sec:method}, we
-propogated photons from the source and through the outflow to an
-`observer' at $r \gg r_{\rm outer}$ that views the entire wind+source
-complex.  Figure~\ref{fig:fiducial_1d} presents the 1D spectrum
-that this observer would record, with the unattenuated flux
-normalized to unit value.   The \ion{Mg}{2} doublet
-shows the canonical `P-Cygni profile' that characterizes a continuum
-source embedded within an outflow.  Strong absorption is evident at
-$\delta v  \equiv (\lambda/\lambda_0 - 1) < -50 \mkms$ in both transitions (equivalent widths, $W^{2796} =
-3.0$\AA\ and $W^{2803} = 1.3$\AA) and each shows emission at
-positive velocities.  For an isotropic and dust-free model, the
-total equivalent width of the doublet must be zero,
-i.e.\ every photon
-absorbed eventually escapes the system, typically at lower
-energy.  The wind simply shuffles the photons in frequency space.
-A simple summation of the absorption and emission equivalent widths
-(Table~\ref{tab:fiducial_EW}) confirms this expectation.
-
-Focusing further on the \ion{Mg}{2} absorption, one notes that the profiles lie
-well above zero intensity and have similar depth even though their $f\lambda$
-values differ by a factor of two.  In standard absorption line
-analysis, this is 
-the tell-tale signature of a `cloud' that has a high optical depth (i.e.\
-saturated) which only partially covers the emitting source
-\citep[e.g.][]{hamann+10}.  Our fiducial wind model, however, 
-{\it entirely covers the source}; the apparent partial covering must
-be related to a different effect.
-Figure~\ref{fig:noemiss} further emphasizes this point by comparing the 
-absorption profiles from Figure~\ref{fig:fiducial_1d} against an
-artificial model where no absorbed photons are 
-re-emitted.   As expected from the
-$\tau_{2796}$ profile (Figure~\ref{fig:fiducial_nvt}), this
-`intrinsic' model
-produces a strong \mgiid\ doublet that absorbs all photons at
-$\delta v \approx -100 \mkms$, i.e.\ $I_{2796}^{\rm min} = \exp(-\tau^{\rm
-  max}_{2796}) \approx 0$.
-The true model, in contrast, has been `filled in' at $\delta v \approx -100
-\mkms$ by photons scattered in the wind.  An
-absorption-line analysis that ignores these effects
-would (i) systematically underestimate the true optical
-depth and (ii) falsely conclude that the wind partially covers the
-source.  We will find that this
-[behaviour] is a generic result, even for wind models that include
-dust and are not fully isotropic.
-
-Turning to the emission profiles of the \mgiid\ doublet, one notes
-that they are also similar with comparable equivalent widths The
-flux of the \mgiib\ transition even exceeds that for \mgiia\ giving a
-line ratio that is far below the $2:1$ ratio that one may have naively
-expected. 
-[Does recombination predict 2:1??]
-The emission profiles are very similar because the gas is optically
-thick yielding comparable total absorption. 
-Furthermore, the flux from \mgiib\ actually exceeds the
-\mgiia\ emission because the wind speed is greater than the velocity separation
-of the doublet, $|\mvr|_{\rm max} > (\Delta v)_{\rm MgII}$.
-Therefore, the red wing of the
-\mgiia\ emission profile is partially absorbed by \mgiib\ and
-re-emitted at lower frequency.  We conclude that the relative
-strengths of the emission lines is sensitive to both the opacity and
-velocity extent of the wind.
-
-Now consider the \ion{Fe}{2} transitions:
-the bottom left panel of Figure~\ref{fig:fiducial_1d} covers the
-majority of the \ion{Fe}{2} UV1 transitions and several are
-shown in the velocity plot.  The line
-profile for \feiib\ is very similar to the \mgiid\ doublet;
-one observes strong absorption to negative velocities and strong
-emission at $\mdv > 0 \mkms$ producing a characteristic P-Cygni profile. 
-Splitting
-the profile at $\mdv = -50 \mkms$, we measure an equivalent width
-$W^{2600}_{\rm a} = 1.16$\AA\ in absorption and $W^{2600}_{\rm e} =
--0.94$\AA\ in emission (Table~\ref{tab:fiducial_EW}) for a total
-equivalent width of $W^{2600}_{\rm TOT} \approx 0.22$\AA.  
-In contrast, the \feiia\ resonance line shows much weaker emission and
-a much higher total equivalent width ($W^{2586}_{\rm TOT} = 0.49$\AA),
-even though the line has a $2 \times$ lower $f\lambda$ value.
-These differences between the \ion{Fe}{2} resonance lines (and with the
-\ion{Mg}{2} doublet) occur because of the complex of non-resonant
-\feiis\ transitions that are coupled to the resonance lines
-(Figure~\ref{fig:energy}).  Specifically, 
-resonance photons absorbed at \feiid\ have a finite probability of
-being re-emitted as a non-resonant photon which then escapes the system
-without further interaction.  The principal effects are to reduce the
-line emission of \feiid\ and to produce non-resonant line-emission (e.g.\
-\feiic).
-
-The reduced \feiia\ emission relative to \feiib\ is related to
-two factors:
-(i) there is an additional downward transition from the
-\zconfig$_{7/2}$ level and 
-(ii) the Einstein A
-coefficients of the non-resonant lines coupled to \feiia\ are comparable to and even
-exceed the Einstein A coefficient of
-the resonant transition.  In contrast, 
-the \feiie\ transition (associated with \feiib)
-has an approximately  $4\times$ smaller A coefficient than the
-corresponding
-resonance line.  Therefore, the majority of photons absorbed at
-$\lambda \approx 2600$\AA\ are re-emitted as \feiib\ photons whereas 
-the majority of photons absorbed at $\lambda \approx 2586$\AA\ are re-emitted 
-at longer wavelengths (\feiic\ or $\lambda 2632$).
-If we were to increase $\tau_{2600}$ (and especially if we include
-gas with $\mvr \approx 0 \mkms$) then the \feiib\ emission is
-significantly suppressed (e.g.\ $\S$~\ref{sec:ISM}).
-The total equivalent width, however, of the three lines connected to the
-\zconfig$_{7/2}$ upper level must still vanish (photons are conserved
-in this isotropic, dust-free model).
-
-The preceding discussion emphasizes the filling-in of resonance
-absorption at $\mdv
-\lesssim -50 \mkms$ and the generation of emission lines at $\mdv \approx
-0 \mkms$ by photons scattered in the wind.  To study the spatial
-extent of this emission, we mapped the emission of the fiducial
-model (see $\S$~\ref{sec:monte} for a description of the algorithm).
-The output is a set of surface-brightness maps in a series of 
-frequency channels yielding a
-dataset analogous to integral-field-unit (IFU) observations.  In
-Figure~\ref{fig:fiducial_ifu_mgii}, we present the output 
-at several velocities relative to the \mgiia\
-transition. At $\mdv = -250 \mkms$, where the wind has an optical
-depth $\tau_{2796} < 1$ (Figure~\ref{fig:fiducial_nvt}),
-the source contributes roughly half of the observed flux.  
-At $\mdv=-100 \mkms$, however, the
-wind absorbs all photons from the source and the observed emission is
-entirely from photons scattered by the wind.  This scattered emission
-actually exceeds the source+wind emission at 
-$\mdv = -250 \mkms$ such that the absorption profile is
-negatively offset from the velocity where $\tau_{2796}$ is maximal
-(Figure~\ref{fig:fiducial_nvt}).
-The net result is
-weaker \ion{Mg}{2} absorption that peaks blueward of the actual peak in the
-optical depth profile.  
-Table~\ref{tab:line_diag} reports several kinematic measurements of
-the absorption and emission features.
-Clearly, these effects complicate estimates for the
-speed, covering fraction, and total column density of the wind.  At
-$\mdv = 0 \mkms$, the wind and source have comparable total flux with the
-latter dominating at higher velocities.
-
-Similar results are observed for the \ion{Fe}{2} resonance
-transitions (Figure~\ref{fig:fiducial_ifu_feii}).
-For transitions to fine-structure levels of the \aconfig, the source
-is unattenuated but there is a significant contribution from photons
-generated in the wind. 
-The results presented in Figures~\ref{fig:fiducial_ifu_mgii} and
-\ref{fig:fiducial_ifu_feii} are sensitive to the radial extent,
-morphology, density and velocity profiles of this galactic-scale
-wind.  Consequently, IFU observations of line emission from low-ion
-transitions may offer the most direct constraints on galactic-scale
-wind properties.
-
-At all velocities, the majority of light comes from the inner regions
-of the wind. 
-The majority of
-\ion{Mg}{2} emission occurs within the inner few kpc, e.g.\ $50-60\%$
-of the light at $\mdv=-100$ to $+100 \mkms$
-comes from $|r| < 3$\,kpc.
-The emission
-is even more centrally concentrated for the \ion{Fe}{2} transitions.
-A proper treatment of these
-distributions is critical to interpret observations
-acquired through a slit, i.e.\ where the aperture has a limited extent
-in one or more dimensions.  A standard longslit on 10m-class
-telescopes, for example, subtends $\approx 1''$ corresponding to
-$5-10$\,kpc for $z \sim 1$.    We return to this issue in
-$\S$~\ref{sec:discuss}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Variations to the Fiducial Model}
-\label{sec:variants}
-
-In this section, we investigate a series of more complex wind
-scenarios
-through modifications to the fiducial model.  These include relaxing
-the assumption of isotropy, introducing dust, adding an ISM
-component within $r_{\rm inner}$, and varying the normalization of the
-optical depth profiles.
-
-\subsection{Anisotropic Winds}
-\label{sec:anisotropic}
-
-The fiducial model assumes an
-isotropic wind with only radial variations in velocity and density. 
-Angular isotropy is obviously an idealized case, but
-it is frequently assumed in studies of galactic-scale outflows
-\citep[e.g.][]{steidel+10}.   There are several reasons, however, to
-consider anisotropic winds.  Firstly, galaxies are not spherically
-symmetric;  the sources driving the
-wind (e.g.\ supernovae, AGN) are very unlikely to be isotropically distributed
-within the galaxy.  
-Secondly, the galactic ISM frequently has a disk-like morphology
-which will suppress the wind preferentially at low galactic latitudes,
-perhaps yielding a bi-conic morphology \citep[e.g.][]{M87}.
-Lastly, the galaxy could be surrounded by an
-anisotropic gaseous halo whose interaction would produce an irregular 
-outflow.
-
-With these considerations in mind, we reanalyzed the fiducial model
-with the 3D algorithm after departing from isotropy.  It is beyond the
-scope of this paper to explore a full suite of anisotropic profiles.
-We consider two simple examples: (i) half the fiducial model, where 
-the density is set to zero for $2\pi$ steradians.  This model is
-viewed from $\phi = 0^\circ$ (source uncovered) 
-to $\phi = 180^\circ$ (source covered); and 
-(ii) a bi-conical wind where the density is set to zero for angles
-$|\theta| < \theta_b$ that and is viewed along the plane of symmetry.
-
-The resulting \ion{Mg}{2} and
-\ion{Fe}{2} profiles for the half wind are compared against the fiducial model
-(isotropic wind) in Figure~\ref{fig:anisotropic}.  
-Examining the \mgiid\ doublet, 
-the $\phi = 0^\circ$ model only shows
-line-emission from photons scattered
-off the back side.  These photons, by definition, have $\mdv \gtrsim 0 \mkms$
-relative to line-center (a subset have $\mdv \lesssim 0 \mkms$ because
-of turbulent motions in the wind). 
-When viewed from the opposite direction ($\phi = 180^\circ$), the
-absorption lines dominate but there is still significant
-line-emission, at $\mdv \approx 0 \mkms$ and at $\mdv < 0 \mkms$ which fills
-in the absorption, from photons that scatter through the wind.  The
-key difference from the isotropic wind is the absence of photons
-scattered to $\mdv > 100 \mkms$;  this also implies deeper 
-\mgiib\ absorption at $\mdv \approx -100 \mkms$. The 
-shift in velocity centroid and asymmetry of the emission lines
-serve to diagnose the degree of wind isotropy, especially in
-conjunction with analysis of the absorption profiles. 
-The results are similar for the \feiid\ resonance lines.  The
-\ion{Fe}{2}$^* \; \lambda 2612$ line, meanwhile, shows most clearly the
-offset in velocity between the source unobscured ($\phi = 0^\circ$)
-and source covered ($\phi = 180^\circ$) cases.  The offset of the
-\feiis\ lines is the most significant 
-difference from the fully isotropic wind.
-
-[Add a paragraph on the bi-conical wind]
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Dust}
-\label{sec:dust}
-
-As described in $\S$~\ref{sec:dust_method}, 
-one generally expects dust in astrophysical environments that contain
-cool gas and metals.  This dust 
-modifies the observed wind profiles in two manners. 
-First, it is a source of opacity for all of 
-the photons.  This suppresses the flux at all
-wavelengths by $\approx \exp(-\mtaud)$ but because we re-normalize the
-profiles, this effect is essentially ignored.  Second, photons that are
-scattered by the wind must travel a greater
-distance to escape and therefore suffer from greater extinction.  A photon that is
-trapped for many scatterings may have a very high probability of being absorbed
-by dust.  
-Section~\ref{sec:dust_method} describes the details on our treatment of dust; we 
-remind the reader here that we assume a constant dust-to-gas ratio 
-that is normalized by the total optical
-depth \taud\ a photon would experience if it traveled from the
-source to infinity without scattering.
-
-In Figure~\ref{fig:dust}, we show the \ion{Mg}{2} and \ion{Fe}{2}
-profiles of the fiducial model ($\mtaud = 0$) against a series of
-models with $\mtaud > 0$.  For the \ion{Mg}{2} transitions, the
-dominant effect is the suppression of line emission at $\mdv \ge 0
-\mkms$.  These `red' photons have scattered off the
-backside of the wind and must travel a longer path than other
-photons.  Dust leads to a differential reddening that increases with 
-velocity relative to line-center. This is a natural consequence of dust
-extinction and is most evident in the \feiic\ 
-emission profile which is symmetrically distributed around
-$\mdv= 0 \mkms$ in the $\mtaud=0$ model.   In terms of absorption, the profiles are
-nearly identical for $\mtaud \le 3$.  One requires very high
-extinction to eventually produce a deepening of the profiles at 
-$\mdv \approx -100 \mkms$.
-
-% The following could go in the Discussion section
-We conclude that dust has only a modest influence on this fiducial model and,
-by inference, models with moderate peak optical depth and
-significant velocity gradients with radius (i.e.\ scenarios where the
-photons scatter one to a few times before exiting).
-For qualitative changes, one requires an extreme level of
-extinction ($\mtaud = 10$).  In this case, the source would be
-extinguished by 15\,magnitudes and could never be observed. 
-Even $\mtaud = 3$ is larger than typically inferred for the
-star-forming galaxies that drive outflows \citep[e.g.][]{dust}.
-For the emission lines,
-the dominant effect is a reduction in the flux 
-with a greater extinction at higher velocities relative to line-center.
-In these respects, dust extinction crudely mimics the behavior of the
-anisotropic
-wind described in Section~\ref{sec:anisotropic}. [Is there a
-distinguishing factor, e.g. flux of 2612/2600??]
-
-\subsection{ISM}
-\label{sec:ISM}
-
-The fiducial model does not include gas associated with
-the interstellar medium of the galaxy, i.e.\ material at $r \sim
-0$\,kpc with $v_{\rm r} \approx 0 \mkms$.  This allowed us to focus on
-results related solely to a wind component.  The decision to ignore the ISM
-was also motivated by the general absence of significant absorption at
-$\mdv \approx 0 \mkms$ in galaxies that exhibit outflows 
-\citep[e.g.][]{wcp+09,rubin09,steidel+10}.
-On the other hand, the stars that comprise the
-source are very likely embedded within and fueled by gas
-of the ISM.  
-Consider, then, a modification to the fiducial model that 
-includes an ISM. 
-Specifically, we assume the ISM component has density $n_{\rm H} = 1 \cm{-3}$ for
-$r_{\rm ISM} \le r < r_{\rm inner}$ with $r_{\rm ISM} = 0.5$\,kpc, 
-an average velocity of $\mvr = 0 \mkms$, and a larger turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-%Figure~\ref{fig:ISM} summarizes the model.
-The resultant optical depth profile $\tau_{2796}$ is identical to the
-fiducial model for $r > 2$\,kpc, has a slightly higher opacity at
-$r=1-2$\,kpc, and has a very large opacity at $r = 0.5-1$\,kpc.
-
-In Figure~\ref{fig:ISM_spec}, the solid curves show the \ion{Mg}{2} and
-\ion{Fe}{2} profiles for the ISM+wind and fiducial 
-models. In comparison, the
-dotted curve shows the intrinsic absorption profile for the ISM+wind
-model corresponding to the (unphysical) case
-where none of the absorbed photons are scattered or re-emitted.   Focus first on the
-\ion{Mg}{2} doublet.  As expected, the dotted curve shows strong
-absorption at $\mdv \approx 0 \mkms$ and blueward.  The full models,
-in contrast, show non-zero flux at these velocities and even a
-normalized flux exceeding unity at $\mdv \approx 0 \mkms$.  In
-fact, the ISM+wind model is nearly identical to the fiducial model;
-the only quantitative difference is that the velocity centroid of
-the emission lines are shifted redward by $\approx +100 \mkms$.
-We have also examined the spatial emission of this model and note
-qualitatively similar results to the fiducial wind model
-(Figures~\ref{fig:fiducial_ifu_mgii} and \ref{fig:fiducial_ifu_feii}).
-
-There are, however, several qualitative differences 
-for the \ion{Fe}{2} transitions. 
-First, the \feiia\ transition in the ISM+wind model
-shows much stronger absorption at $\mdv \approx 0$
-to $-100 \mkms$.  In contrast to the \ion{Mg}{2} doublet,
-the profile is not filled in by scattered photons. Instead, 
-the majority of \feiia\ photons that are absorbed are re-emitted as
-\feiis\~$\lambda\lambda 2612, 2632$ photons.  In fact, the
-\feiia\ profile very nearly matches the profile without re-emission 
-(compare to the dotted lines); this transition provides a
-very good description of the intrinsic ISM+wind optical depth profile.  
-We conclude that resonant transitions that are coupled to (multiple)
-non-resonant, electric dipole transitions offer the best
-diagnosis of ISM absorption.
-
-The differences in the \ion{Fe}{2} absorption profiles are reflected
-in the much higher strengths ($3-10\times$) of emission from
-transitions to the excited states of \aconfig.   This occurs because:
-(1) there is greater absorption by the \feiid\
-resonance lines; (2) the high opacity of the ISM component leads to
-an enhanced conversion of resonance photons with $\mdv \approx 0\mkms$
-into \feiis\ photons.  This is especially notable for the
-\feiib\ transition whose coupled \feiis\ transition shows an equivalent width nearly
-$10\times$ stronger than for the fiducial model.  The relative
-strengths of the \feiib\ and \feiie\ lines provide a direct
-diagnostic on the degree to which the resonance lines are trapped.
-[Comment:  this is a product of $\tau_{2600}$ and the velocity
-gradient]
-
-Because of the high degree of photon trapping within the ISM
-component, this model does suffer more from dust extinction than the
-fiducial model.  We have studied the ISM+wind model including dust
-with $\mtaud=1$ (normalized to include the ISM gas).  All of the 
-emission lines are significantly reduced.  The \ion{Mg}{2} emission is
-affect most because these lines are resonantly trapped.  The \feiis\
-emission is also reduced relative to the dust-free model, but the
-absolute flux still exceeds the fiducial model
-(Table~\ref{tab:line_diag}).
-[Should I show a figure?]
-
-\subsection{Varying $n_{\rm H}^0$}
-
-The final modification we applied to the fiducial model was to
-uniformly vary the normalization of the optical depth profiles.
-Specifically, we ran a series of additional models with $n_H^0$ at
-1/3, 3, and 10 times the fiducial value of $n_H^{0,f} = 0.1 \cm{-3}$.
-The resulting \ion{Mg}{2} and \ion{Fe}{2} profiles are compared
-against the fiducial model in Figure~\ref{fig:norm}.  Inspecting
-\ion{Mg}{2}, one notes that the models with 1/3 and $3 n_H^{0,f}$
-behave as expected.  Higher optical depth leads to greater \mgiia\
-absorption and stronger \mgiib\ emission such that the observed
-\mgiib\ absorption profile weakens.  In the extreme case for the
-normalization of $10 n_H^{0,f}$, the \mgiib\ absorption and \mgiia\
-emission have nearly disappeared and one primarily observes very
-strong \mgiia\ absorption and \mgiib\ emission.
-
-Similar behaviour is observed for the \ion{Fe}{2} transitions.
-Interestingly, the \feiia\ transiions never show significant emission,
-only stronger absorption with increasing $n_H^0$.  In fact, for $n_H^0
-> 2 n_H^{0,f}$ the peak optical depth of \feiia\ actually exceeds that
-for \feiib\ because the latter remains significantly filled-in by
-scattered photons.  [Is there a final point to make?]
-
-\subsection{Summary Table}
-
-Table~\ref{tab:line_diag} presents a series of quantitative measures
-for the \ion{Mg}{2} and \ion{Fe}{2} absorption and emission lines for
-the fiducial model ($\S$~\ref{sec:fiducial}) and a subset of the models
-presented in this section.  Listed are the absorption and emission
-equivalent widths ($W_{\rm a}, W_{\rm e}$), the peak optical depth
-for the absorption $\tau_{\rm pk}$, the
-velocity where the optical depth peaks $v_\tau$, the optical
-depth-weighted velocity centroid $v_{\bar \tau} \equiv \int dv \, v
-\ln[I(v)] / \int dv \ln[I(v)]$, the peak flux $f_{\rm pk}$ in
-emission, the velocity where the flux peaks $v_f$, and the
-flux-weighted velocity centroid of the emission line $v_{\bar f}$.
-We discuss several of these measures in $\S$~\ref{sec:discuss}.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Alternate Wind Models}
-\label{sec:alternate}
-
-\subsection{The Lyman Break Galaxy Model}
-\label{sec:lbg}
-
-The Lyman break galaxies (LBGs), UV color-selected galaxies at $z \sim 3$,
-exhibit cool gas outflows in \ion{Si}{2}, \ion{C}{2},
-etc.\ transitions with speeds up to 1000\,\kms\
-\citep[e.g.][]{lkg+97,pks+98}.
-Researchers have invoked these winds to explain enrichment of
-the intergalactic medium \citep[e.g.][]{aguirre,spa+06}, the origin of the
-damped \lya\ systems \citep{nbf98,schaye01a}, and the formation of
-`red and dead' galaxies \citep[e.g.][]{redgal}.  Although the
-presence of these outflows were established over a decade ago,
-the processes that drive them remain
-unidentified.  Similarly,  current estimates of the mass and energetics of the
-outflow suffer from orders of magnitude uncertainty.
-
-Recently, \citet[][; hereafter S10]{steidel+10} introduced a model to
-explain jointly the average absorption they observed
-toward a set of several hundred LBGs and the average absorption in gas
-observed transverse to these galaxies.  
-Their wind model is defined by two
-expressions: (i) a radial velocity law $\mvr(r)$ and (ii) the covering
-fraction of optically thick `clouds' $f_c(r)$.  For the latter, S10
-envision an 
-ensemble of small, optically thick $(\tau \gg 1)$ clouds that only
-partially cover a galactic-scale source.
-For the velocity law, they adopted the following functional
-form
-
-\begin{equation}
-\mvr = \ltp \frac{A_{\rm LBG}}{1-\alpha} \rtp^{1/2} \ltk r_{\rm
-  inner}^{1-\alpha} - r^{1-\alpha} \rtk^{1/2}
-\label{eqn:LBG_vlaw}
-\end{equation}
-with $A_{\rm LBG}$ the constant that sets the terminal speed,
-$r_{inner}$ the inner radius of the wind (taken to be 1\,kpc), and
-$\alpha$ the power-law exponent that describes how steeply the velocity curve rises.  Their
-analysis of the LBG absorption profiles implied
-a very steeply rising curve with $\alpha \approx 1.3$.
-This velocity expression is shown as a dotted line in 
-Figure~\ref{fig:LBG_Sobolev}a.
-
-The covering fraction of optically thick clouds, meanwhile, was assumed to have
-the functional form
-
-\begin{equation}
-f_c(r) = f_{c,max} \ltp \frac{r}{r_{\rm inner}} \rtp^{-\gamma} \cmma
-\label{eqn:covering}
-\end{equation}
-with $\gamma \approx 0.5$ and $f_{c,max}$ the maximum covering
-fraction.  From this expression and the velocity law, one can recover
-an absorption profile $I_{\rm LBG}(v) = 1 - f_c(r[v])$, written
-explicitly as
-
-\begin{equation}
-I_{\rm LBG}(v) = 1 - f_{c,max} \ltk r_{\rm inner}^{1-\alpha} - \ltp
-\frac{1-\alpha}{A_{\rm LBG}} \rtp v^2 \rtk^{\gamma/(\alpha-1)}
-\perd
-\label{eqn:LBG_I}
-\end{equation}
-The resulting profile for $f_{c,max} = 0.6$, $\gamma=0.5$,
-$\alpha=1.3$, and $A_{\rm LBG} = -192,000 \, \rm km^2 s^{-2} kpc^{-2}$ 
-is displayed in Figure~\ref{fig:LBG_Sobolev}b.
-
-In the following, we consider two methods to analyze the LBG wind.
-Both approaches assume isotropy and adopt the velocity law given by
-Equation~\ref{eqn:LBG_vlaw}.  In one model, we treat the cool gas as a
-diffuse medium with unit covering fraction and a radial density
-profile determined from the Sobolev approximation.  We then apply 
-the Monte Carlo methodology used for the other wind models to predict
-\ion{Mg}{2} and \ion{Fe}{2} line profiles.  In the other model,
-we modify our algorithms to more precisely mimic the concept of an
-ensemble of optically thick clouds with a partial covering fraction on
-galactic scales.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Sobolev approximation}
-\label{sec:Sobolev}
-
-As demonstrated in Figure~\ref{fig:LBG_Sobolev}, the wind velocity for
-the LBG model rises very steeply with increasing radius before
-flattening at large radii.  Under these conditions, the Sobolev
-approximation provies an accurate relation between the optical depth
-of the flowing medium to the
-density and velocity gradient ($d\mvr/dr$) of the gas.  In our case, we 
-generate the optical depth profile in velocity space using Equation~\ref{eqn:LBG_I},
-
-\begin{equation}
-\tau_{\rm LBG}(v) = -\ln \ltk I_{\rm LBG}(v) \rtk \perd
-\label{eqn:tauLBG}
-\end{equation}
-We then invert the Sobolev approximation (Equation~\ref{eqn:Sobolev})
-to derive the radial density profile:
-
-\begin{equation}
-n_{\rm LBG}(r) = \frac{\tau_{\rm LBG}(r) \; d\mvr/dr}{\kappa_\ell
-  \lambda} \cmma
-\label{eqn:Sobolev}
-\end{equation}
-with $\lambda$ the rest wavelength and $\kappa_\ell \equiv f\pi^2
-e^2/m_e c$.
-
-The solid curve in Figure~\ref{fig:LBG_Sobolev}a shows the
-resultant density profile for Mg$^+$ assuming that the \mgiia\ line
-follows the intensity profile drawn in Figure~\ref{fig:LBG_Sobolev}b. 
-This is a relatively extreme density profile.  From the inner radius
-of 1\,kpc to 2\,kpc, the density drops by over 2 orders of
-magnitude including nearly one order of magnitude over the first
-10\,pc.  Beyond 2\,kpc, the density drops even more rapidly, falling
-orders of magnitude from 2 to 100\,kpc.
-
-We verified that the Sobolev-derived density profile shown in
-Figure~\ref{fig:LBG_Sobolev}a
-reproduces the proper
-absorption profile by discretizing the gas into a series of layers
-and calculating the integrated absorption profile.  This
-calculation is shown as a dotted red curve in
-Figure~\ref{fig:LBG_Sobolev}b; it is an excellent
-match to the desired profile (black curve).
-To calculate the optical depth profiles for the other transitions, we
-assume $\mnfe = \mnmg/2$ and scale $\tau$ by the $f\lambda$ product.
-
-We generated \ion{Mg}{2} and \ion{Fe}{2} profiles for this wind
-using the 1D algorithm with no dust extinction; these are shown as
-red curves in Figure~\ref{fig:LBG_spec}.   For this analysis, one
-should focus on the \mgiia\ transition.  The dotted line in the Figure
-shows the intensity profile when one ignores re-emission
-of absorbed photons.  By construction, it is the exact profile\footnote{Note that
-  one should not make this comparison for the other transitions in
-  the Sobolev model because those are scaled down by $f\lambda$ and
-  for \ion{Fe}{2} the reduced Fe$^+$ abundance.} 
-described by Equation~\ref{eqn:LBG_I} and plotted in
-Figure~\ref{fig:LBG_Sobolev}b.   In comparison, the full model (solid,
-red curve)
-shows much weaker absorption, especially at $v = 0$ to $-300 \mkms$
-due to scattered photons.
-In this respect, our LBG-Sobolev model is an
-inaccurate description of the observations. The model
-also predicts significant emission in the \ion{Mg}{2} lines and several of
-the \ion{Fe}{2}$^*$ transitions.   Emission associated with cool gas
-has been observed for \ion{Si}{2}$^*$
-transitions in LBGs \citep{prs+02,shapley03}, but
-the \ion{Fe}{2}$^*$ transitions
-modeled here lie in the near-IR and have not yet been investigated.
-On the other hand, there have been no 
-reported detections of significant line-emission related to low-ion resonance
-transitions (e.g.\ \ion {Mg}{2}) in LBGs, only $z \le 1$ star-forming galaxies
-\citep{wcp+09,rubin09}.  
-The principal result is that the scattering and re-emission of
-absorbed photons significantly alters the predicted absorption profiles
-for the inputted model.  This is, of course, an unavoidable
-consequence of an isotropic, dust-free model with unit covering
-fraction.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\subsubsection{Partial Covering Fraction}
-\label{sec:Covering}
-
-In the previous sub-section, we described a Sobolev solution that
-reproduces the average absorption profile of LBGs in cool gas
-transitions when scattered photons are ignored.  A proper analysis
-that includes scattered photons,
-however, predicts line-profiles that are qualitatively
-different from the observations because these scattered photons fill-in
-absorption and generate significant line emission (similar to the
-fiducial wind model; $\S$~\ref{sec:fiducial}).
-This LBG-Sobolev model, however, differs from
-the one proposed by S10:  those authors proposed an ensemble of optically
-thick clouds with the (partial) covering fraction described by
-Equation~\ref{eqn:covering}, whereas the Sobolev model assumes
-a diffuse medium with a declining density profile but a unit covering
-fraction.  At face value, one may question whether this difference
-causes the contradictory results of the LBG-Sobolev model.
-
-To more properly model the LBG wind described in S10, we 
-performed the following Monte Carlo calculation.  First, we propogated
-a photon from the source until its velocity relative to line-center
-resonates with the wind (the photon escapes if this never occurs).
-The photon then has a probability $P = f_c(r)$ of scattering.  If it
-scatters, we track the photon until it comes into
-resonance again\footnote{Because this wind has a monotonically
-  increasing velocity law, the photon may only interact again if a
-  longer wavelength transition is available, e.g.\ \mgiib\ for a
-  scattered \mgiia\ photon.} or escapes the system.  In this model, all of the
-resonance transitions are assumed to have identical (high) optical
-depth.
-
-The results of the full calculation (absorption plus scattering) are
-shown as the black curve in Figure~\ref{fig:LBG_spec}.  Remarkably, the results
-are very similar to the LBG-Sobolev calculation; scattered photons fill-in
-the absorption profiles at $v \approx 0 \mkms$ and yield significant
-emission lines at $v \gtrsim 0 \mkms$ in the resonance
-lines. Furthermore, significant emission is observed 
-for the \feiis\ transitions, centered at $\mdv \approx 0 \mkms$.  
-In contrast to the \ion{Mg}{2} profiles, the predicted \ion{Fe}{2}
-lines (especially \feiia) much more closely resembl the intrinsic
-profiles (dotted curves).  This occurs because many of these
-absorbed photons flouresce into \feiis\ emission.
-The equivalent width of \feiia\ even exceeds that for \feiib, an
-inversion that, if observed, would strongly support this model.
-
-In principle, these differences may be reduced by increasing the
-assumed abundances of \nmg\ and \nfe.  A robust conclusion of our
-analysis, however, is that these simple models cannot reproduce the
-observed profiles of resonantly trapped lines like the \ion{Mg}{2}
-doublet because of the emission from scattered photons.  In order to
-achieve a significant opacity at $\mdv \approx 0 \mkms$, one must
-either suppress the line-emission (e.g.\ with severe dust extinction) 
-or include a substantial ISM component that absorbs light at $\mdv
-\gtrsim 0 \mkms$ (e.g.\ $\S$~\ref{sec:ISM}).  As we discuss in the
-following section, it is difficult (if not impossible) to fully
-suppress the line-emission.  This is especially true for a scenario
-with partial covering.
-
-Given the essentially perfect correspondence between the LBG-Sobolev and
-LBG partial covering models (for \mgiia), we are motivated to consider
-further the characteristics of the Sobolev model which has 
-an explicit density profile.  It is straightforward, then, to convert the density and
-velocity profiles into distributions of mass, energy, and momentum
-within
-the wind.  These are shown in cumulative form in
-Figure~\ref{fig:LBG_cumul}.  Before discussing the results, we offer
-two cautionary comments: (i) the conversion of \nmg\ to $n_{\rm H}$
-assumes a very poorly constrained scalar factor of $10^{5.47}$.  One
-should give minimal weight to the absolute values for any of the
-quantities;
-(ii) the Sobolev approximation is not a proper description of the S10
-LBG wind model.
-The primary result expressed by Figure~\ref{fig:LBG_cumul} is that the
-majority of energy, mass, and momentum in the wind is transported by
-the outer layers ($r > 20$\,kpc).  This is surprising given that the
-density is $\approx 5$~orders of magnitude lower at these radii than
-at $r = 1$\,pc.  [Is this unphysical?  Can we conflate it to then kill
-the S10 model?]
-
-We also caution that the \ion{C}{4} emission observed for LBGs
-\citep[e.g.][]{cb58} may result from the galactic-scale outflow, not
-only the expected stellar winds of massive stars.
-
-%%%%%%%%%%%%%%%%%%%%%%%
-\subsection{Radiation Pressure}
-
-[Kate: Write the details of velocity + density law]
-
-\begin{equation}
-\mvr(r) = 2\sigma \sqrt{R_g \ltp \frac{1}{R_0} - \frac{1}{r} \rtp
-   + \ln\ltp R_0/r \rtp }
-\end{equation}
-
-\begin{equation}
-n(r) = \frac{dM_{\rm wind}/dt}{r^2 v(r)}
-\end{equation}
-Similar to the fiducial wind model, this wind has a decreasing density
-law with $n_{\rm H}$ roughly proportional to $r^{-2}$ [CHECK].
-To produce a wind whose \mgiia\ optical depth profile peaks at 
-$\tau_{2796}^{\rm max} \gtrsim 10$, we set $R_g = r_{\rm inner} =
-1\,\rm kpc$, $R_0=20\,\rm kpc$, and $\sigma = 125 \mkms$.  The density
-and velocity peak at $r=r_{\rm inner}$ where $n_{\rm H}^0 = 0.07
-\cm{-3}$ and $\mvr = 380 \mkms$.  This corresponds to a mass flow of
-$0.63 \msun\; \rm yr^{-1}$.
-
-Figure~\ref{fig:rad_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
-profiles for a radiatively-driven wind model compared against the
-fiducial wind model.
-In contrast to the fiducial model, the
-velocity of the radiation-driven model decreases with increasing
-radius such that the optical depth peaks at large velocity (here $\mdv
-\approx -400 \mkms$).  At these velocities, the absorption is not
-filled-in by scattered photons such that one recovers absorption lines
-that very nearly match the intrinsic optical depth profile (dotted
-curve).  Although the \ion{Mg}{2} absorption profiles are very
-different from the fiducial model, the \ion{Mg}{2} line-emission has
-similar peak flux and velocity centroids (see also
-Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
-equivalent width, yet the lines are much broader for the
-radiative-driven model. This reflects the fact that the peak optical
-depth occurs at $\mdv \approx -400 \mkms$.
-
-%%%%%%%%%%%%%%%%%%%%
-\subsection{Power-Law Models}
-\label{sec:power}
-
-The models investigated in the previous two sections
-assumed power-law descriptions for both the density and velocity
-laws (Equations~\ref{eqn:density},\ref{eqn:vel}).
-The power-law exponents were arbitrarily chosen, i.e.\ with little physical
-motivation.  In this sub-section, we explore the results for a series
-of other power-law expressions.
-We consider three different density laws ($n_{\rm H} \propto
-r^{-3}, r^{0}, r^2$) and three different velocity laws ($\mvr
-\propto r^{-2}, r^{-1}, r^{0.5}$) for 9 new wind models
-(Table~\ref{tab:plaw_parm}, Figure~\ref{fig:plaws}a).  
-[Comment in the Table how $\mvr$ is
-different when the velocity law is positive]  
-Each of these winds extends over the same inner and outer radii as the
-fiducial model.
-The density and velocity normalizations $n_{\rm H}^0, v^0$ have been
-modified to yield an \mgiia\ optical depth profile that peaks at
-$\tau_{2796}^{\rm max} \approx 10-10^3$ that usually decreases to
-$\tau_{2796} < 1$ (Figure~\ref{fig:plaws}b). [Use Sobolev?]
-All models assume a Doppler parameter
-$b=15\mkms$, full isotropy, and a dust-free environment.
-Lastly, the abundance of Mg$^+$ and Fe$^+$ ions scale with hydrogen as
-in the fiducial model.
-
-Figure~\ref{fig:plaws_spec} presents the \ion{Mg}{2} and \ion{Fe}{2}
-profiles for the full suite of power-law models.  Although these
-models differ qualitatively from the fiducial model in their density
-and velocity laws, the resultant profiles share many of the same
-features.  Each shows significant absorption at $\mdv < 0 \mkms$ with
-the profiles extending to the velocity where $\tau_{2796} < 0.1$
-(Figure~\ref{fig:plaws}b).  All of hte models also exhibit strong
-line-emission, primarily at velocities $\mdv \sim 0 \mkms$.  
-This emission fills-in the \ion{Mg}{2} absorption at $\mdv \gtrsim
--100 \mkms$ such that the profiles never achieve a relative flux less
-than $\approx 0.1$ at these velocities.  [Comment on exceptions]
-Similar to the radiative driven wind ($\S$~\ref{sec:radiate}),
-however, the power-law models that have significant opacity at $\mdv <
--300 \mkms$ have larger peak optical depths.  Another commonality is
-the weak or absent line-emission at \feiia; one instead notes strong
-\feiic\ emission that generally excees the equivalent width of the
-fiducial model.
-
-One of the few distinctions of these models from the fiducial wind is
-the higher peak optical depth of absorption in the \feiib\
-transition.  This is predominantly due to the fact that several of
-these power law models have much higher peak optical depth in all
-transitions.  [Also due to ?]
-Table~\ref{tab:plaw_diag} compares measures of the absorption and
-emission profiles against the fiducial model.
-
-[Comment that $v(r)$ has a greater effect than $n(r)$.]
-
-%\section{Observables}
-%\label{sec:obs}
-%
-%%Although the focus of this paper is to explore the absorption/emission
-%profiles for idealized wind models, we ultimately intend to compare 
-%profiles like these against observations to constrain characteristics
-%of the wind (e.g.\ radial extent, energetics).  In this section we
-%consider a few observables and their dependence on the wind properties.
-%
-%\subsection{Absorption profiles}
-%
-% \begin{enumerate}
-%   \item Peak optical depth
-%     \begin{itemize}
-%       \item Not a robust measure of $\tau_{wind}$
-%       \item Not even a good relative predictor for $\tau$
-%       \item Not a robust predictor of $f_c$
-%       \item Scatter plot of $\tau$ inferred vs.\ $\tau$ true
-%     \end{itemize}
-%   \item Kinematics
-%     \begin{itemize}
-%       \item Nearly robust for $v<v_{min}$
-%       \item But what sets $v_{min}$?
-%       \item Generally get the full extent of the wind speed
-%       \item Plot $v_{pk}$ vs $\tau_{pk}$
-%     \end{itemize}
-%   \item EW
-%     \begin{itemize}
-%       \item Primarily set by $v_{min}(\tau \sim 1)$
-%       \item $f\lambda$ matters, but so do emission channels
-%       \item (EW measured - EW intrinsic) vs.\ EW intrinsic
-%     \end{itemize}
-%   \item Fine-structure
-%     \begin{itemize}
-%       \item Distance to the source
-%     \end{itemize}
-% \end{enumerate}
-%     
-%\subsection{Emission profiles}
-%
-% \begin{enumerate}
-%   \item Resonant lines
-%     \begin{itemize}
-%       \item Kinematics of backside
-%       \item Flux + relative
-%       \item Plot $v_{pk}$ emission vs.\ $v_{pk}$ absorption?
-%    \end{itemize}
-%   \item Fine-structure
-%     \begin{itemize}
-%       \item Flux $\propto \tau_{wind}$ + relative
-%       \item Kinematics (anisotropy)
-%    \end{itemize}
-% \end{enumerate}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Discussion}
-\label{sec:discuss}
-
-Focuses on the observational consequences and implications if our results.
-
-The previous sections presented idealized wind models for
-cool gas outflows, and explored the absorption/emission profiles of
-the \mgiid\ doublet and the \ion{Fe}{2} UV1 multiplet.  In addition to
-the ubiquitous presence of blue-shifted absorption, the wind models
-also predict strong line-emission in both resonance
-and non-resonance transitions.  For isotropic and dust-free scenarios,
-this is a simple convservation of photons: every photon emitted by
-the source eventually escapes the system maintaining an essentially
-zero total equivalent width. A principal result of this paper,
-therefore, is that cool gas outflows should generate detectable 
-line-emission.
-
-Indeed, line-emission from low-ion transitions has been reported from 
-star-forming galaxies that exhibit cool gas outflows.  
-This includes emission related to \ion{Na}{1} \citep{phillips,chen},
-\ion{Mg}{2} emission \citep{wcp+09,rwk+10}, 
-\ion{Si}{2}* emission from LBG galaxies \citep{shapley03},
-and most recently significant \feiis\ emission \citep{rubin+10c}. 
-These authors have proposed a variety of origins for this
-line-emission including AGN activity, recombination in \ion{H}{2}
-regions, and back-scattering off the galactic-scale wind.
-[Are there aspects of those works that are now understood, e.g. the
-difference in FeII 2586 and FeII 2600?]
-Our results suggest that the majority of this line-emission is 
-line-scattered photons in the cool gas outflows of these star-forming
-galaxies.  Indeed, our results indicate that line emission could and
-should be produced by all of these galaxies if the outflows 
-are nearly isotropic. [Add??]
-
-On the other hand,
-there are many examples of galaxies where blue-shifted absorption is
-detected yet the authors report no significant line emission.  This
-includes \ion{Na}{1} flows \cite{rupke,martin,sato}, 
-the \ion{Mg}{2} and \ion{Fe}{2} transitions studied in
-ULIRGS by \cite{mb10}, and the extreme \ion{Mg}{2} outflows identified
-by \cite{tremonti}.  Similarly, there have been no reports of
-resonance line-emission from low-ion transitions in the LBGs\footnote{\citet{pettini02}
-  reported and analyzed \ion{C}{4} line-emission from the lensed LBG
-  cb58, attributing this flux to stellar winds.  We caution, however,
-  that the galactic-scale wind proposed to exist for cb58 should also
-  have contributed to the \ion{C}{4} line-emission.}, and a subset of
-$z \lesssim 1$ galaxies show no detectable \ion{Mg}{2} or \ion{Fe}{2}*
-emission (Rubin et al., in prep). 
-These non-detections appear to contradict a primary conclusion of 
-this paper.   We are motivated, therefore, to
-reassess several of the effects that can reduce the line-emission
-and consider whether these could preclude its detection for many
-star-forming galaxies.  [If MgII emission is 'common' for HII regions,
-why don't we see it *always* when we see OII, Hbeta, etc? Is it
-trapped and then extincted? Same for FeII*]
-
-%% STOPPED HERE %%
-
-Dust is frequently invoked to explain the suppression of line emission
-related toresonantly trapped transitions (e.g.\ \lya).  Indeed, a photon
-that is trapped for many scatterings within a dusty medium will 
-preferentially be extincted relative to a non-resonant photon.  In
-$\S$~\ref{sec:dust}, we examined the effects of dust extinction on 
-\ion{Mg}{2} and \ion{Fe}{2} emission.  The general result was a modest
-suppression of the line flux of the order of (1+\taud)$^{-1}$ instead of
-exp(--\taud). Although the \ion{Mg}{2} photons are resonantly
-trapped, they require only one to a few scatterings
-to escape the wind model and dust has only a
-modest effect.  This results from the moderate opacity of the \ion{Mg}{2}
-doublet (e.g.\ relative to \lya) and also the velocity law of the
-fiducial wind model.
-As we have discussed, in scenarios where the \ion{Mg}{2} photons are
-more effectively trapped (i.e.\ for many scatterings), dust suppresses
-the emission further.
-We also emphasize that the \ion{Fe}{2} resonance photons, especially
-\feiia, are converted to non-resonant photons and escape the wind
-freely.  Therefore, a wind model that trapped \ion{Mg}{2}
-photons for many scatterings would not similarly trap 
-\feiid\ photons.  The effects of dust are much 
-reduced for \ion{Fe}{2}* and, by inference, any other set of
-transitions that are coupled to a fine-structure level (e.g.\
-\ion{Si}{2} and \ion{Si}{2}*).  In summary,
-dust does reduce the line flux relative to the continuum, but we
-conclude that it has only a modest effect on the predicted \ion{Mg}{2}
-and \ion{Fe}{2}* emission.
-
-Another factor that may reduce the line-emission is a
-non-isotropic wind model. One may lower the flux, for example,  by
-removing the backside to the wind (e.g.\ the source itself could
-shadow a significant fraction of the backside).  To zeroth order, the line emission scales
-roughly as $\Omega/4\pi$ where $\Omega$ is the angular extent of the
-wind\footnote{There is also a first order dependence on the actual
-  orientation of the wind, with maximal emission when the backside is
-  fully viewed.}.  Because we require that the wind 
-points toward us, it is difficult to reduce $\Omega$ signficantly
-below $2 \pi$.  Therefore, we expect this effect to reduce the
-emission by at most a factor of order unity.  
-Similarly, an anisotropic source may alter the predicted
-line-emission.  For example, if the backside of the galaxy were
-brighter/fainter then would one predict brighter/fainter emission
-relative to the observed continuum.
-To reduce the emission, the brightest regions
-of the galaxy would need to be oriented toward Earth.  Although this
-would not be a
-generic occurance, most spectroscopic samples are magnitude-limited
-and therefore biased to detecting galaxies when viewed at their
-highest fluxes.
-
-Together, dust and non-isotropic wind models may reduce the line-emission
-of \ion{Mg}{2} and \ion{Fe}{2}
-by a factor of order unity.  This would generally
-not be sufficient, however, to reduce the emission below the typical detection
-limits.
-
-There is another (more subtle) effect that in principle will
-substantially reduce the observed line emission: slit-loss.  As
-described in Figures~\ref{fig:fiducial_ifu_mgii} and
-\ref{fig:ISM_ifu}, emission from the wind is spatially extended with
-a non-zero surface brightness predicted at large radii. This implies 
-a non-negligible luminosity emitted well beyond the galaxy.  
-The majority of observations of star-forming galaxies to date have
-been taken through a spectroscopic slit designed to cover
-the brightest continuum regions of the galaxy. Slits with angular
-extents of $1-1.5''$ subtend roughly $8-15$\,kpc for galaxies at $z>0.5$.
-Therefore, a $1''$ slit covering a galaxy with our fiducial wind would cover
-less than half the wind.  The result will be reduced line emission,
-even when compared to the galaxy continuum.
-
-We explore the effects of slit-loss as follows.
-We model the slit as a perfect, infinitely-long rectangle centered on the
-galaxy.  We then tabulate the equivalent width of the line-emission
-through slits with a range of widths, parameterized by twice the radius
-where the wind has a Sobolev optical depth of $\tau^S = 0.2$ (\rtt).
-The line-emission will be weak beyond
-this radius because the photons have only a low probability of
-interacting with the wind.  For the fiducial wind model, $\mrtt
-\approx 15$\,kpc for the \mgiia\ transition (Figure~\ref{fig:fiducial_nvt}).
-
-The predicted equivalent width in emission \ewe\ relative to the absorption
-equivalent width \ewabs\ is presented in
-Figure~\ref{fig:obs_slit} for a series of transitions for the fiducial
-wind model (black curves).
-[Add LBG, radiative]
-The curves rise very steeply with increasing slit width and then
-plateau when the slit width is $\approx \mrtt$.  
-The results are comparable for other wind models considered
-in this paper (colored curves in Figure~\ref{fig:obs_slit}).
-All of the curves rise so steeply that 
-the effect is of slit-loss is of order unity
-unless the slit-width is very small.   
-Nevertheless, the results do motivate
-extended aperture observations, e.g.\ integral field unit (IFU)
-instrumentation that would map the wind both spatially and spectrally.
-
-Although several effects can reduce the line-emission
-relative to the absorption of the outflow, our analysis
-indicates that detectable line-emission should occur. 
-A principal effect of this emission is
-that it modifies the observed absorption profiles (e.g.\
-Figure~\ref{fig:noemiss}). This may lead to erroneous conclusions
-regarding several characteristics of the flow.  {\it An anaaaalysis of cool gas outflows
-that ignores line-emission may incorrectly conclude that the gas is
-partially covered, has a significantly lower peak optical depth,
-and/or that a $\mdv \sim 0 \mkms$ component is
-absent.}  Figure~\ref{fig:obs_ew} demonstrates one observational
-consequence of the line emission: reduced measurements for the absorption
-equivalent width \ewabs\ of the flow.  In the case of \ion{Mg}{2},
-which has the most affected transitions, the \ewabs\ is reduced by
-$30-50\%$ from the intrinsic absorption.  In turn, one may derive 
-a systematically lower optical depth or velocity extent for the wind,
-and therefore a lower total mass and kinetic energy.  
-The effects are most pronounced for wind
-scenarios where the peak optical depth occurs near $\mdv = 0 \mkms$.
-Geometric projection limits the majority of scattered photon emission to
-have $|\mdv| < 200 \mkms$; therefore,  the absorption profiles
-are filled-in primarily at these velocities.  In
-Figure~\ref{fig:obs_peaktau}, we plot the observed peak optical depth
-$tau_{\rm pk}$ for \mgiia\ 
-versus the velocity where the profile has greatest depth 
-for the various wind models (i.e.\
-$\tau_{\rm pk}$ vs.\ $v_\tau$ from Tables~\ref{tab:line_diag} and
-\ref{tab:plaw_diag}).   In every one of the models, the true peak
-optical depth $\tau_{\rm pk}^{\rm true} > 10$.  For the
-majority of cases with $v_\tau > -300\mkms$, one observes $\tau_{\rm pk} <
-2$ and would infer the wind is not even optically thick!
-This occurs because photons scattered by the wind have `filled-in' the
-absorption at velocity $\mdv \approx 0 \mkms$.  In contrast, the wind
-models with $v_\tau < -400 \mkms$ all give $\tau_{\rm pk} > 3$.  The
-results are similar for the \mgiib\ profile.  In fact, one infers a
-very similar $\tau_{\rm pk}$ for the two lines which would generally
-lead to the false conclusion of partial covering (and, correctly, a
-higher $\tau_{\rm pk}^{\rm true}$).  [Last thought?\
-
-All of these (somewhat negative) effects for \ion{Mg}{2} absorption are reduced
-for the \ion{Fe}{2} absorption profiles, especially for \feiia.  This
-is because a signficant fraction (even a majority) of the
-\ion{Fe}{2} emission is florescent \ion{Fe}{2}* emission at longer
-wavelengths, which has no effect on the absorption profiles. 
-Therefore, the \ion{Fe}{2} absorption equivalent widths (\ewabs) more
-closely follow the intrinsic value, one derives more accurate peak
-optical depths, and the absorption kinematics more faithfully reflect
-the motions of the flow.  Regarding the last point, one also
-predicts a velocity offset between the \ion{Fe}{2} and \ion{Mg}{2}
-centroids (Figure~\ref{fig:obs_vtau}).
-One is simply
-less sensitive to absorption at $v \sim 0 \mkms$ with the \ion{Mg}{2}
-transitions.  This includes gas realted to the ISM of the galaxy and
-also material infalling at a modest speed.  One must take careful
-consideration of line emission, therefore,  before drawing robust
-conclusions aobut the presence/absence of gas with small velocity
-offsets from systemic. [Comment on MgII moving too fast]
-
-We emphasize that all of these effects are heightened by the
-relatively low spectral resolution and S/N characteristic of the data
-obtained on $z>0$ star-forming galaxies.  Figure~\ref{fig:obs_lris}a
-shows one realization of the \mgiid\ doublet for the ISM+wind model
-convolved with the line-spread-function of the Keck/LRIS spectrometer
-(FWHM=250\kms) and an assumed S/N=7 per (1 \AA) pixel.  Both the absorption
-and emission profiles are evident, but it is evident that it will be
-very difficult to resolve the issues discussed above (e.g.\ partial
-covering, incorrect peak optical depth) with these data.  The effects
-are even more difficult to predict for spectral stacks, especially
-when the systemic redshifts are uncertain by $> 10 \mkms$ (e.g.\ S10).
-An example is presnted in Figure~\ref{fig:obs_lris}b, where we have
-averaged 100 identical \ion{Mg}{2} profiles from the fiducial model
-degraded to a S/N=2\,pix$^{-1}$ and assuming a random redshift error
-$\sigma(z) = 100\mkms$.  [Check S10 error] [Note the further shift in
-MgII 2796 due to the instrument resolution]
-
-[Should galaxies with strong \lya\ emission be expected to show
-low-ion emission? Perhaps not if \lya\ is produced by ionizing photons
-from SF regions.]
-
-[Could they have accidentally `sky subtracted' it?  I doubt it]
-
-The previous few paragraphs sound a cautionary and largely negative
-perspective on the implications for absorption-line analysis of
-galactic-scale outflows, in the presence of (expected) significant
-line-emission.   While this does complicate [the analysis],
-observations of the line emission alone offer new and unique
-constraints on the charcteristics of the outflow.  And when coupled
-with the absorption-line data, the two sets of constraints...
-The most direct measure provided by the line emission is an estimate
-of the size and morphology of the outflow \citep[e.g.][]{rubin_emiss}.  
-Line emission is predicted to extend to radii where the Sobolev
-optical depth exceeds a few tenths [is that right?].  The principle
-challenge is to achieve sufficient sensitivity to detect the low
-surface brightness emission.
-
-As Figure~\ref{fig:obs_sb}
-demonstrates, the surface brightness at the inner wind radius of our
-fiducial wind exceeds the outer radius by several orders of magnitude.
-Nevertheless, an instrument that sampled the entire wind (e.g.\ a
-large format IFU or narrow band imager) may detect the emission in
-azimuthally averaged apertures. [Give estimate]
-[Add FeII* to the SB figure]
-
-Of the transitions considered in this paper, \ion{Mg}{2} emission is
-preferred for [this analysis] because 
-(i) it has the largest equivalent width in absorption and
-(ii) there are fewer emission channels per absorption line than for
-\ion{Fe}{2}.  This implies the highest peak and integrated fluxes
-(Figure~\ref{fig:obs_sb}).  With an IFU observation covering all of
-the \ion{Fe}{2} transitions, one could sum the together to enhance the
-signal.
-
-The kinematics of the line emission also offer insight into physical
-characteristics of the wind.
-
-[Relative strengths of MgII 2796 and 2803 speak to $\tau$ and
-$v_r^{max}$]
-
-%%%%%%%%%%%%%%%%%
-
-1)  Emission is a generic prediction of wind models (and something
-which has been essentially ignored aside from \lya).  We can discuss
-the caveats (dust, finite slit size, intrinsic spectrum).
-
-2)  Emission complicates the analysis of absorption at v$\sim$0 km/s, especially in
-resonantly trapped transitions (e.g. MgII, NaI).   This affects tau\_pk,
-C\_f and also offsets the line centroids (e.g. FeII, MgII).  These
-are primarily negative effects.
-
-3)  Emission can be used for good!   This is largely an extension of
-your emission paper, of course.
-
-   (i)  Morphology [MgII is likely best]
-  (ii)  Kinematics  --  FWHM, centroid $=>$  Wind speed, ISM
- (iii)  Flux ratios?  e.g.   f\_2796/f\_2803 and/or f\_2626/f\_2600
-
-[Are MgII and FeII* emission strict predictions of outflows?  People
-have been so focused on absorption.]
-
-[Does recombination predict 2:1 for MgII??]
-[We also emphasize that departures from a 2:1
-ratio indicate that processes other than simple recombination are
-active. ]
-
-[Profiles are modified by {\it many} factors => Difficult to derive
-robust constraints from absorption alone.]
-
-[Is one safe if there is no emission detected?]
-
-[What does MgI tell us about winds?  Why no P-Cygni?]
-
-\section{Concluding remarks}
-\label{sec:conclude}
-
-1. More complicated winds needed
-
-2. Cosmological context (espeicially at $z>2$)
+Complementing the absorption-line observations and analysis,
+Steidel et al.\ (2011; hereafter S+11) have explored the spatial
+extent of \lya\ emission from the CGM surrounding LBGs.  In a stacked,
+narrow-band image of $\approx 100$ LBGs at $z \approx 2.5$ they
+measure a `halo' of low surface brightness \lya\ emission with an
+approximately expoentinal profile $\mu(\rho) \sim \exp{-\rho/b}$ from
+$\rho \approx 10-80$\,kpc with $b \approx 20$\,kpc.  These authors
+interpreted the signal as the scattering of \lya\ photons generated
+within the central LBG by an extended CGM surrounding each galaxy.
+They further reported that the same LBG clumpy wind model that
+reproduces the stacked absorption spectra (S+10) can reproduce the
+kinematics of \lya\ emitted by the galaxy and the extended \lya\
+emission.  At the same time, they allowed that a proper treatment
+including full radiative transfer was highly warranted.
 
@@
 
-\input{Tables/table_atomic.tex}
-\input{Tables/tab_fiducial.tex}
-\input{Tables/tab_fiducial_ew.tex}
-\input{Tables/tab_meas_models.tex}
-\input{Tables/tab_plaw_parm.tex}
-\input{Tables/tab_meas_plaws.tex}
+%\input{Tables/table_atomic.tex}
 
@@
 \epsscale{0.95}
-\plotone{Figures/energy_levels.ps}
+\plotone{Figures/fig_lbg_cover_1d.ps}
 \caption{
-Energy level diagrams for the \mgiid\ doublet and the UV1
-multiplet of \ion{Fe}{2} transitions   
-(based on Figure~7 from \cite{hmt+99}).
-Each transition shown is
-labeled by its rest wavelength (\AA) and Einstein A-coefficient
-(s$^{-1}$). Black upward arrows
-indicate the resonance-line transitions, i.e.\ those connected to the ground
-state.  The 2p$^6$3p configuration of Mg$^+$ is split into
-two energy levels that give rise to the \mgiid\ doublet.  
-Both the 3d$^6$4s ground state and 3d$^6$4p upper level of Fe$^+$
-exhibit fine-structure splitting that gives rise to a series of
-electric-dipole transitions. 
-The downward (green) arrows show the \feiis\ transitions that are connected to the
-resonance-line transitions (i.e.\ they share the same upper energy
-levels).  We also show a pair of levels (\ion{Fe}{2}$^* \lambda\lambda
-2618,2631$) that arise from higher levels in the \zconfig\
-configuration.  These transitions have not yet been observed in
-galactic-scale outflows and are not considered in our analysis.
+1D spectra
 }
-\label{fig:energy}
+\label{fig:1D}
 \end{figure}
@@
 \epsscale{0.8}
-\plotone{Figures/fig_nvtau_vs_r.ps}
+\plotone{Figures/fig_lbg_sb.ps}
 \caption{
-Density (dashed; red), radial velocity (dotted; blue), and
-\mgiia\ optical depth profiles (solid; black) for the fiducial
-wind model (see Table~\ref{tab:fiducial} for details).
-The density and velocity laws are simple $r^{-2}$ and $r^1$
-power-laws.  The optical depth profile was calculated by summing
-the opacity at small and discrete radial intervals in velocity space
-and was then converted to radius with the velocity law.  One notes that
-the wind is optically thick at the inner radius ($r_{\rm inner} =
-1$\,kpc) and becomes optically thin at the outer radius ($r_{\rm
-  outer} = 20$\,kpc).
-Note that the density and velocity curves have been scaled for plotting
-convenience.  
+Surface brightness
 }
-\label{fig:fiducial_nvt}
+\label{fig:SB}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_fiducial_1d.ps}
+%\includegraphics[scale=0.6,angle=90]{Figures/mass_energy.ps}
 \caption{
-{\it Left} -- (Upper) \mgiid\ profiles for the fiducial wind model
-described in Table~\ref{tab:fiducial} and
-Figure~\ref{fig:fiducial_nvt}.  The doublet shows the P-Cygni profiles
-characteristic of an outflow with significant absorption blueward of
-line-center (dashed vertical lines) extending to $v = -1000\mkms$
-and significant emission redward of line-center.  Note
-that even though the peak optical depth of the \ion{Mg}{2} transitions
-is $\tau_{2796}^{\rm max} \approx 30$ at $v \approx -70 \mkms$,
-photons scattered off the outflow fill in the absorption.
-(Lower) \ion{Fe}{2} absorption and emission profiles for the UV1
-multiplet at $\lambda \approx 2600$\AA.  The \feiid\ resonance lines 
-show weaker absorption due to the smaller Fe$^+$ number density and
-lower $f\lambda$ values.  Each also shows a P-Cygni profile, although
-the emission for \feiia\ is significantly weaker than that of the
-\feiib\ and \mgiid\ transitions.  This is because a majority of the
-absorbed \feiia\ photons are converted into
-\ion{Fe}{2}$^*~\lambda\lambda 2612, 2632$ photons.
-{\it Right} -- A subset of the transitions displayed in a velocity
-plot.
+Mass, energy
 }
-\label{fig:fiducial_1d}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_noemiss.ps}
-\caption{
-The solid curves show the line profiles (absorption and emission) of
-the \ion{Mg}{2} and \ion{Fe}{2} resonance lines for the fiducial wind
-model.  These include the effects of scattered photons and show the
-canonical P-Cygni profiles of a source 
-embedded within an outflow.  Overplotted (dotted line) on each transition is
-the predicted absorption profile under the constraint that every
-absorbed photon is lost from the system, i.e.\ no scattering or
-re-emission occurs.   The true profiles have been `filled
-in' significantly by light scattered in the wind.  Ignoring this
-process, one would model the absorption lines with a systematically lower
-optical depth and (incorrectly) conclude that the source is partly covered by the
-gas.  
-}
-\label{fig:noemiss}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_fiducial_ifu_mgii.ps}
-\caption{
-Surface-brightness emission maps around the \mgiia\ transition for the
-source+wind complex of the fiducial model.  The middle panel shows the
-1D spectrum with $v=0 
-\mkms$ corresponding to $\lambda = 2796.35$\AA\ and the dotted vertical
-curves indicate the velocity slices for the emission maps.  The
-source has a size $r_{\rm source} = 0.5$\,kpc, traced by a few
-pixels at the center.   At $v=-250 \mkms$, the wind has an optical
-depth of $\tau_{2796} \approx 1$ and the source contributes
-roughly half of the observed flux.  At $v=-100 \mkms$ the
-wind absorbs all photons from the source and the observed emission is
-entirely due to photons scattered by the wind.  Impressively, this
-emission exceeds the integrated flux at $v = -250\mkms$ such that the
-line center is offset from the peak optical depth.  At $v \ge 0
-\mkms$,  both the source and wind contribute to the observed emission.
-At all velocities, the majority of emission comes from the inner
-$\approx 5$\,kpc.
-}
-\label{fig:fiducial_ifu_mgii}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_feii_ifu.ps}
-\caption{
-(Upper) Surface-brightness emission maps around the \feiib\ transition for the
-source+wind complex.  The middle panel shows the 1D spectrum with $v=0
-\mkms$ corresponding to $\lambda = 2600.173$\AA\ and the dotted vertical
-curves indicating the velocity slices for the emission maps.  
-The results are very similar to those observed for the \mgiid\ doublet
-(Figure~\ref{fig:fiducial_ifu_mgii}).
-(Lower) Surface-brightness emission maps around the \ion{Fe}{2}~$\lambda
-2612$ transition for the 
-source+wind complex.  The middle panel shows the 1D spectrum with $v=0
-\mkms$ corresponding to $\lambda = 2612.654$\AA\ and the dotted vertical
-curves indicating the velocity slices for the emission maps.  
-In this case, the source is unattenuated yet scattered photons from
-the wind also have a significant contribution. 
-}
-\label{fig:fiducial_ifu_feii}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_fiducial_cut.ps}
-\caption{
-The panels show the relative emission from the wind as a function of
-radius for (a) \mgiia\ and (b) \feiib\ in a series of velocity
-channels.  With the exception of $v = -100 \mkms$ for \mgiia, the wind
-has finite transmission such that one observes the source at $r =
-0$\,kpc.  In all cases,  the majority of emission occurs at $r
-\lesssim 2.5$\,kpc, even if one ignores the source emission.
-}
-\label{fig:fiducial_cuts}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_asymm_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-case (black lines) compared against an anisotropic wind blowing into
-only $2\pi$ steradians as viewed from $\theta = 0^\circ$ (source
-uncovered) to $\theta = 180^\circ$ (source covered).  One detects
-significant emission for all orientations of this wind but significant
-absorption only for $\theta \ge 90^\circ$.
-The velocity centroid of the 
-emission shifts from positive to negative velocities as $\theta$
-increases and one transitions from viewing the wind to be behind the
-source to in front.  The velocity centroid of emission, therefore, may
-give a robust measure of wind isotropy.
-}
-\label{fig:anisotropic}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_dust_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-model (black) against a series of models that include 
-dust extinction.  The primary effect is suppression of
-the line-emission relative to the continuum. 
-A more subtle but important effect is that the redder photons in the
-emission lines (corresponding to higher velocity relative to
-line-center) suffer greater extinction.  This is most evident in the
-\feiic\ emission line; it occurs because these photons must
-travel farther to scatter off the backside of the wind.  Note that
-the absorption lines are nearly unmodified until $\mtaud = 10$, a
-level of extinction that would preclude observing the source
-altogether.
-}
-\label{fig:dust}
-\end{figure}
-
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_ism_diagn.ps}
-%\caption{
-%Density (dashed; red), radial velocity (dotted; blue), and
-%\mgiia\ optical depth profiles (solid; black) for the ISM+wind
-%model.  The wind is identical to that from the fiducial model
-%(Figure~\ref{fig:fiducial_nvt}) but this ISM+wind model also includes an ISM component
-%with $n_{\rm H} = 1 \cm{-3}$ that has an average velocity of $\mvr = 0
-%\mkms$ and a large turbulent velocity $b_{\rm ISM} = 40 \mkms$.
-%Note that the density and velocity curves have been scaled for plotting
-%convenience.  
-%}
-%\label{fig:ISM}
-%\end{figure}
-
-\begin{figure}
-\epsscale{0.7}
-\plotone{Figures/fig_ism_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the ISM+wind
-model (red) compared against the fiducial wind model (black). 
-The dotted line traces the predicted absorption profile in the absence
-of re-emission and scattering.
-Regarding the \ion{Mg}{2}~doublet, the primary difference between the
-ISM+wind and the fiducial models is the shift of $\approx 100 \mkms$
-in the emission lines from $v \approx 0 \mkms$ for the fiducial
-model to $v \approx +100\mkms$ for the ISM+wind model. 
-For the ISM+wind model, 
-the \ion{Fe}{2} profiles show qualitative differences. 
-the ISM model.  The \feiid\ resonance transitions each exhibit much
-greater absorption at $v \approx 0 \mkms$ than the fiducial model.
-The resonant line-emission is also substantially
-reduced, implying much higher fluxes for the non-resonant lines (e.g.\
-\feiic).  The lack of scattered \feiia\ photons results in an
-absorption profile that very nearly matches the input opacity profile.
-We conclude that resonance transitions that are strongly coupled to
-non-resonant lines offer the best
-characterization of an ISM component.
-}
-\label{fig:ISM_spec}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_norm_spec.ps}
-\caption{
-Varying normalization
-}
-\label{fig:norm}
-\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_lbg_sobolev.ps}
-\caption{
-(a) The dotted curve shows the velocity law (values are labeled on the
-right side) for the LBG model
-of S10.  Note how rapidly the velocity rises from $r =
-1$ to 2\,kpc.  The solid curve shows the Sobolev solution for the
-Mg$^+$ gas
-density derived from 
-the average absorption profile of LBG galaxies (see below).
-The density drops off as $(r/{\rm kpc}-1)^{-0.6}$ initially and then
-steepens to $(r/{\rm kpc}-1)^{-1.8}$.
-(b) Average absorption profile for LBG cool gas absorption as
-measured and defined by S10
-(black solid curve).  Overplotted on this curve is a (red) dotted line that
-shows the \mgiia\ absorption profile derived from the density (and velocity)
-law shown in the upper panel.  The excellent agreement confirms the
-validity of the Sobolev approximation.
-}
-\label{fig:LBG_Sobolev}
-\end{figure}
-
-\clearpage
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_lbg_spec.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the two
-LBG models considered: (red) the profiles from the 
-Sobolev approximation 
-and (black) a model constructed to faithfully
-correspond to the wind model advocated by S10.  The dotted line
-shows the absorption profiles of the latter model if one were
-to neglect scattered and re-emitted photons.  Similar to the fiducial
-model (Figure~\ref{fig:fiducial_1d}), scattered and re-emitted photons
-significantly modify the absorption profiles (especially \ion{Mg}{2})
-and produce significant emission lines.  
-The result, for \ion{Mg}{2} especially, is a set of profiles that do
-not match the average observed LBG absorption profile.
-Note the excellent agreement
-between the \mgiia\ profile for the two models. [Cast doubt on S10
-here?]
-}
-\label{fig:LBG_spec}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_lbg_cumul.ps}
-\caption{
-Profiles of the \ion{Fe}{2} and \ion{Mg}{2} profiles for the fiducial
-}
-\label{fig:LBG_cumul}
-\end{figure}
-
-%%%% RADIATIVE %%%%%%
-%\begin{figure}
-%\epsscale{0.8}
-%\plotone{Figures/fig_radiation_nvt.ps}
-%\caption{
-%Radiation diagnosed
-%}
-%\label{fig:rad_nvt}
-%\end{figure}
-
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_rad_spec.ps}
-\caption{
-\ion{Mg}{2} and \ion{Fe}{2}
-profiles for a radiation-driven wind model (red) compared against the
-fiducial wind model (black).  In contrast to the fiducial model, the
-velocity of the radiation-driven model decreases with increasing
-radius such that the optical depth peaks at large velocity (here $\mdv
-\approx -400 \mkms$).  At these velocities, the absorption is not
-filled-in by scattered photons such that one recovers absorption lines
-that very nearly match the intrinsic optical depth profile (dotted
-curve).  Although the \ion{Mg}{2} absorption profiles are very
-different from the fiducial model, the \ion{Mg}{2} line-emission has
-similar peak flux and velocity centroids (see also
-Table~\ref{tab:plaw_diag}).  The \feiis\ emisison also has a simiar
-equivalent width, yet the lines are much broader for the
-radiative-driven model. This reflects the fact that the peak optical
-depth occurs at $\mdv \approx -400 \mkms$.
-}
-\label{fig:rad_spec}
-\end{figure}
-
-%%%% POWER LAWS %%%%
-\begin{figure}
-\epsscale{0.8}
-\plotone{Figures/fig_vary_profiles.ps}
-\caption{
-Power-law profiles
-}
-\label{fig:plaws}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_plaw_spec.ps}
-\caption{
-Power-law profiles spectral lines
-}
-\label{fig:plaws_spec}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_slit.ps}
-\caption{
-Slit width effects
-}
-\label{fig:obs_slit}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_ew.ps}
-\caption{
-EW effect
-}
-\label{fig:obs_ew}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_peaktau.ps}
-\caption{
-EW effect
-}
-\label{fig:obs_peaktau}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_vtau.ps}
-\caption{
-Velocity offset
-}
-\label{fig:obs_vtau}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_lris.ps}
-\caption{
-Velocity offset
-}
-\label{fig:obs_lris}
-\end{figure}
-
-\begin{figure}
-\includegraphics[scale=0.6,angle=90]{Figures/fig_obs_sb.ps}
-\caption{
-Surface brightness
-}
-\label{fig:obs_sb}
+\label{fig:mass_energy}
 \end{figure}

### 2011-03-30 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5797 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \newcommand{\naid}{\ion{Na}{1}~$\lambda\lambda 5891, 5897$}
+\newcommand{\mgii}{\ion{Mg}{2}}
 \newcommand{\mgiid}{\ion{Mg}{2}~$\lambda\lambda 2796, 2803$}
@@
 
+In a recent publication \citep[][hereafter PKR11]{pkr11}, 
+we explored the absorption and emission from
+a series of simple wind models with emphasis on the
+\mgiid\ doublet.  In addition to a
+series of idealized models, we also considered two variations of the
+LBG wind model proposed by S+10.  Although we argued that the results
+for \mgii\ should act as an analog for \lya\ because each is a
+resonantly trapped doublet, we return in this paper to consider
+directly ($\S$~\ref{sec:lya}).  We also expand upon our discussion on the required
+energetics and mass flow of such a wind scenario
+($\S$~\ref{sec:energy}).  Unless otherwise indicated, all distances
+are physical under the assumption of a $\Lambda$CDM universe with
+$\Lambda = 0.74$, $\Omega_m = 0.26$ and 
+$H_0 = h_{72} 72 \, \mkms/{\rm Mpc}$ \citep{wmap05}.
+
+\section{\lya\ Emission/Absorption from the LBG Clump Model}
+\label{sec:lya}
+
+The LBG clump model proposed by S+10 envisions an isotropic outflow of
+dense clumps, each optically thick to \lya\ and metal-line
+transitions, but as an ensemble have a partial covering fraction to
+the LBG and background sources.  We discuss in PKR11 our radiative
+transfer treatment for this wind in the context of \mgiid.  In the
+following, we adopt the same prescription but consider
+\lya\footnote{Following standard practice, we treat \lya\ as a single
+  transition instead of a double because the line separation is much less
+  than the astrophysical velocities of interest here.}
+and modify the parameters of the LBG clump model to those presented in
+S+10.
+
+In contrast to PKR11, we include two additional features in the
+model.  First, we have explored two intrinsic emission models for the
+galaxy near the \lya\ line: 
+(i) a flat continuum, primarily generated by O and B stars within the
+star-forming galaxy; and
+(ii) a continuum plus \lya\ emission-line model parameteized by a
+line-width $\sigma_{\rm Ly\alpha}$ and an equivalent width \wlya.
+This line is presumed to be generated by \ion{H}{2} regions within the
+galaxy.  We emphasize that neithre of these simple models are likely
+to describe the complex emission of a star-forming galaxy at \lya.
+Nevertheless, they help capture some of the salient features of the
+LBG clump model.
+
+Second, we have modeled attenuation of photons near \lya\ by the
+intergalactic medium (IGM) surrounding LBGs on scales of $\sim 100\,
+{\rm kpc} - 10$\,Mpc.  Our approach follows the method of
+\cite{santos04}, using the \cite{barkana04} model for infall onto
+galactic halos at $z \approx 3$.  We assume a galaxy with dark matter
+halo mass $M_{\rm DM} \approx 10^{12} \msun$, virial radius $\mrvir 
+= 80$\,kpc, circular velocity $v_{\rm c} = 220 \mkms$, and an
+IGM with $T = 10^4$\,K, and a EUVB with ionization rate $\Gamma =
+10^{-12.5} \, \rm s^{-1}$ \citep{fpl+08}.  With this parameterization,
+we can calculate the density and velocity profiles of gas at $r >
+\mrvir$ for the LBG (and assume the gas at $r<\mrvir$ is dominated by
+the outflow) and apply the Sobolev approximation to calculate the
+optical depth \tauv\ to \lya\ as a function of velocity.  We cuation that
+this $\exp(-\mtauv)$ prescription does not capture the complexity of
+gas on these scales.  Indeed, \cite{zheng10a} have argued that a more
+proper treatment tends to yield higher opacity.
+[INCLUDE THE BOOST?]
+In either case, it is a necessary consideration for modeling the
+observed \lya\ emission from these galaxies.
+
+Figure~\ref{fig:1D} (top panels) presents the 
+calculated 1D \lya\ spectrum for the
+two intrinsic emission models of the galaxy.
+The second panels show the predicted results when one includes
+radiative transfer through the LBG clump model.  Similar to the \mgii\
+results of PKR11, we observe significant absorption by the outflow for
+$v < 0\mkms$.  The absorption actually peaks at $v < 0\mkms$ because
+scattered emission has `filled-in' the absorption for $v \approx 0
+\mkms$.  This emission peaks just redward of $v=0\mkms$, related to
+photons emitted transverse to our sightline and scattered once to
+Earth, and then extends to positive velocity, with a tail to $v
+\approx +500\mkms$.  [Comment on Lya emission line model?]
+The third pair of panels includes the effects of IGM scattering.  For
+the DM halo and IGM model assumed, we find a peak optical depth
+$\mtmax \approx 7$ at $v \approx v_{\rm c}$ that rapidly declines to
+$\mtauv < 0.5$ at $v=0\mkms$.  This implies complete attenuation of
+the \lya\ emission at $v \approx v_{\rm c}$ but only modest
+attenuation at lower velocity.  For this parameterization, it is evident that
+the effects of the IGM cannot be ignored.  If the IGM were just $5
+\times$ more neutral than modeled here, the \lya\ line would be
+completely ``extinguished'' at $v \gtrsim 0 \mkms$, as predicted for
+the $z \sim 6$ universe \citep{zheng+10a}.  By the same token, if the
+galaxy emits ionizing photons then \tmax\ may fall below unity and the
+IGM would play a minor role.  Clearly, a full treatment of these
+effects is warranted for the $z \sim 3$ universe.
+
+In the bottom panels, we present the full model convolved with an
+ideal spectrometer with FWHM~$\approx 250\mkms$ compared against the
+observed, average \lya\ emission profile of LBGs from
+\cite{shapley03}.  
+At this spectral resolution,
+typical of LBG spectroscopic observations, the weak emission that was
+apparent for the continuum model is lost and one predicts a simple
+absorption profile that extends to positive velocity because of IGM
+attenuation.  This model is a very poor description of the data.  
+For the line+continuum intrinsic model, in contrast, it is difficult
+to detect the outflow and the IGM attenuation is completely lost at
+this spectral resolution within the \lya\ emission profile.
+Neither model predicts a significant emission line that is shifted by
+several hundred \kms\ redward of systemic.  Indeed, reviewing the
+results on \mgii\ from PKR11, such a shift is predicted for any
+outflow model that we have considered.  The only scenario in PKR11
+that showed a significant shift was when we included significant
+opacity at $v \approx 0 \mkms$ at the source, i.e.\ an ISM model.
+This has the the effect of altering the intrinsic emission [How?] 
+and when combined with an outflow can yield a redshifted emission
+profile.  [Do this with Lya!] 
+[Comment that infall can produce a redshift \lya\ line too, i.e. Zheng
+et al.]
+
+[Previous authors have modeled the \lya\ profiles of LBGs and have
+concluded the redshift emission is well decribed by an outflow
+\citep[e.g.][]{verhomme}.  Similar to the
+ISM+wind model described above, these outflow models only predict a
+redshift if there is a very large opacity at $v \approx 0\mkms$.  In
+the \cite{verhomme} models, this is accomplished by considering a
+thin expanding shell with a total \ion{H}{1} column density $\mnhi > 10^{20}
+\cm{-2}$.  In this case, the damping wings of the gas imply a large
+opacity at $v \approx 0 \mkms$ provided the shell has a speed less
+than $\approx 500 \mkms$.  This model, then, predicts a very strong
+absorption profile at $v < 0 \mkms$, which is generally not observed
+in the LBG spectra.  One of the few exceptions is the galaxy cb58.]
+
+Now consider the spatial distribution of \lya\ emission.
+Figure~\ref{fig:SB} shows the predicted surface brightness profile
+vs.\ projected radius for the flat-continuum intrinsic model and with
+no IGM attenuation.  The signal is integrated from velocities $v =
+[-100,400]\mkms$. Overplotted on the model, at an arbirtrary
+normalization, is the fitted profile of S+11 to their observations,
+$\mu(\rho) \propt \exp(-\rho/b)$ with $b=20$\,kpc.  In constrast to
+the observations, the clump model predicts that XX\%\ of the
+integrated flux is emitted at $\rho < 10$\,kpc and the model assumes
+an exponential-like profile only at very large radii.  In short, a
+proper radiative transfer treatment of the LBG clump model shows it
+cannot reproduce the observed, extended \lya\ emission.
+
+The explanation for the model's failure is twofold:  
+(1) the covering fraction of the clumps decrease with radius to
+$f_{\rm c} < 0.2$ at $\rho > 50$\,kpc; and
+(2) the velocity gradient at $r>5$\,kpc is very shallow.  Therefore,
+at large radii the outflow absorbs very few photons relative to the
+inner regions.  In terms of the Sobolev approximation, we estimate
+$\tau_{\rm S}(\rho = 60 \, {\rm kpc}) = XX \tau_{\rm S}(\rho=1\, {\rm
+  kpc})$.  
+Note that unlike the kinematic signatures, the inclusion of an ISM
+component at small radii would not alter any of these conclusions.
+[Add a last few lines]
+
 \acknowledgments

### 2011-03-30 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5800 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 $\mu(\rho) \propt \exp(-\rho/b)$ with $b=20$\,kpc.  In constrast to
-the observations, the clump model predicts that XX\%\ of the
+the observations, the clump model predicts that 95\%\ of the
 integrated flux is emitted at $\rho < 10$\,kpc and the model assumes

### 2011-04-01 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5808 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\section{On the Energetics of the LBG Clump Model}
+\label{sec:energy}
+
+In the previous section, we demonstrated that the LBG clump model
+of S+10 does not reproduce the observed \lya\ emission associated with
+LBGs.   We also emphasize, however, that the radiative transfer of
+\lya\ is sensitive to the intrinsic emission of the galaxy ($r \sim
+10$\,kpc), the physics of the gas in the CGM ($r \sim 100$\,kpc), and
+also the property of the IGM on larger scales ($r \sim 1-10$\,Mpc).
+It is possible, therefore, that the observed \lya\ emission is
+dominated by components other than a galactic-scale wind, indirectly
+observed as blue-shifted absorption.  In this respect, the LBG clump
+model cannot be ruled out.
+
 \acknowledgments

### 2011-04-01 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5809 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\mmc}{m_{\rm c}}
 \newcommand{\tpk}{$\tau_{\rm pk}$}
@@
 observed as blue-shifted absorption.  In this respect, the LBG clump
-model cannot be ruled out.
+model cannot be ruled out by its discordance with the \lya\
+observations.
+
+In PKR11, we provided estimates for the energy and mass flux of the
+LBG wind model, as approximated by a Sobolev solution.  We now
+examine the same quantities for the clump model.  Consider a shell of
+thickness $\Delta r$ at radius $r$ from an LBG galaxy.  We may relate
+the number density of clumps $n(r)$ in this shell to the covering
+fraction of the clumps $f_\rm{c}(r)$:
+
+\begin{equation}
+n(r) = \frac{f_{\rm c}(r)}{\sigma} \frac{1}{\Delta r}
+\lable{eqn:density}
+\end{equation}
+with $\sigma$ the cross-section of the clump.  If each clump has a
+mass $m_{\rm c}$ then the mass within the shell is
+
+\begin{equation}
+M_{\Delta r}(r) = 4\pi r^2 f_{\rm c}(r) \, \frac{m_{\rm c}}{\sigma}
+\perd
+\label{eqn:mshell}
+\end{equation}
+Following Sobolev formalism, we set the shell thickness with radius to
+the velocity gradient of the flow
+
+\begin{equation}
+\Delta r = \Delta v_{\rm c} \ltp \frac{dv}{dr} \rtp^{-1}
+\end{equation}
+where $\Delta v_{\rm c}$ characterizes the velocity dispersion of the
+clumps, from any combination of internal or external motions within
+the shell.  In the following we adopt $\Delta v_{\rm c} = 10 \mkms$.
+
+Lastly, we constrain the surface density of the clumps $m_{\rm
+  c}/\sigma$ by demanding each clump be optically thick to the
+metal-line transitions observed by S+10, e.g.\ \ion{Si}{2}~1526.  
+This implies a minimum column density of Si$^+$ ions; we adopt
+$\N{Si^+} > 10^{14} \cm{-2}$.  In turn, this implies a lower limit to
+$m_{\rm c}/\sigma$.  For a solar abundance $n_{\rm H} = 10^{-4.5}
+n_{\rm Si}$ and assuming no ionization correction, we find $N_{\rm H}
+\ge 10^{18.5} \cm{-2}$ and therefore $m_{\rm c} / \sigma \ge 3.3
+\sci{-2} \msun \, \rm pc^{-2}$ when one accounts for helium.
+
+Adopting the minimum value for $\mmc/\sigma$,  we derive the mass,
+mass flux, energy, and power profiles shown in
+Figure~\ref{fig:mass_energy}.
+[Note that the clump flux ($nvr^2$) is nearly constant (increases by a
+factor of 2 somehow!) at $10^{-2}$ clumps/yr].
+Regarding mass, we find the clump model has $M_{\rm TOT} \approx
+10^{10} \msun$ [check] with nearly all of this matter existing at
+radii $r>20$\,kpc.  Ironically, this material accounts for very little
+of the down-the-barrel absorption\footnote{The only indisputable
+  outflow component.} in the model: XX\%\ of the mass in the flow
+corresponds to XX\%\ of the absorption.  
+[Can momentum driven winds get this much energy/mass flux?]
+We conclude that in their attempt to reconcile the absorption
+transverse to LBGs with that along LBG sightlines that S+10 were
+driven to this highly unrealistic scenario.
+
+Both the energy and power of this outflow are predicted to achieve
+very large quantities and, again, most of this occurs at large radii.
+[Discuss \lya\ emission here]
 

### 2011-04-01 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5810 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
+\newcommand{\tmax}{$\tau_v^{\rm max}$}
+\def\N#1{{N({\rm #1})}}
+\newcommand{\mtmax}{\tau_v^{\rm max}}
+\newcommand{\mtauv}{\tau_v}
+\newcommand{\tauv}{$\tau_v$}
 \newcommand{\mmc}{m_{\rm c}}
+\def\mrvir{r_{\rm vir}}
+\def\rvir{$r_{\rm vir}$}
+\def \msun {M_\odot}
+\def\wlya{$W^{\rm Ly\alpha}$}
+\def\mwlya{W^{\rm Ly\alpha}}
 \newcommand{\tpk}{$\tau_{\rm pk}$}
@@
 normalization, is the fitted profile of S+11 to their observations,
-$\mu(\rho) \propt \exp(-\rho/b)$ with $b=20$\,kpc.  In constrast to
+$\mu(\rho) \propto \exp(-\rho/b)$ with $b=20$\,kpc.  In constrast to
 the observations, the clump model predicts that 95\%\ of the
@@
 the number density of clumps $n(r)$ in this shell to the covering
-fraction of the clumps $f_\rm{c}(r)$:
+fraction of the clumps $f_{\rm c}(r)$:
 
@@
 n(r) = \frac{f_{\rm c}(r)}{\sigma} \frac{1}{\Delta r}
-\lable{eqn:density}
+\label{eqn:density}
 \end{equation}
@@
 metal-line transitions observed by S+10, e.g.\ \ion{Si}{2}~1526.  
-This implies a minimum column density of Si$^+$ ions; we adopt
+This implies a minimum column density of Si$^+$ ions;\footnote{For this
+  calculation we adopt the LBG clump model parameters from S+10 that
+  apply to Si$^+$.  In this respect, the estimates may be a lower
+  limit given that the Hydrogen gas is predicted to extend to larger
+  radii.} 
+we adopt
 $\N{Si^+} > 10^{14} \cm{-2}$.  In turn, this implies a lower limit to

### 2011-04-04 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5823 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 blueshifted with respect to the galaxy's stars and nebular regions.
-These data characterize the kinematics of the outflow and may place
+These data characterize the kinematics of the outflow and place
 constraints on the optical depth and/or covering fraction of the
-material.  These ``down-the-barrel'' observations, however, provide
-very weak constraints on the distance of the gas from the galaxy.
+gas.  These ``down-the-barrel'' observations, however, provide
+very weak constraints on the distance of the flow from the galaxy.
 Therefore, the mass, energy, and power of the wind and its subsequent
-affect on the so-called circumgalactic medium of the galaxy remain
+effects on the circumgalactic medium (CGM) of the galaxy and/or the
+intergalctic medium (IGM) beyond it remain
 open and compelling questions.
 
-At $z\sim 3$, the most extensively observed poplution of star-forming
+At $z\sim 3$, the most extensively observed population of star-forming
 galaxies is the Lyman Break Galaxies (LBGs), named for their
-characteristic dip in flux from absorption by the intergalactic medium
-(IGM).  For the past $\sim 15$ years, the group led by C. Steidel has
+characteristic dip in flux due to \lya\ absorption by the IGM.
+For the past $\sim 15$ years, the group led by C. Steidel has
 amassed the largest spectroscopic and imaging datasets on these
-galaxies \citep{steidel96,shapley03,reddyXX}.  These earlier works
+galaxies \citep{steidel96,shapley03,reddyXX}.  Their early works
 demonstrated nearly ubiquitous absorption from low and high-ion
 transitions that is systematically blue-shifted relative to the
-galaxy's stars and nebular emission.  These same spectra also revealed
+galaxy's stars and nebular emission.  These same spectra also reveal
 a diversity of \lya\ emission lines whose properties correlate with galaxy photometric
-and spectroscopic properties \citep{shapley08,cooke08}.  Irrespective
-of the \lya\ equivalent widths \wlya\, however, the line is uniformly
+and spectroscopic properties \citep{shapley08,cooke08}.  
+A nearly generic characteristic of this emission is that
+the line is 
 shifted redward of systemic.  This has been interpted by numerous
-authors as yet another signature of the outflow
+authors as yet another signature a galactic-scale outflow
 \citep[e.g.][]{pettini,verhamme}.
 
-Recently, their
+Recently, the Steidel
 collaboration has published two papers that offer new insight into the
@@
 S+10]{steidel+10}, the authors have stacked low S/N, moderate
-resolution ($R \sim XX$) spectra of background galaxies at the
-rest-wavelengths of foreground LBGs with impact parameters $\rho \sim
+resolution ($R \sim 1000$) spectra of background galaxies at the
+rest-wavelengths of foreground LBGs having impact parameters $\rho \sim
 10-100$\,kpc.  This analysis revealed that LBGs are surrounded by a
-CGM that gives rise to \ion{H}{1}, low-ion (e.g.\ \ion{C}{2}~1334,
-\ion{Si}{2}), and high-ion (e.g.\ \ion{C}{4}) absorption from $\rho
-\approx 0-100$\,kpc.  S+10 modeled the blue-shifted absorption
-observed down-the-barrel with the extended absorption detected to
-large impact parameter as a clumpy, galactic-scale wind with speeds of
-$v \sim 800 \, \mkms$ and radial extend $r \sim 100$\,kpc.  Although
+CGM to nearly $\rho \approx 100$\,kpc 
+that gives rise to \ion{H}{1}, low-ion (e.g.\ \ion{C}{2}~1334,
+\ion{Si}{2}), and high-ion (e.g.\ \ion{C}{4}) absorption. 
+S+10 modeled the blue-shifted absorption
+observed down-the-barrel with this extended CGM absorption 
+as a clumpy, galactic-scale wind with speeds of
+$v \sim 800 \, \mkms$ and radial extent $r \sim 100$\,kpc.  Although
 this wind model is not a unique interpretation of the extend
-\ion{H}{1} absorption \citep{fpk+11}, it appears to satisify the key
-absorption observations.
+\ion{H}{1} absorption \citep{fpk+11}, it apparently satisifies the key
+absorption observables.
 
@@
 narrow-band image of $\approx 100$ LBGs at $z \approx 2.5$ they
-measure a `halo' of low surface brightness \lya\ emission with an
-approximately expoentinal profile $\mu(\rho) \sim \exp{-\rho/b}$ from
+measure a `halo' of low surface brightness, \lya\ emission with an
+approximately exponential profile $\mu(\rho) \sim \exp[-\rho/b]$ from
 $\rho \approx 10-80$\,kpc with $b \approx 20$\,kpc.  These authors
@@
 reproduces the stacked absorption spectra (S+10) can reproduce the
-kinematics of \lya\ emitted by the galaxy and the extended \lya\
+kinematics of \lya\ emitted by the galaxy and also the extended \lya\
 emission.  At the same time, they allowed that a proper treatment
-including full radiative transfer was highly warranted.
+of \lya\ emission that includes a full radiative transfer calculation was warranted.
 
@@
 a series of simple wind models with emphasis on the
-\mgiid\ doublet.  In addition to a
+\mgiid\ doublet and \ion{Fe}{2}~UV1 multiplet.  In addition to a
 series of idealized models, we also considered two variations of the
 LBG wind model proposed by S+10.  Although we argued that the results
-for \mgii\ should act as an analog for \lya\ because each is a
-resonantly trapped doublet, we return in this paper to consider
-directly ($\S$~\ref{sec:lya}).  We also expand upon our discussion on the required
-energetics and mass flow of such a wind scenario
+for \mgii\ should act as an analog for \lya\ (because each is a
+resonantly trapped doublet), we return in this paper to consider
+\lya\ directly ($\S$~\ref{sec:lya}).  We also expand upon our discussion on the required
+energetics and mass flow for such a wind scenario
 ($\S$~\ref{sec:energy}).  Unless otherwise indicated, all distances
@@
 $\Lambda = 0.74$, $\Omega_m = 0.26$ and 
-$H_0 = h_{72} 72 \, \mkms/{\rm Mpc}$ \citep{wmap05}.
+$H_0 = 72 h_{72} \, \mkms/{\rm Mpc}$ \citep{wmap05}.
 

### 2011-04-04 Winds/papers/LBG_Lya/Analysis/Tests/test_static.cc

@@ -1,0 +1,438 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e3;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  1205;     // beginning wavelength (Angstroms)
+double l_stop    =  1225;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  0.0;      // inner boundary radius, in kpc
+double r_outer   = 10.0;      // outer boundary radius, in kpc
+double r_emit    =  0.0;      // boundary to emit from
+double n_0       =  1e0;     // number density at inner boundary
+double n_law     =    2.;      // -1*power law exponent of density law
+double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+double v_law     =    1.0;      // power law of velocity profile
+double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 1; 
+// line center wavelengths
+double lambda_0[]   = {1215.6701};
+// line oscillator strengths
+double f_lu[]       = {0.4164};
[…]

### 2011-04-05 Winds/papers/LBG_Lya/Analysis/Tests/test_static.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5824 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -9,7 +9,7 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  1e3;    // number of photons
+double n_photons =  1e5;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
@@ -184,7 +184,7 @@ void Run_Monte_Carlo(char *outfile)
     lam_emit = lam;
     flg_scatter = 0;
 
-    printf("#  Photon %d, lambda = %.4e \n", i, lam);
+    // printf("#  Photon %d, lambda = %.4e \n", i, lam);
 
     // propogate until escaped
     while (1)
@@ -257,7 +257,7 @@ void Run_Monte_Carlo(char *outfile)
 	if (atau > 60)     xcr = 0.02*exp(1.4*pow(log(atau),0.6));
 	else if (atau >1) xcr = 0.02*exp(0.6*pow(log(atau),1.2));
 	else xcr = 0;
-	printf("#  xcr %.4e, NHI = %.4e \n", xcr, log10(NHI));
+	//printf("#  xcr %.4e, NHI = %.4e \n", xcr, log10(NHI));
 	u1  = sqrt(xcr*xcr-1.0*log(1.0-R11))*cos(2*PI*R10);
 	u2  = sqrt(xcr*xcr-1.0*log(1.0-R11))*sin(2*PI*R10);
 	

### 2011-04-05 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5825 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -48,7 +48,7 @@ double f_lu[]       = {0.4164};
 double abun[]       = {1.};  // Solar metallicity and 1/10 down for dust
 double metallicity       = 1.0;                 // 1 = Solar
  // lines doppler velocity in cm/s
-double v_doppler    =   20*1e5;              
+double v_doppler    =   40631.;  // T=10K
 
 // parameters describing voigt profile
 double Dnu   = v_doppler * 2.466e15 / 2.9979e10 ;   
@@ -179,8 +179,8 @@ void Run_Monte_Carlo(char *outfile)
     // Get initial positions and direction
     Emit(r,D,r_emit);
 
-    // initial wavelength (Uniform continuum)
-    lam = l_start + (l_stop-l_start)*gsl_rng_uniform(rangen);
+    // initial wavelength (Monochromatic at line center)
+    lam = lambda_0[0];
     lam_emit = lam;
     flg_scatter = 0;
 
@@ -191,7 +191,8 @@ void Run_Monte_Carlo(char *outfile)
     {
       // photon wavelength in local frame
       rad = sqrt(r[0]*r[0] + r[1]*r[1] + r[2]*r[2]);
-      vel = Get_Velocity(r,rad)/C_LIGHT;
+      // vel = Get_Velocity(r,rad)/C_LIGHT;
+      vel = 0;
       lam_loc = lam*(1 + vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
 
       // printf("#  rad = %.4e, lambda = %.4e \n", rad, lam_loc);
@@ -295,7 +296,8 @@ void Run_Monte_Carlo(char *outfile)
 
 	// now get change in observer frame wavelength
 	rad = sqrt(r[0]*r[0] + r[1]*r[1] + r[2]*r[2]);
-	vel = Get_Velocity(r,rad)/C_LIGHT;
+	// vel = Get_Velocity(r,rad)/C_LIGHT;
+	vel = 0;
 	if (rad > 0)
 	  lam = lam_loc/(1 + vel*(r[0]*D[0] + r[1]*D[1] + r[2]*D[2])/rad);
       }

### 2011-04-05 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5826 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -22,14 +22,14 @@ int    n_phi     =    1;      // number of phi bins
 
 // grid parameters
 double r_inner   =  0.0;      // inner boundary radius, in kpc
-double r_outer   = 10.0;      // outer boundary radius, in kpc
+double r_outer   = 1.0;      // outer boundary radius, in kpc
 double r_emit    =  0.0;      // boundary to emit from
-double n_0       =  1e0;     // number density at inner boundary
-double n_law     =    2.;      // -1*power law exponent of density law
-double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
-double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
-double v_law     =    1.0;      // power law of velocity profile
-double bipolar   =    0;      // degree of bipolarity
+double n_0       =  3.0934e-6;     // number density at inner boundary
+//double n_law     =    2.;      // -1*power law exponent of density law
+//double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+//double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+//double v_law     =    1.0;      // power law of velocity profile
+//double bipolar   =    0;      // degree of bipolarity
 
 double dust_cs     = 3.33e-24;    // dust cross-section
 double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
@@ -123,9 +123,9 @@ double Get_Velocity(double *x, double r)
 //--------------------------------------------
 double Get_Density(double *x, double r)
 {
-  if (r == 0) return 0;
-  if (r < r_inner) return 0;
-  //  if (r > r_outer) return 0;
+  //if (r == 0) return 0;
+  //if (r < r_inner) return 0;
+  if (r > r_outer) return 0;
   // double mu = x[2]/r;
   return n_0;
 }

### 2011-04-05 Winds/papers/Theory/First/Analysis/Infall/outin_rad_mgii.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5827 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,441 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e7;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  2780;     // beginning wavelength (Angstroms)
+double l_stop    =  2820;     // ending wavelength (Angstroms)
+double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  1.0;      // inner boundary radius, in kpc
+double r_outer   = 100.0;      // outer boundary radius, in kpc
+double r_emit    =  0.2;      // boundary to emit from
+double n_0       =  3e-2;     // number density at inner boundary (cm^-3)
+double r_g    =  4.0;      // Wind parameter (kpc)
+double v_norm    =  250.*1e5;    // velocity at outer boundary (cm/s)
+double r_0    = 1.;      // Launch radius (kpc)
+
+// Infall parameters
+double r_infall = 50.;  // Radius to begin infall  (kpc)
+double n_infall = 1e-2;  // Density at r_infall  (cm^-3)
+double v_infall = -1*100*1e5;  // Radial velocity at r_infall (cm/s)
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_tau   = 0.;          // Optical depth of dust through the wind (r=0 to Infinity)
+//double omnl = 1-n_law;
+//double nH_colm   =  n_0 * pow(r_inner,n_law)  * ( pow(r_outer,omnl)-pow(r_inner,omnl) ) / omnl;
+double dust_norm   =  0.;   // Normalization to give dust_tau
[…]

### 2011-04-05 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5828 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -9,20 +9,20 @@
 #include "spectrum.hh"
 
 // monte carlo parameters
-double n_photons =  1e5;    // number of photons
+double n_photons =  1e3;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  1205;     // beginning wavelength (Angstroms)
-double l_stop    =  1225;     // ending wavelength (Angstroms)
-double l_delta   =   0.1;     // wavelength resolution (Angstroms)
+double l_start   =  1215.5;     // beginning wavelength (Angstroms)
+double l_stop    =  1216;     // ending wavelength (Angstroms)
+double l_delta   =   0.002;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins
 
 // grid parameters
 double r_inner   =  0.0;      // inner boundary radius, in kpc
-double r_outer   = 1.0;      // outer boundary radius, in kpc
+double r_outer   = 10.0;      // outer boundary radius, in kpc
 double r_emit    =  0.0;      // boundary to emit from
 double n_0       =  3.0934e-6;     // number density at inner boundary
 //double n_law     =    2.;      // -1*power law exponent of density law
@@ -48,7 +48,7 @@ double f_lu[]       = {0.4164};
 double abun[]       = {1.};  // Solar metallicity and 1/10 down for dust
 double metallicity       = 1.0;                 // 1 = Solar
  // lines doppler velocity in cm/s
-double v_doppler    =   40631.;  // T=10K
+double v_doppler    =   40631.;  // cm/s :: T=10K
 
 // parameters describing voigt profile
 double Dnu   = v_doppler * 2.466e15 / 2.9979e10 ;   
@@ -84,7 +84,7 @@ int main(int argc, char **argv)
   rangen = gsl_rng_alloc (TypeR);
   
   // initialize the Voigt profile
-  // printf("# Voigt a =  %.3e \n", voigt_a);
[…]

### 2011-04-05 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere2.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5829 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -1,0 +1,441 @@
+#include <mpi.h>
+#include <math.h>
+#include <stdlib.h>
+#include <stdio.h>
+#include <time.h>
+#include <gsl/gsl_rng.h>
+#include "locate_array.hh"
+#include "voigt.hh"
+#include "spectrum.hh"
+
+// monte carlo parameters
+double n_photons =  1e3;    // number of photons
+double stepsize  = 0.01;   // maximum size of photon step 
+
+// output spectrum parameters
+double l_start   =  1215.5;     // beginning wavelength (Angstroms)
+double l_stop    =  1216;     // ending wavelength (Angstroms)
+double l_delta   =   0.002;     // wavelength resolution (Angstroms)
+double F_cont    =    1;      // continuum flux level
+int    n_mu      =    1;      // number of theta bins
+int    n_phi     =    1;      // number of phi bins
+
+// grid parameters
+double r_inner   =  0.0;      // inner boundary radius, in kpc
+double r_outer   = 10.0;      // outer boundary radius, in kpc
+double r_emit    =  0.0;      // boundary to emit from
+double n_0       =  6.4815577e-3; // Gives 2x10^20 cm^-2
+//double n_law     =    2.;      // -1*power law exponent of density law
+//double v_max     =  4.0e7;    // velocity at outer boundary (cm/s)
+//double v_min     =  50.*1e5;    // velocity at inner boundary (cm/s)
+//double v_law     =    1.0;      // power law of velocity profile
+//double bipolar   =    0;      // degree of bipolarity
+
+double dust_cs     = 3.33e-24;    // dust cross-section
+double dust_dens   = 0.;          // density of NH/dust, 1 gives tau=1
+double dust_albedo = 0.0;         // ratio of scattering to absorption
+
+
+// line parameters
+// --------------------------
+ //number of lines to use
+int    n_lines      = 1; 
+// line center wavelengths
+double lambda_0[]   = {1215.6701};
+// line oscillator strengths
+double f_lu[]       = {0.4164};
[…]

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Shared_Codes/kasen_voigt.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5832 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -4,10 +4,8 @@
 #include <stdio.h>
 #include <math.h>
 #include <string.h>
-#include <gsl/gsl_cdf.h>
 #include "voigt.hh"
 
-// Now using an algorithm from Michele (Zaghloul et al. 2007)
 
 void VOIGT::New(int n, double xmax, double a)
 {
@@ -25,53 +23,47 @@ void VOIGT::Compute_Profile()
   int i;
   double y,v,e,expy,expv;
   double xsq, c, q, pic,SQRT_PI;
-  double Hau,error,ffactor;
   
   double ymax = 10*x.Max();
   double dy   = a_param*0.01;
   double ap   = a_param*a_param;
 
-  //initilize integral
-  gsl_integration_workspace * w=gsl_integration_workspace_alloc (1000);
-       
-  //intialize function
-  gsl_function F;
-  F.function = &VOIGT::Integrand;
-
   // zero out
   for (i=0;i<n_x;i++) profile[i] = 0;
 
+  // // do integral over yfrom -infinity to +infinity
+  // for (y = -1*ymax;y<ymax;y+=dy)
+  // {
+  //   expy = exp(-1*y*y);
+  //   for (i=0;i<n_x;i++)
+  //   {
+  //     v = x.Center(i);
+  //     profile[i] += expy/((v-y)*(v-y) + ap)*dy;
+  //   }
+  // }
+
+  // // renormalize
+  // for (i=0;i<n_x;i++) profile[i] = a_param/PI*profile[i]/sqrt(PI);
+
+
   // Numerical Approx
+  SQRT_PI = sqrt(PI);
   for (i=0;i<n_x;i++)
     {
-      voigt_u = x.Center(i);
-      
-      if(a_param < 200){
-	//compute the inegral term for H(a,u)
-	// F.params=&p;
-	//gsl_integration_qags(&F,0.,voigt_u,0,1e-8,1000,w,&Hau,&error); 
-      gsl_integration_qag(&F,0.,voigt_u,0,1e-8,1000,6,w,&Hau,&error); 
-      //compute the factor in the front (2 cases)
-      if(a_param < 26.6){
-	//use full function
-	ffactor=exp(-voigt_u*voigt_u)*cos(2*a_param*voigt_u)*exp(a_param*a_param)*erfc(a_param);
-	Hau=ffactor+1.12837917*Hau;
[…]

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Shared_Codes/miki_voigt.cc

@@ -36,7 +36,12 @@ void VOIGT::Compute_Profile()
        
   //intialize function
   gsl_function F;
+  //>>>MF: This line won't work since you are
+  //passing double (VOIGT::*)(double, void*) to double (*)(double, void*)
+  //This is a problem with C/C++ interaction.
+  //Here http://www.cplusplus.com/forum/general/10435/ there is a way to fix it.
   F.function = &VOIGT::Integrand;
+  
 
   // zero out
   for (i=0;i<n_x;i++) profile[i] = 0;
@@ -48,47 +53,47 @@ void VOIGT::Compute_Profile()
       
       if(a_param < 200){
 	//compute the inegral term for H(a,u)
-	// F.params=&p;
+	//F.params=&p;
 	//gsl_integration_qags(&F,0.,voigt_u,0,1e-8,1000,w,&Hau,&error); 
-      gsl_integration_qag(&F,0.,voigt_u,0,1e-8,1000,6,w,&Hau,&error); 
-      //compute the factor in the front (2 cases)
-      if(a_param < 26.6){
-	//use full function
-	ffactor=exp(-voigt_u*voigt_u)*cos(2*a_param*voigt_u)*exp(a_param*a_param)*erfc(a_param);
-	Hau=ffactor+1.12837917*Hau;
+	gsl_integration_qag(&F,0.,voigt_u,0,1e-8,1000,6,w,&Hau,&error); 
+	//compute the factor in the front (2 cases)
+	if(a_param < 26.6){
+	  //use full function
+	  ffactor=exp(-voigt_u*voigt_u)*cos(2*a_param*voigt_u)*exp(a_param*a_param)*erfc(a_param);
+	  Hau=ffactor+1.12837917*Hau;
+	} else {
+	  //use series expansion
+	  ffactor=exp(-voigt_u*voigt_u)*cos(2*a_param*voigt_u)/(1.7724538*a_param)*
+	    (1.-(0.5/pow(a_param,2.))+(0.75/pow(a_param,4.))-(1.875/pow(a_param,6.))+
+	     (6.5625/pow(a_param,8.))-(29.53125/pow(a_param,10.))+(162.421875/pow(a_param,12.)));
+	  Hau=ffactor+1.12837917*Hau;
+	}
       } else {
-	//use series expansion
[…]

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Shared_Codes/tau_line.cpp

@@ -1,0 +1,104 @@
+/************************************************************************
+This function computes the optical depth 
+in each cell for a line of a given transition
+at a given frequency "frequency"
+
+Each gas cell has a line centre frequency which is corrected for 
+proper motion, assuming the reference frame is zero at the center
+of the galaxy.
+
+*************************************************************************/
+
+
+//Parameter structure used by the integration function
+struct voig_params{ 
+  double a; 
+  double u;
+};
+
+
+//Integral part of the Voig function in the approximation by zaghloul et al. 2007
+double voigt (double x, void * params) {
+  struct voig_params * p = (struct voig_params *)params;
+  double f =exp(-(p->u*p->u-x*x))*sin(2*p->a*(p->u-x));
+  return f;
+}
+
+/************************
+******MAIN FUNCTION******
+************************/
+
+void tau_line(sim_spectra linetau, vector<double> * tau, double frequency, line_cons line, long ncell){
+  
+  //cout<<"TAU_LINE: Computing optical depth in each cell..."<<endl;
+  
+  //set constants (use cgs everywhere)
+  double s=2.654E-2*line.oscill;
+  double clight=2.9979E10;
+  double rest_nu=clight/line.rest_lambda*1E8;
+  double kbol=1.3807E-16;
+
+  //some variable
+  double lineceter_nu,delta_nud,phi;
+  double Hau,error,ffactor;
+  
+  //initilize integral
+  gsl_integration_workspace * w=gsl_integration_workspace_alloc (1000);
+       
+  //intialize function
+  gsl_function F;
+  F.function = &voigt;
+  struct voig_params p;
+
+  //loop over the cells
+  for(long i=0; i<ncell; i++){
+    
+    //this is the frequency of the center line corrected for proper motion of the cell
+    lineceter_nu=linetau.losvel[i]/(clight*1E-5)*rest_nu+rest_nu;
+    //define constants for this cell. Note that Delta(nu_D) is at rest frequency, NOT linecenter
+    delta_nud=(rest_nu/clight)*sqrt(2*kbol*linetau.temp[i]/line.mass+line.turbul*line.turbul);
[…]

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc

@@ -85,6 +85,7 @@ int main(int argc, char **argv)
   
   // initialize the Voigt profile
   printf("# Voigt a =  %.3e \n", voigt_a);
+  printf("# tau_0  =  %.3e \n", 3.31e-14*(12.85*1e5/v_doppler)*n_0*r_outer*KPARSEC);
   voigt.New(nvoigt,voigt_x,voigt_a);
   // printf("# Finished Voigt!");
 
@@ -184,7 +185,7 @@ void Run_Monte_Carlo(char *outfile)
     lam_emit = lam;
     flg_scatter = 0;
 
-     printf("#  Photon %d, lambda = %.4e \n", i, lam);
+    // printf("#  Photon %d, lambda = %.4e \n", i, lam);
 
     // propogate until escaped
     while (1)

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere2.cc

@@ -13,9 +13,9 @@ double n_photons =  1e3;    // number of photons
 double stepsize  = 0.01;   // maximum size of photon step 
 
 // output spectrum parameters
-double l_start   =  1215.5;     // beginning wavelength (Angstroms)
-double l_stop    =  1216;     // ending wavelength (Angstroms)
-double l_delta   =   0.002;     // wavelength resolution (Angstroms)
+double l_start   =  1210.;     // beginning wavelength (Angstroms)
+double l_stop    =  1220;     // ending wavelength (Angstroms)
+double l_delta   =   0.02;     // wavelength resolution (Angstroms)
 double F_cont    =    1;      // continuum flux level
 int    n_mu      =    1;      // number of theta bins
 int    n_phi     =    1;      // number of phi bins

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Shared_Codes/miki_voigt.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5840 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -5,9 +5,10 @@
 #include <math.h>
 #include <string.h>
 #include <gsl/gsl_cdf.h>
-#include "voigt.hh"
+#include "miki_voigt.hh"
 
 // Now using an algorithm from Michele (Zaghloul et al. 2007)
+
 
 void VOIGT::New(int n, double xmax, double a)
 {
@@ -40,8 +41,7 @@ void VOIGT::Compute_Profile()
   //passing double (VOIGT::*)(double, void*) to double (*)(double, void*)
   //This is a problem with C/C++ interaction.
   //Here http://www.cplusplus.com/forum/general/10435/ there is a way to fix it.
-  F.function = &VOIGT::Integrand;
-  
+  F.function = &VOIGT::CallIntegrand;
 
   // zero out
   for (i=0;i<n_x;i++) profile[i] = 0;
@@ -125,7 +125,7 @@ void VOIGT::Print()
 }
 
 
-static double VOIGT::CallIntegrand(double y,void * params)
+static double VOIGT::CallIntegrand(double y,void * v)
 {
   CCallbackHolder * h = static_cast<CCallbackHolder*>(v);
   return h->cls->Integrand(h->data);

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Shared_Codes/miki_voigt.cc
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5845 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -56,6 +56,7 @@ void VOIGT::Compute_Profile()
 	//F.params=&p;
 	//gsl_integration_qags(&F,0.,voigt_u,0,1e-8,1000,w,&Hau,&error); 
 	gsl_integration_qag(&F,0.,voigt_u,0,1e-8,1000,6,w,&Hau,&error); 
+	exit(1);
 	//compute the factor in the front (2 cases)
 	if(a_param < 26.6){
 	  //use full function
@@ -125,10 +126,10 @@ void VOIGT::Print()
 }
 
 
-static double VOIGT::CallIntegrand(double y,void * v)
+double VOIGT::CallIntegrand(double y,void * v)
 {
   CCallbackHolder * h = static_cast<CCallbackHolder*>(v);
-  return h->cls->Integrand(h->data);
+  return h->cls->Integrand(y,h->data);
 }
 
 double VOIGT::Integrand(double y,void * params)

### 2011-04-06 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc

@@ -5,7 +5,7 @@
 #include <time.h>
 #include <gsl/gsl_rng.h>
 #include "locate_array.hh"
-#include "voigt.hh"
+#include "miki_voigt.hh"
 #include "spectrum.hh"
 
 // monte carlo parameters

### 2011-04-20 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5912 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 
-\newcommand{\tmax}{$\tau_v^{\rm max}$}
 \def\N#1{{N({\rm #1})}}
-\newcommand{\mtmax}{\tau_v^{\rm max}}
+\newcommand{\tmax}{$\tau_v^{\rm IGM, max}$}
+\newcommand{\mtmax}{\tau_v^{\rm IGM, max}}
 \newcommand{\mtauv}{\tau_v}
 \newcommand{\tauv}{$\tau_v$}
+\newcommand{\tigm}{$\tau_v^{\rm IGM}$}
+\newcommand{\mtigm}{\tau_v^{\rm IGM}}
 \newcommand{\mmc}{m_{\rm c}}
@@
 dense clumps, each optically thick to \lya\ and metal-line
-transitions, but as an ensemble have a partial covering fraction to
+transitions, but which as an ensemble have a partial covering fraction to
 the LBG and background sources.  We discuss in PKR11 our radiative
 transfer treatment for this wind in the context of \mgiid.  In the
-following, we adopt the same prescription but consider
+following, we adopt the same algorithms but focus on
 \lya\footnote{Following standard practice, we treat \lya\ as a single
@@
   than the astrophysical velocities of interest here.}
-and modify the parameters of the LBG clump model to those presented in
-S+10.
+and modify the parameters of the LBG clump model as appropriate.
 
@@
 galaxy near the \lya\ line: 
-(i) a flat continuum, primarily generated by O and B stars within the
+(i) a flat continuum, assumed to be generated by O and B stars within the
 star-forming galaxy; and
-(ii) a continuum plus \lya\ emission-line model parameteized by a
-line-width $\sigma_{\rm Ly\alpha}$ and an equivalent width \wlya.
-This line is presumed to be generated by \ion{H}{2} regions within the
-galaxy.  We emphasize that neithre of these simple models are likely
+(ii) a continuum plus \lya\ emission-line model parameterized by a
+line-width $\sigma_{\rm Ly\alpha}$ and a \lya\ equivalent width \wlya.
+The \lya\ emission is presumed to be generated by \ion{H}{2} regions within the
+galaxy.  We emphasize that neither of these simple models are likely
 to describe the complex emission of a star-forming galaxy at \lya.
 Nevertheless, they help capture some of the salient features of the
-LBG clump model.
+LBG clump wind model.
 
-Second, we have modeled attenuation of photons near \lya\ by the
-intergalactic medium (IGM) surrounding LBGs on scales of $\sim 100\,
+Second, we have modeled the attenuation of photons near \lya\ by the
+IGM surrounding LBGs on scales of $\sim 100\,
 {\rm kpc} - 10$\,Mpc.  Our approach follows the method of
@@
 = 80$\,kpc, circular velocity $v_{\rm c} = 220 \mkms$, and an
-IGM with $T = 10^4$\,K, and a EUVB with ionization rate $\Gamma =
+IGM with $T = 10^4$\,K.  THis amterial is bathed in a uniform
+extragalactic UV
+background (EUVB) radiation field with ionization rate $\Gamma =
 10^{-12.5} \, \rm s^{-1}$ \citep{fpl+08}.  With this parameterization,
 we can calculate the density and velocity profiles of gas at $r >
-\mrvir$ for the LBG (and assume the gas at $r<\mrvir$ is dominated by
+\mrvir$ for the LBG (and assume the gas at $r\le \mrvir$ is dominated by
 the outflow) and apply the Sobolev approximation to calculate the
-optical depth \tauv\ to \lya\ as a function of velocity.  We cuation that
-this $\exp(-\mtauv)$ prescription does not capture the complexity of
+optical depth $\tigm$ to \lya\ as a function of velocity.
+We caution that
+this $\exp(-\mtigm)$ prescription does not capture the complexity of
 gas on these scales.  Indeed, \cite{zheng10a} have argued that a more
-proper treatment tends to yield higher opacity.
-[INCLUDE THE BOOST?]
-In either case, it is a necessary consideration for modeling the
-observed \lya\ emission from these galaxies.
+proper treatment tends to yield even higher average opacity.
+[INCLUDE THE BOOST? Yes, and justify to match $D_A$]
+[CHECK against Djisktra]
+Therefore, one may wish to consider our estimation of \tigm\ as a
+lower limit.
 
@@
 two intrinsic emission models of the galaxy.
+For the line-emission, we have adopted $\sigma_{\rm Ly\alpha} =
+50\mkms$ and $\mwlya = 100$\AA, the latter of which is suggested for
+actively star-forming galaxies \citep{lya_emit}.
 The second panels show the predicted results when one includes
-radiative transfer through the LBG clump model.  Similar to the \mgii\
+radiative transfer through the LBG clumpy wind model.  Similar to the \mgii\
 results of PKR11, we observe significant absorption by the outflow for
-$v < 0\mkms$.  The absorption actually peaks at $v < 0\mkms$ because
-scattered emission has `filled-in' the absorption for $v \approx 0
-\mkms$.  This emission peaks just redward of $v=0\mkms$, related to
-photons emitted transverse to our sightline and scattered once to
-Earth, and then extends to positive velocity, with a tail to $v
-\approx +500\mkms$.  [Comment on Lya emission line model?]
+$v < 0\mkms$.  
+Although the opacity of the outflow peaks at $v \approx 0 \mkms$, the
+minimum flux is actually observed to be closer to $v \approx -300
+\mkms$ because
+scattered emission `fills-in' the absorption at $v \lesssim 0
+\mkms$.  Most of these scattered photons were
+emitted transverse to our sightline and then scattered once to
+Earth.  The tail of emission to positive velocities ($v
+\approx +500\mkms$) in contrast, are associated with photons that
+scattered off the far-side of this isotropic outflow.  
+We emphasize that this emission is weak in comparison with the
+flux at $v \approx 0 \mkms$, simply because of geometrical projection.
+
+[Emphasize that in this clump model, photons don't diffuse in
+frequency much]
+
 The third pair of panels includes the effects of IGM scattering.  For
@@
 the \lya\ emission at $v \approx v_{\rm c}$ but only modest
-attenuation at lower velocity.  For this parameterization, it is evident that
-the effects of the IGM cannot be ignored.  If the IGM were just $5
+attenuation at lower velocities.  Although the IGM effects for our
+parameterization are relatively modest compared to the outflow, it is evident that
+the IGM cannot be ignored at this redshift.  If the IGM were just $5
 \times$ more neutral than modeled here, the \lya\ line would be
@@
 galaxy emits ionizing photons then \tmax\ may fall below unity and the
-IGM would play a minor role.  Clearly, a full treatment of these
-effects is warranted for the $z \sim 3$ universe.
+IGM would play a minor role.  Clearly, a full treatment 
+is warranted for the $z \sim 3$ universe.
 
-In the bottom panels, we present the full model convolved with an
-ideal spectrometer with FWHM~$\approx 250\mkms$ compared against the
-observed, average \lya\ emission profile of LBGs from
-\cite{shapley03}.  
-At this spectral resolution,
-typical of LBG spectroscopic observations, the weak emission that was
+In the bottom panels we present the full model, convolved with an
+ideal spectrometer having FWHM~$\approx 250\mkms$, compared against the
+average \lya\ emission profile observed for a sample of $z \sim 3$ 
+LBGs \citep{shapley03}. 
+[Match our resolution to Shapley??]
+At this spectral resolution, which is
+typical of LBG spectroscopic observations, the weak emission at $v
+\approx 0 \mkms$ that was
 apparent for the continuum model is lost and one predicts a simple
-absorption profile that extends to positive velocity because of IGM
-attenuation.  This model is a very poor description of the data.  
+absorption profile that extends to positive velocity. 
+This model is a very poor description of the data.  
 For the line+continuum intrinsic model, in contrast, it is difficult
@@
 this spectral resolution within the \lya\ emission profile.
-Neither model predicts a significant emission line that is shifted by
-several hundred \kms\ redward of systemic.  Indeed, reviewing the
-results on \mgii\ from PKR11, such a shift is predicted for any
-outflow model that we have considered.  The only scenario in PKR11
-that showed a significant shift was when we included significant
-opacity at $v \approx 0 \mkms$ at the source, i.e.\ an ISM model.
-This has the the effect of altering the intrinsic emission [How?] 
-and when combined with an outflow can yield a redshifted emission
-profile.  [Do this with Lya!] 
-[Comment that infall can produce a redshift \lya\ line too, i.e. Zheng
-et al.]
+Neither model predicts significant line-emission 
+at several hundred \kms\ redward of systemic.  
+Such emission is {\it not a natural prediction of a clumpy outflow
+  model} where the photons tend to escape because of partial covering
+not photon diffusion.  In fact, reviewing the
+results on \mgii\ from PKR11, such shifts are rare in
+outflow models that we have considered.  The only models in PKR11
+with significant shifts to positive velocity was when there was large 
+opacity at $v \approx 0 \mkms$ near the source, e.g.\ models that
+included an ISM component. In essence, this gas modifies the intrinsic
+line profile of \lya, yielding the standard `double hump' emission and
+then the blue hump is strongly attenuated by the outflow.
+[Test this with Lya!] 
+It is also worth noting that a strict infall scenario on Mpc scales
+also naturaly predicts a redshifted \lya\ line.  The IGM model of
+\cite{zheng+10}, for example, predicts \lya\ emission will be detectd
+at $v \approx +XX \mkms$ from star-forming galaxies.
 
-[Previous authors have modeled the \lya\ profiles of LBGs and have
-concluded the redshift emission is well decribed by an outflow
-\citep[e.g.][]{verhomme}.  Similar to the
-ISM+wind model described above, these outflow models only predict a
+In contrast to our assertions,
+other authors have modeled the \lya\ profiles of LBGs and have
+concluded the redshifted emission is a `clear signature' of an outflow
+\citep[e.g.][]{verhomme}.  
+[page 7]
+
+Similar to the ISM+wind model described above, these outflow models only predict a
 redshift if there is a very large opacity at $v \approx 0\mkms$.  In

### 2011-04-20 Winds/papers/LBG_Lya/lya_lbg.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5913 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 other authors have modeled the \lya\ profiles of LBGs and have
-concluded the redshifted emission is a `clear signature' of an outflow
-\citep[e.g.][]{verhomme}.  
-[page 7]
-
-Similar to the ISM+wind model described above, these outflow models only predict a
-redshift if there is a very large opacity at $v \approx 0\mkms$.  In
-the \cite{verhomme} models, this is accomplished by considering a
-thin expanding shell with a total \ion{H}{1} column density $\mnhi > 10^{20}
-\cm{-2}$.  In this case, the damping wings of the gas imply a large
-opacity at $v \approx 0 \mkms$ provided the shell has a speed less
-than $\approx 500 \mkms$.  This model, then, predicts a very strong
-absorption profile at $v < 0 \mkms$, which is generally not observed
-in the LBG spectra.  One of the few exceptions is the galaxy cb58.]
+concluded the redshifted emission is a `clear signature' of an
+outflow.
+The [most extensive] modeling of \lya\ emissoin by LBGas to date has
+been performed by A. Verhomme and collaborators
+\citep{verhommea,verhommeb}.  Their preferred model has been a thin
+expanding shell characterized by the expansion speed $v_{\rm exp}$ and
+total surface density of \ion{H}{1} gas in the shell.  Although the
+shell's dynamics play a role in the \lya\ emission kinematics, the
+[dominant] aspect for the emergent spectrum is the \ion{H}{1} column
+density.  Indeed, they only predict a dominant emission peak at $v \gg
+0 \mkms$ if $\mnhi > 2\sci{20} \cm{-2}$.  For lower values, the
+emission is preferentially at $v \lesssim +100 \mkms$.  The
+explanation is similar to the ISM model described above;  large \nhi\
+values force diffusion of \lya\ in frequency.  Furthermore, their
+models predict substantial \lya\ absorption at $v < 0 \mkms$.  
+Strong absorption is observed in a handful of individual spectra
+\citep[e.g.][]{cb58,dessauges}, but is not evident in the stacked
+spectra of \cite{shapley93} or \cite{steidel+10}.  
+[Why is there sometimes weak \lya\ emission at $v < 0 \mkms$ in LAEs
+at $z \sim 3$?]
+[Read Shapley et al 2009 paper]
+[Redshfited, asymmetric emission is suggestive of an outflow]
 
@@
 vs.\ projected radius for the flat-continuum intrinsic model and with
-no IGM attenuation.  The signal is integrated from velocities $v =
-[-100,400]\mkms$. Overplotted on the model, at an arbirtrary
+no IGM attenuation.  The signal is integrated over velocities $v =
+[-100,400]\mkms$, which corresponds to the majority of predicted line-emission.
+Overplotted on the model, at an arbirtrary
 normalization, is the fitted profile of S+11 to their observations,
-$\mu(\rho) \propto \exp(-\rho/b)$ with $b=20$\,kpc.  In constrast to
+$\mu(\rho) \propto \exp[-\rho/b]$ with $b=20$\,kpc.  
+Although this model appears to be tending toward such an exponential
+profile at very large impact parameter ($\rho > 50$\,kpc), the model
+predict greater flux and a steeper fall-off at small radii.
+In strong constrast to
 the observations, the clump model predicts that 95\%\ of the
-integrated flux is emitted at $\rho < 10$\,kpc and the model assumes
-an exponential-like profile only at very large radii.  In short, a
-proper radiative transfer treatment of the LBG clump model shows it
-cannot reproduce the observed, extended \lya\ emission.
+integrated flux is emitted at $\rho < 10$\,kpc.  
+It is simply impossible to reconcile the LBG clump model with the
+observed profile, and we further emphasize that including the IGM
+attenutation and/or an intrinsically bright \lya\ emission line only
+worsens the agreement.
 
 The explanation for the model's failure is twofold:  
-(1) the covering fraction of the clumps decrease with radius to
-$f_{\rm c} < 0.2$ at $\rho > 50$\,kpc; and
-(2) the velocity gradient at $r>5$\,kpc is very shallow.  Therefore,
-at large radii the outflow absorbs very few photons relative to the
+(1) the covering fraction of the clumps decrease with increasing radius to
+$f_{\rm c} < 0.2$ at $r > 50$\,kpc; and
+(2) the velocity gradient is very shallow beyond the inner few kpc. Therefore,
+the outflow absorbs very few photons at large radius compared to the
 inner regions.  In terms of the Sobolev approximation, we estimate
-$\tau_{\rm S}(\rho = 60 \, {\rm kpc}) = XX \tau_{\rm S}(\rho=1\, {\rm
-  kpc})$.  
-Note that unlike the kinematic signatures, the inclusion of an ISM
-component at small radii would not alter any of these conclusions.
-[Add a last few lines]
+$\tau_{\rm S}(\rho = 60 \, {\rm kpc}) = 10^{-4} \tau_{\rm S}(\rho=1\, {\rm
+  kpc})$.  [Figure?]
+We further emphasize that the inclusion of an ISM
+component at small radii would not qualitatively alter any of these conclusions.
+Instead, one requires additional sources of \lya\ emission at large
+radii or additional opacity in the CGM far beyond that predicgted by
+the LBG clump model.  We return to these issues in
+$\S$~\ref{sec:later}.
 
@@
 
-In the previous section, we demonstrated that the LBG clump model
-of S+10 does not reproduce the observed \lya\ emission associated with
+In the previous section, we showed that the LBG clump model
+of S+10 cannot on its own reproduce the observed \lya\ emission associated with
 LBGs.   We also emphasize, however, that the radiative transfer of
@@
 10$\,kpc), the physics of the gas in the CGM ($r \sim 100$\,kpc), and
-also the property of the IGM on larger scales ($r \sim 1-10$\,Mpc).
+also the properties of the IGM on larger scales ($r \sim 1-10$\,Mpc).
 It is possible, therefore, that the observed \lya\ emission is
-dominated by components other than a galactic-scale wind, indirectly
-observed as blue-shifted absorption.  In this respect, the LBG clump
-model cannot be ruled out by its discordance with the \lya\
+dominated by components other than a galactic-scale wind.
+In this respect, the LBG clump
+model cannot be ruled out because of its discordance with the \lya\
 observations.
@@
 \end{equation}
-Following Sobolev formalism, we set the shell thickness with radius to
-the velocity gradient of the flow
+Following the Sobolev formalism, we set the shell thickness at a given
+radius according to the velocity gradient of the flow,
 
 \begin{equation}
-\Delta r = \Delta v_{\rm c} \ltp \frac{dv}{dr} \rtp^{-1}
+\Delta r = \Delta v_{\rm c} \ltp \frac{dv}{dr} \rtp^{-1} \cmma
 \end{equation}
 where $\Delta v_{\rm c}$ characterizes the velocity dispersion of the
-clumps, from any combination of internal or external motions within
+clumps.  This velocity dispersion may result from any combination of internal or external motions within
 the shell.  In the following we adopt $\Delta v_{\rm c} = 10 \mkms$.
@@
 we adopt
-$\N{Si^+} > 10^{14} \cm{-2}$.  In turn, this implies a lower limit to
+$\N{Si^+} > 10^{14} \cm{-2}$.  In turn, this yields a lower limit to
 $m_{\rm c}/\sigma$.  For a solar abundance $n_{\rm H} = 10^{-4.5}
@@
 
-Adopting the minimum value for $\mmc/\sigma$,  we derive the mass,
+Adopting the minimum value for $\mmc/\sigma$ from above,  we derive the mass,
 mass flux, energy, and power profiles shown in
@@
 factor of 2 somehow!) at $10^{-2}$ clumps/yr].
-Regarding mass, we find the clump model has $M_{\rm TOT} \approx
-10^{10} \msun$ [check] with nearly all of this matter existing at
-radii $r>20$\,kpc.  Ironically, this material accounts for very little
+Integrating the mass profile of the clumpy wind, we calculate 
+$M_{\rm TOT} \approx 10^{10} \msun$ [check] with nearly all of this
+matter laying at radii $r>20$\,kpc.  Ironically, this material accounts for very little
 of the down-the-barrel absorption\footnote{The only indisputable
@@
 [Can momentum driven winds get this much energy/mass flux?]
-We conclude that in their attempt to reconcile the absorption
-transverse to LBGs with that along LBG sightlines that S+10 were
-driven to this highly unrealistic scenario.
 

### 2011-04-20 Winds/papers/LBG_Lya/lya_lbg.tex
profx
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5914 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 the outflow) and apply the Sobolev approximation to calculate the
-optical depth $\tigm$ to \lya\ as a function of velocity.
+optical depth \tigm\ to \lya\ as a function of velocity.
 We caution that
@@
 [Can momentum driven winds get this much energy/mass flux?]
+This massive outflow was instead motivated by the significant
+absorption toward background sources.
 
@@
 \begin{figure}
-%\includegraphics[scale=0.6,angle=90]{Figures/mass_energy.ps}
+\includegraphics[scale=0.6,angle=90]{Figures/fig_lbg_mass_etc.ps}
 \caption{

### 2011-05-02 Winds/papers/LBG_Lya/Analysis/Tests/test_static_sphere.cc
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5948 ac11df5e-a788-c23b-a8e1-c758c323924d

@@ -10,8 +10,8 @@
 #include "anvoigt.hh"
 
 // monte carlo parameters
-double n_photons =  1e5;    // number of photons
-double stepsize  = 0.01;   // maximum size of photon step 
+double n_photons =  1e3;    // number of photons
+double stepsize  = 100.00;   // maximum size of photon step 
 
 // output spectrum parameters
 double l_start   =  1215.5;     // beginning wavelength (Angstroms)
@@ -54,8 +54,8 @@ double v_doppler    =   40631.;  // cm/s :: T=10K
 // parameters describing voigt profile
 double Dnu   = v_doppler * 2.466e15 / 2.9979e10 ;   
 double voigt_a   = 6.265e8 / (4 * 3.14159 * Dnu);   // gamma/(4 pi Dnu)
-int    nvoigt    = 2000;
-double voigt_x   =  200;  // Allows for over 2000 km/s
+// int    nvoigt    = 2000;
+// double voigt_x   =  200;  // Allows for over 2000 km/s
 // VOIGT voigt;
 ANVOIGT voigt;
 
@@ -86,6 +86,7 @@ int main(int argc, char **argv)
   rangen = gsl_rng_alloc (TypeR);
   
   // initialize the Voigt profile
+  printf("# Doppler =  %.3e \n", v_doppler);
   printf("# Voigt a =  %.3e \n", voigt_a);
   printf("# tau_0  =  %.3e \n", sqrt(3.14159)*3.31e-14*(12.85*1e5/v_doppler)*n_0*r_outer*KPARSEC);
   // voigt.New(nvoigt,voigt_x,voigt_a);
@@ -149,9 +150,10 @@ void Run_Monte_Carlo(char *outfile)
   double u0,u1,u2, R10, R11, rad, vel;
   double uvec[3];
   double nu_d, cross_sec; 
-  double tau_const, atau, NHI, xcr;
+  double tau_const, atau, NHI, xcr, isqpi;
 
-  tau_const = 0.0062344885;   // Constants + f :: Needs N_HI and Dnu
+  // tau_const = 0.0062344885;   // Constants + f :: Needs N_HI and Dnu
+  isqpi = 1./sqrt(PI);
 
   // functions to call
   void MPI_Average_Array(double *, int);
[…]

### 2011-05-02 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@5949 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 dense clumps, each optically thick to \lya\ and metal-line
-transitions, but which as an ensemble have a partial covering fraction to
+transitions, but which as an ensemble have a partial covering fraction
+$f_{\rm c}$ to
 the LBG and background sources.  We discuss in PKR11 our radiative
@@
 \lya\footnote{Following standard practice, we treat \lya\ as a single
-  transition instead of a double because the line separation is much less
+  transition instead of a doublet because the line separation $(\delta
+  v \approx 3.4 \mkms$) is less
   than the astrophysical velocities of interest here.}
@@
 star-forming galaxy; and
-(ii) a continuum plus \lya\ emission-line model parameterized by a
+(ii) a continuum plus single \lya\ emission-line model parameterized by a
 line-width $\sigma_{\rm Ly\alpha}$ and a \lya\ equivalent width \wlya.
@@
 to describe the complex emission of a star-forming galaxy at \lya.
-Nevertheless, they help capture some of the salient features of the
+Nevertheless, they reveal the salient features of the
 LBG clump wind model.
@@
 = 80$\,kpc, circular velocity $v_{\rm c} = 220 \mkms$, and an
-IGM with $T = 10^4$\,K.  THis amterial is bathed in a uniform
+IGM with $T = 10^4$\,K.  This material is bathed in a uniform
 extragalactic UV
@@
 optical depth \tigm\ to \lya\ as a function of velocity.
+We have further increased this optical depth by a factor of 2 to
+better match the average opacity observed for the IGM at this redshift
+\citep[e.g.][]{faucher08}. 
 We caution that
@@
 proper treatment tends to yield even higher average opacity.
-[INCLUDE THE BOOST? Yes, and justify to match $D_A$]
 [CHECK against Djisktra]
-Therefore, one may wish to consider our estimation of \tigm\ as a
+Therefore, one could consider our estimation of \tigm\ to be a
 lower limit.
@@
 For the line-emission, we have adopted $\sigma_{\rm Ly\alpha} =
-50\mkms$ and $\mwlya = 100$\AA, the latter of which is suggested for
+50\mkms$ and $\mwlya = 100$\AA, the latter of which is estimated for
 actively star-forming galaxies \citep{lya_emit}.
@@
 $v < 0\mkms$.  
-Although the opacity of the outflow peaks at $v \approx 0 \mkms$, the
+Although the intrinsic opacity of the outflow peaks at $v \approx 0 \mkms$, the
 minimum flux is actually observed to be closer to $v \approx -300
@@
 We emphasize that this emission is weak in comparison with the
-flux at $v \approx 0 \mkms$, simply because of geometrical projection.
-
-[Emphasize that in this clump model, photons don't diffuse in
-frequency much]
+flux at $v \approx 0 \mkms$, simply because of geometrical effects.
+Clumping models differ qualitatively from diffuse medium scenarios
+with high optical depth in that the latter forces the diffusion of
+\lya\ in frequency space.  In clump models, especially those with
+partial covering, the emission occurs much closer to systemic.
 
@@
 galaxy emits ionizing photons then \tmax\ may fall below unity and the
-IGM would play a minor role.  Clearly, a full treatment 
+IGM would play a very minor role.  Clearly, a full treatment 
 is warranted for the $z \sim 3$ universe.
@@
 this spectral resolution within the \lya\ emission profile.
-Neither model predicts significant line-emission 
+This model predicts significant line-emission, but not 
 at several hundred \kms\ redward of systemic.  
-Such emission is {\it not a natural prediction of a clumpy outflow
-  model} where the photons tend to escape because of partial covering
-not photon diffusion.  In fact, reviewing the
-results on \mgii\ from PKR11, such shifts are rare in
-outflow models that we have considered.  The only models in PKR11
-with significant shifts to positive velocity was when there was large 
-opacity at $v \approx 0 \mkms$ near the source, e.g.\ models that
-included an ISM component. In essence, this gas modifies the intrinsic
-line profile of \lya, yielding the standard `double hump' emission and
-then the blue hump is strongly attenuated by the outflow.
-[Test this with Lya!] 
-It is also worth noting that a strict infall scenario on Mpc scales
+Significant line-emission at $\Delta v \gtrsim +400 \mkms$ is
+{\it not a natural prediction of a clumpy outflow
+  model because the photons do not diffuse in frequency}.
+Another point emphasize by the plots is that the clumpy outflow, on
+its own, cannot produce a large equivalent width of \lya\ emission.
+In an isotropic outflow, the total equivalent width is conserved
+(considerations of dust or anisotropy only tend to reduce the
+emission, e.g.\ PKR11).  This explains the relatively weak emission
+related to the continuum source model.
+
+[Also comment that infall component can easily be lost in \lya]
+
+[Do an ISM + outflow model;  It might predict too much flux at $v
+\approx 0 \mkms$]
+
+%In fact, reviewing the
+%results on \mgii\ from PKR11, such shifts are rare in
+%outflow models that we have considered.  The only models in PKR11
+%with significant shifts to positive velocity was when there was large 
+%opacity at $v \approx 0 \mkms$ near the source, e.g.\ models that
+%included an ISM component. In essence, this gas modifies the intrinsic
+%line profile of \lya, yielding the standard `double hump' emission and
+%then the blue hump is strongly attenuated by the outflow.
+%[Test this with Lya!]
+
+[It is also worth noting that a strict infall scenario on Mpc scales
 also naturaly predicts a redshifted \lya\ line.  The IGM model of
 \cite{zheng+10}, for example, predicts \lya\ emission will be detectd
-at $v \approx +XX \mkms$ from star-forming galaxies.
+at $v \approx +XX \mkms$ from star-forming galaxies.]
 
-In contrast to our assertions,
-other authors have modeled the \lya\ profiles of LBGs and have
-concluded the redshifted emission is a `clear signature' of an
-outflow.
-The [most extensive] modeling of \lya\ emissoin by LBGas to date has
-been performed by A. Verhomme and collaborators
-\citep{verhommea,verhommeb}.  Their preferred model has been a thin
-expanding shell characterized by the expansion speed $v_{\rm exp}$ and
-total surface density of \ion{H}{1} gas in the shell.  Although the
-shell's dynamics play a role in the \lya\ emission kinematics, the
-[dominant] aspect for the emergent spectrum is the \ion{H}{1} column
-density.  Indeed, they only predict a dominant emission peak at $v \gg
-0 \mkms$ if $\mnhi > 2\sci{20} \cm{-2}$.  For lower values, the
-emission is preferentially at $v \lesssim +100 \mkms$.  The
-explanation is similar to the ISM model described above;  large \nhi\
-values force diffusion of \lya\ in frequency.  Furthermore, their
-models predict substantial \lya\ absorption at $v < 0 \mkms$.  
-Strong absorption is observed in a handful of individual spectra
-\citep[e.g.][]{cb58,dessauges}, but is not evident in the stacked
-spectra of \cite{shapley93} or \cite{steidel+10}.  
-[Why is there sometimes weak \lya\ emission at $v < 0 \mkms$ in LAEs
-at $z \sim 3$?]
-[Read Shapley et al 2009 paper]
-[Redshfited, asymmetric emission is suggestive of an outflow]
-
-Now consider the spatial distribution of \lya\ emission.
-Figure~\ref{fig:SB} shows the predicted surface brightness profile
-vs.\ projected radius for the flat-continuum intrinsic model and with
-no IGM attenuation.  The signal is integrated over velocities $v =
-[-100,400]\mkms$, which corresponds to the majority of predicted line-emission.
+Now consider the predicted patial distribution of \lya\ emission.
+Figure~\ref{fig:SB} shows the surface brightness profile
+versus projected radius for the flat-continuum intrinsic model and with
+no IGM attenuation.  The signal has been integrated over velocities $v =
+[-100,400]\mkms$, which correspond to the majority of line-emission
+(Figure~\ref{fig:1D}).
 Overplotted on the model, at an arbirtrary
@@
 $\mu(\rho) \propto \exp[-\rho/b]$ with $b=20$\,kpc.  
-Although this model appears to be tending toward such an exponential
-profile at very large impact parameter ($\rho > 50$\,kpc), the model
-predict greater flux and a steeper fall-off at small radii.
-In strong constrast to
+%Although this model appears to be tending toward such an exponential
+%profile at very large impact parameter ($\rho > 50$\,kpc), 
+In contrast, the model
+predicts much greater flux and a steeper fall-off at small radii.
+In strong conflict with
 the observations, the clump model predicts that 95\%\ of the
@@
 
-The explanation for the model's failure is twofold:  
+The explanation for the clumpy model's failure is twofold:  
 (1) the covering fraction of the clumps decrease with increasing radius to
@@
 $\tau_{\rm S}(\rho = 60 \, {\rm kpc}) = 10^{-4} \tau_{\rm S}(\rho=1\, {\rm
-  kpc})$.  [Figure?]
+  kpc})$.  
 We further emphasize that the inclusion of an ISM
-component at small radii would not qualitatively alter any of these conclusions.
+component at small radii or a central source of \lya\ emission only
+worsens the disagreement. 
 Instead, one requires additional sources of \lya\ emission at large
-radii or additional opacity in the CGM far beyond that predicgted by
+radii or additional opacity in the CGM far in excess of that predicted by
 the LBG clump model.  We return to these issues in
-$\S$~\ref{sec:later}.
+$\S$~\ref{sec:discussion}.
 
@@
 [Discuss \lya\ emission here]
+In contrast to our assertions,
+
+\section{Discussion}
+\label{sec:discussion}
+
+The results presented in $\S$~\ref{sec:lya} demonstrate that the LBG
+clump model proposed by S+10 cannot (on its own) reproduce the
+observed \lya\ emission that is characteristic of LBG galaxies.  The
+model predicts neither significantly shifted \lya\ emission nor even a
+modest surface brightness of extended emission (Figures~\ref{fig:1D},
+\ref{fig:SB}).  Although our analysis focused on this specific clump
+model, the main findings may be generalized to essenctially all clumpy
+wind models, especially those with a partial covering fraction.  
+[READ CLUMP PAPERS AGAIN]
+In these scenarios, photons do not diffuse in frequency and one
+predicts the majority of emission to occur near systemic with a weak
+tail to positive velocities.  One can reduce the emission at $v
+\approx 0 \mkms$ by assuming a non-isotropic wind or a dusty medium 
+(e.g.\ PKR11), but the flux at $\Delta v \gtrsim +400 \mkms$ would
+remain very weak. Regarding the surface brightness, clumpy wind scenarios 
+are [challenged] to yield significant extended
+emission. This is particularly true for winds that increase in
+velocity with radius or that have a declining covering
+fraction;  one simply has too few photons to scatter at large
+radii.  For a flat continuum source, for example, even a wind spanning
+$v = 0 - 500 \mkms$ could only absorb 2\AA\ of equivalent width.  
+Spread across over 100~kpc$^2$, this implies an essentially negligible
+surface brightness.  The only possible [out] is a model that
+[resonates] with the very bright \lya\ emission from the galaxy, 
+presumably at $v \approx 0 \mkms$.  This would imply clumps at large
+radii with modest velocities, i.e.\ a scenario not driven by an
+outflow.\footnote{Simlar arguments hold for the even brighter \lya\
+  `blobs'.  Indeed, unless one assumes a bright quasar is embedded
+  within these phenomena \citep{hpz+09}, one must include additional
+ sources of emission throughout the blob.}.
+
+[Should we use Dan's algorithm to invert the surface brightness
+profile into a Sobolev solution?]
+
+Before concluding, we comment on two scenarios that may explain the
+observed \lya\ emission for LBGs.  Regarding the \lya\ kinematics, we
+have emphasized that the observed velocity shift demands a high
+opacity gas to force photon diffusion in frequency space.  Following
+\cite{neufeld91}, a static slab of gas with optical depth $\tau_0 >
+10^X$ and $b \approx 10 \mkms$ (i.e.\ $\mnhi > 10^{X} \cm{-2}$) would
+produce significant line-emission at $\Delta v \gtrsim +400 \mkms$.
+
+In contrast to our assertions,
+other authors have modeled the \lya\ profiles of LBGs and have
+concluded the redshifted emission is a `clear signature' of an
+outflow.
+The [most extensive] modeling of \lya\ emissoin by LBGas to date has
+been performed by A. Verhomme and collaborators
+\citep{verhommea,verhommeb}.  Their preferred model has been a thin
+expanding shell characterized by the expansion speed $v_{\rm exp}$ and
+total surface density of \ion{H}{1} gas in the shell.  Although the
+shell's dynamics play a role in the \lya\ emission kinematics, the
+[dominant] aspect for the emergent spectrum is the \ion{H}{1} column
+density.  Indeed, they only predict a dominant emission peak at $v \gg
+0 \mkms$ if $\mnhi > 2\sci{20} \cm{-2}$.  For lower values, the
+emission is preferentially at $v \lesssim +100 \mkms$.  The
+explanation is similar to the ISM model described above;  large \nhi\
+values force diffusion of \lya\ in frequency.  Furthermore, their
+models predict substantial \lya\ absorption at $v < 0 \mkms$.  
+Strong absorption is observed in a handful of individual spectra
+\citep[e.g.][]{cb58,dessauges}, but is not evident in the stacked
+spectra of \cite{shapley93} or \cite{steidel+10}.  
+[Why is there sometimes weak \lya\ emission at $v < 0 \mkms$ in LAEs
+at $z \sim 3$?]
+[Redshfited, asymmetric emission is suggestive of an outflow]
 

### 2012-03-30 Winds/papers/LBG_Lya/lya_lbg.tex
jxp
git-svn-id: https://svn.ucolick.org/xsvn/trunk/radtrans@6694 ac11df5e-a788-c23b-a8e1-c758c323924d

@@
 \cite{neufeld91}, a static slab of gas with optical depth $\tau_0 >
-10^X$ and $b \approx 10 \mkms$ (i.e.\ $\mnhi > 10^{X} \cm{-2}$) would
+10^7$ and $b \approx 10 \mkms$ (i.e.\ $\mnhi > 5\sci{20} \cm{-2}$) would
 produce significant line-emission at $\Delta v \gtrsim +400 \mkms$.  
+Such column densities are characteristics of the Galactic ISM and are
+frequently observed as so-called damped \lya\ systems in the spectra
+of background quasars and gamma-ray burst (GRB) afterglows
+\citep[e.g.][]{phw05,wgp05,pcd+08}.   Indeed, if GRBs trace
+representative star-forming regions of high-$z$ galaxies, one
+regularly observes \ion{H}{1} gas with $\tau_0 > 10^7$ \citep{otherguy,pcd+08}.
 
-In contrast to our assertions,
-other authors have modeled the \lya\ profiles of LBGs and have
-concluded the redshifted emission is a `clear signature' of an
-outflow.
-The [most extensive] modeling of \lya\ emissoin by LBGas to date has
-been performed by A. Verhomme and collaborators
-\citep{verhommea,verhommeb}.  Their preferred model has been a thin
+In this ISM scenario, \lya\ emission will occur at both positive and
+negative velocities relative to systemic.  For LBGs, however, one
+generally observes only emission at $\Delta v \gg 0 \mkms$.  
+One would therefore require the outflow to significantly absorb the
+blue peak of \lya\ emission.  This implies two important predictions: 
+(i) the system has very high opacity to \lya\ at $v \approx 0 \mkms$,
+i.e.\ one expects a DLA absorption profile;
+(ii) an LBG outflow with low opacity should whow \lya\ emission at
+$\Delta v < 0 \mkms$.  On the latter point, \cite{erb+10} recently
+reported on an LBG with weak low-ion absorption that also shows
+significantly \lya\ emission at positive velocities.  [But no DLA!!]
+Similarly, \cite{heckman+11} have published several examples of
+star-forming systems at low-$z$ that have weak low-ion absorption in
+their outflows and also significant blue-shifted \lya\ emission.  
+[COMMENT ON DLA NOW]
+
+[Consider the effects of spectral resolution on \lya\ + DLA]
+
+An alternative model (which need not be entirely distinct) is to
+locate the high opacity \ion{H}{1} gas within the outflow.  This is
+the principal feature of the expanding shell models of
+A. Verhomme and collaborators \citep{verhommea,verhommeb}.  
+Their preferred model has been a thin
 expanding shell characterized by the expansion speed $v_{\rm exp}$ and
@@
 spectra of \cite{shapley93} or \cite{steidel+10}.  
-[Why is there sometimes weak \lya\ emission at $v < 0 \mkms$ in LAEs
-at $z \sim 3$?]
-[Redshfited, asymmetric emission is suggestive of an outflow]
+[FOLLOW THE WEAK METALS, e.g. 1808]
+
+Neither of the models proposed above are likely to yield significant
+spatially-extended \lya\ emission.  In fact, we consider it very
+difficult ot construct a clumpy or diffuse medium model that would
+reproduce the observed surface brightness profile of S+11.  We suspect
+instead that the diffuse emission is generated by sources (e.g.\
+satellite galaxies) that surround the LBG.  Indeed, \cite{kasen+11}
+predict from cosmological simulations of star-forming galaxies very
+similar average emission profiles from XXX.
+
+[FINISH WITH A BRIEF DISCUSSION ON IMPLICATIONS FOR THE CLUMP OUTFLOW]
 
